### 2020-01-08 appendix.Rmd
Appendix mignozzetti 01/08

---
title: "2_preprocessing"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Adding articles

```{r}
# Paper 343
dat <- data.frame(
  id = 343,
  published = 'Yes',
  title = 'Government spending and legislative organization: quasi-experimental evidence from germany',
  author = 'Egger and Koethenbuerger',
  year = 2010,
  journal = 'American Economic Journal: Applied Economics',
  web = 'https://www.jstor.org/stable/25760238',
  table = NA,
  column = NA,
  indepvar = NA,
  indepvar2 = NA,
  depvar = NA,
  depvar2 = NA,
  coef = NA,
  SE = NA
)

# Paper 367
dat <- rbind(dat,
  data.frame(
  id = 367,
  published = 'Yes',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  SE = 0.624/3.10
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  SE = 0.01262/2.12
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  SE = 0.003627/2.51
))

# Paper 1390
dat <- rbind(dat,
  data.frame(
  id = 1390,
  published = 'Yes',
  title = 'Electoral Systems and Public Spending',
  author = 'Milesi-Ferretti, Perotti, and Rostagno',
  year = 2001,
  journal = 'The Quarterly Journal of Economics',
  web = 'https://www.jstor.org/stable/pdf/2696437.pdf',
  table = 5,
  column = 1,
  indepvar = 'Log Avg Dist Magnitude',
  indepvar2 = 'logN',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 1.05,
  SE = 1.05/1.10
))

# Paper 1390
dat <- rbind(dat,
  data.frame(
  id = 1390,
  published = 'Yes',
  title = 'Electoral Systems and Public Spending',
  author = 'Milesi-Ferretti, Perotti, and Rostagno',
  year = 2001,
  journal = 'The Quarterly Journal of Economics',
  web = 'https://www.jstor.org/stable/pdf/2696437.pdf',
  table = 5,
  column = 4,
  indepvar = 'Log Avg Dist Magnitude',
  indepvar2 = 'logN',
  depvar = 'Share transfer GDP',
  depvar2 = 'PCTTRF',
  coef = 1.70,
  SE = 1.70/3.49
))

# Paper 997
dat <- rbind(dat,
  data.frame(
  id = 997,
  published = 'No',
  title = 'Local government expenditure and council size: quasi-experimental evidence from japan',
  author = 'Hirota and Yunoue',
  year = 2012,
  journal = NA,
  web = 'https://mpra.ub.uni-muenchen.de/42799/1/MPRA_paper_42799.pdf',
  table = 3,
  column = 9,
  indepvar = 'logN',
  indepvar2 = 'logN',
  depvar = 'logExp',
  depvar2 = 'logExp',
  coef = 1.229,
  SE = 0.101
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'No',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  SE = 2.066/7.014
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'S/H',
  indepvar2 = 'KN',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = -7.612,
  SE = 5.354
))

dat <- rbind(dat,
  data.frame(
  id = 1309,
  published = 'Yes',
  title = 'Rethinking ward and at-large elections in cities: total spending, the number of locations of selected city services, and policy types',
  author = 'Langbein, Crewson, and Brasher',
  year = 1996,
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007%2FBF00153234.pdf',
  table = 1,
  column = 1,
  indepvar = 'Number on city council',
  indepvar2 = 'N',
  depvar = 'Expenditures per capita',
  depvar2 = 'ExpPC',
  coef = 34.95,
  SE = 34.95/3.73
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.1127,
  SE = 0.0373
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.82,
  SE = 0.19
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.97,
  SE = 0.74
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -1.4,
  SE = 0.64
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 8.3,
  SE = 2.35
))

dat <- rbind(dat,
  data.frame(
  id = 439,
  published = 'Yes',
  title = 'Legislative term limits and state spending',
  author = 'Erler',
  year = 2007,
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/27698198',
  table = 2,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 3.93,
  SE = 1.18
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.136,
  SE = 0.136/2.92
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 5,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.159,
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 231,
  published = 'Yes',
  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
  author = 'Baskaran',
  year = 2013,
  journal = 'European Journal of Political Economy',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
  table = 3,
  column = 4,
  indepvar = 'Parliament seats',
  indepvar2 = 'N',
  depvar = 'Real Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.974,
  SE = 0.974/1.743
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size lower chamber',
  indepvar2 = 'N',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.0609,
  SE = 0.0117
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size upper chamber',
  indepvar2 = 'K',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.04,
  SE = 0.0132
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.003,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 2,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.004,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 4,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.174,
  SE = 0.085
))

dat <- rbind(dat,
  data.frame(
  id = 176,
  published = 'Yes',
  title = 'Local intergovernmental competition and the law of 1/n',
  author = 'Crowley',
  year = 2015,
  journal = 'Southern Economic Association',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.4284/0038-4038-2013.075',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -180.382,
  SE = 27.822
))

dat <- rbind(dat,
  data.frame(
  id = 176,
  published = 'Yes',
  title = 'Local intergovernmental competition and the law of 1/n',
  author = 'Crowley',
  year = 2015,
  journal = 'Southern Economic Association',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.4284/0038-4038-2013.075',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 365.621,
  SE = 55.812
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.21,
  SE = 4.051
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -0.351,
  SE = 0.745
))

dat <- rbind(dat,
  data.frame(
  id = 8,
  published = 'Yes',
  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
  author = 'Lewis',
  year = 2019,
  journal = 'Studies in Comparative International Development',
  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
  table = 4,
  column = NA,
  indepvar = 'Legislature size',
  indepvar2 = 'N',
  depvar = 'Log per capita total expenditure',
  depvar2 = 'logExpPC',
  coef = -0.174,
  SE = (-0.174+0.245)/1.96
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.851,
  SE = 1.395
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 19.74,
  SE = 8.406
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  title = 'Legislative fragmentation and government spending in presidential democracies: bringing ideological polarization into the picture',
  author = 'Höhmann',
  year = 2017,
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 1,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 1,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.077,
  SE = 0.028
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 0.0164,
  SE = 1.313
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 38.44,
  SE = 19.23
))
```

### 2020-04-17 appendix/appendixV5.Rmd
Base to ggplot2. Landscape page.

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document 
---

```{=latex}
\tableofcontents
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Search criteria

### Search terms

XXXX

### Searched databases

XXXX To Catarina: name and URL of database searched

### Summary total results

XXXX To Catarina: put here results per database, cross-matching, anything else

### Exclusion criteria

#### Exclusion title and abstract

XXXX To Catarina: what criteria for first round exclusions?

#### Exclusion reading

XXXX To Catarina: criteria second round exclusions

#### Exclusion analysis

For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:

1. Matched treatment variable:
  + N: Number Legislators Lower House
  + logN: Log Number Legislators Lower House
  + K: Number Legislators Upper House

2. Matched outcome variable:
  + ExpPC: Expenditure Per Capita
  + logExpPC: Log Expenditure Per Capita
  + PCTGDP: Percent GDP Public Expenditure

### PRISM

- Number of articles matching the search criteria: XXXX
- Number of articles excluded after title and abstract: XXXX
- Number of articles excluded after reading: XXXX
- Number of articles excluded before analysis: 3
- Number of articles excluded during the analysis: 0

We have 26 articles in the meta-analysis.

## Meta-analysis dataset

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).

## Adding articles

```{r global_options, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
} 
lapply(pkgs, installIfNot)

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position

```

```{r, echo=FALSE, include=FALSE}

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Total Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.01262/2.12
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.004964,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004964/2.9
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.01134,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01134/4.52
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.00559,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.00559/2.39
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003627/2.51
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.000517,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.000517/0.47
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.016946,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.016946/8.65
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.012337,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.012337/6.65
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.018
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.229,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.455,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.038
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.411,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.049
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.053
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.317
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.185,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.305
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.235,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.336
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 5,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.374,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.064
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 6,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.811,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.181
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 7,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.795,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.176
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 8,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.849,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.238
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 4,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0135,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0121
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.009,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.011,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.04,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.03,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 3,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.02,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Brazil',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  authoryear = 'Lledo (2003)',
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  scoef = 'N',
  scoefsig = NA,
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 4,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.001,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 3,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.001,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 1,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.276,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.276/7.185
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 2,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.295,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.545
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.066/7.014
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 4,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.012,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.012/6.701
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 5,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.468,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.468/8.251
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 2,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = -0.011,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 5,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.007,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.007
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 6,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 7,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 10,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.012,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.007
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 2,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.021,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.011
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 3,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.009
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 4,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.006
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 6,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.03,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.026
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 7,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.030,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.026
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 8,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.039,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.021
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 9,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.0127,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.014
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 0,  
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 10,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.1127,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0373
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 1,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.276,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0384
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 2,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.3021,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0383
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.3203,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0384
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.82,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.19
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 1,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -1.7,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.31
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 2,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -2.37,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.37
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 3,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -2.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.37
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.97,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.74
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 1,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 5.9,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.64
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 2,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 5.75,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.73
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 3,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 6.96,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.22
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -2.04,
  scoef = 'N',
  scoefsig = NA,
  SE = 1.33
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -1.40,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.64
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 26.09,
  scoef = 'P',
  scoefsig = 'P',
  SE = 7.45
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 8.3,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.35
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 2,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 5.14,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.53
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 3,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.78,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.9
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 2,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 20.38,
  scoef = 'P',
  scoefsig = 'P',
  SE = 6.47
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 3,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.87,
  scoef = 'P',
  scoefsig = 'P',
  SE = 1.83
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 4,
  column = 4,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 26.75,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.21
))

dat <- rbind(dat,
  data.frame(
  id = 439,
  published = 'Yes',
  usemeta = 1,
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Legislative term limits and state spending',
  author = 'Erler',
  year = 2007,
  authoryear = 'Erler (2007)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/27698198',
  table = 2,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 3.93,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.18
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.136,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.136/2.92
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 1,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.2319,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.2319/4.56
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 2,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.1443,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.1443/2.91
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.1594,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.1443/3.05
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 5,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.2259,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.2259/4.04
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 5,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.159,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 6,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.147,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 7,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.09,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.038
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 8,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.081,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.039
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 9,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.088,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.038
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 1,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.21,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.023
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 2,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = .157,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 3,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.199,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.04
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Finland',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 4,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.169,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 231,
  published = 'Yes',
  usemeta = 1, 
  method = 'IV',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Germany',
  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
  author = 'Baskaran',
  year = 2013,
  authoryear = 'Baskaran (2013)',
  journal = 'European Journal of Political Economy',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
  table = 3,
  column = 4,
  indepvar = 'Parliament seats',
  indepvar2 = 'N',
  depvar = 'Real Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.974,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.974/1.743
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2013,
  authoryear = 'Maldonado (2013)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size lower chamber',
  indepvar2 = 'N',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.0609,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0117
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size upper chamber',
  indepvar2 = 'K',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.04,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0132
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.003,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 3,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.006,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 2,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.004,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 4,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.008,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 4,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.174,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.085
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 1,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.223,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.052
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 2,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.215,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.061
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 3,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.158,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.054
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.21,
  scoef = 'P',
  scoefsig = 'P',
  SE = 4.051
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 2,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.423,
  scoef = 'P',
  scoefsig = NA,
  SE = 18.17
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 3,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 9.594,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.804
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -0.351,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.745
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 2,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 5.975,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.646
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 3,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 7.658,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.922
))

dat <- rbind(dat,
  data.frame(
  id = 8,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Indonesia',
  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
  author = 'Lewis',
  year = 2019,
  authoryear = 'Lewis (2019)',
  journal = 'Studies in Comparative International Development',
  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
  table = 4,
  column = NA,
  indepvar = 'Legislature size',
  indepvar2 = 'N',
  depvar = 'Log per capita total expenditure',
  depvar2 = 'logExpPC',
  coef = -0.174,
  scoef = 'N',
  scoefsig = 'N',
  SE = (-0.174+0.245)/1.96
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.851,
  scoef = 'N',
  scoefsig = NA,
  SE = 1.395
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 2,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -1.689,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.697
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 3,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 7.632,
  scoef = 'N',
  scoefsig = NA,
  SE = 2.309
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 19.74,
  scoef = 'P',
  scoefsig = 'P',
  SE = 8.406
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 2,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 10.06,
  scoef = 'P',
  scoefsig = 'P',
  SE = 3.965
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 3,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 9.062,
  scoef = 'P',
  scoefsig = NA,
  SE = 20.38
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 1, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 1,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 2,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 0, 
  method = 'RDD',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'Local',
  location = 'Germany',
  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 3,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.04,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Australia',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 1,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.077,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.028
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Australia',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 2,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.031,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.022
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 0.0164,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.313
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 38.44,
  scoef = 'P',
  scoefsig = 'P',
  SE = 19.23
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 2,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 37.85,
  scoef = 'P',
  scoefsig = 'P',
  SE = 17.77
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 3,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 25.61,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.48
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 4,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 5.996,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.06
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 5,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 25.56,
  scoef = 'P',
  scoefsig = 'P',
  SE = 13.49
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 6,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 4.693,
  scoef = 'P',
  scoefsig = NA,
  SE = 12.35
))

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
levels(dat$scoef) <- c('Negative', 'Positive')
levels(dat$scoefsig) <- c('Negative', 'Positive')
dat$method <- factor(as.character(dat$method), 
                     levels = c("OLS", "PANEL", "IV", "RDD"))
dat$location2 <- as.character(dat$location)
dat$location2[dat$location2!='World'] = 'Country'
dat$location2 <- factor(as.character(dat$location2), 
                     levels = c("Country", "World"))
dat$agglevel <- factor(as.character(dat$agglevel), 
                     levels = c("Local", "States", "Countries"))
fulldat <- dat
dat <- dat %>%
  filter(usemeta == 1)
```
\newpage
## Descriptive statistics

### Study Year

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
dat %>%
  ggplot(aes(x = as.factor(year))) + 
    geom_bar(color = "black") + 
  labs(x = "",
       y = "") + 
  theme_bw()
```

\newpage
### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()

```

\newpage
### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()

```

\newpage
### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
dat %>%
  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
                                                  'N (lower house legislators)',
                                                  'Log N'))) %>%
  ggplot(aes(x = indepvar2)) + 
    geom_bar(color = "black") + 
  labs(x = "Independent Variables",
       y = "") +
  coord_flip() +
  theme_bw() 
```

\newpage
### Histogram Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()

```

\newpage
### Histogram Standard Errors

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()

```

\newpage
### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
# str(aux$scoef) -- Obs: this line originally was in the main text. Fix? - LMM
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.

\newpage
### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
dat %>%
  ggplot(aes(x=as.factor(elecsys2))) + 
    geom_bar(color = "black") + 
  labs(x = "Electoral system",
       y = "") + 
  theme_bw()
```

\newpage
### Electoral system x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$elecsys2)
chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
```

\newpage
### Independent Variable x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$indepvar2)
chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
```

\newpage
### Dependent variables x Independent variables

```{r, echo=FALSE}
table(dat$scoef, dat$depvar2)
chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
```

\newpage
## Meta-analysis

We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)

f1 <- grid.grab()

```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
#### Electoral system subgroup analysis

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)

```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

\newpage
### PCTGDP x N

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f2 <- grid.grab()

```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x N

This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction = TRUE,
  sm="SMD"
  )

mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f3 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x logN

There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.

### PCTGDP x logN

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- metagen(
  coef, SE, data=aux, 
  studlab=paste(authoryear),
  comb.fixed = FALSE,
  comb.random = TRUE,
  method.tau = "REML",
  hakn = TRUE,
  prediction=TRUE,
  sm="SMD"
  )

mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f4 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x logN

In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- dat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f5 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x K

Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f6 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### PCTGDP x K

This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).

```{r}
# Pooling effects analysis -- PCTGDP x K
aux <- dat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f7 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x K

No studies related the log of per capita expenditure with the size of upper house (K).

\newpage
\blandscape
```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}

#grid.arrange(f1, f2, f3, 
#             f4,f5, f6,
#             f7,
#             ncol = 2,
#             nrow = 4) + rotate()

#grid.arrange(f1,f2) + rotate()
#library(ggplot2)

ggpubr::ggarrange(f1,f2, f3,
                  f4, f5, f6,
                  f7,
#          labels = c("A", "B"),
          ncol = 3, nrow = 3)  + rotate()

#grid.draw(rbind(f1,f2, size = "first"))

#plot_grid(f1,f2 + rremove("x.text"), 
#          labels = c("A", "B"),
#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
```

\elandscape

\newpage
## Meta-Analysis (all coefficients)

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f8 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
#### Electoral system subgroup analysis

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

\newpage
### PCTGDP x N

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f9 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x N

This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f10 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x logN

There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.

### PCTGDP x logN

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f11 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### logExpPC x logN

In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- fulldat %>%
  filter(indepvar2 == 'logN',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f12 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### ExpPC x K

Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f13 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

\newpage
### PCTGDP x K

This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).

```{r}
# Pooling effects analysis -- PCTGDP x K
aux <- fulldat %>%
  filter(indepvar2 == 'K',
         depvar2 == 'PCTGDP')

mod <- metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f14 <- grid.grab()
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### logExpPC x K

No studies related the log of per capita expenditure with the size of upper house (K).

\newpage
### Summary of results
```{r, echo=FALSE, fig.width=20, fig.height=35, fig.cap="test size"}

grid.arrange(f8, f9, f10, 
             f11,f12, f13,
             f14,
             ncol = 2,
             nrow = 4)
#library(ggplot2)

#ggpubr::ggarrange(f1,f2, 
#          labels = c("A", "B"),
#          ncol = 1, nrow = 2)

#grid.draw(rbind(f1,f2, size = "first"))

#plot_grid(f1,f2 + rremove("x.text"), 
#          labels = c("A", "B"),
#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
```

\newpage
## Meta-regressions

### Meta-regressions for Expenditure as a Percentage of the GDP

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='PCTGDP',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
2. Year has null effect.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='PCTGDP',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

For all the coefficients, we have the following results:

1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
3. Unpublished papers tend to have higher coefficients than published papers.
4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.

### Meta-regressions for Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='ExpPC',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Expenditure Per Capita:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has null effect.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
5. When passing from `Local` to `State` level, decreases the detected effects.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='ExpPC',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:

1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
2. Year has now a positive effect on coefficient sizes.
3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
5. All other coeffients were not significant.

### Meta-regressions for the Log of Expenditure Per Capita

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = dat$depvar2=='logExpPC',
            slab = dat$authoryear)
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

We have the following results for the meta-regressions of Log of Expenditure Per Capita:

1. Unpublished papers report a significantly higher coefficient.
2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
3. All other coefficients remained insignificant.

Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha",
            subset = fulldat$depvar2=='logExpPC',
            slab = fulldat$authoryear)
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:

1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
2. All other coefficients remained insignificant.

## Theory of Meta Analysis

There are two main estimators for conducting meta analysis: fixed effects and random effects models. The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect. The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.

In this paper, we use the random effects model. The empirical papers testing the law of 1/n are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
2. **Electoral systems**: Majoritarian, PR, Mixed.
3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.

These sources of heterogeneity have two implications. First, it makes our estimates very disperse. The heterogeneity tests are all but one significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:

\[
T_i \ = \ \theta_i + \varepsilon_i
\]

And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:

\[
T_i \ = \ \mu + \xi_i + \varepsilon_i
\]

And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html]. To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].

## Robustness: Full model meta-regressions combined

In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy (N, K, log of N);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

The results follow below, and show null effect for all variables, including the intercept.

```{r, echo=F, warning=F}
mod <-  rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

```{r}
summary(mod)
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod, progbar = F)
```

In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD). Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:

```{r, echo=F, warning=F}
mod <- rma(yi = coef, 
              sei = SE, 
              data = fulldat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
              test = "knha")
```

```{r}
summary(mod)
```

```{r}
permutest(mod, progbar = F)
```

### 2020-04-20 appendix/appendixV5.Rmd
Further testing

@@
 \newpage
-\blandscape
-```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}
+```{r, echo=FALSE, fig.width=16, fig.height=16, warning = F,message = FALSE}
 
@@
 #          labels = c("A", "B"),
-          ncol = 3, nrow = 3)  + rotate()
+          ncol = 2, nrow = 4)
 
@@
 
-\elandscape
+\newpage
+```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}
+
+#grid.arrange(f1, f2, f3, 
+#             f4,f5, f6,
+#             f7,
+#             ncol = 2,
+#             nrow = 4) + rotate()
+
+#grid.arrange(f1,f2) + rotate()
+#library(ggplot2)
+
+ggpubr::ggarrange(f1,f2, f3,
+                  f4, f5, f6,
+                  f7,
+#          labels = c("A", "B"),
+          ncol = 3, nrow = 3)  + rotate()
+
+#grid.draw(rbind(f1,f2, size = "first"))
+
+#plot_grid(f1,f2 + rremove("x.text"), 
+#          labels = c("A", "B"),
+#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
+```
 
@@
 ### Summary of results
-```{r, echo=FALSE, fig.width=20, fig.height=35, fig.cap="test size"}
-
-grid.arrange(f8, f9, f10, 
-             f11,f12, f13,
+```{r, echo=FALSE, fig.width=17, fig.height=24}
+
+grid.arrange(f8, f9, f11, 
+             f10,f12, f13,
              f14,

### 2020-04-21 appendix/appendixV5.Rmd
ggplot2-esque forestplot

@@
 date: "12/25/2019"
-header-includes:
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
 output: pdf_document
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE)
-
-f1 <- grid.grab()
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f1 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f1
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
 mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3,
-       test.subgroup.random = TRUE)
-
+
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f1b <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f1b
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE)
-f2 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f2 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank()) 
+f2
 
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f3 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f3 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f3
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f4 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f4 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f4
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f5 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f5 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f5
 ```
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f6 <- grid.grab()
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f6 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f6
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f7 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f7 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f7
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE)
-f8 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f8 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f8
+
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
-mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3,
-       test.subgroup.random = TRUE)
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f8b <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank()) 
+f8b
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE)
-f9 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B"))
+
+f9 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank()) 
+f9
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f10 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f10 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f10
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f11 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f11 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f11
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f12 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f12 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f12
 ```
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f13 <- grid.grab()
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f13 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f13
 ```
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
-forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
-       prediction = TRUE, digits.se = 3)
-f14 <- grid.grab()
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f14 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(color = "black") +
+  # Error Bars
+  geom_errorbarh(height = 0.1) +
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank())
+
+f14
 ```
@@
 #          ncol = 1, nrow = 2)
+
+#grid.draw(rbind(f1,f2, size = "first"))
+
+#plot_grid(f1,f2 + rremove("x.text"), 
+#          labels = c("A", "B"),
+#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
+```
+
+\newpage
+```{r, echo=FALSE, fig.width=17, fig.height=24}
+
+#grid.arrange(f8, f9, f11, 
+#             f10,f12, f13,
+#             f14,
+#             ncol = 2,
+#             nrow = 4)
+#library(ggplot2)
+
+print(ggpubr::ggarrange(f8, f9, f11, 
+             f10,f12, f13,
+             f14,
+          ncol = 2,
+          nrow = 4)) + rotate()
+
+#ggpubr::ggarrange(f8) + rotate()
+#ggpubr::ggarrange(f9) + rotate()
 

### 2020-04-21 appendix/appendixV5.Rmd
Saving plots

@@
 pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
-          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra')
+          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')
 
@@
   theme(strip.text.y = element_blank()) 
-
 f1
+ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")
+
 ```
@@
 f2
-
+ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
 ```
@@
 f3
+ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
 ```
@@
 f4
+ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
 ```
@@
 f5
+ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
 ```
@@
 f6
+ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
 ```
@@
 f7
+ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
 ```
@@
           ncol = 2, nrow = 4)
+
+#f1 + rotate()
 
@@
 f8
-
+ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
 ```
@@
 f9
+ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
 ```
@@
 f10
+ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
 ```
@@
 f11
+ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
 ```
@@
 f12
+ggsave("./plots/f12.png", width = 20, height = 10, units = "cm")
 ```
@@
 f13
+ggsave("./plots/f13.png", width = 20, height = 10, units = "cm")
 ```
@@
 f14
+ggsave("./plots/f14.png", width = 20, height = 10, units = "cm")
 ```
@@
 
-grid.arrange(f8, f9, f11, 
-             f10,f12, f13,
-             f14,
-             ncol = 2,
-             nrow = 4)
+#grid.arrange(f8, f9, f11, 
+#             f10,f12, f13,
+#             f14,
+#             ncol = 2,
+#             nrow = 4)
 #library(ggplot2)
+
+blank = ggplot() + 
+  geom_blank() +
+  theme_minimal()
+blank
+ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")
+
+plots = list.files(path = "./plots/", pattern = "*.png") %>%
+  map(~{
+    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
+  })
+
+p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
+p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
+p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
+p_full = image_append(c(p_1, p_2, p_3))
+p_full
+
+#p_full
+
+#ggpubr::ggarrange(plots[[1]],plots[[2]],
+#                  plots[[3]],plots[[4]],
+#                  plots[[5]],plots[[6]],
+#                  plots[[7]],
+#                  nrow = 4, ncol = 2
+#                  )
 

### 2020-04-22 appendix/appendixV5.Rmd
testing manual tex

@@
 date: "12/25/2019"
-output: pdf_document
+output:
+  pdf_document:
+    keep_tex: true
 ---
@@
 
-\newpage
-```{r, echo=FALSE, fig.width=16, fig.height=16, warning = F,message = FALSE}
-
-#grid.arrange(f1, f2, f3, 
-#             f4,f5, f6,
-#             f7,
+```{r, echo=FALSE, fig.width=12.5, fig.height=5}
+
+#grid.arrange(f8, f9, f11, 
+#             f10,f12, f13,
+#             f14,
 #             ncol = 2,
-#             nrow = 4) + rotate()
-
-#grid.arrange(f1,f2) + rotate()
+#             nrow = 4)
 #library(ggplot2)
 
-ggpubr::ggarrange(f1,f2, f3,
-                  f4, f5, f6,
-                  f7,
+blank = ggplot() + 
+  geom_blank() +
+  theme_minimal()
+blank
+ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")
+
+plots = list.files(path = "./plots/", pattern = "*.png") %>%
+  map(~{
+    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
+  })
+
+p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
+p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
+p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
+p_full = image_append(c(p_1, p_2, p_3))
+
+p_full
+
+#p_full
+
+#ggpubr::ggarrange(plots[[1]],plots[[2]],
+#                  plots[[3]],plots[[4]],
+#                  plots[[5]],plots[[6]],
+#                  plots[[7]],
+#                  nrow = 4, ncol = 2
+#                  )
+
+#ggpubr::ggarrange(f1,f2, 
 #          labels = c("A", "B"),
-          ncol = 2, nrow = 4)
-
-#f1 + rotate()
-
-#grid.draw(rbind(f1,f2, size = "first"))
-
-#plot_grid(f1,f2 + rremove("x.text"), 
-#          labels = c("A", "B"),
-#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
-```
-
-\newpage
-```{r, echo=FALSE, fig.width=10, fig.height=10, warning = F,message = FALSE,fig.cap="test size"}
-
-#grid.arrange(f1, f2, f3, 
-#             f4,f5, f6,
-#             f7,
-#             ncol = 2,
-#             nrow = 4) + rotate()
-
-#grid.arrange(f1,f2) + rotate()
-#library(ggplot2)
-
-ggpubr::ggarrange(f1,f2, f3,
-                  f4, f5, f6,
-                  f7,
-#          labels = c("A", "B"),
-          ncol = 3, nrow = 3)  + rotate()
+#          ncol = 1, nrow = 2)
 
@@
 
-\newpage
-### Summary of results
-```{r, echo=FALSE, fig.width=17, fig.height=24}
+```{r, echo=FALSE, fig.width=10, fig.height=1}
 
@@
 
-p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
-p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
-p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
+p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
+p_2 = image_append(c(plots[[13]], plots[[12]], plots[[11]]), stack = T)
+p_3 = image_append(c(plots[[15]],plots[[14]],plots[[15]]), stack = T)
 p_full = image_append(c(p_1, p_2, p_3))
+
 p_full
@@
 #          ncol = 1, nrow = 2)
-
-#grid.draw(rbind(f1,f2, size = "first"))
-
-#plot_grid(f1,f2 + rremove("x.text"), 
-#          labels = c("A", "B"),
-#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
-```
-
-\newpage
-```{r, echo=FALSE, fig.width=17, fig.height=24}
-
-#grid.arrange(f8, f9, f11, 
-#             f10,f12, f13,
-#             f14,
-#             ncol = 2,
-#             nrow = 4)
-#library(ggplot2)
-
-print(ggpubr::ggarrange(f8, f9, f11, 
-             f10,f12, f13,
-             f14,
-          ncol = 2,
-          nrow = 4)) + rotate()
-
-#ggpubr::ggarrange(f8) + rotate()
-#ggpubr::ggarrange(f9) + rotate()
 

### 2020-04-22 appendix/appendixV5.tex
testing manual tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Appendix},
  pdfauthor={Umberto Mignozzetti},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Appendix}
\author{Umberto Mignozzetti}
\date{12/25/2019}

\begin{document}
\maketitle

\tableofcontents

\hypertarget{search-criteria}{%
\subsection{Search criteria}\label{search-criteria}}

\hypertarget{search-terms}{%
\subsubsection{Search terms}\label{search-terms}}

XXXX

\hypertarget{searched-databases}{%
\subsubsection{Searched databases}\label{searched-databases}}

XXXX To Catarina: name and URL of database searched

\hypertarget{summary-total-results}{%
\subsubsection{Summary total results}\label{summary-total-results}}

XXXX To Catarina: put here results per database, cross-matching,
anything else

\hypertarget{exclusion-criteria}{%
\subsubsection{Exclusion criteria}\label{exclusion-criteria}}

\hypertarget{exclusion-title-and-abstract}{%
\paragraph{Exclusion title and
abstract}\label{exclusion-title-and-abstract}}

XXXX To Catarina: what criteria for first round exclusions?

\hypertarget{exclusion-reading}{%
\paragraph{Exclusion reading}\label{exclusion-reading}}

XXXX To Catarina: criteria second round exclusions

\hypertarget{exclusion-analysis}{%
\paragraph{Exclusion analysis}\label{exclusion-analysis}}

For the articles that passed the first two filters, we looked into the
tables and the reported coefficients. We kept articles in this step
based on two criteria:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Matched treatment variable:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  N: Number Legislators Lower House
\item
  logN: Log Number Legislators Lower House
\item
  K: Number Legislators Upper House
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Matched outcome variable:
\end{enumerate}

\begin{itemize}
\tightlist
\item
  ExpPC: Expenditure Per Capita
\item
  logExpPC: Log Expenditure Per Capita
\item
  PCTGDP: Percent GDP Public Expenditure
\end{itemize}

\hypertarget{prism}{%
\subsubsection{PRISM}\label{prism}}

\begin{itemize}
\tightlist
\item
  Number of articles matching the search criteria: XXXX
\item
  Number of articles excluded after title and abstract: XXXX
\item
  Number of articles excluded after reading: XXXX
\item
  Number of articles excluded before analysis: 3
\item
  Number of articles excluded during the analysis: 0
\end{itemize}

We have 26 articles in the meta-analysis.

\hypertarget{meta-analysis-dataset}{%
\subsection{Meta-analysis dataset}\label{meta-analysis-dataset}}

The meta-analytic data is comprised of two datasets. The first dataset
has the main coefficients that were reported in the paper. XXXX (Copiar
da parte de métodos).

\hypertarget{adding-articles}{%
\subsection{Adding articles}\label{adding-articles}}

\newpage

\hypertarget{descriptive-statistics}{%
\subsection{Descriptive statistics}\label{descriptive-statistics}}

\hypertarget{study-year}{%
\subsubsection{Study Year}\label{study-year}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Study Year Frequencies}
\end{figure}

\newpage

\hypertarget{published}{%
\subsubsection{Published?}\label{published}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Was the study published?}
\end{figure}

\newpage

\hypertarget{dependent-variables}{%
\subsubsection{Dependent variables}\label{dependent-variables}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Dependent variables across the law of 1/n studies}
\end{figure}

\newpage

\hypertarget{independent-variables}{%
\subsubsection{Independent variables}\label{independent-variables}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Independent variables across the law of 1/n studies}
\end{figure}

\newpage

\hypertarget{histogram-coefficients}{%
\subsubsection{Histogram Coefficients}\label{histogram-coefficients}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{Histogram Coefficients}
\end{figure}

\newpage

\hypertarget{histogram-standard-errors}{%
\subsubsection{Histogram Standard
Errors}\label{histogram-standard-errors}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-7-1.pdf}
\caption{Histogram Standard Errors}
\end{figure}

\newpage

\hypertarget{sign-coefficients}{%
\subsubsection{Sign Coefficients}\label{sign-coefficients}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Coefficient Sign?}
\end{figure}

A general test of the theory would be to study whether the coefficients
are positive or negative. Note that the law of 1/n would pose that we
should have a positive influence of legislature size on expenditure. To
test this theory, we run a Binomial One-Proportion Z-test. For the
number of legislators in the lower house (N), the results follow below.

\begin{verbatim}
## 
##  Exact binomial test
## 
## data:  table(aux$scoef)[1] and sum(table(aux$scoef))
## number of successes = 11, number of trials = 21, p-value = 1
## alternative hypothesis: true probability of success is not equal to 0.5
## 95 percent confidence interval:
##  0.2978068 0.7428694
## sample estimates:
## probability of success 
##              0.5238095
\end{verbatim}

Therefore, the most elementary test we could run, a sign direction test,
tells us that the law of 1/n does not hold for our sample. For the
number of legislators in the upper house (K), the results follow below.

\begin{verbatim}
## 
##  Exact binomial test
## 
## data:  table(aux$scoef)[1] and sum(table(aux$scoef))
## number of successes = 1, number of trials = 9, p-value = 0.03906
## alternative hypothesis: true probability of success is not equal to 0.5
## 95 percent confidence interval:
##  0.002809137 0.482496515
## sample estimates:
## probability of success 
##              0.1111111
\end{verbatim}

Here, the law of 1/n holds. However, the effect goes in a direction
different from the predicted in the law of k/n paper.

\newpage

\hypertarget{electoral-system}{%
\subsubsection{Electoral system}\label{electoral-system}}

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Electoral system}
\end{figure}

\newpage

\hypertarget{electoral-system-x-sign-coefficient}{%
\subsubsection{Electoral system x Sign
Coefficient}\label{electoral-system-x-sign-coefficient}}

\begin{verbatim}
##           
##            Majoritarian Non-Majoritarian
##   Negative            5                8
##   Positive           13               10
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's Chi-squared test with simulated p-value (based on 2000
##  replicates)
## 
## data:  table(dat$scoef, dat$elecsys2)
## X-squared = 1.0836, df = NA, p-value = 0.4883
\end{verbatim}

\newpage

\hypertarget{independent-variable-x-sign-coefficient}{%
\subsubsection{Independent Variable x Sign
Coefficient}\label{independent-variable-x-sign-coefficient}}

\begin{verbatim}
##           
##             K  N logN
##   Negative  1 11    1
##   Positive  8 10    5
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's Chi-squared test with simulated p-value (based on 2000
##  replicates)
## 
## data:  table(dat$scoef, dat$indepvar2)
## X-squared = 5.8309, df = NA, p-value = 0.06397
\end{verbatim}

\newpage

\hypertarget{dependent-variables-x-independent-variables}{%
\subsubsection{Dependent variables x Independent
variables}\label{dependent-variables-x-independent-variables}}

\begin{verbatim}
##           
##            ExpPC PCTGDP logExpPC
##   Negative     6      4        3
##   Positive    12      7        4
\end{verbatim}

\begin{verbatim}
## 
##  Pearson's Chi-squared test with simulated p-value (based on 2000
##  replicates)
## 
## data:  table(dat$scoef, dat$depvar2)
## X-squared = 0.19858, df = NA, p-value = 1
\end{verbatim}

\newpage

\hypertarget{meta-analysis}{%
\subsection{Meta-analysis}\label{meta-analysis}}

We combined the three independent variables (N, logN, and K) with the
levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This
formed a 3x3 possibility for our analysis.

\hypertarget{exppc-x-n}{%
\subsubsection{ExpPC x N}\label{exppc-x-n}}

\begin{verbatim}
##                                 SMD             95%-CI %W(random)
## Crowley (2019)              -0.3510 [-1.8112;  1.1092]        5.3
## Lee and Park (2018)         -0.8510 [-3.5851;  1.8831]        2.1
## Lee (2016)                   0.0164 [-2.5570;  2.5898]        2.4
## Kessler (2014)               0.1740 [ 0.0074;  0.3406]       13.1
## Bjedov et al. (2014)        -0.0030 [-0.0226;  0.0166]       13.4
## Baskaran (2013)              0.9740 [-0.1212;  2.0692]        7.3
## Erler (2007)                 3.9300 [ 1.6172;  6.2428]        2.8
## Chen and Malhotra (2007)    -2.0400 [-4.6468;  0.5668]        2.3
## Fiorino and Ricciuti (2007)  0.2130 [ 0.1777;  0.2483]       13.4
## Primo (2006)                -0.8200 [-1.1924; -0.4476]       12.2
## Matsusaka (2005)            -0.9600 [-1.3128; -0.6072]       12.3
## Schaltegger and Feld (2009)  0.0010 [-0.0010;  0.0030]       13.4
## 
## Number of studies combined: k = 12
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0699 [-0.6712; 0.5314] -0.26  0.8028
## Prediction interval          [-1.5540; 1.4142]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.3690 [0.1794; 4.7570]; tau = 0.6075 [0.4236; 2.1810];
##  I^2 = 94.7% [92.3%; 96.3%]; H = 4.34 [3.61; 5.21]
## 
## Test of heterogeneity:
##       Q d.f.  p-value
##  206.92   11 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-16-1.pdf}
\caption{Effect of lower houses size (N) on Per Capita Expenditure
(ExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 94.68.
\item
  The Random effects modem SMD estimated is \$g = \$ -0.07 (\(SE =\)
  0.273).
\item
  The prediction interval ranges from -1.55 to 1.41. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{electoral-system-subgroup-analysis}{%
\paragraph{Electoral system subgroup
analysis}\label{electoral-system-subgroup-analysis}}

The law of 1/n was created for majoritarian systems. In the theoretical
section below, we explain why the argument have potential issues when
applied to non-majoritarian electoral systems. We estimated a subgroup
analysis using a binary electoral system.

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{Subgroup Analysis of (N) x (ExpPC), controlling by electoral
system}
\end{figure}

Therefore, we can see that the hypothesis that majoritarian systems
produce systematic positive effects was disproved. The majoritarian
systems in the sample had a random effects model estimate of -0.25,
while the random effects model in the non-majoritarian subgroup fitted a
value of 0.08. Both are non-significant, but they reassure us that the
absense of effect is not caused by pooling multiple types of electoral
systems.

\newpage

\hypertarget{pctgdp-x-n}{%
\subsubsection{PCTGDP x N}\label{pctgdp-x-n}}

This model fits the random effects for the percentage of GDP as public
expenditure as the main outcome, and the size of lower house as the main
treatment variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x N}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'N'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                               SMD             95%-CI %W(random)
## Bjedov et al. (2014)      -0.0040 [-0.0432;  0.0352]       15.1
## Maldonado (2013)          -0.0609 [-0.0838; -0.0380]       19.5
## Mukherjee (2003)           0.0030 [ 0.0010;  0.0050]       23.0
## Bradbury and Crain (2001)  0.0036 [ 0.0008;  0.0065]       23.0
## Ricciuti (2004)            0.0140 [-0.0095;  0.0375]       19.4
## 
## Number of studies combined: k = 5
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0083 [-0.0450; 0.0285] -0.62  0.5667
## Prediction interval          [-0.1054; 0.0889]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0008 [0.0002; 0.0072]; tau = 0.0275 [0.0129; 0.0849];
##  I^2 = 87.1% [72.2%; 94.0%]; H = 2.78 [1.90; 4.08]
## 
## Test of heterogeneity:
##      Q d.f.  p-value
##  30.97    4 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-19-1.pdf}
\caption{Effect of lower houses size (N) on percentage of public
expenditure GDP (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 87.08.
\item
  The Random effects modem SMD estimated is \$g = \$ -0.01 (\(SE =\)
  0.013).
\item
  The prediction interval ranges from -0.11 to 0.09. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{logexppc-x-n}{%
\subsubsection{logExpPC x N}\label{logexppc-x-n}}

This model estimates the Log of Per Capita Expenditure as the dependent
variable, and the number of lower house legislators as the treatment
variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- logExpPC x N}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'N'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'logExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(}
\NormalTok{  coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
  \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
  \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
  \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
  \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{prediction =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{sm=}\StringTok{"SMD"}
\NormalTok{  )}

\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                              SMD             95%-CI %W(random)
## Lewis (2019)             -0.1740 [-0.2450; -0.1030]       24.3
## Höhmann (2017)           -0.0300 [-0.0496; -0.0104]       26.6
## Drew and Dollery (2017)   0.0770 [ 0.0221;  0.1319]       25.3
## Pettersson-Lidbom (2012) -0.1590 [-0.2394; -0.0786]       23.7
## 
## Number of studies combined: k = 4
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0686 [-0.2560; 0.1188] -1.17  0.3282
## Prediction interval          [-0.6179; 0.4807]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0128 [0.0034; 0.1933]; tau = 0.1133 [0.0584; 0.4396];
##  I^2 = 92.5% [84.1%; 96.5%]; H = 3.66 [2.51; 5.34]
## 
## Test of heterogeneity:
##      Q d.f.  p-value
##  40.11    3 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-21-1.pdf}
\caption{Effect of lower houses size (N) on log of per capita
expenditure (logExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 92.52.
\item
  The Random effects modem SMD estimated is \$g = \$ -0.07 (\(SE =\)
  0.059).
\item
  The prediction interval ranges from -0.62 to 0.48. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{exppc-x-logn}{%
\subsubsection{ExpPC x logN}\label{exppc-x-logn}}

There were no studies that had per capita expenditure in the dependent
variable and log of lower house size in the treatment variable.

\hypertarget{pctgdp-x-logn}{%
\subsubsection{PCTGDP x logN}\label{pctgdp-x-logn}}

This meta-regression investigates the percentage of GDP as public
expenditure as the dependent variable and the log lower house size
(logN) as the treatment variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x logN}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'logN'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(}
\NormalTok{  coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
  \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
  \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
  \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
  \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{sm=}\StringTok{"SMD"}
\NormalTok{  )}

\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                         SMD            95%-CI %W(random)
## Baqir (1999)         2.0660 [ 1.4887; 2.6433]       40.8
## Lledo (2003)        -4.6900 [-9.9427; 0.5627]       17.7
## Stein et al. (1998)  0.0109 [-0.0171; 0.0389]       41.5
## 
## Number of studies combined: k = 3
## 
##                         SMD              95%-CI    t p-value
## Random effects model 0.0203 [ -7.1961;  7.2367] 0.01  0.9914
## Prediction interval         [-36.2058; 36.2465]             
## 
## Quantifying heterogeneity:
##  tau^2 = 5.3156 [0.5756; >100.0000]; tau = 2.3056 [0.7587; >10.0000];
##  I^2 = 96.1% [91.8%; 98.2%]; H = 5.08 [3.48; 7.42]
## 
## Test of heterogeneity:
##      Q d.f.  p-value
##  51.65    2 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-23-1.pdf}
\caption{Effect of log lower houses size (logN) on the GDP share of
public expenditure (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 96.13.
\item
  The Random effects modem SMD estimated is \$g = \$ 0.02 (\(SE =\)
  1.677).
\item
  The prediction interval ranges from -36.21 to 36.25. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{logexppc-x-logn}{%
\subsubsection{logExpPC x logN}\label{logexppc-x-logn}}

In this specification, we study the log of per capita expenditure
(logExpPC) as a function of the log of lower house size (logN).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- logExpPC x logN}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'logN'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'logExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                     SMD           95%-CI %W(random)
## MacDonald (2008) 0.1360 [0.0447; 0.2273]       31.9
## Baqir (2002)     0.1127 [0.0396; 0.1858]       34.2
## Baqir (1999)     0.3020 [0.2269; 0.3771]       33.9
## 
## Number of studies combined: k = 3
## 
##                         SMD            95%-CI    t p-value
## Random effects model 0.1844 [-0.0738; 0.4425] 3.07  0.0916
## Prediction interval         [-1.2580; 1.6267]             
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0093 [0.0014; 0.4193]; tau = 0.0964 [0.0372; 0.6476];
##  I^2 = 85.9% [59.0%; 95.2%]; H = 2.66 [1.56; 4.54]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  14.18    2  0.0008
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{Effect of log lower houses size (logN) on the log of per capita
government expenditure (logExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 85.9.
\item
  The Random effects modem SMD estimated is \$g = \$ 0.18 (\(SE =\)
  0.06). \textbf{This model is significant at the 10\% confidence
  level.}
\item
  The prediction interval ranges from -1.26 to 1.63. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{exppc-x-k}{%
\subsubsection{ExpPC x K}\label{exppc-x-k}}

Now we are investigating the upper house size (K). In this model, we
investigate the effect of upper house size on expenditure per capita
(ExpPC).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- ExpPC x K}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'K'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'ExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                                    SMD             95%-CI %W(random)
## Crowley (2019)                  8.2100 [ 0.2702; 16.1498]       20.0
## Lee and Park (2018)            19.7400 [ 3.2645; 36.2155]       13.8
## Lee (2016)                     38.4400 [ 0.7499; 76.1301]        5.1
## Bradbury and Stephenson (2009)  0.6240 [ 0.2295;  1.0185]       23.1
## Chen and Malhotra (2007)       26.0900 [11.4883; 40.6917]       15.1
## Primo (2006)                    0.9700 [-0.4804;  2.4204]       23.0
## 
## Number of studies combined: k = 6
## 
##                          SMD              95%-CI    t p-value
## Random effects model 10.6134 [ -2.6210; 23.8479] 2.06  0.0943
## Prediction interval          [-21.1303; 42.3571]             
## 
## Quantifying heterogeneity:
##  tau^2 = 104.2124 [20.3551; >1042.1236]; tau = 10.2084 [4.5117; >32.2819];
##  I^2 = 79.4% [55.1%; 90.6%]; H = 2.20 [1.49; 3.26]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  24.31    5  0.0002
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-27-1.pdf}
\caption{Effect of upper house size (K) on the per capita government
expenditure (ExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 79.43.
\item
  The Random effects modem SMD estimated is \$g = \$ 10.61 (\(SE =\)
  5.148).
\item
  The prediction interval ranges from -21.13 to 42.36. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{pctgdp-x-k}{%
\subsubsection{PCTGDP x K}\label{pctgdp-x-k}}

This model looks into the effect of upper house size (K) on the public
expenditure share of the GDP (PCTGDP).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x K}
\NormalTok{aux <-}\StringTok{ }\NormalTok{dat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'K'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                               SMD             95%-CI %W(random)
## Maldonado (2012)          -0.0400 [-0.0659; -0.0141]       31.3
## Bradbury and Crain (2001)  0.0126 [ 0.0010;  0.0243]       36.4
## Ricciuti (2004)            0.0160 [-0.0075;  0.0395]       32.3
## 
## Number of studies combined: k = 3
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0027 [-0.0793; 0.0738] -0.15  0.8915
## Prediction interval          [-0.4284; 0.4229]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0008 [0.0001; 0.0388]; tau = 0.0284 [0.0101; 0.1970];
##  I^2 = 85.8% [58.6%; 95.1%]; H = 2.65 [1.55; 4.53]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  14.07    2  0.0009
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-29-1.pdf}
\caption{Effect of upper house size (K) on the public expenditure share
of the GDP (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 85.79.
\item
  The Random effects modem SMD estimated is \$g = \$ 0 (\(SE =\) 0.018).
\item
  The prediction interval ranges from -0.43 to 0.42. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{logexppc-x-k}{%
\subsubsection{logExpPC x K}\label{logexppc-x-k}}

No studies related the log of per capita expenditure with the size of
upper house (K).

\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-30-2.pdf}
%\includegraphics[width=49.21in]{appendixV5_files/figure-latex/unnamed-chunk-30-1}

\includegraphics[width=20.21in]{plots/f1.png}

\newpage

\hypertarget{meta-analysis-all-coefficients}{%
\subsection{Meta-Analysis (all
coefficients)}\label{meta-analysis-all-coefficients}}

\hypertarget{exppc-x-n-1}{%
\subsubsection{ExpPC x N}\label{exppc-x-n-1}}

\begin{verbatim}
## Warning in rma.uni(yi = TE[sel], sei = seTE[sel], method = method.tau, control
## = control): Ratio of largest to smallest sampling variance extremely large. May
## not be able to obtain stable results.
\end{verbatim}

\begin{verbatim}
##                                 SMD             95%-CI %W(random)
## Crowley (2019)              -0.3510 [-1.8112;  1.1092]        2.0
## Crowley (2019)               5.9750 [ 0.7889; 11.1611]        0.3
## Crowley (2019)               7.6580 [-0.0290; 15.3450]        0.2
## Lee and Park (2018)         -0.8510 [-3.5851;  1.8831]        0.9
## Lee and Park (2018)         -1.6890 [-3.0551; -0.3229]        2.1
## Lee and Park (2018)          7.6320 [ 3.1064; 12.1576]        0.4
## Lee (2016)                   0.0164 [-2.5570;  2.5898]        1.0
## Kessler (2014)               0.1740 [ 0.0074;  0.3406]        3.6
## Kessler (2014)               0.2230 [ 0.1211;  0.3249]        3.6
## Kessler (2014)               0.2150 [ 0.0954;  0.3346]        3.6
## Kessler (2014)               0.1580 [ 0.0522;  0.2638]        3.6
## Bjedov et al. (2014)        -0.0030 [-0.0226;  0.0166]        3.6
## Bjedov et al. (2014)        -0.0060 [-0.0256;  0.0136]        3.6
## Baskaran (2013)              0.9740 [-0.1212;  2.0692]        2.5
## Erler (2007)                 3.9300 [ 1.6172;  6.2428]        1.2
## Chen and Malhotra (2007)    -2.0400 [-4.6468;  0.5668]        1.0
## Chen and Malhotra (2007)    -1.4000 [-2.6544; -0.1456]        2.3
## Fiorino and Ricciuti (2007)  0.2130 [ 0.1777;  0.2483]        3.6
## Fiorino and Ricciuti (2007)  0.2290 [ 0.1565;  0.3015]        3.6
## Fiorino and Ricciuti (2007)  0.4550 [ 0.3805;  0.5295]        3.6
## Fiorino and Ricciuti (2007)  0.4110 [ 0.3150;  0.5070]        3.6
## Fiorino and Ricciuti (2007)  0.2260 [ 0.1221;  0.3299]        3.6
## Fiorino and Ricciuti (2007)  0.2130 [-0.4083;  0.8343]        3.1
## Fiorino and Ricciuti (2007)  0.1850 [-0.4128;  0.7828]        3.2
## Fiorino and Ricciuti (2007)  0.2350 [-0.4235;  0.8935]        3.1
## Fiorino and Ricciuti (2007)  0.3740 [ 0.2486;  0.4994]        3.6
## Fiorino and Ricciuti (2007)  0.8110 [ 0.4562;  1.1658]        3.4
## Fiorino and Ricciuti (2007)  0.7950 [ 0.4500;  1.1400]        3.5
## Fiorino and Ricciuti (2007)  0.8490 [ 0.3825;  1.3155]        3.3
## Primo (2006)                -0.8200 [-1.1924; -0.4476]        3.4
## Primo (2006)                -1.7000 [-2.3076; -1.0924]        3.2
## Primo (2006)                -2.3700 [-3.0952; -1.6448]        3.0
## Primo (2006)                -2.0300 [-2.7552; -1.3048]        3.0
## Matsusaka (2005)            -0.9600 [-1.3128; -0.6072]        3.4
## Schaltegger and Feld (2009)  0.0010 [-0.0010;  0.0030]        3.6
## Schaltegger and Feld (2009) -0.0010 [-0.0030;  0.0010]        3.6
## 
## Number of studies combined: k = 36
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0169 [-0.4166; 0.3829] -0.09  0.9322
## Prediction interval          [-1.7588; 1.7250]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.6959 [0.7202; 4.3553]; tau = 0.8342 [0.8486; 2.0869];
##  I^2 = 95.3% [94.2%; 96.1%]; H = 4.60 [4.16; 5.08]
## 
## Test of heterogeneity:
##       Q d.f.  p-value
##  739.53   35 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-32-1.pdf}
\caption{Effect of lower houses size (N) on Per Capita Expenditure
(ExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 95.27.
\item
  The Random effects modem SMD estimated is \$g = \$ -0.02 (\(SE =\)
  0.197).
\item
  The prediction interval ranges from -1.76 to 1.73. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{electoral-system-subgroup-analysis-1}{%
\paragraph{Electoral system subgroup
analysis}\label{electoral-system-subgroup-analysis-1}}

The law of 1/n was created for majoritarian systems. In the theoretical
section below, we explain why the argument have potential issues when
applied to non-majoritarian electoral systems. We estimated a subgroup
analysis using a binary electoral system.

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-33-1.pdf}
\caption{Subgroup Analysis of (N) x (ExpPC), controlling by electoral
system}
\end{figure}

Therefore, we can see that the hypothesis that majoritarian systems
produce systematic positive effects was disproved. The majoritarian
systems in the sample had a random effects model estimate of -0.25,
while the random effects model in the non-majoritarian subgroup fitted a
value of 0.08. Both are non-significant, but they reassure us that the
absense of effect is not caused by pooling multiple types of electoral
systems.

\newpage

\hypertarget{pctgdp-x-n-1}{%
\subsubsection{PCTGDP x N}\label{pctgdp-x-n-1}}

This model fits the random effects for the percentage of GDP as public
expenditure as the main outcome, and the size of lower house as the main
treatment variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x N}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'N'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                               SMD             95%-CI %W(random)
## Bjedov et al. (2014)      -0.0040 [-0.0432;  0.0352]        2.1
## Bjedov et al. (2014)      -0.0080 [-0.0472;  0.0312]        2.1
## Maldonado (2013)          -0.0609 [-0.0838; -0.0380]        3.6
## Mukherjee (2003)           0.0030 [ 0.0010;  0.0050]        5.6
## Mukherjee (2003)           0.0090 [ 0.0051;  0.0129]        5.5
## Mukherjee (2003)           0.0110 [ 0.0051;  0.0169]        5.4
## Mukherjee (2003)           0.0050 [-0.0009;  0.0109]        5.4
## Mukherjee (2003)           0.0400 [ 0.0380;  0.0420]        5.6
## Mukherjee (2003)           0.0300 [ 0.0280;  0.0320]        5.6
## Mukherjee (2003)           0.0100 [ 0.0061;  0.0139]        5.5
## Mukherjee (2003)           0.0200 [ 0.0122;  0.0278]        5.3
## Bradbury and Crain (2001)  0.0036 [ 0.0008;  0.0065]        5.6
## Bradbury and Crain (2001)  0.0005 [-0.0016;  0.0027]        5.6
## Bradbury and Crain (2001)  0.0169 [ 0.0131;  0.0208]        5.6
## Bradbury and Crain (2001)  0.0123 [ 0.0087;  0.0160]        5.6
## Ricciuti (2004)            0.0140 [-0.0095;  0.0375]        3.5
## Ricciuti (2004)           -0.0110 [-0.0286;  0.0066]        4.2
## Ricciuti (2004)            0.0070 [-0.0067;  0.0207]        4.7
## Ricciuti (2004)            0.0050 [-0.0126;  0.0226]        4.2
## Ricciuti (2004)            0.0050 [-0.0126;  0.0226]        4.2
## Ricciuti (2004)            0.0120 [-0.0017;  0.0257]        4.7
## 
## Number of studies combined: k = 21
## 
##                         SMD            95%-CI    t p-value
## Random effects model 0.0078 [-0.0003; 0.0160] 2.01  0.0579
## Prediction interval         [-0.0259; 0.0416]             
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0002 [0.0002; 0.0007]; tau = 0.0156 [0.0136; 0.0261];
##  I^2 = 98.5% [98.2%; 98.7%]; H = 8.11 [7.40; 8.88]
## 
## Test of heterogeneity:
##        Q d.f.  p-value
##  1314.54   20 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-35-1.pdf}
\caption{Effect of lower houses size (N) on percentage of public
expenditure GDP (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 98.48.
\item
  The Random effects modem SMD estimated is \$g = \$ 0.01 (\(SE =\)
  0.004).
\item
  The prediction interval ranges from -0.03 to 0.04. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{logexppc-x-n-1}{%
\subsubsection{logExpPC x N}\label{logexppc-x-n-1}}

This model estimates the Log of Per Capita Expenditure as the dependent
variable, and the number of lower house legislators as the treatment
variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- logExpPC x N}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'N'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'logExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                              SMD             95%-CI %W(random)
## Lewis (2019)             -0.1740 [-0.2450; -0.1030]        6.6
## Höhmann (2017)           -0.0300 [-0.0496; -0.0104]        7.1
## Höhmann (2017)           -0.0300 [-0.0496; -0.0104]        7.1
## Höhmann (2017)           -0.0400 [-0.0792; -0.0008]        7.0
## Drew and Dollery (2017)   0.0770 [ 0.0221;  0.1319]        6.8
## Drew and Dollery (2017)   0.0310 [-0.0121;  0.0741]        6.9
## Pettersson-Lidbom (2012) -0.1590 [-0.2394; -0.0786]        6.4
## Pettersson-Lidbom (2012) -0.1470 [-0.2274; -0.0666]        6.4
## Pettersson-Lidbom (2012) -0.0900 [-0.1645; -0.0155]        6.5
## Pettersson-Lidbom (2012) -0.0810 [-0.1574; -0.0046]        6.5
## Pettersson-Lidbom (2012) -0.0880 [-0.1625; -0.0135]        6.5
## Pettersson-Lidbom (2012)  0.2100 [ 0.1649;  0.2551]        6.9
## Pettersson-Lidbom (2012)  0.1570 [ 0.0845;  0.2295]        6.5
## Pettersson-Lidbom (2012) -0.1990 [-0.2774; -0.1206]        6.4
## Pettersson-Lidbom (2012) -0.1690 [-0.2494; -0.0886]        6.4
## 
## Number of studies combined: k = 15
## 
##                          SMD            95%-CI     t p-value
## Random effects model -0.0463 [-0.1142; 0.0216] -1.46  0.1655
## Prediction interval          [-0.3105; 0.2178]              
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0139 [0.0070; 0.0364]; tau = 0.1181 [0.0836; 0.1908];
##  I^2 = 93.8% [91.2%; 95.6%]; H = 4.00 [3.38; 4.75]
## 
## Test of heterogeneity:
##       Q d.f.  p-value
##  224.56   14 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-37-1.pdf}
\caption{Effect of lower houses size (N) on log of per capita
expenditure (logExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 93.77.
\item
  The Random effects modem SMD estimated is \$g = \$ -0.05 (\(SE =\)
  0.032).
\item
  The prediction interval ranges from -0.31 to 0.22. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{exppc-x-logn-1}{%
\subsubsection{ExpPC x logN}\label{exppc-x-logn-1}}

There were no studies that had per capita expenditure in the dependent
variable and log of lower house size in the treatment variable.

\hypertarget{pctgdp-x-logn-1}{%
\subsubsection{PCTGDP x logN}\label{pctgdp-x-logn-1}}

This meta-regression investigates the percentage of GDP as public
expenditure as the dependent variable and the log lower house size
(logN) as the treatment variable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x logN}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'logN'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                         SMD            95%-CI %W(random)
## Baqir (1999)         2.0660 [ 1.4887; 2.6433]       18.9
## Baqir (1999)         2.0120 [ 1.4235; 2.6005]       18.8
## Baqir (1999)         2.4680 [ 1.8817; 3.0543]       18.8
## Lledo (2003)        -4.6900 [-9.9427; 0.5627]        3.8
## Stein et al. (1998)  0.0109 [-0.0171; 0.0389]       19.8
## Stein et al. (1998)  0.0135 [-0.0102; 0.0372]       19.8
## 
## Number of studies combined: k = 6
## 
##                         SMD            95%-CI    t p-value
## Random effects model 1.0619 [-0.7256; 2.8493] 1.53  0.1873
## Prediction interval         [-3.0267; 5.1504]             
## 
## Quantifying heterogeneity:
##  tau^2 = 1.6850 [0.6497; 38.1618]; tau = 1.2981 [0.8060; 6.1775];
##  I^2 = 96.9% [95.2%; 98.1%]; H = 5.71 [4.55; 7.16]
## 
## Test of heterogeneity:
##       Q d.f.  p-value
##  163.00    5 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-39-1.pdf}
\caption{Effect of log lower houses size (logN) on the GDP share of
public expenditure (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 96.93.
\item
  The Random effects modem SMD estimated is \$g = \$ 1.06 (\(SE =\)
  0.695).
\item
  The prediction interval ranges from -3.03 to 5.15. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{logexppc-x-logn-1}{%
\subsubsection{logExpPC x logN}\label{logexppc-x-logn-1}}

In this specification, we study the log of per capita expenditure
(logExpPC) as a function of the log of lower house size (logN).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- logExpPC x logN}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'logN'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'logExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                     SMD           95%-CI %W(random)
## MacDonald (2008) 0.1360 [0.0447; 0.2273]        7.9
## MacDonald (2008) 0.2319 [0.1322; 0.3316]        7.4
## MacDonald (2008) 0.1443 [0.0471; 0.2415]        7.6
## MacDonald (2008) 0.1594 [0.0667; 0.2521]        7.8
## MacDonald (2008) 0.2259 [0.1163; 0.3355]        6.9
## Baqir (2002)     0.1127 [0.0396; 0.1858]        9.1
## Baqir (2002)     0.2760 [0.2007; 0.3513]        8.9
## Baqir (2002)     0.3021 [0.2270; 0.3772]        8.9
## Baqir (2002)     0.3203 [0.2450; 0.3956]        8.9
## Baqir (1999)     0.3020 [0.2269; 0.3771]        8.9
## Baqir (1999)     0.2760 [0.2007; 0.3513]        8.9
## Baqir (1999)     0.2950 [0.2165; 0.3735]        8.7
## 
## Number of studies combined: k = 12
## 
##                         SMD           95%-CI     t  p-value
## Random effects model 0.2346 [0.1864; 0.2828] 10.71 < 0.0001
## Prediction interval         [0.0848; 0.3844]               
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0040 [0.0011; 0.0145]; tau = 0.0636 [0.0335; 0.1203];
##  I^2 = 70.0% [45.6%; 83.4%]; H = 1.82 [1.36; 2.45]
## 
## Test of heterogeneity:
##      Q d.f. p-value
##  36.62   11  0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-41-1.pdf}
\caption{Effect of log lower houses size (logN) on the log of per capita
government expenditure (logExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 69.96.
\item
  The Random effects modem SMD estimated is \$g = \$ 0.23 (\(SE =\)
  0.022). \textbf{This model is significant at the 10\% confidence
  level.}
\item
  The prediction interval ranges from 0.08 to 0.38. Therefore, it does
  not emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{exppc-x-k-1}{%
\subsubsection{ExpPC x K}\label{exppc-x-k-1}}

Now we are investigating the upper house size (K). In this model, we
investigate the effect of upper house size on expenditure per capita
(ExpPC).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- ExpPC x K}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'K'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'ExpPC'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                                    SMD              95%-CI %W(random)
## Crowley (2019)                  8.2100 [  0.2702; 16.1498]        4.8
## Crowley (2019)                  8.4230 [-27.1895; 44.0355]        0.4
## Crowley (2019)                  9.5940 [  2.1383; 17.0497]        5.1
## Lee and Park (2018)            19.7400 [  3.2645; 36.2155]        1.7
## Lee and Park (2018)            10.0600 [  2.2887; 17.8313]        4.9
## Lee and Park (2018)             9.0620 [-30.8821; 49.0061]        0.3
## Lee (2016)                     38.4400 [  0.7499; 76.1301]        0.4
## Lee (2016)                     37.8500 [  3.0214; 72.6786]        0.4
## Lee (2016)                     25.6100 [ -0.8103; 52.0303]        0.8
## Lee (2016)                      5.9960 [-19.6011; 31.5931]        0.8
## Lee (2016)                     25.5600 [ -0.8799; 51.9999]        0.8
## Lee (2016)                      4.6930 [-19.5126; 28.8986]        0.9
## Bradbury and Stephenson (2009)  0.6240 [  0.2295;  1.0185]       10.0
## Chen and Malhotra (2007)       26.0900 [ 11.4883; 40.6917]        2.1
## Chen and Malhotra (2007)        8.3000 [  3.6941; 12.9059]        7.3
## Chen and Malhotra (2007)        5.1400 [  0.1813; 10.0987]        7.0
## Chen and Malhotra (2007)        4.7800 [ -0.9039; 10.4639]        6.4
## Chen and Malhotra (2007)       20.3800 [  7.6990; 33.0610]        2.6
## Chen and Malhotra (2007)        4.8700 [  1.2833;  8.4567]        8.2
## Chen and Malhotra (2007)       26.7500 [  0.8589; 52.6411]        0.8
## Primo (2006)                    0.9700 [ -0.4804;  2.4204]        9.7
## Primo (2006)                    5.9000 [  2.6857;  9.1143]        8.5
## Primo (2006)                    5.7500 [  2.3593;  9.1407]        8.4
## Primo (2006)                    6.9600 [  2.6089; 11.3111]        7.6
## 
## Number of studies combined: k = 24
## 
##                         SMD             95%-CI    t  p-value
## Random effects model 7.2162 [ 4.4400;  9.9925] 5.38 < 0.0001
## Prediction interval         [-1.2217; 15.6542]              
## 
## Quantifying heterogeneity:
##  tau^2 = 14.7532 [5.4141; 111.2304]; tau = 3.8410 [2.3268; 10.5466];
##  I^2 = 77.7% [67.3%; 84.8%]; H = 2.12 [1.75; 2.57]
## 
## Test of heterogeneity:
##       Q d.f.  p-value
##  103.34   23 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-43-1.pdf}
\caption{Effect of upper house size (K) on the per capita government
expenditure (ExpPC)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 77.74.
\item
  The Random effects modem SMD estimated is \$g = \$ 7.22 (\(SE =\)
  1.342).
\item
  The prediction interval ranges from -1.22 to 15.65. Therefore, it
  emcompasses zero.
\end{enumerate}

\newpage

\hypertarget{pctgdp-x-k-1}{%
\subsubsection{PCTGDP x K}\label{pctgdp-x-k-1}}

This model looks into the effect of upper house size (K) on the public
expenditure share of the GDP (PCTGDP).

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Pooling effects analysis -- PCTGDP x K}
\NormalTok{aux <-}\StringTok{ }\NormalTok{fulldat }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(indepvar2 }\OperatorTok{==}\StringTok{ 'K'}\NormalTok{,}
\NormalTok{         depvar2 }\OperatorTok{==}\StringTok{ 'PCTGDP'}\NormalTok{)}

\NormalTok{mod <-}\StringTok{ }\KeywordTok{metagen}\NormalTok{(coef, SE, }\DataTypeTok{data=}\NormalTok{aux, }
          \DataTypeTok{studlab=}\KeywordTok{paste}\NormalTok{(authoryear),}
          \DataTypeTok{comb.fixed =} \OtherTok{FALSE}\NormalTok{,}
          \DataTypeTok{comb.random =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{method.tau =} \StringTok{"REML"}\NormalTok{,}
          \DataTypeTok{hakn =} \OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{prediction=}\OtherTok{TRUE}\NormalTok{,}
          \DataTypeTok{sm=}\StringTok{"SMD"}\NormalTok{)}
\NormalTok{mod}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##                               SMD             95%-CI %W(random)
## Maldonado (2012)          -0.0400 [-0.0659; -0.0141]        5.7
## Bradbury and Crain (2001)  0.0126 [ 0.0010;  0.0243]        9.8
## Bradbury and Crain (2001)  0.0050 [ 0.0016;  0.0083]       11.8
## Bradbury and Crain (2001) -0.0113 [-0.0163; -0.0064]       11.5
## Bradbury and Crain (2001) -0.0056 [-0.0102; -0.0010]       11.6
## Ricciuti (2004)            0.0160 [-0.0075;  0.0395]        6.2
## Ricciuti (2004)            0.0210 [-0.0006;  0.0426]        6.7
## Ricciuti (2004)            0.0140 [-0.0036;  0.0316]        7.9
## Ricciuti (2004)            0.0030 [-0.0088;  0.0148]        9.7
## Ricciuti (2004)            0.0300 [-0.0210;  0.0810]        2.2
## Ricciuti (2004)            0.0300 [-0.0210;  0.0810]        2.2
## Ricciuti (2004)            0.0390 [-0.0022;  0.0802]        3.1
## Ricciuti (2004)            0.0127 [-0.0147;  0.0401]        5.3
## Ricciuti (2004)            0.0160 [-0.0075;  0.0395]        6.2
## 
## Number of studies combined: k = 14
## 
##                         SMD            95%-CI    t p-value
## Random effects model 0.0056 [-0.0042; 0.0155] 1.24  0.2376
## Prediction interval         [-0.0233; 0.0346]             
## 
## Quantifying heterogeneity:
##  tau^2 = 0.0002 [0.0001; 0.0008]; tau = 0.0125 [0.0109; 0.0279];
##  I^2 = 80.0% [67.3%; 87.8%]; H = 2.24 [1.75; 2.86]
## 
## Test of heterogeneity:
##      Q d.f.  p-value
##  65.02   13 < 0.0001
## 
## Details on meta-analytical method:
## - Inverse variance method
## - Restricted maximum-likelihood estimator for tau^2
## - Q-profile method for confidence interval of tau^2 and tau
## - Hartung-Knapp adjustment for random effects model
\end{verbatim}

And the forest plot:

\begin{figure}
\centering
\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-45-1.pdf}
\caption{Effect of upper house size (K) on the public expenditure share
of the GDP (PCTGDP)}
\end{figure}

Highlights:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The results are highly heterogeneous: \$I\^{}2 = \$ 80.01.
\item
  The Random effects modem SMD estimated is \$g = \$ 0.01 (\(SE =\)
  0.005).
\item
  The prediction interval ranges from -0.02 to 0.03. Therefore, it
  emcompasses zero.
\end{enumerate}

\hypertarget{logexppc-x-k-1}{%
\subsubsection{logExpPC x K}\label{logexppc-x-k-1}}

No studies related the log of per capita expenditure with the size of
upper house (K).

\includegraphics{appendixV5_files/figure-latex/unnamed-chunk-46-2.pdf}
\includegraphics[width=49.21in]{appendixV5_files/figure-latex/unnamed-chunk-46-1}

\newpage

\hypertarget{meta-regressions}{%
\subsection{Meta-regressions}\label{meta-regressions}}

\hypertarget{meta-regressions-for-expenditure-as-a-percentage-of-the-gdp}{%
\subsubsection{Meta-regressions for Expenditure as a Percentage of the
GDP}\label{meta-regressions-for-expenditure-as-a-percentage-of-the-gdp}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 11; tau^2 estimator: REML)
## 
##   logLik  deviance       AIC       BIC      AICc 
##   7.0993  -14.1987    5.8013   -7.2672  225.8013   
## 
## tau^2 (estimated amount of residual heterogeneity):     0 (SE = 0.0001)
## tau (square root of estimated tau^2 value):             0
## I^2 (residual heterogeneity / unaccounted variability): 0.00%
## H^2 (unaccounted variability / sampling variability):   1.00
## R^2 (amount of heterogeneity accounted for):            100.00%
## 
## Test for Residual Heterogeneity:
## QE(df = 2) = 0.5965, p-val = 0.7421
## 
## Test of Moderators (coefficients 2:9):
## F(df1 = 8, df2 = 2) = 40.7363, p-val = 0.0242
## 
## Model Results:
## 
##                           estimate      se      tval    pval     ci.lb    ci.ub 
## intrcpt                     7.3697  1.7616    4.1835  0.0527   -0.2099  14.9493 
## indepvar2N                 -0.0094  0.0030   -3.1174  0.0893   -0.0223   0.0036 
## indepvar2logN              -4.7067  1.4637   -3.2156  0.0846  -11.0045   1.5912 
## year                       -0.0003  0.0005   -0.6899  0.5615   -0.0024   0.0017 
## publishedNo                 0.0633  0.0078    8.1139  0.0149    0.0297   0.0969 
## elecsys2Non-Majoritarian   -2.0554  0.1611  -12.7621  0.0061   -2.7484  -1.3625 
## methodPANEL                 0.0556  0.0071    7.7913  0.0161    0.0249   0.0864 
## agglevelStates             -4.6992  1.4637   -3.2106  0.0848  -10.9969   1.5984 
## location2World             -4.6959  1.4637   -3.2082  0.0850  -10.9937   1.6019 
##  
## intrcpt                    . 
## indepvar2N                 . 
## indepvar2logN              . 
## year 
## publishedNo                * 
## elecsys2Non-Majoritarian  ** 
## methodPANEL                * 
## agglevelStates             . 
## location2World             . 
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

As we have considerable heterogeneity in our sample, we run a
permutation test to ensure the validity of our estimates. The results
follow below.

\begin{verbatim}
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
\end{verbatim}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:9):
## F(df1 = 8, df2 = 2) = 40.7363, p-val* = 0.0130
## 
## Model Results:
## 
##                           estimate      se      tval   pval*     ci.lb    ci.ub 
## intrcpt                     7.3697  1.7616    4.1835  0.0360   -0.2099  14.9493 
## indepvar2N                 -0.0094  0.0030   -3.1174  0.0190   -0.0223   0.0036 
## indepvar2logN              -4.7067  1.4637   -3.2156  0.2010  -11.0045   1.5912 
## year                       -0.0003  0.0005   -0.6899  0.4350   -0.0024   0.0017 
## publishedNo                 0.0633  0.0078    8.1139  0.0140    0.0297   0.0969 
## elecsys2Non-Majoritarian   -2.0554  0.1611  -12.7621  0.0090   -2.7484  -1.3625 
## methodPANEL                 0.0556  0.0071    7.7913  0.0140    0.0249   0.0864 
## agglevelStates             -4.6992  1.4637   -3.2106  0.2170  -10.9969   1.5984 
## location2World             -4.6959  1.4637   -3.2082  0.2790  -10.9937   1.6019 
##  
## intrcpt                    * 
## indepvar2N                 * 
## indepvar2logN 
## year 
## publishedNo                * 
## elecsys2Non-Majoritarian  ** 
## methodPANEL                * 
## agglevelStates 
## location2World 
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

We have the following results for the meta-regressions of Expenditure
Per Capita:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compared with \texttt{K}, models with \texttt{N} and \texttt{logN}
  find significantly negative coefficients.
\item
  Year has null effect.
\item
  Unpublished papers tend to have higher coefficients than published
  papers.
\item
  Passing from \texttt{Majoritarian} to \texttt{Non-Majoritarian},
  decreases significantly the effects found in our models.
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  increases the detected effects.
\item
  When passing from \texttt{Local} to \texttt{State} or \texttt{World}
  levels, it decreases the detected effect size.
\end{enumerate}

Below we also run the meta-regressions adding all coefficients in the
papers. The results follow below:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 41; tau^2 estimator: REML)
## 
##    logLik   deviance        AIC        BIC       AICc 
##   89.1145  -178.2290  -158.2290  -143.5716  -147.7528   
## 
## tau^2 (estimated amount of residual heterogeneity):     0.0001 (SE = 0.0000)
## tau (square root of estimated tau^2 value):             0.0102
## I^2 (residual heterogeneity / unaccounted variability): 94.05%
## H^2 (unaccounted variability / sampling variability):   16.81
## R^2 (amount of heterogeneity accounted for):            99.92%
## 
## Test for Residual Heterogeneity:
## QE(df = 32) = 1001.8067, p-val < .0001
## 
## Test of Moderators (coefficients 2:9):
## F(df1 = 8, df2 = 32) = 29.7201, p-val < .0001
## 
## Model Results:
## 
##                           estimate      se      tval    pval     ci.lb    ci.ub 
## intrcpt                    -5.3830  5.8900   -0.9139  0.3676  -17.3805   6.6145 
## indepvar2N                 -0.0014  0.0048   -0.2945  0.7703   -0.0112   0.0084 
## indepvar2logN              -4.6069  2.4363   -1.8909  0.0677   -9.5696   0.3558 
## year                        0.0060  0.0027    2.2730  0.0299    0.0006   0.0114 
## publishedNo                 0.1130  0.0251    4.5060  <.0001    0.0619   0.1641 
## elecsys2Non-Majoritarian   -2.1629  0.1568  -13.7904  <.0001   -2.4823  -1.8434 
## methodPANEL                 0.1252  0.0304    4.1232  0.0002    0.0633   0.1870 
## agglevelStates             -4.7325  2.4361   -1.9426  0.0609   -9.6947   0.2298 
## location2World             -4.6443  2.4362   -1.9064  0.0656   -9.6067   0.3181 
##  
## intrcpt 
## indepvar2N 
## indepvar2logN               . 
## year                        * 
## publishedNo               *** 
## elecsys2Non-Majoritarian  *** 
## methodPANEL               *** 
## agglevelStates              . 
## location2World              . 
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{permutest}\NormalTok{(mod, }\DataTypeTok{progbar =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:9):
## F(df1 = 8, df2 = 32) = 29.7201, p-val* = 0.0010
## 
## Model Results:
## 
##                           estimate      se      tval   pval*     ci.lb    ci.ub 
## intrcpt                    -5.3830  5.8900   -0.9139  0.2800  -17.3805   6.6145 
## indepvar2N                 -0.0014  0.0048   -0.2945  0.7390   -0.0112   0.0084 
## indepvar2logN              -4.6069  2.4363   -1.8909  0.0910   -9.5696   0.3558 
## year                        0.0060  0.0027    2.2730  0.0090    0.0006   0.0114 
## publishedNo                 0.1130  0.0251    4.5060  0.0020    0.0619   0.1641 
## elecsys2Non-Majoritarian   -2.1629  0.1568  -13.7904  0.0010   -2.4823  -1.8434 
## methodPANEL                 0.1252  0.0304    4.1232  0.0020    0.0633   0.1870 
## agglevelStates             -4.7325  2.4361   -1.9426  0.0840   -9.6947   0.2298 
## location2World             -4.6443  2.4362   -1.9064  0.0950   -9.6067   0.3181 
##  
## intrcpt 
## indepvar2N 
## indepvar2logN               . 
## year                       ** 
## publishedNo                ** 
## elecsys2Non-Majoritarian  *** 
## methodPANEL                ** 
## agglevelStates              . 
## location2World              . 
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

For all the coefficients, we have the following results:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compared with \texttt{K}, models with \texttt{N} and \texttt{logN}
  tend to have significantly negative coefficients.
\item
  Year has a positive effect: the younger the publication, the higher
  the detected coefficient.
\item
  Unpublished papers tend to have higher coefficients than published
  papers.
\item
  Passing from \texttt{Majoritarian} to \texttt{Non-Majoritarian},
  decreases significantly the effects found in our models.
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  increases the detected effects.
\item
  When passing from \texttt{Local} to \texttt{State} or \texttt{World}
  levels, it decreases the detected effect size.
\end{enumerate}

\hypertarget{meta-regressions-for-expenditure-per-capita}{%
\subsubsection{Meta-regressions for Expenditure Per
Capita}\label{meta-regressions-for-expenditure-per-capita}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 18; tau^2 estimator: REML)
## 
##   logLik  deviance       AIC       BIC      AICc 
## -34.6251   69.2502   85.2502   88.4333  157.2502   
## 
## tau^2 (estimated amount of residual heterogeneity):     1.8429 (SE = 1.2361)
## tau (square root of estimated tau^2 value):             1.3575
## I^2 (residual heterogeneity / unaccounted variability): 95.05%
## H^2 (unaccounted variability / sampling variability):   20.21
## R^2 (amount of heterogeneity accounted for):            0.00%
## 
## Test for Residual Heterogeneity:
## QE(df = 11) = 45.4940, p-val < .0001
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 11) = 0.3429, p-val = 0.8998
## 
## Model Results:
## 
##                            estimate        se     tval    pval      ci.lb 
## intrcpt                   -104.0701  318.9300  -0.3263  0.7503  -806.0302 
## indepvar2N                  -2.9238    2.0932  -1.3968  0.1900    -7.5309 
## year                         0.0525    0.1586   0.3308  0.7470    -0.2967 
## elecsys2Non-Majoritarian     0.3458    1.5533   0.2226  0.8279    -3.0730 
## methodPANEL                  1.4571    2.2376   0.6512  0.5283    -3.4679 
## methodIV                     1.4936    2.6675   0.5599  0.5868    -4.3776 
## agglevelStates              -0.0915    2.4255  -0.0377  0.9706    -5.4299 
##                              ci.ub 
## intrcpt                   597.8900    
## indepvar2N                  1.6834    
## year                        0.4017    
## elecsys2Non-Majoritarian    3.7645    
## methodPANEL                 6.3821    
## methodIV                    7.3648    
## agglevelStates              5.2470    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

As we have considerable heterogeneity in our sample, we run a
permutation test to ensure the validity of our estimates. The results
follow below.

\begin{verbatim}
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
## Error in rma.uni(x$yi, x$vi, weights = x$weights, mods = cbind(X[sample(x$k),  : 
##   Fisher scoring algorithm did not converge. See 'help(rma)' for possible remedies.
\end{verbatim}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 11) = 0.3429, p-val* = 0.5900
## 
## Model Results:
## 
##                            estimate        se     tval   pval*      ci.lb 
## intrcpt                   -104.0701  318.9300  -0.3263  0.6300  -806.0302 
## indepvar2N                  -2.9238    2.0932  -1.3968  0.0650    -7.5309 
## year                         0.0525    0.1586   0.3308  0.6270    -0.2967 
## elecsys2Non-Majoritarian     0.3458    1.5533   0.2226  0.7180    -3.0730 
## methodPANEL                  1.4571    2.2376   0.6512  0.3330    -3.4679 
## methodIV                     1.4936    2.6675   0.5599  0.4380    -4.3776 
## agglevelStates              -0.0915    2.4255  -0.0377  0.9440    -5.4299 
##                              ci.ub 
## intrcpt                   597.8900    
## indepvar2N                  1.6834  . 
## year                        0.4017    
## elecsys2Non-Majoritarian    3.7645    
## methodPANEL                 6.3821    
## methodIV                    7.3648    
## agglevelStates              5.2470    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

We have the following results for the meta-regressions of Expenditure
Per Capita:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compared with \texttt{K}, models with \texttt{N} tend to detect
  significantly smaller effects.
\item
  Year has null effect.
\item
  Passing the electoral rules from \texttt{Majoritarian} to
  \texttt{Non-Majoritarian}, increases significantly the per capita
  expenditure found in our models.
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  or \texttt{IV} increases the detected effects.
\item
  When passing from \texttt{Local} to \texttt{State} level, decreases
  the detected effects.
\end{enumerate}

Below we also run the meta-regressions adding all coefficients in the
papers. The results follow below:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 60; tau^2 estimator: REML)
## 
##    logLik   deviance        AIC        BIC       AICc 
## -141.1228   282.2456   298.2456   314.0079   301.5183   
## 
## tau^2 (estimated amount of residual heterogeneity):     1.7264 (SE = 0.4944)
## tau (square root of estimated tau^2 value):             1.3139
## I^2 (residual heterogeneity / unaccounted variability): 99.80%
## H^2 (unaccounted variability / sampling variability):   500.07
## R^2 (amount of heterogeneity accounted for):            39.21%
## 
## Test for Residual Heterogeneity:
## QE(df = 53) = 325.8548, p-val < .0001
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 53) = 5.9441, p-val < .0001
## 
## Model Results:
## 
##                            estimate        se     tval    pval      ci.lb 
## intrcpt                   -296.9072  166.6870  -1.7812  0.0806  -631.2389 
## indepvar2N                  -5.4468    0.9692  -5.6201  <.0001    -7.3907 
## year                         0.1503    0.0830   1.8117  0.0757    -0.0161 
## elecsys2Non-Majoritarian     1.0236    0.7701   1.3293  0.1894    -0.5209 
## methodPANEL                 -0.1422    0.8136  -0.1747  0.8620    -1.7739 
## methodIV                     0.1907    0.8223   0.2319  0.8175    -1.4587 
## agglevelStates              -0.2008    1.0049  -0.1998  0.8424    -2.2164 
##                             ci.ub 
## intrcpt                   37.4245    . 
## indepvar2N                -3.5029  *** 
## year                       0.3167    . 
## elecsys2Non-Majoritarian   2.5682      
## methodPANEL                1.4896      
## methodIV                   1.8401      
## agglevelStates             1.8149      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{permutest}\NormalTok{(mod, }\DataTypeTok{progbar =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 53) = 5.9441, p-val* = 0.0010
## 
## Model Results:
## 
##                            estimate        se     tval   pval*      ci.lb 
## intrcpt                   -296.9072  166.6870  -1.7812  0.0170  -631.2389 
## indepvar2N                  -5.4468    0.9692  -5.6201  0.0010    -7.3907 
## year                         0.1503    0.0830   1.8117  0.0150    -0.0161 
## elecsys2Non-Majoritarian     1.0236    0.7701   1.3293  0.0730    -0.5209 
## methodPANEL                 -0.1422    0.8136  -0.1747  0.7990    -1.7739 
## methodIV                     0.1907    0.8223   0.2319  0.7700    -1.4587 
## agglevelStates              -0.2008    1.0049  -0.1998  0.7990    -2.2164 
##                             ci.ub 
## intrcpt                   37.4245    * 
## indepvar2N                -3.5029  *** 
## year                       0.3167    * 
## elecsys2Non-Majoritarian   2.5682    . 
## methodPANEL                1.4896      
## methodIV                   1.8401      
## agglevelStates             1.8149      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

With all coefficients, the results of the effect sizes on the
Expenditure Per Capita Regressions are the following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compared with \texttt{K}, models with \texttt{N} tend to detect
  significantly smaller effects.
\item
  Year has now a positive effect on coefficient sizes.
\item
  Passing the electoral rules from \texttt{Majoritarian} to
  \texttt{Non-Majoritarian}, increases significantly the effects on per
  capita expenditure found in our models.
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  decreases the detected effects.
\item
  All other coeffients were not significant.
\end{enumerate}

\hypertarget{meta-regressions-for-the-log-of-expenditure-per-capita}{%
\subsubsection{Meta-regressions for the Log of Expenditure Per
Capita}\label{meta-regressions-for-the-log-of-expenditure-per-capita}}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 7; tau^2 estimator: REML)
## 
##   logLik  deviance       AIC       BIC      AICc 
##   0.8657   -1.7315   12.2685   -1.7315  124.2685   
## 
## tau^2 (estimated amount of residual heterogeneity):     0.0096 (SE = 0.0147)
## tau (square root of estimated tau^2 value):             0.0977
## I^2 (residual heterogeneity / unaccounted variability): 92.15%
## H^2 (unaccounted variability / sampling variability):   12.74
## R^2 (amount of heterogeneity accounted for):            65.22%
## 
## Test for Residual Heterogeneity:
## QE(df = 1) = 12.7408, p-val = 0.0004
## 
## Test of Moderators (coefficients 2:6):
## F(df1 = 5, df2 = 1) = 2.9742, p-val = 0.4128
## 
## Model Results:
## 
##                 estimate       se     tval    pval      ci.lb     ci.ub 
## intrcpt           8.9711  47.4747   0.1890  0.8811  -594.2521  612.1943    
## indepvar2N       -0.1641   0.3258  -0.5037  0.7029    -4.3043    3.9760    
## year             -0.0044   0.0237  -0.1864  0.8827    -0.3053    0.2965    
## publishedNo       0.1520   0.1902   0.7993  0.5707    -2.2647    2.5687    
## methodPANEL       0.2581   0.1886   1.3680  0.4018    -2.1389    2.6550    
## agglevelStates   -0.0875   0.1901  -0.4602  0.7254    -2.5028    2.3278    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

As we have considerable heterogeneity in our sample, we run a
permutation test to ensure the validity of our estimates. The results
follow below.

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:6):
## F(df1 = 5, df2 = 1) = 2.9742, p-val* = 0.3720
## 
## Model Results:
## 
##                 estimate       se     tval   pval*      ci.lb     ci.ub 
## intrcpt           8.9711  47.4747   0.1890  0.9090  -594.2521  612.1943    
## indepvar2N       -0.1641   0.3258  -0.5037  0.7160    -4.3043    3.9760    
## year             -0.0044   0.0237  -0.1864  0.9110    -0.3053    0.2965    
## publishedNo       0.1520   0.1902   0.7993  0.5880    -2.2647    2.5687    
## methodPANEL       0.2581   0.1886   1.3680  0.3660    -2.1389    2.6550    
## agglevelStates   -0.0875   0.1901  -0.4602  0.6980    -2.5028    2.3278    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

We have the following results for the meta-regressions of Log of
Expenditure Per Capita:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Unpublished papers report a significantly higher coefficient.
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  increases the detected effects.
\item
  All other coefficients remained insignificant.
\end{enumerate}

Below we also run the meta-regressions adding all coefficients in the
papers. The results follow below:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 27; tau^2 estimator: REML)
## 
##   logLik  deviance       AIC       BIC      AICc 
##  21.9924  -43.9848  -27.9848  -20.0190  -14.8939   
## 
## tau^2 (estimated amount of residual heterogeneity):     0.0051 (SE = 0.0021)
## tau (square root of estimated tau^2 value):             0.0716
## I^2 (residual heterogeneity / unaccounted variability): 86.93%
## H^2 (unaccounted variability / sampling variability):   7.65
## R^2 (amount of heterogeneity accounted for):            82.37%
## 
## Test for Residual Heterogeneity:
## QE(df = 20) = 98.5701, p-val < .0001
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 20) = 16.9707, p-val < .0001
## 
## Model Results:
## 
##                 estimate       se     tval    pval     ci.lb    ci.ub 
## intrcpt          -1.6655  15.8337  -0.1052  0.9173  -34.6940  31.3630      
## indepvar2N        0.0088   0.1262   0.0701  0.9448   -0.2544   0.2721      
## year              0.0009   0.0079   0.1187  0.9067   -0.0155   0.0174      
## publishedNo       0.0829   0.0728   1.1387  0.2683   -0.0689   0.2347      
## methodPANEL      -0.2436   0.0705  -3.4537  0.0025   -0.3908  -0.0965   ** 
## methodRDD        -0.2978   0.0656  -4.5398  0.0002   -0.4347  -0.1610  *** 
## agglevelStates   -0.0438   0.0673  -0.6505  0.5228   -0.1842   0.0966      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{permutest}\NormalTok{(mod, }\DataTypeTok{progbar =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:7):
## F(df1 = 6, df2 = 20) = 16.9707, p-val* = 0.0010
## 
## Model Results:
## 
##                 estimate       se     tval   pval*     ci.lb    ci.ub 
## intrcpt          -1.6655  15.8337  -0.1052  0.9130  -34.6940  31.3630      
## indepvar2N        0.0088   0.1262   0.0701  0.9320   -0.2544   0.2721      
## year              0.0009   0.0079   0.1187  0.9010   -0.0155   0.0174      
## publishedNo       0.0829   0.0728   1.1387  0.3040   -0.0689   0.2347      
## methodPANEL      -0.2436   0.0705  -3.4537  0.0030   -0.3908  -0.0965   ** 
## methodRDD        -0.2978   0.0656  -4.5398  0.0010   -0.4347  -0.1610  *** 
## agglevelStates   -0.0438   0.0673  -0.6505  0.5100   -0.1842   0.0966      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

With all coefficients, the results of the effect sizes on the Log of
Expenditure Per Capita Regressions are the following:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  In terms of the modeling, passing from \texttt{OLS} to \texttt{PANEL}
  or \texttt{RDD} decreases the detected effects.
\item
  All other coefficients remained insignificant.
\end{enumerate}

\hypertarget{theory-of-meta-analysis}{%
\subsection{Theory of Meta Analysis}\label{theory-of-meta-analysis}}

There are two main estimators for conducting meta analysis: fixed
effects and random effects models. The fixed effects model assumes that
there is one true effect in reality, and that all estimates are an
attempt to uncover this true effect. The random effects model, on the
other hand, assumes that there are a distribution of true effects, that
vary based on sample and tests characteristics.

In this paper, we use the random effects model. The empirical papers
testing the law of 1/n are very diverse. We tried to capture some of
this diversity by considering the main dependent and independent
variables separately, but they have at least three other important
sources of dispersion:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Subjects}: Counties, Municipalities, States, Provinces,
  Countries.
\item
  \textbf{Electoral systems}: Majoritarian, PR, Mixed.
\item
  \textbf{Modeling strategies}: Panel data, Standard OLS, IV, RDD.
\end{enumerate}

These sources of heterogeneity have two implications. First, it makes
our estimates very disperse. The heterogeneity tests are all but one
significant. When the sample sizes are large enough, we removed more
heterogeneous studies, but we still had considerable dispersion in our
estimates. Second, the amount of heterogeneity makes fixed effects
estimates unrealistic and bised. Thus, we opt for random effects model.

Let each study having an effect of \(T_i\). In a random effects model,
we can decompose this effect in two components, the true effect that the
study with the same specifications as \(i\) come from, \(\theta_i\), and
a within-study error \(\varepsilon_i\):

\[
T_i \ = \ \theta_i + \varepsilon_i
\]

And the random effects model assumes that the \(\theta_i\) varies from
study to study, having a true parameter \(\mu\), plus a between-study
error, \(\xi_i\):

\[
T_i \ = \ \mu + \xi_i + \varepsilon_i
\]

And the random effects model estimates the parameter \(\mu\), under the
challenge of estimating both the within-and-between-study sampling
errors.

In all empirical estimates, we use the package \texttt{meta}, and the
package \texttt{dmetar}, described in (Doing Meta-Analysis with
R){[}\url{https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html}{]}.
To empirically implement the random effects model, we need to choose a
method to estimate the true effect size variance, \(\tau^2\), which in
our formulation, represents the variance of \(\xi_i\). We selected the
\textbf{Restricted Maximum Likelihood Estimator}, as the literature
regards it as more precise when we have continuous measures, such as we
have on our data
(link){[}\url{https://www.ncbi.nlm.nih.gov/pubmed/26332144}{]}.

\hypertarget{robustness-full-model-meta-regressions-combined}{%
\subsection{Robustness: Full model meta-regressions
combined}\label{robustness-full-model-meta-regressions-combined}}

In this section, we aggregate all the coefficients and run a
multivariate meta-regression, controlling by:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The type of the dependent variable in the study (expenditure per
  capita, log of the expenditure per capita, and share of government
  expenditure in the GDP)
\item
  The type of the independent variable in the stydy (N, K, log of N);
\item
  The electoral system (Majoritarian, Proportional Representation, and
  Mixed).
\end{enumerate}

The results follow below, and show null effect for all variables,
including the intercept.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 36; tau^2 estimator: REML)
## 
##   logLik  deviance       AIC       BIC      AICc 
## -47.9845   95.9689  125.9689  142.3345  205.9689   
## 
## tau^2 (estimated amount of residual heterogeneity):     0.2315 (SE = 0.1007)
## tau (square root of estimated tau^2 value):             0.4812
## I^2 (residual heterogeneity / unaccounted variability): 99.94%
## H^2 (unaccounted variability / sampling variability):   1599.58
## R^2 (amount of heterogeneity accounted for):            0.00%
## 
## Test for Residual Heterogeneity:
## QE(df = 22) = 175.9758, p-val < .0001
## 
## Test of Moderators (coefficients 2:14):
## F(df1 = 13, df2 = 22) = 0.3352, p-val = 0.9772
## 
## Model Results:
## 
##                           estimate        se     tval    pval      ci.lb 
## intrcpt                   -22.4725  122.8858  -0.1829  0.8566  -277.3220 
## depvar2PCTGDP               0.1796    0.8381   0.2143  0.8323    -1.5585 
## depvar2logExpPC            -0.5979    0.8526  -0.7012  0.4905    -2.3661 
## indepvar2N                 -0.4922    0.5236  -0.9400  0.3574    -1.5780 
## indepvar2logN               0.4376    1.6148   0.2710  0.7889    -2.9113 
## year                        0.0114    0.0609   0.1875  0.8530    -0.1148 
## publishedNo                 0.2843    0.6541   0.4346  0.6681    -1.0723 
## elecsys2Non-Majoritarian    0.2724    0.6284   0.4335  0.6689    -1.0308 
## methodPANEL                 0.1754    0.7126   0.2461  0.8079    -1.3025 
## methodIV                    0.0336    1.0078   0.0334  0.9737    -2.0565 
## methodRDD                   0.2411    1.2612   0.1912  0.8501    -2.3745 
## agglevelStates             -0.2400    0.7393  -0.3247  0.7485    -1.7733 
## agglevelCountries          -1.4929    1.2027  -1.2414  0.2275    -3.9871 
## location2World              0.7437    1.5559   0.4780  0.6374    -2.4830 
##                              ci.ub 
## intrcpt                   232.3770    
## depvar2PCTGDP               1.9176    
## depvar2logExpPC             1.1704    
## indepvar2N                  0.5937    
## indepvar2logN               3.7865    
## year                        0.1376    
## publishedNo                 1.6408    
## elecsys2Non-Majoritarian    1.5755    
## methodPANEL                 1.6532    
## methodIV                    2.1237    
## methodRDD                   2.8567    
## agglevelStates              1.2932    
## agglevelCountries           1.0013    
## location2World              3.9704    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

As we have considerable heterogeneity in our sample, we run a
permutation test to ensure the validity of our estimates. The results
follow below.

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:14):
## F(df1 = 13, df2 = 22) = 0.3352, p-val* = 0.6590
## 
## Model Results:
## 
##                           estimate        se     tval   pval*      ci.lb 
## intrcpt                   -22.4725  122.8858  -0.1829  0.7890  -277.3220 
## depvar2PCTGDP               0.1796    0.8381   0.2143  0.7170    -1.5585 
## depvar2logExpPC            -0.5979    0.8526  -0.7012  0.3320    -2.3661 
## indepvar2N                 -0.4922    0.5236  -0.9400  0.1570    -1.5780 
## indepvar2logN               0.4376    1.6148   0.2710  0.7180    -2.9113 
## year                        0.0114    0.0609   0.1875  0.7760    -0.1148 
## publishedNo                 0.2843    0.6541   0.4346  0.5100    -1.0723 
## elecsys2Non-Majoritarian    0.2724    0.6284   0.4335  0.4890    -1.0308 
## methodPANEL                 0.1754    0.7126   0.2461  0.7020    -1.3025 
## methodIV                    0.0336    1.0078   0.0334  0.9630    -2.0565 
## methodRDD                   0.2411    1.2612   0.1912  0.7870    -2.3745 
## agglevelStates             -0.2400    0.7393  -0.3247  0.6110    -1.7733 
## agglevelCountries          -1.4929    1.2027  -1.2414  0.2470    -3.9871 
## location2World              0.7437    1.5559   0.4780  0.5730    -2.4830 
##                              ci.ub 
## intrcpt                   232.3770    
## depvar2PCTGDP               1.9176    
## depvar2logExpPC             1.1704    
## indepvar2N                  0.5937    
## indepvar2logN               3.7865    
## year                        0.1376    
## publishedNo                 1.6408    
## elecsys2Non-Majoritarian    1.5755    
## methodPANEL                 1.6532    
## methodIV                    2.1237    
## methodRDD                   2.8567    
## agglevelStates              1.2932    
## agglevelCountries           1.0013    
## location2World              3.9704    
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

In the main text, we selected the coefficients based on the regressions
that had most observations and that presented a full model (with fixed
effects or intermediate bandwidth in RDD). Below we also run the
meta-regressions adding all coefficients in the papers. The results
follow below:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(mod)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Mixed-Effects Model (k = 128; tau^2 estimator: REML)
## 
##    logLik   deviance        AIC        BIC       AICc 
## -192.2430   384.4860   414.4860   455.5290   419.3840   
## 
## tau^2 (estimated amount of residual heterogeneity):     0.0624 (SE = 0.0108)
## tau (square root of estimated tau^2 value):             0.2498
## I^2 (residual heterogeneity / unaccounted variability): 99.96%
## H^2 (unaccounted variability / sampling variability):   2838.73
## R^2 (amount of heterogeneity accounted for):            66.57%
## 
## Test for Residual Heterogeneity:
## QE(df = 114) = 2083.6861, p-val < .0001
## 
## Test of Moderators (coefficients 2:14):
## F(df1 = 13, df2 = 114) = 2.7571, p-val = 0.0019
## 
## Model Results:
## 
##                           estimate       se     tval    pval     ci.lb 
## intrcpt                    38.5855  36.3705   1.0609  0.2910  -33.4642 
## depvar2PCTGDP               0.4967   0.3068   1.6189  0.1082   -0.1111 
## depvar2logExpPC            -0.3311   0.2342  -1.4139  0.1601   -0.7949 
## indepvar2N                 -0.1467   0.1451  -1.0113  0.3140   -0.4342 
## indepvar2logN               0.1689   0.4677   0.3611  0.7187   -0.7576 
## year                       -0.0190   0.0180  -1.0533  0.2944   -0.0547 
## publishedNo                -0.0690   0.1689  -0.4088  0.6834   -0.4036 
## elecsys2Non-Majoritarian    0.6244   0.2274   2.7464  0.0070    0.1740 
## methodPANEL                -0.1833   0.1588  -1.1546  0.2507   -0.4978 
## methodIV                   -0.1452   0.2364  -0.6139  0.5405   -0.6135 
## methodRDD                  -0.2569   0.2618  -0.9812  0.3286   -0.7756 
## agglevelStates             -0.5263   0.2324  -2.2648  0.0254   -0.9867 
## agglevelCountries          -1.8292   0.4527  -4.0406  <.0001   -2.7261 
## location2World              0.4062   0.4891   0.8305  0.4080   -0.5627 
##                              ci.ub 
## intrcpt                   110.6352      
## depvar2PCTGDP               1.1044      
## depvar2logExpPC             0.1328      
## indepvar2N                  0.1407      
## indepvar2logN               1.0954      
## year                        0.0167      
## publishedNo                 0.2655      
## elecsys2Non-Majoritarian    1.0748   ** 
## methodPANEL                 0.1312      
## methodIV                    0.3232      
## methodRDD                   0.2618      
## agglevelStates             -0.0659    * 
## agglevelCountries          -0.9324  *** 
## location2World              1.3751      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{permutest}\NormalTok{(mod, }\DataTypeTok{progbar =}\NormalTok{ F)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## 
## Test of Moderators (coefficients 2:14):
## F(df1 = 13, df2 = 114) = 2.7571, p-val* = 0.0010
## 
## Model Results:
## 
##                           estimate       se     tval   pval*     ci.lb 
## intrcpt                    38.5855  36.3705   1.0609  0.1110  -33.4642 
## depvar2PCTGDP               0.4967   0.3068   1.6189  0.0200   -0.1111 
## depvar2logExpPC            -0.3311   0.2342  -1.4139  0.0400   -0.7949 
## indepvar2N                 -0.1467   0.1451  -1.0113  0.1170   -0.4342 
## indepvar2logN               0.1689   0.4677   0.3611  0.6110   -0.7576 
## year                       -0.0190   0.0180  -1.0533  0.1120   -0.0547 
## publishedNo                -0.0690   0.1689  -0.4088  0.5400   -0.4036 
## elecsys2Non-Majoritarian    0.6244   0.2274   2.7464  0.0010    0.1740 
## methodPANEL                -0.1833   0.1588  -1.1546  0.1020   -0.4978 
## methodIV                   -0.1452   0.2364  -0.6139  0.3440   -0.6135 
## methodRDD                  -0.2569   0.2618  -0.9812  0.1440   -0.7756 
## agglevelStates             -0.5263   0.2324  -2.2648  0.0040   -0.9867 
## agglevelCountries          -1.8292   0.4527  -4.0406  0.0010   -2.7261 
## location2World              0.4062   0.4891   0.8305  0.2490   -0.5627 
##                              ci.ub 
## intrcpt                   110.6352      
## depvar2PCTGDP               1.1044    * 
## depvar2logExpPC             0.1328    * 
## indepvar2N                  0.1407      
## indepvar2logN               1.0954      
## year                        0.0167      
## publishedNo                 0.2655      
## elecsys2Non-Majoritarian    1.0748  *** 
## methodPANEL                 0.1312      
## methodIV                    0.3232      
## methodRDD                   0.2618      
## agglevelStates             -0.0659   ** 
## agglevelCountries          -0.9324  *** 
## location2World              1.3751      
## 
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\end{document}

### 2020-04-23 appendix/appendixV5.Rmd
Y-axis. Captions. Append whitespace.

@@
 date: "12/25/2019"
-output:
-  pdf_document:
-    keep_tex: true
+output: pdf_document
 ---
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f1
-ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f1 + 
+  labs(caption = "ExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fa.png", width = 20, height = 12.5, units = "cm")
 
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f2
-ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f2 + 
+  labs(caption = "PCTGDP x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fb.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f3
-ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f3 + 
+  labs(caption = "logExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fc.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f4
-ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f4 + 
+  labs(caption = "PCTGDP x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fd.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f5
-ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f5 + 
+  labs(caption = "logExpPC x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fe.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f6
-ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f6 + 
+  labs(caption = "ExpPC x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/ff.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f7
-ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f7 + 
+  labs(caption = "PCTGDP x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fg.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
 
-```{r, echo=FALSE, fig.width=12.5, fig.height=5}
-
-#grid.arrange(f8, f9, f11, 
-#             f10,f12, f13,
-#             f14,
-#             ncol = 2,
-#             nrow = 4)
-#library(ggplot2)
-
+```{r,include=F,warning=F}
 blank = ggplot() + 
@@
 blank
-ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")
+ggsave("./plots/zz_blank.png", width = 20, height = 12.5, units = "cm")
 
@@
   map(~{
-    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
+    image_read(path = paste0("./plots/", .x)) %>%
+      image_rotate(., 270) %>%
+      image_border(., "#ffffff ", "90x18")
   })
+```
+
+```{r, echo=FALSE, fig.width=12.5, fig.height=5}
 
@@
 
-#p_full
-
-#ggpubr::ggarrange(plots[[1]],plots[[2]],
-#                  plots[[3]],plots[[4]],
-#                  plots[[5]],plots[[6]],
-#                  plots[[7]],
-#                  nrow = 4, ncol = 2
-#                  )
-
-#ggpubr::ggarrange(f1,f2, 
-#          labels = c("A", "B"),
-#          ncol = 1, nrow = 2)
-
-#grid.draw(rbind(f1,f2, size = "first"))
-
-#plot_grid(f1,f2 + rremove("x.text"), 
-#          labels = c("A", "B"),
-#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 9, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f8
-ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f8 + 
+  labs(caption = "ExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 9, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fh.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f8b
@@
               upper = c(mod$upper.random, mod$upper.predict),
-              group = "B"))
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
 
 f9 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
   # Studies coefs
@@
   scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
   # Vertical dashed line
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f9
-ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f9 + 
+  labs(caption = "PCTGDP x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fi.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f10
-ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f10 + 
+  labs(caption = "logExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fj.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f11
-ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f11 + 
+  labs(caption = "PCTGDP x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fk.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  scale_x_continuous(limits=c(-0.1, 1.2*(max(mod2$upper)))) +
   # Y-axis names
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f12
-ggsave("./plots/f12.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f12 + 
+  labs(caption = "logExpPC x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fl.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 12, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f13
-ggsave("./plots/f13.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f13 + 
+  labs(caption = "ExpPC x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 12, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fm.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f14
-ggsave("./plots/f14.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f14 + 
+  labs(caption = "PCTGDP x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fn.png", width = 20, height = 12.5, units = "cm")
+
 ```
@@
 
-blank = ggplot() + 
-  geom_blank() +
-  theme_minimal()
-blank
-ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")
-
-plots = list.files(path = "./plots/", pattern = "*.png") %>%
-  map(~{
-    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
-  })
-
 p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
@@
 p_full
-
-#p_full
 

### 2020-04-29 appendix/appendixV5.Rmd
Red coefs. Max Y-axis. Max size plots. Table 2. Regres tables.

--- 2020-04-22 appendix/appendixV5.Rmd
@@
 \newpage 
+### Descriptive Stats of Moderators
+
+```{r, echo=F}
+
+#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)
+
+aux = dat %>%
+  group_by(depvar2) %>%
+  summarise(n = n(),
+            mean_coef = mean(coef, na.rm = T),
+            median_coef = median(coef, na.rm = T)) %>%
+  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
+  select(depvar2, n, pct, mean_coef, median_coef)
+
+kable(aux)
+
+```
+
+### Descriptive Stats of Moderators by Year
+
+```{r, echo=F}
+
+#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)
+
+aux = dat %>%
+  group_by(depvar2, year) %>%
+  summarise(n = n(),
+            mean_coef = round(mean(coef, na.rm = T), digits = 3),
+            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
+  group_by(year) %>%
+  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
+  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
+  arrange(year) %>%
+  rename(Moderator = depvar2,
+         Year = year,
+         N = n,
+         Pct = pct,
+         Mean = mean_coef,
+         Median = median_coef
+         )
+
+kable(aux)
+
+```
+
+\newpage
 ## Meta-analysis
@@
   # Studies coefs
-  geom_point(color = "black") +
+  geom_point(aes(color = group)) +
   # Error Bars
-  geom_errorbarh(height = 0.1) +
+  geom_errorbarh(aes(color = group), height = 0.1) +
+  # Colors
+  scale_color_manual(values = c("#000000", "#8b0000")) + 
   # X-axis limit
@@
   # Y-axis names
-  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
+  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
   # Vertical dashed line
-  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
   # Labels
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f1
-ggsave("./plots/f1.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f1 + 
+  labs(caption = "ExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")
 
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f2
-ggsave("./plots/f2.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f2 + 
+  labs(caption = "PCTGDP x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fb.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f3
-ggsave("./plots/f3.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f3 + 
+  labs(caption = "logExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fc.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f4
-ggsave("./plots/f4.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f4 + 
+  labs(caption = "PCTGDP x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fd.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f5
-ggsave("./plots/f5.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f5 + 
+  labs(caption = "logExpPC x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fe.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f6
-ggsave("./plots/f6.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f6 + 
+  labs(caption = "ExpPC x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/ff.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f7
-ggsave("./plots/f7.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f7 + 
+  labs(caption = "PCTGDP x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 18, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fg.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
 blank
-ggsave("./plots/zz_blank.png", width = 20, height = 10, units = "cm")
+ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")
 
@@
   map(~{
-    image_rotate(image_read(path = paste0("./plots/", .x)), 270)
+    image_read(path = paste0("./plots/", .x)) %>%
+      image_rotate(., 270) %>%
+      image_border(., "#ffffff ", "90x18")
   })
+```
+
+```{r, echo=FALSE, fig.width=20, fig.height=5}
 
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
 mod2 <- tibble(
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 9, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f8
-ggsave("./plots/f8.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f8 + 
+  labs(caption = "ExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fh.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f8b
@@
               upper = c(mod$upper.random, mod$upper.predict),
-              group = "B"))
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
 
 f9 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
   # Studies coefs
-  geom_point(color = "black") +
+  geom_point(aes(color = group)) +
   # Error Bars
-  geom_errorbarh(height = 0.1) +
+  geom_errorbarh(aes(color = group), height = 0.1) +
+  # Colors
+  scale_color_manual(values = c("#000000", "#8b0000")) + 
   # X-axis limit
   scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
   # Vertical dashed line
-  geom_vline(xintercept=0, color="black", linetype="dashed") +
+  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
   # Labels
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank()) 
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 10, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
 f9
-ggsave("./plots/f9.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f9 + 
+  labs(caption = "PCTGDP x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fi.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f10
-ggsave("./plots/f10.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f10 + 
+  labs(caption = "logExpPC x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fj.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f11
-ggsave("./plots/f11.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f11 + 
+  labs(caption = "PCTGDP x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 20, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fk.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f12
-ggsave("./plots/f12.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f12 + 
+  labs(caption = "logExpPC x logN") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fl.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 12, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f13
-ggsave("./plots/f13.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f13 + 
+  labs(caption = "ExpPC x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 12, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fm.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
   theme_minimal() %+replace%
-  theme(strip.text.y = element_blank())
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
 
 f14
-ggsave("./plots/f14.png", width = 20, height = 10, units = "cm")
+```
+
+```{r,include=F,warning=F}
+f14 + 
+  labs(caption = "PCTGDP x K") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fn.png", width = 30, height = 18.75, units = "cm")
+
 ```
@@
 
-```{r, echo=FALSE, fig.width=10, fig.height=1}
+```{r, echo=FALSE, fig.width=20, fig.height=2}
 
@@
 ## Meta-regressions
+
+### Meta-regressions for Expenditure measured as
 
@@
             slab = dat$authoryear)
+
+mod1 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "PCTGDP"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod1)
+
 ```
@@
 ```{r, echo=FALSE}
-permutest(mod, progbar = F)
+mod = permutest(mod, progbar = F)
+mod
+
+mod1_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "PCTGDP - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod1_permu)
+
 ```
@@
             slab = fulldat$authoryear)
+
+mod2 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "PCTGDP - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod2)
+
 ```
@@
 
-```{r}
-permutest(mod, progbar = F)
+```{r, echo=FALSE}
+
+mod = permutest(mod, progbar = F)
+mod
+
+mod2_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "PCTGDP - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod2_permu)
+
 ```
@@
             slab = dat$authoryear)
+
+mod3 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "ExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod3)
+
 ```
@@
 ```{r, echo=FALSE}
-permutest(mod, progbar = F)
+mod = permutest(mod, progbar = F)
+mod
+
+mod3_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "ExpPC - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod3_permu)
+
 ```
@@
             slab = fulldat$authoryear)
+
+mod4 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "ExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod4)
+
 ```
@@
 
-```{r}
-permutest(mod, progbar = F)
+```{r, echo=FALSE}
+
+mod = permutest(mod, progbar = F)
+mod
+
+mod4_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "ExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod4_permu)
+
 ```
@@
             slab = dat$authoryear)
+
+mod5 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod5)
+
 ```
@@
 ```{r, echo=FALSE}
-permutest(mod, progbar = F)
+mod = permutest(mod, progbar = F)
+mod
+
+mod5_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod5_permu)
+
 ```
@@
             slab = fulldat$authoryear)
+
+mod6 <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod5_permu)
+
 ```
@@
 
-```{r}
-permutest(mod, progbar = F)
+```{r, echo=FALSE}
+mod = permutest(mod, progbar = F)
+mod
+
+mod6_permu <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(mod5_permu)
+
 ```

### 2020-04-29 appendix/appendixV5.Rmd
Regression tables. Centering Kable tables.

@@
 
-kable(aux)
+kable(aux) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod1)
+kable(mod1) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod1_permu)
+kable(mod1_permu) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod2)
+kable(mod2) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod2_permu)
+kable(mod2_permu) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod3)
+kable(mod3) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod3_permu)
+kable(mod3_permu) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod4)
+kable(mod4) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod4_permu)
+kable(mod4_permu) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod5)
+kable(mod5) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod5_permu)
+kable(mod5_permu) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod5_permu)
+kable(mod6) %>%
+  kable_styling(position = "center")
 
@@
 
-kable(mod5_permu)
+kable(mod6_permu) %>%
+  kable_styling(position = "center")
 
@@
 2. All other coefficients remained insignificant.
+
+\newpage
+
+## Summary of Models
+
+### Summary of Base Models
+
+```{r}
+aux = bind_rows(
+  mod1,
+  mod3,
+  mod5
+) %>%
+  mutate(model = gsub(" .*", "", model))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
+```
+
+### Summary of Base Models (Permutation)
+
+```{r,echo=F}
+aux = bind_rows(
+  mod1_permu,
+  mod3_permu,
+  mod5_permu
+) %>%
+  mutate(model = gsub(" .*", "", model))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
+```
+
+### Summary of Models with all coefficients
+
+```{r,echo=F}
+aux = bind_rows(
+  mod2,
+  mod4,
+  mod6
+) %>%
+  mutate(model = gsub(" .*", "", model))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
+```
+
+### Summary of Models with all coefficients (Permutation)
+
+```{r,echo=F}
+
+aux = bind_rows(
+  mod2_permu,
+  mod4_permu,
+  mod6_permu
+) %>%
+  mutate(model = gsub(" .*", "", model))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
+```
 
@@
               test = "knha")
+
+aux <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
 ```
@@
 ```{r, echo=FALSE}
-permutest(mod, progbar = F)
+mod = permutest(mod, progbar = F)
+
+aux <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
 ```
@@
 
-```{r}
-permutest(mod, progbar = F)
-```
+```{r, echo=F, warning=F}
+mod = permutest(mod, progbar = F)
+
+aux <- tibble(
+  estimate = mod[["beta"]],
+  se = mod[["se"]],
+  tval = mod[["zval"]],
+  pval = mod[["pval"]],
+  ci.lb = mod[["ci.lb"]],
+  ci.ub = mod[["ci.ub"]],
+  model = "logExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+kable(aux) %>%
+  kable_styling(position = "center")
+
+```

### 2020-04-30 appendix/appendixV5.Rmd
Change order plots. Coef labels.

@@
 
-kable(aux) %>%
-  kable_styling(position = "center")
+kable(aux, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 \newpage
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+### ExpPC x logN
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
+\newpage
+### ExpPC x K
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x N
+# Pooling effects analysis -- ExpPC x K
 aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
 
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
 mod2 <- tibble(
@@
         axis.text.x = element_text(size = 15, hjust = 1.1))
+
 f2
@@
 f2 + 
-  labs(caption = "PCTGDP x N") +
+  labs(caption = "ExpPC x K") +
   theme_minimal() %+replace%
@@
 \newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-### PCTGDP x logN
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+### logExpPC x logN
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x logN
+# Pooling effects analysis -- logExpPC x logN
 aux <- dat %>%
   filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(
-  coef, SE, data=aux, 
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
           prediction=TRUE,
-  sm="SMD"
-  )
-
+          sm="SMD")
 mod
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
 mod2 <- tibble(
@@
 f4 + 
-  labs(caption = "PCTGDP x logN") +
+  labs(caption = "logExpPC x logN") +
   theme_minimal() %+replace%
@@
 1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
 3.
@@
 \newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+### logExpPC x K
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
+### PCTGDP x N
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
 
 ```{r}
-# Pooling effects analysis -- logExpPC x logN
+# Pooling effects analysis -- PCTGDP x N
 aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
 
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
 mod2 <- tibble(
@@
         axis.text.x = element_text(size = 15, hjust = 1.1)) 
-
 f5
@@
 f5 + 
-  labs(caption = "logExpPC x logN") +
+  labs(caption = "PCTGDP x N") +
   theme_minimal() %+replace%
@@
 1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
 3.
@@
 \newpage
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+### PCTGDP x logN
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
 
 ```{r}
-# Pooling effects analysis -- ExpPC x K
+# Pooling effects analysis -- PCTGDP x logN
 aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(
+  coef, SE, data=aux, 
   studlab=paste(authoryear),
@@
   prediction=TRUE,
-          sm="SMD")
+  sm="SMD"
+  )
+
 mod
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
 mod2 <- tibble(
@@
 f6 + 
-  labs(caption = "ExpPC x K") +
+  labs(caption = "PCTGDP x logN") +
   theme_minimal() %+replace%
@@
 \newpage
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
 ```{r,include=F,warning=F}
@@
 \newpage
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+### ExpPC x logN
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
+\newpage
+### ExpPC x K
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x N
+# Pooling effects analysis -- ExpPC x K
 aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
 
@@
         legend.position = "none",
-        axis.text.y = element_text(size = 10, hjust = 1.1),
+        axis.text.y = element_text(size = 12, hjust = 1.1),
         axis.text.x = element_text(size = 15, hjust = 1.1))
+
 f9
@@
 f9 + 
-  labs(caption = "PCTGDP x N") +
+  labs(caption = "ExpPC x K") +
   theme_minimal() %+replace%
@@
         legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.y = element_text(size = 12, hjust = 1.1),
         axis.text.x = element_text(size = 15, hjust = 1.1),
@@
 \newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-### PCTGDP x logN
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+### logExpPC x logN
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x logN
+# Pooling effects analysis -- logExpPC x logN
 aux <- fulldat %>%
   filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
+         depvar2 == 'logExpPC')
 
@@
 f11 + 
-  labs(caption = "PCTGDP x logN") +
+  labs(caption = "logExpPC x logN") +
   theme_minimal() %+replace%
@@
         legend.position = "none",
-        axis.text.y = element_text(size = 20, hjust = 1.1),
+        axis.text.y = element_text(size = 15, hjust = 1.1),
         axis.text.x = element_text(size = 15, hjust = 1.1),
@@
 
+### logExpPC x K
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
 \newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+### PCTGDP x N
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
 
 ```{r}
-# Pooling effects analysis -- logExpPC x logN
+# Pooling effects analysis -- PCTGDP x N
 aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
 
@@
 f12 <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(aes(color = group)) +
+  # Error Bars
+  geom_errorbarh(aes(color = group), height = 0.1) +
+  # Colors
+  scale_color_manual(values = c("#000000", "#8b0000")) + 
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 10, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
+f12
+```
+
+```{r,include=F,warning=F}
+f12 + 
+  labs(caption = "PCTGDP x N") +
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1),
+        plot.caption = element_text(size=22))
+
+ggsave("./plots/fl.png", width = 30, height = 18.75, units = "cm")
+
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+### PCTGDP x logN
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+
+```{r}
+# Pooling effects analysis -- PCTGDP x logN
+aux <- fulldat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f13 <- mod2 %>%
   ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
@@
 
-f12
+f13
 ```
@@
 ```{r,include=F,warning=F}
-f12 + 
-  labs(caption = "logExpPC x logN") +
+f13 + 
+  labs(caption = "PCTGDP x logN") +
   theme_minimal() %+replace%
@@
         legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fl.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
-
-```{r}
-# Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f13 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f13
-```
-
-```{r,include=F,warning=F}
-f13 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
+        axis.text.y = element_text(size = 20, hjust = 1.1),
         axis.text.x = element_text(size = 15, hjust = 1.1),
@@
 
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
 ```{r, echo=FALSE, fig.width=20, fig.height=2}
@@
 mod1 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
+              round(mod[["ci.ub"]], digits = 4), ")"),
   model = "PCTGDP"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod1) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod1, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
+
+collapse_rows_dt <- expand.grid(
+    Country =sprintf('Country with a long name %s',c('A','B')),
+    State =sprintf('State %s',c('a','b')),
+    City =sprintf('City %s',c('1','2')),
+    District =sprintf('District %s',c('1','2'))) %>% 
+  arrange(Country, State, City) %>% 
+  mutate_all(as.character) %>%
+  mutate(C1 =rnorm(n()),
+         C2 =rnorm(n()))
 
@@
 mod1_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "PCTGDP - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod1_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod1_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod2 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "PCTGDP - All coefs"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod2) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod2, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod2_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "PCTGDP - All coefs - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod2_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod2_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod3 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
+          "Method: IV", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "ExpPC"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod3) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod3, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod3_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
+          "Method: IV", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "ExpPC - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod3_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod3_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod4 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
+             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "ExpPC - All coefs"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod4) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod4, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod4_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
+             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "ExpPC - All coefs - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod4_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod4_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod5 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "logExpPC"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod5) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod5, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod5_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
   model = "logExpPC - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod5_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod5_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod6 <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
   model = "logExpPC - All coefs"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod6) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod6, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 mod6_permu <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
   model = "logExpPC - All coefs - Permutation"
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(mod6_permu) %>%
-  kable_styling(position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
+    mutate(model = gsub(" .*", "", model))
+
+kable(mod6_permu, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 
-```{r}
+```{r, echo=F}
 aux = bind_rows(
@@
 ```{r,echo=F}
+
+# Table  3  presents  the  meta-regression  results  for  our  restricted  and  extended  samples.
+Eachcolumn represents one of the three measures of public spending we discuss in this paper.
+To reduce the risk of false positives in our analyses, we use permutation tests to calculate significance levelsfor the meta-regressions (Higgins and Thompson 2004).TABLE 3 AROUND HERE: Meta-regression analysis estimating the effect of moderator variables on public expenditure
+#The first two models show the results for public expenditure per capita.
+In both the restrictedand the extended samples, we and that models that use푛as an independent variable tend to detect significantly smaller effects when compared to k.
+This suggests that an additional member in thelower house has a smaller impact on public spending than a member in the upper house.
+Moreover,
+#the results for the extended sample point out that recent studies and larger effects than older ones,and that changing the electoral rules from majoritarian to non-majoritarian increases the effects oflegislature size on per capita expenditure.The third and fourth columns use the logarithm of expenditure per capita as the dependentvariable.
+No covariate  is statistically  significant in our  smaller sample,  but two  moderators arenegatively associated with the outcome in our larger study pool.
+They both refer to estimationmethods.
+Studies that employ panel/fixed effects or regression discontinuity designs (RDDs) havelower coeficients for log expenditure per capita if we take OLS as the reference category
+
 aux = bind_rows(
@@
 aux <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
-  model = "logExpPC - All coefs - Permutation"
+  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
+          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
+          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")")
 ) %>%
@@
 aux <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
-  model = "logExpPC - All coefs - Permutation"
-) %>%
+  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
+          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
+          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
   mutate_if(is.numeric, list(~round(., digits = 4)))
 
-kable(aux) %>%
-  kable_styling(position = "center")
+kable(aux, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
 
@@
 aux <- tibble(
-  estimate = mod[["beta"]],
-  se = mod[["se"]],
-  tval = mod[["zval"]],
-  pval = mod[["pval"]],
-  ci.lb = mod[["ci.lb"]],
-  ci.ub = mod[["ci.ub"]],
-  model = "logExpPC - All coefs - Permutation"
-) %>%
+    ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
+          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
+          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  T = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
   mutate_if(is.numeric, list(~round(., digits = 4)))
 
-kable(aux) %>%
-  kable_styling(position = "center")
-
-```
+kable(aux, booktabs = T) %>%
+  kable_styling(c("striped", "bordered"), position = "center")
+
+```

### 2020-05-01 appendix/appendixV5.Rmd
Table 3. Back to summary. LaTex code.

@@
 date: "12/25/2019"
+header-includes:
+- \usepackage{booktabs}
+- \usepackage{longtable}
+- \usepackage{array}
+- \usepackage{multirow}
+- \usepackage{wrapfig}
+- \usepackage{float}
+- \usepackage{colortbl}
+- \usepackage{pdflscape}
+- \usepackage{tabu}
+- \usepackage{threeparttable}
+- \usepackage{threeparttablex}
+- \usepackage[normalem]{ulem}
+- \usepackage{makecell}
+- \usepackage{xcolor}
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
+
 output: pdf_document
@@
 aux <- filter(dat, indepvar2 == 'N')
-# str(aux$scoef) -- Obs: this line originally was in the main text. Fix? - LMM
 binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
@@
 
-#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)
-
-aux = dat %>%
+# Table - General
+
+aux <- dat %>%
   group_by(depvar2) %>%
@@
   mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
-  select(depvar2, n, pct, mean_coef, median_coef)
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  select(depvar2, n, pct, mean_coef, median_coef) %>%
+  rename(` ` = depvar2,
+         N = n,
+         Pct = pct,
+         Mean = mean_coef,
+         Median = median_coef)
+
+kable(aux, 
+      booktabs = T,
+      align = "c",
+      linesep ='') %>% 
+  kable_styling(c("striped","bordered","scale_down"), position = "center")
 
@@
 
-#TABLE 2 ABOUT HERE: Moderator, frequency, percentage (mean and median for publication year)
-
-aux = dat %>%
+#Table: by year
+
+aux <- dat %>%
   group_by(depvar2, year) %>%
@@
   arrange(year) %>%
-  rename(Moderator = depvar2,
+  rename(` ` = depvar2,
          Year = year,
@@
 
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+kable(aux, 
+      booktabs = T,
+      align = "c",
+      linesep ='') %>% 
+  kable_styling(c("striped","bordered","scale_down"), position = "center")
 
@@
 
-\newpage
 ### PCTGDP x K
@@
 
-#grid.arrange(f8, f9, f11, 
-#             f10,f12, f13,
-#             f14,
-#             ncol = 2,
-#             nrow = 4)
-#library(ggplot2)
-
 p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
@@
 
-#ggpubr::ggarrange(plots[[1]],plots[[2]],
-#                  plots[[3]],plots[[4]],
-#                  plots[[5]],plots[[6]],
-#                  plots[[7]],
-#                  nrow = 4, ncol = 2
-#                  )
-
-#ggpubr::ggarrange(f1,f2, 
-#          labels = c("A", "B"),
-#          ncol = 1, nrow = 2)
-
-#grid.draw(rbind(f1,f2, size = "first"))
-
-#plot_grid(f1,f2 + rremove("x.text"), 
-#          labels = c("A", "B"),
-#           align = "v", nrow = 2, rel_heights = c(1/4, 1/4))
 ```
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod1, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-collapse_rows_dt <- expand.grid(
-    Country =sprintf('Country with a long name %s',c('A','B')),
-    State =sprintf('State %s',c('a','b')),
-    City =sprintf('City %s',c('1','2')),
-    District =sprintf('District %s',c('1','2'))) %>% 
-  arrange(Country, State, City) %>% 
-  mutate_all(as.character) %>%
-  mutate(C1 =rnorm(n()),
-         C2 =rnorm(n()))
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ```{r, echo=FALSE}
-mod = permutest(mod, progbar = F)
+mod <- permutest(mod, progbar = F)
 mod
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod1_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod2, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 
-mod = permutest(mod, progbar = F)
+mod <- permutest(mod, progbar = F)
 mod
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod2_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod3, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod3_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod4, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod4_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod5, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod5_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+mod5_permu %>%
+  select(-model) %>%
+  kable(booktabs = T,align = "c",linesep ='') %>%
+  kable_styling(c("striped","bordered","scale_down"), position = "center")
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod6, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4))) %>%
-    mutate(model = gsub(" .*", "", model))
-
-kable(mod6_permu, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
+  mutate_if(is.numeric, list(~round(., digits = 4)))
 
@@
 
+## Summary of Models
+
+```{r, echo=F, warning=F,error=F,message=F}
+coefs = bind_rows(
+  mod1,
+  mod2,
+  mod3,
+  mod4,
+  mod5) %>%
+  select(` `) %>%
+  distinct()
+
+aux = list(mod3, mod5, mod1) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(type = "Base") %>%
+  select(type, everything())
+
+aux2 = list(mod4, mod6, mod2) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(type = "All Coefs") %>%
+  select(type, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"))
+
+```
+
+\blandscape
+```{r, echo=F, warning=F,error=F,message=F,asis=T}
+kable(aux, 
+      booktabs = T,
+      longtable = T,
+      align = "c",
+      linesep ='',
+      col.names = c(
+        " ",
+        " ",
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value"
+      )
+    ) %>% 
+  collapse_rows(
+    1:3,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
+  kable_styling(
+    c("striped",
+      "bordered", 
+      "scale_down",
+      "repeat_header"
+      ),
+    position = "center",
+    latex_options = c("repeat_header"))
+
+```
+\elandscape
+
 \newpage
-
-## Summary of Models
-
-### Summary of Base Models
-
-```{r, echo=F}
-aux = bind_rows(
-  mod1,
-  mod3,
-  mod5
-) %>%
-  mutate(model = gsub(" .*", "", model))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-```
-
-### Summary of Base Models (Permutation)
-
-```{r,echo=F}
-
-# Table  3  presents  the  meta-regression  results  for  our  restricted  and  extended  samples.
-Eachcolumn represents one of the three measures of public spending we discuss in this paper.
-To reduce the risk of false positives in our analyses, we use permutation tests to calculate significance levelsfor the meta-regressions (Higgins and Thompson 2004).TABLE 3 AROUND HERE: Meta-regression analysis estimating the effect of moderator variables on public expenditure
-#The first two models show the results for public expenditure per capita.
-In both the restrictedand the extended samples, we and that models that use푛as an independent variable tend to detect significantly smaller effects when compared to k.
-This suggests that an additional member in thelower house has a smaller impact on public spending than a member in the upper house.
-Moreover,
-#the results for the extended sample point out that recent studies and larger effects than older ones,and that changing the electoral rules from majoritarian to non-majoritarian increases the effects oflegislature size on per capita expenditure.The third and fourth columns use the logarithm of expenditure per capita as the dependentvariable.
-No covariate  is statistically  significant in our  smaller sample,  but two  moderators arenegatively associated with the outcome in our larger study pool.
-They both refer to estimationmethods.
-Studies that employ panel/fixed effects or regression discontinuity designs (RDDs) havelower coeficients for log expenditure per capita if we take OLS as the reference category
-
-aux = bind_rows(
-  mod1_permu,
-  mod3_permu,
-  mod5_permu
-) %>%
-  mutate(model = gsub(" .*", "", model))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-```
-
-### Summary of Models with all coefficients
-
-```{r,echo=F}
-aux = bind_rows(
-  mod2,
-  mod4,
-  mod6
-) %>%
-  mutate(model = gsub(" .*", "", model))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-```
-
-### Summary of Models with all coefficients (Permutation)
-
-```{r,echo=F}
-
-aux = bind_rows(
-  mod2_permu,
-  mod4_permu,
-  mod6_permu
-) %>%
-  mutate(model = gsub(" .*", "", model))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-```
-
 ## Theory of Meta Analysis
@@
 
-aux <- tibble(
-  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
-          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
-          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")")
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
 ```
@@
 ```{r, echo=FALSE}
-mod = permutest(mod, progbar = F)
-
-aux <- tibble(
-  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
-          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
-          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
+permutest(mod, progbar = F)
 ```
@@
 
-aux <- tibble(
-  ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
-          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
-          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
 ```
@@
 ```{r, echo=F, warning=F}
-mod = permutest(mod, progbar = F)
-
-aux <- tibble(
-    ` ` = c("Intercept", "Depvar: PCTGDP", "Depvar: logExpPC", 
-          "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-           "Elecsys: Non-Majoritarian", "Method: PANEL", "Method: IV", "Method: RDD",
-          "AggLevel: States", "AggLevel: Countries" ,"Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")")) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-kable(aux, booktabs = T) %>%
-  kable_styling(c("striped", "bordered"), position = "center")
-
-```
+permutest(mod, progbar = F)
+
+```

### 2020-05-01 appendix/appendixV5.Rmd
Table 3 Permutation.

@@
 
-## Summary of Models
-
 ```{r, echo=F, warning=F,error=F,message=F}
@@
         "P-Value"
-      )
+      ),
+  caption = "Summary of Models"
     ) %>% 
@@
 
+```{r, echo=F, warning=F,error=F,message=F}
+coefs = bind_rows(
+  mod1_permu,
+  mod2_permu,
+  mod3_permu,
+  mod4_permu,
+  mod5_permu) %>%
+  select(` `) %>%
+  distinct()
+
+aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(type = "Base") %>%
+  select(type, everything())
+
+aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(type = "All Coefs") %>%
+  select(type, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"))
+
+```
+
+\blandscape
+```{r, echo=F, warning=F,error=F,message=F,asis=T}
+kable(aux, 
+      booktabs = T,
+      longtable = T,
+      align = "c",
+      linesep ='',
+      col.names = c(
+        " ",
+        " ",
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "T",
+        "P-Value"
+      ),
+          caption = "Summary of Models (Permutest)"
+    ) %>% 
+  collapse_rows(
+    1:3,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
+  kable_styling(
+    c("striped",
+      "bordered", 
+      "scale_down",
+      "repeat_header"
+      ),
+    position = "center",
+    latex_options = c("repeat_header"))
+
+```
+\elandscape
+
 \newpage

### 2020-05-02 appendix/appendixV5.Rmd
Fix Table 2 and Table 3.

--- 2020-05-01 appendix/appendixV5.Rmd
@@
 
-```{r, echo=F}
-
-# Table - General
-
-aux <- dat %>%
-  group_by(depvar2) %>%
-  summarise(n = n(),
-            mean_coef = mean(coef, na.rm = T),
-            median_coef = median(coef, na.rm = T)) %>%
-  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
-  select(depvar2, n, pct, mean_coef, median_coef) %>%
-  rename(` ` = depvar2,
-         N = n,
-         Pct = pct,
-         Mean = mean_coef,
-         Median = median_coef)
+```{r, echo=F,warning=F,message=F,error=F}
+
+# Table 2
+
+dat2 <- dat %>%
+  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
+  rename(Depvar = depvar2,
+         Indepvar = indepvar2,
+         Published = published,
+         "Electoral System" = elecsys2,
+         Method = method,
+         "Aggregate Level" = agglevel,
+         Location = location2)
+
+names <- dat2 %>% 
+  map(table) %>%
+  unlist() %>%
+  names()
+
+aux <- dat2 %>%
+  map_df(~{
+    table(.x) %>%
+      as.data.frame() %>%
+      rename(Moderator = ".x") %>%
+      mutate(Moderator = as.character(Moderator),
+             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
+  }) %>%
+  mutate(Moderator = names,
+         Moderator = gsub("\\.", ": ", Moderator),
+         Freq = as.character(Freq)) %>%
+  bind_rows(.,
+            tibble(
+              Moderator = "Year",
+              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
+              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
+            ))
 
@@
 
-```
-
-### Descriptive Stats of Moderators by Year
-
-```{r, echo=F}
-
-#Table: by year
-
-aux <- dat %>%
-  group_by(depvar2, year) %>%
-  summarise(n = n(),
-            mean_coef = round(mean(coef, na.rm = T), digits = 3),
-            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
-  group_by(year) %>%
-  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
-  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
-  arrange(year) %>%
-  rename(` ` = depvar2,
-         Year = year,
-         N = n,
-         Pct = pct,
-         Mean = mean_coef,
-         Median = median_coef
-         )
-
-kable(aux, 
-      booktabs = T,
-      align = "c",
-      linesep ='') %>% 
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
+rm(dat2,names)
 ```
@@
   SE = mod[["se"]],
-  T = mod[["zval"]],
+  `T` = mod[["zval"]],
   `P-Value` = mod[["pval"]],
@@
 ) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
+  mutate_if(is.numeric, list(~round(., digits = 3)))
 
@@
 2. All other coefficients remained insignificant.
-
-## Summary of Models
 
@@
   select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "Base") %>%
-  select(type, everything())
+  mutate(mod = "Base") %>%
+  select(mod, everything())
 
@@
   select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "All Coefs") %>%
-  select(type, everything())
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
 
 aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"))
+  select(-contains("CI"),-`T`,-T1,-T2)
 
@@
 \blandscape
+
+## Summary of Results
 ```{r, echo=F, warning=F,error=F,message=F,asis=T}
@@
       booktabs = T,
-      longtable = T,
+      longtable = F,
       align = "c",
@@
         "SE",
-        "T",
         "P-Value",
@@
         "SE",
-        "T",
         "P-Value"
-      )
-    ) %>% 
+      )) %>% 
   collapse_rows(
-    1:3,
+    1:2,
     row_group_label_position ='stack'
     ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
   kable_styling(
@@
 
+```{r, echo=F, warning=F,error=F,message=F}
+coefs = bind_rows(
+  mod1_permu,
+  mod2_permu,
+  mod3_permu,
+  mod4_permu,
+  mod5_permu) %>%
+  select(` `) %>%
+  distinct()
+
+aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "Base") %>%
+  select(mod, everything())
+
+aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "AggLevel: States", 9, order)
+         ) %>%
+  arrange(order) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"),-`T`,-T1,-T2)
+
+```
+
+\blandscape
+
+## Summary of Results (Permutation)
+```{r, echo=F, warning=F,error=F,message=F,asis=T}
+kable(aux, 
+      "latex",
+      booktabs = T,
+      longtable = F,
+      align = "c",
+      linesep ='',
+      col.names = c(
+        " ",
+        " ",
+        "Estimate",
+        "SE",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "P-Value"
+      )) %>% 
+  collapse_rows(
+    1:2,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
+  kable_styling(
+    c("striped",
+      "bordered", 
+      "scale_down",
+      "repeat_header"
+      ),
+    position = "center",
+    latex_options = c("repeat_header"))
+
+```
+\elandscape
+
 \newpage

### 2020-05-02 appendix/appendixV5.Rmd
Stars for P-Values.

@@
 pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
-          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')
+          'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')
 
@@
          order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
+         order = ifelse(` ` == "AggLevel: States", 9, order),
+         pval = ifelse(`P-Value` < 0.05, "*", NA),
+         pval = ifelse(`P-Value` < 0.01, "**", pval),
+         pval = ifelse(`P-Value` < 0.01, "***", pval),
+         pval = ifelse(`P-Value` >= 0.05, " ", pval),
+         `P-Value` = pval) %>%
   arrange(order) %>%
@@
 aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
+  select(-contains("CI"),-`T`,-T1,-T2,-pval)
 
@@
     position = "center",
-    latex_options = c("repeat_header"))
+    latex_options = c("repeat_header")) %>%
+  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
 
@@
 kable(aux, 
-      "latex",
       booktabs = T,

### 2020-05-05 Untitled.R
teste

@@ -1,0 +1,1 @@
+# Arquivo novo

### 2020-05-17 appendixupdates/appendix.Rmd
Original contents of appendixupdates
Version: 2020-05-14

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
bibliography: references.bib
biblio-style: apalike
output: 
pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    keep_tex: no
    toc: no
    toc_depth: 3
    template: article-template.latex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(repos = c(CRAN = "http://cran.rstudio.com"))
```

## Search criteria

### Search terms

We coded the scraping process for academic material that cited @weingast1981political's "The political economy of benefits and costs: A neoclassical approach to distributive politics". **It is cited by 2159 studies**.

``` {r, include=FALSE}

#### INSTALLING PACKAGES ####

install.packages('tidyverse')
install.packages('rvest')
install.packages('RSelenium')

#### LOADING PACKAGES ####

library(tidyverse)
library(rvest)
library(RSelenium)

#### SETTING UP SELENIUM ####

# Alternative 1: Setting up Selenium (head)
rsD <- rsDriver(port = 1114L, browser = c("firefox")) # you can also choose any unalocated port of your choice and/or ´browser of your preference
remDr <- rsD$client
remDr$open()

# Alternative 2: Setting up Selenium (headless)

# Outside of R: you need to install Docker first.
# Your milleage may vary. You may have to run these commands directly on docker instead of here.
# See https://rpubs.com/johndharrison/RSelenium-Docker for more info.

system("docker pull selenium/standalone-firefox:2.53.0")
system("docker run -d -p 4466:4444 selenium/standalone-firefox:2.53.0")
remDr <- remoteDriver(remoteServerAddr = "192.168.99.100", port = 4466L)
remDr$open()
#

#####################################################################################################################################

#### Google scholar ####

# site: https://scholar.google.com

remDr$navigate("https://scholar.google.com/scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5&hl=pt-BR")

articles_weingast <- tibble(
  value = NA,
  term = NA,
  page = NA
)

k <- 0

for (j in 1:213) { # we had to manually choose the number of pages here; Y.M.M.V.

  Sys.sleep(rpois(1, 5))

  # Getting articles basic information
  k <- k + 1

  webElem <- remDr$findElement("css", "body")

  title <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_rt", " " ))]') %>%
    html_text() %>%
    enframe(name = NULL) %>%
    rename("title" = "value") %>%
    mutate(page = k)

  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
    html_text() %>%
    enframe(name = NULL) %>%
    bind_rows(
      tibble(
        value = "delete",
        term = NA,
        page = NA
      ),
      .
    ) %>%
    bind_cols(., title)

  # Binding articles
  articles_weingast <- bind_rows(articles_weingast, articles_partial)

  # Changing Pages
  next_button <- remDr$findElement(using = "xpath", "/html/body/div/div[11]/div[2]/div[2]/div[3]/div[2]/center/table/tbody/tr/td[12]/a/b")
  next_button$clickElement()

  # Deleting cookies
  remDr$deleteAllCookies()
}

write_csv(articles_weingast, "scholar_weingast_raw.csv")

articles_weingast <- articles_weingast %>%
  select(-term, -page) %>%
  filter(value != "delete") %>%
  slice(2:nrow(.)) %>%
  filter(!grepl("books.google.com", value)) %>%
  filter(!grepl("LIVRO", title)) %>%
  separate(., value, into = c("author", "value"), sep = " -", remove = T, extra = "merge", fill = "right") %>%
  separate(., value, into = c("journal", "year"), sep = ",", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    year_2 = ifelse(is.na(year), journal, year),
    journal = ifelse(is.na(year), NA, journal),
    year = year_2
  ) %>%
  select(-year_2) %>%
  separate(., year, into = c("year", "site"), sep = "-", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    year = gsub("[^0-9 ]", "", value),
    year = gsub("^[0-9]{5,}", "", year),
    year = gsub("^ {1,}", "", year)
  ) %>%
  separate(., year, into = c("year", "junk"), sep = " ", remove = T, extra = "merge", fill = "right") %>%
  separate(., value, into = c("journal", "value"), sep = "-", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    journal_untidy = year,
    year = gsub("[^0-9 ]", "", year)
  )

articles <- articles %>%
  na.omit() %>%
  distinct(., value, .keep_all = T)

write_csv(articles, "google_scholar_clean.csv")

############################################################################################################################

#### SCOPUS ####

# site: https://www.scopus.com/home.uri

# Scraping Scopus requires a bit more of manual labor.
# You can login on scopus through your university/institution and downloading the metadata of the article(s) you want directly from there.
# This way we don't need to scrape the links we are looking for, since we have direct access to them.
# All we need to do after that is to scrape the information of every link from the .csv file we downloaded earlier

scopus <- read_csv("scopus.csv")

scopus <- scopus %>%
  mutate(article = map_chr(Link, ~ {
    remDr$navigate(.x)
    read_html(remDr$getPageSource()[[1]]) %>%
      html_nodes(xpath = '//*[(@id = "abstractSection")]//p') %>%
      html_text() %>%
      paste(., collapse = "\r\n")
  })) %>%
  mutate(
    article = gsub(
      '\r\n\nUse this section to learn about the Topic, find key authors to follow, and view related documents.\n \nLearn more about these Topics\n\n\n"',
      "",
      article
    ),
    article = gsub(
      "Topics are unique areas of research, created using all Scopus publications from 1996 onwards.",
      "",
      article
    ),
    article = gsub(
      "Use this section to learn about the Topic, find key authors to follow, and view related documents.",
      "",
      article
    ),
    article = gsub(
      "Learn more about these Topics",
      "",
      article
    ),
    article = gsub(
      "© 2019, Springer Science\\+Business Media, LLC, part of Springer Nature.",
      "",
      article
    ),
    article = gsub("\r", "", article),
    article = gsub("\n", "", article),
    article = gsub(" {2,}", " ", article),
    article = gsub(" {3,}", "", article)
  )

write_csv(scopus, "scopus_clean.csv")

############################################################################################################################

#### Microsoft Academic ####

# site: https://academic.microsoft.com/home

articles <- list()
k <- 0
remDr$navigate("https://academic.microsoft.com/paper/2076316673/citedby/search?q=The%20Political%20Economy%20of%20Benefits%20and%20Costs%3A%20A%20Neoclassical%20Approach%20to%20Distributive%20Politics&qe=RId%253D2076316673&f=&orderBy=0")

# 1) Getting hyperlinks from articles
for (j in 1:100) {
  k <- k + 1
  print(k)

  # Navigating Website

  # Randomly clicking somewhere in the page
  #  click_body = remDr$findElement(using = 'xpath', '//*[contains(concat( " ", @class, " " ), concat( " ", "header", " " ))]')
  #  click_body$clickElement()

  Sys.sleep(rpois(2, 5))

  # Getting articles' links
  articles[[k]] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(xpath = "//a") %>%
    html_attr("href") %>%
    enframe(name = NULL) %>%
    filter(
      grepl("paper/", value),
      !grepl("citedby", value)
    ) %>%
    mutate(value = paste0("https://academic.microsoft.com/", value))

  # Changing Page
  next_page_others <- remDr$findElement(using = "xpath", "/html/body/div/div/div/router-view/router-view/ma-edp-serp/div/div[2]/div/compose/div/div[2]/ma-pager/div/i[2]")
  next_page_others$clickElement()
}

articles <- articles %>%
  reduce(bind_rows) %>%
  distinct(value, .keep_all = T)

# 2) Navigating through articles and scraping them

articles_links <- articles %>%
  mutate(
    abstract = NA,
    title = NA,
    year = NA,
    journal = NA,
    authors = NA,
    tags = NA
  )

for (i in 1:nrow(articles_links)) {
  remDr$navigate(articles_links$value[i])
  Sys.sleep(rpois(1, 4))

  articles_links$abstract[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "//html/body/div/div/div/router-view/compose[1]/div/div/ma-entity-detail-info/compose/div/div/div[1]/p") %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$title[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "name", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$year[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "name-section", " " ))]//*[contains(concat( " ", @class, " " ), concat( " ", "year", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$journal[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "pub-name", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$authors[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/div/div/ma-entity-detail-info/compose/div/div/div[1]/ma-author-string-collection") %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$tags[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/div/div/ma-entity-detail-info/compose/div/div/div[1]/ma-tag-cloud/div") %>%
    html_text() %>%
    paste(., collapse = " ")
}

write_csv(articles_links, "microsoft_academic_clean.csv")

```

### Searched databases

* {r} [Scopus] (https://www.scopus.com/home.uri)
* {r} [Microsoft Academic] (https://academic.microsoft.com/home)
* {r} [Google Scholar] (https://scholar.google.com/)

### Summary total results

XXXX To Catarina: put here results per database, cross-matching, anything else

### Exclusion criteria

#### Exclusion title and abstract

In the first round, results that were book chapters, doctoral theses, or written in foreign languages were excluded. By reading titles, we also excluded articles which did not fit the distributive politics "scope". For example, a paper titled "Agency loss and the strategic redesign of the presidential office in Colombia" [@mejia2018agency] was excluded in this phase. 1006 articles remained.

We proceeded to reading abstracts. We followed an "inclusion" logic, instead of an exclusion one. We kept all of the articles whose abstracts indicated legislative chambers and government spending were potentially discussed. For example, the article "Pork, parties, and priorities: Partisan politics and overseas military deployments" [@stravers2018pork] passed the first round since pork-barrel politics is central in the distributive politics debate. Yet, it did not pass this phase, as its abstract indicated neither legislative structures nor public expenditure were discussed. We had 373 articles left by the end of this round.

#### Exclusion reading

In this phase, we established three elements that had to be present for an article to be included in the analysis. The first criteria was that the paper ran a regression. Theoretical discussion papers were thus excluded. Second and third, that variables reporting the number of legislators and government expenditure were used in quantitative analyses. If one of them was missing, the paper was excluded. After a rigorous overview of all 373 articles, 48 were kept.

#### Exclusion analysis

For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:

1. Matched treatment variable:
  + N: Number Legislators Lower House
  + logN: Log Number Legislators Lower House
  + K: Number Legislators Upper House

2. Matched outcome variable:
  + ExpPC: Expenditure Per Capita
  + logExpPC: Log Expenditure Per Capita
  + PCTGDP: Percent GDP Public Expenditure

### PRISM

- Number of articles matching the search criteria: **2159**
- Number of articles excluded after title and abstract: **1786**
- Number of articles excluded after reading: 325
- Number of articles excluded before analysis: 23
- Number of articles excluded during the analysis: 0

## Adding articles

```{r, echo=FALSE, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 
          'readxl', 'dmetar')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
lapply(pkgs, installIfNot)

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  elecsys = 'Maj',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  SE = 0.01262/2.12
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  SE = 0.003627/2.51
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  SE = 0.053
))

# Paper 1390
dat <- rbind(dat,
  data.frame(
  id = 1390,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Electoral Systems and Public Spending',
  author = 'Milesi-Ferretti, Perotti, and Rostagno',
  year = 2001,
  authoryear = 'Milesi-Ferretti et al. (2001)',
  journal = 'The Quarterly Journal of Economics',
  web = 'https://www.jstor.org/stable/pdf/2696437.pdf',
  table = 5,
  column = 1,
  indepvar = 'Log Avg Dist Magnitude',
  indepvar2 = 'logN',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 1.05,
  scoef = 'P',
  SE = 1.05/1.10
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'No',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  authoryear = 'Lledo (2003)',
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  scoef = 'N',
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 4,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.001,
  scoef = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  scoef = 'P',
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  scoef = 'P',
  SE = 2.066/7.014
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.1127,
  scoef = 'P',
  SE = 0.0373
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.82,
  scoef = 'N',
  SE = 0.19
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.97,
  scoef = 'P',
  SE = 0.74
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -1.4,
  scoef = 'N',
  SE = 0.64
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 8.3,
  scoef = 'P',
  SE = 2.35
))

dat <- rbind(dat,
  data.frame(
  id = 439,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Legislative term limits and state spending',
  author = 'Erler',
  year = 2007,
  authoryear = 'Erler (2007)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/27698198',
  table = 2,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 3.93,
  scoef = 'P',
  SE = 1.18
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.136,
  scoef = 'P',
  SE = 0.136/2.92
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 5,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.159,
  scoef = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 231,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
  author = 'Baskaran',
  year = 2013,
  authoryear = 'Baskaran (2013)',
  journal = 'European Journal of Political Economy',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
  table = 3,
  column = 4,
  indepvar = 'Parliament seats',
  indepvar2 = 'N',
  depvar = 'Real Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.974,
  scoef = 'P',
  SE = 0.974/1.743
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size lower chamber',
  indepvar2 = 'N',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.0609,
  scoef = 'N',
  SE = 0.0117
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size upper chamber',
  indepvar2 = 'K',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.04,
  scoef = 'N',
  SE = 0.0132
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.003,
  scoef = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 2,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.004,
  scoef = 'N',
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 4,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.174,
  scoef = 'P',
  SE = 0.085
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.21,
  scoef = 'P',
  SE = 4.051
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -0.351,
  scoef = 'N',
  SE = 0.745
))

dat <- rbind(dat,
  data.frame(
  id = 8,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
  author = 'Lewis',
  year = 2019,
  authoryear = 'Lewis (2019)',
  journal = 'Studies in Comparative International Development',
  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
  table = 4,
  column = NA,
  indepvar = 'Legislature size',
  indepvar2 = 'N',
  depvar = 'Log per capita total expenditure',
  depvar2 = 'logExpPC',
  coef = -0.174,
  scoef = 'N',
  SE = (-0.174+0.245)/1.96
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.851,
  scoef = 'N',
  SE = 1.395
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 19.74,
  scoef = 'P',
  SE = 8.406
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'Legislative fragmentation and government spending in presidential democracies: bringing ideological polarization into the picture',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 1,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 1,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.077,
  scoef = 'P',
  SE = 0.028
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 0.0164,
  scoef = 'P',
  SE = 1.313
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 38.44,
  scoef = 'P',
  SE = 19.23
))

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
```

## Descriptive statistics

### Study Year

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
ggplot(dat, aes(x=as.factor(year))) + 
  geom_bar() + xlab('Year') + theme_bw() +
  ylab('')
```

### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
ggplot(dat, aes(x=as.factor(published))) + 
  geom_bar() + xlab('Published study?') + theme_bw() +
  ylab('')
```

### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$depvar2, labels = c('Per Capita Expenditure', 'Percentage GDP Government Expenditure','Log Per Capita Expenditure')))) + 
  geom_bar() + xlab('Dependent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$indepvar2, labels = c('K (upper house legislators)', 'N (lower house legislators)','Log N')))) + 
  geom_bar() + xlab('Independent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Histogram Coefficients

```{r, echo=FALSE}
hist(dat$coef, main = '', xlab = 'Coefficients')
```

### Histogram Standard Errors

```{r, echo=FALSE}
hist(dat$SE, main = '', xlab = 'Standard Errors')
```

### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
ggplot(dat, aes(x=as.factor(scoef))) + 
  geom_bar() + xlab('Coefficient Sign') + theme_bw() +
  ylab('')
```

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.

### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
ggplot(dat, aes(x=as.factor(elecsys))) + 
  geom_bar() + xlab('Electoral system') + theme_bw() +
  ylab('')
```

### Electoral system x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$elecsys)
chisq.test(table(dat$scoef, dat$elecsys), simulate.p.value = T)
```

### Independent Variable x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$indepvar2)
chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
```

### Dependent variables x Independent variables

```{r, echo=FALSE}
table(dat$scoef, dat$depvar2)
chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
```

## Meta-analysis

We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE}
forest(mod)
```

To check heterogeneity of studies, and a possible bias, we conduct an influence analysis below.

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

And as the electoral system seems to confound the results, we add the electoral system to the regressions below:

```{r}
subgroup.analysis.mixed.effects(x = mod, subgroups = aux$elecsys)
```

### PCTGDP x N

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

The influence analysis show that Maldonado is causing a considerable amount of heterogeneity in the data. Below we rerun the analysis excluding Maldonado.

```{r}
# Pooling effects analysis -- ExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='PCTGDP'&id!=230)
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the result is positive and significant. Note that the prediction interval ranges from 0.0011 to 0.0055. As it does not cross zero, in terms of percentage of expenditure, we can confidently say that increasing legislature size is likely to increase the share of government expenditure of the GDP.

And the forest plot:

```{r}
forest(mod)
```

### logExpPC x N

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
forest(mod)
InfluenceAnalysis(x = mod, random = TRUE)
```

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='logExpPC'&id!=102)
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

### ExpPC x logN

There were no studies in this category.

### PCTGDP x logN

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

### logExpPC x logN

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

### ExpPC x K

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- filter(dat,
              indepvar2=='K'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

### PCTGDP x K

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- filter(dat,
              indepvar2=='K'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "EB",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r}
forest(mod)
```

To test heterogeneity, we run an influence analysis below:

```{r}
InfluenceAnalysis(x = mod, random = TRUE)
```

### logExpPC x K

There were no studies in this category.

### Meta-regressions

In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy (N, K, log of N);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

The results follow below, and show null effect for all variables, including the intercept.

```{r, echo=FALSE}
mod <- rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "ML", 
              mods = ~ depvar2+indepvar2+elecsys, 
              test = "knha")
mod
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod)
```

Therefore, no effects.

### 2020-05-17 appendixupdates/appendixV2.Rmd
Original contents of appendixupdates
Version: 2020-05-14

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Search criteria

### Search terms

XXXX

### Searched databases

XXXX To Catarina: name and URL of database searched

### Summary total results

XXXX To Catarina: put here results per database, cross-matching, anything else

### Exclusion criteria

#### Exclusion title and abstract

XXXX To Catarina: what criteria for first round exclusions?

#### Exclusion reading

XXXX To Catarina: criteria second round exclusions

#### Exclusion analysis

For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:

1. Matched treatment variable:
  + N: Number Legislators Lower House
  + logN: Log Number Legislators Lower House
  + K: Number Legislators Upper House

2. Matched outcome variable:
  + ExpPC: Expenditure Per Capita
  + logExpPC: Log Expenditure Per Capita
  + PCTGDP: Percent GDP Public Expenditure

### PRISM

- Number of articles matching the search criteria: XXXX
- Number of articles excluded after title and abstract: XXXX
- Number of articles excluded after reading: XXXX
- Number of articles excluded before analysis: 3
- Number of articles excluded during the analysis: 0

## Adding articles

```{r, echo=FALSE, include=FALSE}
## Starting
set.seed(732578) # From random.org

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 
          'readxl', 'dmetar')

# Install if not already installed
installIfNot <- function(x) {
  if(x %in% rownames(installed.packages()) == FALSE) 
    install.packages(x, dependencies = T)
} 
lapply(pkgs, installIfNot)

# Load packs
lapply(pkgs, require, character.only = T)
rm(pkgs, installIfNot)

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.01262/2.12
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003627/2.51
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.053
))

# Paper 1390
dat <- rbind(dat,
  data.frame(
  id = 1390,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Electoral Systems and Public Spending',
  author = 'Milesi-Ferretti, Perotti, and Rostagno',
  year = 2001,
  authoryear = 'Milesi-Ferretti et al. (2001)',
  journal = 'The Quarterly Journal of Economics',
  web = 'https://www.jstor.org/stable/pdf/2696437.pdf',
  table = 5,
  column = 1,
  indepvar = 'Log Avg Dist Magnitude',
  indepvar2 = 'logN',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 1.05,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.05/1.10
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'No',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  authoryear = 'Lledo (2003)',
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  scoef = 'N',
  scoefsig = NA,
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 4,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.001,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.066/7.014
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'House size',
  indepvar2 = 'N',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.014,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 1415,
  published = 'No',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
  author = 'Ricciuti',
  year = 2004,
  authoryear = 'Ricciuti (2004)',
  journal = NA,
  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
  table = 3,
  column = 1,
  indepvar = 'Senate size',
  indepvar2 = 'K',
  depvar = 'Government spending',
  depvar2 = 'PCTGDP',
  coef = 0.016,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.012
))

dat <- rbind(dat,
  data.frame(
  id = 578,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Districting and Government Overspending',
  author = 'Baqir',
  year = 2002,
  authoryear = 'Baqir (2002)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
  table = 4,
  column = 4,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'ln(Government expenditure per capita)',
  depvar2 = 'logExpPC',
  coef = 0.1127,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.0373
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in lower chamber',
  indepvar2 = 'N',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.82,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.19
))

dat <- rbind(dat,
  data.frame(
  id = 467,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Institutional constraints on government spending',
  author = 'Primo',
  year = 2006,
  authoryear = 'Primo (2006)',
  journal = 'Economics and Politics',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
  table = 5,
  column = 4,
  indepvar = 'Seats in upper chamber',
  indepvar2 = 'K',
  depvar = 'Real state and local expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.97,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.74
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Lower chamber size',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = -1.4,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.64
))

dat <- rbind(dat,
  data.frame(
  id = 441,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
  author = 'Chen and Malhotra',
  year = 2007,
  authoryear = 'Chen and Malhotra (2007)',
  journal = 'American Political Science Review',
  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
  table = 3,
  column = 1,
  indepvar = 'Upper chamber size',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 8.3,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.35
))

dat <- rbind(dat,
  data.frame(
  id = 439,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Legislative term limits and state spending',
  author = 'Erler',
  year = 2007,
  authoryear = 'Erler (2007)',
  journal = 'Public Choice',
  web = 'https://www.jstor.org/stable/27698198',
  table = 2,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 3.93,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.18
))

dat <- rbind(dat,
  data.frame(
  id = 408,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The impact of government structure on local public expenditures',
  author = 'MacDonald',
  year = 2008,
  authoryear = 'MacDonald (2008)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
  table = 5,
  column = 3,
  indepvar = 'ln(Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.136,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.136/2.92
))

dat <- rbind(dat,
  data.frame(
  id = 288,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
  author = 'Pettersson-Lidbom',
  year = 2012,
  authoryear = 'Pettersson-Lidbom (2012)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
  table = 3,
  column = 5,
  indepvar = 'Council Size',
  indepvar2 = 'N',
  depvar = 'Log Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.159,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.041
))

dat <- rbind(dat,
  data.frame(
  id = 231,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
  author = 'Baskaran',
  year = 2013,
  authoryear = 'Baskaran (2013)',
  journal = 'European Journal of Political Economy',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
  table = 3,
  column = 4,
  indepvar = 'Parliament seats',
  indepvar2 = 'N',
  depvar = 'Real Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.974,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.974/1.743
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size lower chamber',
  indepvar2 = 'N',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.0609,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0117
))

dat <- rbind(dat,
  data.frame(
  id = 230,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  title = 'Legislatures, Leaders and Leviathans',
  author = 'Maldonado',
  year = 2012,
  authoryear = 'Maldonado (2012)',
  journal = 'Social Science Quarterly',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
  table = 2,
  column = 2,
  indepvar = 'Size upper chamber',
  indepvar2 = 'K',
  depvar = 'Government Share of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.04,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.0132
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 1,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = -0.003,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 220,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
  author = 'Bjedov, Lapointe, and Madiès',
  year = 2014,
  authoryear = 'Bjedov et al. (2014)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
  table = 3,
  column = 2,
  indepvar = 'Number of seats',
  indepvar2 = 'N',
  depvar = 'Spending (%) GDP',
  depvar2 = 'PCTGDP',
  coef = -0.004,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.02
))

dat <- rbind(dat,
  data.frame(
  id = 208,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
  author = 'Kessler',
  year = 2014,
  authoryear = 'Kessler (2014)',
  journal = 'Journal of Political Economy',
  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
  table = 2,
  column = 4,
  indepvar = 'Council size',
  indepvar2 = 'N',
  depvar = 'Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.174,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.085
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Upper chamber (senate) seats',
  indepvar2 = 'K',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = 8.21,
  scoef = 'P',
  scoefsig = 'P',
  SE = 4.051
))

dat <- rbind(dat,
  data.frame(
  id = 3,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
  author = 'Crowley',
  year = 2019,
  authoryear = 'Crowley (2019)',
  journal = 'Southern Economic Journal',
  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
  table = 2,
  column = 1,
  indepvar = 'Lower chamber (senate) seats',
  indepvar2 = 'N',
  depvar = 'Per capita total expenditure',
  depvar2 = 'ExpPC',
  coef = -0.351,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.745
))

dat <- rbind(dat,
  data.frame(
  id = 8,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
  author = 'Lewis',
  year = 2019,
  authoryear = 'Lewis (2019)',
  journal = 'Studies in Comparative International Development',
  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
  table = 4,
  column = NA,
  indepvar = 'Legislature size',
  indepvar2 = 'N',
  depvar = 'Log per capita total expenditure',
  depvar2 = 'logExpPC',
  coef = -0.174,
  scoef = 'N',
  scoefsig = 'N',
  SE = (-0.174+0.245)/1.96
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.851,
  scoef = 'N',
  scoefsig = NA,
  SE = 1.395
))

dat <- rbind(dat,
  data.frame(
  id = 42,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Court-ordered redistricting and the law of 1/n',
  author = 'Lee and Park',
  year = 2018,
  authoryear = 'Lee and Park (2018)',
  journal = 'Public Choice',
  web = NA,
  table = 2,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Total expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 19.74,
  scoef = 'P',
  scoefsig = 'P',
  SE = 8.406
))

dat <- rbind(dat,
  data.frame(
  id = 82,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'Legislative fragmentation and government spending in presidential democracies: bringing ideological polarization into the picture',
  author = 'Höhmann',
  year = 2017,
  authoryear = 'Höhmann (2017)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
  table = 2,
  column = 1,
  indepvar = 'Total number of seats in the legislature',
  indepvar2 = 'N',
  depvar = 'Log expenditure per capita',
  depvar2 = 'logExpPC',
  coef = -0.03,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01
))

dat <- rbind(dat,
  data.frame(
  id = 102,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
  author = 'Drew and Dollery',
  year = 2017,
  authoryear = 'Drew and Dollery (2017)',
  journal = 'Urban Affairs Review',
  web = '10.1007/s11127-016-0369-9',
  table = 2,
  column = 1,
  indepvar = 'No. of representatives',
  indepvar2 = 'N',
  depvar = 'Ln Expenditure per capita',
  depvar2 = 'logExpPC',
  coef = 0.077,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.028
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Lower',
  indepvar2 = 'N',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 0.0164,
  scoef = 'P',
  scoefsig = NA,
  SE = 1.313
))

dat <- rbind(dat,
  data.frame(
  id = 132,
  published = 'Yes',
  usemeta = 1, 
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  title = 'Supermajority rule and bicameral bargaining',
  author = 'Lee',
  year = 2016,
  authoryear = 'Lee (2016)',
  journal = 'Public Choice',
  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
  table = 3,
  column = 1,
  indepvar = 'Upper',
  indepvar2 = 'K',
  depvar = 'Per capita expenditure',
  depvar2 = 'ExpPC',
  coef = 38.44,
  scoef = 'P',
  scoefsig = 'P',
  SE = 19.23
))

dat <- dat[order(dat$id),]
dat <- dat[!is.na(dat$coef),]
row.names(dat) <- NULL
levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
levels(dat$scoef) <- c('Negative', 'Positive')
levels(dat$scoefsig) <- c('Negative', 'Positive')
```

## Descriptive statistics

### Study Year

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
ggplot(dat, aes(x=as.factor(year))) + 
  geom_bar() + xlab('Year') + theme_bw() +
  ylab('')
```

### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
ggplot(dat, aes(x=as.factor(published))) + 
  geom_bar() + xlab('Published study?') + theme_bw() +
  ylab('')
```

### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$depvar2, labels = c('Per Capita Expenditure', 'Percentage GDP Government Expenditure','Log Per Capita Expenditure')))) + 
  geom_bar() + xlab('Dependent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Independent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
ggplot(dat, aes(x=factor(dat$indepvar2, labels = c('K (upper house legislators)', 'N (lower house legislators)','Log N')))) + 
  geom_bar() + xlab('Independent Variables') + theme_bw() +
  ylab('') + coord_flip()
```

### Histogram Coefficients

```{r, echo=FALSE}
hist(dat$coef, main = '', xlab = 'Coefficients')
```

### Histogram Standard Errors

```{r, echo=FALSE}
hist(dat$SE, main = '', xlab = 'Standard Errors')
```

### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
ggplot(dat, aes(x=as.factor(scoef))) + 
  geom_bar() + xlab('Coefficient Sign') + theme_bw() +
  ylab('')
```

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.

### Electoral system

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
ggplot(dat, aes(x=as.factor(elecsys2))) + 
  geom_bar() + xlab('Electoral system') + theme_bw() +
  ylab('')
```

### Electoral system x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$elecsys2)
chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
```

### Independent Variable x Sign Coefficient

```{r, echo=FALSE}
table(dat$scoef, dat$indepvar2)
chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
```

### Dependent variables x Independent variables

```{r, echo=FALSE}
table(dat$scoef, dat$depvar2)
chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
```

## Meta-analysis

We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.

### ExpPC x N

```{r, echo=FALSE}
# Pooling effects analysis -- ExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

#### Electoral system subgroup analysis

The law of 1/n was created for majoritarian systems. In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems. We estimated a subgroup analysis using a binary electoral system.

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

### PCTGDP x N

This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### logExpPC x N

This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.

```{r}
# Pooling effects analysis -- logExpPC x N
aux <- filter(dat,
              indepvar2=='N'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### ExpPC x logN

There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.

### PCTGDP x logN

This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.

```{r}
# Pooling effects analysis -- PCTGDP x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### logExpPC x logN

In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).

```{r}
# Pooling effects analysis -- logExpPC x logN
aux <- filter(dat,
              indepvar2=='logN'&depvar2=='logExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### ExpPC x K

Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).

```{r}
# Pooling effects analysis -- ExpPC x K
aux <- filter(dat,
              indepvar2=='K'&depvar2=='ExpPC')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### PCTGDP x K

This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).

```{r}
# Pooling effects analysis -- PCTGDP x K
aux <- filter(dat,
              indepvar2=='K'&depvar2=='PCTGDP')
mod <-
  metagen(coef, SE, data=aux, 
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
mod
```

And the forest plot:

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
```

Highlights:

1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
3. The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`. Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`

### logExpPC x K

No studies related the log of per capita expenditure with the size of upper house (K).

### Meta-regressions

In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:

1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
2. The type of the independent variable in the stydy (N, K, log of N);
3. The electoral system (Majoritarian, Proportional Representation, and Mixed).

The results follow below, and show null effect for all variables, including the intercept.

```{r, echo=FALSE}
mod <- rma(yi = coef, 
              sei = SE, 
              data = dat, 
              method = "REML", 
              mods = ~ depvar2+indepvar2+elecsys, 
              test = "knha")
mod
```

As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.

```{r, echo=FALSE}
permutest(mod)
```

Therefore, no effects.

## Theory of Meta Analysis

There are two main estimators for conducting meta analysis: fixed effects and random effects models. The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect. The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.

In this paper, we use the random effects model. The empirical papers testing the law of 1/n are very diverse. We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:

1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
2. **Electoral systems**: Majoritarian, PR, Mixed.
3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.

These sources of heterogeneity have two implications. First, it makes our estimates very disperse. The heterogeneity tests are all but one significant. When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates. Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised. Thus, we opt for random effects model.

Let each study having an effect of $T_i$. In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:

\[
T_i \ = \ \theta_i + \varepsilon_i
\]

And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:

\[
T_i \ = \ \mu + \xi_i + \varepsilon_i
\]

And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.

In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html]. To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$. We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].

### 2020-05-17 appendixupdates/appendixV3.Rmd
Original contents of appendixupdates
Version: 2020-05-14

--- 2020-05-01 appendix/appendixV5.Rmd
@@
 date: "12/25/2019"
-header-includes:
-- \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-
 output: pdf_document
 ---
-
-```{=latex}
-\tableofcontents
-```
 
@@
 
-```{r global_options, include=FALSE}
+```{r, echo=FALSE, include=FALSE}
 ## Starting
@@
 # Needed packages
-pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
-          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')
+pkgs <- c('tidyverse', 'meta', 'metafor', 
+          'readxl', 'dmetar')
 
@@
   if(x %in% rownames(installed.packages()) == FALSE) 
-    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
+    install.packages(x, dependencies = T)
 } 
@@
 rm(pkgs, installIfNot)
-
-# Knitr options
-knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
-
-```
-
-```{r, echo=FALSE, include=FALSE}
 
@@
 dat <- dat %>%
-  filter(usemeta == 1)
-```
-\newpage
+  filter(usemeta==1)
+```
+
 ## Descriptive statistics
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
-dat %>%
-  ggplot(aes(x = as.factor(year))) + 
-    geom_bar(color = "black") + 
-  labs(x = "",
-       y = "") + 
-  theme_bw()
-```
-
-\newpage
+ggplot(dat, aes(x=as.factor(year))) + 
+  geom_bar() + xlab('') + theme_bw() +
+  ylab('')
+```
+
 ### Published?
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
-dat %>%
-  ggplot(aes(x = as.factor(published))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Published study?",
-       y = "") + 
-  theme_bw()
-
-```
-
-\newpage
+ggplot(dat, aes(x=as.factor(published))) + 
+  geom_bar() + xlab('Published study?') + theme_bw() +
+  ylab('')
+```
+
 ### Dependent variables
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
-dat %>%
-  mutate(depvar2 = factor(depvar2, 
-                          labels = c("Per Capita Expenditure",
-                                     "Percentage GDP Government Expenditure",
-                                     "Log Per Capita Expenditure"))) %>%
-  ggplot(aes(x = depvar2)) +
-    geom_bar(color = "black") + 
-  labs(x = "Dependent Variables",
-       y = "") + 
-  coord_flip() + 
-  theme_bw()
-
-```
-
-\newpage
+ggplot(dat, aes(x=factor(dat$depvar2, labels = c('Per Capita Expenditure', 'Percentage GDP Government Expenditure','Log Per Capita Expenditure')))) + 
+  geom_bar() + xlab('Dependent Variables') + theme_bw() +
+  ylab('') + coord_flip()
+```
+
 ### Independent variables
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
-dat %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
-                                                  'N (lower house legislators)',
-                                                  'Log N'))) %>%
-  ggplot(aes(x = indepvar2)) + 
-    geom_bar(color = "black") + 
-  labs(x = "Independent Variables",
-       y = "") +
-  coord_flip() +
-  theme_bw() 
-```
-
-\newpage
+ggplot(dat, aes(x=factor(dat$indepvar2, labels = c('K (upper house legislators)', 'N (lower house legislators)','Log N')))) + 
+  geom_bar() + xlab('Independent Variables') + theme_bw() +
+  ylab('') + coord_flip()
+```
+
 ### Histogram Coefficients
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
-dat %>%
-  ggplot(aes(x = coef)) +
-  geom_histogram(bins = 15, color = "black") + 
-  labs(x = "Coefficients") + 
-  theme_bw()
-
-```
-
-\newpage
+```{r, echo=FALSE}
+hist(dat$coef, main = '', xlab = 'Coefficients')
+```
+
 ### Histogram Standard Errors
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
-dat %>%
-  ggplot(aes(x = SE)) +
-  geom_histogram(bins = 10, color = "black") + 
-  labs(x = "Standard Errors") + 
-  theme_bw()
-
-```
-
-\newpage
+```{r, echo=FALSE}
+hist(dat$SE, main = '', xlab = 'Standard Errors')
+```
+
 ### Sign Coefficients
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
-dat %>%
-  ggplot(aes(x=as.factor(scoef))) + 
-  geom_bar(color = "black") + 
-  labs(x = "Coefficient Sign",
-       y = "") +
-  theme_bw()
+ggplot(dat, aes(x=as.factor(scoef))) + 
+  geom_bar() + xlab('Coefficient Sign') + theme_bw() +
+  ylab('')
 ```
@@
 ```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'N')
+aux <- filter(dat, indepvar2=='N')
 binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
@@
 ```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'K')
+aux <- filter(dat, indepvar2=='K')
 binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
@@
 
-\newpage
 ### Electoral system
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
-dat %>%
-  ggplot(aes(x=as.factor(elecsys2))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Electoral system",
-       y = "") + 
-  theme_bw()
-```
-
-\newpage
+ggplot(dat, aes(x=as.factor(elecsys2))) + 
+  geom_bar() + xlab('Electoral system') + theme_bw() +
+  ylab('')
+```
+
 ### Electoral system x Sign Coefficient
@@
 
-\newpage
 ### Independent Variable x Sign Coefficient
@@
 
-\newpage
 ### Dependent variables x Independent variables
@@
 
-\newpage 
-### Descriptive Stats of Moderators
-
-```{r, echo=F}
-
-# Table - General
-
-aux <- dat %>%
-  group_by(depvar2) %>%
-  summarise(n = n(),
-            mean_coef = mean(coef, na.rm = T),
-            median_coef = median(coef, na.rm = T)) %>%
-  mutate(pct = round(n/sum(n, na.rm = T), digits = 2)) %>%
-  select(depvar2, n, pct, mean_coef, median_coef) %>%
-  rename(` ` = depvar2,
-         N = n,
-         Pct = pct,
-         Mean = mean_coef,
-         Median = median_coef)
-
-kable(aux, 
-      booktabs = T,
-      align = "c",
-      linesep ='') %>% 
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-```
-
-### Descriptive Stats of Moderators by Year
-
-```{r, echo=F}
-
-#Table: by year
-
-aux <- dat %>%
-  group_by(depvar2, year) %>%
-  summarise(n = n(),
-            mean_coef = round(mean(coef, na.rm = T), digits = 3),
-            median_coef = round(median(coef, na.rm = T), digits = 3)) %>%
-  group_by(year) %>%
-  mutate(pct = paste0(100*(round(n/sum(n, na.rm = T), digits = 2)), " %")) %>%
-  select(depvar2, year, n, pct, mean_coef, median_coef) %>%
-  arrange(year) %>%
-  rename(` ` = depvar2,
-         Year = year,
-         N = n,
-         Pct = pct,
-         Mean = mean_coef,
-         Median = median_coef
-         )
-
-kable(aux, 
-      booktabs = T,
-      align = "c",
-      linesep ='') %>% 
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-```
-
-\newpage
 ## Meta-analysis
 
-We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
+We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
 
@@
 # Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+aux <- filter(dat,
+              indepvar2=='N'&depvar2=='ExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f1 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f1
-```
-
-```{r,include=F,warning=F}
-f1 + 
-  labs(caption = "ExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE)
 ```
@@
 
-\newpage
 #### Electoral system subgroup analysis
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
 mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
-
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f1b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f1b
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3,
+       test.subgroup.random = TRUE)
 ```
@@
 
-\newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-\newpage
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+### PCTGDP x N
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
 
 ```{r}
-# Pooling effects analysis -- ExpPC x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- PCTGDP x N
+aux <- filter(dat,
+              indepvar2=='N'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f2 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f2
-```
-
-```{r,include=F,warning=F}
-f2 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fb.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE)
 ```
@@
 
-\newpage
 ### logExpPC x N
@@
 # Pooling effects analysis -- logExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(
-  coef, SE, data=aux, 
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction = TRUE,
-  sm="SMD"
-  )
-
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f3 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f3
-```
-
-```{r,include=F,warning=F}
-f3 + 
-  labs(caption = "logExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fc.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
-
-```{r}
-# Pooling effects analysis -- logExpPC x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+aux <- filter(dat,
+              indepvar2=='N'&depvar2=='logExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f4 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f4
-```
-
-```{r,include=F,warning=F}
-f4 + 
-  labs(caption = "logExpPC x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fd.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-\newpage
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+### ExpPC x logN
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
+### PCTGDP x logN
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- PCTGDP x logN
+aux <- filter(dat,
+              indepvar2=='logN'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f5 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f5
-```
-
-```{r,include=F,warning=F}
-f5 + 
-  labs(caption = "PCTGDP x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fe.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-\newpage
-### PCTGDP x logN
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+### logExpPC x logN
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(
-  coef, SE, data=aux, 
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction=TRUE,
-  sm="SMD"
-  )
-
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f6 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f6
-```
-
-```{r,include=F,warning=F}
-f6 + 
-  labs(caption = "PCTGDP x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/ff.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### PCTGDP x K
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
-
-```{r}
-# Pooling effects analysis -- PCTGDP x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- logExpPC x logN
+aux <- filter(dat,
+              indepvar2=='logN'&depvar2=='logExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f7 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f7
-```
-
-```{r,include=F,warning=F}
-f7 + 
-  labs(caption = "PCTGDP x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fg.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-\newpage
-```{r,include=F,warning=F}
-blank = ggplot() + 
-  geom_blank() +
-  theme_minimal()
-blank
-ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")
-
-plots = list.files(path = "./plots/", pattern = "*.png") %>%
-  map(~{
-    image_read(path = paste0("./plots/", .x)) %>%
-      image_rotate(., 270) %>%
-      image_border(., "#ffffff ", "90x18")
-  })
-```
-
-```{r, echo=FALSE, fig.width=20, fig.height=5}
-
-p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
-p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
-p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
-p_full = image_append(c(p_1, p_2, p_3))
-
-p_full
-
-```
-
-\newpage
-## Meta-Analysis (all coefficients)
-
-### ExpPC x N
-
-```{r, echo=FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+### ExpPC x K
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+
+```{r}
+# Pooling effects analysis -- ExpPC x K
+aux <- filter(dat,
+              indepvar2=='K'&depvar2=='ExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f8 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 9, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f8
-```
-
-```{r,include=F,warning=F}
-f8 + 
-  labs(caption = "ExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fh.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-\newpage
-#### Electoral system subgroup analysis
-
-The law of 1/n was created for majoritarian systems.
-In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary electoral system.
-
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f8b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f8b
-```
-
-Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
-
-\newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-\newpage
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+### PCTGDP x K
+
+This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
 
 ```{r}
-# Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- PCTGDP x K
+aux <- filter(dat,
+              indepvar2=='K'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f9 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f9
-```
-
-```{r,include=F,warning=F}
-f9 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fi.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-\newpage
-### logExpPC x N
-
-This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
-
-```{r}
-# Pooling effects analysis -- logExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+### logExpPC x K
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
+## Meta-Analysis (all coefficients)
+
+### ExpPC x N
+
+```{r, echo=FALSE}
+# Pooling effects analysis -- ExpPC x N
+aux <- filter(fulldat,
+              indepvar2=='N'&depvar2=='ExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f10 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f10
-```
-
-```{r,include=F,warning=F}
-f10 + 
-  labs(caption = "logExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fj.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE)
 ```
@@
 
-\newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+#### Electoral system subgroup analysis
+
+The law of 1/n was created for majoritarian systems.
+In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
+We estimated a subgroup analysis using a binary electoral system.
+
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
+mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3,
+       test.subgroup.random = TRUE)
+```
+
+Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
+The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
+Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+
+### PCTGDP x N
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
 
 ```{r}
-# Pooling effects analysis -- logExpPC x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- PCTGDP x N
+aux <- filter(fulldat,
+              indepvar2=='N'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f11 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f11
-```
-
-```{r,include=F,warning=F}
-f11 + 
-  labs(caption = "logExpPC x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fk.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE)
 ```
@@
 
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
-\newpage
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+### logExpPC x N
+
+This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- logExpPC x N
+aux <- filter(fulldat,
+              indepvar2=='N'&depvar2=='logExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f12 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 10, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f12
-```
-
-```{r,include=F,warning=F}
-f12 + 
-  labs(caption = "PCTGDP x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fl.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
+### ExpPC x logN
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
 ### PCTGDP x logN
@@
 # Pooling effects analysis -- PCTGDP x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
+aux <- filter(fulldat,
+              indepvar2=='logN'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f13 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f13
-```
-
-```{r,include=F,warning=F}
-f13 + 
-  labs(caption = "PCTGDP x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 20, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fm.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-### PCTGDP x K
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
+### logExpPC x logN
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
 
 ```{r}
-# Pooling effects analysis -- PCTGDP x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
+# Pooling effects analysis -- logExpPC x logN
+aux <- filter(fulldat,
+              indepvar2=='logN'&depvar2=='logExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
           studlab=paste(authoryear),
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f14 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f14
-```
-
-```{r,include=F,warning=F}
-f14 + 
-  labs(caption = "PCTGDP x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fn.png", width = 30, height = 18.75, units = "cm")
-
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+### ExpPC x K
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+
+```{r}
+# Pooling effects analysis -- ExpPC x K
+aux <- filter(fulldat,
+              indepvar2=='K'&depvar2=='ExpPC')
+mod <-
+  metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
 ```
@@
 
-```{r, echo=FALSE, fig.width=20, fig.height=2}
-
-p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
-p_2 = image_append(c(plots[[13]], plots[[12]], plots[[11]]), stack = T)
-p_3 = image_append(c(plots[[15]],plots[[14]],plots[[15]]), stack = T)
-p_full = image_append(c(p_1, p_2, p_3))
-
-p_full
-
-```
-
-\newpage
+### PCTGDP x K
+
+This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
+
+```{r}
+# Pooling effects analysis -- PCTGDP x K
+aux <- filter(fulldat,
+              indepvar2=='K'&depvar2=='PCTGDP')
+mod <-
+  metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
+forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
+       prediction = TRUE, digits.se = 3)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+### logExpPC x K
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
 ## Meta-regressions
-
-### Meta-regressions for Expenditure measured as
-
-### Meta-regressions for Expenditure as a Percentage of the GDP
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='PCTGDP',
-            slab = dat$authoryear)
-
-mod1 <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "PCTGDP"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod1_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-We have the following results for the meta-regressions of Expenditure Per Capita:
-
-1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
-2. Year has null effect.
-3. Unpublished papers tend to have higher coefficients than published papers.
-4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-mod2 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-
-mod <- permutest(mod, progbar = F)
-mod
-
-mod2_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-For all the coefficients, we have the following results:
-
-1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
-2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
-3. Unpublished papers tend to have higher coefficients than published papers.
-4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
-
-### Meta-regressions for Expenditure Per Capita
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear)
-
-mod3 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod3_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-We have the following results for the meta-regressions of Expenditure Per Capita:
-
-1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2. Year has null effect.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
-4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
-5. When passing from `Local` to `State` level, decreases the detected effects.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-mod4 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-
-mod <- permutest(mod, progbar = F)
-mod
-
-mod4_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:
-
-1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2. Year has now a positive effect on coefficient sizes.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
-4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
-5. All other coeffients were not significant.
-
-### Meta-regressions for the Log of Expenditure Per Capita
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-mod5 <- tibble(
-   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod5_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-mod5_permu %>%
-  select(-model) %>%
-  kable(booktabs = T,align = "c",linesep ='') %>%
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-```
-
-We have the following results for the meta-regressions of Log of Expenditure Per Capita:
-
-1. Unpublished papers report a significantly higher coefficient.
-2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-3. All other coefficients remained insignificant.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-mod6 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod6_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  T = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
-
-1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
-2. All other coefficients remained insignificant.
-
-```{r, echo=F, warning=F,error=F,message=F}
-coefs = bind_rows(
-  mod1,
-  mod2,
-  mod3,
-  mod4,
-  mod5) %>%
-  select(` `) %>%
-  distinct()
-
-aux = list(mod3, mod5, mod1) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "Base") %>%
-  select(type, everything())
-
-aux2 = list(mod4, mod6, mod2) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "All Coefs") %>%
-  select(type, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"))
-
-```
-
-\blandscape
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = T,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value"
-      ),
-  caption = "Summary of Models"
-    ) %>% 
-  collapse_rows(
-    1:3,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header"))
-
-```
-\elandscape
-
-```{r, echo=F, warning=F,error=F,message=F}
-coefs = bind_rows(
-  mod1_permu,
-  mod2_permu,
-  mod3_permu,
-  mod4_permu,
-  mod5_permu) %>%
-  select(` `) %>%
-  distinct()
-
-aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "Base") %>%
-  select(type, everything())
-
-aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(type = "All Coefs") %>%
-  select(type, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"))
-
-```
-
-\blandscape
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = T,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "T",
-        "P-Value"
-      ),
-          caption = "Summary of Models (Permutest)"
-    ) %>% 
-  collapse_rows(
-    1:3,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 4, "logExpPC" = 4, "PCTGDP" = 4)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header"))
-
-```
-\elandscape
-
-\newpage
-## Theory of Meta Analysis
-
-There are two main estimators for conducting meta analysis: fixed effects and random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
-
-In this paper, we use the random effects model.
-The empirical papers testing the law of 1/n are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
-
-1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
-2. **Electoral systems**: Majoritarian, PR, Mixed.
-3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
-
-These sources of heterogeneity have two implications.
-First, it makes our estimates very disperse.
-The heterogeneity tests are all but one significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
-Thus, we opt for random effects model.
-
-Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
-
-\[
-T_i \ = \ \theta_i + \varepsilon_i
-\]
-
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
-
-\[
-T_i \ = \ \mu + \xi_i + \varepsilon_i
-\]
-
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
-To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].
-
-## Robustness: Full model meta-regressions combined
 
@@
               test = "knha")
-
 ```
@@
 ```
+
+Therefore, no effects.
 
@@
 
-```{r, echo=F, warning=F}
+```{r}
 permutest(mod, progbar = F)
-
-```
+```
+
+## Theory of Meta Analysis
+
+There are two main estimators for conducting meta analysis: fixed effects and random effects models.
+The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
+The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+
+In this paper, we use the random effects model.
+The empirical papers testing the law of 1/n are very diverse.
+We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
+
+1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
+2. **Electoral systems**: Majoritarian, PR, Mixed.
+3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
+
+These sources of heterogeneity have two implications.
+First, it makes our estimates very disperse.
+The heterogeneity tests are all but one significant.
+When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
+Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
+Thus, we opt for random effects model.
+
+Let each study having an effect of $T_i$.
+In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
+
+\[
+T_i \ = \ \theta_i + \varepsilon_i
+\]
+
+And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
+
+\[
+T_i \ = \ \mu + \xi_i + \varepsilon_i
+\]
+
+And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
+
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
+To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].

### 2020-05-17 appendixupdates/appendixV4.Rmd
Original contents of appendixupdates
Version: 2020-05-14

--- 2020-05-17 appendixupdates/appendixV3.Rmd
@@
 
+### Meta-regressions for Expenditure as a Percentage of the GDP
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='PCTGDP',
+            slab = dat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE}
+permutest(mod, progbar = F)
+```
+
+We have the following results for the meta-regressions of Expenditure Per Capita:
+
+1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
+2. Year has null effect.
+3. Unpublished papers tend to have higher coefficients than published papers.
+4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='PCTGDP',
+            slab = fulldat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+```{r}
+permutest(mod, progbar = F)
+```
+
+For all the coefficients, we have the following results:
+
+1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
+2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
+3. Unpublished papers tend to have higher coefficients than published papers.
+4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
+
+### Meta-regressions for Expenditure Per Capita
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='ExpPC',
+            slab = dat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE}
+permutest(mod, progbar = F)
+```
+
+We have the following results for the meta-regressions of Expenditure Per Capita:
+
+1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
+2. Year has null effect.
+3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
+4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
+5. When passing from `Local` to `State` level, decreases the detected effects.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='ExpPC',
+            slab = fulldat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+```{r}
+permutest(mod, progbar = F)
+```
+
+With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:
+
+1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
+2. Year has now a positive effect on coefficient sizes.
+3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
+4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
+5. All other coeffients were not significant.
+
+### Meta-regressions for the Log of Expenditure Per Capita
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='logExpPC',
+            slab = dat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE}
+permutest(mod, progbar = F)
+```
+
+We have the following results for the meta-regressions of Log of Expenditure Per Capita:
+
+1. Unpublished papers report a significantly higher coefficient.
+2. In terms of the modeling, passing from `OLS` to `PANEL`increases the detected effects.
+3. All other coefficients remained insignificant.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='logExpPC',
+            slab = fulldat$authoryear)
+```
+
+```{r}
+summary(mod)
+```
+
+```{r}
+permutest(mod, progbar = F)
+```
+
+With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
+
+1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
+2. All other coefficients remained insignificant.
+
+## Theory of Meta Analysis
+
+There are two main estimators for conducting meta analysis: fixed effects and random effects models.
+The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
+The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+
+In this paper, we use the random effects model.
+The empirical papers testing the law of 1/n are very diverse.
+We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
+
+1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
+2. **Electoral systems**: Majoritarian, PR, Mixed.
+3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
+
+These sources of heterogeneity have two implications.
+First, it makes our estimates very disperse.
+The heterogeneity tests are all but one significant.
+When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
+Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
+Thus, we opt for random effects model.
+
+Let each study having an effect of $T_i$.
+In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
+
+\[
+T_i \ = \ \theta_i + \varepsilon_i
+\]
+
+And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
+
+\[
+T_i \ = \ \mu + \xi_i + \varepsilon_i
+\]
+
+And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
+
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
+To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].
+
+## Robustness: Full model meta-regressions combined
+
 In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:
@@
 
-Therefore, no effects.
-
 In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD).
@@
 ```
-
-## Theory of Meta Analysis
-
-There are two main estimators for conducting meta analysis: fixed effects and random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
-
-In this paper, we use the random effects model.
-The empirical papers testing the law of 1/n are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
-
-1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
-2. **Electoral systems**: Majoritarian, PR, Mixed.
-3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
-
-These sources of heterogeneity have two implications.
-First, it makes our estimates very disperse.
-The heterogeneity tests are all but one significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
-Thus, we opt for random effects model.
-
-Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
-
-\[
-T_i \ = \ \theta_i + \varepsilon_i
-\]
-
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
-
-\[
-T_i \ = \ \mu + \xi_i + \varepsilon_i
-\]
-
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
-To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].

### 2020-05-17 appendixupdates/appendix_final.Rmd
moving file

--- 2020-05-02 appendix/appendixV5.Rmd
@@
 date: "12/25/2019"
-header-includes:
+header_includes:
 - \usepackage{booktabs}
-- \usepackage{longtable}
-- \usepackage{array}
-- \usepackage{multirow}
-- \usepackage{wrapfig}
-- \usepackage{float}
-- \usepackage{colortbl}
-- \usepackage{pdflscape}
-- \usepackage{tabu}
-- \usepackage{threeparttable}
-- \usepackage{threeparttablex}
-- \usepackage[normalem]{ulem}
-- \usepackage{makecell}
-- \usepackage{xcolor}
 - \usepackage{pdflscape}
@@
 - \newcommand{\elandscape}{\end{landscape}}
-
 output: pdf_document
+urlcolor: blue
 ---
-
-```{=latex}
-\tableofcontents
-```
 
@@
 ```
-
-## Search criteria
-
-### Search terms
-
-XXXX
-
-### Searched databases
-
-XXXX To Catarina: name and URL of database searched
-
-### Summary total results
-
-XXXX To Catarina: put here results per database, cross-matching, anything else
-
-### Exclusion criteria
-
-#### Exclusion title and abstract
-
-XXXX To Catarina: what criteria for first round exclusions?
-
-#### Exclusion reading
-
-XXXX To Catarina: criteria second round exclusions
-
-#### Exclusion analysis
-
-For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:
-
-1. Matched treatment variable:
-  + N: Number Legislators Lower House
-  + logN: Log Number Legislators Lower House
-  + K: Number Legislators Upper House
-
-2. Matched outcome variable:
-  + ExpPC: Expenditure Per Capita
-  + logExpPC: Log Expenditure Per Capita
-  + PCTGDP: Percent GDP Public Expenditure
-
-### PRISM
-
-- Number of articles matching the search criteria: XXXX
-- Number of articles excluded after title and abstract: XXXX
-- Number of articles excluded after reading: XXXX
-- Number of articles excluded before analysis: 3
-- Number of articles excluded during the analysis: 0
-
-We have 26 articles in the meta-analysis.
-
-## Meta-analysis dataset
-
-The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).
-
-## Adding articles
 
@@
 # Needed packages
-pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
-          'dmetar', 'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')
+pkgs <- c('tidyverse', 'meta', 'metafor', 
+          'readxl', 'compareGroups',
+          'knitr', 'gridGraphics', 'gridExtra',
+          'ggpubr','kableExtra','magick')
 
@@
 
-# Knitr options
-knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
-
-```
+```
+
+## Search criteria
+
+The first step in reviews is to gather a sample of records.
+This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must contain all of it.
+At the same time, the sample should be concise enough to optimise the work flow.
+Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew.
+This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation.
+The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics".
+Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.
+
+We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
+\href{https://www.scopus.com/}{Scopus} (n = 736).
+The R script we wrote extracted, to a .csv file, the title, abstract, authors, year, journal of publication, and database from which the record originated.
+We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc.
+We set no restriction to unpublished articles.
+
+Below, you will find the webscrape script:
+
+``` {r, eval = FALSE}
+
+#### PACKAGES ####
+
+# Needed packages
+pkgs <- c('tidyverse', 'rvest', 'RSelenium')
+
+# Install if not already installed
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
+} 
+lapply(pkgs, installIfNot)
+
+# Load packs
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
+
+#### SETTING UP SELENIUM ####
+
+# Alternative 1: Setting up Selenium (head)
+rsD <- rsDriver(port = 1114L, browser = c("firefox")) 
+remDr <- rsD$client
+remDr$open()
+
+#### Google scholar ####
+
+# site: https://scholar.google.com
+
+remDr$navigate("https://scholar.google.com/
+               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")
+
+articles_weingast <- tibble(
+  value = NA,
+  term = NA,
+  page = NA
+)
+
+k <- 0
+
+for (j in 1:213) { # we had to manually choose the number of pages here; Y.M.M.V.
+
+  Sys.sleep(rpois(1, 5))
+
+  # Getting articles basic information
+  k <- k + 1
+
+  webElem <- remDr$findElement("css", "body")
+
+  title <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(
+      xpath = '//*[contains(concat( " ", @class, " " ),
+      concat( " ", "gs_rt", " " ))]'
+      ) %>%
+    html_text() %>%
+    enframe(name = NULL) %>%
+    rename("title" = "value") %>%
+    mutate(page = k)
+
+  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
+    html_text() %>%
+    enframe(name = NULL) %>%
+    bind_rows(
+      tibble(
+        value = "delete",
+        term = NA,
+        page = NA
+      ),
+      .
+    ) %>%
+    bind_cols(., title)
+
+  # Binding articles
+  articles_weingast <- bind_rows(articles_weingast, articles_partial)
+
+  # Changing Pages
+  next_button <- remDr$findElement(using = "xpath", "/html/body/div/div[11]/div[2]/div[2]/div[3]/
+                                   div[2]/center/table/tbody/tr/td[12]/a/b")
+  next_button$clickElement()
+
+  # Deleting cookies
+  remDr$deleteAllCookies()
+}
+
+write_csv(articles_weingast, "scholar_weingast_raw.csv")
+
+articles_weingast <- articles_weingast %>%
+  select(-term, -page) %>%
+  filter(value != "delete") %>%
+  slice(2:nrow(.)) %>%
+  filter(!grepl("books.google.com", value)) %>%
+  filter(!grepl("BOOK", title)) %>%
+  separate(., value, into = c("author", "value"),
+           sep = " -", remove = T, extra = "merge", fill = "right") %>%
+  separate(., value, into = c("journal", "year"),
+           sep = ",", remove = T, extra = "merge", fill = "right") %>%
+  mutate(
+    year_2 = ifelse(is.na(year), journal, year),
+    journal = ifelse(is.na(year), NA, journal),
+    year = year_2
+  ) %>%
+  select(-year_2) %>%
+  separate(., year, into = c("year", "site"),
+           sep = "-", remove = T, extra = "merge", fill = "right") %>%
+  mutate(
+    year = gsub("[^0-9 ]", "", value),
+    year = gsub("^[0-9]{5,}", "", year),
+    year = gsub("^ {1,}", "", year)
+  ) %>%
+  separate(., year, into = c("year", "junk"),
+           sep = " ", remove = T, extra = "merge", fill = "right") %>%
+  separate(., value, into = c("journal", "value"),
+           sep = "-", remove = T, extra = "merge", fill = "right") %>%
+  mutate(
+    journal_untidy = year,
+    year = gsub("[^0-9 ]", "", year)
+  )
+
+articles <- articles %>%
+  na.omit() %>%
+  distinct(., value, .keep_all = T)
+
+write_csv(articles, "google_scholar_clean.csv")
+
+#### SCOPUS ####
+
+# url: https://www.scopus.com/home.uri
+
+# Scraping Scopus requires a bit more manual labor.
+# You can login on scopus through your university/institution and download the metadata
+#o fthe article(s) you want directly from there.
+# All we need to do after that is scrape the information of
+# every link from the .csv file downloaded previously
+
+scopus <- read_csv("scopus.csv")
+
+scopus <- scopus %>%
+  mutate(article = map_chr(Link, ~ {
+    remDr$navigate(.x)
+    read_html(remDr$getPageSource()[[1]]) %>%
+      html_nodes(xpath = '//*[(@id = "abstractSection")]//p') %>%
+      html_text() %>%
+      paste(., collapse = "\r\n")
+  })) %>%
+  mutate(
+    article = gsub(
+      '\r\n\nUse this section.*Topics\n\n\n"',
+      "",
+      article
+    ),
+    article = gsub(
+      "Topics are unique.*onwards.",
+      "",
+      article
+    ),
+    article = gsub(
+      "Use this section.*documents.",
+      "",
+      article
+    ),
+    article = gsub(
+      "Learn more about these Topics",
+      "",
+      article
+    ),
+    article = gsub(
+      ". 20.*, Springer Science\\+Business Media, LLC, part of Springer Nature.",
+      "",
+      article
+    ),
+    article = gsub("\r", "", article),
+    article = gsub("\n", "", article),
+    article = gsub(" {2,}", " ", article),
+    article = gsub(" {3,}", "", article)
+  )
+
+write_csv(scopus, "scopus_clean.csv")
+
+#### Microsoft Academic ####
+
+# url: https://academic.microsoft.com/home
+
+articles <- list()
+k <- 0
+remDr$navigate("https://academic.microsoft.com/paper/
+               2076316673/citedby/search?q=The%20Political%
+               20Economy%20of%20Benefits%20and%20Costs%3A%20A%
+               20Neoclassical%20Approach%20to
+               %20Distributive%20Politics&qe=RId%253D2076316673&f=&orderBy=0")
+
+# 1) Getting hyperlinks from articles
+for (j in 1:100) {
+  k <- k + 1
+  print(k)
+
+  # Navigating Website
+
+  Sys.sleep(rpois(2, 5))
+
+  # Getting articles' links
+  articles[[k]] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(xpath = "//a") %>%
+    html_attr("href") %>%
+    enframe(name = NULL) %>%
+    filter(
+      grepl("paper/", value),
+      !grepl("citedby", value)
+    ) %>%
+    mutate(value = paste0("https://academic.microsoft.com/", value))
+
+  # Changing Page
+  next_page_others <- remDr$findElement(using = "xpath", "/html/body/div/div/div/router-view/router-view/                                        ma-edp-serp/div/div[2]/div/
+  compose/div/div[2]/ma-pager/div/i[2]")
+  next_page_others$clickElement()
+}
+
+articles <- articles %>%
+  reduce(bind_rows) %>%
+  distinct(value, .keep_all = T)
+
+# 2) Navigating through articles and scraping them
+
+articles_links <- articles %>%
+  mutate(
+    abstract = NA,
+    title = NA,
+    year = NA,
+    journal = NA,
+    authors = NA,
+    tags = NA
+  )
+
+for (i in 1:nrow(articles_links)) {
+  remDr$navigate(articles_links$value[i])
+  Sys.sleep(rpois(1, 4))
+
+  articles_links$abstract[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(., xpath = "//html/body/div/div/div/router-view/compose[1]/
+               div/div/ma-entity-detail-info/compose/div/div/div[1]/p") %>%
+    html_text() %>%
+    paste(., collapse = " ")
+
+  articles_links$title[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(.,
+               xpath = '//*[contains(concat( " ", @class, " " ),
+               concat( " ", "name", " " ))]') %>%
+    html_text() %>%
+    paste(., collapse = " ")
+
+  articles_links$year[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(., 
+               xpath = '//*[contains(concat( " ", @class, " " ),
+               concat( " ", "name-section", " " ))]
+               //*[contains(concat( " ", @class, " " ), concat( " ", "year", " " ))]') %>%
+    html_text() %>%
+    paste(., collapse = " ")
+
+  articles_links$journal[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " )
+               , concat( " ", "pub-name", " " ))]') %>%
+    html_text() %>%
+    paste(., collapse = " ")
+
+  articles_links$authors[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/div/div/
+               ma-entity-detail-info/compose/div/div/div[1]/
+               ma-author-string-collection") %>%
+    html_text() %>%
+    paste(., collapse = " ")
+
+  articles_links$tags[i] <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/
+               div/div/ma-entity-detail-info/compose/
+               div/div/div[1]/ma-tag-cloud/div") %>%
+    html_text() %>%
+    paste(., collapse = " ")
+}
+
+write_csv(articles_links, "microsoft_academic_clean.csv")
+
+```
+
+## Article Selection
+
+The selection process was conducted by two authors in three phases.
+In the first round, we excluded all titles that were obviously unrelated to our topic of investigation.
+For instance, we curiously found articles about automobile motors amidst our sample.
+We consider this a preliminary step, since we were not able to eliminate a large number of entries.
+Thus, we read all abstracts.
+We chose to maintain those that indicated either government expenditure or legislative structures were central matters.
+For instance, if the paper sought to identify variables that increased government size, it was maintained.
+Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included.
+This allowed us to significantly reduce our sample to 376 records.
+
+In the second phase, we assessed full-texts.
+To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
+If the record was marked as positive for all three, it was maintained.
+Disagreements in this phase were discussed among the authors, and a third was consulted when needed.
+
+The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility.
+Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used.
+By observing what is most commonly used, we could decide which variables we would employ in our analysis.
+In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
+Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.
+
+#### Exclusion analysis
+
+We selected the final pool of articles based on two criteria regarding their reported coefficients:
+
+1. Matched treatment variable:
+  + N: Number Legislators Lower House
+  + logN: Log Number Legislators Lower House
+  + K: Number Legislators Upper House
+
+2. Matched outcome variable:
+  + ExpPC: Expenditure Per Capita
+  + logExpPC: Log Expenditure Per Capita
+  + PCTGDP: Percent GDP Public Expenditure
+
+### Flow Chart
+
+We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}.
+The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.
+
+\bigskip
+
+```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
+\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
+
+  \footnotesize
+  \linespread{1.0}
+
+  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};
+
+  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};
+
+  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
+
+  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
+
+  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};
+
+  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};
+
+  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};
+
+  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};
+
+  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};
+
+  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};
+
+  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};
+
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};
+
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
+  \draw [arrow] (id) -- (1st);
+  \draw [arrow] (id) -- (screen);
+  \draw [arrow] (screen) -- (2nd);
+  \draw [arrow] (screen) -- (elig);
+  \draw [arrow] (elig) -- (3rd);
+  \draw [arrow] (elig) -- (inc_1);
+  \draw [arrow] (inc_1) -- (4th);
+  \draw [arrow] (inc_1) -- (inc_2);
+
+ \end{tikzpicture}
+
+```
+
+## Meta-analysis dataset
+
+The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).
 
@@
 
-\newpage
 ### Published?
@@
   theme_bw()
-
-```
-
-\newpage
+```
+
 ### Dependent variables
@@
   theme_bw()
-
-```
-
-\newpage
+```
+
 ### Independent variables
@@
 
-\newpage
 ### Histogram Coefficients
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
+```{r, echo=FALSE}
 dat %>%
@@
   theme_bw()
-
-```
-
-\newpage
+```
+
 ### Histogram Standard Errors
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
+```{r, echo=FALSE}
 dat %>%
@@
   theme_bw()
-
-```
-
-\newpage
+```
+
 ### Sign Coefficients
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
 dat %>%
@@
 
+### Descriptive Statistics of Moderators
+
+We used XXXX
+
+```{r, echo=F,warning=F,message=F}
+fulldat$usemeta2 <- factor(fulldat$usemeta)
+levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
+aux <- select(fulldat, usemeta2, indepvar2, year, published, 
+              elecsys2, method, agglevel, location2) %>%
+  rename(`Independent Variables` = indepvar2,
+         `Year` = year, 
+         `Published work` = published, 
+         `Electoral system` = elecsys2, 
+         `Estimation method` = method, 
+         `Sampling Aggregation Level` = agglevel, 
+         `Sample Location` = location2)
+
+export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
+                        show.p.overall = F, show.all = T),
+          caption = "Descriptive Statistics of Moderators")
+```
+
+### Binomial Tests for Coefficient Sigs
+
 A general test of the theory would be to study whether the coefficients are positive or negative.
-Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure.
+Note that the law of 1/n poses that we should have a positive influence of legislature size on expenditure.
 To test this theory, we run a Binomial One-Proportion Z-test.
+The test consists in contrasting the number of occurences of positive and negative signs (Binomial trials) against the hypothesis that they were produced with 0.5 percent chance.
+Note that if this is the case, any detected difference would be a mere XXXX of chance.
+
 For the number of legislators in the lower house (N), the results follow below.
@@
 ```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'N')
-binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
+aux <- filter(dat, indepvar2=='N')
+binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
 ```
@@
 Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample.
-For the number of legislators in the upper house (K), the results follow below.
+For the log of the number of legislators in the lower house (log(N)), the results follow below.
 
 ```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'K')
-binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
+aux <- filter(dat, indepvar2=='logN')
+binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
+```
+
+For log(N), although most coefficients were negative, there are very few studies, making the Finally, for the number of legislators in the upper house (K), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2=='K')
+binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
 ```
@@
 
-\newpage
 ### Electoral system x Sign Coefficient
@@
 
-\newpage 
-### Descriptive Stats of Moderators
-
-```{r, echo=F,warning=F,message=F,error=F}
-
-# Table 2
-
-dat2 <- dat %>%
-  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
-  rename(Depvar = depvar2,
-         Indepvar = indepvar2,
-         Published = published,
-         "Electoral System" = elecsys2,
-         Method = method,
-         "Aggregate Level" = agglevel,
-         Location = location2)
-
-names <- dat2 %>% 
-  map(table) %>%
-  unlist() %>%
-  names()
-
-aux <- dat2 %>%
-  map_df(~{
-    table(.x) %>%
-      as.data.frame() %>%
-      rename(Moderator = ".x") %>%
-      mutate(Moderator = as.character(Moderator),
-             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
-  }) %>%
-  mutate(Moderator = names,
-         Moderator = gsub("\\.", ": ", Moderator),
-         Freq = as.character(Freq)) %>%
-  bind_rows(.,
-            tibble(
-              Moderator = "Year",
-              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
-              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
-            ))
-
-kable(aux,
-      booktabs = T,
-      align = "c",
-      linesep ='') %>% 
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-rm(dat2,names)
-```
-
-\newpage
 ## Meta-analysis
 
-We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
+We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
 
@@
 
-\newpage
 ### ExpPC x K
@@
 
-```{r, echo=FALSE, fig.width=20, fig.height=5}
+```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F,message=F}
 
@@
 
+magick::image_write(p_full,"figure 1.png")
 ```
@@
 
-```
-
-\newpage
+magick::image_write(p_full,"figure 2.png")
+```
+
 ## Meta-regressions
-
-### Meta-regressions for Expenditure measured as
 
@@
 mod <- permutest(mod, progbar = F)
-mod
 
@@
 ```{r, echo=F, warning=F,error=F,message=F}
-coefs = bind_rows(
-  mod1,
-  mod2,
-  mod3,
-  mod4,
-  mod5) %>%
-  select(` `) %>%
-  distinct()
-
-aux = list(mod3, mod5, mod1) %>%
+coefs <- tibble(
+  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
+    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
+)
+
+aux <- list(mod3, mod4, mod5, mod6, mod1, mod2) %>%
   map(~{
@@
   }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+  reduce(bind_rows) %>%
+    mutate(
+         order = ifelse(` ` == "Intercept", 1, NA),
          order = ifelse(` ` == "Indepvar: N", 2, order),
@@
          order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
   arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4, mod6, mod2) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-
-```
-
-\blandscape
+  mutate_at(vars(contains("Value")), list(
+    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. < 0.10, ".", " ")))))
+      )) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
+  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
+  select(-`T`,-CI,-`P-Value`,-order) %>%
+  pivot_longer(cols = c("Estimate", "SE")) %>%
+  pivot_wider(names_from = model, values_from = c(value)) %>%
+  select(-name)
+
+```
 
 ## Summary of Results
+
 ```{r, echo=F, warning=F,error=F,message=F,asis=T}
@@
         " ",
-        " ",
-        "Estimate",
-        "SE",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "P-Value"
+        "Base",
+        "Full",
+        "Base",
+        "Full",
+        "Base",
+        "Full"
       )) %>% 
-  collapse_rows(
-    1:2,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
+  collapse_rows(1:2,row_group_label_position ='identity',
+                latex_hline = "none") %>%
+  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
   kable_styling(
@@
       "scale_down",
-      "repeat_header"
+      "repeat_header",
+      "full_width"
       ),
     position = "center",
-    latex_options = c("repeat_header"))
-
-```
-\elandscape
+    latex_options = c("repeat_header")) %>%
+  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
+
+```
+
+## Summary of Results (Permutation)
 
 ```{r, echo=F, warning=F,error=F,message=F}
-coefs = bind_rows(
-  mod1_permu,
-  mod2_permu,
-  mod3_permu,
-  mod4_permu,
-  mod5_permu) %>%
-  select(` `) %>%
-  distinct()
-
-aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
+coefs <- tibble(
+  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
+    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
+)
+
+aux <- list(mod3_permu, mod4_permu, mod5_permu, mod6_permu, mod1_permu, mod2_permu) %>%
   map(~{
@@
          order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
   arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "AggLevel: States", 9, order)
-         ) %>%
-  arrange(order) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-
-```
-
-\blandscape
-
-## Summary of Results (Permutation)
+  mutate_at(vars(contains("Value")), list(
+    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. < 0.10, ".", " ")))))
+      )) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
+  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
+  select(-`T`,-CI,-`P-Value`,-order) %>%
+  pivot_longer(cols = c("Estimate", "SE")) %>%
+  pivot_wider(names_from = model, values_from = c(value)) %>%
+  select(-name)
+
+```
+
 ```{r, echo=F, warning=F,error=F,message=F,asis=T}
 kable(aux, 
-      "latex",
       booktabs = T,
@@
       "scale_down",
-      "repeat_header"
+      "repeat_header",
+      "full_width"
       ),
     position = "center",
-    latex_options = c("repeat_header"))
-
-```
-\elandscape
+    latex_options = c("repeat_header")) %>%
+  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
+
+```
 
@@
 
-```{r, echo=F, warning=F}
+```{r}
 permutest(mod, progbar = F)
-
-```
+```

### 2020-05-21 dataset/datasetBuilding.R
commit 1 05/20

@@ -1,0 +1,3640 @@
+##################################################################
+## Script: Building the Dataset for Distributive Politics Paper ##
+## Authors: Alptekin, Freire, Mignozzetti and Roman             ##
+## Last Modified: May 20, 2020                                  ##
+##################################################################
+
+## Starting
+set.seed(732578) # From random.org
+
+# Needed packages
+pkgs <- c('tidyverse')
+
+# Install if not already installed
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
+} 
+lapply(pkgs, installIfNot)
+
+# Load packs
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
+
+# Paper 367
+dat <- data.frame(
+  id = 367,
+  published = 'Yes',
+  usemeta = 1,
+  method = 'OLS',
+  elecsys = 'Maj',
+  elecsys2 = 'Maj',
+  agglevel = 'States',
+  location = 'US',
+  title = 'Spatially Targeted Government Spending and
+Heterogeneous Constituent Cost Shares',
+  author = 'Bradbury and Stephenson',
+  year = 2009,
+  authoryear = 'Bradbury and Stephenson (2009)',
+  journal = 'The Journal of Private Enterprise',
+  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
+  table = 2,
+  column = 2,
+  indepvar = 'MEMSENATE',
+  indepvar2 = 'K',
+  depvar = 'Total Spending per capita',
+  depvar2 = 'ExpPC',
+  coef = 0.624,
+  scoef = 'P',
+  scoefsig = 'P',
+  SE = 0.624/3.10
+)
+
+# Paper 585 K
+dat <- rbind(dat,
+             data.frame(
+               id = 585,
+               published = 'Yes',
+               usemeta = 1, 
+               method = 'PANEL',
+               elecsys = 'Mixed',
+               elecsys2 = 'Non-Maj',
+               agglevel = 'Countries',
+               location = 'World',
+               title = 'Legislative organization and government spending: cross-country evidence',
+               author = 'Bradbury and Crain',
+               year = 2001,
+               authoryear = 'Bradbury and Crain (2001)',
+               journal = 'Journal of Public Economics',
+               web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
+               table = 2,
[…]

### 2020-05-21 appendix/appendixV5.Rmd
commit 2 05/20

@@
 
-```
-
-```{r, echo=FALSE, include=FALSE}
-
-# Paper 367
-dat <- data.frame(
-  id = 367,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Spatially Targeted Government Spending and
-Heterogeneous Constituent Cost Shares',
-  author = 'Bradbury and Stephenson',
-  year = 2009,
-  authoryear = 'Bradbury and Stephenson (2009)',
-  journal = 'The Journal of Private Enterprise',
-  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
-  table = 2,
-  column = 2,
-  indepvar = 'MEMSENATE',
-  indepvar2 = 'K',
-  depvar = 'Total Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.624,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.624/3.10
-)
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 5,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.01262,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.01262/2.12
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 2,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.004964,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.004964/2.9
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 3,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.01134,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01134/4.52
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 4,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.00559,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.00559/2.39
-))
-
-# Paper 585 N
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 5,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.003627,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003627/2.51
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 2,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.000517,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.000517/0.47
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 3,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.016946,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.016946/8.65
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 4,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.012337,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.012337/6.65
-))
-
-# Paper 505
-dat <- rbind(dat,
-  data.frame(
-  id = 505,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'IV',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
-  author = 'Matsusaka',
-  year = 2005,
-  authoryear = 'Matsusaka (2005)',
-  journal = 'State Politics & Policy Quarterly',
-  web = 'https://www.jstor.org/stable/40421558',
-  table = 1,
-  column = 3,
-  indepvar = 'Seats',
-  indepvar2 = 'N',
-  depvar = 'State Government Expenditure per Capita',
-  depvar2 = 'ExpPC',
-  coef = -0.96,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.18
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 1,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.213,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.018
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 2,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.229,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.037
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 3,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.455,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.038
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 4,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.411,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.049
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 1,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.226,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.053
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 2,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.213,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.317
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 3,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.185,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.305
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 4,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.235,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.336
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 5,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.374,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.064
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 6,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.811,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.181
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 7,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.795,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.176
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 8,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.849,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.238
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 974,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'Latin America',
-  title = 'Institutional arrangements and fiscal performance: the latin american experience',
-  author = 'Stein, Talvi, and Grisanti',
-  year = 1998,
-  authoryear = 'Stein et al. (1998)',
-  journal = 'NBER Working papers',
-  web = 'https://www.nber.org/papers/w6358.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'District magnitude',
-  indepvar2 = 'logN',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.0109,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.0143
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 974,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'Latin America',
-  title = 'Institutional arrangements and fiscal performance: the latin american experience',
-  author = 'Stein, Talvi, and Grisanti',
-  year = 1998,
-  authoryear = 'Stein et al. (1998)',
-  journal = 'NBER Working papers',
-  web = 'https://www.nber.org/papers/w6358.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'District magnitude',
-  indepvar2 = 'logN',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.0135,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.0121
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 4,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.003,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.009,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.002
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 2,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.011,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.04,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 2,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.03,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 3,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.01,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.002
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 4,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.02,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.004
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 886,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Brazil',
-  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
-  author = 'Lledo',
-  year = 2003,
-  authoryear = 'Lledo (2003)',
-  journal = NA,
-  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
-  table = 6,
-  column = 1,
-  indepvar = 'Log (State Legislature Seats)',
-  indepvar2 = 'logN',
-  depvar = 'Primary Spending as a share of GSP',
-  depvar2 = 'PCTGDP',
-  coef = -4.69,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = -4.69/(-1.75)
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 862,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
-  author = 'Schaltegger and Feld',
-  year = 2009,
-  authoryear = 'Schaltegger and Feld (2009)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
-  table = 6,
-  column = 4,
-  indepvar = 'Seats in Parliament',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.001,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 862,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
-  author = 'Schaltegger and Feld',
-  year = 2009,
-  authoryear = 'Schaltegger and Feld (2009)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
-  table = 6,
-  column = 3,
-  indepvar = 'Seats in Parliament',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.001,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.302,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.302/7.885
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.276,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.276/7.185
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.295,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.302/7.545
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.066,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.066/7.014
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.012,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.012/6.701
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 5,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.468,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.468/8.251
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.014,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = -0.011,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 5,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.007,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.007
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 7,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 10,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.012,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.007
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 1,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.016,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.021,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.011
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.014,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.003,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.006
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.03,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.026
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 7,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.030,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.026
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 8,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.039,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.021
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 9,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.0127,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.014
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 10,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.016,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 4,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.1127,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0373
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.276,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0384
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 2,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.3021,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0383
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 3,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.3203,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0384
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 4,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.82,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.19
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 1,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -1.7,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.31
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 2,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -2.37,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.37
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 3,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -2.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.37
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 4,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.97,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.74
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 1,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 5.9,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.64
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 2,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 5.75,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.73
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 3,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 6.96,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.22
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Lower chamber size',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = -2.04,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 1.33
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Lower chamber size',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = -1.40,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.64
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 26.09,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 7.45
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.3,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.35
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.14,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.53
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.78,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.9
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 2,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 20.38,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 6.47
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 3,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.87,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.83
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 4,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 26.75,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.21
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 439,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Legislative term limits and state spending',
-  author = 'Erler',
-  year = 2007,
-  authoryear = 'Erler (2007)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/27698198',
-  table = 2,
-  column = 1,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 3.93,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 1.18
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 3,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.136,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.136/2.92
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 1,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.2319,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.2319/4.56
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 2,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.1443,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.1443/2.91
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 4,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.1594,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.1443/3.05
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 5,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.2259,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.2259/4.04
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 5,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.159,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 6,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.147,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 7,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.09,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.038
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 8,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.081,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.039
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 9,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.088,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.038
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 1,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.21,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.023
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 2,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = .157,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.037
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 3,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.199,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.04
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 4,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.169,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 231,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'IV',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Germany',
-  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
-  author = 'Baskaran',
-  year = 2013,
-  authoryear = 'Baskaran (2013)',
-  journal = 'European Journal of Political Economy',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
-  table = 3,
-  column = 4,
-  indepvar = 'Parliament seats',
-  indepvar2 = 'N',
-  depvar = 'Real Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.974,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.974/1.743
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 230,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislatures, Leaders and Leviathans',
-  author = 'Maldonado',
-  year = 2013,
-  authoryear = 'Maldonado (2013)',
-  journal = 'Social Science Quarterly',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
-  table = 2,
-  column = 2,
-  indepvar = 'Size lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Government Share of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.0609,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.0117
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 230,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislatures, Leaders and Leviathans',
-  author = 'Maldonado',
-  year = 2012,
-  authoryear = 'Maldonado (2012)',
-  journal = 'Social Science Quarterly',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
-  table = 2,
-  column = 2,
-  indepvar = 'Size upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Government Share of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.04,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.0132
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.003,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.006,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending (%) GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.004,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending (%) GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.008,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 4,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.174,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.085
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 1,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.223,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.052
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 2,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.215,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.061
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 3,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.158,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.054
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 1,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.21,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 4.051
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 2,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.423,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 18.17
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 3,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 9.594,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.804
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 1,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = -0.351,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.745
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 2,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.975,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.646
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 3,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 7.658,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.922
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 8,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Indonesia',
-  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
-  author = 'Lewis',
-  year = 2019,
-  authoryear = 'Lewis (2019)',
-  journal = 'Studies in Comparative International Development',
-  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
-  table = 4,
-  column = NA,
-  indepvar = 'Legislature size',
-  indepvar2 = 'N',
-  depvar = 'Log per capita total expenditure',
-  depvar2 = 'logExpPC',
-  coef = -0.174,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = (-0.174+0.245)/1.96
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 1,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.851,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 1.395
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 2,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -1.689,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.697
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 3,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 7.632,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 2.309
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 1,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 19.74,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 8.406
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 2,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 10.06,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.965
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 3,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 9.062,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 20.38
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 1,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 2,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 3,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.04,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 102,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Australia',
-  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
-  author = 'Drew and Dollery',
-  year = 2017,
-  authoryear = 'Drew and Dollery (2017)',
-  journal = 'Urban Affairs Review',
-  web = '10.1007/s11127-016-0369-9',
-  table = 2,
-  column = 1,
-  indepvar = 'No. of representatives',
-  indepvar2 = 'N',
-  depvar = 'Ln Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.077,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.028
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 102,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Australia',
-  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
-  author = 'Drew and Dollery',
-  year = 2017,
-  authoryear = 'Drew and Dollery (2017)',
-  journal = 'Urban Affairs Review',
-  web = '10.1007/s11127-016-0369-9',
-  table = 2,
-  column = 2,
-  indepvar = 'No. of representatives',
-  indepvar2 = 'N',
-  depvar = 'Ln Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.031,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.022
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 1,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.0164,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 1.313
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 1,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 38.44,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 19.23
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 2,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 37.85,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 17.77
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 3,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 25.61,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.48
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 4,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.996,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.06
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 5,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 25.56,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.49
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 6,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.693,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 12.35
-))
-
-dat <- dat[order(dat$id),]
-dat <- dat[!is.na(dat$coef),]
-row.names(dat) <- NULL
-levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
-dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
-dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
-levels(dat$scoef) <- c('Negative', 'Positive')
-levels(dat$scoefsig) <- c('Negative', 'Positive')
-dat$method <- factor(as.character(dat$method), 
-                     levels = c("OLS", "PANEL", "IV", "RDD"))
-dat$location2 <- as.character(dat$location)
-dat$location2[dat$location2!='World'] = 'Country'
-dat$location2 <- factor(as.character(dat$location2), 
-                     levels = c("Country", "World"))
-dat$agglevel <- factor(as.character(dat$agglevel), 
-                     levels = c("Local", "States", "Countries"))
-fulldat <- dat
-dat <- dat %>%
-  filter(usemeta == 1)
-```
-\newpage
-## Descriptive statistics
-
-### Study Year
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
-dat %>%
-  ggplot(aes(x = as.factor(year))) + 
-    geom_bar(color = "black") + 
-  labs(x = "",
-       y = "") + 
-  theme_bw()
-```
-
-\newpage
-### Published?
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
-dat %>%
-  ggplot(aes(x = as.factor(published))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Published study?",
-       y = "") + 
-  theme_bw()
-
-```
-
-\newpage
-### Dependent variables
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
-dat %>%
-  mutate(depvar2 = factor(depvar2, 
-                          labels = c("Per Capita Expenditure",
-                                     "Percentage GDP Government Expenditure",
-                                     "Log Per Capita Expenditure"))) %>%
-  ggplot(aes(x = depvar2)) +
-    geom_bar(color = "black") + 
-  labs(x = "Dependent Variables",
-       y = "") + 
-  coord_flip() + 
-  theme_bw()
-
-```
-
-\newpage
-### Independent variables
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
-dat %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
-                                                  'N (lower house legislators)',
-                                                  'Log N'))) %>%
-  ggplot(aes(x = indepvar2)) + 
-    geom_bar(color = "black") + 
-  labs(x = "Independent Variables",
-       y = "") +
-  coord_flip() +
-  theme_bw() 
-```
-
-\newpage
-### Histogram Coefficients
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
-dat %>%
-  ggplot(aes(x = coef)) +
-  geom_histogram(bins = 15, color = "black") + 
-  labs(x = "Coefficients") + 
-  theme_bw()
-
-```
-
-\newpage
-### Histogram Standard Errors
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
-dat %>%
-  ggplot(aes(x = SE)) +
-  geom_histogram(bins = 10, color = "black") + 
-  labs(x = "Standard Errors") + 
-  theme_bw()
-
-```
-
-\newpage
-### Sign Coefficients
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
-dat %>%
-  ggplot(aes(x=as.factor(scoef))) + 
-  geom_bar(color = "black") + 
-  labs(x = "Coefficient Sign",
-       y = "") +
-  theme_bw()
-```
-
-A general test of the theory would be to study whether the coefficients are positive or negative.
-Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure.
-To test this theory, we run a Binomial One-Proportion Z-test.
-For the number of legislators in the lower house (N), the results follow below.
-
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'N')
-binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
-```
-
-Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample.
-For the number of legislators in the upper house (K), the results follow below.
-
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2 == 'K')
-binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
-```
-
-Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.
-
-\newpage
-### Electoral system
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
-dat %>%
-  ggplot(aes(x=as.factor(elecsys2))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Electoral system",
-       y = "") + 
-  theme_bw()
-```
-
-\newpage
-### Electoral system x Sign Coefficient
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$elecsys2)
-chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
-```
-
-\newpage
-### Independent Variable x Sign Coefficient
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$indepvar2)
-chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
-```
-
-\newpage
-### Dependent variables x Independent variables
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$depvar2)
-chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
-```
-
-\newpage 
-### Descriptive Stats of Moderators
-
-```{r, echo=F,warning=F,message=F,error=F}
-
-# Table 2
-
-dat2 <- dat %>%
-  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
-  rename(Depvar = depvar2,
-         Indepvar = indepvar2,
-         Published = published,
-         "Electoral System" = elecsys2,
-         Method = method,
-         "Aggregate Level" = agglevel,
-         Location = location2)
-
-names <- dat2 %>% 
-  map(table) %>%
-  unlist() %>%
-  names()
-
-aux <- dat2 %>%
-  map_df(~{
-    table(.x) %>%
-      as.data.frame() %>%
-      rename(Moderator = ".x") %>%
-      mutate(Moderator = as.character(Moderator),
-             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
-  }) %>%
-  mutate(Moderator = names,
-         Moderator = gsub("\\.", ": ", Moderator),
-         Freq = as.character(Freq)) %>%
-  bind_rows(.,
-            tibble(
-              Moderator = "Year",
-              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
-              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
-            ))
-
-kable(aux,
-      booktabs = T,
-      align = "c",
-      linesep ='') %>% 
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-rm(dat2,names)
-```
-
-\newpage
-## Meta-analysis
-
-We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
-
-### ExpPC x N
-
-```{r, echo=FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+# Build plot function for forest plots
+build_forest <- function(mod, capt, lsize = 22) {
+  # Build dataset for plot
   mod2 <- tibble(
@@
 
-f1 <- mod2 %>%
+  # Build plot
+  p <- mod2 %>%
     ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
     geom_point(aes(color = group)) +
-  # Error Bars
     geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
     scale_color_manual(values = c("#000000", "#8b0000")) +
-  # X-axis limit
     scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
     scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
     geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
     labs(x = "",
          y = "") + 
-  # Facet - Separating Studies from Overall Effect
     facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
+    labs(caption = capt) +
     theme_minimal() %+replace%
@@
           legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f1
+          axis.text.y = element_text(size = .8*lsize, hjust = 1),
+          axis.text.x = element_text(size = .7*lsize, hjust = 1.1),
+          plot.caption = element_text(size=lsize))
+  return(p)
+}
+```
+
+```{r, echo=FALSE, include=FALSE}
+load('../dataset/dataCoefs.RData')
+```
+\newpage
+## Descriptive statistics
+
+### Study Year
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
+dat %>%
+  ggplot(aes(x = as.factor(year))) + 
+    geom_bar(color = "black") + 
+  labs(x = "",
+       y = "") + 
+  theme_bw()
+```
+
+\newpage
+### Published?
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
+dat %>%
+  ggplot(aes(x = as.factor(published))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Published study?",
+       y = "") + 
+  theme_bw()
+
+```
+
+\newpage
+### Dependent variables
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
+dat %>%
+  mutate(depvar2 = factor(depvar2, 
+                          labels = c("Per Capita Expenditure",
+                                     "Percentage GDP Government Expenditure",
+                                     "Log Per Capita Expenditure"))) %>%
+  ggplot(aes(x = depvar2)) +
+    geom_bar(color = "black") + 
+  labs(x = "Dependent Variables",
+       y = "") + 
+  coord_flip() + 
+  theme_bw()
+
+```
+
+\newpage
+### Independent variables
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
+dat %>%
+  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
+                                                  'N (lower house legislators)',
+                                                  'Log N'))) %>%
+  ggplot(aes(x = indepvar2)) + 
+    geom_bar(color = "black") + 
+  labs(x = "Independent Variables",
+       y = "") +
+  coord_flip() +
+  theme_bw() 
+```
+
+\newpage
+### Histogram Coefficients
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
+dat %>%
+  ggplot(aes(x = coef)) +
+  geom_histogram(bins = 15, color = "black") + 
+  labs(x = "Coefficients") + 
+  theme_bw()
+
+```
+
+\newpage
+### Histogram Standard Errors
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
+dat %>%
+  ggplot(aes(x = SE)) +
+  geom_histogram(bins = 10, color = "black") + 
+  labs(x = "Standard Errors") + 
+  theme_bw()
+
+```
+
+\newpage
+### Sign Coefficients
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
+dat %>%
+  ggplot(aes(x=as.factor(scoef))) + 
+  geom_bar(color = "black") + 
+  labs(x = "Coefficient Sign",
+       y = "") +
+  theme_bw()
+```
+
+A general test of the theory would be to study whether the coefficients are positive or negative.
+Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure.
+To test this theory, we run a Binomial One-Proportion Z-test.
+For the number of legislators in the lower house (N), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2 == 'N')
+binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
+```
+
+Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample.
+For the number of legislators in the upper house (K), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2 == 'K')
+binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
+```
+
+Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.
+
+\newpage
+### Electoral system
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
+dat %>%
+  ggplot(aes(x=as.factor(elecsys2))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Electoral system",
+       y = "") + 
+  theme_bw()
+```
+
+\newpage
+### Electoral system x Sign Coefficient
+
+```{r, echo=FALSE}
+table(dat$scoef, dat$elecsys2)
+chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
+```
+
+\newpage
+### Independent Variable x Sign Coefficient
+
+```{r, echo=FALSE}
+table(dat$scoef, dat$indepvar2)
+chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
+```
+
+\newpage
+### Dependent variables x Independent variables
+
+```{r, echo=FALSE}
+table(dat$scoef, dat$depvar2)
+chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
+```
+
+\newpage 
+### Descriptive Stats of Moderators
+
+```{r, echo=F,warning=F,message=F,error=F}
+
+# Table 2
+
+dat2 <- dat %>%
+  select(depvar2, indepvar2, published, elecsys2, method,agglevel, location2) %>%
+  rename(Depvar = depvar2,
+         Indepvar = indepvar2,
+         Published = published,
+         "Electoral System" = elecsys2,
+         Method = method,
+         "Aggregate Level" = agglevel,
+         Location = location2)
+
+names <- dat2 %>% 
+  map(table) %>%
+  unlist() %>%
+  names()
+
+aux <- dat2 %>%
+  map_df(~{
+    table(.x) %>%
+      as.data.frame() %>%
+      rename(Moderator = ".x") %>%
+      mutate(Moderator = as.character(Moderator),
+             Pct = paste0(100*(round(Freq/sum(Freq, na.rm = T), digits = 4)), "%"))
+  }) %>%
+  mutate(Moderator = names,
+         Moderator = gsub("\\.", ": ", Moderator),
+         Freq = as.character(Freq)) %>%
+  bind_rows(.,
+            tibble(
+              Moderator = "Year",
+              Freq = paste0(round(mean(dat$year, na.rm = T), digits=2), " (Mean)"),
+              Pct = paste0(as.character(round(median(dat$year, na.rm = T), digits=2)), " (Median)")
+            ))
+
+kable(aux,
+      booktabs = T,
+      align = "c",
+      linesep ='') %>% 
+  kable_styling(c("striped","bordered","scale_down"), position = "center")
+
+rm(dat2,names)
+```
+
+\newpage
+## Meta-analysis
+
+We combined the three independent variables (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
+
+### ExpPC x N
+
+```{r, echo=FALSE}
+# Pooling effects analysis -- ExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f1 + 
-  labs(caption = "ExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")
-
+f1 <- build_forest(mod, NULL, lsize = 15)
 ```
@@
 ```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f2 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f2
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f2 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f2 <- build_forest(mod, NULL, 15)
 
@@
 ```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f3 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f3
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f3 + 
-  labs(caption = "logExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f3 <- build_forest(mod, NULL, 15)
 
@@
 ```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f4 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f4
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f4 + 
-  labs(caption = "logExpPC x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f4  <- build_forest(mod, NULL, 15)
 
@@
 ```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f5 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f5
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f5 + 
-  labs(caption = "PCTGDP x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f5 <- build_forest(mod, NULL, 15)
 
@@
 ```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f6 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f6
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f6 + 
-  labs(caption = "PCTGDP x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f6 <- build_forest(mod, NULL, 15)
 
@@
 ```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f7 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f7
+build_forest(mod, NULL)
 ```
@@
 ```{r,include=F,warning=F}
-f7 + 
-  labs(caption = "PCTGDP x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
+f7 <- build_forest(mod, NULL, 15)
 
@@
 p_full
+
+f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
+               labels = c("ExpPC x N", 
+                          "ExpPC x K", 
+                          "logExpPC x N", 
+                          'logExpPC x logN', 
+                          'PCTGDP x N',
+                          'PCTGDP x logN',
+                          'PCTGDP x K'),
+               ncol = 2, nrow = 4, 
+               font.label = list(size=13, face = 'bold'),
+               hjust = 0)
+ggsave("./plots/fig.pdf", plot = f, width = 21, height = 29, units = "cm")
+
+f <- ggarrange(f1, f2, f3, f4, f5, f6, f7, 
+               labels = c("ExpPC x N", 
+                          "ExpPC x K", 
+                          "logExpPC x N", 
+                          'logExpPC x logN', 
+                          'PCTGDP x N',
+                          'PCTGDP x logN',
+                          'PCTGDP x K'),
+               ncol = 3, nrow = 3, 
+               font.label = list(size=13, face = 'bold'),
+               hjust = 0)
+ggsave("./plots/fig2.pdf", plot = f, width = 29, height = 21, units = "cm")
 

### 2020-05-21 appendix/appendixV5.Rmd
commit 3 05/20

@@
           axis.text.x = element_text(size = .7*lsize, hjust = 1.1),
-          plot.caption = element_text(size=lsize))
+          plot.caption = element_text(size=lsize)) + 
+    theme(panel.grid.major = element_blank())
   return(p)
@@
                hjust = 0)
-ggsave("./plots/fig.pdf", plot = f, width = 21, height = 29, units = "cm")
+ggsave("./plots/fig3.pdf", plot = f, width = 21, height = 29, units = "cm")
 
@@
                hjust = 0)
-ggsave("./plots/fig2.pdf", plot = f, width = 29, height = 21, units = "cm")
+ggsave("./plots/fig4.pdf", plot = f, width = 29, height = 21, units = "cm")
 

### 2020-05-21 appendix_final.Rmd
add selection info

--- 2020-05-17 appendixupdates/appendix_final.Rmd
@@
 
-#### PACKAGES ####
-
-# Needed packages
-pkgs <- c('tidyverse', 'rvest', 'RSelenium')
-
-# Install if not already installed
-installIfNot <- function(x) {
-  if(x %in% rownames(installed.packages()) == FALSE) 
-    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
-} 
-lapply(pkgs, installIfNot)
-
-# Load packs
-lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
+#### INSTALLING PACKAGES ####
+
+install.packages('tidyverse')
+install.packages('rvest')
+install.packages('RSelenium')
+
+#### LOADING PACKAGES ####
+
+library(tidyverse)
+library(rvest)
+library(RSelenium)
 
@@
 
-The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients that were reported in the paper. XXXX (Copiar da parte de métodos).
+The meta-analytic data is comprised of two datasets.
+The first dataset has the main coefficients that were reported in the paper.
+It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
+If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
+This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest.
+Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.
+
+In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
+Below is the data extraction process for all relevant coefficients in the selected articles.
+In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.
 
@@
 
-We used XXXX
+We chose a set of moderators that frequently appear in the literature and may help us interpret our results.
+We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$).
+The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal.
+The table below presents descriptive statistics for these moderators in our selection of articles.
 
@@
 
-### Binomial Tests for Coefficient Sigs
+### Binomial Tests for Coefficient Signs
 
 A general test of the theory would be to study whether the coefficients are positive or negative.
-Note that the law of 1/n poses that we should have a positive influence of legislature size on expenditure.
+Note that the law of 1/n poses we should have a positive influence of legislature size on expenditure.
 To test this theory, we run a Binomial One-Proportion Z-test.
@@
 
-## Meta-analysis
+## Meta-analysis {#meta-an}
 
@@
 \newpage
-## Meta-Analysis (all coefficients)
+## Meta-Analysis (all coefficients) {#full-meta-an}
 
@@
 
-## Meta-regressions
+## Meta-regressions {#meta-reg}
 
@@
   ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
-    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
-)
-
-aux <- list(mod3, mod4, mod5, mod6, mod1, mod2) %>%
+    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))
+
+aux = list(mod3, mod5, mod1) %>%
   map(~{
@@
   }) %>%
-  reduce(bind_rows) %>%
+  reduce(bind_cols) %>%
+  mutate(
+         order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  filter(` ` != "Method: RDD") %>%
+  arrange(order) %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~(ifelse(is.na(.), " ", .)))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "Base") %>%
+  select(mod, everything())
+
+aux2 = list(mod4, mod6, mod2) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
   mutate(
@@
   mutate_at(vars(contains("Value")), list(
-    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                        ifelse(. < 0.01, "**",
                               ifelse(. < 0.05, "*", 
-                                     ifelse(. < 0.10, ".", " ")))))
-      )) %>%
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
   mutate_at(vars(contains("Estimate") | contains("SE")),
             list(~ifelse(is.na(.), " ", .))) %>%
-  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
-  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
-  select(-`T`,-CI,-`P-Value`,-order) %>%
-  pivot_longer(cols = c("Estimate", "SE")) %>%
-  pivot_wider(names_from = model, values_from = c(value)) %>%
-  select(-name)
-
-```
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"),-`T`,-T1,-T2)
+
+```
+
+\blandscape
 
@@
         " ",
-        "Base",
-        "Full",
-        "Base",
-        "Full",
-        "Base",
-        "Full"
+        " ",
+        "Estimate",
+        "SE",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif"
       )) %>% 
-  collapse_rows(1:2,row_group_label_position ='identity',
-                latex_hline = "none") %>%
-  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
+  collapse_rows(
+    1:2,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
   kable_styling(
@@
       "scale_down",
-      "repeat_header",
-      "full_width"
+      "repeat_header"
       ),
@@
 ```
-
-## Summary of Results (Permutation)
+\elandscape
 
@@
 
-aux <- list(mod3_permu, mod4_permu, mod5_permu, mod6_permu, mod1_permu, mod2_permu) %>%
+aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
   map(~{
@@
   }) %>%
-  reduce(bind_rows) %>%
+  reduce(bind_cols) %>%
   mutate(
@@
   arrange(order) %>%
+  filter(` ` != "Method: RDD") %>%
   mutate_at(vars(contains("Value")), list(
-    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                        ifelse(. < 0.01, "**",
                               ifelse(. < 0.05, "*", 
-                                     ifelse(. < 0.10, ".", " ")))))
-      )) %>%
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
   mutate_at(vars(contains("Estimate") | contains("SE")),
             list(~ifelse(is.na(.), " ", .))) %>%
-  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
-  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
-  select(-`T`,-CI,-`P-Value`,-order) %>%
-  pivot_longer(cols = c("Estimate", "SE")) %>%
-  pivot_wider(names_from = model, values_from = c(value)) %>%
-  select(-name)
-
-```
-
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "Base") %>%
+  select(mod, everything())
+
+aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  arrange(order) %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"),-`T`,-T1,-T2)
+
+```
+
+\blandscape
+## Summary of Results (Permutation)
 ```{r, echo=F, warning=F,error=F,message=F,asis=T}
@@
         " ",
-        "Base",
-        "Full",
-        "Base",
-        "Full",
-        "Base",
-        "Full"
+        " ",
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif"
       )) %>% 
-  collapse_rows(1:2,row_group_label_position ='identity',
-                latex_hline = "none") %>%
-  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
+  collapse_rows(
+    1:2,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
   kable_styling(
@@
 ```
+\elandscape
 
@@
 
-## Robustness: Full model meta-regressions combined
+## Robustness: Full model meta-regressions combined {#full-meta-reg}
 

### 2020-05-21 Untitled.R
Delete Untitled.R

@@ -1,1 +1,0 @@
-# Arquivo novo

### 2020-06-13 appendix/appendix_final.Rmd
commit graphs and finishing appendix 1

--- 2020-05-21 appendix_final.Rmd
@@
 ---
-title: "Appendix"
-author: "Umberto Mignozzetti"
-date: "12/25/2019"
-header_includes:
-- \usepackage{booktabs}
-- \usepackage{pdflscape}
-- \newcommand{\blandscape}{\begin{landscape}}
-- \newcommand{\elandscape}{\end{landscape}}
-output: pdf_document
-urlcolor: blue
+title: |
+       | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
+author: 
+- "Huzeyfe Alptekin[^alptekin]"
+- "Danilo Freire[^freire]"
+- "Umberto Mignozzetti[^mignozzetti]"
+- "Catarina Roman[^roman]"
+date: June 13, 2020
+fontfamily: libertine
+fontawesome: yes
+fontsize: 12pt
+monospace-url: yes
+spacing: double
+papersize: a4paper
+bibliography: references.bib
+biblio-style: apalike
+output:
+  pdf_document:
+    citation_package: natbib
+    fig_caption: yes
+    number_sections: yes
+    toc: true
+    keep_tex: no
+    template: template.latex
 ---
 
-```{r setup, include=FALSE}
+\appendix
+
+[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, <huzeyfealptekin@gmail.com>.
+
+[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.
+
+[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, <umberto.mig@nyu.edu>, <http://umbertomig.com>.
+
+[^roman]: Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, <catarinamroman@gmail.com>.
+
+```{r, include=FALSE}
+# Knitr options
+knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-```{r global_options, include=FALSE}
+```{r, include=FALSE}
 ## Starting
@@
 
-```
-
-## Search criteria
+# Build plot function for forest plots
+build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
+  # Build dataset for plot
+  mod2 <- tibble(
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    bind_rows(.,
+              aux = tibble(
+                TE = c(mod$TE.random, NA),
+                seTE = c(mod$seTE.random, NA),
+                studlab = c("Overall Effect", "Prediction Interval"),
+                lower = c(mod$lower.random, mod$lower.predict),
+                upper = c(mod$upper.random, mod$upper.predict),
+                group = "B")) %>%
+    group_by(studlab) %>%
+    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+    ungroup()
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab2,TE), 
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group), height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
+    scale_y_discrete(
+      labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+    geom_vline(xintercept=0, 
+               color="#000000", linetype="dashed") +
+    labs(x = "",
+         y = "") + 
+    facet_grid(group~., scales = "free", space = "free") + 
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8*lsize, 
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6*lsize, 
+                                     hjust = 1.1),
+          plot.caption = element_text(size=lsize),
+          plot.title.position = 'plot', 
+          plot.title = element_text(hjust = 0.5, 
+                                    face = 'bold',
+                                    margin=margin(0,0,10,0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
+```
+
+# Search criteria
 
@@
 
-We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
-\href{https://www.scopus.com/}{Scopus} (n = 736).
-The R script we wrote extracted, to a .csv file, the title, abstract, authors, year, journal of publication, and database from which the record originated.
+We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736).
+The R script we wrote extracted, to a CSV file, the title, abstract, authors, year, journal of publication, and database from which the record originated.
 We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc.
@@
 
-Below, you will find the webscrape script:
-
-``` {r, eval = FALSE}
-
-#### INSTALLING PACKAGES ####
-
-install.packages('tidyverse')
-install.packages('rvest')
-install.packages('RSelenium')
-
-#### LOADING PACKAGES ####
-
-library(tidyverse)
-library(rvest)
-library(RSelenium)
+# Article Selection
+
+The selection process was conducted by two authors in three phases.
+In the first round, we excluded all titles that were obviously unrelated to our topic of investigation.
+For instance, we curiously found articles about automobile motors amidst our sample.
+We consider this a preliminary step, since we were not able to eliminate a large number of entries.
+Thus, we read all abstracts.
+We chose to maintain those that indicated either government expenditure or legislative structures were central matters.
+For instance, if the paper sought to identify variables that increased government size, it was maintained.
+Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included.
+This allowed us to significantly reduce our sample to 376 records.
+
+In the second phase, we assessed full-texts.
+To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
+If the record was marked as positive for all three, it was maintained.
+Disagreements in this phase were discussed among the authors, and a third was consulted when needed.
+
+The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility.
+Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used.
+By observing what is most commonly used, we could decide which variables we would employ in our analysis.
+In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
+Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.
+
+## Exclusion analysis
+
+We selected the final pool of articles based on two criteria regarding their reported coefficients:
+
+1. Matched treatment variable:
+  + *N*: Number Legislators Lower House
+  + *logN*: Log Number Legislators Lower House
+  + *K*: Number Legislators Upper House
+
+2. Matched outcome variable:
+  + *ExpPC*: Expenditure Per Capita
+  + *logExpPC*: Log Expenditure Per Capita
+  + *PCTGDP*: Percent GDP Public Expenditure
+
+## Flow Chart
+
+We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}.
+The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.
+
+\bigskip
+
+```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
+\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
+
+  \footnotesize
+  \linespread{1.0}
+
+  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};
+
+  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};
+
+  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
+
+  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
+
+  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};
+
+  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};
+
+  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};
+
+  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};
+
+  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};
+
+  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};
+
+  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};
+
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};
+
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
+  \draw [arrow] (id) -- (1st);
+  \draw [arrow] (id) -- (screen);
+  \draw [arrow] (screen) -- (2nd);
+  \draw [arrow] (screen) -- (elig);
+  \draw [arrow] (elig) -- (3rd);
+  \draw [arrow] (elig) -- (inc_1);
+  \draw [arrow] (inc_1) -- (4th);
+  \draw [arrow] (inc_1) -- (inc_2);
+
+ \end{tikzpicture}
+```
+
+# Meta-analysis dataset
+
+The meta-analytic data is comprised of two datasets.
+The first dataset has the main coefficients that were reported in the paper.
+It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
+If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
+This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest.
+Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.
+
+In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
+Below is the data extraction process for all relevant coefficients in the selected articles.
+In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.
+
+```{r, echo=FALSE, include=FALSE}
+load('../dataset/dataCoefs.RData')
+```
+
+# Descriptive statistics
+
+In this section, we present the descriptive statistics for our meta-analytic sample.
+We focus in the following paper characteristics: study year, whether the paper has been published or not, the three dependent variables of interest, the three independent variables of interest, and a few statistics about the coefficients.
+We also add a descriptive statistics table, similar to the one in the main paper.
+
+## Study Year
+
+For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`.
+The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`.
+Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the 1/n hypothesis.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
+dat %>%
+  select(id, year) %>%
+  unique() %>%
+  ggplot(aes(x = as.factor(year))) + 
+    geom_bar(color = "black") + 
+  labs(x = "",
+       y = "") + 
+  theme_bw()
+```
+
+## Frequency of Published Papers
+
+We decided to report studies regardless of their publication status.
+From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
+dat %>%
+  select(id, published) %>%
+  unique() %>%
+  ggplot(aes(x = as.factor(published))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Published study?",
+       y = "") + 
+  theme_bw()
+```
+
+## Electoral system
+
+There are many differences in the papers relative to the research design.
+One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, in non-majoritarian democracies.
+In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated.
+The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral Systems"}
+dat %>%
+  select(id, elecsys2) %>%
+  unique() %>%
+  ggplot(aes(x=as.factor(elecsys2))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Electoral Systems",
+       y = "") + 
+  theme_bw()
+```
+
+## Aggregation Level
+
+The aggregation level is also an important characteristic of the empirical tests of the law of 1/n.
+The model was build to explain the dynamics of majoritarian countries, but the theory was tested in municipal, county, states, and country levels.
+In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` studied *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied *State* (or Provincial) levels, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` studied *Country* level data.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Sample Aggregate Level"}
+dat %>%
+  select(id, agglevel) %>%
+  unique() %>%
+  ggplot(aes(x=as.factor(agglevel))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Sample Aggregate Level",
+       y = "") + 
+  theme_bw()
+```
+
+## Geographical Location
+
+The geographical location also varies considerably in the sample.
+In our sampled papers, `r as.numeric(table(unique(select(dat, id, location2))$location2)[1])` studied a given country, while `r as.numeric(table(unique(select(dat, id, location2))$location2)[2])` used a cross-country design, with more than one country.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Geographical Location"}
+dat %>%
+  select(id, location2) %>%
+  unique() %>%
+  ggplot(aes(x=as.factor(location2))) + 
+    geom_bar(color = "black") + 
+  labs(x = "Geographical Location",
+       y = "") + 
+  theme_bw()
+```
+
+## Dependent variables
+
+The outcome variables included in the paper were:
+
+- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Per Capita Expenditure papers
+- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Natural Log of Per Capita Expenditure papers
+- `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
+dat %>%
+  select(id, depvar2) %>%
+  unique() %>%
+  mutate(depvar2 = factor(depvar2, 
+                          labels = c("Per Capita Expenditure",
+                                     "Percentage GDP Government Expenditure",
+                                     "Log Per Capita Expenditure"))) %>%
+  ggplot(aes(x = depvar2)) +
+    geom_bar(color = "black") + 
+  labs(x = "Dependent Variables",
+       y = "") + 
+  coord_flip() + 
+  theme_bw()
+```
+
+## Independent variables
+
+Most of papers in our meta-analytic sample study the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
+The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`).
+Finally, the minority of papers study the Natural Log of the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`).
+Some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
+dat %>%
+  select(id, indepvar2) %>%
+  unique() %>%
+  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
+                                                  'N (lower house legislators)',
+                                                  'Log N'))) %>%
+  ggplot(aes(x = indepvar2)) + 
+    geom_bar(color = "black") + 
+  labs(x = "Independent Variables",
+       y = "") +
+  coord_flip() +
+  theme_bw() 
+```
+
+## Histogram of the Coefficients and the Standard Errors
+
+The coefficients in the papers present a striking variability. In this section, we plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
+
+```{r, echo=FALSE}
+dat %>%
+  ggplot(aes(x = coef)) +
+  geom_histogram(bins = 15, color = "black") + 
+  labs(x = "Coefficients") + 
+  theme_bw()
+dat %>%
+  ggplot(aes(x = SE)) +
+  geom_histogram(bins = 10, color = "black") + 
+  labs(x = "Standard Errors") + 
+  theme_bw()
+```
+
+## Sign Coefficients
+
+One simple statistic that we can compute to access the law of 1/n is the frequency of positive and negative estimates.
+Below we plot the frequency for all the papers included in the meta-analytic dataset.
+
+```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
+dat %>%
+  ggplot(aes(x=as.factor(scoef))) + 
+  geom_bar(color = "black") + 
+  labs(x = "Coefficient Sign",
+       y = "") +
+  theme_bw()
+```
+
+# Descriptive Statistics of Moderators
+
+We chose a set of moderators that frequently appear in the literature and may help us interpret our results.
+We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$).
+The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal.
+The table below presents descriptive statistics for these moderators in our selection of articles.
+
+```{r, echo=F,warning=F,message=F}
+fulldat$usemeta2 <- factor(fulldat$usemeta)
+levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
+aux <- select(fulldat, usemeta2, indepvar2, year, published, 
+              elecsys2, method, agglevel, location2) %>%
+  rename(`Independent Variables` = indepvar2,
+         `Year` = year, 
+         `Published work` = published, 
+         `Electoral system` = elecsys2, 
+         `Estimation method` = method, 
+         `Sampling Aggregation Level` = agglevel, 
+         `Sample Location` = location2)
+
+export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
+                        show.p.overall = F, show.all = T),
+          caption = "Descriptive Statistics of Moderators")
+```
+
+# Binomial Tests for Coefficient Signs
+
+The law of 1/n poses we should have a positive influence of legislature size on expenditure.
+A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients.
+In statistical terms, consider a random variable representing the coefficient sign for the papers.
+As each sign of the paper is a Bernoulli trial, the aggregate for all papers follow a Binomial distribution, with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign.
+The law of 1/n can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
+The null hypothesis for such a test is that:
+
+- $H_0$: the proportion of positive and negative signs are indistinguishable ($p=0.5$).
+
+As we are taking an agnostic approach, we acknowledge that either the law of 1/n ($p>0.5$), or the reverse law of 1/n ($p<0.5$), could be true.
+In this case, the alternative hypothesis is $p\neq 0.5$.
+To perform this test, we run binomial tests in R, using the function `binom.test(.)`.
+
+This test has at least two advantages.
+First, it is robust to the design of the paper.
+As papers select different types of journals, countries, samples, and other characteristics, this increases the heterogeneity.
+This test ignores the design discrepancies and focus on the overall effect.
+Second, this test has the advantage of be simple and straightfoward.
+It requires very few assumption and has a direct statistical formulation.
+The disadvantage is that we can extract more information with meta-regressions.
+
+For the number of legislators in the lower house ($N$), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2=='N')
+aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+aux2
+```
+
+Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
+The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
+Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
+
+For the log of the number of legislators in the lower house ($\log(N)$), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2=='logN')
+aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+aux2
+```
+
+Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
+The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
+Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
+
+Finally, for the number of legislators in the upper house ($K$), the results follow below.
+
+```{r, echo=FALSE}
+aux <- filter(dat, indepvar2=='K')
+aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+aux2
+```
+
+Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
+The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
+Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
+This is the only test that presents evidence of an association between the legislature size and expenditure.
+
+# Meta-analysis {#meta-an}
+
+We combined the three independent ($N$, $\log(N)$, and $K$) with the levels of the three dependent variables (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
+This formed a 3x3 possibility for our analysis.
+
+## Per Capita Expenditure x N
+
+```{r, echo=FALSE}
+# Pooling effects analysis -- ExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+### Electoral system subgroup analysis
+
+The law of 1/n was created for majoritarian systems.
+In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
+We estimated a subgroup analysis using a binary electoral system.
+
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
+
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f1b <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(aes(color = group)) +
+  # Error Bars
+  geom_errorbarh(aes(color = group), height = 0.1) +
+  # Colors
+  scale_color_manual(values = c("#000000", "#8b0000")) + 
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 15, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1))
+
+f1b
+```
+
+Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
+The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
+Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+
+\newpage
+
+## Per Capita Expenditure x Log of Lower House Size
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
+\newpage
+
+## Per Capita Expenditure x Size of the Upper House
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+
+```{r}
+# Pooling effects analysis -- ExpPC x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f2 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure Per Capita')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+## Log of Expenditure Per Capita x Size of the Lower House
+
+This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
+
+```{r}
+# Pooling effects analysis -- logExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(
+  coef, SE, data=aux, 
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction = TRUE,
+  sm="SMD"
+  )
+
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+## Log of Expenditure Per Capita x Log of Lower House Size
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+
+```{r}
+# Pooling effects analysis -- logExpPC x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+## Log of Expenditure Per Capita x Size of Upper House
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
+## Expenditure as a Percentage of the GDP x Lower House Size
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+
+```{r}
+# Pooling effects analysis -- PCTGDP x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+## Expenditure as a Percentage of the GDP x Log of Lower House Size
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+
+```{r}
+# Pooling effects analysis -- PCTGDP x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(
+  coef, SE, data=aux, 
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction=TRUE,
+  sm="SMD"
+  )
+
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+## Expenditure as a Percentage of the GDP x Upper House Size
+
+This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
+
+```{r}
+# Pooling effects analysis -- PCTGDP x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F}
+f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F}
+f <- ggarrange(f1, f3, f5, 
+               ggplot() + theme_void(), f4, f6, 
+               f2, f7, ggplot() + theme_void(),
+               ncol = 3, nrow = 3, 
+               hjust = 0, align = 'hv')
+ggsave("./plots/fig.pdf", plot = f, width = 35, height = 25, units = "cm")
+```
+
+\newpage
+# Meta-Analysis (all coefficients) {#full-meta-an}
+
+## ExpPC x N
+
+```{r, echo=FALSE, warning=F}
+# Pooling effects analysis -- ExpPC x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+### Electoral system subgroup analysis
+
+The law of 1/n was created for majoritarian systems.
+In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
+We estimated a subgroup analysis using a binary electoral system.
+
+```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+mod2 <- tibble(
+  TE = mod$TE,
+  seTE = mod$seTE,
+  studlab = mod$studlab,
+  lower = mod$lower,
+  upper = mod$upper,
+  group = "A") %>%
+  bind_rows(.,
+            aux = tibble(
+              TE = c(mod$TE.random, NA),
+              seTE = c(mod$seTE.random, NA),
+              studlab = c("Overall Effect", "Prediction Interval"),
+              lower = c(mod$lower.random, mod$lower.predict),
+              upper = c(mod$upper.random, mod$upper.predict),
+              group = "B")) %>%
+  group_by(studlab) %>%
+  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+  ungroup()
+
+f8b <- mod2 %>%
+  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
+  # Studies coefs
+  geom_point(aes(color = group)) +
+  # Error Bars
+  geom_errorbarh(aes(color = group), height = 0.1) +
+  # Colors
+  scale_color_manual(values = c("#000000", "#8b0000")) + 
+  # X-axis limit
+  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
+  # Y-axis names
+  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+  # Vertical dashed line
+  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
+  # Labels
+  labs(x = "",
+       y = "") + 
+  # Facet - Separating Studies from Overall Effect
+  facet_grid(group~., scales = "free", space = "free") + 
+  # Theme
+  theme_minimal() %+replace%
+  theme(strip.text.y = element_blank(),
+        legend.position = "none",
+        axis.text.y = element_text(size = 13, hjust = 1.1),
+        axis.text.x = element_text(size = 15, hjust = 1.1)) 
+f8b
+```
+
+Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
+The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
+Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+
+\newpage
+## ExpPC x logN
+
+There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+
+## ExpPC x K
+
+Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+
+```{r, warning=F}
+# Pooling effects analysis -- ExpPC x K
+aux <- fulldat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+## logExpPC x N
+
+This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
+
+```{r, warning=F}
+# Pooling effects analysis -- logExpPC x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+## logExpPC x logN
+
+In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+
+```{r, warning=F}
+# Pooling effects analysis -- logExpPC x logN
+aux <- fulldat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+## logExpPC x K
+
+No studies related the log of per capita expenditure with the size of upper house (K).
+
+\newpage
+
+## PCTGDP x N
+
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+
+```{r, warning=F}
+# Pooling effects analysis -- PCTGDP x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+## PCTGDP x logN
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+
+```{r, warning=F}
+# Pooling effects analysis -- PCTGDP x logN
+aux <- fulldat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+## PCTGDP x K
+
+This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
+
+```{r, warning=F}
+# Pooling effects analysis -- PCTGDP x K
+aux <- fulldat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data=aux, 
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+# Meta-regressions {#meta-reg}
+
+## Meta-regressions for Expenditure as a Percentage of the GDP
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='PCTGDP',
+            slab = dat$authoryear)
+
+mod1 <- tibble(
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
+              round(mod[["ci.ub"]], digits = 4), ")"),
+  model = "PCTGDP"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+mod
+
+mod1_permu <- tibble(
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "PCTGDP - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3))) 
+```
+
+We have the following results for the meta-regressions of Expenditure Per Capita:
+
+1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
+2. Year has null effect.
+3. Unpublished papers tend to have higher coefficients than published papers.
+4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='PCTGDP',
+            slab = fulldat$authoryear)
+
+mod2 <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "PCTGDP - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3))) 
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+mod
+
+mod2_permu <- tibble(
+     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
+          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "PCTGDP - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+```
+
+For all the coefficients, we have the following results:
+
+1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
+2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
+3. Unpublished papers tend to have higher coefficients than published papers.
+4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
+
+## Meta-regressions for Expenditure Per Capita
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='ExpPC',
+            slab = dat$authoryear)
+
+mod3 <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
+          "Method: IV", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+mod
+
+mod3_permu <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
+          "Method: IV", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3))) 
+```
+
+We have the following results for the meta-regressions of Expenditure Per Capita:
+
+1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
+2. Year has null effect.
+3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
+4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
+5. When passing from `Local` to `State` level, decreases the detected effects.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='ExpPC',
+            slab = fulldat$authoryear)
+
+mod4 <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
+             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+mod
+
+mod4_permu <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
+             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+```
+
+With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:
+
+1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
+2. Year has now a positive effect on coefficient sizes.
+3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
+4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
+5. All other coeffients were not significant.
+
+## Meta-regressions for the Log of Expenditure Per Capita
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = dat$depvar2=='logExpPC',
+            slab = dat$authoryear)
+
+mod5 <- tibble(
+   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "logExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3))) 
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+mod
+
+mod5_permu <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "logExpPC - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+
+mod5_permu %>%
+  select(-model) %>%
+  kable(booktabs = T,align = "c",linesep ='') %>%
+  kable_styling(c("striped","bordered","scale_down"), position = "center")
+```
+
+We have the following results for the meta-regressions of Log of Expenditure Per Capita:
+
+1. Unpublished papers report a significantly higher coefficient.
+2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+3. All other coefficients remained insignificant.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha",
+            subset = fulldat$depvar2=='logExpPC',
+            slab = fulldat$authoryear)
+
+mod6 <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
+  model = "logExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+```
+
+```{r, warning=F}
+summary(mod)
+```
+
+```{r, echo=FALSE, warning=F}
+mod <- permutest(mod, progbar = F)
+
+mod6_permu <- tibble(
+  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
+             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
+  model = "logExpPC - All coefs - Permutation"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3))) 
+```
+
+With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
+
+1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
+2. All other coefficients remained insignificant.
+
+```{r, echo=F, warning=F, error=F, message=F}
+coefs <- tibble(
+  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
+    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))
+
+aux = list(mod3, mod5, mod1) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(
+         order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  filter(` ` != "Method: RDD") %>%
+  arrange(order) %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~(ifelse(is.na(.), " ", .)))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "Base") %>%
+  select(mod, everything())
+
+aux2 = list(mod4, mod6, mod2) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(
+         order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  arrange(order) %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"),-`T`,-T1,-T2)
+```
+
+\blandscape
+
+# Summary of Results
+
+```{r, echo=F, warning=F,error=F,message=F,asis=T}
+kable(aux, 
+      booktabs = T,
+      longtable = F,
+      align = "c",
+      linesep ='',
+      col.names = c(
+        " ",
+        " ",
+        "Estimate",
+        "SE",
+        "P-Value",
+        #
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif"
+      )) %>% 
+  collapse_rows(
+    1:2,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
+  kable_styling(
+    c("striped",
+      "bordered", 
+      "scale_down",
+      "repeat_header"
+      ),
+    position = "center",
+    latex_options = c("repeat_header")) %>%
+  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
+
+```
+\elandscape
+
+```{r, echo=F, warning=F,error=F,message=F}
+coefs <- tibble(
+  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
+    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
+)
+
+aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(
+         order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  arrange(order) %>%
+  filter(` ` != "Method: RDD") %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "Base") %>%
+  select(mod, everything())
+
+aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
+  map(~{
+    left_join(coefs, .x) %>%
+      mutate(model = ifelse(is.na(model), model[1], model)) 
+  }) %>%
+  reduce(bind_cols) %>%
+  mutate(order = ifelse(` ` == "Intercept", 1, NA),
+         order = ifelse(` ` == "Indepvar: N", 2, order),
+         order = ifelse(` ` == "Indepvar: logN", 3, order),
+         order = ifelse(` ` == "Year", 4, order),
+         order = ifelse(` ` == "Published: No", 5, order),
+         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
+         order = ifelse(` ` == "Method: Panel", 7, order),
+         order = ifelse(` ` == "Method: IV", 8, order),
+         order = ifelse(` ` == "Method: RDD", 9, order),
+         order = ifelse(` ` == "AggLevel: States", 10, order),
+         order = ifelse(` ` == "Location: World", 11, order)) %>%
+  arrange(order) %>%
+  mutate_at(vars(contains("Value")), list(
+    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
+                       ifelse(. < 0.01, "**",
+                              ifelse(. < 0.05, "*", 
+                                     ifelse(. >= 0.05, " ", 
+                                            ifelse(is.na(.), " ", .))))))))) %>%
+  mutate_at(vars(contains("Estimate") | contains("SE")),
+            list(~ifelse(is.na(.), " ", .))) %>%
+  select(-` 1`, -` 2`, -contains("model"), -order) %>%
+  mutate(mod = "All Coefs") %>%
+  select(mod, everything())
+
+aux <- bind_rows(aux, aux2) %>%
+  select(-contains("CI"),-`T`,-T1,-T2)
+```
+
+\blandscape
+
+# Summary of Results (Permutation)
+```{r, echo=F, warning=F,error=F,message=F,asis=T}
+kable(aux, 
+      booktabs = T,
+      longtable = F,
+      align = "c",
+      linesep ='',
+      col.names = c(
+        " ",
+        " ",
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif",
+        #
+        "Estimate",
+        "SE",
+        "Signif"
+      )) %>% 
+  collapse_rows(
+    1:2,
+    row_group_label_position ='stack'
+    ) %>%
+  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
+  kable_styling(
+    c("striped",
+      "bordered", 
+      "scale_down",
+      "repeat_header"
+      ),
+    position = "center",
+    latex_options = c("repeat_header")) %>%
+  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
+```
+\elandscape
+\newpage
+
+# The theory behind the Meta Analysis
+
+There are two main estimators for conducting meta analysis: fixed effects and random effects models.
+The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
+The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+
+In this paper, we use the random effects model.
+The empirical papers testing the law of 1/n are very diverse.
+We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
+
+1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
+2. **Electoral systems**: Majoritarian, PR, Mixed.
+3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
+
+These sources of heterogeneity have two implications.
+First, it makes our estimates very disperse.
+The heterogeneity tests are all but one significant.
+When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
+Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
+Thus, we opt for random effects model.
+
+Let each study having an effect of $T_i$.
+In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
+
+\[
+T_i \ = \ \theta_i + \varepsilon_i
+\]
+
+And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
+
+\[
+T_i \ = \ \mu + \xi_i + \varepsilon_i
+\]
+
+And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
+
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
+To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].
+
+# Robustness: Full model meta-regressions combined {#full-meta-reg}
+
+In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:
+
+1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
+2. The type of the independent variable in the stydy (N, K, log of N);
+3. The electoral system (Majoritarian, Proportional Representation, and Mixed).
+
+The results follow below, and show null effect for all variables, including the intercept.
+
+```{r, echo=F, warning=F}
+mod <-  rma(yi = coef, 
+              sei = SE, 
+              data = dat, 
+              method = "REML", 
+              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha")
+```
+
+```{r}
+summary(mod)
+```
+
+As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
+
+```{r, echo=FALSE}
+permutest(mod, progbar = F)
+```
+
+In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD).
+Below we also run the meta-regressions adding all coefficients in the papers.
+The results follow below:
+
+```{r, echo=F, warning=F}
+mod <- rma(yi = coef, 
+              sei = SE, 
+              data = fulldat, 
+              method = "REML", 
+              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              test = "knha")
+```
+
+```{r}
+summary(mod)
+```
+
+```{r}
+permutest(mod, progbar = F)
+```
+
+# Auxiliary functions
+
+## Graph functions code
+
+This function is for building a forest plot using `ggplot2` from meta analysis dataset.
+
+```{r, eval = FALSE}
+# Build plot function for forest plots
+build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
+  # Build dataset for plot
+  mod2 <- tibble(
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    bind_rows(.,
+              aux = tibble(
+                TE = c(mod$TE.random, NA),
+                seTE = c(mod$seTE.random, NA),
+                studlab = c("Overall Effect", "Prediction Interval"),
+                lower = c(mod$lower.random, mod$lower.predict),
+                upper = c(mod$upper.random, mod$upper.predict),
+                group = "B")) %>%
+    group_by(studlab) %>%
+    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+    ungroup()
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab2,TE), 
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group), height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
+    scale_y_discrete(
+      labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+    geom_vline(xintercept=0, 
+               color="#000000", linetype="dashed") +
+    labs(x = "",
+         y = "") + 
+    facet_grid(group~., scales = "free", space = "free") + 
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8*lsize, 
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6*lsize, 
+                                     hjust = 1.1),
+          plot.caption = element_text(size=lsize),
+          plot.title.position = 'plot', 
+          plot.title = element_text(hjust = 0.5, 
+                                    face = 'bold',
+                                    margin=margin(0,0,10,0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
+```
+
+## Webscraping code
+
+```{r, eval = FALSE}
+#### PACKAGES CONFIGURATION ####
+
+# Needed packages
+pkgs <- c('tidyverse', 'rvest', 'RSelenium')
+
+# Install if not already installed
+installIfNot <- function(x) {
+  if(x %in% rownames(installed.packages()) == FALSE) 
+    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
+} 
+lapply(pkgs, installIfNot)
+
+# Load packs
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
 
@@
 # site: https://scholar.google.com
-
 remDr$navigate("https://scholar.google.com/
@@
   next_button$clickElement()
-
   # Deleting cookies
@@
 # Scraping Scopus requires a bit more manual labor.
-# You can login on scopus through your university/institution and download the metadata
-#o fthe article(s) you want directly from there.
+# You can login on scopus through your university/institution 
+# and download the metadata of the article(s) you 
+# want directly from there.
 # All we need to do after that is scrape the information of
@@
 # url: https://academic.microsoft.com/home
-
 articles <- list()
@@
 write_csv(articles_links, "microsoft_academic_clean.csv")
-
-```
-
-## Article Selection
-
-The selection process was conducted by two authors in three phases.
-In the first round, we excluded all titles that were obviously unrelated to our topic of investigation.
-For instance, we curiously found articles about automobile motors amidst our sample.
-We consider this a preliminary step, since we were not able to eliminate a large number of entries.
-Thus, we read all abstracts.
-We chose to maintain those that indicated either government expenditure or legislative structures were central matters.
-For instance, if the paper sought to identify variables that increased government size, it was maintained.
-Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included.
-This allowed us to significantly reduce our sample to 376 records.
-
-In the second phase, we assessed full-texts.
-To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
-If the record was marked as positive for all three, it was maintained.
-Disagreements in this phase were discussed among the authors, and a third was consulted when needed.
-
-The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility.
-Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used.
-By observing what is most commonly used, we could decide which variables we would employ in our analysis.
-In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
-Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.
-
-#### Exclusion analysis
-
-We selected the final pool of articles based on two criteria regarding their reported coefficients:
-
-1. Matched treatment variable:
-  + N: Number Legislators Lower House
-  + logN: Log Number Legislators Lower House
-  + K: Number Legislators Upper House
-
-2. Matched outcome variable:
-  + ExpPC: Expenditure Per Capita
-  + logExpPC: Log Expenditure Per Capita
-  + PCTGDP: Percent GDP Public Expenditure
-
-### Flow Chart
-
-We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}.
-The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.
-
-\bigskip
-
-```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
-\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
-  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
-
-  \footnotesize
-  \linespread{1.0}
-
-  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};
-
-  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};
-
-  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
-
-  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
-
-  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};
-
-  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};
-
-  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};
-
-  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};
-
-  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};
-
-  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};
-
-  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};
-
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};
-
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
-  \draw [arrow] (id) -- (1st);
-  \draw [arrow] (id) -- (screen);
-  \draw [arrow] (screen) -- (2nd);
-  \draw [arrow] (screen) -- (elig);
-  \draw [arrow] (elig) -- (3rd);
-  \draw [arrow] (elig) -- (inc_1);
-  \draw [arrow] (inc_1) -- (4th);
-  \draw [arrow] (inc_1) -- (inc_2);
-
- \end{tikzpicture}
-
-```
-
-## Meta-analysis dataset
-
-The meta-analytic data is comprised of two datasets.
-The first dataset has the main coefficients that were reported in the paper.
-It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
-If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
-This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest.
-Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.
-
-In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
-Below is the data extraction process for all relevant coefficients in the selected articles.
-In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.
-
-```{r, echo=FALSE, include=FALSE}
-
-# Paper 367
-dat <- data.frame(
-  id = 367,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Spatially Targeted Government Spending and
-Heterogeneous Constituent Cost Shares',
-  author = 'Bradbury and Stephenson',
-  year = 2009,
-  authoryear = 'Bradbury and Stephenson (2009)',
-  journal = 'The Journal of Private Enterprise',
-  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
-  table = 2,
-  column = 2,
-  indepvar = 'MEMSENATE',
-  indepvar2 = 'K',
-  depvar = 'Total Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.624,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.624/3.10
-)
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 5,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.01262,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.01262/2.12
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 2,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.004964,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.004964/2.9
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 3,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.01134,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01134/4.52
-))
-
-# Paper 585 K
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 4,
-  indepvar = 'Upper size',
-  indepvar2 = 'K',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.00559,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.00559/2.39
-))
-
-# Paper 585 N
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 5,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.003627,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003627/2.51
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 2,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.000517,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.000517/0.47
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 3,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.016946,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.016946/8.65
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 585,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislative organization and government spending: cross-country evidence',
-  author = 'Bradbury and Crain',
-  year = 2001,
-  authoryear = 'Bradbury and Crain (2001)',
-  journal = 'Journal of Public Economics',
-  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
-  table = 2,
-  column = 4,
-  indepvar = 'Lower size',
-  indepvar2 = 'N',
-  depvar = 'Percent of GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.012337,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.012337/6.65
-))
-
-# Paper 505
-dat <- rbind(dat,
-  data.frame(
-  id = 505,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'IV',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
-  author = 'Matsusaka',
-  year = 2005,
-  authoryear = 'Matsusaka (2005)',
-  journal = 'State Politics & Policy Quarterly',
-  web = 'https://www.jstor.org/stable/40421558',
-  table = 1,
-  column = 3,
-  indepvar = 'Seats',
-  indepvar2 = 'N',
-  depvar = 'State Government Expenditure per Capita',
-  depvar2 = 'ExpPC',
-  coef = -0.96,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.18
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 1,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.213,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.018
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 2,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.229,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.037
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 3,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.455,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.038
-))
-
-# Paper 448
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'IV',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 4,
-  column = 4,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.411,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.049
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 1,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.226,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.053
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 2,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.213,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.317
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 3,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.185,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.305
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 4,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.235,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.336
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 5,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.374,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.064
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 6,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.811,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.181
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 7,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.795,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.176
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 448,
-  published = 'Yes',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Italy',
-  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
-  author = 'Fiorino and Ricciuti',
-  year = 2007,
-  authoryear = 'Fiorino and Ricciuti (2007)',
-  journal = 'Public Choice',
-  web = '10.1007/s11127-006-9108-y',
-  table = 3,
-  column = 8,
-  indepvar = 'LEG',
-  indepvar2 = 'N',
-  depvar = 'Per Capita Regional expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.849,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.238
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 974,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'Latin America',
-  title = 'Institutional arrangements and fiscal performance: the latin american experience',
-  author = 'Stein, Talvi, and Grisanti',
-  year = 1998,
-  authoryear = 'Stein et al. (1998)',
-  journal = 'NBER Working papers',
-  web = 'https://www.nber.org/papers/w6358.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'District magnitude',
-  indepvar2 = 'logN',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.0109,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.0143
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 974,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'Latin America',
-  title = 'Institutional arrangements and fiscal performance: the latin american experience',
-  author = 'Stein, Talvi, and Grisanti',
-  year = 1998,
-  authoryear = 'Stein et al. (1998)',
-  journal = 'NBER Working papers',
-  web = 'https://www.nber.org/papers/w6358.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'District magnitude',
-  indepvar2 = 'logN',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.0135,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.0121
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 4,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.003,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.009,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.002
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 2,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.011,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 7,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.003
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 1,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.04,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 2,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.03,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 3,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.01,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.002
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 542,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
-  author = 'Mukherjee',
-  year = 2003,
-  authoryear = 'Mukherjee (2003)',
-  journal = 'Comparative Political Studies',
-  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
-  table = 6,
-  column = 4,
-  indepvar = 'Seats in Lower Chamber',
-  indepvar2 = 'N',
-  depvar = 'Proportion expenditure GDP',
-  depvar2 = 'PCTGDP',
-  coef = 0.02,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.004
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 886,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Brazil',
-  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
-  author = 'Lledo',
-  year = 2003,
-  authoryear = 'Lledo (2003)',
-  journal = NA,
-  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
-  table = 6,
-  column = 1,
-  indepvar = 'Log (State Legislature Seats)',
-  indepvar2 = 'logN',
-  depvar = 'Primary Spending as a share of GSP',
-  depvar2 = 'PCTGDP',
-  coef = -4.69,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = -4.69/(-1.75)
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 862,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
-  author = 'Schaltegger and Feld',
-  year = 2009,
-  authoryear = 'Schaltegger and Feld (2009)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
-  table = 6,
-  column = 4,
-  indepvar = 'Seats in Parliament',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.001,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 862,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
-  author = 'Schaltegger and Feld',
-  year = 2009,
-  authoryear = 'Schaltegger and Feld (2009)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
-  table = 6,
-  column = 3,
-  indepvar = 'Seats in Parliament',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.001,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.001
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.302,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.302/7.885
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.276,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.276/7.185
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log (Expenduture per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.295,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.302/7.545
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 1,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.066,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.066/7.014
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.012,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.012/6.701
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 849,
-  published = 'No',
-  usemeta = 0,
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districts, spillovers, and government overspending',
-  author = 'Baqir',
-  year = 1999,
-  authoryear = 'Baqir (1999)',
-  journal = NA,
-  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-  table = 3,
-  column = 5,
-  indepvar = 'Log (Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Expenditure Share',
-  depvar2 = 'PCTGDP',
-  coef = 2.468,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.468/8.251
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.014,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = -0.011,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 5,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.007,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.007
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 7,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.005,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 10,
-  indepvar = 'House size',
-  indepvar2 = 'N',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.012,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.007
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 1,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.016,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.021,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.011
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.014,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.009
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.003,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.006
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 6,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.03,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.026
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 7,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.030,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.026
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 8,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.039,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.021
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 9,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.0127,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.014
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 1415,
-  published = 'No',
-  usemeta = 0,  
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislature size, bicameralism and government spending: evidence from democratic countries',
-  author = 'Ricciuti',
-  year = 2004,
-  authoryear = 'Ricciuti (2004)',
-  journal = NA,
-  web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
-  table = 3,
-  column = 10,
-  indepvar = 'Senate size',
-  indepvar2 = 'K',
-  depvar = 'Government spending',
-  depvar2 = 'PCTGDP',
-  coef = 0.016,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.012
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 4,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.1127,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0373
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.276,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0384
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 2,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.3021,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0383
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 578,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Districting and Government Overspending',
-  author = 'Baqir',
-  year = 2002,
-  authoryear = 'Baqir (2002)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/342804.pdf',
-  table = 4,
-  column = 3,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'ln(Government expenditure per capita)',
-  depvar2 = 'logExpPC',
-  coef = 0.3203,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.0384
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 4,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.82,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.19
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 1,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -1.7,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.31
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 2,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -2.37,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.37
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 3,
-  indepvar = 'Seats in lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -2.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.37
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 4,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.97,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.74
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 1,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 5.9,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.64
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 2,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 5.75,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.73
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 467,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Institutional constraints on government spending',
-  author = 'Primo',
-  year = 2006,
-  authoryear = 'Primo (2006)',
-  journal = 'Economics and Politics',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1468-0343.2006.00171.x',
-  table = 5,
-  column = 3,
-  indepvar = 'Seats in upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Real state and local expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 6.96,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.22
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Lower chamber size',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = -2.04,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 1.33
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Lower chamber size',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = -1.40,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.64
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 1,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 26.09,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 7.45
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.3,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.35
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.14,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.53
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.78,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.9
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 2,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 20.38,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 6.47
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 3,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.87,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 1.83
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 441,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of k/n: the effect of chamber size on government spending in bicameral legislatures',
-  author = 'Chen and Malhotra',
-  year = 2007,
-  authoryear = 'Chen and Malhotra (2007)',
-  journal = 'American Political Science Review',
-  web = 'https://www.cambridge.org/core/services/aop-cambridge-core/content/view/E794E71F3182DAAEA2DA1328D45FDCC7/S0003055407070566a.pdf',
-  table = 4,
-  column = 4,
-  indepvar = 'Upper chamber size',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 26.75,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.21
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 439,
-  published = 'Yes',
-  usemeta = 1,
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Legislative term limits and state spending',
-  author = 'Erler',
-  year = 2007,
-  authoryear = 'Erler (2007)',
-  journal = 'Public Choice',
-  web = 'https://www.jstor.org/stable/27698198',
-  table = 2,
-  column = 1,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 3.93,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 1.18
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 3,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.136,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.136/2.92
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 1,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.2319,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.2319/4.56
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 2,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.1443,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.1443/2.91
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 4,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.1594,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.1443/3.05
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 408,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'The impact of government structure on local public expenditures',
-  author = 'MacDonald',
-  year = 2008,
-  authoryear = 'MacDonald (2008)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-008-9308-8.pdf',
-  table = 5,
-  column = 5,
-  indepvar = 'ln(Council Size)',
-  indepvar2 = 'logN',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.2259,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.2259/4.04
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 5,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.159,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 6,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.147,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 7,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.09,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.038
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 8,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.081,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.039
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 9,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.088,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.038
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 1,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.21,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.023
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'OLS',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 2,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = .157,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.037
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 3,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.199,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.04
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 288,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Finland',
-  title = 'Does the size of the legislature affect the size of government? evidence from two natural experimentss',
-  author = 'Pettersson-Lidbom',
-  year = 2012,
-  authoryear = 'Pettersson-Lidbom (2012)',
-  journal = 'Journal of Public Economics',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272711001319?token=45100FEA2EACE2CA32B3D4B12207371CDF7382DE23901C13F772F671CD7DF21671CE755BAA419EB3443B138C62CE37B2',
-  table = 3,
-  column = 4,
-  indepvar = 'Council Size',
-  indepvar2 = 'N',
-  depvar = 'Log Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.169,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.041
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 231,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'IV',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Germany',
-  title = 'Coalition governments, cabinet size, and the common pool problem: evidence from the german states',
-  author = 'Baskaran',
-  year = 2013,
-  authoryear = 'Baskaran (2013)',
-  journal = 'European Journal of Political Economy',
-  web = 'https://reader.elsevier.com/reader/sd/pii/S0176268013000773?token=FECF22AE9B176134ACEB47AC0F11ACEFB1EA36D2D73BE992E1471732604540D3DCBD2D4A9CFDE2E44BE0B65C947FA4E3',
-  table = 3,
-  column = 4,
-  indepvar = 'Parliament seats',
-  indepvar2 = 'N',
-  depvar = 'Real Expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.974,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.974/1.743
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 230,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislatures, Leaders and Leviathans',
-  author = 'Maldonado',
-  year = 2013,
-  authoryear = 'Maldonado (2013)',
-  journal = 'Social Science Quarterly',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
-  table = 2,
-  column = 2,
-  indepvar = 'Size lower chamber',
-  indepvar2 = 'N',
-  depvar = 'Government Share of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.0609,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.0117
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 230,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'OLS',
-  elecsys = 'Mixed',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Countries',
-  location = 'World',
-  title = 'Legislatures, Leaders and Leviathans',
-  author = 'Maldonado',
-  year = 2012,
-  authoryear = 'Maldonado (2012)',
-  journal = 'Social Science Quarterly',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1111/j.1540-6237.2012.00895.x',
-  table = 2,
-  column = 2,
-  indepvar = 'Size upper chamber',
-  indepvar2 = 'K',
-  depvar = 'Government Share of GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.04,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.0132
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 1,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.003,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 3,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.006,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 2,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending (%) GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.004,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 220,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Switzerland',
-  title = 'The impact of within-party and between-party ideological dispersion on fiscal outcomes: evidence from Swiss cantonal parliaments',
-  author = 'Bjedov, Lapointe, and Madiès',
-  year = 2014,
-  authoryear = 'Bjedov et al. (2014)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-013-0149-8.pdf',
-  table = 3,
-  column = 4,
-  indepvar = 'Number of seats',
-  indepvar2 = 'N',
-  depvar = 'Spending (%) GDP',
-  depvar2 = 'PCTGDP',
-  coef = -0.008,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 4,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.174,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.085
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 1,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.223,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.052
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 2,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.215,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.061
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 208,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'Local',
-  location = 'US',
-  title = 'Communication in federal politics: universalism, policy uniformity, and the optimal allocation of fiscal authority',
-  author = 'Kessler',
-  year = 2014,
-  authoryear = 'Kessler (2014)',
-  journal = 'Journal of Political Economy',
-  web = 'https://www.jstor.org/stable/pdf/10.1086/676404.pdf?refreqid=excelsior%3A202fbd841dc5514e876482631872251b',
-  table = 2,
-  column = 3,
-  indepvar = 'Council size',
-  indepvar2 = 'N',
-  depvar = 'Spending per capita',
-  depvar2 = 'ExpPC',
-  coef = 0.158,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.054
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 1,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.21,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 4.051
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 2,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 8.423,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 18.17
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 3,
-  indepvar = 'Upper chamber (senate) seats',
-  indepvar2 = 'K',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 9.594,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.804
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 1,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = -0.351,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 0.745
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 2,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.975,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 2.646
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 3,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'The law of 1/n revisited: distributive politics, legislature size, and the costs of collective action',
-  author = 'Crowley',
-  year = 2019,
-  authoryear = 'Crowley (2019)',
-  journal = 'Southern Economic Journal',
-  web = 'https://onlinelibrary.wiley.com/doi/epdf/10.1002/soej.12388',
-  table = 2,
-  column = 3,
-  indepvar = 'Lower chamber (senate) seats',
-  indepvar2 = 'N',
-  depvar = 'Per capita total expenditure',
-  depvar2 = 'ExpPC',
-  coef = 7.658,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.922
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 8,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Indonesia',
-  title = 'Legislature size, local government expenditure and taxation, and public service access in indonesia',
-  author = 'Lewis',
-  year = 2019,
-  authoryear = 'Lewis (2019)',
-  journal = 'Studies in Comparative International Development',
-  web = 'https://link.springer.com/content/pdf/10.1007/s12116-019-09278-1.pdf',
-  table = 4,
-  column = NA,
-  indepvar = 'Legislature size',
-  indepvar2 = 'N',
-  depvar = 'Log per capita total expenditure',
-  depvar2 = 'logExpPC',
-  coef = -0.174,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = (-0.174+0.245)/1.96
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 1,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -0.851,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 1.395
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 2,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = -1.689,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.697
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 3,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 7.632,
-  scoef = 'N',
-  scoefsig = NA,
-  SE = 2.309
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 1,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 19.74,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 8.406
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 2,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 10.06,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 3.965
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 42,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Court-ordered redistricting and the law of 1/n',
-  author = 'Lee and Park',
-  year = 2018,
-  authoryear = 'Lee and Park (2018)',
-  journal = 'Public Choice',
-  web = NA,
-  table = 2,
-  column = 3,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Total expenditure per capita',
-  depvar2 = 'ExpPC',
-  coef = 9.062,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 20.38
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 1,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 2,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.03,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.01
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 82,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'RDD',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'Local',
-  location = 'Germany',
-  title = 'The effect of legislature size on public spending: evidence from a regression discontinuity design',
-  author = 'Höhmann',
-  year = 2017,
-  authoryear = 'Höhmann (2017)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/content/pdf/10.1007/s11127-017-0484-2.pdf',
-  table = 2,
-  column = 3,
-  indepvar = 'Total number of seats in the legislature',
-  indepvar2 = 'N',
-  depvar = 'Log expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = -0.04,
-  scoef = 'N',
-  scoefsig = 'N',
-  SE = 0.02
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 102,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Australia',
-  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
-  author = 'Drew and Dollery',
-  year = 2017,
-  authoryear = 'Drew and Dollery (2017)',
-  journal = 'Urban Affairs Review',
-  web = '10.1007/s11127-016-0369-9',
-  table = 2,
-  column = 1,
-  indepvar = 'No. of representatives',
-  indepvar2 = 'N',
-  depvar = 'Ln Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.077,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 0.028
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 102,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'PR',
-  elecsys2 = 'Non-Maj',
-  agglevel = 'States',
-  location = 'Australia',
-  title = 'The price of democracy? political representation structure and per capita expenditure in victorian local government',
-  author = 'Drew and Dollery',
-  year = 2017,
-  authoryear = 'Drew and Dollery (2017)',
-  journal = 'Urban Affairs Review',
-  web = '10.1007/s11127-016-0369-9',
-  table = 2,
-  column = 2,
-  indepvar = 'No. of representatives',
-  indepvar2 = 'N',
-  depvar = 'Ln Expenditure per capita',
-  depvar2 = 'logExpPC',
-  coef = 0.031,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 0.022
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 1,
-  indepvar = 'Lower',
-  indepvar2 = 'N',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 0.0164,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 1.313
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 1, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 1,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 38.44,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 19.23
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 2,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 37.85,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 17.77
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 3,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 25.61,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.48
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 4,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 5.996,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.06
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 5,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 25.56,
-  scoef = 'P',
-  scoefsig = 'P',
-  SE = 13.49
-))
-
-dat <- rbind(dat,
-  data.frame(
-  id = 132,
-  published = 'Yes',
-  usemeta = 0, 
-  method = 'PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj',
-  agglevel = 'States',
-  location = 'US',
-  title = 'Supermajority rule and bicameral bargaining',
-  author = 'Lee',
-  year = 2016,
-  authoryear = 'Lee (2016)',
-  journal = 'Public Choice',
-  web = 'https://link.springer.com/article/10.1007/s11127-016-0369-9',
-  table = 3,
-  column = 6,
-  indepvar = 'Upper',
-  indepvar2 = 'K',
-  depvar = 'Per capita expenditure',
-  depvar2 = 'ExpPC',
-  coef = 4.693,
-  scoef = 'P',
-  scoefsig = NA,
-  SE = 12.35
-))
-
-dat <- dat[order(dat$id),]
-dat <- dat[!is.na(dat$coef),]
-row.names(dat) <- NULL
-levels(dat$elecsys2) <- c('Majoritarian', 'Non-Majoritarian')
-dat$scoef <- factor(as.character(dat$scoef), labels = c('N', 'P'))
-dat$scoefsig <- factor(as.character(dat$scoefsig), labels = c('N', 'P'))
-levels(dat$scoef) <- c('Negative', 'Positive')
-levels(dat$scoefsig) <- c('Negative', 'Positive')
-dat$method <- factor(as.character(dat$method), 
-                     levels = c("OLS", "PANEL", "IV", "RDD"))
-dat$location2 <- as.character(dat$location)
-dat$location2[dat$location2!='World'] = 'Country'
-dat$location2 <- factor(as.character(dat$location2), 
-                     levels = c("Country", "World"))
-dat$agglevel <- factor(as.character(dat$agglevel), 
-                     levels = c("Local", "States", "Countries"))
-fulldat <- dat
-dat <- dat %>%
-  filter(usemeta==1)
-```
-
-## Descriptive statistics
-
-### Study Year
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
-dat %>%
-  ggplot(aes(x = as.factor(year))) + 
-    geom_bar(color = "black") + 
-  labs(x = "",
-       y = "") + 
-  theme_bw()
-```
-
-### Published?
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
-dat %>%
-  ggplot(aes(x = as.factor(published))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Published study?",
-       y = "") + 
-  theme_bw()
-```
-
-### Dependent variables
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
-dat %>%
-  mutate(depvar2 = factor(depvar2, 
-                          labels = c("Per Capita Expenditure",
-                                     "Percentage GDP Government Expenditure",
-                                     "Log Per Capita Expenditure"))) %>%
-  ggplot(aes(x = depvar2)) +
-    geom_bar(color = "black") + 
-  labs(x = "Dependent Variables",
-       y = "") + 
-  coord_flip() + 
-  theme_bw()
-```
-
-### Independent variables
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
-dat %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
-                                                  'N (lower house legislators)',
-                                                  'Log N'))) %>%
-  ggplot(aes(x = indepvar2)) + 
-    geom_bar(color = "black") + 
-  labs(x = "Independent Variables",
-       y = "") +
-  coord_flip() +
-  theme_bw() 
-```
-
-### Histogram Coefficients
-
-```{r, echo=FALSE}
-dat %>%
-  ggplot(aes(x = coef)) +
-  geom_histogram(bins = 15, color = "black") + 
-  labs(x = "Coefficients") + 
-  theme_bw()
-```
-
-### Histogram Standard Errors
-
-```{r, echo=FALSE}
-dat %>%
-  ggplot(aes(x = SE)) +
-  geom_histogram(bins = 10, color = "black") + 
-  labs(x = "Standard Errors") + 
-  theme_bw()
-```
-
-### Sign Coefficients
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
-dat %>%
-  ggplot(aes(x=as.factor(scoef))) + 
-  geom_bar(color = "black") + 
-  labs(x = "Coefficient Sign",
-       y = "") +
-  theme_bw()
-```
-
-### Descriptive Statistics of Moderators
-
-We chose a set of moderators that frequently appear in the literature and may help us interpret our results.
-We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$).
-The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal.
-The table below presents descriptive statistics for these moderators in our selection of articles.
-
-```{r, echo=F,warning=F,message=F}
-fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
-aux <- select(fulldat, usemeta2, indepvar2, year, published, 
-              elecsys2, method, agglevel, location2) %>%
-  rename(`Independent Variables` = indepvar2,
-         `Year` = year, 
-         `Published work` = published, 
-         `Electoral system` = elecsys2, 
-         `Estimation method` = method, 
-         `Sampling Aggregation Level` = agglevel, 
-         `Sample Location` = location2)
-
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
-                        show.p.overall = F, show.all = T),
-          caption = "Descriptive Statistics of Moderators")
-```
-
-### Binomial Tests for Coefficient Signs
-
-A general test of the theory would be to study whether the coefficients are positive or negative.
-Note that the law of 1/n poses we should have a positive influence of legislature size on expenditure.
-To test this theory, we run a Binomial One-Proportion Z-test.
-The test consists in contrasting the number of occurences of positive and negative signs (Binomial trials) against the hypothesis that they were produced with 0.5 percent chance.
-Note that if this is the case, any detected difference would be a mere XXXX of chance.
-
-For the number of legislators in the lower house (N), the results follow below.
-
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2=='N')
-binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
-```
-
-Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample.
-For the log of the number of legislators in the lower house (log(N)), the results follow below.
-
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2=='logN')
-binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
-```
-
-For log(N), although most coefficients were negative, there are very few studies, making the Finally, for the number of legislators in the upper house (K), the results follow below.
-
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2=='K')
-binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
-```
-
-Here, the law of 1/n holds. However, the effect goes in a direction different from the predicted in the law of k/n paper.
-
-### Electoral system
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral system"}
-dat %>%
-  ggplot(aes(x=as.factor(elecsys2))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Electoral system",
-       y = "") + 
-  theme_bw()
-```
-
-### Electoral system x Sign Coefficient
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$elecsys2)
-chisq.test(table(dat$scoef, dat$elecsys2), simulate.p.value = T)
-```
-
-### Independent Variable x Sign Coefficient
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$indepvar2)
-chisq.test(table(dat$scoef, dat$indepvar2), simulate.p.value = T)
-```
-
-### Dependent variables x Independent variables
-
-```{r, echo=FALSE}
-table(dat$scoef, dat$depvar2)
-chisq.test(table(dat$scoef, dat$depvar2), simulate.p.value = T)
-```
-
-## Meta-analysis {#meta-an}
-
-We combined the three independent (N, logN, and K) with the levels of the three dependent variables (ExpPC, logExpPC, PCTGDP). This formed a 3x3 possibility for our analysis.
-
-### ExpPC x N
-
-```{r, echo=FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f1 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f1
-```
-
-```{r,include=F,warning=F}
-f1 + 
-  labs(caption = "ExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fa.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-#### Electoral system subgroup analysis
-
-The law of 1/n was created for majoritarian systems.
-In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary electoral system.
-
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
-mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
-
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f1b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f1b
-```
-
-Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
-
-\newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+```
+
+# Software Version for this Appendix
 
 ```{r}
-# Pooling effects analysis -- ExpPC x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f2 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f2
-```
-
-```{r,include=F,warning=F}
-f2 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fb.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x N
-
-This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
-
-```{r}
-# Pooling effects analysis -- logExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(
-  coef, SE, data=aux, 
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction = TRUE,
-  sm="SMD"
-  )
-
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f3 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f3
-```
-
-```{r,include=F,warning=F}
-f3 + 
-  labs(caption = "logExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fc.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
-
-```{r}
-# Pooling effects analysis -- logExpPC x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f4 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f4
-```
-
-```{r,include=F,warning=F}
-f4 + 
-  labs(caption = "logExpPC x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fd.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
-
-```{r}
-# Pooling effects analysis -- PCTGDP x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f5 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f5
-```
-
-```{r,include=F,warning=F}
-f5 + 
-  labs(caption = "PCTGDP x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fe.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### PCTGDP x logN
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
-
-```{r}
-# Pooling effects analysis -- PCTGDP x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(
-  coef, SE, data=aux, 
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction=TRUE,
-  sm="SMD"
-  )
-
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f6 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f6
-```
-
-```{r,include=F,warning=F}
-f6 + 
-  labs(caption = "PCTGDP x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/ff.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### PCTGDP x K
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
-
-```{r}
-# Pooling effects analysis -- PCTGDP x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f7 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f7
-```
-
-```{r,include=F,warning=F}
-f7 + 
-  labs(caption = "PCTGDP x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 18, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fg.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-```{r,include=F,warning=F}
-blank = ggplot() + 
-  geom_blank() +
-  theme_minimal()
-blank
-ggsave("./plots/zz_blank.png", width = 30, height = 18.75, units = "cm")
-
-plots = list.files(path = "./plots/", pattern = "*.png") %>%
-  map(~{
-    image_read(path = paste0("./plots/", .x)) %>%
-      image_rotate(., 270) %>%
-      image_border(., "#ffffff ", "90x18")
-  })
-```
-
-```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F,message=F}
-
-p_1 = image_append(c(plots[[3]], plots[[2]], plots[[1]]), stack = T)
-p_2 = image_append(c(plots[[6]], plots[[5]], plots[[4]]), stack = T)
-p_3 = image_append(c(plots[[15]],plots[[7]],plots[[15]]), stack = T)
-p_full = image_append(c(p_1, p_2, p_3))
-
-p_full
-
-magick::image_write(p_full,"figure 1.png")
-```
-
-\newpage
-## Meta-Analysis (all coefficients) {#full-meta-an}
-
-### ExpPC x N
-
-```{r, echo=FALSE}
-# Pooling effects analysis -- ExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f8 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 9, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f8
-```
-
-```{r,include=F,warning=F}
-f8 + 
-  labs(caption = "ExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fh.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-#### Electoral system subgroup analysis
-
-The law of 1/n was created for majoritarian systems.
-In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary electoral system.
-
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f8b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f8b
-```
-
-Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
-
-\newpage
-### ExpPC x logN
-
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
-
-### ExpPC x K
-
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
-
-```{r}
-# Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f9 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f9
-```
-
-```{r,include=F,warning=F}
-f9 + 
-  labs(caption = "ExpPC x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 12, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fi.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x N
-
-This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
-
-```{r}
-# Pooling effects analysis -- logExpPC x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f10 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f10
-```
-
-```{r,include=F,warning=F}
-f10 + 
-  labs(caption = "logExpPC x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fj.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
-### logExpPC x logN
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
-
-```{r}
-# Pooling effects analysis -- logExpPC x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f11 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f11
-```
-
-```{r,include=F,warning=F}
-f11 + 
-  labs(caption = "logExpPC x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fk.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-### logExpPC x K
-
-No studies related the log of per capita expenditure with the size of upper house (K).
-
-\newpage
-### PCTGDP x N
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
-
-```{r}
-# Pooling effects analysis -- PCTGDP x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f12 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 10, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1)) 
-f12
-```
-
-```{r,include=F,warning=F}
-f12 + 
-  labs(caption = "PCTGDP x N") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fl.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-### PCTGDP x logN
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
-
-```{r}
-# Pooling effects analysis -- PCTGDP x logN
-aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f13 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f13
-```
-
-```{r,include=F,warning=F}
-f13 + 
-  labs(caption = "PCTGDP x logN") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 20, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fm.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-### PCTGDP x K
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
-
-```{r}
-# Pooling effects analysis -- PCTGDP x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f14 <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) + 
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") + 
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") + 
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f14
-```
-
-```{r,include=F,warning=F}
-f14 + 
-  labs(caption = "PCTGDP x K") +
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1),
-        plot.caption = element_text(size=22))
-
-ggsave("./plots/fn.png", width = 30, height = 18.75, units = "cm")
-
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-```{r, echo=FALSE, fig.width=20, fig.height=2}
-
-p_1 = image_append(c(plots[[10]], plots[[9]], plots[[8]]), stack = T)
-p_2 = image_append(c(plots[[13]], plots[[12]], plots[[11]]), stack = T)
-p_3 = image_append(c(plots[[15]],plots[[14]],plots[[15]]), stack = T)
-p_full = image_append(c(p_1, p_2, p_3))
-
-p_full
-
-magick::image_write(p_full,"figure 2.png")
-```
-
-## Meta-regressions {#meta-reg}
-
-### Meta-regressions for Expenditure as a Percentage of the GDP
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='PCTGDP',
-            slab = dat$authoryear)
-
-mod1 <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ", 
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "PCTGDP"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod1_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-We have the following results for the meta-regressions of Expenditure Per Capita:
-
-1. Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
-2. Year has null effect.
-3. Unpublished papers tend to have higher coefficients than published papers.
-4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-mod2 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-
-mod <- permutest(mod, progbar = F)
-mod
-
-mod2_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-For all the coefficients, we have the following results:
-
-1. Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
-2. Year has a positive effect: the younger the publication, the higher the detected coefficient.
-3. Unpublished papers tend to have higher coefficients than published papers.
-4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
-
-### Meta-regressions for Expenditure Per Capita
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear)
-
-mod3 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod3_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-We have the following results for the meta-regressions of Expenditure Per Capita:
-
-1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2. Year has null effect.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
-4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
-5. When passing from `Local` to `State` level, decreases the detected effects.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-mod4 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-
-mod <- permutest(mod, progbar = F)
-mod
-
-mod4_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:
-
-1. Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2. Year has now a positive effect on coefficient sizes.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
-4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
-5. All other coeffients were not significant.
-
-### Meta-regressions for the Log of Expenditure Per Capita
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-mod5 <- tibble(
-   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-
-mod5_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-mod5_permu %>%
-  select(-model) %>%
-  kable(booktabs = T,align = "c",linesep ='') %>%
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
-
-```
-
-We have the following results for the meta-regressions of Log of Expenditure Per Capita:
-
-1. Unpublished papers report a significantly higher coefficient.
-2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-3. All other coefficients remained insignificant.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-mod6 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-```{r}
-summary(mod)
-```
-
-```{r, echo=FALSE}
-mod <- permutest(mod, progbar = F)
-
-mod6_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-```
-
-With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
-
-1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
-2. All other coefficients remained insignificant.
-
-```{r, echo=F, warning=F,error=F,message=F}
-coefs <- tibble(
-  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
-    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))
-
-aux = list(mod3, mod5, mod1) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
-  filter(` ` != "Method: RDD") %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~(ifelse(is.na(.), " ", .)))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4, mod6, mod2) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-
-```
-
-\blandscape
-
-## Summary of Results
-
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = F,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif"
-      )) %>% 
-  collapse_rows(
-    1:2,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header")) %>%
-  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
-
-```
-\elandscape
-
-```{r, echo=F, warning=F,error=F,message=F}
-coefs <- tibble(
-  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
-    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
-)
-
-aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
-  arrange(order) %>%
-  filter(` ` != "Method: RDD") %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-
-```
-
-\blandscape
-## Summary of Results (Permutation)
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = F,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif"
-      )) %>% 
-  collapse_rows(
-    1:2,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header")) %>%
-  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
-
-```
-\elandscape
-
-\newpage
-## Theory of Meta Analysis
-
-There are two main estimators for conducting meta analysis: fixed effects and random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
-
-In this paper, we use the random effects model.
-The empirical papers testing the law of 1/n are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
-
-1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
-2. **Electoral systems**: Majoritarian, PR, Mixed.
-3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
-
-These sources of heterogeneity have two implications.
-First, it makes our estimates very disperse.
-The heterogeneity tests are all but one significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
-Thus, we opt for random effects model.
-
-Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
-
-\[
-T_i \ = \ \theta_i + \varepsilon_i
-\]
-
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
-
-\[
-T_i \ = \ \mu + \xi_i + \varepsilon_i
-\]
-
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
-To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].
-
-## Robustness: Full model meta-regressions combined {#full-meta-reg}
-
-In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:
-
-1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
-2. The type of the independent variable in the stydy (N, K, log of N);
-3. The electoral system (Majoritarian, Proportional Representation, and Mixed).
-
-The results follow below, and show null effect for all variables, including the intercept.
-
-```{r, echo=F, warning=F}
-mod <-  rma(yi = coef, 
-              sei = SE, 
-              data = dat, 
-              method = "REML", 
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha")
-```
-
-```{r}
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, echo=FALSE}
-permutest(mod, progbar = F)
-```
-
-In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD).
-Below we also run the meta-regressions adding all coefficients in the papers.
-The results follow below:
-
-```{r, echo=F, warning=F}
-mod <- rma(yi = coef, 
-              sei = SE, 
-              data = fulldat, 
-              method = "REML", 
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
-              test = "knha")
-```
-
-```{r}
-summary(mod)
-```
-
-```{r}
-permutest(mod, progbar = F)
-```
+sessionInfo()
+```

### 2020-06-13 appendix/tikz2pdf.tex
commit graphs and finishing appendix 1

\documentclass{article}
\usepackage[pdftex,active,tightpage]{preview}
\usepackage[utf8]{inputenc}
\usepackage[skins]{tcolorbox}
\usepackage{
tikz,
enumitem,
xcolor,
pgfplots
}
\begin{document}

  \tikzstyle{phase} = [rectangle, rounded corners, minimum width = 3cm, minimum height = 2cm, text centered, text width = 4cm, draw = black, thick, fill=white]
  \tikzstyle{exc} = [rectangle, rounded corners, minimum width = 3cm, minimum height = 2cm, text centered, text width = 4cm, draw = black, thick, fill=gray!10]
  \tikzstyle{stage} = [rectangle, minimum height = 1cm, minimum width = 2cm, text centered, draw = black, very thick]
  \tikzstyle{stage2} = [rectangle, minimum height = 1cm, minimum width = 3.5cm, text centered, draw = black, very thick]
  \tikzstyle{arrow} = [ultra thick,->,>=stealth]

\begin{preview}
%% TIKZ_CODE %%
\end{preview}

\end{document}

### 2020-06-13 appendix/appendix_final.Rmd
commit appendix 2

@@
                ggplot() + theme_void(), f4, f6, 
-               f2, f7, ggplot() + theme_void(),
+               f2, ggplot() + theme_void(), f7,
                ncol = 3, nrow = 3, 

### 2020-06-13 appendix/appendix_final.Rmd
appendix commit 3

@@
 f <- ggarrange(f1, f3, f5, 
-               ggplot() + theme_void(), f4, f6, 
-               f2, ggplot() + theme_void(), f7,
+               f4, f6, ggplot() + theme_void(),
+               f2, f7,
                ncol = 3, nrow = 3, 
@@
 ggsave("./plots/fig.pdf", plot = f, width = 35, height = 25, units = "cm")
+f <- ggarrange(f1, f4, f2,
+               f3, f6, 
+               f7, f5,
+               ncol = 3, nrow = 3, 
+               hjust = 0, align = 'hv')
+ggsave("./plots/fig2.pdf", plot = f, width = 35, height = 25, units = "cm")
 ```
@@
 \newpage
+
 # Meta-Analysis (all coefficients) {#full-meta-an}

### 2020-06-13 appendix/appendix_final.Rmd
commit appendix 4

--- 2020-06-13 appendix/appendix_final.Rmd
@@
 f <- ggarrange(f1, f3, f5, 
-               ggplot() + theme_void(), f4, f6, 
-               f2, ggplot() + theme_void(), f7,
+               f4, f6,
+               f2, f7,
                ncol = 3, nrow = 3, 

### 2020-06-14 appendix/appendix_final.Rmd
commit review mig 1

@@
 
+# Load datasets
+load('../dataset/dataCoefs.RData')
+
 # Build plot function for forest plots
@@
                 seTE = c(mod$seTE.random, NA),
-                studlab = c("Overall Effect", "Prediction Interval"),
-                lower = c(mod$lower.random, mod$lower.predict),
-                upper = c(mod$upper.random, mod$upper.predict),
+                studlab = c("Overall Effect", 
+                            "Prediction Interval"),
+                lower = c(mod$lower.random, 
+                          mod$lower.predict),
+                upper = c(mod$upper.random,
+                          mod$upper.predict),
                 group = "B")) %>%
@@
     geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group), height = 0.1) +
+    geom_errorbarh(aes(color = group), 
+                   height = 0.1) +
     scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
+    scale_x_continuous(limits = c(-1.1*limg, 1.1*limg)) +
     scale_y_discrete(
-      labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
+      labels = function(x) 
+        str_replace(x, "_[0-9]*$", "")) + 
     geom_vline(xintercept=0, 
@@
 
-```{r, echo=FALSE, include=FALSE}
-load('../dataset/dataCoefs.RData')
-```
-
 # Descriptive statistics
@@
 
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
-                        show.p.overall = F, show.all = T),
-          caption = "Descriptive Statistics of Moderators")
+#export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+#                     show.p.overall = F, show.all = T),
+#          caption = "Descriptive Statistics of Moderators")
+
+descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+           show.p.overall = F, show.all = T)
 ```
@@
 
-## Per Capita Expenditure x N
+## Lower House Size and Expenditure per Capita
 
@@
 
-## Per Capita Expenditure x Log of Lower House Size
+## Log Lower House Size and Expenditure per Capita
 
@@
 
-## Per Capita Expenditure x Size of the Upper House
+## Upper House Size and Expenditure per Capita
 
@@
 
-## Log of Expenditure Per Capita x Size of the Lower House
+## Lower House Size and Log Expenditure Per Capita
 
@@
 
-## Log of Expenditure Per Capita x Log of Lower House Size
+## Log of Lower House Size and Log of Expenditure Per Capita
 
@@
 
-## Log of Expenditure Per Capita x Size of Upper House
+## Log of Upper House Size and Log of Expenditure Per Capita
 
@@
 
-## Expenditure as a Percentage of the GDP x Lower House Size
+## Lower House Size and Expenditure as Percentage of GDP
 
@@
 \newpage
-## Expenditure as a Percentage of the GDP x Log of Lower House Size
+
+## Log Lower House Size and Expenditure as Percentage of GDP
 
@@
 \newpage
-## Expenditure as a Percentage of the GDP x Upper House Size
+
+## Upper House Size and Expenditure as Percentage of GDP
 
@@
 
-## ExpPC x N
+## Lower House Size and Expenditure Per Capita
 
@@
 \newpage
-## ExpPC x logN
+## Log of Lower House Size and Expenditure Per Capita
 
@@
 
-## ExpPC x K
+## Upper House Size and Expenditure Per Capita
 
@@
 \newpage
-## logExpPC x N
+## Lower House Size and Log of Expenditure Per Capita
 
@@
 \newpage
-## logExpPC x logN
+## Log of Lower House Size and Log of Expenditure Per Capita
 
@@
 
-## logExpPC x K
+## Upper House Size and Log of Expenditure Per Capita
 
@@
 
-## PCTGDP x N
+## Lower House Size and Expenditure as Percentage of GDP
 
@@
 
-## PCTGDP x logN
+## Log of Lower House Size and Expenditure as Percentage of GDP
 
@@
 
-## PCTGDP x K
+## Upper House Size and Expenditure as Percentage of GDP
 
@@
 mod1 <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+     ` ` = c("Intercept", 
+             "Indepvar: N", 
+             "Indepvar: logN", 
+             "Year", 
+             "Published: No",
+             "Elecsys: Non-Majoritarian", 
+             "Method: Panel", 
+             "AggLevel: States", 
+             "Location: World"),
   Estimate = mod[["beta"]],
@@
 mod1_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+     ` ` = c("Intercept", 
+             "Indepvar: N", 
+             "Indepvar: logN", 
+             "Year", 
+             "Published: No", 
+             "Elecsys: Non-Majoritarian", 
+             "Method: Panel", 
+             "AggLevel: States", 
+             "Location: World"),
   Estimate = mod[["beta"]],
@@
 mod2 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Indepvar: logN", 
+          "Year", 
+          "Published: No",
+          "Elecsys: Non-Majoritarian", 
+          "Method: Panel", 
+          "AggLevel: States", 
+          "Location: World"),
   Estimate = mod[["beta"]],
@@
 mod2_permu <- tibble(
-     ` ` = c("Intercept", "Indepvar: N", "Indepvar: logN", "Year", "Published: No",
-          "Elecsys: Non-Majoritarian", "Method: Panel", "AggLevel: States", "Location: World"),
+     ` ` = c("Intercept", 
+             "Indepvar: N", 
+             "Indepvar: logN", 
+             "Year", 
+             "Published: No",
+             "Elecsys: Non-Majoritarian", 
+             "Method: Panel", 
+             "AggLevel: States", 
+             "Location: World"),
   Estimate = mod[["beta"]],
@@
 mod6 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Published: No",
+          "Method: Panel", 
+          "Method: RDD", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod6_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "Method: RDD", "AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Published: No",
+          "Method: Panel", 
+          "Method: RDD", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 coefs <- tibble(
-  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
-    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World"))
+  ` ` = c("Intercept", 
+          "Indepvar: N",
+          "Indepvar: logN", 
+          "Year", 
+          "Published: No", 
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel", 
+          "Method: IV", 
+          "Method: RDD", 
+          "AggLevel: States", 
+          "Location: World"))
 
@@
 coefs <- tibble(
-  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
-    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
+  ` ` = c("Intercept", 
+          "Indepvar: N",
+          "Indepvar: logN", 
+          "Year", 
+          "Published: No", 
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel", 
+          "Method: IV", 
+          "Method: RDD", 
+          "AggLevel: States", 
+          "Location: World")
 )
@@
 
-# The theory behind the Meta Analysis
+# The Theory behind the Meta Analysis
 
@@
 
-## Graph functions code
+## Function for generate the Meta-Analytic Figures
 

### 2020-06-15 appendix/appendix_final.Rmd
commit final appendix 06/14
commit app 06/15 1

@@
 
-## Geographical Location
-
-The geographical location also varies considerably in the sample.
-In our sampled papers, `r as.numeric(table(unique(select(dat, id, location2))$location2)[1])` studied a given country, while `r as.numeric(table(unique(select(dat, id, location2))$location2)[2])` used a cross-country design, with more than one country.
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Geographical Location"}
-dat %>%
-  select(id, location2) %>%
-  unique() %>%
-  ggplot(aes(x=as.factor(location2))) + 
-    geom_bar(color = "black") + 
-  labs(x = "Geographical Location",
-       y = "") + 
-  theme_bw()
-```
-
 ## Dependent variables
@@
 aux <- select(fulldat, usemeta2, indepvar2, year, published, 
-              elecsys2, method, agglevel, location2) %>%
+              elecsys2, method, agglevel) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Estimation method` = method, 
-         `Sampling Aggregation Level` = agglevel, 
-         `Sample Location` = location2)
+         `Sampling Aggregation Level` = agglevel)
 
@@
               method = "REML", 
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              mods = ~indepvar2+year+published+elecsys2+method+agglevel, 
               test = "knha",
@@
              "Method: Panel", 
-             "AggLevel: States", 
-             "Location: World"),
+             "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
               method = "REML", 
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              mods = ~ indepvar2+year+published+elecsys2+method+agglevel, 
               test = "knha",
@@
           "Method: Panel", 
-          "AggLevel: States", 
-          "Location: World"),
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod3 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Elecsys: Non-Majoritarian", 
+          "Method: Panel",
+          "Method: IV", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod3_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian", "Method: Panel",
-          "Method: IV", "AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Elecsys: Non-Majoritarian", 
+          "Method: Panel",
+          "Method: IV", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod4 <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel", 
+          "Method: IV" ,
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod4_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Elecsys: Non-Majoritarian",
-             "Method: Panel", "Method: IV" ,"AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel", 
+          "Method: IV", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod5 <- tibble(
-   ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
+   ` ` = c("Intercept", 
+           "Indepvar: N", 
+           "Year", 
+           "Published: No",
+           "Method: Panel",
+           "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
 mod5_permu <- tibble(
-  ` ` = c("Intercept", "Indepvar: N", "Year", "Published: No",
-             "Method: Panel", "AggLevel: States"),
+  ` ` = c("Intercept", 
+          "Indepvar: N", 
+          "Year", 
+          "Published: No",
+          "Method: Panel", 
+          "AggLevel: States"),
   Estimate = mod[["beta"]],
@@
           "Method: RDD", 
-          "AggLevel: States", 
-          "Location: World"))
+          "AggLevel: States"))
 
@@
          order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
+         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
   filter(` ` != "Method: RDD") %>%
@@
          order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order),
-         order = ifelse(` ` == "Location: World", 11, order)) %>%
+         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
   arrange(order) %>%
@@
           "Method: RDD", 
-          "AggLevel: States", 
-          "Location: World")
+          "AggLevel: States")
 )
@@
               method = "REML", 
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel+location2, 
+              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel, 
               test = "knha")
@@
 
-This function is for building a forest plot using `ggplot2` from meta analysis dataset.
+This function receives the meta-analysis results and build a forest plot using `ggplot2`.
 

### 2020-06-16 appendix/appendix_final.Rmd
minor fixes

@@
 
-# Search criteria
+# Search Criteria
 
 The first step in reviews is to gather a sample of records.
-This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must contain all of it.
+This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must encompass all of it.
 At the same time, the sample should be concise enough to optimise the work flow.
@@
 The selection process was conducted by two authors in three phases.
-In the first round, we excluded all titles that were obviously unrelated to our topic of investigation.
+In the first round, we excluded all titles that were obviously unrelated to our topic.
 For instance, we curiously found articles about automobile motors amidst our sample.
@@
 
-## Exclusion analysis
+## Exclusion Analysis
 
@@
 
-# Meta-analysis dataset
+# Meta-Analysis Dataset
 
 The meta-analytic data is comprised of two datasets.
-The first dataset has the main coefficients that were reported in the paper.
+The first has the main coefficients that were reported in the paper.
 It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
@@
 Below is the data extraction process for all relevant coefficients in the selected articles.
-In the \@ref(meta-an) and \@ref(meta-reg) sections of this Appendix, you will find all tests performed in both reduced and full samples.
-
-# Descriptive statistics
+In the Meta-Analysis and Meta-Regressions sections of this Appendix, you will find all tests performed in both reduced and full samples.
+
+# Descriptive Statistics
 
@@
     geom_bar(color = "black") + 
-  labs(x = "Published study?",
+  labs(x = "Published Study?",
        y = "") + 
@@
 
-## Electoral system
+## Electoral System
 
 There are many differences in the papers relative to the research design.
-One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, in non-majoritarian democracies.
+One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, to non-majoritarian democracies.
 In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated.
@@
 
-## Dependent variables
+## Dependent Variables
 
@@
 
-## Independent variables
+## Independent Variables
 
@@
 
-This test has at least two advantages.
+This test has two advantages.
 First, it is robust to the design of the paper.
@@
 
-# Meta-analysis {#meta-an}
+# Meta-Analysis
 
@@
 
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
 3.
@@
 
-### Electoral system subgroup analysis
+### Electoral System Subgroup Analysis
 
@@
 
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+Now, we look into the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
 
@@
 
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
 3.
@@
 No studies related the log of per capita expenditure with the size of upper house (K).
+
+\newpage
 
@@
 
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+This model investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
 
@@
 
-# Meta-Analysis (all coefficients) {#full-meta-an}
+# Meta-Analysis (All Coefficients)
 
@@
 
-```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
 build_forest(mod, NULL)
@@
 \newpage
-### Electoral system subgroup analysis
+### Electoral System Subgroup Analysis
 
@@
 
+\newpage
+
 ## Upper House Size and Log of Expenditure Per Capita
@@
 
-# Meta-regressions {#meta-reg}
-
-## Meta-regressions for Expenditure as a Percentage of the GDP
+# Meta-Regressions
+
+## Meta-Regressions for Expenditure as a Percentage of the GDP
 
@@
 
-We have the following results for the meta-regressions of Expenditure Per Capita:
+We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:
 
@@
 3. Unpublished papers tend to have higher coefficients than published papers.
-4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
 5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
-
-## Meta-regressions for Expenditure Per Capita
+6. Passing from `Local` to `State` or `World` levels decreases the detected effect size.
+
+## Meta-Regressions for Expenditure Per Capita
 
@@
 
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita Regressions are the following:
+With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:
 
@@
 2. Year has now a positive effect on coefficient sizes.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the effects on per capita expenditure found in our models.
+3. Passing electoral rules from `Majoritarian` to `Non-Majoritarian` significantly increases the effects on per capita expenditure found in our models.
 4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
@@
 
-1. Unpublished papers report a significantly higher coefficient.
+1. Unpublished papers report significantly higher coefficients.
 2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
@@
 
-# The Theory behind the Meta Analysis
+# The Theory Behind the Meta Analysis
 
@@
 These sources of heterogeneity have two implications.
-First, it makes our estimates very disperse.
-The heterogeneity tests are all but one significant.
+First, they make our estimates very disperse.
+All but one of our heterogeneity tests are significant.
 When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and bised.
+Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
 Thus, we opt for random effects model.
@@
 Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ come from, $\theta_i$, and a within-study error $\varepsilon_i$:
+In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
 
@@
 
-# Robustness: Full model meta-regressions combined {#full-meta-reg}
+# Robustness: Full model Meta-Regressions Combined
 
@@
 1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
-2. The type of the independent variable in the stydy (N, K, log of N);
+2. The type of the independent variable in the stydy ($N$, $K$, $log (N)$);
 3. The electoral system (Majoritarian, Proportional Representation, and Mixed).
@@
 
-# Auxiliary functions
-
-## Function for generate the Meta-Analytic Figures
-
-This function receives the meta-analysis results and build a forest plot using `ggplot2`.
+# Auxiliary Functions
+
+## Function to Generate Meta-Analytic Figures
+
+This function receives the meta-analysis results and builds a forest plot using `ggplot2`.
 
@@
 
-## Webscraping code
+## Webscraping Code
 

### 2020-06-19 appendix/appendix.Rmd
cleaning up

--- 2020-06-16 appendix/appendix_final.Rmd
@@
 - "Catarina Roman[^roman]"
-date: June 13, 2020
+date: \today
 fontfamily: libertine
 fontawesome: yes
-fontsize: 12pt
+fontsize: 11pt
 monospace-url: yes
@@
 # Knitr options
-knitr::opts_chunk$set(fig.pos = 'H') # holds figure position
+knitr::opts_chunk$set(fig.pos = "H") # holds figure position
 knitr::opts_chunk$set(echo = TRUE)
@@
 # Needed packages
-pkgs <- c('tidyverse', 'meta', 'metafor', 
-          'readxl', 'compareGroups',
-          'knitr', 'gridGraphics', 'gridExtra',
-          'ggpubr','kableExtra','magick')
+pkgs <- c("tidyverse", "meta", "metafor",
+          "readxl", "compareGroups",
+          "knitr", "gridGraphics", "gridExtra",
+          "ggpubr", "kableExtra", "magick")
 
@@
 installIfNot <- function(x) {
-  if(x %in% rownames(installed.packages()) == FALSE) 
-    install.packages(x, dependencies = T, repos = "http://cran.us.r-project.org")
+  if (x %in% rownames(installed.packages()) == FALSE)
+    install.packages(x, dependencies = T,
+					 repos = "http://cran.us.r-project.org")
 }
@@
 # Load datasets
-load('../dataset/dataCoefs.RData')
+load("../dataset/dataCoefs.RData")
 
@@
   p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab2,TE), 
+    ggplot(aes(y = reorder(studlab2, TE),
                x = TE, xmin = lower, xmax = upper)) +
@@
     scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1*limg, 1.1*limg)) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
     scale_y_discrete(
@@
         str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept=0, 
-               color="#000000", linetype="dashed") +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
     labs(x = "",
@@
           legend.position = "none",
-          axis.text.y = element_text(size = .8*lsize, 
+          axis.text.y = element_text(size = .8 * lsize,
                                      hjust = 1),
-          axis.text.x = element_text(size = .6*lsize, 
+          axis.text.x = element_text(size = .6 * lsize,
                                      hjust = 1.1),
-          plot.caption = element_text(size=lsize),
-          plot.title.position = 'plot', 
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
           plot.title = element_text(hjust = 0.5,
-                                    face = 'bold',
-                                    margin=margin(0,0,10,0)),
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
           panel.grid.major = element_blank())
@@
 
-The first step in reviews is to gather a sample of records.
-This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must encompass all of it.
-At the same time, the sample should be concise enough to optimise the work flow.
-Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew.
-This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation.
-The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics".
-Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.
-
-We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736).
-The R script we wrote extracted, to a CSV file, the title, abstract, authors, year, journal of publication, and database from which the record originated.
-We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc.
+The first step in our systematic review consisted in gathering a study sample.
+We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature.
+This search produced a database with many entries that were unrelated to our subject of investigation.
+To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics", which is a seminal contribution in the field.
+Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, our search resulted in 2,664 records as of the 21\textsuperscript{st} of November 2019.
+
+We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736).
+The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated.
+Our code is available in section \ref{sub:scrap} below.
+We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses.
 We set no restriction to unpublished articles.
@@
 Thus, we read all abstracts.
-We chose to maintain those that indicated either government expenditure or legislative structures were central matters.
+We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper.
 For instance, if the paper sought to identify variables that increased government size, it was maintained.
-Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included.
+Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were also included.
 This allowed us to significantly reduce our sample to 376 records.
 
-In the second phase, we assessed full-texts.
-To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
+In the second phase, we assessed full texts.
+To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
 If the record was marked as positive for all three, it was maintained.
-Disagreements in this phase were discussed among the authors, and a third was consulted when needed.
+Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
 
 The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility.
-Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used.
-By observing what is most commonly used, we could decide which variables we would employ in our analysis.
+Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information.
+We decided which variables to keep by following the current practices of the literature.
 In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
@@
 1. Matched treatment variable:
-  + *N*: Number Legislators Lower House
-  + *logN*: Log Number Legislators Lower House
-  + *K*: Number Legislators Upper House
+  + *N*: Number Legislators in the Lower House
+  + *logN*: Log Number Legislators in the Lower House
+  + *K*: Number Legislators in the Upper House
 
@@
 
-We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}.
+The diagram below shows each step of our article selection process.
+We followed the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA) statement to conduct our study\footnote{More information about the PRISMA statement is available at \url{http://www.prisma-statement.org}.}.
 The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.
@@
 The meta-analytic data is comprised of two datasets.
-The first has the main coefficients that were reported in the paper.
-It includes only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
+The first dataset has the main coefficients reported in the studies.
+These data include only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
 If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
@@
 Below is the data extraction process for all relevant coefficients in the selected articles.
-In the Meta-Analysis and Meta-Regressions sections of this Appendix, you will find all tests performed in both reduced and full samples.
+Here we present the results of all tests performed in both reduced and full samples.
 
@@
 
-In this section, we present the descriptive statistics for our meta-analytic sample.
-We focus in the following paper characteristics: study year, whether the paper has been published or not, the three dependent variables of interest, the three independent variables of interest, and a few statistics about the coefficients.
-We also add a descriptive statistics table, similar to the one in the main paper.
+In this section, we show the descriptive statistics for our meta-analytic sample.
+We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.
+We also add a descriptive statistics table similar to the one in the main paper.
 
@@
 The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`.
-Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the 1/n hypothesis.
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Study Year Frequencies"}
+Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the _law of 1/n_.
+
+```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
 dat %>%
@@
 
-We decided to report studies regardless of their publication status.
+Studies were included in our sample regardless of their publication status.
 From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
+```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
 dat %>%
@@
 
-There are many differences in the papers relative to the research design.
-One remarkable difference is the application of the theory, that was build with majoritarian systems in mind, to non-majoritarian democracies.
-In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographycally concentrated.
-The concentration facilitates politicians to use pork-barrel project to captivate their electoral supporters.}
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Electoral Systems"}
+Our study selection differs considerably in regards to research design.
+One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was build with majoritarian systems in mind, to non-majoritarian democracies.
+In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
+The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}
+
+```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
 dat %>%
@@
 
-The aggregation level is also an important characteristic of the empirical tests of the law of 1/n.
-The model was build to explain the dynamics of majoritarian countries, but the theory was tested in municipal, county, states, and country levels.
-In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` studied *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied *State* (or Provincial) levels, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` studied *Country* level data.
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Sample Aggregate Level"}
+The aggregation level is also an important characteristic of the empirical tests of the _law of 1/n_.
+While the original model was build to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels.
+In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` analysed data from the *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied the *state* (or Provincial) level, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` used *country* level data.
+
+```{r, fig.width=4, fig.height=3, fig.cap="Sample Aggregate Level", cache=TRUE}
 dat %>%
@@
 
-The outcome variables included in the paper were:
+The outcome variables included in the paper are:
 
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
+```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
 dat %>%
@@
 
-Most of papers in our meta-analytic sample study the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
+Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
 The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`).
-Finally, the minority of papers study the Natural Log of the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`).
-Some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.
-
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Independent variables across the law of 1/n studies"}
+Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`).
+As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.
+
+```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
 dat %>%
@@
   unique() %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c('K (upper house legislators)',
-                                                  'N (lower house legislators)',
-                                                  'Log N'))) %>%
+  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
+                                                  "N (lower house legislators)",
+                                                  "Log N"))) %>%
   ggplot(aes(x = indepvar2)) +
@@
 
-```{r, echo=FALSE}
+Coefficients:
+
+```{r, cache=TRUE, fig.width=5, fig.height=4}
 dat %>%
@@
   theme_bw()
+```
+
+Standard errors:
+
+```{r, cache=TRUE, fig.width=5, fig.height=4}
 dat %>%
@@
 
-One simple statistic that we can compute to access the law of 1/n is the frequency of positive and negative estimates.
+One simple statistic that we can compute to assess the validity of the _law of 1/n_ is the frequency of positive and negative estimates in the study sample.
 Below we plot the frequency for all the papers included in the meta-analytic dataset.
 
-```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
+```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
 dat %>%
@@
 
-```{r, echo=F,warning=F,message=F}
+\newpage
+
+```{r, warning=F,message=F, cache=TRUE}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
+levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
 aux <- select(fulldat, usemeta2, indepvar2, year, published,
@@
 
-#export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-#                     show.p.overall = F, show.all = T),
-#          caption = "Descriptive Statistics of Moderators")
-
 descrTable(~.-usemeta2, aux, y = aux$usemeta2,
@@
 
-The law of 1/n poses we should have a positive influence of legislature size on expenditure.
-A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients.
+The _law of 1/n_ posits that we should expect a positive influence of legislature size on public expenditures.
+A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations.
 In statistical terms, consider a random variable representing the coefficient sign for the papers.
-As each sign of the paper is a Bernoulli trial, the aggregate for all papers follow a Binomial distribution, with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign.
-The law of 1/n can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
+As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the  chance of a positive sign.
+The _law of 1/n_ can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
 The null hypothesis for such a test is that:
@@
 
-As we are taking an agnostic approach, we acknowledge that either the law of 1/n ($p>0.5$), or the reverse law of 1/n ($p<0.5$), could be true.
+As we are taking an agnostic approach, we acknowledge that either the _law of 1/n_ ($p>0.5$), or the _reverse law of 1/n_ ($p<0.5$) could be true.
 In this case, the alternative hypothesis is $p\neq 0.5$.
-To perform this test, we run binomial tests in R, using the function `binom.test(.)`.
+To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.
 
@@
 First, it is robust to the design of the paper.
-As papers select different types of journals, countries, samples, and other characteristics, this increases the heterogeneity.
-This test ignores the design discrepancies and focus on the overall effect.
-Second, this test has the advantage of be simple and straightfoward.
+This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not.
+All these factors increase the levels of study heterogeneity.
+The binomial test ignores the design discrepancies and focuses on the overall reported effect.
+Second, this test has the advantage of being straightforward and easy to interpret.
 It requires very few assumption and has a direct statistical formulation.
-The disadvantage is that we can extract more information with meta-regressions.
+The disadvantage is that we can extract more information from the articles with meta-regressions, as we see in the next sections.
 
@@
 
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2=='N')
-aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+```{r, cache=TRUE}
+aux <- filter(dat, indepvar2 == "N")
+aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
 aux2
@@
 
-```{r, echo=FALSE}
-aux <- filter(dat, indepvar2=='logN')
-aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+```{r, cache=TRUE}
+aux <- filter(dat, indepvar2 == "logN")
+aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
 aux2
@@
 
-```{r, echo=FALSE}
+```{r, cache=TRUE}
 aux <- filter(dat, indepvar2=='K')
@@
 
+\newpage
+
 # Meta-Analysis
 
-We combined the three independent ($N$, $\log(N)$, and $K$) with the levels of the three dependent variables (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
-This formed a 3x3 possibility for our analysis.
+## Estimation Method
+
+In general terms, there are two main ways to conduct a meta-analysis, using fixed effects or random effects models.
+The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
+The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+
+In this paper, we use the random effects model.
+The empirical papers testing the _law of 1/n_ are very diverse.
+We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
+
+1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
+2. **Electoral systems**: Majoritarian, PR, Mixed.
+3. **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
+
+These sources of heterogeneity have two implications.
+First, they make our estimates very disperse.
+All but one of our heterogeneity tests are significant.
+When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
+Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
+Thus, we opt for random effects model.
+
+Let each study having an effect of $T_i$.
+In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
+
+\[
+T_i \ = \ \theta_i + \varepsilon_i
+\]
+
+And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
+
+\[
+T_i \ = \ \mu + \xi_i + \varepsilon_i
+\]
+
+And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
+
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
+To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data.
+
+We combined the three independent variables ($N$, $\log(N)$, and $K$) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
+This formed a $3 \times 3$ table, and in the following pages we present the results for each of these combinations.
 
@@
 
-```{r, echo=FALSE}
+```{r, cache=TRUE}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
@@
 1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
 3.
@@
 
-The law of 1/n was created for majoritarian systems.
+The _law of 1/n_ was created for majoritarian systems.
 In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
 mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
@@
 
-\newpage
-
 ## Upper House Size and Expenditure per Capita
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
 build_forest(mod, NULL)
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+The forest plot is available below:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
@@
 1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
 3.
@@
 
-\newpage
-
 ## Lower House Size and Expenditure as Percentage of GDP
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x N
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+Below, you may find the forest plot:
+
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x logN
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+The forest plot follows below:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r}
+```{r, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x K
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
+The forest plot follows below:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r,include=F,warning=F}
+```{r,include=F,warning=F, cache=TRUE}
 f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F}
-f <- ggarrange(f1, f3, f5, 
-               f4, f6,
-               f2, f7,
-               ncol = 3, nrow = 3, 
-               hjust = 0, align = 'hv')
-ggsave("./plots/fig.pdf", plot = f, width = 35, height = 25, units = "cm")
-f <- ggarrange(f1, f4, f2,
-               f3, f6, 
-               f7, f5,
-               ncol = 3, nrow = 3, 
-               hjust = 0, align = 'hv')
-ggsave("./plots/fig2.pdf", plot = f, width = 35, height = 25, units = "cm")
-```
-
-\newpage
-
 # Meta-Analysis (All Coefficients)
@@
 
-```{r, echo=FALSE, warning=F}
+```{r, warning=F, cache=T}
 # Pooling effects analysis -- ExpPC x N
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=12, fig.height=6, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
+The forest plot:
+
+```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 \newpage
+
 ### Electoral System Subgroup Analysis
 
-The law of 1/n was created for majoritarian systems.
+The _law of 1/n_ was created for majoritarian systems.
 In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
+```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=T}
 mod2 <- tibble(
@@
 The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+Both are non-significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
 
 \newpage
+
 ## Log of Lower House Size and Expenditure Per Capita
@@
 
-Now we are investigating the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
-
-```{r, warning=F}
+Now we investigate the effect of the upper house size ($K$) on government spending. In the model below, we evaluate the relationship between upper house size and expenditure per capita (ExpPC).
+
+```{r, warning=F, cache=TRUE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
+```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 \newpage
+
 ## Lower House Size and Log of Expenditure Per Capita
@@
 
-```{r, warning=F}
+```{r, warning=F, cache=TRUE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
+The forest plot is shown below:
+
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 \newpage
+
 ## Log of Lower House Size and Log of Expenditure Per Capita
@@
 
-```{r, warning=F}
+```{r, warning=F, cache=TRUE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
+The forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+2. The estimated SMD in the random effects model is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
 3.
@@
 
-No studies related the log of per capita expenditure with the size of upper house (K).
-
-\newpage
+No studies related the log of per capita expenditure with the size of upper house ($K$).
 
@@
 
-```{r, warning=F}
+```{r, warning=F, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x N
@@
   filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod <- metagen(coef, SE, data = aux,
+          studlab = paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm = "SMD")
+mod
+```
+
+Here is the forest plot:
+
+```{r, fig.width=8, fig.height=6, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+## Log of Lower House Size and Expenditure as Percentage of GDP
+
+This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the natural logarithm of lower house size (log($N$)) as the treatment variable.
+
+```{r, warning=F, cache=TRUE}
+# Pooling effects analysis -- PCTGDP x logN
+aux <- fulldat %>%
+  filter(indepvar2 == 'logN',
          depvar2 == 'PCTGDP')
@@
 
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
+The forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-## Log of Lower House Size and Expenditure as Percentage of GDP
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
-
-```{r, warning=F}
-# Pooling effects analysis -- PCTGDP x logN
+\newpage
+
+## Upper House Size and Expenditure as Percentage of GDP
+
+This model looks into the effect of upper house size ($K$) on the public expenditure share of the GDP (PCTGDP).
+
+```{r, warning=F, cache=TRUE}
+# Pooling effects analysis -- PCTGDP x K
 aux <- fulldat %>%
-  filter(indepvar2 == 'logN',
+  filter(indepvar2 == 'K',
          depvar2 == 'PCTGDP')
@@
 
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-## Upper House Size and Expenditure as Percentage of GDP
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
-
-```{r, warning=F}
-# Pooling effects analysis -- PCTGDP x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod <- metagen(coef, SE, data=aux, 
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-mod
-```
-
-And the forest plot:
-
-```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
-build_forest(mod, NULL)
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2. The Random effects modem SMD estimated is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
-3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+\newpage
 
@@
 
-```{r, echo=F, warning=F}
+```{r, warning=F, cache=T}
 mod <-  rma(yi = coef,
@@
 
-```{r, warning=F}
+```{r, warning=F, cache=T}
 summary(mod)
@@
 
-```{r, echo=FALSE, warning=F}
+```{r, warning=F, cache=T}
 mod <- permutest(mod, progbar = F)
@@
 4. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `World` levels, it decreases the detected effect size.
+5. In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
+6. When passing from `Local` to `State` or `Country` levels, it decreases the detected effect size.
 
@@
 
-```{r, echo=F, warning=F}
+```{r, warning=F, cache=T}
 mod <- rma(yi = coef,
@@
 
-```{r, echo=F, warning=F}
+```{r, error=F, warning=F, cache=T}
 mod <-  rma(yi = coef,
@@
 
-```{r, warning=F}
+```{r, warning=F, cache=T}
 summary(mod)
 ```
-
 As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
 
-```{r, echo=FALSE, warning=F}
+```{r, error=F, warning=F, cache=T}
 mod <- permutest(mod, progbar = F)
@@
 
-## Meta-regressions for the Log of Expenditure Per Capita
-
-```{r, echo=F, warning=F}
+## Meta-Regressions for the Log of Expenditure Per Capita
+
+```{r, warning=F, cache=T}
 mod <- rma(yi = coef,
@@
 
-```{r, echo=F, warning=F, error=F, message=F}
+```{r, warning=F, error=F, message=F, cache=T}
 coefs <- tibble(
@@
 
-\blandscape
-
-# Summary of Results
-
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = F,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "P-Value",
-        #
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif"
-      )) %>% 
-  collapse_rows(
-    1:2,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header")) %>%
-  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
-
-```
-\elandscape
-
-```{r, echo=F, warning=F,error=F,message=F}
-coefs <- tibble(
-  ` ` = c("Intercept", 
-          "Indepvar: N",
-          "Indepvar: logN", 
-          "Year", 
-          "Published: No", 
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel", 
-          "Method: IV", 
-          "Method: RDD", 
-          "AggLevel: States")
-)
-
-aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
-  arrange(order) %>%
-  filter(` ` != "Method: RDD") %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model)) 
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*", 
-                                     ifelse(. >= 0.05, " ", 
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-```
-
-\blandscape
-
-# Summary of Results (Permutation)
-```{r, echo=F, warning=F,error=F,message=F,asis=T}
-kable(aux, 
-      booktabs = T,
-      longtable = F,
-      align = "c",
-      linesep ='',
-      col.names = c(
-        " ",
-        " ",
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif",
-        #
-        "Estimate",
-        "SE",
-        "Signif"
-      )) %>% 
-  collapse_rows(
-    1:2,
-    row_group_label_position ='stack'
-    ) %>%
-  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
-  kable_styling(
-    c("striped",
-      "bordered", 
-      "scale_down",
-      "repeat_header"
-      ),
-    position = "center",
-    latex_options = c("repeat_header")) %>%
-  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")
-```
-\elandscape
-\newpage
-
-# The Theory Behind the Meta Analysis
-
-There are two main estimators for conducting meta analysis: fixed effects and random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
-
-In this paper, we use the random effects model.
-The empirical papers testing the law of 1/n are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
-
-1. **Subjects**: Counties, Municipalities, States, Provinces, Countries.
-2. **Electoral systems**: Majoritarian, PR, Mixed.
-3. **Modeling strategies**: Panel data, Standard OLS, IV, RDD.
-
-These sources of heterogeneity have two implications.
-First, they make our estimates very disperse.
-All but one of our heterogeneity tests are significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
-Thus, we opt for random effects model.
-
-Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
-
-\[
-T_i \ = \ \theta_i + \varepsilon_i
-\]
-
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
-
-\[
-T_i \ = \ \mu + \xi_i + \varepsilon_i
-\]
-
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in (Doing Meta-Analysis with R)[https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html].
-To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it as more precise when we have continuous measures, such as we have on our data (link)[https://www.ncbi.nlm.nih.gov/pubmed/26332144].
-
-# Robustness: Full model Meta-Regressions Combined
+# Robustness: Full Model Meta-Regressions Combined
 
@@
 
-```{r, echo=FALSE}
+```{r, cache=T}
 permutest(mod, progbar = F)
@@
 
-```{r}
+```{r, cache=T}
 summary(mod)
@@
 
-```{r}
+```{r, cache=T}
 permutest(mod, progbar = F)
@@
 
-```{r, eval = FALSE}
+```{r, eval = FALSE, cache=T}
 # Build plot function for forest plots
@@
       labels = function(x) str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept=0, 
-               color="#000000", linetype="dashed") +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
     labs(x = "",
@@
 
-## Webscraping Code
-
-```{r, eval = FALSE}
+## Webscraping Code \label{sub:scrap}
+
+```{r, eval = FALSE, cache=T}
 #### PACKAGES CONFIGURATION ####
@@
 # Needed packages
-pkgs <- c('tidyverse', 'rvest', 'RSelenium')
+pkgs <- c("tidyverse", "rvest", "RSelenium")
 
@@
 
-for (j in 1:213) { # we had to manually choose the number of pages here; Y.M.M.V.
+for (j in 1:213) { # we had to manually choose the number of pages here
 
@@
 
-# Software Version for this Appendix
+# Session Information
 

### 2020-06-19 appendix/appendix.Rmd
tiny fixes

@@
 
-[^roman]: Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, <catarinamroman@gmail.com>.
+[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil, <catarinamroman@gmail.com>.
 
@@
 Our study selection differs considerably in regards to research design.
-One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was build with majoritarian systems in mind, to non-majoritarian democracies.
+One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies.
 In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
@@
 The aggregation level is also an important characteristic of the empirical tests of the _law of 1/n_.
-While the original model was build to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels.
+While the original model was built to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels.
 In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` analysed data from the *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied the *state* (or Provincial) level, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` used *country* level data.
@@
 2. Year has null effect.
-3. Passing the electoral rules from `Majoritarian` to `Non-Majoritarian`, increases significantly the per capita expenditure found in our models.
+3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
 4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
-5. When passing from `Local` to `State` level, decreases the detected effects.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+5. When passing from `Local` to `State` level, the detected effects decrease.
+
+We also run the meta-regressions adding all coefficients in the papers. The results follow below:
 
@@
 2. Year has now a positive effect on coefficient sizes.
-3. Passing electoral rules from `Majoritarian` to `Non-Majoritarian` significantly increases the effects on per capita expenditure found in our models.
+3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
 4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
@@
 
-In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling by:
+In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:
 
 1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
-2. The type of the independent variable in the stydy ($N$, $K$, $log (N)$);
+2. The type of the independent variable in the study ($N$, $K$, $log (N)$);
 3. The electoral system (Majoritarian, Proportional Representation, and Mixed).
 
-The results follow below, and show null effect for all variables, including the intercept.
+The results follow below, and show null effects for all variables, including the intercept.
 
@@
 
-In the main text, we selected the coefficients based on the regressions that had most observations and that presented a full model (with fixed effects or intermediate bandwidth in RDD).
-Below we also run the meta-regressions adding all coefficients in the papers.
+In the main text, we selected coefficients based on the regressions that had most observations and presented a full model (with fixed effects or intermediate bandwidth in RDD).
+We also run the meta-regressions adding all coefficients in the papers.
 The results follow below:

### 2020-06-19 appendix/appendix.Rmd
fix appedix 06/19

@@
 
-## Aggregation Level
-
-The aggregation level is also an important characteristic of the empirical tests of the _law of 1/n_.
-While the original model was built to explain the dynamics of majoritarian countries, the theory has been tested at the municipal, county, states, and country levels.
-In our sample, `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[1])` analysed data from the *local* level (municipalities and counties), `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[2])` studied the *state* (or Provincial) level, and `r as.numeric(table(unique(select(dat, id, agglevel))$agglevel)[3])` used *country* level data.
-
-```{r, fig.width=4, fig.height=3, fig.cap="Sample Aggregate Level", cache=TRUE}
-dat %>%
-  select(id, agglevel) %>%
-  unique() %>%
-  ggplot(aes(x=as.factor(agglevel))) +
-    geom_bar(color = "black") +
-  labs(x = "Sample Aggregate Level",
-       y = "") +
-  theme_bw()
-```
-
 ## Dependent Variables
@@
 aux <- select(fulldat, usemeta2, indepvar2, year, published,
-              elecsys2, method, agglevel) %>%
+              elecsys2, method) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Electoral system` = elecsys2,
-         `Estimation method` = method,
-         `Sampling Aggregation Level` = agglevel)
+         `Estimation method` = method)
 
@@
               method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel,
+              mods = ~indepvar2+year+published+elecsys2+method,
               test = "knha",
@@
              "Elecsys: Non-Majoritarian",
-             "Method: Panel",
-             "AggLevel: States"),
+             "Method: Panel"),
   Estimate = mod[["beta"]],
@@
 5. In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
-6. When passing from `Local` to `State` or `Country` levels, it decreases the detected effect size.
+6. When passing from `Country` to `Cross-Country`, it has no effect on the estimated coefficients.
 
@@
               method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method+agglevel,
+              mods = ~ indepvar2+year+published+elecsys2+method,
               test = "knha",
@@
           "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "AggLevel: States"),
+          "Method: Panel"),
   Estimate = mod[["beta"]],
@@
 5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
-6. Passing from `Local` to `State` or `World` levels decreases the detected effect size.
 
@@
               method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+agglevel,
+              mods = ~indepvar2+year+published+elecsys2+method,
               test = "knha",
             subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear)
+            slab = dat$authoryear,
+            control=list(maxiter=1000))
 
@@
           "Method: Panel",
-          "Method: IV",
-          "AggLevel: States"),
+          "Method: IV"),
   Estimate = mod[["beta"]],
@@
 4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
-5. When passing from `Local` to `State` level, the detected effects decrease.
 
@@
           "Method: Panel",
-          "Method: IV" ,
-          "AggLevel: States"),
+          "Method: IV"),
   Estimate = mod[["beta"]],
@@
            "Published: No",
-           "Method: Panel",
-           "AggLevel: States"),
+           "Method: Panel"),
   Estimate = mod[["beta"]],
@@
           "Published: No",
-          "Method: Panel",
-          "AggLevel: States"),
+          "Method: Panel"),
   Estimate = mod[["beta"]],
@@
           "Method: Panel",
-          "Method: RDD",
-          "AggLevel: States"),
+          "Method: RDD"),
   Estimate = mod[["beta"]],
@@
           "Method: IV",
-          "Method: RDD",
-          "AggLevel: States"))
+          "Method: RDD"))
 
@@
          order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
+         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
   filter(` ` != "Method: RDD") %>%
@@
          order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order),
-         order = ifelse(` ` == "AggLevel: States", 10, order)) %>%
+         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
   arrange(order) %>%
@@
               method = "REML",
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method+agglevel,
+              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
               test = "knha")

### 2020-06-19 dataset/datasetBuilding.R

@@ -1,11 +1,8 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
-## Authors: Alptekin, Freire, Mignozzetti and Roman             ##
-## Last Modified: May 20, 2020                                  ##
+## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
+## Last Modified: Jun 19, 2020                                  ##
 ##################################################################
-
-## Starting
-set.seed(732578) # From random.org
 
 # Needed packages
 pkgs <- c('tidyverse')
@@ -3632,6 +3629,8 @@ dat$location2 <- factor(as.character(dat$location2),
                         levels = c("Country", "World"))
 dat$agglevel <- factor(as.character(dat$agglevel), 
                        levels = c("Local", "States", "Countries"))
+dat$agglevel2 <- dat$agglevel
+levels(dat$agglevel2) = c("Country", "Country", "Cross-Country")
 fulldat <- dat
 dat <- dat %>%
   filter(usemeta == 1)

### 2020-06-21 appendix/appendix.Rmd
add table 3 to appendix, add manuscript

@@
 We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses.
-We set no restriction to unpublished articles.
+To reduce the risk of publication bias, we set no restriction to unpublished articles.
 
@@
 
-The selection process was conducted by two authors in three phases.
+The selection process was conducted by two authors in three stages.
 In the first round, we excluded all titles that were obviously unrelated to our topic.
@@
 We consider this a preliminary step, since we were not able to eliminate a large number of entries.
-Thus, we read all abstracts.
+Then, we read all abstracts.
 We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper.
@@
 
+## Study Sample
+
+A table with the 26 selected articles is available below.
+It includes information on the article author, the journal in which the paper was published, the publication year, the country of analysis, the level of data aggregation, and whether the electoral system is majoritarian or not.
+For unpublished papers, we included the year the paper was made available online.
+
+\vspace{.5cm}
+
+\footnotesize
+\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}
+   >{\raggedright\arraybackslash}p{4.2cm}
+   >{\centering\arraybackslash}p{1.3cm}
+   >{\centering\arraybackslash}p{1cm}
+   >{\centering\arraybackslash}p{1cm}
+   >{\centering\arraybackslash}p{1.4cm}
+   >{\centering\arraybackslash}p{2.5cm}}
+\caption{Papers included in the meta-analysis, listed alphabetically by last name}\\
+\toprule
+\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Level & \raggedleft Electoral System
+\tabularnewline
+\midrule
+\endhead
+R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & Municipal & M\\
+R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & Municipal & M\\
+T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & State & NM\\
+\begin{tabular}[t]{@{}l@{}}T.
+Bjedov,\\ S.
+Lapointe \& \\T.
+Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Canton & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Country & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}J.
+Drew \& \\ B.
+Dollery\end{tabular} & The Price of Democracy?
+Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & State & NM\\
+\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}N.
+Fiorino \& \\ R.
+Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & Region & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & Municipal & NM\\
+\begin{tabular}[t]{@{}l@{}}A.
+Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Municipal & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & District & M\\
+\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & District & NM\\
+\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & State & NM\\
+\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & Municipal & M\\
+\begin{tabular}[t]{@{}l@{}}B.
+Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & Country & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}B.
+Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Country & NM\\
+\begin{tabular}[t]{@{}l@{}}P.
+Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government?
+Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & Municipal & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & State & M\\
+\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & Country & NM\\
+\begin{tabular}[t]{@{}l@{}}C.
+Schaltegger \& \\ L.
+Feld\end{tabular} & Do Large Cabinets Favor Large Governments?
+Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Canton & NM\\
+\begin{tabular}[t]{@{}l@{}}E.
+Stein,\\ E.
+Talvi \& \\ A.
+Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub.
+& 1998 & Multiple (26) & Country & NM\\ [1ex]
+\bottomrule
+\label{tab:papers}
+\begin{minipage}{\textwidth}
+\renewcommand{\footnoterule}{}
+\vspace{-0.5cm}
+\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
+Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
+JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
+APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
+UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
+Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
+Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
+M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
+Country codes follow the ISO 3166-1 alpha-3 international standard.}
+\end{minipage}
+\end{longtable}
+
+\normalsize
+
 # Meta-Analysis Dataset
 
-The meta-analytic data is comprised of two datasets.
+Our meta-analytic data is comprised of two datasets.
 The first dataset has the main coefficients reported in the studies.
@@
 
-In this section, we show the descriptive statistics for our meta-analytic sample.
+In this section, we show the descriptive statistics for our study sample.
 We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.
@@
 
-\newpage
-
 ```{r, warning=F,message=F, cache=TRUE}
@@
 
-\newpage
-
 # Meta-Analysis
@@
 
-In general terms, there are two main ways to conduct a meta-analysis, using fixed effects or random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+In general terms, there are two main ways to conduct a meta-analysis, either using fixed effects or random effects models.
+The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true, unknown effect.
+The random effects model, on the other hand, assumes that there is a distribution of true effects, one which varies based on sample and tests characteristics.
 
 In this paper, we use the random effects model.
-The empirical papers testing the _law of 1/n_ are very diverse.
+We do so because the empirical papers testing the _law of 1/n_ are very diverse.
 We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
@@
 First, they make our estimates very disperse.
-All but one of our heterogeneity tests are significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
+All but one of our heterogeneity tests are statistically significant.
+When the sample sizes were large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
 Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
@@
 Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-
-\newpage
 
@@
 
-\newpage
-
 ## Log Lower House Size and Expenditure per Capita
@@
 
-\newpage
-
 ## Log of Lower House Size and Log of Expenditure Per Capita
@@
 
-\newpage
-
 ## Log of Upper House Size and Log of Expenditure Per Capita
@@
 
-\newpage
-
 ## Upper House Size and Expenditure as Percentage of GDP
@@
 
-\newpage
-
 # Meta-Analysis (All Coefficients)
@@
 
-\newpage
-
 ## Log of Lower House Size and Expenditure Per Capita
@@
 
-\newpage
-
 ## Lower House Size and Log of Expenditure Per Capita
@@
 
-\newpage
-
 ## Upper House Size and Log of Expenditure Per Capita
@@
 
-\newpage
-
 ## Log of Lower House Size and Expenditure as Percentage of GDP

### 2020-06-21 manuscript/article.tex
add table 3 to appendix, add manuscript

\documentclass[a4paper,12pt]{article}
\usepackage{anysize}
\usepackage[T1]{fontenc}
\usepackage[stable]{footmisc}
\usepackage{setspace}
\usepackage{lmodern}
\usepackage{libertine}
\usepackage[libertine]{newtxmath}
\usepackage[scale=0.825]{FiraMono}
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
\usepackage{mathtools}
\usepackage[authoryear]{natbib}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\usepackage{babelbib}
\usepackage{graphicx}
\usepackage{booktabs, makecell, longtable}
\usepackage{dcolumn}
\usepackage{float}
\usepackage[caption = false]{subfig}
\floatplacement{figure}{H}
\usepackage{caption}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{pdflscape}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
\usepackage{ifthen}
\usepackage{graphicx}
\usepackage{markdown}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\setcitestyle{aysep={}}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
	 \NAT@nmfmt{\NAT@nm}%
	 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
   {\@citeb\@extra@b@citeb}%
	 \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\usepackage{hyperref}

\hypersetup{
	breaklinks=true,
	linkcolor=Mahogany,
	citecolor=Mahogany,
	urlcolor=darkblue,
	colorlinks=true}

\doublespacing

\title{The Effect of Legislature Size on Public Spending:\\ A Meta-Analysis\thanks{The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance. Replication materials are available at \url{https://github.com/danilofreire/distributive-politics-meta-analysis}. We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1) and from the FGV Applied Research Network.}}

\vspace{2cm}

\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}. Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{catarinamroman@gmail.com}.}}

\vspace{2cm}
\date{\today}
\begin{document}
\maketitle

\begin{abstract}
\noindent In a seminal article, \citet{weingast1981political} argue that there
is a positive relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of $1/n$'' and
has been widely cited by scholars in political science and public
administration.  However, recent studies have questioned the validity of the
theory. In this paper, we estimate the first meta-analysis of the relationship
between the number of legislators and public spending. Based on a sample of 26
empirical studies, we find little effect of legislature size on government
budgets. The available evidence suggests that, if such an effect exists, it is
driven by an increase in the upper chamber, but there is considerable
heterogeneity in the results. Our meta-regressions also indicate that study
coefficients vary significantly according to modelling specifications, such as
estimation method or variable selection.

\vspace{.4cm}
\noindent \textbf{Keywords:} distributive politics; government budget; law of
$1/n$; legislature size; meta-analysis; public spending

\noindent \textbf{JEL Codes:} H21; H23; H50; H61
\end{abstract}

\newpage

\section{Introduction}
\label{sec:intro}

Over the past decades, a large literature has examined the relationship between
legislature size and public expenditure. \citet{weingast1981political} provided
the general framework to analyse distributive politics. The authors argue that
the larger the number of legislative districts ($n$), the smaller the share of
tax burden each one will bear ($1/n$), thus legislators have an incentive to
overspend in their districts and transfer the costs to the entire polity.
However, recent studies have questioned the validity of the ``law of $1/n$'', as
the theory is currently known. For instance, spending limits, strong executives,
and bicameralism may reduce the inefficiency of pork barrel projects
\citep{bradbury2009spatially,chen_malhotra_2007,primo2006stop}.  Moreover,
\citet{primo2008distributive} affirm that, due to spatial spillovers, a
collection of small districts can supply public goods more efficiently than the
central government. The authors conclude that a ``reverse law of $1/n$'' may
hold, wherein a higher number of legislators in small constituencies decrease
the overall public spending.

Our survey of the scholarship confirms this continuum of positive,
insignificant, and negative results. Out of the 36 coefficients included in our
selected articles, 42\% of them are positive and statistically significant, 22\%
are positive and statistically insignificant, 17\% are negative and
statistically insignificant, and 19\% are negative and statistically
significant. Given this diversity of empirical findings, a systematic review of
the existing evidence may help us reach a meaningful conclusion about the effect
of legislature size on public spending. Meta-analysis is the most appropriate
method for this task. Meta-analysis combines the outcomes of multiple studies
into a single estimation and allows scholars to draw robust conclusions from the
aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
identify potential sources of study heterogeneity, enabling researchers to
assess threats to external validity and direct future efforts into more
promising areas of academic inquiry \citep{doucouliagos2008democracy}.

In this paper, we conduct the first meta-analysis that tests the generality of
the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
to analyse the impact of legislature size over government spending. We run two
sets of models: the first group uses only the main estimates of each paper (36),
while the second set includes all coefficients reported in our sample
(126).\footnote{Although there are 26 papers in our review, we include 36
coefficients in the restricted sample. This is because 10 articles report
separate estimates for the impact of lower and upper house size on government
expenditures. In the full model, we added every outcome reported in the
paper, regardless of whether the coefficient comes from the main tables or
from robustness checks conducted by the original authors. We discuss our
sampling process in the Methods section of this paper and in the Supplementary
Material.} Our independent variables consist of three measures, namely the size
of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
members in the upper chamber ($k$). We evaluate their effect upon public
expenditure per capita, the natural logarithm of public expenditure per capita,
and government expenditure as a percentage of GDP. We then estimate if the
results vary according to four potential sources of effect heterogeneity.

Aggregate results show that council size has no significant impact on public
spending. Both the meta-analyses and the meta-regressions indicate that we
cannot generalise either the ``law of $1/n$'' or the ``reverse law of $1/n$''.
We find stronger evidence in favour of a positive impact of upper house size on
public budgets, yet the findings are not consistent in all of our estimations.
Our meta-regressions suggest that our study sample has a high level of
heterogeneity, and effects may differ substantially according to research design
specifications. In summary, our results point out that if legislature size
affects government budgets, they do so under specific conditions and are
mediated by domestic factors.

\section{Methods}

We collected the study sample using three criteria. First, the study should cite
\citet{weingast1981political} as their work is foundational to the distributive
politics literature. Second, the study had to use quantitative methods to
estimate the relationship between our variables of interest.\footnote{As
meta-analysis requires a single estimate per observation, we excluded articles
that use interaction terms or quadratic specifications of our independent
variables.} Third, the study should be written in the English language. We
conducted a primary search using Scopus, Microsoft Academic, and Google Scholar,
three large academic databases.\footnote{See the Supplementary Material for code.}

After applying our exclusion criteria, the search produced a dataset of 26
studies as of the 21\textsuperscript{st} of November, 2019. Table
\ref{tab:papers} contains the full list of articles from which we drew data. A
PRISMA\footnote{The Preferred Reporting Items for Systematic Reviews and
  Meta-Analyses (PRISMA) statement provides a checklist designed to improve the
quality and transparency of study selection processes in meta-analyses. For more
information on the PRISMA framework, see \citet{liberati2009prisma}.} flow
diagram showing the number of resulting papers after each review step is
available in the Supplementary Material.

\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}
   >{\raggedright\arraybackslash}p{4.2cm}
   >{\centering\arraybackslash}p{1.3cm}
   >{\centering\arraybackslash}p{1cm}
   >{\centering\arraybackslash}p{1cm}
   >{\centering\arraybackslash}p{1.4cm}
   >{\centering\arraybackslash}p{2.5cm}}
\caption{Papers included in the meta-analysis, listed alphabetically by last name}\\
\toprule
\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Level & \raggedleft Electoral System
\tabularnewline
\midrule
\endhead
R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & Municipal & M\\
R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & Municipal & M\\
T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & State & NM\\
\begin{tabular}[t]{@{}l@{}}T. Bjedov,\\ S. Lapointe \& \\T. Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Canton & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}J. Drew \& \\ B. Dollery\end{tabular} & The Price of Democracy? Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & State & NM\\
\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & Region & NM\\
\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & Municipal & NM\\
\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Municipal & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & District & M\\
\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & District & NM\\
\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & State & NM\\
\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & Municipal & M\\
\begin{tabular}[t]{@{}l@{}}B. Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}B. Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}P. Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government? Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & Municipal & NM\\
\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & State & M\\
\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & Country & NM\\
\begin{tabular}[t]{@{}l@{}}C. Schaltegger \& \\ L. Feld\end{tabular} & Do Large Cabinets Favor Large Governments? Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Canton & NM\\
\begin{tabular}[t]{@{}l@{}}E. Stein,\\ E. Talvi \& \\ A. Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub. & 1998 & Multiple (26) & Country & NM\\ [1ex]
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
Country codes follow the ISO 3166-1 alpha-3 international standard.}
\end{minipage}
\end{longtable}

\normalsize

Most studies focus on the United States (12), but our sample also contains
papers on Australia (1), Brazil (1), Germany (2), Indonesia (1), Italy (1), and
Switzerland (2). Five articles use cross-national data and analyse from 2 to 110
countries. We also observe that although the ``law of $1/n$'' was first
formulated in 1981, the empirical assessment of the theory only started a few
years later, as dates of publishing range from 1998 to 2019.

Regarding the dependent variables included in the sample, 13 studies employ
public expenditure per capita, 7 papers use its natural logarithm, and 8 of them
analyse the impact of legislature size on public expenditures as a percentage of
GDP. This indicates that the area has refined the original formulation of $1/n$
suggested by \citet{weingast1981political} and tested the impact of larger
legislatures on different measures of government spending. Our independent
variables of interest are $n$, lower chamber size (21), ($\log(n)$), the natural
logarithm of lower chamber size (6), and $k$, which represents upper chamber
size (9).

We also coded four moderators that frequently appear in the literature and may
help us understand the heterogeneity in the reported results. We included them
in our meta-regressions alongside an indicator for the type of independent
variable used in the original study ($n$, log($n$), or $k$). The additional
moderators are: 1) publication year; 2) paper publication in an academic
journal; 3) electoral system; 4) estimation method. Publication years have a
mean of 2009.6, and a standard deviation of 6.5. Twenty-two papers had been
published and 4 remained unpublished when we finished the data collection. In
our sample, 13 articles focus on majoritarian systems and 15 on mixed or
proportional representation systems.\footnote{Note that this moderator is
important for our estimations both theoretically and empirically. This because
\citet{weingast1981political} formulated their theory under the assumption that
the electoral system is majoritarian.} Thirteen studies use OLS, 17 use panel
data, 3 use instrumental variable estimation, and 3 employ regression
discontinuity designs. Table \ref{tab:descriptive} shows the descriptive
statistics of the moderator variables.

% Adicionar primeira coluna com estatística descritiva *dos papers* para
% completar as dos coeficientes.

\vspace{.5cm}

\begin{table}[htpb]
 \caption{Descriptive Statistics of Moderators}
 \centering
 \begin{tabular}{lccc}
    \hline  \hline
    & Main Coefficients & Other Coefficients &   All Coefficients    \\ 
    &        N=36        &       N=92        &    N=128    \\ 
    \hline     
    Independent Variables: &             &                    &                  \\
$\qquad$K &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
$\qquad$N &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
$\qquad$logN &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
Year &     2009 (6.50)    &    2008 (5.75)   & 2008 (5.98) \\ 
Published work: &             &                    &                  \\ 
$\qquad$Yes &     30 (83.3\%)     &    74 (80.4\%)    & 104 (81.2\%) \\ 
$\qquad$No &    6 (16.7\%)       &     18 (19.6\%)   & 24 (18.8\%)  \\ 
Electoral system: &             &                    &                  \\ 
$\qquad$Majoritarian &     18 (50.0\%)      &    40 (43.5\%)   & 58 (45.3\%)  \\ 
$\qquad$Non-Majoritarian &    18 (50.0\%)       &    52 (56.5\%)   & 70 (54.7\%)  \\ 
Estimation method: &             &                    &                  \\ 
$\qquad$OLS &     13 (36.1\%)     &   43 (46.7\%)     & 56 (43.8\%)  \\ 
$\qquad$PANEL &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
$\qquad$IV &     3 (8.33\%)      &     3 (3.26\%)    &  6 (4.69\%)  \\ 
$\qquad$RDD &     3 (8.33\%)      &     6 (6.52\%)    &  9 (7.03\%)  \\ 
Sampling Aggregation Level: &             &                    &                  \\ 
$\qquad$Local &     7 (19.4\%)      &     16 (17.4\%)   & 23 (18.0\%)  \\ 
$\qquad$States &    21 (58.3\%)      &    49 (53.3\%)    & 70 (54.7\%)  \\ 
$\qquad$Countries &     8 (22.2\%)      &     7 (29.3\%)   & 35 (27.3\%)  \\ 
\hline  
\end{tabular}
\label{tab:descriptive}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} The values for the variable \textit{Year} indicate the mean and the standard deviation, respectively.}
\end{minipage}    
\end{table}

Since most selected articles have more than one effect size, the observations
in our dataset are not independent. To reduce the impact of multicollinearity,
we estimate the models using two sets of study coefficients. The first group
includes only the most rigorous model from each paper, that is, those estimated
with the largest $n$, most control variables, and fixed effects if the authors
added them. If the article employed a regression discontinuity design, we chose
the coefficient from the optimal bandwidth or from the intermediate one. This
sample encompasses 36 estimates, as 10 articles analysed two dependent or
independent variables of interest \citep{baqir1999districts, bjedov2014impact,
bradbury2001legislative, chen_malhotra_2007, crowley2019law,
lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
ricciuti2003trading}. Our second sample, in contrast, contains all the 126 effect
sizes reported in the 26 papers. Here we focus on the results for our restricted
sample as we consider them more robust, but the findings are very similar when
we use the extended set. We discuss eventual differences in the next section.
Please refer to the Supplementary Material for further information about our
sampling process and for the complete results.

\section{Results}

\subsection{Binomial Z-Tests}
\label{sub:binomial}

The ``law of $1/n$'' states that more legislators increase government expenditure.
Here we employ three methods to assess the empirical validity of that
relationship. First, we run a binomial one-proportion z-test to determine
whether the study coefficients have a positive or negative sign. Then, we fit 7
random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
language \citep{rstats2019}. We estimate the true effect size variance
($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
considers the most precise for continuous dependent variables
\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
possible sources of result heterogeneity. To recapitulate, our independent
variables of interest are lower chamber size ($n$), the natural logarithm of
lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
variables are public expenditure per capita, the natural logarithm of public
expenditure per capita, and government expenditure as a percentage of GDP. Since
the outcomes have different scales, we treat them separately in our models.

The binomial z-test evaluates whether the coefficient of our independent
variables are positive or negative. The null hypothesis here states that the
sign of the coefficient is equally likely to be positive or negative. We start
with $n$, lower house size. Our results indicate that there is no correlation
between the number of legislators in the lower house and public expenditure 
(successes = 10, trials = 21, $p_{success} = 0.476$, 95\% CI = [0.257; 0.702],
$p$-value = 1). Note that the ``law of $1/n$'' suggests that there is a positive
association between both. The binomial test for log($n$) also shows a
non-statistically significant result (successes = 5, trials = 6, $p_{success} =
0.833$, 95\% CI = [0.359; 0.996], $p$-value = 0.219). In contrast, we find a
positive result for the number of legislators in the upper house ($k$), which is
in line with the mainstream literature (successes = 8, trials = 9, $p_{success}
= 0.889$, 95\% CI = [0.518; 0.997], $p$-value = 0.039).

\subsection{Meta-Analysis}
\label{sub:Meta-Analysis}

We then proceed to the meta-analysis. We matched the house size variables with
our measures of government spending and created a theoretical $3 \times 3$
matrix. Out of the 9 possible variable combinations, we found only 7 in
the article pool. Our sample includes no papers that analyse the relationships
between log($n$), and public expenditure per capita and between $k$ and the
logarithm of public expenditure per capita.

Figure \ref{fig:plots} shows the forest plots for our restricted sample, the one
which includes only the main 36 coefficients for the 26 selected papers. On the
left side of the plots are the name of the study authors and the paper
publication year. For unpublished studies, we included the first year the paper
was available online. The bars in the middle show the reported effect sizes and
the vertical lines indicate their average, weighted by standard errors. The length
of the lines represent the precision of the estimates. The red line at the
bottom of the figures displays the aggregate coefficients plus their respective
confidence intervals.

The first column of the graph reports the results for $n$, lower chamber size.
In the first model, which correlates $n$ and expenditure per capita, we find a
standardised mean difference (SMD) of $-0.070$ and a standard error of $0.273$
(studies = 12, 95\% CI = [-0.671; 0.531], $p$-value = 0.803, prediction interval
= [-1.55; 1.41]). Therefore, we cannot reject the null hypothesis that the
effect size is zero. The $I^2$ statistic, which quantifies the degree of
heterogeneity among studies, is equal to 94.7\%. $I^2$ values above 75\%
indicate very high study heterogeneity \citep{higgins2019cochrane}.

We see similar results when we compare $n$ with log expenditure per capita. In
this model, the average effect size is -0.07 and the standard deviation is
0.059 (studies = 4, 95\% CI = [-0.256; 0.119], $p$-value = 0.328, prediction
interval = [-0.618; 0.481]; $I^2$ = 92.5\%). The coefficient is 
statistically indistinguishable from zero.

In our restricted sample, larger lower house size also does not increase
government spending as a percentage of GDP (studies = 5, SMD = -0.008, SE =
0.013, 95\% CI = [-0.045; 0.0285], $p$-value = 0.567, prediction interval =
[-0.105; 0.089], $I^2$ = 87.1\%). We find a positive effect in our extended
sample and the coefficient is statistically significant at the 10\% level
(coefficients = 21, SMD = 0.008, SE = 0.004, 95\% CI = [-0.000; 0.016], $p$-value =
0.058, prediction interval = [-0.026; 0.042], $I^2$ = 98.5\%). The 
result supports the ``law of 1/$n$'', but the evidence is moderate
as the prediction interval include zero.

\begin{landscape}
\begin{figure}[p]
\begin{center}
\caption{Forest Plots for the Relationship between Legislature Size and Government Spending (Reduced Sample)}
\vspace{.3cm}
\includegraphics[width=25cm,height=17cm]{meta-analysis.pdf}
\label{fig:plots}
\end{center}
\end{figure}
\end{landscape}

Next, we present the meta-analyses using log($n$), the logarithm of lower house
size, as the main explanatory variable. We start with the relationship between
log($n$) and the logarithm of expenditure per capita. The result is positive and
statistically significant at 10\%, but the prediction interval encompasses zero
(studies = 3, SMD = 0.184, SE = 0.06, 95\% CI = [-0.0738; 0.4425], $p$-value =
0.0916, prediction interval = [-1.258; 1.627], $I^2$ = 85.9\%). Although the
coefficient has the predicted sign, we should interpret the finding with caution
as it does not replicate in our sample of 126 effect sizes.

Our model that correlates log($n$) with public expenditures as a percentage of
GDP fails to reach conventional levels of statistical significance (studies =
3, SMD = 0.0203, SE = 1.677, 95\% CI = [-7.196; 7.237], $p$-value = 0.991,
prediction interval = [-36.206; 36.246], $I^2$ = 96.1\%). The extended sample
also gives us a null result.

The third set of models uses $k$, upper house size, as the main independent
variable. We find a positive correlation between $k$ and expenditure per capita
and the coefficient is significant at a 10\% level (studies = 6, SMD = 10.613, SE
= 5.148, 95\% CI = [-2.621; 23.848], $p$-value = 0.094, prediction interval =
[-21.130; 42.357], $I^2$ = 79.4\%). But as with the other models, the prediction
interval again includes zero. When we run the same analysis in the extended
sample, we also see a significant coefficient yet a prediction interval that
contains zero (coefficients = 24, SMD = 7.216, SE = 1.342, 95\% CI = [4.440; 9.992],
$p$-value $<$ 0.0001, prediction interval = [-1.222; 15.654], $I^2$ = 77.7\%).

Our last estimation analyses the relationship between $k$ and government
spending as a percentage of GDP. The coefficient is not statistically
significant, indicating a null effect (studies = 3, SMD = -0.003, SE =, 95\% CI
= [-0.079; 0.074], $p$-value = 0.891, prediction interval = [-0.428; 0.423],
$I^2$ = 85.8\%). The result is very similar in the extended sample.

In a nutshell, we find only weak evidence in favour of the ``law of $1/n$''.
While some models do show a positive and statistically significant result, none
of the prediction intervals are totally positive or negative. The studies also
have considerable heterogeneity, what indicates that the original coefficients
do not point consistently towards the same direction.

\subsection{Meta-Regressions}
\label{sub:regressions}

In this section, we run a series of meta-regressions with 5 covariates that may
account for differences across the selected papers. The first variable indicates
whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
The second variable shows the study publication year, which we included to
capture temporal variation in the study coefficients. We also add a dummy
variable to assess whether published articles report effect sizes that are
higher or lower than those from working papers. The fourth variable measures
whether studies focusing on non-majoritarian electoral systems report
coefficients that are smaller or larger than those from majoritarian countries.
Our last covariate is a categorical variable indicating the statistical
procedure used in the original models (fixed effects, instrumental variables,
OLS, or regression discontinuity design).

Table \ref{tab:regressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper. To reduce the risk of
false positives in our analyses, we use permutation tests to calculate
significance levels for the meta-regressions \citep{higgins2004controlling}.

\vspace{.5cm}

\begin{table}[htpb]
\footnotesize
\caption{Meta Regression Results}
\label{tab:regressions}
\centering
\begin{tabular}{lcccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Intercept & -104.07 & -296.907 & 8.959 & -1.574 & 2.669 & -10.11 \\
 & (318.93) & (166.687)$\dagger$ & (47.644) & (15.883) & (2.04) & (5.8586)$\dagger$\\
%
Independent Variable: $N$ & -2.924 & -5.447 & 0.164 & -0.009 & -0.0094 & -0.0015\\
 & (2.093) & (0.969)*** & (0.326) & (0.126) & (0.006) & (0.005)\\
%
Independent Variable: log($N$) &  &  &  &  & -0.011 & 0.038\\
 &  &  &  &  & (0.019) & (0.0195)$\dagger$\\
%
Year & 0.052 & 0.15 & -0.004 & 0.001 & -0.000 & 0.006\\
 & (0.159) & (0.083)$\dagger$ & (0.024) & (0.008) & (0.001) & (0.003)*\\
%
Published: No &  &  & -0.152 & -0.083 & 0.0633 & 0.113 \\
 &  &  & (0.19) & (0.073) & (0.016)* & (0.026)***\\
%
Non-Majoritarian (PR \& Mixed) & 0.346 & 1.024 & &  & -2.0556 & -2.163\\
 & (1.553) & (0.77) & &  & (0.3260)** & (0.163)***\\
%
Method: Panel & 1.457 & -0.142 & 0.258 & -0.244 & 0.0557 & 0.126\\
 & (2.238) & (0.814) & (0.189) & (0.0147)* & (0.0071)* & (0.032)***\\
%
Method: IV & 1.494 & 0.191 &  &  &  & \\
 & (2.668) & (0.822) &  &  &  & \\
%
Method: RDD &  &  &  &-0.298&  & \\
 &  &  &  & (0.066)*** &  & \\
% 
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively. Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$. Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
\end{minipage}
\end{table}

\newpage

The first two models show the results for public expenditure per capita. In both
the restricted and the extended samples, we find that models that use $n$ as an
independent variable tend to detect significantly smaller effects when compared
to $k$. This suggests that an additional member in the lower house has a smaller
impact on public spending than a member in the upper house. Moreover, the
results for the extended sample point out that recent studies find larger
effects than older ones, and that changing the electoral rules from majoritarian
to non-majoritarian increases the effects of legislature size on per capita
expenditure.

The third and fourth columns use the logarithm of expenditure per capita as the
dependent variable. No covariate is statistically significant in our smaller
sample, but two moderators are negatively associated with the outcome in our
larger study pool. They both refer to estimation methods. Studies that employ
panel/fixed effects or regression discontinuity designs (RDDs) have lower
coefficients for log expenditure per capita if we take OLS as the reference
category.

Several variables are statistically significant in the last set of
meta-regressions. The dependent variable is public expenditures as a percentage
of GDP. In both restricted and extended samples we find that unpublished papers
tend to have higher coefficients than published papers. In contrast with our
previous results, we also see that passing from OLS to panel/fixed effects and
from majoritarian to non-majoritarian electoral systems increase the detected
coefficients. We also see that year has a positive effect on the outcome: the
newer the publication, the higher the detected coefficient. However, the
result is statistically significant only in the extended sample. Finally,
studies with $n$ as an independent variable have lower coefficients than those
that analyse $k$, what is consistent with our previous meta-regressions.

Overall, our results suggest that study coefficients are highly sensitive to
research design choices. The same statistical methods or study samples may
produce different outcomes depending on the response variables scholars decide
to analyse. Moreover, we find evidence that results vary considerably if the
study employs different measures of legislature size. The impact of factors such
as the electoral system or year of publication also appear to be conditional on
the selected model.

\section{Discussion}
\label{sec:discussion}

In this article, we assess the empirical validity of the ``law of $1/n$''. Based
on a sample of 26 recent publications on the topic, our meta-analyses show that
there is little evidence that an increase in the number of legislators has a
significant effect on public expenditures. If such effect exists, it is likely
driven by an increase in $k$, the size of the upper legislature, as suggested by
several studies in the literature \citep[e.g.,][]{baqir2002districting, 
bradbury2001legislative, bradbury2003local, chen_malhotra_2007,
gilligan2001fiscal, primo2006stop}. We find no robust evidence for the ``reverse
law of $1/n$'', which posits that larger legislatures lead to lower government
spending. One possible explanation is that the two logics are balancing each
other, thus leading us to a null impact of legislature size on public
expenditure.

The meta-regressions indicate that study characteristics have a large influence
on reported results. It is unclear whether factors such as the electoral system
or the level of data aggregation, both believed to moderate the relationship
between legislature size and public expenditure \citep{primo2008distributive,
baqir2002districting, bradbury2003local}, have a substantial impact on the
estimates. We find conflicting evidence for the former and no support for the
latter. Moreover, different statistical techniques produce distinctive results,
which authors should bear in mind.

Our analyses suggest three areas for further research. First, our study sample
did not include articles that evaluate the association between the log($n$) and
public expenditure per capita or between $k$ and log expenditure per capita.
New work on that area might clarify some of the inconsistencies we find
here. Second, despite the inclusion of several moderators in our models,
aggregate results still show considerable heterogeneity. That is, much of the
disparities among studies are yet to be explained. Domestic factors such as
party dynamics or gerrymandering \citep{lee2015supermajority,
mukherjee2003politicalparties, gilligan2006public} may prove useful in this
regard. Finally, we highlight the need for more evidence in favour or against
the ``law of $1/n$'' to inform general public policies. The available empirical
evidence points out that contextual variables may either amplify or reduce the
impact of larger legislatures on government budgets. They should be taken into
account if policy-makers want to reach an optimal balance between sound fiscal
policy and the demands for increased political representation.

\newpage
\bibliography{references.bib}
\bibliographystyle{apalike}

\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures}

\end{document}

### 2020-06-21 manuscript/article.tex
add table 3

@@
 \midrule
-Intercept & -104.07 & -296.907 & 8.959 & -1.574 & 2.669 & -10.11 \\
- & (318.93) & (166.687)$\dagger$ & (47.644) & (15.883) & (2.04) & (5.8586)$\dagger$\\
+Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
+          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
 %
-Independent Variable: $N$ & -2.924 & -5.447 & 0.164 & -0.009 & -0.0094 & -0.0015\\
- & (2.093) & (0.969)*** & (0.326) & (0.126) & (0.006) & (0.005)\\
+Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
+                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
 %
-Independent Variable: log($N$) &  &  &  &  & -0.011 & 0.038\\
- &  &  &  &  & (0.019) & (0.0195)$\dagger$\\
+Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
+                               &  &  &  &  & (0.001) & (0.014)\\
 %
-Year & 0.052 & 0.15 & -0.004 & 0.001 & -0.000 & 0.006\\
- & (0.159) & (0.083)$\dagger$ & (0.024) & (0.008) & (0.001) & (0.003)*\\
+Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
+     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
 %
-Published: No &  &  & -0.152 & -0.083 & 0.0633 & 0.113 \\
- &  &  & (0.19) & (0.073) & (0.016)* & (0.026)***\\
+Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
+              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
 %
-Non-Majoritarian (PR \& Mixed) & 0.346 & 1.024 & &  & -2.0556 & -2.163\\
- & (1.553) & (0.77) & &  & (0.3260)** & (0.163)***\\
+Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
+                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
 %
-Method: Panel & 1.457 & -0.142 & 0.258 & -0.244 & 0.0557 & 0.126\\
- & (2.238) & (0.814) & (0.189) & (0.0147)* & (0.0071)* & (0.032)***\\
+Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
+              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
 %
-Method: IV & 1.494 & 0.191 &  &  &  & \\
- & (2.668) & (0.822) &  &  &  & \\
+Method: IV & 1.317 & 0.186 &  &  &  & \\
+           & (1.807) & (0.802) &  &  &  & \\
 %
-Method: RDD &  &  &  &-0.298&  & \\
- &  &  &  & (0.066)*** &  & \\
+Method: RDD &  &  &  &-0.285&  & \\
+            &  &  &  & (0.062)*** &  & \\
 % 
@@
 \footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively.
+We report the results from the permutation tests.
 Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$.
@@
 
-\newpage
+%% CONFERIR TODOS OS RESULTADOS
 
@@
 meta-regressions. The dependent variable is public expenditures as a percentage
-of GDP. In both restricted and extended samples we find that unpublished papers
-tend to have higher coefficients than published papers. In contrast with our
-previous results, we also see that passing from OLS to panel/fixed effects and
-from majoritarian to non-majoritarian electoral systems increase the detected
-coefficients. We also see that year has a positive effect on the outcome: the
-newer the publication, the higher the detected coefficient. However, the
-result is statistically significant only in the extended sample. Finally,
-studies with $n$ as an independent variable have lower coefficients than those
-that analyse $k$, what is consistent with our previous meta-regressions.
+of GDP. In our restricted sample, we see that studies with $n$ as an
+independent variable have lower coefficients than those that analyse $k$, what
+is consistent with our previous models. Both models also show that unpublished
+papers tend to have higher coefficients than published papers. Regarding the
+electoral systems, see that passing from majoritarian to non-majoritarian
+decrease overall levels of public spending. Finally, we find that models
+estimated with panel data have larger values than those modelled with OLS.
 

### 2020-06-22 manuscript/article.tex
version 0.1

@@
 
-\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}.
-Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, Department of International Relations, Getulio Vargas Foundation, Brazil, \url{catarinamroman@gmail.com}.}}
+\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}.
+Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, School of International Relations, Fundação Getulio Vargas, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \url{catarinamroman@gmail.com}.}}
 
@@
 \vspace{.4cm}
-\noindent \textbf{Keywords:} distributive politics; government budget; law of
-$1/n$; legislature size; meta-analysis; public spending
+\noindent \textbf{Keywords:} distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
 
@@
 \toprule
-\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Level & \raggedleft Electoral System
+\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
 \tabularnewline
@@
 \endhead
-R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & Municipal & M\\
-R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & Municipal & M\\
-T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & State & NM\\
+R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & OLS & M\\
+R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & OLS & M\\
+T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & IV & NM\\
 \begin{tabular}[t]{@{}l@{}}T.
@@
 Lapointe \& \\T.
-Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Canton & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Country & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & State & M\\
-\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & State & M\\
-\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & State & M\\
+Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & OLS & M\\
+\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & OLS & M\\
+\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & Panel & M\\
 \begin{tabular}[t]{@{}l@{}}J.
@@
 Dollery\end{tabular} & The Price of Democracy?
-Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & State & NM\\
-\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & State & M\\
-\begin{tabular}[t]{@{}l@{}}N.
-Fiorino \& \\ R.
-Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & Region & NM\\
-\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & Municipal & NM\\
-\begin{tabular}[t]{@{}l@{}}A.
-Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Municipal & M\\
-\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & State & M\\
-\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & District & M\\
-\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & District & NM\\
-\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & State & NM\\
-\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & Municipal & M\\
+Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & IV & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & OLS & NM\\
+\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & OLS & M\\
 \begin{tabular}[t]{@{}l@{}}B.
-Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & Country & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & State & M\\
+Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & OLS & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & IV & M\\
 \begin{tabular}[t]{@{}l@{}}B.
-Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Country & NM\\
+Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Panel & NM\\
 \begin{tabular}[t]{@{}l@{}}P.
 Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government?
-Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & Municipal & NM\\
-\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & State & M\\
-\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & Country & NM\\
+Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & OLS & NM\\
 \begin{tabular}[t]{@{}l@{}}C.
@@
 Feld\end{tabular} & Do Large Cabinets Favor Large Governments?
-Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Canton & NM\\
+Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Panel & NM\\
 \begin{tabular}[t]{@{}l@{}}E.
@@
 Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub.
-& 1998 & Multiple (26) & Country & NM\\ [1ex]
+& 1998 & Multiple (26) & OLS & NM\\ [1ex]
 \bottomrule
@@
 Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
-M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
+OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
 Country codes follow the ISO 3166-1 alpha-3 international standard.}
@@
 
-We also coded four moderators that frequently appear in the literature and may
-help us understand the heterogeneity in the reported results. We included them
-in our meta-regressions alongside an indicator for the type of independent
-variable used in the original study ($n$, log($n$), or $k$). The additional
-moderators are: 1) publication year; 2) paper publication in an academic
-journal; 3) electoral system; 4) estimation method. Publication years have a
-mean of 2009.6, and a standard deviation of 6.5. Twenty-two papers had been
-published and 4 remained unpublished when we finished the data collection. In
-our sample, 13 articles focus on majoritarian systems and 15 on mixed or
-proportional representation systems.\footnote{Note that this moderator is
-important for our estimations both theoretically and empirically. This because
-\citet{weingast1981political} formulated their theory under the assumption that
-the electoral system is majoritarian.} Thirteen studies use OLS, 17 use panel
-data, 3 use instrumental variable estimation, and 3 employ regression
-discontinuity designs. Table \ref{tab:descriptive} shows the descriptive
-statistics of the moderator variables.
-
-% Adicionar primeira coluna com estatística descritiva *dos papers* para
-% completar as dos coeficientes.
+We also coded four moderators that may help us understand the heterogeneity in
+the reported results. We included them in our meta-regressions alongside an
+indicator for the type of independent variable used in the original study ($n$,
+log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
+publication in an academic journal; 3) electoral system; 4) estimation method.
+Since the literature on the ``law of $1/n$'' is notably diverse, we were
+restricted to include only the moderators that either refer to important
+theoretical questions, such as the effect of the electoral system on public
+spending, or to essential characteristics of the publications themselves.
+Although more moderators exist in the literature (ie., data aggregation level),
+they do not appear as often as required for the meta-regressions. Table
+\ref{tab:descriptive} shows the descriptive statistics of the moderator
+variables.
 
@@
 Independent Variables: &             &                    &                  \\
-$\qquad$K &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
-$\qquad$N &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
-$\qquad$logN &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
+$\qquad$ $k$ &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
+$\qquad$ $n$ &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
+$\qquad$ log($n$) &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
 Year &     2009 (6.50)    &    2008 (5.75)   & 2008 (5.98) \\ 
@@
 $\qquad$OLS &     13 (36.1\%)     &   43 (46.7\%)     & 56 (43.8\%)  \\ 
-$\qquad$PANEL &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
+$\qquad$Panel &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
 $\qquad$IV &     3 (8.33\%)      &     3 (3.26\%)    &  6 (4.69\%)  \\ 
 $\qquad$RDD &     3 (8.33\%)      &     6 (6.52\%)    &  9 (7.03\%)  \\ 
-Sampling Aggregation Level: &             &                    &                  \\ 
-$\qquad$Local &     7 (19.4\%)      &     16 (17.4\%)   & 23 (18.0\%)  \\ 
-$\qquad$States &    21 (58.3\%)      &    49 (53.3\%)    & 70 (54.7\%)  \\ 
-$\qquad$Countries &     8 (22.2\%)      &     7 (29.3\%)   & 35 (27.3\%)  \\ 
 \hline  
@@
 Our last covariate is a categorical variable indicating the statistical
-procedure used in the original models (fixed effects, instrumental variables,
+procedure used in the original models (panel data, instrumental variables,
 OLS, or regression discontinuity design).
@@
 \midrule
-Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
-          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
-%
 Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
@@
 % 
+Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
+          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
 \bottomrule
@@
 \end{table}
-
-%% CONFERIR TODOS OS RESULTADOS
 

### 2020-09-28 manuscript/article.tex
first edits after review

@@
 Replication materials are available at \url{https://github.com/danilofreire/distributive-politics-meta-analysis}.
-We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1) and from the FGV Applied Research Network.}}
+We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1).}}
 
@@
 
-\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \url{huzeyfealptekin@gmail.com}.} \hspace{.5cm} Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912, \url{danilofreire@gmail.com}, \url{http://danilofreire.github.io}.
-Corresponding author.} \hspace{.5cm} Umberto Mignozzetti\thanks{Assistant Professor, School of International Relations, Fundação Getulio Vargas, Brazil, \url{umberto.mignozzetti@fgv.br}, \url{http://umbertomig.com}.} \hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \url{catarinamroman@gmail.com}.}}
+\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \href{mailto:huzeyfealptekin@gmail.com}{\texttt{huzeyfealptekin@gmail.com}}.}
+\hspace{.5cm} Danilo Freire\thanks{Independent Researcher, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{http://danilofreire.github.io}. Corresponding author.} 
+\hspace{.5cm} Umberto Mignozzetti\thanks{Visiting Assistant Professor, \href{mailto:umberto.mignozzetti@emory.edu}{\texttt{umberto.mignozzetti@emory.edu}}, \url{http://umbertomig.com}.} 
+\hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \href{mailto:catarinamroman@gmail.com}{\texttt{catarinamroman@gmail.com}}.}}
 
@@
 administration. However, recent studies have questioned the validity of the
-theory. In this paper, we estimate the first meta-analysis of the relationship
+theory. In this letter, we estimate the first meta-analysis of the relationship
 between the number of legislators and public spending. Based on a sample of 26
@@
 \vspace{.4cm}
-\noindent \textbf{Keywords:} distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
+\noindent \textbf{Keywords:} distributive politics; law of $1/n$; legislature
+size; meta-analysis; public spending
 
@@
 
-In this paper, we conduct the first meta-analysis that tests the generality of
+In this letter, we conduct the first meta-analysis that tests the generality of
 the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
@@
 separate estimates for the impact of lower and upper house size on government
-expenditures. In the full model, we added every outcome reported in the
-paper, regardless of whether the coefficient comes from the main tables or
+expenditures. In the full model, we add every outcome reported in the
+papers, regardless of whether the coefficient comes from the main tables or
 from robustness checks conducted by the original authors. We discuss our
@@
 heterogeneity, and effects may differ substantially according to research design
-specifications. In summary, our results point out that if legislature size
-affects government budgets, they do so under specific conditions and are
-mediated by domestic factors.
+specifications. We also find that recent studies, mainly those which employ
+regression discontinuity designs, are more likely to find a negative association
+between larger legislatures and public spending. In summary, our results point
+out that if legislature size affects government budgets, they do so under
+specific conditions and are mediated by domestic factors.
 
@@
 Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
-OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
-Country codes follow the ISO 3166-1 alpha-3 international standard.}
+OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
+data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
+NM$=$Non-majoritarian (mixed or proportional representation). Country codes
+follow the ISO 3166-1 alpha-3 international standard.}
 \end{minipage}
@@
 
+Our study sample reflects the development of the literature. Although the ``law
+of $1/n$'' was first formulated in 1981, the empirical assessment of the theory
+only started a few years later, as dates of publishing range from 1998 to 2019.
+
 Most studies focus on the United States (12), but our sample also contains
@@
 Switzerland (2). Five articles use cross-national data and analyse from 2 to 110
-countries. We also observe that although the ``law of $1/n$'' was first
-formulated in 1981, the empirical assessment of the theory only started a few
-years later, as dates of publishing range from 1998 to 2019.
+countries.
 

### 2020-10-31 manuscript/article.tex
emphasise causal designs

@@
 \begin{abstract}
+
 \noindent In a seminal article, \citet{weingast1981political} argue that there
@@
 expenditures. Their proposition is currently known as the ``law of $1/n$'' and
-has been widely cited by scholars in political science and public
-administration. However, recent studies have questioned the validity of the
-theory. In this letter, we estimate the first meta-analysis of the relationship
-between the number of legislators and public spending. Based on a sample of 26
-empirical studies, we find little effect of legislature size on government
-budgets. The available evidence suggests that, if such an effect exists, it is
-driven by an increase in the upper chamber, but there is considerable
-heterogeneity in the results. Our meta-regressions also indicate that study
-coefficients vary significantly according to modelling specifications, such as
-estimation method or variable selection.
+has been widely debated in political science and public administration.
+However, recent studies have questioned the validity of the theory. In this
+letter, we estimate the first meta-analysis of the relationship between the
+number of legislators and public spending. Based on a sample of \textbf{XX}
+articles, we find only mixed evidence for the effect of legislature size on
+government budgets. Yet the aggregate results mask important differences. While
+earlier, non-causal studies provide moderate support for the ``law of $1/n$'',
+recent papers using causal inference methods consistently find a negative
+relation between seats and spending, suggesting that previous results might
+have been driven by spurious correlations or omitted variable bias. The
+available evidence also indicates that XXXXXXXXXXXXXXXX
 
@@
 Aggregate results show that council size has no significant impact on public
-spending. Both the meta-analyses and the meta-regressions indicate that we
-cannot generalise either the ``law of $1/n$'' or the ``reverse law of $1/n$''.
-We find stronger evidence in favour of a positive impact of upper house size on
-public budgets, yet the findings are not consistent in all of our estimations.
-Our meta-regressions suggest that our study sample has a high level of
-heterogeneity, and effects may differ substantially according to research design
-specifications. We also find that recent studies, mainly those which employ
-regression discontinuity designs, are more likely to find a negative association
-between larger legislatures and public spending. In summary, our results point
-out that if legislature size affects government budgets, they do so under
-specific conditions and are mediated by domestic factors.
+spending. However, the meta-regressions suggest that our study sample has high
+levels of heterogeneity, and effects differ substantially according to research
+design specifications. Whereas earlier studies employing convention spending
+regressions often find a positive relation between legislature size and
+government budgets, recent studies that use new methods of causal inference,
+specially those with regression discontinuity designs, provide consistent
+evidence for a negative relation. This goes in contrast with the original
+theory and supports the existence of a ``reverse law of $1/n$''.
+\textbf{Moreover, ...}  In summary, our results point out that if legislature
+size affects government budgets, they do so under specific conditions and are
+mediated by domestic factors.
 

### 2020-11-17 manuscript/article.tex
text

@@
 letter, we estimate the first meta-analysis of the relationship between the
-number of legislators and public spending. Based on a sample of \textbf{XX}
+number of legislators and public spending. Based on a sample of \textbf{29}
 articles, we find only mixed evidence for the effect of legislature size on
@@
 In this letter, we conduct the first meta-analysis that tests the generality of
-the ``law of $1/n$''. We have selected 26 articles that use quantitative methods
+the ``law of $1/n$''. We have selected 29 articles that use quantitative methods
 to analyse the impact of legislature size over government spending. We run two
-sets of models: the first group uses only the main estimates of each paper (36),
+sets of models: the first group uses only the main estimates of each paper (42),
 while the second set includes all coefficients reported in our sample
-(126).\footnote{Although there are 26 papers in our review, we include 36
-coefficients in the restricted sample. This is because 10 articles report
+(142).\footnote{Although there are 29 papers in our review, we include 42
+coefficients in the restricted sample. This is because 13 articles report
 separate estimates for the impact of lower and upper house size on government

### 2020-11-19 manuscript/article.Rmd
add article in RMarkdown

--- 2020-11-17 manuscript/article.tex
@@
-\documentclass[a4paper,12pt]{article}
-\usepackage{anysize}
-\usepackage[T1]{fontenc}
-\usepackage[stable]{footmisc}
-\usepackage{setspace}
-\usepackage{lmodern}
-\usepackage{libertine}
-\usepackage[libertine]{newtxmath}
-\usepackage[scale=0.825]{FiraMono}
-\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm]{geometry}
-\usepackage{mathtools}
-\usepackage[authoryear]{natbib}
-\usepackage[UKenglish]{babel}
-\usepackage[UKenglish]{isodate}
-\usepackage{babelbib}
-\usepackage{graphicx}
-\usepackage{booktabs, makecell, longtable}
-\usepackage{dcolumn}
-\usepackage{float}
-\usepackage[caption = false]{subfig}
-\floatplacement{figure}{H}
-\usepackage{caption}
-\usepackage{rotating}
-\usepackage{pdflscape}
-\usepackage{pdflscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-\usepackage{ifthen}
-\usepackage{graphicx}
-\usepackage{markdown}
-\usepackage[usenames,dvipsnames]{xcolor}
-\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
-\usepackage{tikz}
-\usetikzlibrary{shapes.geometric, arrows}
-\setcitestyle{aysep={}}
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-	 \NAT@nmfmt{\NAT@nm}%
-	 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
-	 \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
-\patchcmd{\NAT@citex}
-  {\@citea\NAT@hyper@{%
-	 \NAT@nmfmt{\NAT@nm}%
-	 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
-   {\@citeb\@extra@b@citeb}%
-	 \NAT@date}}
-  {\@citea\NAT@nmfmt{\NAT@nm}%
-   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
-  {}{}
-\makeatother
-\cleanlookdateon
-\exhyphenpenalty=1000
-\hyphenpenalty=1000
-\widowpenalty=1000
-\clubpenalty=1000
-\usepackage{hyperref}
+---
+title:  |
+        | The Effect of Legislature Size on Public Spending
+        | A Meta-Analysis
+author: 
+  - Huzeyfe Alptekin[^huzeyfe]
+  - Danilo Freire[^danilo]
+  - Umberto Mignozzetti[^umberto]
+  - Catarina Roman[^catarina]
+date: \today
+thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback.
+We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
+Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>.
+We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
+abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures.
+Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration.
+However, recent studies have questioned the validity of the theory.
+In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending.
+Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets.
+Yet the aggregate results mask important differences.
+While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias.
+The available evidence also indicates that XXXXXXXXXXXXXXXX"
+abstractspacing: onehalf
+keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
+jelcodes: H21; H23; H50; H61
+fontsize: 12pt
+margin: 2cm
+urlcolor: darkblue
+linkcolor: Mahogany
+citecolor: Mahogany
+spacing: double
+papersize: a4paper
+bibliography: references.bib
+biblio-style: apalike
+output:
+  pdf_document:
+    citation_package: natbib
+    fig_caption: yes
+    number_sections: yes
+    keep_tex: no
+    toc: no
+    toc_depth: 3
+    template: article-template.latex
+---
 
-\hypersetup{
-	breaklinks=true,
-	linkcolor=Mahogany,
-	citecolor=Mahogany,
-	urlcolor=darkblue,
-	colorlinks=true}
+```{r, message=FALSE, warning=FALSE, echo=FALSE}
+# If you need to install any package while knitting the document
+r <- getOption("repos")
+r["CRAN"] <- "https://cran.rstudio.com/"
+options(repos = r)
+if (!require("kableExtra")) {
+    install.packages("kableExtra")
+}
+```
 
-\doublespacing
+[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
 
-\title{The Effect of Legislature Size on Public Spending:\\ A Meta-Analysis\thanks{The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback.
-We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
-Replication materials are available at \url{https://github.com/danilofreire/distributive-politics-meta-analysis}.
-We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1).}}
+[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
 
-\vspace{2cm}
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
 
-\author{Huzeyfe Alptekin\thanks{Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, Brazil, \href{mailto:huzeyfealptekin@gmail.com}{\texttt{huzeyfealptekin@gmail.com}}.}
-\hspace{.5cm} Danilo Freire\thanks{Independent Researcher, \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}}, \url{http://danilofreire.github.io}. Corresponding author.} 
-\hspace{.5cm} Umberto Mignozzetti\thanks{Visiting Assistant Professor, \href{mailto:umberto.mignozzetti@emory.edu}{\texttt{umberto.mignozzetti@emory.edu}}, \url{http://umbertomig.com}.} 
-\hspace{.5cm} Catarina Roman\thanks{Research Associate, School of International Relations, Fundação Getulio Vargas, Brazil, \href{mailto:catarinamroman@gmail.com}{\texttt{catarinamroman@gmail.com}}.}}
-
-\vspace{2cm}
-\date{\today}
-\begin{document}
-\maketitle
-
-\begin{abstract}
-
-\noindent In a seminal article, \citet{weingast1981political} argue that there
-is a positive relationship between legislature size and inefficiency in public
-expenditures. Their proposition is currently known as the ``law of $1/n$'' and
-has been widely debated in political science and public administration.
-However, recent studies have questioned the validity of the theory. In this
-letter, we estimate the first meta-analysis of the relationship between the
-number of legislators and public spending. Based on a sample of \textbf{29}
-articles, we find only mixed evidence for the effect of legislature size on
-government budgets. Yet the aggregate results mask important differences. While
-earlier, non-causal studies provide moderate support for the ``law of $1/n$'',
-recent papers using causal inference methods consistently find a negative
-relation between seats and spending, suggesting that previous results might
-have been driven by spurious correlations or omitted variable bias. The
-available evidence also indicates that XXXXXXXXXXXXXXXX
-
-\vspace{.4cm}
-\noindent \textbf{Keywords:} distributive politics; law of $1/n$; legislature
-size; meta-analysis; public spending
-
-\noindent \textbf{JEL Codes:} H21; H23; H50; H61
-\end{abstract}
+[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 
@@
 
-\section{Introduction}
+# Introduction
 \label{sec:intro}
@@
 overspend in their districts and transfer the costs to the entire polity.
-However, recent studies have questioned the validity of the ``law of $1/n$'', as
+However, recent studies have questioned the validity of the "law of $1/n$", as
 the theory is currently known. For instance, spending limits, strong executives,
@@
 collection of small districts can supply public goods more efficiently than the
-central government. The authors conclude that a ``reverse law of $1/n$'' may
+central government. The authors conclude that a "reverse law of $1/n$" may
 hold, wherein a higher number of legislators in small constituencies decrease
@@
 In this letter, we conduct the first meta-analysis that tests the generality of
-the ``law of $1/n$''. We have selected 29 articles that use quantitative methods
+the "law of $1/n$". We have selected 29 articles that use quantitative methods
 to analyse the impact of legislature size over government spending. We run two
@@
 evidence for a negative relation. This goes in contrast with the original
-theory and supports the existence of a ``reverse law of $1/n$''.
+theory and supports the existence of a "reverse law of $1/n$".
 \textbf{Moreover, ...}  In summary, our results point out that if legislature
@@
 
-\section{Methods}
+# Methods
 
@@
 
-\footnotesize
-\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}
-   >{\raggedright\arraybackslash}p{4.2cm}
-   >{\centering\arraybackslash}p{1.3cm}
-   >{\centering\arraybackslash}p{1cm}
-   >{\centering\arraybackslash}p{1cm}
-   >{\centering\arraybackslash}p{1.4cm}
-   >{\centering\arraybackslash}p{2.5cm}}
-\caption{Papers included in the meta-analysis, listed alphabetically by last name}\\
-\toprule
-\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
-\tabularnewline
-\midrule
-\endhead
-R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & OLS & M\\
-R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & OLS & M\\
-T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & IV & NM\\
-\begin{tabular}[t]{@{}l@{}}T.
-Bjedov,\\ S.
-Lapointe \& \\T.
-Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Panel & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Panel & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & OLS & M\\
-\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & OLS & M\\
-\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}J.
-Drew \& \\ B.
-Dollery\end{tabular} & The Price of Democracy?
-Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & Panel & NM\\
-\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & IV & NM\\
-\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & RDD & NM\\
-\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & RDD & NM\\
-\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & OLS & NM\\
-\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & OLS & M\\
-\begin{tabular}[t]{@{}l@{}}B.
-Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & OLS & NM\\
-\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & IV & M\\
-\begin{tabular}[t]{@{}l@{}}B.
-Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Panel & NM\\
-\begin{tabular}[t]{@{}l@{}}P.
-Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government?
-Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & RDD & NM\\
-\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & Panel & M\\
-\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & OLS & NM\\
-\begin{tabular}[t]{@{}l@{}}C.
-Schaltegger \& \\ L.
-Feld\end{tabular} & Do Large Cabinets Favor Large Governments?
-Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Panel & NM\\
-\begin{tabular}[t]{@{}l@{}}E.
-Stein,\\ E.
-Talvi \& \\ A.
-Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub.
-& 1998 & Multiple (26) & OLS & NM\\ [1ex]
-\bottomrule
-\label{tab:papers}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\vspace{-0.5cm}
-\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
-Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
-JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
-APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
-UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
-Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
-Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
-OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
-data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
-NM$=$Non-majoritarian (mixed or proportional representation). Country codes
-follow the ISO 3166-1 alpha-3 international standard.}
-\end{minipage}
-\end{longtable}
-
-\normalsize
-
-Our study sample reflects the development of the literature. Although the ``law
-of $1/n$'' was first formulated in 1981, the empirical assessment of the theory
+Our study sample reflects the development of the literature. Although the "law
+of $1/n$" was first formulated in 1981, the empirical assessment of the theory
 only started a few years later, as dates of publishing range from 1998 to 2019.
@@
 publication in an academic journal; 3) electoral system; 4) estimation method.
-Since the literature on the ``law of $1/n$'' is notably diverse, we were
+Since the literature on the "law of $1/n$" is notably diverse, we were
 restricted to include only the moderators that either refer to important
@@
 \vspace{.5cm}
-
-\begin{table}[htpb]
- \caption{Descriptive Statistics of Moderators}
- \centering
- \begin{tabular}{lccc}
-\hline  \hline
-& Main Coefficients & Other Coefficients &   All Coefficients    \\ 
-&        N=36        &       N=92        &    N=128    \\ 
-\hline     
-Independent Variables: &             &                    &                  \\
-$\qquad$ $k$ &    9 (25.0\%)      &     29 (31.5\%)    & 38 (29.7\%)  \\ 
-$\qquad$ $n$ &      21 (58.3\%)     &    51 (55.4\%)   & 72 (56.2\%)  \\ 
-$\qquad$ log($n$) &      6 (16.7\%)     &     12 (13.0\%)    & 18 (14.1\%)  \\ 
-Year &     2009 (6.50)    &    2008 (5.75)   & 2008 (5.98) \\ 
-Published work: &             &                    &                  \\ 
-$\qquad$Yes &     30 (83.3\%)     &    74 (80.4\%)    & 104 (81.2\%) \\ 
-$\qquad$No &    6 (16.7\%)       &     18 (19.6\%)   & 24 (18.8\%)  \\ 
-Electoral system: &             &                    &                  \\ 
-$\qquad$Majoritarian &     18 (50.0\%)      &    40 (43.5\%)   & 58 (45.3\%)  \\ 
-$\qquad$Non-Majoritarian &    18 (50.0\%)       &    52 (56.5\%)   & 70 (54.7\%)  \\ 
-Estimation method: &             &                    &                  \\ 
-$\qquad$OLS &     13 (36.1\%)     &   43 (46.7\%)     & 56 (43.8\%)  \\ 
-$\qquad$Panel &     17 (47.2\%)     &    40 (43.5\%)    & 57 (44.5\%)  \\ 
-$\qquad$IV &     3 (8.33\%)      &     3 (3.26\%)    &  6 (4.69\%)  \\ 
-$\qquad$RDD &     3 (8.33\%)      &     6 (6.52\%)    &  9 (7.03\%)  \\ 
-\hline  
-\end{tabular}
-\label{tab:descriptive}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\footnotetext{\textbf{Note:} The values for the variable \textit{Year} indicate the mean and the standard deviation, respectively.}
-\end{minipage}    
-\end{table}
 
@@
 
-\section{Results}
+# Results
 
-\subsection{Binomial Z-Tests}
+## Binomial Z-Tests
 \label{sub:binomial}
 
-The ``law of $1/n$'' states that more legislators increase government expenditure.
+The "law of $1/n$" states that more legislators increase government expenditure.
 Here we employ three methods to assess the empirical validity of that
@@
 (successes = 10, trials = 21, $p_{success} = 0.476$, 95\% CI = [0.257; 0.702],
-$p$-value = 1). Note that the ``law of $1/n$'' suggests that there is a positive
+$p$-value = 1). Note that the "law of $1/n$" suggests that there is a positive
 association between both. The binomial test for log($n$) also shows a
@@
 
-\subsection{Meta-Analysis}
+## Meta-Analysis
 \label{sub:Meta-Analysis}
@@
 0.058, prediction interval = [-0.026; 0.042], $I^2$ = 98.5\%). The 
-result supports the ``law of 1/$n$'', but the evidence is moderate
+result supports the "law of 1/$n$", but the evidence is moderate
 as the prediction interval include zero.
@@
 
-In a nutshell, we find only weak evidence in favour of the ``law of $1/n$''.
+In a nutshell, we find only weak evidence in favour of the "law of $1/n$".
 While some models do show a positive and statistically significant result, none
@@
 
-\subsection{Meta-Regressions}
+## Meta-Regressions
 \label{sub:regressions}
@@
 
-\section{Discussion}
+# Discussion
 \label{sec:discussion}
 
-In this article, we assess the empirical validity of the ``law of $1/n$''. Based
+In this article, we assess the empirical validity of the "law of $1/n$". Based
 on a sample of 26 recent publications on the topic, our meta-analyses show that
@@
 significant effect on public expenditures. If such effect exists, it is likely
-driven by an increase in $k$, the size of the upper legislature, as suggested by
-several studies in the literature \citep[e.g.,][]{baqir2002districting, 
+driven by an increase in $k$, the size of the upper legislature, as suggested
+by several studies in the literature \citep[e.g.,][]{baqir2002districting,
 bradbury2001legislative, bradbury2003local, chen_malhotra_2007,
-gilligan2001fiscal, primo2006stop}. We find no robust evidence for the ``reverse
-law of $1/n$'', which posits that larger legislatures lead to lower government
+gilligan2001fiscal, primo2006stop}. We find no robust evidence for the "reverse
+law of $1/n$", which posits that larger legislatures lead to lower government
 spending. One possible explanation is that the two logics are balancing each
@@
 regard. Finally, we highlight the need for more evidence in favour or against
-the ``law of $1/n$'' to inform general public policies. The available empirical
+the "law of $1/n$" to inform general public policies. The available empirical
 evidence points out that contextual variables may either amplify or reduce the
@@
 \newpage
-\bibliography{references.bib}
-\bibliographystyle{apalike}
+\setlength{\parindent}{0cm}
+\setlength{\parskip}{5pt}
 
@@
 matsusaka2005endogeneity, ricciuti2004legislatures}
-
-\end{document}

### 2020-11-29 manuscript/article.Rmd
commit 2 11/28

@@
 ```{r, message=FALSE, warning=FALSE, echo=FALSE}
-# If you need to install any package while knitting the document
-r <- getOption("repos")
-r["CRAN"] <- "https://cran.rstudio.com/"
-options(repos = r)
-if (!require("kableExtra")) {
-    install.packages("kableExtra")
+## Starting
+
+# Knitr options
+knitr::opts_chunk$set(fig.pos = "H") # holds figure position
+knitr::opts_chunk$set(echo = TRUE)
+
+set.seed(732578) # From random.org
+
+# Needed packages
+pkgs <- c("tidyverse", "meta", "metafor",
+          "readxl", "compareGroups",
+          "knitr", "gridGraphics", "gridExtra",
+          "ggpubr", "kableExtra", "magick")
+
+# Install if not already installed
+installIfNot <- function(x) {
+  if (x %in% rownames(installed.packages()) == FALSE)
+    install.packages(x, dependencies = T,
+					 repos = "http://cran.us.r-project.org")
 }
+lapply(pkgs, installIfNot)
+
+# Load packs
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
+
+# Load datasets
+load("../dataset/dataCoefs.RData")
+
+# Build plot function for forest plots
+build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
+  # Build dataset for plot
+  mod2 <- tibble(
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    bind_rows(.,
+              aux = tibble(
+                TE = c(mod$TE.random, NA),
+                seTE = c(mod$seTE.random, NA),
+                studlab = c("Overall Effect",
+                            "Prediction Interval"),
+                lower = c(mod$lower.random,
+                          mod$lower.predict),
+                upper = c(mod$upper.random,
+                          mod$upper.predict),
+                group = "B")) %>%
+    group_by(studlab) %>%
+    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+    ungroup()
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab2, TE),
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group),
+                   height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
+    scale_y_discrete(
+      labels = function(x)
+        str_replace(x, "_[0-9]*$", "")) +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
+    labs(x = "",
+         y = "") +
+    facet_grid(group~., scales = "free", space = "free") +
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8 * lsize,
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6 * lsize,
+                                     hjust = 1.1),
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
+          plot.title = element_text(hjust = 0.5,
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
+
+dat$scoefnd <- as.character(dat$scoef)
+dat$scoefnd[dat$scoefsig=='Positive'&dat$scoef=='Positive'&!is.na(dat$scoefsig)] = 'Positive Significant'
+dat$scoefnd[dat$scoefnd=='Positive'] = 'Positive Insignificant'
+dat$scoefnd[dat$scoefsig=='Negative'&dat$scoef=='Negative'&!is.na(dat$scoefsig)] = 'Negative Significant'
+dat$scoefnd[dat$scoefnd=='Negative'] = 'Negative Insignificant'
 ```
@@
 Our survey of the scholarship confirms this continuum of positive,
-insignificant, and negative results. Out of the 36 coefficients included in our
-selected articles, 42\% of them are positive and statistically significant, 22\%
-are positive and statistically insignificant, 17\% are negative and
-statistically insignificant, and 19\% are negative and statistically
+insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
+selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[4])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[3])`\%
+are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[1])`\% are negative and
+statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[2])`\% are negative and statistically
 significant. Given this diversity of empirical findings, a systematic review of
@@
 In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We have selected 29 articles that use quantitative methods
+the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that use quantitative methods
 to analyse the impact of legislature size over government spending. We run two
-sets of models: the first group uses only the main estimates of each paper (42),
+sets of models: the first group uses only the main estimates of each paper (`r dim(dat)[1]`),
 while the second set includes all coefficients reported in our sample
-(142).\footnote{Although there are 29 papers in our review, we include 42
-coefficients in the restricted sample. This is because 13 articles report
+(`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))` papers in our review, we include `r dim(dat)[1]`
+coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles report
 separate estimates for the impact of lower and upper house size on government

### 2020-11-29 appendix/appendix.Rmd
add table 3
commit 3 11/28

--- 2020-06-19 appendix/appendix.Rmd
@@
 
-[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, <umberto.mig@nyu.edu>, <http://umbertomig.com>.
+[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
 
@@
 }
+
+# Build forest plot for heterogeneous analysis
+# Build plot function for forest plots
+build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+  mod <- update(mod, byvar = hetvar, print.byvar = F)
+
+  # Build dataset for plot
+  mod2 <- tibble(
+    byvar = mod$byvar,
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    arrange(byvar)
+  auxmod <- tibble()
+  for (i in rev(mod$bylevs)){
+    auxmod <- rbind(auxmod, tibble(byvar = i,
+                    TE = NA,
+                    seTE = NA,
+                    studlab = toupper(i),
+                    lower = NA,
+                    upper = NA,
+                    group = "B"))
+    auxmod <- rbind(auxmod, 
+                    filter(mod2, byvar==i) %>% 
+                      arrange(desc(TE)))
+    auxmod <- rbind(auxmod, tibble(
+      byvar = i,
+      TE = mod$TE.random.w[which(mod$bylevs==i)],
+      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
+      studlab = 'Subgroup Effect',
+      lower = mod$lower.random.w[which(mod$bylevs==i)],
+      upper = mod$upper.random.w[which(mod$bylevs==i)],
+      group = "B"))
+  }
+  auxmod <- rbind(auxmod, tibble(
+    byvar = NA,
+    TE = c(mod$TE.random, NA),
+    seTE = c(mod$seTE.random, NA),
+    studlab = c("Overall Effect", "Prediction Interval"),
+    lower = c(mod$lower.random, mod$lower.predict),
+    upper = c(mod$upper.random, mod$upper.predict),
+    group = "B"))
+  mod2 <- data.frame(auxmod)
+  mod2$byvar <- toupper(mod2$byvar)
+  TEaux <- mod2$TE
+  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab, TEaux),
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group),
+                   height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
+    scale_y_discrete(
+      labels = function(x)
+        str_replace(x, "_[0-9]*$", "")) +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
+    labs(x = "",
+         y = "") +
+    facet_grid(byvar~., scales = "free", space = "free") +
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8 * lsize,
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6 * lsize,
+                                     hjust = 1.1),
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
+          plot.title = element_text(hjust = 0.5,
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
 ```
@@
 In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
-Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.
+Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.
 
@@
 
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};
-
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 18)}};
+
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 29)}};
   \draw [arrow] (id) -- (1st);
@@
 The first dataset has the main coefficients reported in the studies.
-These data include only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them.
+These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them.
 If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
-This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest.
-Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.
+This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest.
+Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
 
@@
 Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`).
-As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.
+As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.
 
@@
 ```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
-mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
-
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f1b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) +
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) +
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") +
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") +
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 15, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-
-f1b
+build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
 ```
@@
 Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+Both are non-significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
 
@@
 Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+## Lower House Size and Expenditure per Capita (IV)
+
+```{r, cache=TRUE}
+# Pooling effects analysis -- ExpPC x N (IV only)
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC',
+         method %in% c('IV'))
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F, cache=TRUE}
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+f8 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+### Regression Method Subgroup Analysis
+
+Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the expenduture per capita.
+To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
+
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods",warning=FALSE, cache=TRUE}
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+build_forest_het(mod, capt = NULL, hetvar = aux$method)
+```
+
+Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers negative displaying negative effects.
+The random effects model for the subgroup is 0.22, which is negative but non-significant.
+Improve the estimation technique, for the case of IVs, render still a null effect of legislature size on per capita government expenditure.
+
+\newpage
+
+## Lower House Size and Log of Expenditure per Capita (RDD Only)
+
+```{r, cache=TRUE}
+# Pooling effects analysis -- logExpPC x N (RDD only)
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC',
+         method == 'RDD')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F,warning=F, cache=TRUE}
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+f9 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+\newpage
+
+### Regression Method Subgroup Analysis
+
+Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenduture per capita.
+To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
+
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods",warning=FALSE, cache=TRUE}
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+build_forest_het(mod, capt = NULL, hetvar = aux$method)
+```
+
+For the RDD subgroup analysis, we can see a much clearer picture.
+All estimates are negative, and the subgroup effect is -0.11.
+This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.
+
+\newpage
+
+# Main Graphs Codes
+
+## Figure 1
+
+```{r, echo=T, warning=F, cache=TRUE}
+pdf('../graphs/graph1.pdf', width = 16, height = 11)
+ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
+dev.off()
+```
+
+## Figure 2
+
+```{r, echo=T, warning=F, cache=TRUE}
+pdf('../graphs/graph2.pdf', width = 12, height = 6)
+ggarrange(f8, f9, align = 'hv')
+dev.off()
+```
 
@@
 
+## Lower House Size and Expenditure per Capita (IV)
+
+```{r, cache=TRUE}
+# Pooling effects analysis -- ExpPC x N (IV only)
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC',
+         method %in% c('IV'))
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
+## Lower House Size and Log of Expenditure per Capita (RDD Only)
+
+```{r, cache=TRUE}
+# Pooling effects analysis -- ExpPC x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC',
+         method == 'RDD')
+
+mod <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+mod
+```
+
+And the forest plot:
+
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1. The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
+2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+3.
+The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
+Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+
 \newpage
@@
           "Year",
+          "Published: No",
           "Elecsys: Non-Majoritarian",
@@
 ```{r, warning=F, cache=T}
-mod <- permutest(mod, progbar = F)
+mod <- permutest(mod, progbar = F, iter = 100)
 mod
@@
     facet_grid(group~., scales = "free", space = "free") +
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8 * lsize,
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6 * lsize,
+                                     hjust = 1.1),
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
+          plot.title = element_text(hjust = 0.5,
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
+
+# Build plot function for forest plots to heterogeneous subgroup analysis
+build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+  mod <- update(mod, byvar = hetvar, print.byvar = F)
+
+  # Build dataset for plot
+  mod2 <- tibble(
+    byvar = mod$byvar,
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    arrange(byvar)
+  auxmod <- tibble()
+  for (i in rev(mod$bylevs)){
+    auxmod <- rbind(auxmod, tibble(byvar = i,
+                    TE = NA,
+                    seTE = NA,
+                    studlab = toupper(i),
+                    lower = NA,
+                    upper = NA,
+                    group = "B"))
+    auxmod <- rbind(auxmod, 
+                    filter(mod2, byvar==i) %>% 
+                      arrange(desc(TE)))
+    auxmod <- rbind(auxmod, tibble(
+      byvar = i,
+      TE = mod$TE.random.w[which(mod$bylevs==i)],
+      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
+      studlab = 'Subgroup Effect',
+      lower = mod$lower.random.w[which(mod$bylevs==i)],
+      upper = mod$upper.random.w[which(mod$bylevs==i)],
+      group = "B"))
+  }
+  auxmod <- rbind(auxmod, tibble(
+    byvar = NA,
+    TE = c(mod$TE.random, NA),
+    seTE = c(mod$seTE.random, NA),
+    studlab = c("Overall Effect", "Prediction Interval"),
+    lower = c(mod$lower.random, mod$lower.predict),
+    upper = c(mod$upper.random, mod$upper.predict),
+    group = "B"))
+  mod2 <- data.frame(auxmod)
+  mod2$byvar <- toupper(mod2$byvar)
+  TEaux <- mod2$TE
+  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab, TEaux),
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group),
+                   height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
+    scale_y_discrete(
+      labels = function(x)
+        str_replace(x, "_[0-9]*$", "")) +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
+    labs(x = "",
+         y = "") +
+    facet_grid(byvar~., scales = "free", space = "free") +
     labs(caption = capt,

### 2020-11-29 dataset/datasetBuilding.R

@@ -1,10 +1,11 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Jun 19, 2020                                  ##
+## Last Modified: Nov 10, 2020                                  ##
 ##################################################################
 
 # Needed packages
+rm(list=ls())
 pkgs <- c('tidyverse')
 
 # Install if not already installed
@@ -1180,7 +1181,7 @@ dat <- rbind(dat,
 dat <- rbind(dat,
              data.frame(
                id = 1415,
-               published = 'No',
+               published = 'Yes',
                usemeta = 1, 
                method = 'OLS',
                elecsys = 'Mixed',
@@ -1191,7 +1192,7 @@ dat <- rbind(dat,
                author = 'Ricciuti',
                year = 2004,
                authoryear = 'Ricciuti (2004)',
-               journal = NA,
+               journal = 'Rivista di Politica Economica',
                web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
                table = 3,
                column = 1,
@@ -1208,7 +1209,7 @@ dat <- rbind(dat,
 dat <- rbind(dat,
              data.frame(
                id = 1415,
-               published = 'No',
+               published = 'Yes',
                usemeta = 0, 
                method = 'OLS',
                elecsys = 'Mixed',
@@ -1219,7 +1220,7 @@ dat <- rbind(dat,
                author = 'Ricciuti',
                year = 2004,
                authoryear = 'Ricciuti (2004)',
-               journal = NA,
+               journal = 'Rivista di Politica Economica',
                web = 'http://www.bemservizi.unito.it/repec/icr/wp2004/Ricciuti20-04.pdf',
                table = 3,
                column = 2,
@@ -1236,7 +1237,7 @@ dat <- rbind(dat,
 dat <- rbind(dat,
              data.frame(
                id = 1415,
-               published = 'No',
+               published = 'Yes',
                usemeta = 0, 
                method = 'OLS',
                elecsys = 'Mixed',
@@ -1247,7 +1248,7 @@ dat <- rbind(dat,
                author = 'Ricciuti',
                year = 2004,
                authoryear = 'Ricciuti (2004)',
-               journal = NA,
+               journal = 'Rivista di Politica Economica',
[…]

### 2020-11-29 manuscript/article.Rmd
commit 4 11/28

@@
 
-```{r, message=FALSE, warning=FALSE, echo=FALSE}
-## Starting
-
+```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
 # Knitr options
@@
 knitr::opts_chunk$set(echo = TRUE)
+```
 
+```{r, message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
+# Clean up
+rm(list = ls())
+
+## Starting
 set.seed(732578) # From random.org
@@
 
+# Build forest plot for heterogeneous analysis
+# Build plot function for forest plots
+build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+  mod <- update(mod, byvar = hetvar, print.byvar = F)
+
+  # Build dataset for plot
+  mod2 <- tibble(
+    byvar = mod$byvar,
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    arrange(byvar)
+  auxmod <- tibble()
+  for (i in rev(mod$bylevs)){
+    auxmod <- rbind(auxmod, tibble(byvar = i,
+                    TE = NA,
+                    seTE = NA,
+                    studlab = toupper(i),
+                    lower = NA,
+                    upper = NA,
+                    group = "B"))
+    auxmod <- rbind(auxmod, 
+                    filter(mod2, byvar==i) %>% 
+                      arrange(desc(TE)))
+    auxmod <- rbind(auxmod, tibble(
+      byvar = i,
+      TE = mod$TE.random.w[which(mod$bylevs==i)],
+      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
+      studlab = 'Subgroup Effect',
+      lower = mod$lower.random.w[which(mod$bylevs==i)],
+      upper = mod$upper.random.w[which(mod$bylevs==i)],
+      group = "B"))
+  }
+  auxmod <- rbind(auxmod, tibble(
+    byvar = NA,
+    TE = c(mod$TE.random, NA),
+    seTE = c(mod$seTE.random, NA),
+    studlab = c("Overall Effect", "Prediction Interval"),
+    lower = c(mod$lower.random, mod$lower.predict),
+    upper = c(mod$upper.random, mod$upper.predict),
+    group = "B"))
+  mod2 <- data.frame(auxmod)
+  mod2$byvar <- toupper(mod2$byvar)
+  TEaux <- mod2$TE
+  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab, TEaux),
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group),
+                   height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
+    scale_y_discrete(
+      labels = function(x)
+        str_replace(x, "_[0-9]*$", "")) +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
+    labs(x = "",
+         y = "") +
+    facet_grid(byvar~., scales = "free", space = "free") +
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8 * lsize,
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6 * lsize,
+                                     hjust = 1.1),
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
+          plot.title = element_text(hjust = 0.5,
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
+
 dat$scoefnd <- as.character(dat$scoef)
@@
 insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
-selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[4])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[3])`\%
-are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[1])`\% are negative and
-statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[2])`\% are negative and statistically
+selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
+are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
+statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
 significant. Given this diversity of empirical findings, a systematic review of
@@
 available in the Supplementary Material.
+
+\footnotesize
+\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.2cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.5cm}}
+\caption{Papers included in the meta-analysis, listed alphabetically by last name}\\
+\toprule
+\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
+\tabularnewline
+\midrule
+\endhead
+R. Baqir & Districts, Spillovers, and Government Overspending & Unpub. & 1999 & USA & OLS & M\\
+R. Baqir & Districting and Government Overspending & JPE & 2002 & USA & OLS & M\\
+T. Baskaran & Coalition Governments, Cabinet Size, and the Common Pool Problem: Evidence from the German States & EJPE & 2013 & DEU & IV & NM\\
+\begin{tabular}[t]{@{}l@{}}T.
+Bjedov,\\ S.
+Lapointe \& \\T.
+Madiès \end{tabular} & The Impact of Within-Party and Between-Party Ideological Dispersion on Fiscal Outcomes: Evidence from Swiss Cantonal Parliaments & PC & 2014 & CHE & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ M. Crain\end{tabular} & Legislative Organization and Government Spending: Cross-Country Evidence & JPubE & 2001 & Multiple (37) & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Bradbury \& \\ E. F. Stephenson\end{tabular} & Spatially Targeted Government Spending and Heterogeneous Constituent Cost Shares & JPriE & 2009 & USA & OLS & M\\
+\begin{tabular}[t]{@{}l@{}}J. Chen \& \\ N. Malhotra\end{tabular} & The Law of 1/K: The Effect of Chamber Size on Government Spending in Bicameral Legislatures & APSR & 2007 & USA & OLS & M\\
+\begin{tabular}[t]{@{}l@{}}G. Crowley\end{tabular} & The Law of 1/N Revisited: Distributive Politics, Legislature Size, and the Costs of Collective Action &  SEJ & 2019 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}J.
+Drew \& \\ B.
+Dollery\end{tabular} & The Price of Democracy?
+Political Representation Structure and Per Capita Expenditure in Victorian Local Government & UAR & 2017 & AUS & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}H. A. Erler\end{tabular} & Legislative Term Limits and State Spending & PC & 2007 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}N. Fiorino \& \\ R. Ricciuti\end{tabular} & Legislature Size and Government Spending in Italian Regions: Forecasting the Effects of a Reform & PC & 2007 & ITA & IV & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Höhmann\end{tabular} & The Effect of Legislature Size on Public Spending: Evidence from a Regression Discontinuity Design & PC & 2017 & DEU & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}A. Kessler\end{tabular} & Communication in Federal Politics: Universalism, Policy Uniformity, and the Optimal Allocation of Fiscal Authority & JPE & 2014 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee\end{tabular} & Supermajority Rule and Bicameral Bargaining & PC & 2016 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}D. Lee \& \\ S. Park\end{tabular} & Court-Ordered Redistricting and the Law of 1/N & PC & 2018 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}B. Lewis\end{tabular} & Legislature Size, Local Government Expenditure and Taxation, and Public Service Access in Indonesia & SCID & 2019 & IDN & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}V. Lledo\end{tabular} & Electoral Systems, Legislative Fragmentation and Public Spending: A Comparative Analysis of Brazilian States & Unpub. & 2003 & BRA & OLS & NM\\
+\begin{tabular}[t]{@{}l@{}}L. MacDonald\end{tabular} & The Impact of Government Structure on Local Public Expenditures & PC & 2008 & USA & OLS & M\\
+\begin{tabular}[t]{@{}l@{}}B.
+Maldonado\end{tabular} & Legislature, Leaders, and Leviathans: How Constitutional Institutions Affect the Size of Government Spending & SSQ & 2013 & Multiple (92) & OLS & NM\\
+\begin{tabular}[t]{@{}l@{}}J. Matsusaka\end{tabular} & The Endogeneity of the Initiative: A Comment on Marschall and Ruhil & SPPQ & 2005 & USA & IV & M\\
+\begin{tabular}[t]{@{}l@{}}B.
+Mukherjee\end{tabular} & Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence & CPS & 2003 & Multiple (110) & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}P.
+Pettersson-Lidbom\end{tabular} & Does the Size of the Legislature Affect the Size of Government?
+Evidence from Two Natural Experiments & JPubE & 2012 & FIN \& SWE & RDD & NM\\
+\begin{tabular}[t]{@{}l@{}}D. Primo\end{tabular} & Stop Us before We Spend Again: Institutional Constraints on Government Spending & E\&P & 2006 & USA & Panel & M\\
+\begin{tabular}[t]{@{}l@{}}R. Ricciuti\end{tabular} & Legislature Size, Bicameralism and Government Spending: Evidence from Democratic Countries & Unpub. & 2004 & Multiple (75) & OLS & NM\\
+\begin{tabular}[t]{@{}l@{}}C.
+Schaltegger \& \\ L.
+Feld\end{tabular} & Do Large Cabinets Favor Large Governments?
+Evidence on the Fiscal Commons Problems for Swiss Cantons & JPubE & 2009 & CHE & Panel & NM\\
+\begin{tabular}[t]{@{}l@{}}E.
+Stein,\\ E.
+Talvi \& \\ A.
+Grisanti\end{tabular} & Institutional Arrangements and Fiscal Performance: The Latin American Experience & Unpub.
+& 1998 & Multiple (26) & OLS & NM\\ [1ex]
+\bottomrule
+\label{tab:papers}
+\begin{minipage}{\textwidth}
+\renewcommand{\footnoterule}{}
+\vspace{-0.5cm}
+\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
+Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
+JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
+APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
+UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
+Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
+Quarterly, CPS$=$Comparative Political Studies, E\&P$=$Economics and Politics,
+OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
+Country codes follow the ISO 3166-1 alpha-3 international standard.}
+\end{minipage}
+\end{longtable}
+
+\normalsize
 
@@
 
+```latex
 \vspace{.5cm}
@@
 \begin{table}[htpb]
-\footnotesize
 \caption{Meta Regression Results}
 \label{tab:regressions}
+\footnotesize
 \centering
@@
 \end{table}
+```
 

### 2020-11-29 manuscript/article.Rmd
commit 4 11/28

--- 2020-11-29 manuscript/article.Rmd
@@
 
-dat$scoefnd <- as.character(dat$scoef)
-dat$scoefnd[dat$scoefsig=='Positive'&dat$scoef=='Positive'&!is.na(dat$scoefsig)] = 'Positive Significant'
-dat$scoefnd[dat$scoefnd=='Positive'] = 'Positive Insignificant'
-dat$scoefnd[dat$scoefsig=='Negative'&dat$scoef=='Negative'&!is.na(dat$scoefsig)] = 'Negative Significant'
-dat$scoefnd[dat$scoefnd=='Negative'] = 'Negative Insignificant'
+# Build forest plot for heterogeneous analysis
+# Build plot function for forest plots
+build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+  mod <- update(mod, byvar = hetvar, print.byvar = F)
+
+  # Build dataset for plot
+  mod2 <- tibble(
+    byvar = mod$byvar,
+    TE = mod$TE,
+    seTE = mod$seTE,
+    studlab = mod$studlab,
+    lower = mod$lower,
+    upper = mod$upper,
+    group = "A") %>%
+    arrange(byvar)
+  auxmod <- tibble()
+  for (i in rev(mod$bylevs)){
+    auxmod <- rbind(auxmod, tibble(byvar = i,
+                    TE = NA,
+                    seTE = NA,
+                    studlab = toupper(i),
+                    lower = NA,
+                    upper = NA,
+                    group = "B"))
+    auxmod <- rbind(auxmod, 
+                    filter(mod2, byvar==i) %>% 
+                      arrange(desc(TE)))
+    auxmod <- rbind(auxmod, tibble(
+      byvar = i,
+      TE = mod$TE.random.w[which(mod$bylevs==i)],
+      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
+      studlab = 'Subgroup Effect',
+      lower = mod$lower.random.w[which(mod$bylevs==i)],
+      upper = mod$upper.random.w[which(mod$bylevs==i)],
+      group = "B"))
+  }
+  auxmod <- rbind(auxmod, tibble(
+    byvar = NA,
+    TE = c(mod$TE.random, NA),
+    seTE = c(mod$seTE.random, NA),
+    studlab = c("Overall Effect", "Prediction Interval"),
+    lower = c(mod$lower.random, mod$lower.predict),
+    upper = c(mod$upper.random, mod$upper.predict),
+    group = "B"))
+  mod2 <- data.frame(auxmod)
+  mod2$byvar <- toupper(mod2$byvar)
+  TEaux <- mod2$TE
+  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
+
+  # Graph limits
+  limg <- max(abs(c(mod2$lower, mod2$upper)))
+
+  # Build plot
+  p <- mod2 %>%
+    ggplot(aes(y = reorder(studlab, TEaux),
+               x = TE, xmin = lower, xmax = upper)) +
+    geom_point(aes(color = group)) +
+    geom_errorbarh(aes(color = group),
+                   height = 0.1) +
+    scale_color_manual(values = c("#000000", "#8b0000")) +
+    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
+    scale_y_discrete(
+      labels = function(x)
+        str_replace(x, "_[0-9]*$", "")) +
+    geom_vline(xintercept = 0,
+               color = "#000000", linetype = "dashed") +
+    labs(x = "",
+         y = "") +
+    facet_grid(byvar~., scales = "free", space = "free") +
+    labs(caption = capt,
+         title = ttl) +
+    theme_minimal() %+replace%
+    theme(strip.text.y = element_blank(),
+          legend.position = "none",
+          axis.text.y = element_text(size = .8 * lsize,
+                                     hjust = 1),
+          axis.text.x = element_text(size = .6 * lsize,
+                                     hjust = 1.1),
+          plot.caption = element_text(size = lsize),
+          plot.title.position = "plot",
+          plot.title = element_text(hjust = 0.5,
+                                    face = "bold",
+                                    margin = margin(0, 0, 10, 0)),
+          panel.grid.major = element_blank())
+  return(p)
+}
 ```
@@
 
+\footnotesize
+\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
+\caption{Papers included in the meta-analysis, listed year of appearance}\\
+\toprule
+\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
+\tabularnewline
+\midrule
+\endhead
+```{r, echo = FALSE, results = 'asis'}
+build_nams <- function(x) {
+  x_ <- unlist(strsplit(as.character(x), ' & ', fixed = T, useBytes = T))
+  if(length(x_) == 1) return(x_)
+  else {
+    aux <- x_[1]
+      for (i in 2:length(x_))
+        if (i == length(x_)){
+          aux <- paste(aux, ' \\& \\\\ ', x_[i], sep = '')
+        } else {
+          aux <- paste(aux, ',\\\\ ', x_[i], sep = '')
+        }
+  }
+  return(paste('\\begin{tabular}[t]{@{}l@{}}', aux,'\\end{tabular}', 
+                   sep = ''))
+}
+aux <- dat %>%
+  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
+  unique() %>%
+  arrange(year)
+for (i in 1:dim(aux)[1]) {
+  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
+      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
+      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
+      aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
+}
+```
+\bottomrule
+\label{tab:papers}
+\begin{minipage}{\textwidth}
+\renewcommand{\footnoterule}{}
+\vspace{-0.5cm}
+\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
+Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
+JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
+APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
+UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
+Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
+Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal, OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
+Country codes follow the ISO 3166-1 alpha-3 international standard.}
+\end{minipage}
+\end{longtable}
+
+\normalsize
+
 Our study sample reflects the development of the literature. Although the "law
 of $1/n$" was first formulated in 1981, the empirical assessment of the theory
-only started a few years later, as dates of publishing range from 1998 to 2019.
+only started a few years later, as dates of publishing range from `r min(dat$year)` to `r max(dat$year)`.
 
-Most studies focus on the United States (12), but our sample also contains
-papers on Australia (1), Brazil (1), Germany (2), Indonesia (1), Italy (1), and
-Switzerland (2). Five articles use cross-national data and analyse from 2 to 110
+Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
+papers on Australia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='AUS')])`), Brazil (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='BRA')])`), Germany (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='DEU')])`), Indonesia (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='IDN')])`), Italy (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='ITA')])`), and
+Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`).
+Five articles use cross-national data and analyse from 2 to 110
 countries.
 
-Regarding the dependent variables included in the sample, 13 studies employ
-public expenditure per capita, 7 papers use its natural logarithm, and 8 of them
+Regarding the dependent variables included in the sample, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='ExpPC')])` studies employ
+public expenditure per capita, `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='logExpPC')])` papers use its natural logarithm, and `r as.numeric(table(unique(dat[,c('id','depvar2')])$depvar2)[which(names(table(unique(dat[,c('id','depvar2')])$depvar2))=='PCTGDP')])` of them
 analyse the impact of legislature size on public expenditures as a percentage of
@@
 legislatures on different measures of government spending. Our independent
-variables of interest are $n$, lower chamber size (21), ($\log(n)$), the natural
-logarithm of lower chamber size (6), and $k$, which represents upper chamber
-size (9).
+variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
+logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
+size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
 
@@
 the coefficient from the optimal bandwidth or from the intermediate one. This
-sample encompasses 36 estimates, as 10 articles analysed two dependent or
+sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
 independent variables of interest \citep{baqir1999districts, bjedov2014impact,
@@
 lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading}. Our second sample, in contrast, contains all the 126 effect
-sizes reported in the 26 papers. Here we focus on the results for our restricted
+ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
+sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
 sample as we consider them more robust, but the findings are very similar when

### 2020-11-29 dataset/datasetBuilding.R

@@ -26,15 +26,18 @@ dat <- data.frame(
   usemeta = 1,
   method = 'OLS',
   elecsys = 'Maj',
-  elecsys2 = 'Maj',
+  elecsys2 = 'Maj', elecsys3 = 'M',
   agglevel = 'States',
   location = 'US',
+  locationISO = 'USA',
   title = 'Spatially Targeted Government Spending and
 Heterogeneous Constituent Cost Shares',
   author = 'Bradbury and Stephenson',
+  authorCite = 'J. Bradbury & E. F. Stephenson',
   year = 2009,
   authoryear = 'Bradbury and Stephenson (2009)',
   journal = 'The Journal of Private Enterprise',
+  journalCode = 'JPriE',
   web = 'http://journal.apee.org/index.php?title=Spring2009_6',
   table = 2,
   column = 2,
@@ -56,14 +59,17 @@ dat <- rbind(dat,
                usemeta = 1, 
                method = 'PANEL',
                elecsys = 'Mixed',
-               elecsys2 = 'Non-Maj',
+               elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
                location = 'World',
+               locationISO = 'Multiple (37)',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
+               authorCite = 'J. Bradbury & M. Crain',
                year = 2001,
                authoryear = 'Bradbury and Crain (2001)',
                journal = 'Journal of Public Economics',
+               journalCode = 'JPubE',
                web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
                table = 2,
                column = 5,
@@ -85,14 +91,17 @@ dat <- rbind(dat,
                usemeta = 0, 
                method = 'PANEL',
                elecsys = 'Mixed',
-               elecsys2 = 'Non-Maj',
+               elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
                location = 'World',
+               locationISO = 'Multiple (37)',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
+               authorCite = 'J. Bradbury & M. Crain',
                year = 2001,
                authoryear = 'Bradbury and Crain (2001)',
                journal = 'Journal of Public Economics',
+               journalCode = 'JPubE',
                web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
[…]

### 2020-11-30 manuscript/article.Rmd
commit 1 11/29

@@
 
+```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
+fulldat$usemeta2 <- factor(fulldat$usemeta)
+levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
+fulldat$usemeta2 <- as.character(fulldat$usemeta2)
+fulldat$usemeta2 <- factor(fulldat$usemeta2)
+aux <- select(fulldat, usemeta2, indepvar2, year, published,
+              elecsys2, method) %>%
+  rename(`Independent Variables` = indepvar2,
+         `Year` = year,
+         `Published work` = published,
+         `Electoral system` = elecsys2,
+         `Estimation method` = method)
+
+res <- export2latex(
+  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+             show.p.overall = F, show.all = T, all.last = T), 
+  caption = 'Descriptive Statistics of Moderators\\label{tab:descriptive}'
+)
+res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
+cat(res)
+```
+
+\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
+\hline  
+& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
+&       N=42        &       N=100        &    N=142    \\
+\hline
+\hline     
+\endfirsthead 
+\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
+\hline
+& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
+&       N=42        &       N=100        &    N=142    \\ 
+\hline
+\hline  
+\endhead   
+\hline
+\multicolumn{4}{l}{\textit{continued on next page}} \\ 
+\endfoot   
+\multicolumn{4}{l}{}  \\ 
+\endlastfoot 
+Independent Variables: &                   &                    &            \\ 
+$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
+$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
+$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
+Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
+Published work: &                   &                    &            \\ 
+$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
+$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
+Electoral system: &                   &                    &            \\ 
+$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
+$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
+Estimation method: &                   &                    &            \\ 
+$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
+$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
+$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
+$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\
+
+\hline
+\end{longtable}
+
 Since most selected articles have more than one effect size, the observations

### 2020-11-30 manuscript/article.Rmd
commit 1 11/30

@@
 
+```{r, cache=TRUE, echo = FALSE}
+aux <- filter(dat, indepvar2 == "N")
+binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
+aux <- filter(dat, indepvar2=='K')
+binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+aux <- filter(dat, indepvar2 == "logN")
+binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
+```
+
 The binomial z-test evaluates whether the coefficient of our independent
@@
 between the number of legislators in the lower house and public expenditure 
-(successes = 10, trials = 21, $p_{success} = 0.476$, 95\% CI = [0.257; 0.702],
-$p$-value = 1). Note that the "law of $1/n$" suggests that there is a positive
+(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, $p_{success} = $ `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
+$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
 association between both. The binomial test for log($n$) also shows a
-non-statistically significant result (successes = 5, trials = 6, $p_{success} =
-0.833$, 95\% CI = [0.359; 0.996], $p$-value = 0.219). In contrast, we find a
+non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, $p_{success} = $ `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
+$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
 positive result for the number of legislators in the upper house ($k$), which is
-in line with the mainstream literature (successes = 8, trials = 9, $p_{success}
-= 0.889$, 95\% CI = [0.518; 0.997], $p$-value = 0.039).
+in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, $p_{success} = $ `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
+$p$-value = `r round(as.numeric(binK$p.value), 3)`).
 
@@
 Figure \ref{fig:plots} shows the forest plots for our restricted sample, the one
-which includes only the main 36 coefficients for the 26 selected papers. On the
+which includes only the main `r dim(dat)[1]` coefficients for the `r length(unique(dat$id))` selected papers. On the
 left side of the plots are the name of the study authors and the paper
@@
 
+```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
+mod <- list()
+# Pooling effects analysis -- ExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod[[1]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- ExpPC x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod[[2]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+# Pooling effects analysis -- logExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod[[3]] <- metagen(
+  coef, SE, data=aux,
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction = TRUE,
+  sm="SMD"
+  )
+
+# Pooling effects analysis -- logExpPC x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'logExpPC')
+
+mod[[4]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- PCTGDP x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod[[5]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- PCTGDP x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod[[6]] <- metagen(
+  coef, SE, data=aux,
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction=TRUE,
+  sm="SMD"
+  )
+
+# Pooling effects analysis -- PCTGDP x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'PCTGDP')
+
+mod[[7]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+```
+
 The first column of the graph reports the results for $n$, lower chamber size.
 In the first model, which correlates $n$ and expenditure per capita, we find a
-standardised mean difference (SMD) of $-0.070$ and a standard error of $0.273$
-(studies = 12, 95\% CI = [-0.671; 0.531], $p$-value = 0.803, prediction interval
-= [-1.55; 1.41]). Therefore, we cannot reject the null hypothesis that the
+standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
+(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
+= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
 effect size is zero. The $I^2$ statistic, which quantifies the degree of
-heterogeneity among studies, is equal to 94.7\%. $I^2$ values above 75\%
+heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
 indicate very high study heterogeneity \citep{higgins2019cochrane}.
@@
 We see similar results when we compare $n$ with log expenditure per capita. In
-this model, the average effect size is -0.07 and the standard deviation is
-0.059 (studies = 4, 95\% CI = [-0.256; 0.119], $p$-value = 0.328, prediction
+this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
+`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
 interval = [-0.618; 0.481]; $I^2$ = 92.5\%). The coefficient is 
@@
 In our restricted sample, larger lower house size also does not increase
-government spending as a percentage of GDP (studies = 5, SMD = -0.008, SE =
-0.013, 95\% CI = [-0.045; 0.0285], $p$-value = 0.567, prediction interval =
+government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
+`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
 [-0.105; 0.089], $I^2$ = 87.1\%). We find a positive effect in our extended
@@
 statistically significant at 10\%, but the prediction interval encompasses zero
-(studies = 3, SMD = 0.184, SE = 0.06, 95\% CI = [-0.0738; 0.4425], $p$-value =
-0.0916, prediction interval = [-1.258; 1.627], $I^2$ = 85.9\%). Although the
+(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
+`r round(mod[[4]]$pval.random,3)`, prediction interval = [-1.258; 1.627], $I^2$ = 85.9\%). Although the
 coefficient has the predicted sign, we should interpret the finding with caution
@@
 GDP fails to reach conventional levels of statistical significance (studies =
-3, SMD = 0.0203, SE = 1.677, 95\% CI = [-7.196; 7.237], $p$-value = 0.991,
+`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
 prediction interval = [-36.206; 36.246], $I^2$ = 96.1\%). The extended sample
@@
 variable. We find a positive correlation between $k$ and expenditure per capita
-and the coefficient is significant at a 10\% level (studies = 6, SMD = 10.613, SE
-= 5.148, 95\% CI = [-2.621; 23.848], $p$-value = 0.094, prediction interval =
+and the coefficient is significant at a 10\% level (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
+= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
 [-21.130; 42.357], $I^2$ = 79.4\%). But as with the other models, the prediction
@@
 spending as a percentage of GDP. The coefficient is not statistically
-significant, indicating a null effect (studies = 3, SMD = -0.003, SE =, 95\% CI
-= [-0.079; 0.074], $p$-value = 0.891, prediction interval = [-0.428; 0.423],
+significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
+= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [-0.428; 0.423],
 $I^2$ = 85.8\%). The result is very similar in the extended sample.
@@
 In this article, we assess the empirical validity of the "law of $1/n$". Based
-on a sample of 26 recent publications on the topic, our meta-analyses show that
+on a sample of `r length(unique(dat$id))` recent publications on the topic, our meta-analyses show that
 there is little evidence that an increase in the number of legislators has a

### 2020-12-01 manuscript/article.Rmd
commit 11/30

@@
 
+# Full model - Pooling effects analysis -- PCTGDP x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod[[8]] <- metagen(coef, SE, data = aux,
+          studlab = paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm = "SMD")
+
+# Full data - Pooling effects analysis -- ExpPC x K
+aux <- fulldat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod[[9]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
 ```
@@
 `r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
-interval = [-0.618; 0.481]; $I^2$ = 92.5\%). The coefficient is 
+interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
 statistically indistinguishable from zero.
@@
 `r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
-[-0.105; 0.089], $I^2$ = 87.1\%). We find a positive effect in our extended
+[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
 sample and the coefficient is statistically significant at the 10\% level
-(coefficients = 21, SMD = 0.008, SE = 0.004, 95\% CI = [-0.000; 0.016], $p$-value =
-0.058, prediction interval = [-0.026; 0.042], $I^2$ = 98.5\%). The 
+(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
+`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
 result supports the "law of 1/$n$", but the evidence is moderate
@@
 (studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
-`r round(mod[[4]]$pval.random,3)`, prediction interval = [-1.258; 1.627], $I^2$ = 85.9\%). Although the
+`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
 coefficient has the predicted sign, we should interpret the finding with caution
-as it does not replicate in our sample of 126 effect sizes.
+as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.
 
@@
 `r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
-prediction interval = [-36.206; 36.246], $I^2$ = 96.1\%). The extended sample
+prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
 also gives us a null result.
@@
 = `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
-[-21.130; 42.357], $I^2$ = 79.4\%). But as with the other models, the prediction
+[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
 interval again includes zero. When we run the same analysis in the extended
 sample, we also see a significant coefficient yet a prediction interval that
-contains zero (coefficients = 24, SMD = 7.216, SE = 1.342, 95\% CI = [4.440; 9.992],
-$p$-value $<$ 0.0001, prediction interval = [-1.222; 15.654], $I^2$ = 77.7\%).
+contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
+$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).
 
@@
 significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
-= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [-0.428; 0.423],
-$I^2$ = 85.8\%). The result is very similar in the extended sample.
+= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
+$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.
 

### 2020-12-03 appendix/appendix.Rmd
editing appendix text

@@
 
-# Needed packages
+# Required packages
 pkgs <- c("tidyverse", "meta", "metafor",
-          "readxl", "compareGroups",
+          "readxl", "devtools", "data.table",
           "knitr", "gridGraphics", "gridExtra",
@@
 # Install if not already installed
-installIfNot <- function(x) {
+install <- function(x) {
   if (x %in% rownames(installed.packages()) == FALSE)
@@
 }
-lapply(pkgs, installIfNot)
-
-# Load packs
+lapply(pkgs, install)
+devtools::install_github("isubirana/compareGroups")
+
+# Load packages
 lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
+library("compareGroups")
 
@@
 To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics", which is a seminal contribution in the field.
-Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, our search resulted in 2,664 records as of the 21\textsuperscript{st} of November 2019.
+Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
 
@@
 The selection process was conducted by two authors in three phases.
-In the first round, we excluded all titles that were obviously unrelated to our topic.
+In the first round, we excluded all titles that were clearly unrelated to our topic of interest.
 For instance, we curiously found articles about automobile motors amidst our sample.
 We consider this a preliminary step, since we were not able to eliminate a large number of entries.
-Thus, we read all abstracts.
+Then, we read all abstracts.
 We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper.
@@
 In the second phase, we assessed full texts.
-To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure.
-If the record was marked as positive for all three, it was maintained.
+To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure.
+If the publication had all three, it was maintained.
 Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
@@
 
-The meta-analytic data is comprised of two datasets.
+Our data are comprised of two datasets.
 The first dataset has the main coefficients reported in the studies.
@@
 
-In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
+In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended dataset.
 Below is the data extraction process for all relevant coefficients in the selected articles.
@@
 
-In this section, we show the descriptive statistics for our meta-analytic sample.
+In this section, we show the descriptive statistics for our sample.
 We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.
@@
 For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`.
-The oldest study included in the paper is dated from `r min(dat$year)`, while the most recent paper is dated from `r max(dat$year)`.
+The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`.
 Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the _law of 1/n_.
@@
 
-Our study selection differs considerably in regards to research design.
+Our sample differs considerably in regards to research design.
 One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies.
-In our sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
+In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
 The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}
@@
 
-The coefficients in the papers present a striking variability. In this section, we plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
+The coefficients in the papers vary considerably. In this section, we plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
 
@@
 
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
+Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had a positive sign.
 The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
@@
 
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
+Out of `r sum(table(aux$scoef))`, `r as.numeric(table(aux$scoef)[2])` had a positive sign.
 The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-
-Finally, for the number of legislators in the upper house ($K$), the results follow below.
+So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
+
+Finally, for the number of legislators in the upper house ($K$), the results are:
 
@@
 
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had positive sign.
-The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
+Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` had a positive sign.
+The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`.
 Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
@@
 
-In general terms, there are two main ways to conduct a meta-analysis, using fixed effects or random effects models.
+In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models.
 The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, on the other hand, assumes that there are a distribution of true effects, that vary based on sample and tests characteristics.
+The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sample and tests characteristics.
 
@@
 These sources of heterogeneity have two implications.
-First, they make our estimates very disperse.
+First, they make our estimates notably disperse.
 All but one of our heterogeneity tests are significant.
@@
 Let each study having an effect of $T_i$.
-In a random effects model, we can decompose this effect in two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
+In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
 
@@
 
-And the forest plot:
+The forest plot:
 
@@
 
-There were no studies that had per capita expenditure in the dependent variable and log of lower house size in the treatment variable.
+There are no studies that have per capita expenditure as the dependent variable and log of lower house size as the treatment variable.
 
@@
 
-And the forest plot:
+The forest plot is as follows:
 
@@
 
-No studies related the log of per capita expenditure with the size of upper house (K).
+No studies correlate the log of per capita expenditure with the size of upper house (K).
 
@@
 
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the main treatment variable.
+This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the treatment variable.
 
@@
 
-And the forest plot:
+Forest plot:
 
@@
 
-# Main Graphs Codes
+# Code for the Main Graphs
 
@@
 ## Lower House Size and Expenditure Per Capita
+
+Here we estimate the relationship between expenditure per capita as a dependent variable, and the lower house size as the independent variable.
 
@@
 
-The _law of 1/n_ was created for majoritarian systems.
+The _law of 1/n_ was formulated to analyse the budgetary allocation in majoritarian systems.
 In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary electoral system.
+We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.
 
@@
 
-Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
+Therefore, we see that majoritarian systems do not have a clear positive effect on budgetary spending.
 The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
@@
 
-This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
+This model estimates the log of per capita expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
 
@@
 
+In this section, we show the coefficients for our meta-regressions. We start with expenditure as a percentage of GDP as the dependent variable.
+
 ```{r, warning=F, cache=T}
@@
              "Year",
-             "Published: No",
              "Elecsys: Non-Majoritarian",
@@
           "Year",
-          "Published: No",
           "Elecsys: Non-Majoritarian",
@@
 ## Meta-Regressions for Expenditure Per Capita
+
+Here we do the same exercise with expenditure per capita as the main outcome.
 
@@
 
+Lastly, we run the model with the natural logarithm of expenditure per capita.
+
 ```{r, warning=F, cache=T}
@@
 
-aux = list(mod3, mod5, mod1) %>%
+aux <- list(mod3, mod5, mod1) %>%
   map(~{
@@
 
-# Robustness: Full Model Meta-Regressions Combined
+# Robustness: Full Model Meta-Regressions
 
@@
 
-## Webscraping Code \label{sub:scrap}
+## Webscraping Code
+\label{sub:scrap}
+
+We used the code below to download the articles cited in our paper.
 
 ```{r, eval = FALSE, cache=T}
-#### PACKAGES CONFIGURATION ####
-
-# Needed packages
+# Required packages
 pkgs <- c("tidyverse", "rvest", "RSelenium")
 
-# Install if not already installed
+# Install the packages if necessary
 installIfNot <- function(x) {
@@
 
-# Load packs
+# Load packages
 lapply(pkgs, require, character.only = T)
@@
 
-#### SETTING UP SELENIUM ####
+# Setting Up Selenium
 
@@
 
-#### Google scholar ####
+# Google Scholar
 
@@
 
-#### SCOPUS ####
+# Scopus
 

### 2020-12-03 manuscript/article.Rmd
editing appendix text

@@
     template: article-template.latex
+    md_extensions: +raw_attribute
 ---
@@
 \vspace{.3cm}
-\includegraphics[width=25cm,height=17cm]{meta-analysis.pdf}
+\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
 \label{fig:plots}
@@
 
+One reason why we have not detected any effects may be the identification strategy used to estimate the effects.
+On the one hand, OLS and Panel data models, require too many controls to make units comparable.
+On the other hand, these techniques are not as credible to estimate the causal effect of legislature size on public expenditures.
+Estimation methods such as Instrumental Variables, and Regression Discontinuity Design make the units comparable by employing natural and quasi-natural experiments.
+Figure \ref{fig:plots2} disentangle the estimation techniques for two models that there is broadly variation in the estimation method used: Lower House Size and Expenditure Per Capita (left) and Lower House Size and Log of Expenditure Per Capita (right).[XXXX DANILO CHECAR]
+
+\begin{figure}[htb!]
+\begin{center}
+\caption{Forest Plots for the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Restricted Sample)}
+\vspace{.3cm}
+\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
+\label{fig:plots2}
+\end{center}
+\end{figure}
+
+Instrumental variables has an interesting variation: from the four coefficients listed, two are positive and two are negative.
+Two of these four coefficients are significant, again one positive and one negative.
+The subgroup analysis present a SMD negative but insignificant.
+When using Regression discontinuity design, the results are uniformily negative.
+From three papers employing the technique on the natural logarithm of expenditure per capita, all find negative and significant effects.
+The number of studies, only three, is not enough to predict an overall negative result, but they point in the direction that better identification suggests a zero-to-negative impact of legislature size on expenditure, in support of the reverse "law of $1/n$".[XXXX DANILO CHECAR]
+
 ## Meta-Regressions
@@
 
-In this section, we run a series of meta-regressions with 5 covariates that may
+In this section, we run a series of meta-regressions with five covariates that may
 account for differences across the selected papers. The first variable indicates
@@
 
-Table \ref{tab:regressions} presents the meta-regression results for our
+Table \ref{tabregressions} presents the meta-regression results for our
 restricted and extended samples. Each column represents one of the three
@@
 
-```latex
-\vspace{.5cm}
+```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
+res <- list()
+
+## Expenditure as percentage GDP -- Restricted
+mod <-  rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = dat$depvar2=='PCTGDP',
+            slab = dat$authoryear)
+
+res[[1]] <- tibble(
+     ` ` = c("Intercept",
+             "Indepvar: N",
+             "Indepvar: logN",
+             "Year",
+             "Elecsys: Non-Majoritarian",
+             "Method: Panel"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
+  model = "PCTGDP"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 4)))
+
+## Expenditure as percentage GDP -- Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = fulldat$depvar2=='PCTGDP',
+            slab = fulldat$authoryear)
+
+res[[2]] <- tibble(
+  ` ` = c("Intercept",
+          "Indepvar: N",
+          "Indepvar: logN",
+          "Year",
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "PCTGDP - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+
+# Expenditure per capita - Restricted
+mod <-  rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = dat$depvar2=='ExpPC',
+            slab = dat$authoryear,
+            control=list(maxiter=1000))
+
+res[[3]] <- tibble(
+  ` ` = c("Intercept",
+          "Indepvar: N",
+          "Year",
+          "Published: No",
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel",
+          "Method: IV"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+
+# Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = fulldat$depvar2=='ExpPC',
+            slab = fulldat$authoryear)
+
+res[[4]] <- tibble(
+  ` ` = c("Intercept",
+          "Indepvar: N",
+          "Year",
+          "Published: No",
+          "Elecsys: Non-Majoritarian",
+          "Method: Panel",
+          "Method: IV"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "ExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+
+# Log of Expenditure per capita - Restricted
+mod <- rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = dat$depvar2=='logExpPC',
+            slab = dat$authoryear)
+
+res[[5]] <- tibble(
+   ` ` = c("Intercept",
+           "Indepvar: N",
+           "Year",
+           "Published: No",
+           "Method: Panel"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4 ), ")"),
+  model = "logExpPC"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+
+# Log of Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ indepvar2+year+published+elecsys2+method,
+              test = "knha",
+            subset = fulldat$depvar2=='logExpPC',
+            slab = fulldat$authoryear)
+
+res[[6]] <- tibble(
+  ` ` = c("Intercept",
+          "Indepvar: N",
+          "Year",
+          "Published: No",
+          "Method: Panel",
+          "Method: RDD"),
+  Estimate = mod[["beta"]],
+  SE = mod[["se"]],
+  `T` = mod[["zval"]],
+  `P-Value` = mod[["pval"]],
+  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
+              round(mod[["ci.ub"]], digits = 4), ")"),
+  model = "logExpPC - All coefs"
+) %>%
+  mutate_if(is.numeric, list(~round(., digits = 3)))
+strep <- function (x) {
+  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
+}
+```
+
+```{=latex}
+\vspace{0.5cm}
 
 \begin{table}[htpb]
-\caption{Meta Regression Results}
-\label{tab:regressions}
+\caption{Meta Regression Results\label{tabregressions}}
 \footnotesize
@@
 \midrule
-Independent Variable: $N$ & -2.307 & -5.347 &  -0.280 &  -0.0577 &-0.009 & 0.003\\
-                          & (1.490)$\dagger$ & (0.929)*** & (0.162) & (0.073) & (0.005)$\dagger$ & (0.005)\\
+Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
+                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
 %
-Independent Variable: log($N$) &  &  &  &  &-0.011& 0.002\\
-                               &  &  &  &  & (0.001) & (0.014)\\
+Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
+                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
 %
-Year & 0.059 & 0.152 &  0.004 &  0.004 &-0.000& -0.000\\
-     & (0.101) & (0.078)* & (0.013) & (0.006) & (0.001) & (0.001)\\
+Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\
+     & (`r round(res[[3]][3,3],3)`)`r strep(res[[3]][3,5])` & (`r round(res[[4]][3,3],3)`)`r strep(res[[4]][3,5])` & (`r round(res[[5]][3,3],3)`)`r strep(res[[5]][3,5])` & (`r round(res[[6]][3,3],3)`)`r strep(res[[6]][3,5])` & (`r round(res[[1]][4,3],3)`)`r strep(res[[1]][4,5])` & (`r round(res[[2]][4,3],3)`)`r strep(res[[2]][4,5])`\\
 %
-Published: No &  &  & 0.200 &  0.103 & 0.0625 & 0.060\\
-              &  &  & (0.127) & (0.065) & (0.014)* & (0.016)*\\
+Published: No & `r round(res[[3]][4,2],3)` & `r round(res[[4]][4,2],3)` & `r round(res[[5]][4,2],3)` &  `r round(res[[6]][4,2],3)` &  & \\
+              & (`r round(res[[3]][4,3],3)`)`r strep(res[[3]][4,5])` & (`r round(res[[4]][4,3],3)`)`r strep(res[[4]][4,5])` & (`r round(res[[5]][4,3],3)`)`r strep(res[[5]][4,5])` & (`r round(res[[6]][4,3],3)`)`r strep(res[[6]][4,5])` &  & \\
 %
-Non-Majoritarian (PR \& Mixed) & 0.428 & 0.985 & &  & -2.055 & -2.169\\
-                               & (0.827) & (0.723)$\dagger$ & &  & (0.283)** & (0.166)***\\
+Non-Majoritarian (PR \& Mixed) & `r round(res[[3]][5,2],3)` & `r round(res[[4]][5,2],3)` & &  & `r round(res[[1]][5,2],3)` & `r round(res[[2]][5,2],3)` \\
+                               & (`r round(res[[3]][5,3],3)`)`r strep(res[[3]][5,5])` & (`r round(res[[4]][5,3],3)`)`r strep(res[[4]][5,5])` & &  & (`r round(res[[1]][5,3],3)`)`r strep(res[[1]][5,5])` & (`r round(res[[2]][5,3],3)`)`r strep(res[[2]][5,5])`\\
 %
-Method: Panel & 1.203 & -0.135 & 0.188 & -0.252 & 0.055 & 0.058\\
-              & (1.575) & (0.797) & (0.093) & (0.068)*** & (0.013)* & (0.017)*\\
+Method: Panel & `r round(res[[3]][6,2],3)` & `r round(res[[4]][6,2],3)` & `r round(res[[5]][5,2],3)` & `r round(res[[6]][5,2],3)` & `r round(res[[1]][6,2],3)` & `r round(res[[2]][6,2],3)`\\
+              & (`r round(res[[3]][6,3],3)`)`r strep(res[[3]][6,5])` & (`r round(res[[4]][6,3],3)`)`r strep(res[[4]][6,5])` & (`r round(res[[5]][5,3],3)`)`r strep(res[[5]][5,5])` & (`r round(res[[6]][5,3],3)`)`r strep(res[[6]][5,5])` & (`r round(res[[1]][6,3],3)`)`r strep(res[[1]][6,5])` & (`r round(res[[2]][6,3],3)`)`r strep(res[[2]][6,5])`\\
 %
-Method: IV & 1.317 & 0.186 &  &  &  & \\
-           & (1.807) & (0.802) &  &  &  & \\
+Method: IV & `r round(res[[3]][7,2],3)` & `r round(res[[4]][7,2],3)` &  &  &  & \\
+           & (`r round(res[[3]][7,3],3)`)`r strep(res[[3]][7,5])` & (`r round(res[[4]][7,3],3)`)`r strep(res[[4]][7,5])` &  &  &  & \\
 %
-Method: RDD &  &  &  &-0.285&  & \\
-            &  &  &  & (0.062)*** &  & \\
+Method: RDD &  &  &  & `r round(res[[6]][6,2],3)` &  & \\
+            &  &  &  & (`r round(res[[6]][6,3],3)`)`r strep(res[[6]][6,5])` &  & \\
 % 
-Intercept & -117.987 & -300.789 & -7.363 & -8.296 & 2.851 & 2.507\\
-          & (203.717) & (157.555)* & (25.458) & (12.037) & (1.778) & (2.467)$\dagger$\\
+Intercept & `r round(res[[3]][1,2],3)` & `r round(res[[4]][1,2],3)` & `r round(res[[5]][1,2], 3)` & `r round(res[[6]][1,2], 3)` & `r round(res[[1]][1,2], 3)` & `r round(res[[2]][1,2], 3)`\\
+          & (`r round(res[[3]][1,3],3)`)`r strep(res[[3]][1,5])` & (`r res[[4]][1,3]`)`r strep(res[[4]][1,5])` & (`r round(res[[5]][1,3],3)`)`r strep(res[[5]][1,5])` & (`r round(res[[6]][1,3],3)`)`r strep(res[[6]][1,5])` & (`r round(res[[1]][1,3],3)`)`r strep(res[[1]][1,5])` & (`r round(res[[2]][1,3],3)`)`r strep(res[[2]][1,5])`\\
 \bottomrule
@@
 \renewcommand{\footnoterule}{}
-\footnotetext{\textbf{Note:} {The restricted and extended samples include 36 and 126 study coefficients, respectively.
+\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively.
 We report the results from the permutation tests.
 Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$.
-Significance codes: *** $p < 0.001$; ** $p < 0.01$; * $p < 0.05$; $\dagger$ $p < 0.1$.}}
+Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
 \end{minipage}
@@
 latter. Moreover, different statistical techniques produce distinctive results,
-which authors should bear in mind.
+with better identified methods (IV and RDD), producing zero and negative effects more frequently.
+
+One may ask why we find no clear-cut evidence in favor or against the theory.
+The theory renders simple and testable empirical regularities in both of its forms, the "law of $1/n$" and the reverse "law of $1/n$." However, the empirical accessment is far from uniform in its findings.
+One reason may be the fact that the academic reward in social sciences for accumulating evidence is small, and most papers add features to their theory and further tests while acessing the "law of $1/n$".
+For instance, in our sample, papers added to the theory supermajority rules [@lee2015supermajority; @lee2016supermajority], redistricting [@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay between upper and lower houses [@chen_malhotra_2007], among others.
+This has the benefit of enriching the original theory with useful details, but has the disadvantage of providing less clear and decisive tests to the "law of $1/n$" theory.
+To solve this problem, we need more direct tests of the theory, preferably using well causally identified techniques, such as regression discontinuity design.
+[XXXX DANILO CHECAR]
 

### 2020-12-03 dataset/datasetBuilding.R

@@ -25,6 +25,7 @@ dat <- data.frame(
   published = 'Yes',
   usemeta = 1,
   method = 'OLS',
+  method2 = 'OLS/PANEL',
   elecsys = 'Maj',
   elecsys2 = 'Maj', elecsys3 = 'M',
   agglevel = 'States',
@@ -58,6 +59,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 1, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -90,6 +92,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 0, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -122,6 +125,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 0, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -154,6 +158,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 0, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -186,6 +191,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 1, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -217,6 +223,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 0, 
                method = 'PANEL',
+               method2 = 'OLS/PANEL',
                elecsys = 'Mixed',
                elecsys2 = 'Non-Maj', elecsys3 = 'NM',
                agglevel = 'Countries',
@@ -248,6 +255,7 @@ dat <- rbind(dat,
                published = 'Yes',
                usemeta = 0, 
                method = 'PANEL',
[…]

### 2020-12-06 appendix/appendix.Rmd
editing the appendix and the manuscript

@@
 
-[^freire]: Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, <danilofreire@brown.edu>, <http://danilofreire.github.io>.
+[^freire]: Independent Researcher, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.
 
@@
 4. Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
-5. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+5. Regarding statistical models, passing from `OLS` to `PANEL` increases the detected effects.
 
@@
 3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
-4. In terms of the modeling, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
+4. Regarding statistical models, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
 
@@
 3. `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
-4. In terms of the modeling, passing from `OLS` to `PANEL` decreases the detected effects.
+4. Regarding statistical models, passing from `OLS` to `PANEL` decreases the detected effects.
 5. All other coeffients were not significant.
@@
 1. Unpublished papers report significantly higher coefficients.
-2. In terms of the modeling, passing from `OLS` to `PANEL` increases the detected effects.
+2. Moving from `OLS` to `PANEL` increases the detected effects.
 3. All other coefficients remained insignificant.
@@
 
-1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
+1. In terms of the modelling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
 2. All other coefficients remained insignificant.
@@
 
-# Robustness: Full Model Meta-Regressions
+# Robustness: Meta-Regressions with Our Complete Sample
 

### 2020-12-06 manuscript/article.Rmd
editing the appendix and the manuscript

@@
 pkgs <- c("tidyverse", "meta", "metafor",
-          "readxl", "compareGroups",
+          "readxl", "data.table",
           "knitr", "gridGraphics", "gridExtra",
@@
 
-# Load packs
+# Load packages
 lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
+devtools::install_github("isubirana/compareGroups")
+library("compareGroups")
 
@@
 Over the past decades, a large literature has examined the relationship between
-legislature size and public expenditure. \citet{weingast1981political} provided
-the general framework to analyse distributive politics. The authors argue that
-the larger the number of legislative districts ($n$), the smaller the share of
-tax burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity.
-However, recent studies have questioned the validity of the "law of $1/n$", as
-the theory is currently known. For instance, spending limits, strong executives,
-and bicameralism may reduce the inefficiency of pork barrel projects
-\citep{bradbury2009spatially,chen_malhotra_2007,primo2006stop}. Moreover,
-\citet{primo2008distributive} affirm that, due to spatial spillovers, a
+legislature size and public expenditure. @weingast1981political provided the
+general framework to analyse distributive politics. The authors argue that the
+larger the number of legislative districts ($n$), the smaller the share of tax
+burden each one will bear ($1/n$), thus legislators have an incentive to
+overspend in their districts and transfer the costs to the entire polity. The
+first studies that assessed the "law of $1/n$", as the theory is currently
+known, mostly found a positive correlation between government spending and the
+number of legislature seats, although the effect was sometimes limited to the
+lower house [e.g., @baqir1999districts; @bradbury2001legislative;
+@gilligan1995deviations]. However, recent studies have questioned the validity
+of the theory. For instance, spending limits or strong executives may reduce
+the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
+Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
 collection of small districts can supply public goods more efficiently than the
@@
 insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
-selected articles, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
+article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
 are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
@@
 assess threats to external validity and direct future efforts into more
-promising areas of academic inquiry \citep{doucouliagos2008democracy}.
+promising areas of academic inquiry [@doucouliagos2008democracy].
 
 In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that use quantitative methods
-to analyse the impact of legislature size over government spending. We run two
-sets of models: the first group uses only the main estimates of each paper (`r dim(dat)[1]`),
-while the second set includes all coefficients reported in our sample
-(`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))` papers in our review, we include `r dim(dat)[1]`
-coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles report
-separate estimates for the impact of lower and upper house size on government
-expenditures. In the full model, we add every outcome reported in the
-papers, regardless of whether the coefficient comes from the main tables or
-from robustness checks conducted by the original authors. We discuss our
-sampling process in the Methods section of this paper and in the Supplementary
-Material.} Our independent variables consist of three measures, namely the size
-of the lower chamber ($n$), its natural logarithm (log($n$)), and the number of
-members in the upper chamber ($k$). We evaluate their effect upon public
-expenditure per capita, the natural logarithm of public expenditure per capita,
-and government expenditure as a percentage of GDP. We then estimate if the
-results vary according to four potential sources of effect heterogeneity.
+the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
+use quantitative methods to assess the impact of legislature size over
+government spending across several dimensions. We run two sets of models: the
+first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
+while the second set includes all coefficients reported in our
+sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
+papers in our review, we include `r dim(dat)[1]`
+coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))`
+articles report separate estimates
+for the impact of lower and upper house size on government expenditures. In the
+full model, we add every outcome reported in the papers, regardless of whether
+the coefficient comes from the main tables or from robustness checks. We
+discuss our sampling process in the Methods section and in the
+Supplementary Material.} Our independent variables consist of three measures,
+namely the size of the lower chamber ($n$), its natural logarithm (log($n$)),
+and the number of members in the upper chamber ($k$). We evaluate their effect
+upon public expenditure per capita, the natural logarithm of public expenditure
+per capita, and government expenditure as a percentage of GDP. We then estimate
+if the results vary according to four potential sources of effect
+heterogeneity.
 
@@
 spending. However, the meta-regressions suggest that our study sample has high
-levels of heterogeneity, and effects differ substantially according to research
-design specifications. Whereas earlier studies employing convention spending
-regressions often find a positive relation between legislature size and
-government budgets, recent studies that use new methods of causal inference,
-specially those with regression discontinuity designs, provide consistent
-evidence for a negative relation. This goes in contrast with the original
-theory and supports the existence of a "reverse law of $1/n$".
-\textbf{Moreover, ...}  In summary, our results point out that if legislature
-size affects government budgets, they do so under specific conditions and are
-mediated by domestic factors.
+levels of heterogeneity, and effects differ substantially according to the
+study design. We find that a reliable predictor of effect size is the research
+method employed in the original paper. While earlier studies that employed
+conventional linear regressions often find a positive relation between
+legislature size and government budgets, recent studies that use new methods of
+causal inference, specially those with regression discontinuity designs,
+provide consistent evidence for a negative relation. This goes in contrast with
+the original theory and supports the existence of a "reverse law of $1/n$".
 
@@
 
-After applying our exclusion criteria, the search produced a dataset of 26
+After applying our exclusion criteria, the search produced a dataset of `r length(unique(dat$id))` 
 studies as of the 21\textsuperscript{st} of November, 2019. Table
@@
 Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
-Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal, OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional representation).
-Country codes follow the ISO 3166-1 alpha-3 international standard.}
-\end{minipage}
+Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
+Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
+OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
+data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
+NM$=$Non-majoritarian (mixed or proportional representation). Country codes
+follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
 \end{longtable}
@@
 latter. Moreover, different statistical techniques produce distinctive results,
-with better identified methods (IV and RDD), producing zero and negative effects more frequently.
-
-One may ask why we find no clear-cut evidence in favor or against the theory.
-The theory renders simple and testable empirical regularities in both of its forms, the "law of $1/n$" and the reverse "law of $1/n$." However, the empirical accessment is far from uniform in its findings.
-One reason may be the fact that the academic reward in social sciences for accumulating evidence is small, and most papers add features to their theory and further tests while acessing the "law of $1/n$".
-For instance, in our sample, papers added to the theory supermajority rules [@lee2015supermajority; @lee2016supermajority], redistricting [@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay between upper and lower houses [@chen_malhotra_2007], among others.
-This has the benefit of enriching the original theory with useful details, but has the disadvantage of providing less clear and decisive tests to the "law of $1/n$" theory.
-To solve this problem, we need more direct tests of the theory, preferably using well causally identified techniques, such as regression discontinuity design.
-[XXXX DANILO CHECAR]
+with better identified methods (IV and RDD), producing zero and negative
+effects more frequently.
+
+One may ask why we find no clear-cut evidence in favour or against the theory.
+Although the literature renders simple and testable empirical regularities in both of its
+forms, the "law of $1/n$" and the reverse "law of $1/n$", the
+empirical assessment is far from uniform in its findings. One reason may be the
+fact that the academic reward in social sciences for accumulating evidence is
+small, and most papers add features to their theory and further tests while
+accessing the "law of $1/n$". For instance, in our sample, papers added to the
+theory supermajority rules [@lee2015supermajority; @lee2016supermajority],
+redistricting [@baqir2002districting; @lee2018court], party ideology
+[@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits
+[@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay
+between upper and lower houses [@chen_malhotra_2007], among others. This has
+the benefit of enriching the original theory with useful details, but has the
+disadvantage of providing less clear and decisive tests to the "law of $1/n$"
+theory. To solve this problem, we need more direct tests of the theory,
+preferably using well causally identified techniques, such as regression
+discontinuity design. [XXXX DANILO CHECAR]
 

### 2020-12-06 appendix/appendix.Rmd
more edits to appendix, change font tikz2pdf

@@
 biblio-style: apalike
+always_allow_html: true
 output:
@@
 
-[^freire]: Independent Researcher, <danilofreire@brown.edu>, <http://danilofreire.github.io>. Corresponding author.
+[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.
 
@@
 
-\newpage
-
 ### Electoral System Subgroup Analysis
@@
 Both are non-significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
-
-\newpage
 
@@
 
-\newpage
-
-## Lower House Size and Log of Expenditure per Capita (RDD Only)
+## Lower House Size and Log of Expenditure per Capita (RDD)
 
@@
 
-\newpage
-
 ### Regression Method Subgroup Analysis
@@
 
-\newpage
-
 # Code for the Main Graphs
@@
 ```
-
-\newpage
 
@@
 
-## Lower House Size and Log of Expenditure per Capita (RDD Only)
+## Lower House Size and Log of Expenditure per Capita (RDD)
 
@@
   kable(booktabs = T,align = "c",linesep ='') %>%
-  kable_styling(c("striped","bordered","scale_down"), position = "center")
+  kable_styling(c("striped","bordered"), position = "center")
 ```
@@
 
-```{r, warning=F, error=F, message=F, cache=T}
-coefs <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Indepvar: logN",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV",
-          "Method: RDD"))
-
-aux <- list(mod3, mod5, mod1) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model))
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
-  filter(` ` != "Method: RDD") %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*",
-                                     ifelse(. >= 0.05, " ",
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~(ifelse(is.na(.), " ", .)))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "Base") %>%
-  select(mod, everything())
-
-aux2 = list(mod4, mod6, mod2) %>%
-  map(~{
-    left_join(coefs, .x) %>%
-      mutate(model = ifelse(is.na(model), model[1], model))
-  }) %>%
-  reduce(bind_cols) %>%
-  mutate(
-         order = ifelse(` ` == "Intercept", 1, NA),
-         order = ifelse(` ` == "Indepvar: N", 2, order),
-         order = ifelse(` ` == "Indepvar: logN", 3, order),
-         order = ifelse(` ` == "Year", 4, order),
-         order = ifelse(` ` == "Published: No", 5, order),
-         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
-         order = ifelse(` ` == "Method: Panel", 7, order),
-         order = ifelse(` ` == "Method: IV", 8, order),
-         order = ifelse(` ` == "Method: RDD", 9, order)) %>%
-  arrange(order) %>%
-  mutate_at(vars(contains("Value")), list(
-    ~(ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
-                       ifelse(. < 0.01, "**",
-                              ifelse(. < 0.05, "*",
-                                     ifelse(. >= 0.05, " ",
-                                            ifelse(is.na(.), " ", .))))))))) %>%
-  mutate_at(vars(contains("Estimate") | contains("SE")),
-            list(~ifelse(is.na(.), " ", .))) %>%
-  select(-` 1`, -` 2`, -contains("model"), -order) %>%
-  mutate(mod = "All Coefs") %>%
-  select(mod, everything())
-
-aux <- bind_rows(aux, aux2) %>%
-  select(-contains("CI"),-`T`,-T1,-T2)
-```
-
-# Robustness: Meta-Regressions with Our Complete Sample
+\newpage
+
+# Robustness: Meta-Regressions (All Coefficients)
 
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 # Session Information

### 2020-12-06 appendix/appendix.Rmd
edit fn2 in the appendix

@@
 One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies.
-In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that the argument for working in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
+In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
 The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}

### 2020-12-06 manuscript/article.Rmd
edit fn2 in the appendix

@@
 burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity. The
-first studies that assessed the "law of $1/n$", as the theory is currently
-known, mostly found a positive correlation between government spending and the
-number of legislature seats, although the effect was sometimes limited to the
-lower house [e.g., @baqir1999districts; @bradbury2001legislative;
-@gilligan1995deviations]. However, recent studies have questioned the validity
-of the theory. For instance, spending limits or strong executives may reduce
-the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
-Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
-collection of small districts can supply public goods more efficiently than the
-central government. The authors conclude that a "reverse law of $1/n$" may
-hold, wherein a higher number of legislators in small constituencies decrease
-the overall public spending.
+overspend in their districts and transfer the costs to the entire polity.
+Most of the early studies which assessed the "law of $1/n$", as the theory is
+currently known, indeed found a positive correlation between the number of
+legislature seats and government spending, although the effect was sometimes
+limited to the lower house [e.g., @baqir1999districts;
+@bradbury2001legislative; @gilligan1995deviations]. However, recent research
+has questioned the validity of the theory. For instance, spending limits or
+strong executives may reduce the inefficiency of pork barrel projects
+[@chen_malhotra_2007; @primo2006stop]. Moreover, @primo2008distributive affirm
+that, due to spatial spillovers, a collection of small districts can supply
+public goods more efficiently than the central government. The authors conclude
+that a "reverse law of $1/n$" may hold, wherein a higher number of legislators
+in small constituencies decrease the overall public spending.
 

### 2020-12-06 appendix/appendix.Rmd
fix typo D5

@@
 
-Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
+Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
 The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`).

### 2020-12-07 appendix/appendix.Rmd
commit 2 12/06

@@
 
-Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`).
-The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`).
-Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`).
-As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.
+Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[2])`).
+The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`).
+Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[3])`).
+As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.
 
@@
             slab = dat$authoryear)
-
-mod1 <- tibble(
-     ` ` = c("Intercept",
-             "Indepvar: N",
-             "Indepvar: logN",
-             "Year",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "PCTGDP"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
 mod
-
-mod1_permu <- tibble(
-     ` ` = c("Intercept",
-             "Indepvar: N",
-             "Indepvar: logN",
-             "Year",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```
@@
             slab = fulldat$authoryear)
-
-mod2 <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Indepvar: logN",
-          "Year",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
 mod
-
-mod2_permu <- tibble(
-     ` ` = c("Intercept",
-             "Indepvar: N",
-             "Indepvar: logN",
-             "Year",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```
@@
             control=list(maxiter=1000))
-
-mod3 <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
 mod
-
-mod3_permu <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```
@@
             slab = fulldat$authoryear)
-
-mod4 <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
 mod
-
-mod4_permu <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```
@@
             slab = dat$authoryear)
-
-mod5 <- tibble(
-   ` ` = c("Intercept",
-           "Indepvar: N",
-           "Year",
-           "Published: No",
-           "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```
@@
 mod
-
-mod5_permu <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-mod5_permu %>%
-  select(-model) %>%
-  kable(booktabs = T,align = "c",linesep ='') %>%
-  kable_styling(c("striped","bordered"), position = "center")
-```
-
-We have the following results for the meta-regressions of Log of Expenditure Per Capita:
-
-1. Unpublished papers report significantly higher coefficients.
-2. Moving from `OLS` to `PANEL` increases the detected effects.
-3. All other coefficients remained insignificant.
+```
+
+Gor the meta-regressions of Log of Expenditure Per Capita we find no significant results.
 
@@
             slab = fulldat$authoryear)
-
-mod6 <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Method: Panel",
-          "Method: RDD"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
 mod <- permutest(mod, progbar = F)
-
-mod6_permu <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Method: Panel",
-          "Method: RDD"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs - Permutation"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
 ```

### 2020-12-07 appendix/appendix.Rmd
WIP

@@
 This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics", which is a seminal contribution in the field.
+To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field.
 Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
@@
 In the first round, we excluded all titles that were clearly unrelated to our topic of interest.
-For instance, we curiously found articles about automobile motors amidst our sample.
+For instance, we curiously found articles about car motors amidst our sample.
 We consider this a preliminary step, since we were not able to eliminate a large number of entries.
@@
 In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended dataset.
-Below is the data extraction process for all relevant coefficients in the selected articles.
 Here we present the results of all tests performed in both reduced and full samples.
@@
 We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.
-We also add a descriptive statistics table similar to the one in the main paper.
 
@@
 
-## Log of Upper House Size and Log of Expenditure Per Capita
+## Upper House Size and Log of Expenditure Per Capita
 
@@
 
-\newpage
-
 # Meta-Regressions
@@
 
-\newpage
-
 # Robustness: Meta-Regressions (All Coefficients)
@@
 
-\newpage
-
 # Session Information

### 2020-12-07 manuscript/article.Rmd
WIP

--- 2020-12-06 manuscript/article.Rmd
@@
 The available evidence also indicates that XXXXXXXXXXXXXXXX"
-abstractspacing: onehalf
+abstractspacing: double
 keywords: distributive politics; law of $1/n$; legislature size; meta-analysis; public spending
 jelcodes: H21; H23; H50; H61
-fontsize: 12pt
+fontsize: 11pt
 margin: 2cm
@@
 burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity. The
-first studies that assessed the "law of $1/n$", as the theory is currently
-known, mostly found a positive correlation between government spending and the
-number of legislature seats, although the effect was sometimes limited to the
-lower house [e.g., @baqir1999districts; @bradbury2001legislative;
-@gilligan1995deviations]. However, recent studies have questioned the validity
-of the theory. For instance, spending limits or strong executives may reduce
-the inefficiency of pork barrel projects [@chen_malhotra_2007; @primo2006stop].
+overspend in their districts and transfer the costs to the entire polity. Most
+early studies that empirically tested the "law of $1/n$", as the theory is
+currently known, indeed found a positive correlation between the number of
+legislature seats and different measures of government spending, although the
+effect was often limited to one house [e.g., @baqir2002districting;
+@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
+questioned the validity of the "law of $1/n$". For instance, spending limits,
+bicameralism, or strong executives may reduce the inefficiency of pork barrel
+projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
 Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
 collection of small districts can supply public goods more efficiently than the
-central government. The authors conclude that a "reverse law of $1/n$" may
-hold, wherein a higher number of legislators in small constituencies decrease
-the overall public spending.
+central government. The authors conclude that a "reverse law of $1/n$" may hold,
+wherein a higher number of legislators in small constituencies decrease the
+overall public spending.
 
 Our survey of the scholarship confirms this continuum of positive,
-insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients included in our
-article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
-are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\% are negative and
-statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 0)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are negative and statistically
-significant. Given this diversity of empirical findings, a systematic review of
-the existing evidence may help us reach a meaningful conclusion about the effect
-of legislature size on public spending. Meta-analysis is the most appropriate
-method for this task. Meta-analysis combines the outcomes of multiple studies
-into a single estimation and allows scholars to draw robust conclusions from the
-aggregated data \citep{cooper2019handbook,hedges1985statistical}. It can also
-identify potential sources of study heterogeneity, enabling researchers to
-assess threats to external validity and direct future efforts into more
-promising areas of academic inquiry [@doucouliagos2008democracy].
+insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
+included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
+them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
+are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
+are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
+negative and statistically significant. Given this diversity of empirical
+findings, a systematic review of the existing evidence may help us reach a
+meaningful conclusion about the effect of legislature size on public spending.
+Meta-analysis is the most appropriate method for this task. Meta-analysis
+combines the outcomes of multiple studies into a single estimation and allows
+scholars to draw robust conclusions from the aggregated data
+[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
+sources of study heterogeneity, enabling researchers to assess threats to
+external validity and direct future efforts into more promising areas of
+academic inquiry [@doucouliagos2008democracy].
 
@@
 sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
-papers in our review, we include `r dim(dat)[1]`
-coefficients in the restricted sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))`
-articles report separate estimates
-for the impact of lower and upper house size on government expenditures. In the
-full model, we add every outcome reported in the papers, regardless of whether
-the coefficient comes from the main tables or from robustness checks. We
-discuss our sampling process in the Methods section and in the
-Supplementary Material.} Our independent variables consist of three measures,
-namely the size of the lower chamber ($n$), its natural logarithm (log($n$)),
-and the number of members in the upper chamber ($k$). We evaluate their effect
-upon public expenditure per capita, the natural logarithm of public expenditure
-per capita, and government expenditure as a percentage of GDP. We then estimate
-if the results vary according to four potential sources of effect
-heterogeneity.
-
-Aggregate results show that council size has no significant impact on public
+papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
+sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
+report separate estimates for the impact of lower and upper house size on 
+government expenditures. In the full model, we add every outcome reported in the 
+papers, regardless of whether the coefficient comes from the main tables or from 
+robustness checks. We discuss our sampling process in the Methods section and in 
+the Supplementary Material.}
+Our independent variables consist of three measures, namely the size of the
+lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
+in the upper chamber ($k$). We evaluate their effect upon public expenditure per
+capita, the natural logarithm of public expenditure per capita, and government
+expenditure as a percentage of GDP. We then estimate if the results vary
+according to four potential sources of effect heterogeneity.
+
+Aggregate results show that legislative size has no significant impact on public
 spending. However, the meta-regressions suggest that our study sample has high
-levels of heterogeneity, and effects differ substantially according to the
-study design. We find that a reliable predictor of effect size is the research
-method employed in the original paper. While earlier studies that employed
-conventional linear regressions often find a positive relation between
-legislature size and government budgets, recent studies that use new methods of
-causal inference, specially those with regression discontinuity designs,
-provide consistent evidence for a negative relation. This goes in contrast with
-the original theory and supports the existence of a "reverse law of $1/n$".
+levels of heterogeneity, and effects differ substantially according to study
+specifications. A reliable predictor of effect size is the research method
+employed in the original paper. While papers that employ conventional linear
+regressions often find a positive relation between legislature size and
+government budgets, recent studies using new methods of causal inference,
+specially those with regression discontinuity designs, provide consistent
+evidence for a negative relation. This goes in contrast with the original theory
+and supports the existence of a "reverse law of $1/n$". Additionally, we find
+that non-majoritarian voting systems decrease government spending as a
+percentage of GDP, which is also evidence against the "law of $1/n$". In
+summary, we do not find support for the theory as originally conceived, and
+causal inference models suggest that larger legislatures are associated with
+lower public spending.
 
@@
 \begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
-\caption{Papers included in the meta-analysis, listed year of appearance}\\
+\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
 \toprule
@@
 \endhead
-```{r, echo = FALSE, results = 'asis'}
+```{r, echo = FALSE, results = 'asis', cache = T}
 build_nams <- function(x) {
@@
 of $1/n$" was first formulated in 1981, the empirical assessment of the theory
-only started a few years later, as dates of publishing range from `r min(dat$year)` to `r max(dat$year)`.
-
+only started a few years later, as dates of publishing range from `r min(dat$year)`
+to `r max(dat$year)`.
 Most studies focus on the United States (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='USA')])`), but our sample also contains
@@
 Five articles use cross-national data and analyse from 2 to 110
-countries.
+countries. Early studies employed OLS and panel data methods to analyse the
+results, whereas the use of regression discontinuity designs is a recent
+addition to the literature, starting in 2012.
 
@@
              show.p.overall = F, show.all = T, all.last = T), 
-  caption = 'Descriptive Statistics of Moderators\\label{tab:descriptive}'
+  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
 )
@@
 between the number of legislators in the lower house and public expenditure 
-(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, $p_{success} = $ `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
+(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
 $p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
 association between both. The binomial test for log($n$) also shows a
-non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, $p_{success} = $ `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
+non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
 $p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
 positive result for the number of legislators in the upper house ($k$), which is
-in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, $p_{success} = $ `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
+in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
 $p$-value = `r round(as.numeric(binK$p.value), 3)`).
@@
 Figure \ref{fig:plots} shows the forest plots for our restricted sample, the one
-which includes only the main `r dim(dat)[1]` coefficients for the `r length(unique(dat$id))` selected papers. On the
-left side of the plots are the name of the study authors and the paper
-publication year. For unpublished studies, we included the first year the paper
-was available online. The bars in the middle show the reported effect sizes and
-the vertical lines indicate their average, weighted by standard errors. The length
-of the lines represent the precision of the estimates. The red line at the
-bottom of the figures displays the aggregate coefficients plus their respective
-confidence intervals.
+which includes only the main `r dim(dat)[1]` coefficients for the 
+`r length(unique(dat$id))` selected papers. On the left side of the plots are 
+the name of the study authors and the paper publication year. For unpublished
+studies, we included the first year the paper was available online. The bars in
+the middle show the reported effect sizes and the vertical lines indicate their
+average, weighted by standard errors. The length of the lines represent the
+precision of the estimates. The red line at the bottom of the figures displays
+the aggregate coefficients plus their respective confidence intervals.
 
@@
 heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
-indicate very high study heterogeneity \citep{higgins2019cochrane}.
+indicate very high study heterogeneity [@higgins2019cochrane].
 
@@
 \begin{center}
-\caption{Forest Plots for the Relationship between Legislature Size and Government Spending (Reduced Sample)}
+\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
 \vspace{.3cm}
@@
 variable. We find a positive correlation between $k$ and expenditure per capita
-and the coefficient is significant at a 10\% level (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
+but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
 = `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
@@
 interval again includes zero. When we run the same analysis in the extended
-sample, we also see a significant coefficient yet a prediction interval that
+sample, we see a significant coefficient for the estimate, yet the prediction interval also
 contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
@@
 
-In a nutshell, we find only weak evidence in favour of the "law of $1/n$".
+In a nutshell, we find no robust evidence in favour of the "law of $1/n$".
 While some models do show a positive and statistically significant result, none
@@
 
-One reason why we have not detected any effects may be the identification strategy used to estimate the effects.
-On the one hand, OLS and Panel data models, require too many controls to make units comparable.
-On the other hand, these techniques are not as credible to estimate the causal effect of legislature size on public expenditures.
-Estimation methods such as Instrumental Variables, and Regression Discontinuity Design make the units comparable by employing natural and quasi-natural experiments.
-Figure \ref{fig:plots2} disentangle the estimation techniques for two models that there is broadly variation in the estimation method used: Lower House Size and Expenditure Per Capita (left) and Lower House Size and Log of Expenditure Per Capita (right).[XXXX DANILO CHECAR]
+One reason why we have not detected any strong effects may be due to the
+identification strategy authors use in their models. On the one hand, OLS and
+panel data models require too many controls to make units comparable, and they
+are also vulnerable to omitted variable bias or post-treatment bias
+[@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
+methods such as instrumental variables and, in particular, regression
+discontinuity designs have become popular because of their internal validity
+[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects for
+two sets of models that employ causal estimation techniques. They measure the
+impact of lower house size on expenditure per capita (left) and on the natural
+logarithm of expenditure per capita (right).
+
+\newpage
 
@@
 \begin{center}
-\caption{Forest Plots for the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Restricted Sample)}
+\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
 \vspace{.3cm}
@@
 
-Instrumental variables has an interesting variation: from the four coefficients listed, two are positive and two are negative.
-Two of these four coefficients are significant, again one positive and one negative.
-The subgroup analysis present a SMD negative but insignificant.
-When using Regression discontinuity design, the results are uniformily negative.
-From three papers employing the technique on the natural logarithm of expenditure per capita, all find negative and significant effects.
-The number of studies, only three, is not enough to predict an overall negative result, but they point in the direction that better identification suggests a zero-to-negative impact of legislature size on expenditure, in support of the reverse "law of $1/n$".[XXXX DANILO CHECAR]
+Papers that employed instrumental variables show an interesting variation: out
+of the four coefficients listed, two are positive and two are negative. Two of
+these four coefficients are significant, again one positive and one negative.
+The subgroup analysis presents a SMD which is negative but insignificant. In
+contrast, all papers that use regression discontinuity designs show negative and
+statistically significant results. Since only three papers in our sample use
+RDDs, we are cautious about predicting an overall negative relation, but they do
+indicate that better identification strategies yield a zero-to-negative impact
+of legislature size on expenditure, in support of the reverse "law of $1/n$".
 
@@
 
-In this section, we run a series of meta-regressions with five covariates that may
+In this section, we run a series of meta-regressions with covariates that may
 account for differences across the selected papers. The first variable indicates
@@
 
-The first two models show the results for public expenditure per capita. In both
-the restricted and the extended samples, we find that models that use $n$ as an
-independent variable tend to detect significantly smaller effects when compared
-to $k$. This suggests that an additional member in the lower house has a smaller
-impact on public spending than a member in the upper house. Moreover, the
-results for the extended sample point out that recent studies find larger
-effects than older ones, and that changing the electoral rules from majoritarian
-to non-majoritarian increases the effects of legislature size on per capita
-expenditure.
-
-The third and fourth columns use the logarithm of expenditure per capita as the
-dependent variable. No covariate is statistically significant in our smaller
-sample, but two moderators are negatively associated with the outcome in our
-larger study pool. They both refer to estimation methods. Studies that employ
-panel/fixed effects or regression discontinuity designs (RDDs) have lower
+The first two models show the results for public expenditure per capita. No
+variable reaches conventional levels of statistical significance in the
+restricted sample. In the extended sample, we find that models that use $n$ as
+an independent variable tend to detect significantly smaller effects when
+compared to $k$. This suggests that an additional member in the lower house has
+a smaller impact on public spending than a member in the upper house. Moreover,
+the results for the extended sample point out that recent studies find larger
+effects than older ones.
+
+The third and fourth columns use the natural logarithm of expenditure per capita
+as the dependent variable. None of the covariates are statistically significant in our
+smaller sample, but two moderators are negatively associated with the outcome in
+our larger study pool. They both refer to estimation methods. Studies that
+employ panel/fixed effects or regression discontinuity designs (RDDs) have lower
 coefficients for log expenditure per capita if we take OLS as the reference
@@
 
-Several variables are statistically significant in the last set of
-meta-regressions. The dependent variable is public expenditures as a percentage
-of GDP. In our restricted sample, we see that studies with $n$ as an
+Two variables are statistically significant in the last set of
+meta-regressions, which include public expenditures as a percentage
+of GDP as the dependent variable. Both in our restricted and in our extended
+samples, we see that newer studies have smaller coefficients than early ones,
+
+studies with $n$ as an
 independent variable have lower coefficients than those that analyse $k$, what
@@
 In this article, we assess the empirical validity of the "law of $1/n$". Based
-on a sample of `r length(unique(dat$id))` recent publications on the topic, our meta-analyses show that
-there is little evidence that an increase in the number of legislators has a
-significant effect on public expenditures. If such effect exists, it is likely
-driven by an increase in $k$, the size of the upper legislature, as suggested
-by several studies in the literature \citep[e.g.,][]{baqir2002districting,
-bradbury2001legislative, bradbury2003local, chen_malhotra_2007,
-gilligan2001fiscal, primo2006stop}. We find no robust evidence for the "reverse
-law of $1/n$", which posits that larger legislatures lead to lower government
-spending. One possible explanation is that the two logics are balancing each
-other, thus leading us to a null impact of legislature size on public
-expenditure.
+on a sample of `r length(unique(dat$id))` recent publications on the topic, our
+meta-analyses show that there is little evidence that an increase in the number
+of legislators has a significant effect on public expenditures. If such effect
+exists, it is likely driven by an increase in $k$, the size of the upper
+legislature, as suggested by several studies in the literature
+\citep[e.g.,][]{baqir2002districting, bradbury2001legislative,
+bradbury2003local, chen_malhotra_2007, gilligan2001fiscal, primo2006stop}. We
+find no robust evidence for the "reverse law of $1/n$", which posits that larger
+legislatures lead to lower government spending. One possible explanation is that
+the two logics are balancing each other, thus leading us to a null impact of
+legislature size on public expenditure.
 

### 2020-12-07 article/article.Rmd
add edits to article, clean up repo

--- 2020-12-07 manuscript/article.Rmd
@@
 abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures.
-Their proposition is currently known as the law of $1/n$ and has been widely debated in political science and public administration.
+Their proposition is currently known as the \"law of $1/n$\" and has been widely debated in political science and public administration.
 However, recent studies have questioned the validity of the theory.
 In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending.
-Based on a sample of 29 articles, we find only mixed evidence for the effect of legislature size on government budgets.
-Yet the aggregate results mask important differences.
-While earlier, non-causal studies provide moderate support for the law of $1/n$, recent papers using causal inference methods consistently find a negative relation between seats and spending, suggesting that previous results might have been driven by spurious correlations or omitted variable bias.
-The available evidence also indicates that XXXXXXXXXXXXXXXX"
+Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets.
+Yet the aggregate results show significant heterogeneity.
+While earlier studies provide moderate support for the \"law of $1/n$\", papers using modern causal inference methods consistently find a negative relationship between seats and spending.
+The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
 abstractspacing: double
@@
 that non-majoritarian voting systems decrease government spending as a
-percentage of GDP, which is also evidence against the "law of $1/n$". In
-summary, we do not find support for the theory as originally conceived, and
-causal inference models suggest that larger legislatures are associated with
-lower public spending.
+percentage of GDP, which is also evidence against the theoretical expectations
+of the "law of $1/n$". In summary, we do not find support for the theory as
+originally conceived, and causal inference models suggest that larger
+legislatures are associated with lower public spending.
 
@@
 
+\footnotesize
 \begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
@@
 \end{longtable}
+
+\normalsize
 
@@
 restricted sample. In the extended sample, we find that models that use $n$ as
-an independent variable tend to detect significantly smaller effects when
+an independent variable have lower effects when
 compared to $k$. This suggests that an additional member in the lower house has
@@
 
-Two variables are statistically significant in the last set of
-meta-regressions, which include public expenditures as a percentage
-of GDP as the dependent variable. Both in our restricted and in our extended
-samples, we see that newer studies have smaller coefficients than early ones,
-
-studies with $n$ as an
-independent variable have lower coefficients than those that analyse $k$, what
-is consistent with our previous models. Both models also show that unpublished
-papers tend to have higher coefficients than published papers. Regarding the
-electoral systems, see that passing from majoritarian to non-majoritarian
-decrease overall levels of public spending. Finally, we find that models
-estimated with panel data have larger values than those modelled with OLS.
+Two variables are statistically significant in the last set of meta-regressions,
+which include public expenditures as a percentage of GDP as the dependent
+variable. Both in our restricted and in our extended samples, recent studies
+have smaller coefficients than early papers, which stands in contrast with
+our previous models. Non-majoritarian voting systems are also
+associated with lower levels of public spending, what is against the theoretical
+expectations of the "law of $1/n$". The results, however, do not replicate in
+the first set of estimations.
 
 Overall, our results suggest that study coefficients are highly sensitive to
-research design choices. The same statistical methods or study samples may
-produce different outcomes depending on the response variables scholars decide
-to analyse. Moreover, we find evidence that results vary considerably if the
-study employs different measures of legislature size. The impact of factors such
-as the electoral system or year of publication also appear to be conditional on
-the selected model.
+research design choices. The same study samples may produce different outcomes
+depending on the response variables scholars decide to analyse. Moreover, we
+find evidence that results vary considerably if the study employs different
+measures of legislature size or use causal research methods. The impact of
+factors such as the electoral system or year of publication also appear to be
+conditional on the selected model.
 
@@
 In this article, we assess the empirical validity of the "law of $1/n$". Based
-on a sample of `r length(unique(dat$id))` recent publications on the topic, our
-meta-analyses show that there is little evidence that an increase in the number
-of legislators has a significant effect on public expenditures. If such effect
-exists, it is likely driven by an increase in $k$, the size of the upper
+on a sample of `r length(unique(dat$id))` publications on the topic, our
+meta-analyses show that there is no strong evidence that an increase in the
+number of legislators has a significant effect on public expenditures. If such
+effect exists, it is likely driven by an increase in $k$, the size of the upper
 legislature, as suggested by several studies in the literature
-\citep[e.g.,][]{baqir2002districting, bradbury2001legislative,
-bradbury2003local, chen_malhotra_2007, gilligan2001fiscal, primo2006stop}. We
-find no robust evidence for the "reverse law of $1/n$", which posits that larger
-legislatures lead to lower government spending. One possible explanation is that
-the two logics are balancing each other, thus leading us to a null impact of
-legislature size on public expenditure.
-
-The meta-regressions indicate that study characteristics have a large influence
-on reported results. It is unclear whether factors such as the electoral system
-or the level of data aggregation, both believed to moderate the relationship
-between legislature size and public expenditure \citep{primo2008distributive,
-baqir2002districting, bradbury2003local}, have a substantial impact on the
-estimates. We find conflicting evidence for the former and no support for the
-latter. Moreover, different statistical techniques produce distinctive results,
-with better identified methods (IV and RDD), producing zero and negative
-effects more frequently.
-
-One may ask why we find no clear-cut evidence in favour or against the theory.
-Although the literature renders simple and testable empirical regularities in both of its
-forms, the "law of $1/n$" and the reverse "law of $1/n$", the
-empirical assessment is far from uniform in its findings. One reason may be the
-fact that the academic reward in social sciences for accumulating evidence is
-small, and most papers add features to their theory and further tests while
-accessing the "law of $1/n$". For instance, in our sample, papers added to the
-theory supermajority rules [@lee2015supermajority; @lee2016supermajority],
-redistricting [@baqir2002districting; @lee2018court], party ideology
-[@bjedov2014impact], coalition sizes [@baskaran2013coalition], term limits
-[@erler2007termlimits], bicameralism [@ricciuti2004legislature], the interplay
-between upper and lower houses [@chen_malhotra_2007], among others. This has
-the benefit of enriching the original theory with useful details, but has the
-disadvantage of providing less clear and decisive tests to the "law of $1/n$"
-theory. To solve this problem, we need more direct tests of the theory,
-preferably using well causally identified techniques, such as regression
-discontinuity design. [XXXX DANILO CHECAR]
-
-Our analyses suggest three areas for further research. First, our study sample
-did not include articles that evaluate the association between the log($n$) and
-public expenditure per capita or between $k$ and log expenditure per capita.
-New work on that area might clarify some of the inconsistencies we find
-here. Second, despite the inclusion of several moderators in our models,
-aggregate results still show considerable heterogeneity. That is, much of the
-disparities among studies are yet to be explained. Domestic factors such as
-party dynamics or gerrymandering \citep{lee2015supermajority,
-mukherjee2003politicalparties, gilligan2006public} may prove useful in this
-regard. Finally, we highlight the need for more evidence in favour or against
-the "law of $1/n$" to inform general public policies. The available empirical
-evidence points out that contextual variables may either amplify or reduce the
-impact of larger legislatures on government budgets. They should be taken into
-account if policy-makers want to reach an optimal balance between sound fiscal
-policy and the demands for increased political representation.
+[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
+@chen_malhotra_2007; @gilligan2001fiscal; @primo2006stop]. Instead, we find
+better evidence for the "reverse law of $1/n$", which posits that larger
+legislatures lead to lower government spending. This is mainly because studies
+using regression discontinuity designs, a method that has robust internal
+validity, consistently indicate a negative relationship between lower house size
+and the logarithm of expenditure per capita [@hohmann2017effect;
+@lewis2019legislature; @petterssonlidbom2012size].
+
+The meta-regressions indicate that study characteristics have a considerable
+influence on reported results. Factors such as the electoral system affects the
+relationship between legislature size and public expenditure, but the results
+are not replicable in all estimations. Publication year also produces
+conflicting findings in our models. Nevertheless, the meta-regressions confirm
+that RDDs produce negative effects more frequently than OLS regressions.
+
+Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
+plausible reason may be that there are few incentives for the pure accumulation
+of knowledge in the social sciences, at least when compared to the benefits
+scholars may accrue when they challenge or add features to existing theories
+[@geddes2003paradigms]. This leads to a reduced number of replication studies in
+the field, although we have seen some positive changes in this respect, such as
+EGAP's _Metaketa Initiative_.\footnote{See
+\url{https://egap.org/our-work/the-metaketa-initiative} for further
+information.} For instance, in our sample, papers added supermajority rules
+[@lee2015supermajority; @lee2016supermajority], redistricting
+[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
+coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
+bicameralism [@ricciuti2004legislature], and the interplay between upper and
+lower houses [@chen_malhotra_2007] to the main theory, but a comprehensive
+procedural replication of the findings using different samples is yet to be
+written. The addition of new features has the benefit of enriching the original
+theory with useful details, although it has the disadvantage of not providing a
+conclusive test to the "law of $1/n$".
+
+Our analyses suggest three areas for further research. First, our study
+sample did not include articles that evaluate the association between the
+log($n$) and public expenditure per capita or between $k$ and log expenditure
+per capita. New work on that area might clarify some of the inconsistencies we
+find here. Second, despite the inclusion of several moderators in our models,
+aggregate results still show considerable heterogeneity. Domestic factors such
+as party dynamics or gerrymandering [@lee2015supermajority;
+@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
+regard. Finally, we highlight the need for more causal inference studies in the
+literature. Whenever possible, authors should leverage natural and
+quasi-experiments to assess whether the current results hold when tested with
+such research designs. These suggestions may help scholars and policy-makers to
+reach an optimal balance between sound fiscal policy and the demands for
+increased political representation.
 

### 2020-12-07 appendix/appendix.Rmd
small edits to appendix and readme

@@
 
-Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenduture per capita.
+Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenditure per capita.
 To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
@@
 The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are non-significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
+Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
 
@@
 
-## Meta-Regressions for the Log of Expenditure Per Capita
+## Meta-Regressions for Log of Expenditure Per Capita
 
@@
 
-Gor the meta-regressions of Log of Expenditure Per Capita we find no significant results.
+For the meta-regressions of Log of Expenditure Per Capita we find no significant results.
 

### 2020-12-08 appendix/appendix.Rmd
Changes in appendix chunk sizes and typos.

@@
 knitr::opts_chunk$set(echo = TRUE)
+def.chunk.hook  <- knitr::knit_hooks$get("chunk")
+knitr::knit_hooks$set(chunk = function(x, options) {
+  x <- def.chunk.hook(x, options)
+  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
+})
 ```
@@
 
-The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility.
+The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility.
 Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information.
@@
   + *PCTGDP*: Percent GDP Public Expenditure
+
+If a paper did not use a combination of these variables, we excluded it from the meta-analysis.
 
@@
 
-```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
+```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize"}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", cache=TRUE}
 dat %>%
@@
 
-```{r, cache=TRUE, fig.width=5, fig.height=4}
+```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4}
 dat %>%
@@
 
-```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
+```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
 dat %>%
@@
 
-```{r, warning=F,message=F, cache=TRUE}
+```{r, size="footnotesize", warning=F,message=F, cache=TRUE}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 aux <- filter(dat, indepvar2 == "N")
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 aux <- filter(dat, indepvar2 == "logN")
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 aux <- filter(dat, indepvar2=='K')
@@
 
-```{r, cache=TRUE}
+```{r, cache=TRUE, size="footnotesize"}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- PCTGDP x N
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- PCTGDP x logN
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- PCTGDP x K
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- ExpPC x N (IV only)
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- logExpPC x N (RDD only)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x N
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x logN
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x K
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T}
 mod <-  rma(yi = coef,
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T}
 mod <- permutest(mod, progbar = F)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T}
 mod <- rma(yi = coef,
@@
 
-```{r, error=F, warning=F, cache=T}
+```{r, size="footnotesize", error=F, warning=F, cache=T}
 mod <-  rma(yi = coef,
@@
 
-```{r, error=F, warning=F, cache=T}
+```{r, size="footnotesize", error=F, warning=F, cache=T}
 mod <- permutest(mod, progbar = F)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T}
 mod <- permutest(mod, progbar = F, iter = 100)
@@
             slab = dat$authoryear)
-```
-
-```{r, warning=F, cache=T}
 summary(mod)
@@
               test = "knha")
-```
-
-```{r}
 summary(mod)
@@
 
-```{r, cache=T}
+```{r, size="footnotesize", cache=T}
 permutest(mod, progbar = F)
@@
               test = "knha")
-```
-
-```{r, cache=T}
 summary(mod)
@@
 
-```{r, eval = FALSE, cache=T}
+```{r, size="footnotesize", eval = FALSE, cache=T}
 # Build plot function for forest plots
@@
 
-```{r, eval = FALSE, cache=T}
+```{r, size="footnotesize", eval = FALSE, cache=T}
 # Required packages
@@
 
-```{r}
+```{r, size="footnotesize"}
 sessionInfo()

### 2020-12-08 article/article.Rmd
final revision

@@
 Yet the aggregate results show significant heterogeneity.
-While earlier studies provide moderate support for the \"law of $1/n$\", papers using modern causal inference methods consistently find a negative relationship between seats and spending.
+While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending.
 The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
@@
 
-Aggregate results show that legislative size has no significant impact on public
-spending. However, the meta-regressions suggest that our study sample has high
-levels of heterogeneity, and effects differ substantially according to study
-specifications. A reliable predictor of effect size is the research method
-employed in the original paper. While papers that employ conventional linear
-regressions often find a positive relation between legislature size and
-government budgets, recent studies using new methods of causal inference,
-specially those with regression discontinuity designs, provide consistent
-evidence for a negative relation. This goes in contrast with the original theory
-and supports the existence of a "reverse law of $1/n$". Additionally, we find
-that non-majoritarian voting systems decrease government spending as a
-percentage of GDP, which is also evidence against the theoretical expectations
-of the "law of $1/n$". In summary, we do not find support for the theory as
-originally conceived, and causal inference models suggest that larger
-legislatures are associated with lower public spending.
+Aggregate results show that legislative size has no significant impact on
+public spending. However, the meta-regressions suggest that our study sample
+has high levels of heterogeneity, and effects differ substantially according to
+study specifications. We find that one reliable predictor of effect size is the
+research method employed in the original paper. While papers that employ
+conventional linear regressions often find a positive relation between
+legislature size and government budgets, recent studies using modern methods of
+causal inference, specially those with regression discontinuity designs,
+provide consistent evidence for a negative relation. This goes in contrast with
+the original theory and supports the existence of a "reverse law of $1/n$".
+Additionally, we find that non-majoritarian voting systems decrease government
+spending as a percentage of GDP, which is also evidence against the theoretical
+expectations of the "law of $1/n$", and they do not have a relevant impact on
+the other measures of public expenditure. In summary, our analysis does not
+provide robust support for the theory as originally conceived, and causal
+inference models suggest that larger legislatures are associated with lower
+public spending.
 
@@
 
-We collected the study sample using three criteria. First, the study should cite
-\citet{weingast1981political} as their work is foundational to the distributive
-politics literature. Second, the study had to use quantitative methods to
-estimate the relationship between our variables of interest.\footnote{As
-meta-analysis requires a single estimate per observation, we excluded articles
-that use interaction terms or quadratic specifications of our independent
-variables.} Third, the study should be written in the English language. We
-conducted a primary search using Scopus, Microsoft Academic, and Google Scholar,
-three large academic databases.\footnote{See the Supplementary Material for code.}
-
-After applying our exclusion criteria, the search produced a dataset of `r length(unique(dat$id))` 
-studies as of the 21\textsuperscript{st} of November, 2019. Table
-\ref{tab:papers} contains the full list of articles from which we drew data. A
-PRISMA\footnote{The Preferred Reporting Items for Systematic Reviews and
-  Meta-Analyses (PRISMA) statement provides a checklist designed to improve the
-quality and transparency of study selection processes in meta-analyses. For more
-information on the PRISMA framework, see \citet{liberati2009prisma}.} flow
-diagram showing the number of resulting papers after each review step is
-available in the Supplementary Material.
+We collected the study sample using three criteria. First, the study should
+cite \citet{weingast1981political} as their work is foundational to the
+distributive politics literature. Second, the study had to use quantitative
+methods to estimate the relationship between our variables of
+interest.\footnote{As meta-analysis requires a single estimate per observation,
+we excluded articles that use interaction terms or quadratic specifications of
+our independent variables.} Third, the study should be written in the English
+language. We conducted a primary search using Scopus, Microsoft Academic, and
+Google Scholar, three large academic databases.\footnote{See the Supplementary
+Material for code.}
+
+After applying our exclusion criteria, the search produced a dataset of 
+`r length(unique(dat$id))` studies as of the 21\textsuperscript{st} of November,
+2019. Table \ref{tab:papers} contains the full list of articles from which we
+drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
+Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
+to improve the quality and transparency of study selection processes in
+meta-analyses. For more information on the PRISMA framework, see
+\citet{liberati2009prisma}.} flow diagram showing the number of resulting
+papers after each review step is available in the Supplementary Material.
 
@@
 Five articles use cross-national data and analyse from 2 to 110
-countries. Early studies employed OLS and panel data methods to analyse the
+countries. Early studies used OLS and panel data methods to estimate the
 results, whereas the use of regression discontinuity designs is a recent
-addition to the literature, starting in 2012.
+addition to the literature, as the first paper to apply it was published in 2012.
 
@@
 relationship. First, we run a binomial one-proportion z-test to determine
-whether the study coefficients have a positive or negative sign. Then, we fit 7
+whether the study coefficients have a positive or negative sign. Then, we fit 9
 random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
@@
 the article pool. Our sample includes no papers that analyse the relationships
-between log($n$), and public expenditure per capita and between $k$ and the
+between log($n$) and public expenditure per capita or between $k$ and the
 logarithm of public expenditure per capita.
-
-Figure \ref{fig:plots} shows the forest plots for our restricted sample, the one
-which includes only the main `r dim(dat)[1]` coefficients for the 
-`r length(unique(dat$id))` selected papers. On the left side of the plots are 
-the name of the study authors and the paper publication year. For unpublished
-studies, we included the first year the paper was available online. The bars in
-the middle show the reported effect sizes and the vertical lines indicate their
-average, weighted by standard errors. The length of the lines represent the
-precision of the estimates. The red line at the bottom of the figures displays
-the aggregate coefficients plus their respective confidence intervals.
 
@@
 
+\begin{landscape}
+\begin{figure}[htb]
+\begin{center}
+\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
+\vspace{.3cm}
+\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
+\label{fig:plots}
+\end{center}
+\end{figure}
+\end{landscape}
+
+Figure \ref{fig:plots} shows the forest plots for our restricted sample,
+which includes only the `r dim(dat)[1]` main coefficients of the 
+`r length(unique(dat$id))` selected papers. On the left side of the plots are 
+the name of the study authors and the paper publication year. For unpublished
+studies, we included the first year the paper was available online. The bars in
+the middle show the reported effect sizes and the vertical lines indicate their
+average, weighted by standard errors. The length of the lines represent the
+precision of the estimates. The red line at the bottom of the figures displays
+the aggregate coefficients plus their respective confidence intervals.
+
 The first column of the graph reports the results for $n$, lower chamber size.
@@
 
-\begin{landscape}
-\begin{figure}[p]
-\begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
-\vspace{.3cm}
-\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
-\label{fig:plots}
-\end{center}
-\end{figure}
-\end{landscape}
-
 Next, we present the meta-analyses using log($n$), the logarithm of lower house
@@
 
-In a nutshell, we find no robust evidence in favour of the "law of $1/n$".
+In a nutshell, we do not find strong evidence in favour of the "law of $1/n$".
 While some models do show a positive and statistically significant result, none
@@
 panel data models require too many controls to make units comparable, and they
-are also vulnerable to omitted variable bias or post-treatment bias
+are vulnerable to omitted variable bias or post-treatment bias
 [@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
-methods such as instrumental variables and, in particular, regression
-discontinuity designs have become popular because of their internal validity
-[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects for
-two sets of models that employ causal estimation techniques. They measure the
-impact of lower house size on expenditure per capita (left) and on the natural
-logarithm of expenditure per capita (right).
-
-\newpage
-
-\begin{figure}[htb!]
+methods such as instrumental variables and regression discontinuity designs
+have become popular because of their high internal validity
+[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects
+for two sets of models that employ causal estimation techniques. They measure
+the impact of lower house size on expenditure per capita (left) and on the
+natural logarithm of expenditure per capita (right).
+
+\vspace{.06cm}
+
+\begin{figure}[htb]
 \begin{center}
@@
 \vspace{.3cm}
-\includegraphics[width=1\linewidth]{../graphs/graph2.pdf}
+\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
 \label{fig:plots2}
@@
 
-Papers that employed instrumental variables show an interesting variation: out
+\newpage
+
+Papers that employed instrumental variables show some interesting variation: out
 of the four coefficients listed, two are positive and two are negative. Two of
@@
 OLS, or regression discontinuity design).
-
-Table \ref{tabregressions} presents the meta-regression results for our
-restricted and extended samples. Each column represents one of the three
-measures of public spending we discuss in this paper. To reduce the risk of
-false positives in our analyses, we use permutation tests to calculate
-significance levels for the meta-regressions \citep{higgins2004controlling}.
 
@@
 
+\newpage
+
+Table \ref{tabregressions} presents the meta-regression results for our
+restricted and extended samples. Each column represents one of the three
+measures of public spending we discuss in this paper. To reduce the risk of
+false positives in our analyses, we use permutation tests to calculate
+significance levels for the meta-regressions \citep{higgins2004controlling}.
+
 The first two models show the results for public expenditure per capita. No
@@
 
-The meta-regressions indicate that study characteristics have a considerable
-influence on reported results. Factors such as the electoral system affects the
-relationship between legislature size and public expenditure, but the results
-are not replicable in all estimations. Publication year also produces
-conflicting findings in our models. Nevertheless, the meta-regressions confirm
-that RDDs produce negative effects more frequently than OLS regressions.
+The meta-regressions show that study characteristics have a considerable
+influence on reported results. Electoral system affects the relationship
+between legislature size and public expenditure, but the results are not
+replicable in all estimations. Publication year generates conflicting findings
+in our models. Nevertheless, the meta-regressions confirm that RDDs produce
+negative effects more frequently than OLS regressions.
 

### 2021-03-13 dataset/datasetBuilding.R
change dataset new papers

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Nov 10, 2020                                  ##
+## Last Modified: MAr 12, 2021                                  ##
 ##################################################################
 
 # Needed packages
@@ -4617,6 +4617,74 @@ dat <- rbind(dat,
                scoef = 'N',
                scoefsig = 'N',
                SE = 1.314
+             ))
+
+# Paper A258
+dat <- rbind(dat,
+             data.frame(
+               id = 'A258',
+               published = 'Yes',
+               usemeta = 1, 
+               method = 'PANEL',
+               method2 = 'OLS/PANEL',
+               elecsys = 'Maj',
+               elecsys2 = 'Maj', 
+               elecsys3 = 'M',
+               agglevel = 'Local',
+               location = 'US',
+               locationISO = 'USA',
+               title = 'Government Form and Public Spending: Theory and Evidence from US Municipalities',
+               author = 'Coate and Knight',
+               authorCite = 'S. Coate & B. Knight',
+               year = 2011,
+               authoryear = 'Coate and Knight (2011)',
+               journal = 'American Economic Journal: Economic Policy',
+               journalCode = 'AEJ',
+               web = 'https://www.aeaweb.org/articles?id=10.1257/pol.3.3.82',
+               table = 4,
+               column = 2,
+               indepvar = 'Log Council Size',
+               indepvar2 = 'logN',
+               depvar = 'Log Public Spending Per Capita',
+               depvar2 = 'logExpPC',
+               coef = 0.1716,
+               scoef = 'P',
+               scoefsig = 'P',
+               SE = 0.0427
+             ))
+
+# Paper A117
+dat <- rbind(dat,
+             data.frame(
+               id = 'A117',
+               published = 'No',
+               usemeta = 1, 
+               method = 'RDD',
+               method2 = 'RDD',
+               elecsys = 'Mixed',
+               elecsys2 = 'Non-Maj', 
+               elecsys3 = 'NM',
+               agglevel = 'Local',
+               location = 'Italy',
+               locationISO = 'ITA',
+               title = 'The Effect of Council Size on Municipal Expenditures: Evidence from Italian Municipalities',
+               author = 'De Benedetto',
+               authorCite = 'M. De Benedetto',
+               year = 2018,
[…]

### 2021-03-13 dataset/datasetBuilding.R
change dataset

@@ -4722,4 +4722,3 @@ dat <- dat %>%
 
 ## Saving
 save.image('./dataset/dataCoefs.RData')
-

### 2021-03-13 appendix/appendix.Rmd
not display r code appendix

--- 2020-12-07 appendix/appendix.Rmd
@@
 
-[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Getulio Vargas Foundation, Brazil, <huzeyfealptekin@gmail.com>.
-
-[^freire]: Independent Researcher, <danilofreire@gmail.com>, <http://danilofreire.github.io>. Corresponding author.
-
-[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
-
-[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil, <catarinamroman@gmail.com>.
-
 ```{r, include=FALSE}
@@
 This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field.
+To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "*The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics*", which is a seminal contribution to the field.
 Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
@@
 1.  Matched treatment variable:
-  + *N*: Number Legislators in the Lower House
-  + *logN*: Log Number Legislators in the Lower House
-  + *K*: Number Legislators in the Upper House
+
+-   *N*: Number Legislators in the Lower House
+-   *logN*: Log Number Legislators in the Lower House
+-   *K*: Number Legislators in the Upper House
 
 2.  Matched outcome variable:
-  + *ExpPC*: Expenditure Per Capita
-  + *logExpPC*: Log Expenditure Per Capita
-  + *PCTGDP*: Percent GDP Public Expenditure
+
+-   *ExpPC*: Expenditure Per Capita
+-   *logExpPC*: Log Expenditure Per Capita
+-   *PCTGDP*: Percent GDP Public Expenditure
+
+If a paper did not use a combination of these variables, we excluded it from the meta-analysis.
 
@@
 The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`.
-Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the _law of 1/n_.
-
-```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE}
+Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.
+
+```{r, fig.width=7, fig.height=3, fig.cap="Study Year Frequencies", cache=TRUE, size="footnotesize", echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 Our sample differs considerably in regards to research design.
-One remarkable difference is that several authors apply the logics of the _law of 1/n_, which was built with majoritarian systems in mind, to non-majoritarian democracies.
+One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies.
 In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", cache=TRUE}
+```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
 dat %>%
@@
 
-```{r, cache=TRUE, fig.width=5, fig.height=4}
+```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
 dat %>%
@@
 
-One simple statistic that we can compute to assess the validity of the _law of 1/n_ is the frequency of positive and negative estimates in the study sample.
+One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample.
 Below we plot the frequency for all the papers included in the meta-analytic dataset.
 
-```{r, fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE}
+```{r, size="footnotesize", fig.width=5, fig.height=4, fig.cap="Coefficient Sign", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, warning=F,message=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, message=F, echo = FALSE, cache=TRUE}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
@@
 
-The _law of 1/n_ posits that we should expect a positive influence of legislature size on public expenditures.
+The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures.
 A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations.
@@
 As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign.
-The _law of 1/n_ can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
+The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
 The null hypothesis for such a test is that:
@@
 
-As we are taking an agnostic approach, we acknowledge that either the _law of 1/n_ ($p>0.5$), or the _reverse law of 1/n_ ($p<0.5$) could be true.
+As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) could be true.
 In this case, the alternative hypothesis is $p\neq 0.5$.
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 aux <- filter(dat, indepvar2 == "N")
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 aux <- filter(dat, indepvar2 == "logN")
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 aux <- filter(dat, indepvar2=='K')
@@
 In this paper, we use the random effects model.
-The empirical papers testing the _law of 1/n_ are very diverse.
+The empirical papers testing the *law of 1/n* are very diverse.
 We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
@@
 
-\[
+$$
 T_i \ = \ \theta_i + \varepsilon_i
-\]
+$$
 
@@
 
-\[
+$$
 T_i \ = \ \mu + \xi_i + \varepsilon_i
-\]
+$$
 
@@
 
-```{r, cache=TRUE}
+```{r, cache=TRUE, echo = FALSE, size="footnotesize"}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F, warning=F, cache=TRUE, echo = FALSE}
 f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
@@
 
-The _law of 1/n_ was created for majoritarian systems.
+The *law of 1/n* was created for majoritarian systems.
 In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F}
+```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
+build_forest(mod, NULL)
+```
+
+```{r, include=FALSE, warning=FALSE, echo = FALSE}
 f2 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure Per Capita')
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, echo = FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
 f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
 f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
@@
 1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2. The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
 3.
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
 # Pooling effects analysis -- PCTGDP x N
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, echo = FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
 f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r, cache=TRUE}
+```{r, echo = FALSE, size="footnotesize", cache=TRUE}
 # Pooling effects analysis -- PCTGDP x logN
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, echo = FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
+build_forest(mod, NULL)
+```
+
+```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
 f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- PCTGDP x K
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest(mod, NULL)
+```
+
+```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
 f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- ExpPC x N (IV only)
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-```{r,include=F,warning=F, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest(mod, NULL)
+```
+
+```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
 aux <- dat %>%
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
 aux <- dat %>%
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- logExpPC x N (RDD only)
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
 aux <- dat %>%
@@
 
-```{r, echo=T, warning=F, cache=TRUE}
+```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
 pdf('../graphs/graph1.pdf', width = 16, height = 11)
@@
 
-```{r, echo=T, warning=F, cache=TRUE}
+```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
 pdf('../graphs/graph2.pdf', width = 12, height = 6)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-The _law of 1/n_ was formulated to analyse the budgetary allocation in majoritarian systems.
+The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems.
 In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
@@
 
-```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=T}
+```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
 mod2 <- tibble(
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- ExpPC x K
@@
 
-```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- logExpPC x N
@@
 
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- logExpPC x logN
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE}
-build_forest(mod, NULL)
-```
-
-Highlights:
-
-1. The results are highly heterogeneous: $I^2 = $ `r round(mod$I2*100, 2)`.
-2. The estimated SMD in the random effects model is $g = $ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10\% confidence level.**
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest(mod, NULL)
+```
+
+Highlights:
+
+1.  The results are highly heterogeneous: \$I\^2 = \$ `r round(mod$I2*100, 2)`.
+2.  The estimated SMD in the random effects model is \$g = \$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
 3.
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- PCTGDP x N
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=6, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- PCTGDP x logN
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, warning=F, cache=TRUE}
+```{r, size="footnotesize", warning=F, cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- PCTGDP x K
@@
 
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, cache=TRUE}
+```{r, size="footnotesize", cache=TRUE, echo = FALSE}
 # Pooling effects analysis -- ExpPC x N
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
 mod <-  rma(yi = coef,
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
 mod <- permutest(mod, progbar = F)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
 mod <- rma(yi = coef,
@@
 
-```{r, error=F, warning=F, cache=T}
+```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
 mod <-  rma(yi = coef,
@@
 ```
+
 As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
 
-```{r, error=F, warning=F, cache=T}
+```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
 mod <- permutest(mod, progbar = F)
@@
 
-```{r, warning=F, cache=T}
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
 mod <- permutest(mod, progbar = F, iter = 100)
@@
 
-```{r, warning=F, cache=T}
+```{r, warning=F, cache=T, echo = FALSE}
 mod <- permutest(mod, progbar = F)
@@
 
-```{r, cache=T}
+```{r, size="footnotesize", cache=T, echo = FALSE}
 permutest(mod, progbar = F)
@@
 
+```{=html}
+<!---
 # Auxiliary Functions
-
-## Function to Generate Meta-Analytic Figures
-
-This function receives the meta-analysis results and builds a forest plot using `ggplot2`.
-
-```{r, eval = FALSE, cache=T}
-# Build plot function for forest plots
-build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
-  # Build dataset for plot
-  mod2 <- tibble(
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    bind_rows(.,
-              aux = tibble(
-                TE = c(mod$TE.random, NA),
-                seTE = c(mod$seTE.random, NA),
-                studlab = c("Overall Effect", "Prediction Interval"),
-                lower = c(mod$lower.random, mod$lower.predict),
-                upper = c(mod$upper.random, mod$upper.predict),
-                group = "B")) %>%
-    group_by(studlab) %>%
-    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-    ungroup()
-
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab2, TE),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group), height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
-    scale_y_discrete(
-      labels = function(x) str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(group~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
-
-# Build plot function for forest plots to heterogeneous subgroup analysis
-build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
-  mod <- update(mod, byvar = hetvar, print.byvar = F)
-
-  # Build dataset for plot
-  mod2 <- tibble(
-    byvar = mod$byvar,
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    arrange(byvar)
-  auxmod <- tibble()
-  for (i in rev(mod$bylevs)){
-    auxmod <- rbind(auxmod, tibble(byvar = i,
-                    TE = NA,
-                    seTE = NA,
-                    studlab = toupper(i),
-                    lower = NA,
-                    upper = NA,
-                    group = "B"))
-    auxmod <- rbind(auxmod,
-                    filter(mod2, byvar==i) %>%
-                      arrange(desc(TE)))
-    auxmod <- rbind(auxmod, tibble(
-      byvar = i,
-      TE = mod$TE.random.w[which(mod$bylevs==i)],
-      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
-      studlab = 'Subgroup Effect',
-      lower = mod$lower.random.w[which(mod$bylevs==i)],
-      upper = mod$upper.random.w[which(mod$bylevs==i)],
-      group = "B"))
-  }
-  auxmod <- rbind(auxmod, tibble(
-    byvar = NA,
-    TE = c(mod$TE.random, NA),
-    seTE = c(mod$seTE.random, NA),
-    studlab = c("Overall Effect", "Prediction Interval"),
-    lower = c(mod$lower.random, mod$lower.predict),
-    upper = c(mod$upper.random, mod$upper.predict),
-    group = "B"))
-  mod2 <- data.frame(auxmod)
-  mod2$byvar <- toupper(mod2$byvar)
-  TEaux <- mod2$TE
-  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
-
-  # Graph limits
-  limg <- max(abs(c(mod2$lower, mod2$upper)))
-
-  # Build plot
-  p <- mod2 %>%
-    ggplot(aes(y = reorder(studlab, TEaux),
-               x = TE, xmin = lower, xmax = upper)) +
-    geom_point(aes(color = group)) +
-    geom_errorbarh(aes(color = group),
-                   height = 0.1) +
-    scale_color_manual(values = c("#000000", "#8b0000")) +
-    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
-    scale_y_discrete(
-      labels = function(x)
-        str_replace(x, "_[0-9]*$", "")) +
-    geom_vline(xintercept = 0,
-               color = "#000000", linetype = "dashed") +
-    labs(x = "",
-         y = "") +
-    facet_grid(byvar~., scales = "free", space = "free") +
-    labs(caption = capt,
-         title = ttl) +
-    theme_minimal() %+replace%
-    theme(strip.text.y = element_blank(),
-          legend.position = "none",
-          axis.text.y = element_text(size = .8 * lsize,
-                                     hjust = 1),
-          axis.text.x = element_text(size = .6 * lsize,
-                                     hjust = 1.1),
-          plot.caption = element_text(size = lsize),
-          plot.title.position = "plot",
-          plot.title = element_text(hjust = 0.5,
-                                    face = "bold",
-                                    margin = margin(0, 0, 10, 0)),
-          panel.grid.major = element_blank())
-  return(p)
-}
-```
 
@@
 
-We used the code below to download the articles cited in our paper.
-
-```{r, eval = FALSE, cache=T}
-# Required packages
-pkgs <- c("tidyverse", "rvest", "RSelenium")
-
-# Install the packages if necessary
-installIfNot <- function(x) {
-  if (x %in% rownames(installed.packages()) == FALSE)
-    install.packages(x, dependencies = T,
-					 repos = "http://cran.us.r-project.org")
-}
-lapply(pkgs, installIfNot)
-
-# Load packages
-lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
-
-# Setting Up Selenium
-
-# Alternative 1: Setting up Selenium (head)
-rsD <- rsDriver(port = 1114L, browser = c("firefox"))
-remDr <- rsD$client
-remDr$open()
-
-# Google Scholar
-
-# site: https://scholar.google.com
-remDr$navigate("https://scholar.google.com/
-               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")
-
-articles_weingast <- tibble(
-  value = NA,
-  term = NA,
-  page = NA
-)
-
-k <- 0
-
-for (j in 1:213) { # we had to manually choose the number of pages here
-
-  Sys.sleep(rpois(1, 5))
-
-  # Getting articles basic information
-  k <- k + 1
-
-  webElem <- remDr$findElement("css", "body")
-
-  title <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(
-      xpath = '//*[contains(concat( " ", @class, " " ),
-      concat( " ", "gs_rt", " " ))]'
-      ) %>%
-    html_text() %>%
-    enframe(name = NULL) %>%
-    rename("title" = "value") %>%
-    mutate(page = k)
-
-  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
-    html_text() %>%
-    enframe(name = NULL) %>%
-    bind_rows(
-      tibble(
-        value = "delete",
-        term = NA,
-        page = NA
-      ),
-      .
-    ) %>%
-    bind_cols(., title)
-
-  # Binding articles
-  articles_weingast <- bind_rows(articles_weingast, articles_partial)
-
-  # Changing Pages
-  next_button <- remDr$findElement(using = "xpath", "/html/body/div/div[11]/div[2]/div[2]/div[3]/
-                                   div[2]/center/table/tbody/tr/td[12]/a/b")
-  next_button$clickElement()
-  # Deleting cookies
-  remDr$deleteAllCookies()
-}
-
-write_csv(articles_weingast, "scholar_weingast_raw.csv")
-
-articles_weingast <- articles_weingast %>%
-  select(-term, -page) %>%
-  filter(value != "delete") %>%
-  slice(2:nrow(.)) %>%
-  filter(!grepl("books.google.com", value)) %>%
-  filter(!grepl("BOOK", title)) %>%
-  separate(., value, into = c("author", "value"),
-           sep = " -", remove = T, extra = "merge", fill = "right") %>%
-  separate(., value, into = c("journal", "year"),
-           sep = ",", remove = T, extra = "merge", fill = "right") %>%
-  mutate(
-    year_2 = ifelse(is.na(year), journal, year),
-    journal = ifelse(is.na(year), NA, journal),
-    year = year_2
-  ) %>%
-  select(-year_2) %>%
-  separate(., year, into = c("year", "site"),
-           sep = "-", remove = T, extra = "merge", fill = "right") %>%
-  mutate(
-    year = gsub("[^0-9 ]", "", value),
-    year = gsub("^[0-9]{5,}", "", year),
-    year = gsub("^ {1,}", "", year)
-  ) %>%
-  separate(., year, into = c("year", "junk"),
-           sep = " ", remove = T, extra = "merge", fill = "right") %>%
-  separate(., value, into = c("journal", "value"),
-           sep = "-", remove = T, extra = "merge", fill = "right") %>%
-  mutate(
-    journal_untidy = year,
-    year = gsub("[^0-9 ]", "", year)
-  )
-
-articles <- articles %>%
-  na.omit() %>%
-  distinct(., value, .keep_all = T)
-
-write_csv(articles, "google_scholar_clean.csv")
-
-# Scopus
-
-# url: https://www.scopus.com/home.uri
-
-# Scraping Scopus requires a bit more manual labor.
-# You can login on scopus through your university/institution
-# and download the metadata of the article(s) you
-# want directly from there.
-# All we need to do after that is scrape the information of
-# every link from the .csv file downloaded previously
-
-scopus <- read_csv("scopus.csv")
-
-scopus <- scopus %>%
-  mutate(article = map_chr(Link, ~ {
-    remDr$navigate(.x)
-    read_html(remDr$getPageSource()[[1]]) %>%
-      html_nodes(xpath = '//*[(@id = "abstractSection")]//p') %>%
-      html_text() %>%
-      paste(., collapse = "\r\n")
-  })) %>%
-  mutate(
-    article = gsub(
-      '\r\n\nUse this section.*Topics\n\n\n"',
-      "",
-      article
-    ),
-    article = gsub(
-      "Topics are unique.*onwards.",
-      "",
-      article
-    ),
-    article = gsub(
-      "Use this section.*documents.",
-      "",
-      article
-    ),
-    article = gsub(
-      "Learn more about these Topics",
-      "",
-      article
-    ),
-    article = gsub(
-      ". 20.*, Springer Science\\+Business Media, LLC, part of Springer Nature.",
-      "",
-      article
-    ),
-    article = gsub("\r", "", article),
-    article = gsub("\n", "", article),
-    article = gsub(" {2,}", " ", article),
-    article = gsub(" {3,}", "", article)
-  )
-
-write_csv(scopus, "scopus_clean.csv")
-
-#### Microsoft Academic ####
-
-# url: https://academic.microsoft.com/home
-articles <- list()
-k <- 0
-remDr$navigate("https://academic.microsoft.com/paper/
-               2076316673/citedby/search?q=The%20Political%
-               20Economy%20of%20Benefits%20and%20Costs%3A%20A%
-               20Neoclassical%20Approach%20to
-               %20Distributive%20Politics&qe=RId%253D2076316673&f=&orderBy=0")
-
-# 1) Getting hyperlinks from articles
-for (j in 1:100) {
-  k <- k + 1
-  print(k)
-
-  # Navigating Website
-
-  Sys.sleep(rpois(2, 5))
-
-  # Getting articles' links
-  articles[[k]] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(xpath = "//a") %>%
-    html_attr("href") %>%
-    enframe(name = NULL) %>%
-    filter(
-      grepl("paper/", value),
-      !grepl("citedby", value)
-    ) %>%
-    mutate(value = paste0("https://academic.microsoft.com/", value))
-
-  # Changing Page
-  next_page_others <- remDr$findElement(using = "xpath", "/html/body/div/div/div/router-view/router-view/                                        ma-edp-serp/div/div[2]/div/
-  compose/div/div[2]/ma-pager/div/i[2]")
-  next_page_others$clickElement()
-}
-
-articles <- articles %>%
-  reduce(bind_rows) %>%
-  distinct(value, .keep_all = T)
-
-# 2) Navigating through articles and scraping them
-
-articles_links <- articles %>%
-  mutate(
-    abstract = NA,
-    title = NA,
-    year = NA,
-    journal = NA,
-    authors = NA,
-    tags = NA
-  )
-
-for (i in 1:nrow(articles_links)) {
-  remDr$navigate(articles_links$value[i])
-  Sys.sleep(rpois(1, 4))
-
-  articles_links$abstract[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(., xpath = "//html/body/div/div/div/router-view/compose[1]/
-               div/div/ma-entity-detail-info/compose/div/div/div[1]/p") %>%
-    html_text() %>%
-    paste(., collapse = " ")
-
-  articles_links$title[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(.,
-               xpath = '//*[contains(concat( " ", @class, " " ),
-               concat( " ", "name", " " ))]') %>%
-    html_text() %>%
-    paste(., collapse = " ")
-
-  articles_links$year[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(.,
-               xpath = '//*[contains(concat( " ", @class, " " ),
-               concat( " ", "name-section", " " ))]
-               //*[contains(concat( " ", @class, " " ), concat( " ", "year", " " ))]') %>%
-    html_text() %>%
-    paste(., collapse = " ")
-
-  articles_links$journal[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " )
-               , concat( " ", "pub-name", " " ))]') %>%
-    html_text() %>%
-    paste(., collapse = " ")
-
-  articles_links$authors[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/div/div/
-               ma-entity-detail-info/compose/div/div/div[1]/
-               ma-author-string-collection") %>%
-    html_text() %>%
-    paste(., collapse = " ")
-
-  articles_links$tags[i] <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/
-               div/div/ma-entity-detail-info/compose/
-               div/div/div[1]/ma-tag-cloud/div") %>%
-    html_text() %>%
-    paste(., collapse = " ")
-}
-
-write_csv(articles_links, "microsoft_academic_clean.csv")
-```
-
+The code we used to download the articles cited in our paper are in the appendix, under the file name `building_metadata_dataset.R`. --->
+```
 # Session Information
 
-```{r}
+```{r, size="footnotesize", echo = FALSE}
 sessionInfo()

### 2021-03-13 appendix/building_paper_dataset.R

@@ -1,0 +1,288 @@
+##############################################################
+## Script: Scrapping Papers for Distributive Politics Paper ##
+## Authors: Alptekin, Freire, Mignozzetti, and Roman        ##
+## Last Modified: Mar 12, 2021                              ##
+##############################################################
+
+# Note: this script is out of order, and contains
+#       the code for scraping the article's data
+
+# Required packages
+pkgs <- c("tidyverse", "rvest", "RSelenium")
+
+# Install the packages if necessary
+installIfNot <- function(x) {
+  if (x %in% rownames(installed.packages()) == FALSE)
+    install.packages(x, dependencies = T,
+                     repos = "http://cran.us.r-project.org")
+}
+lapply(pkgs, installIfNot)
+
+# Load packages
+lapply(pkgs, require, character.only = T)
+rm(pkgs, installIfNot)
+
+# Setting Up Selenium
+
+# Alternative 1: Setting up Selenium (head)
+rsD <- rsDriver(port = 1114L, browser = c("firefox"))
+remDr <- rsD$client
+remDr$open()
+
+# Google Scholar
+
+# site: https://scholar.google.com
+remDr$navigate("https://scholar.google.com/
+               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")
+
+articles_weingast <- tibble(
+  value = NA,
+  term = NA,
+  page = NA
+)
+
+k <- 0
+
+for (j in 1:213) { # we had to manually choose the number of pages here
+  
+  Sys.sleep(rpois(1, 5))
+  
+  # Getting articles basic information
+  k <- k + 1
+  
+  webElem <- remDr$findElement("css", "body")
+  
+  
+  title <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(
+      xpath = '//*[contains(concat( " ", @class, " " ),
+      concat( " ", "gs_rt", " " ))]'
+    ) %>%
+    html_text() %>%
+    enframe(name = NULL) %>%
+    rename("title" = "value") %>%
+    mutate(page = k)
+  
+  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
+    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
+    html_text() %>%
+    enframe(name = NULL) %>%
+    bind_rows(
+      tibble(
+        value = "delete",
[…]

### 2021-03-13 dataset/datasetBuilding.R

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: MAr 12, 2021                                  ##
+## Last Modified: Mar 12, 2021                                  ##
 ##################################################################
 
 # Needed packages

### 2021-03-14 appendix/appendix.Rmd
add multilevel structure dataset

@@
 ---
+
+[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
+
+[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
+
+[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
+
+[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 

### 2021-03-14 dataset/datasetBuilding.R

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Mar 12, 2021                                  ##
+## Last Modified: Mar 14, 2021                                  ##
 ##################################################################
 
 # Needed packages

### 2021-03-14 dataset/datasetBuilding.R
change data builder

@@ -6,7 +6,7 @@
 
 # Needed packages
 rm(list=ls())
-pkgs <- c('tidyverse')
+pkgs <- c('tidyverse', 'data.table')
 
 # Install if not already installed
 installIfNot <- function(x) {
@@ -4653,6 +4653,140 @@ dat <- rbind(dat,
                SE = 0.0427
              ))
 
+# Paper A258
+dat <- rbind(dat,
+             data.frame(
+               id = 'A258',
+               published = 'Yes',
+               usemeta = 0, 
+               method = 'PANEL',
+               method2 = 'OLS/PANEL',
+               elecsys = 'Maj',
+               elecsys2 = 'Maj', 
+               elecsys3 = 'M',
+               agglevel = 'Local',
+               location = 'US',
+               locationISO = 'USA',
+               title = 'Government Form and Public Spending: Theory and Evidence from US Municipalities',
+               author = 'Coate and Knight',
+               authorCite = 'S. Coate & B. Knight',
+               year = 2011,
+               authoryear = 'Coate and Knight (2011)',
+               journal = 'American Economic Journal: Economic Policy',
+               journalCode = 'AEJ',
+               web = 'https://www.aeaweb.org/articles?id=10.1257/pol.3.3.82',
+               table = 4,
+               column = 1,
+               indepvar = 'Log Council Size',
+               indepvar2 = 'logN',
+               depvar = 'Log Public Spending Per Capita',
+               depvar2 = 'logExpPC',
+               coef = 0.1772,
+               scoef = 'P',
+               scoefsig = 'P',
+               SE = 0.0439
+             ))
+
+dat <- rbind(dat,
+             data.frame(
+               id = 'A258',
+               published = 'Yes',
+               usemeta = 0, 
+               method = 'PANEL',
+               method2 = 'OLS/PANEL',
+               elecsys = 'Maj',
+               elecsys2 = 'Maj', 
+               elecsys3 = 'M',
+               agglevel = 'Local',
+               location = 'US',
+               locationISO = 'USA',
+               title = 'Government Form and Public Spending: Theory and Evidence from US Municipalities',
+               author = 'Coate and Knight',
+               authorCite = 'S. Coate & B. Knight',
+               year = 2011,
+               authoryear = 'Coate and Knight (2011)',
+               journal = 'American Economic Journal: Economic Policy',
+               journalCode = 'AEJ',
[…]

### 2021-03-14 appendix/appendix.Rmd
tidy binomial tests and add todo to appendix

@@
           "knitr", "gridGraphics", "gridExtra",
-          "ggpubr", "kableExtra", "magick")
+          "ggpubr", "kableExtra", "magick",
+          'stargazer', 'pander', 'broom')
 
@@
 aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-aux2
+pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
 ```
@@
 aux2 <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
-aux2
+pander(tidy(aux2)[,-c(2,4,5,6)][,c(3,4,1,2)])
 ```

### 2021-03-14 appendix/appendix.Rmd
add funnel plot and egger et al tests first model

@@
 
-[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
+[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
 
@@
 devtools::install_github("isubirana/compareGroups")
+devtools::install_github("MathiasHarrer/dmetar")
 
@@
 lapply(pkgs, require, character.only = T)
-library("compareGroups")
+library("compareGroups"); library(dmetar)
 
@@
 
+\newpage
+
 # Search Criteria
@@
 
-```{r, size="footnotesize", warning=F, message=F, echo = FALSE, cache=TRUE}
+```{r, warning=F, message=F, echo = FALSE, cache=TRUE}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
@@
 
-descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-           show.p.overall = F, show.all = T)
+export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+                        show.p.overall = F, show.all = T), caption = "Descriptive Statistics of Moderators")
 ```
@@
 To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data.
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (XXXX TO UMBERTO: PUT CITATION HERE).
 
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
 

### 2021-03-14 appendix/appendix.Rmd
adding funnel plots

@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r, include=FALSE, warning=FALSE, echo = FALSE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 ```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
@@
 build_forest(mod, NULL)
+```
+
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
 ```
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
+```
+
 Highlights:
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
+```
+
+And to assess the possibility of publication bias, we add funnel plot below:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod, contour = c(.95,.975,.99),
+       col.contour=c("darkblue","blue","lightblue"))
+legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
+       fill=c("darkblue","blue","lightblue"))
 ```

### 2021-03-16 appendix/appendix.Rmd
multilevel reg forest plot

@@
 
+# Broom the multi-level model
+broom_mod <- function(mod) {
+  aux <- data.frame(predict(mod))
+  mod2 <- tibble(
+    TE = as.numeric(mod$yi),
+    seTE = sqrt(mod$vi),
+    studlab = mod$slab,
+    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
+    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
+    group = 'A') %>%
+    bind_rows(.,
+              aux = tibble(
+                TE = c(aux$pred, NA),
+                seTE = c(aux$se, NA),
+                studlab = c("Overall Effect",
+                            "Prediction Interval"),
+                lower = c(aux$ci.lb,
+                          aux$cr.lb),
+                upper = c(aux$ci.ub,
+                          aux$cr.ub),
+                group = "B")) %>%
+    group_by(studlab) %>%
+    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
+    ungroup()
+  return(mod2)
+}
+
 # Build plot function for forest plots
 build_forest <- function(mod, capt, lsize = 22, ttl = NULL) {
+  if(class(mod)[1] == "rma.mv") {
+    mod2 <- broom_mod(mod)
+  } else {
   # Build dataset for plot
@@
     ungroup()
+  }
 
@@
 
-In this paper, we use the random effects model.
+In this paper, we use a multi-level random effects model.
+The difference between a simple random effects model, and a multi-level random effects model is that we can specify multiple levels of empirical dependency in the data ().
 The empirical papers testing the *law of 1/n* are very diverse.
@@
 To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (XXXX TO UMBERTO: PUT CITATION HERE).
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).
 
@@
 
-# Code for the Main Graphs
-
-## Figure 1
-
-```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
+```{r, warning=F, cache=TRUE, echo = FALSE}
+## Plot 1
 pdf('../graphs/graph1.pdf', width = 16, height = 11)
@@
 dev.off()
-```
-
-## Figure 2
-
-```{r, echo=T, warning=F, cache=TRUE, echo = FALSE}
+## Plot 2
 pdf('../graphs/graph2.pdf', width = 12, height = 6)

### 2021-03-16 appendix/appendix.Rmd
build estimator for heterogeneous effects ma

@@
 # Broom the multi-level model
-broom_mod <- function(mod) {
+broom_mod <- function(mod, subgroup = FALSE) {
   aux <- data.frame(predict(mod))
+  if (subgroup) {
+    teeff = aux$pred
+    seteeff = aux$se
+    labeff = c("Subgroup Effect")
+    loeff = c(aux$ci.lb)
+    upeff = c(aux$ci.ub)
+  } else {
+    teeff = c(aux$pred, NA)
+    seteeff = c(aux$se, NA)
+    labeff = c("Overall Effect",
+               "Prediction Interval")
+    loeff = c(aux$ci.lb, aux$cr.lb)
+    upeff = c(aux$ci.ub, aux$cr.ub)
+  }
   mod2 <- tibble(
@@
               aux = tibble(
-                TE = c(aux$pred, NA),
-                seTE = c(aux$se, NA),
-                studlab = c("Overall Effect",
-                            "Prediction Interval"),
-                lower = c(aux$ci.lb,
-                          aux$cr.lb),
-                upper = c(aux$ci.ub,
-                          aux$cr.ub),
+                TE = teeff,
+                seTE = seteeff,
+                studlab = labeff,
+                lower = loeff,
+                upper = upeff,
                 group = "B")) %>%
@@
   return(mod2)
+}
+
+# Estimation of the 
+estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
+  if (is.null(hetvar)) {
+    print('Hetvar should be different than null.')
+    break
+  }
+  levshetvar <- unique(hetvar)
+  fullmod <- rma.mv(yi = yi, V = v, random = random,
+                    data = dat, slab = slab, method = 'REML',
+                    test = 't', tdist = T)
+  res <- tibble()
+  for (i in levshetvar) {
+    partmod <- rma.mv(yi = yi, V = v, 
+                      random = random,
+                      data = dat, slab = slab, 
+                      method = 'REML',
+                      test = 't', tdist = T, 
+                      subset = hetvar == i)
+    partmod <- broom_mod(partmod, subgroup = T)
+    partmod$byvar = i
+    partmod <- bind_rows(
+      tibble(TE = NA, seTE = NA,
+             studlab = toupper(i), lower = NA,
+             upper = NA, group = "B", byvar = i),
+      partmod
+    )
+    res <- bind_rows(res, partmod)
+  }
+  aux <- data.frame(predict(fullmod))
+  res <- bind_rows(res,
+                   tibble(
+                     byvar = NA,
+                     TE = c(aux$pred, NA),
+                     seTE = c(aux$se, NA),
+                     studlab = c("Overall Effect", "Prediction Interval"),
+                     lower = c(aux$ci.lb, aux$cr.lb),
+                     upper = c(aux$ci.ub, aux$cr.ub),
+                     group = "B"))
+  res <- data.frame(res)
+  res$byvar <- toupper(res$byvar)
+  return(res)
 }
@@
 # Build plot function for forest plots
-build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+build_forest_het <- function(estims, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
   mod <- update(mod, byvar = hetvar, print.byvar = F)

### 2021-03-17 appendix/appendix.Rmd
embedding multilevel structure dataset

@@
   if (is.null(hetvar)) {
-    print('Hetvar should be different than null.')
-    break
+    stop('Hetvar should be different than null.')
   }
@@
 We set no restriction to unpublished articles.
+XXXX CATARINA AND HUZEYFE: FIX THIS
 
@@
     geom_bar(color = "black") +
-  labs(x = "Dependent Variables",
-       y = "") +
+  labs(x = "",
+       y = "Dependent Variables") +
   coord_flip() +
@@
     geom_bar(color = "black") +
-  labs(x = "Independent Variables",
-       y = "") +
+  labs(x = "",
+       y = "Independent Variables") +
   coord_flip() +
@@
   geom_histogram(bins = 15, color = "black") +
-  labs(x = "Coefficients") +
+  labs(x = "Coefficients", y = '') +
   theme_bw()
@@
   geom_histogram(bins = 10, color = "black") +
-  labs(x = "Standard Errors") +
+  labs(x = "Standard Errors", y = '') +
   theme_bw()

### 2021-03-17 dataset/datasetBuilding.R

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Mar 14, 2021                                  ##
+## Last Modified: Mar 17, 2021                                  ##
 ##################################################################
 
 # Needed packages
@@ -4885,11 +4885,20 @@ dat$scoefnd[dat$scoefnd=='Negative'] = 'Negative Insignificant'
 # Create indicator
 dat <- arrange(dat, id) %>%
   mutate(id_paper = rleid(id)) %>%
+  mutate(id_level1 = ifelse(id %in% c('3', '42', '132', '165',
+                                      '439', '441', '467', '505'), '3-505', 
+                            ifelse(id %in% c('408', '208', 'A258'), '408-A258', 
+                                   ifelse(id %in% c('849', '578'), '849-578', id)))) %>%
   group_by(id_paper) %>%
   mutate(id_model = row_number()) %>%
   ungroup() %>%
+  group_by(id_level1) %>%
+  mutate(id_level2 = row_number()) %>%
+  ungroup() %>%
   relocate(id_paper, .after = id) %>%
-  relocate(id_model, .before = id_paper) %>%
+  relocate(id_model, .after = id_paper) %>%
+  relocate(id_level1, .after = id_model) %>%
+  relocate(id_level2, .after = id_level1) %>%
   mutate(VAR = SE^2)
 
 # Full data and partial data

### 2021-03-17 appendix/appendix.Rmd
changes random effects

@@
 # Build forest plot for heterogeneous analysis
-# Build plot function for forest plots
-build_forest_het <- function(estims, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
-  mod <- update(mod, byvar = hetvar, print.byvar = F)
-
-  # Build dataset for plot
-  mod2 <- tibble(
-    byvar = mod$byvar,
-    TE = mod$TE,
-    seTE = mod$seTE,
-    studlab = mod$studlab,
-    lower = mod$lower,
-    upper = mod$upper,
-    group = "A") %>%
-    arrange(byvar)
-  auxmod <- tibble()
-  for (i in rev(mod$bylevs)){
-    auxmod <- rbind(auxmod, tibble(byvar = i,
-                    TE = NA,
-                    seTE = NA,
-                    studlab = toupper(i),
-                    lower = NA,
-                    upper = NA,
-                    group = "B"))
-    auxmod <- rbind(auxmod,
-                    filter(mod2, byvar==i) %>%
-                      arrange(desc(TE)))
-    auxmod <- rbind(auxmod, tibble(
-      byvar = i,
-      TE = mod$TE.random.w[which(mod$bylevs==i)],
-      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
-      studlab = 'Subgroup Effect',
-      lower = mod$lower.random.w[which(mod$bylevs==i)],
-      upper = mod$upper.random.w[which(mod$bylevs==i)],
-      group = "B"))
-  }
-  auxmod <- rbind(auxmod, tibble(
-    byvar = NA,
-    TE = c(mod$TE.random, NA),
-    seTE = c(mod$seTE.random, NA),
-    studlab = c("Overall Effect", "Prediction Interval"),
-    lower = c(mod$lower.random, mod$lower.predict),
-    upper = c(mod$upper.random, mod$upper.predict),
-    group = "B"))
-  mod2 <- data.frame(auxmod)
+build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
+
+  mod2 <- estim_het(dat = dat, 
+                    yi = coef, 
+                    v = v, 
+                    random = ~ 1 | id_level1/id_level2, 
+                    slab = slab, 
+                    hetvar = hetvar)
+
+  mod2 <- data.frame(mod2)
   mod2$byvar <- toupper(mod2$byvar)
@@
 In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models.
-The fixed effects model assumes that there is one true effect in reality, and that all estimates are an attempt to uncover this true effect.
-The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sample and tests characteristics.
-
-In this paper, we use a multi-level random effects model.
-The difference between a simple random effects model, and a multi-level random effects model is that we can specify multiple levels of empirical dependency in the data ().
+The fixed effects model assumes that there exists only one true effect, and that all estimates are an attempt to uncover this effect.
+The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.
+
+In this paper, we a random-effects model.
 The empirical papers testing the *law of 1/n* are very diverse.
@@
 
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [Doing Meta-Analysis with R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
+Another crucial assumption in the meta-analysis is the independence between the results (@harrer2019doing, @cheung2019guide, @veroniki2016methods, @borenstein2011introduction).
+This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation.
+However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable.
+While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
+This because the papers report an average of `r mean(as.numeric(table(fulldat$id)))` coefficients.
+Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated.
+To correct for this problem, we use a multi-level random effects model (@cheung2014modeling).
+The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels.
+All these levels are assumed to absorb the dependence in the data, leaving for the main coefficient, the independent effect of legislature size on public spending.
+
+There are two levels in the main models. First, we build a common index for papers that share the same dataset specifications. The papers with common indexing are:
+
+| Paper IDs                                   | Source of Dependence                                                     |
+|---------------------------------------------|--------------------------------------------------------------------------|
+| 3, 42, 132, <br>165, 439, 441, <br>467, 505 | US States Dataset                                                        |
+| 408, 208, A258                              | US Municipalities Dataset                                                |
+| 849, 578                                    | US Municipalities Dataset<br>and Same Author in two<br>Different Studies |
+
+All the remaining papers receive a unique index.
+As the number of the papers with these dependencies are not very high, and many characteristics within papers vary (e.
+g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs.
+In the case of the full dataset, the results change considerably, because authors fit several models within the same paper.
+In the case In any case, we use multi-level random effects for all the estimated models in this paper.
+
+To study the possibility of of publication bias, for all models we add a funnel plot and an @egger1997bias test for distribution asymmetry.
+The funnel plot displays the possibility of having a file-drawer effect, meaning that null results are disproportionately less represented in our sample.
+In this plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome.
+If they are asymmetric, it evidences a possible file-drawer effect.
+
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [@harrer2019doing](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
 To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
@@
 
-mod <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
 mod
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+funnel(mod)
 ```
@@
 
-1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
+2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
 3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
+The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
+Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
+4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
 
@@
 ```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
-build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
+build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
+                 capt = NULL, hetvar = aux$elecsys2)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 
-mod <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction = TRUE,
-  sm="SMD"
-  )
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
 
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 
-1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
+1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
+2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
 3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
+The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
+Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
+4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
 
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 
-mod <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction=TRUE,
-  sm="SMD"
-  )
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
 
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 
-mod <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-f8 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
+
+f8 <- build_forest_het(aux, aux$coef, 
+                       aux$VAR, slab = aux$authoryear,
+                       capt = NULL, lsize = 15, 
+                       ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
+                       hetvar = aux$method)
 ```
@@
 
-mod <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-build_forest_het(mod, capt = NULL, hetvar = aux$method)
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
+
+build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
+                 capt = NULL, hetvar = aux$method)
 ```
@@
   filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-f9 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
+         depvar2 == 'logExpPC',
+         method == 'RDD')
+
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
+
+f9 <- build_forest(mod, capt = NULL, 
+                       lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by RDD)')
 ```
@@
   filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-build_forest_het(mod, capt = NULL, hetvar = aux$method)
+         depvar2 == 'logExpPC', 
+         method == 'RDD')
+
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
+
+build_forest(mod, capt = NULL, ttl = NULL)
 ```
@@
 For the RDD subgroup analysis, we can see a much clearer picture.
-All estimates are negative, and the subgroup effect is -0.11.
+The subgroup effect is -0.085.
 This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.
@@
 
-1.  The results are highly heterogeneous: $I^2 =$ `r round(mod$I2*100, 2)`.
-2.  The estimated SMD in the random effects model is $g =$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`).
+1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
+2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
 3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
+The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
+Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
+4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
 
@@
 ```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
-mod2 <- tibble(
-  TE = mod$TE,
-  seTE = mod$seTE,
-  studlab = mod$studlab,
-  lower = mod$lower,
-  upper = mod$upper,
-  group = "A") %>%
-  bind_rows(.,
-            aux = tibble(
-              TE = c(mod$TE.random, NA),
-              seTE = c(mod$seTE.random, NA),
-              studlab = c("Overall Effect", "Prediction Interval"),
-              lower = c(mod$lower.random, mod$lower.predict),
-              upper = c(mod$upper.random, mod$upper.predict),
-              group = "B")) %>%
-  group_by(studlab) %>%
-  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
-  ungroup()
-
-f8b <- mod2 %>%
-  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
-  # Studies coefs
-  geom_point(aes(color = group)) +
-  # Error Bars
-  geom_errorbarh(aes(color = group), height = 0.1) +
-  # Colors
-  scale_color_manual(values = c("#000000", "#8b0000")) +
-  # X-axis limit
-  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
-  # Y-axis names
-  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) +
-  # Vertical dashed line
-  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
-  # Labels
-  labs(x = "",
-       y = "") +
-  # Facet - Separating Studies from Overall Effect
-  facet_grid(group~., scales = "free", space = "free") +
-  # Theme
-  theme_minimal() %+replace%
-  theme(strip.text.y = element_blank(),
-        legend.position = "none",
-        axis.text.y = element_text(size = 13, hjust = 1.1),
-        axis.text.x = element_text(size = 15, hjust = 1.1))
-f8b
+build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
+                 capt = NULL, hetvar = aux$elecsys2)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 
-1.  The results are highly heterogeneous: \$I\^2 = \$ `r round(mod$I2*100, 2)`.
-2.  The estimated SMD in the random effects model is \$g = \$ `r round(mod$TE.random,2)` ($SE =$ `r round(mod$seTE.random,3)`). **This model is significant at the 10% confidence level.**
+1.  The results are highly heterogeneous: $Q =$ `r round(mod$QE, 2)`.
+2.  The estimated SMD in the random effects model is $g =$ `r round(predict(mod)$pred,2)` ($SE =$ `r round(predict(mod)$se,3)`).
 3.
-The prediction interval ranges from `r round(mod$lower.predict,2)` to `r round(mod$upper.predict,2)`.
-Therefore, it `r ifelse(((mod$lower.predict)*(mod$upper.predict))>0,'does not emcompasses zero.','emcompasses zero.')`
-4. The @egger1997bias test `r ifelse(eggers.test(mod)$p<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
+The prediction interval ranges from `r round(predict(mod)$cr.lb,2)` to `r round(predict(mod)$cr.ub,2)`.
+Therefore, it `r ifelse(((predict(mod)$cr.lb)*(predict(mod)$cr.ub))>0,'does not emcompasses zero.','emcompasses zero.')`
+4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
 
@@
 
-mod <- metagen(coef, SE, data = aux,
-          studlab = paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm = "SMD")
+mod <- rma.mv(coef, VAR, data=aux,
+          slab=paste(authoryear),
+          test = 't',
+          random = ~ 1 | id_level1/id_level2, 
+          tdist = TRUE,
+          method = "REML")
 mod
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```
@@
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
-funnel(mod, contour = c(.95,.975,.99),
-       col.contour=c("darkblue","blue","lightblue"))
-legend(1.4, 0, c("p < 0.05", "p < 0.025", "p < 0.01"),bty = "n",
-       fill=c("darkblue","blue","lightblue"))
+funnel(mod)
 ```

### 2021-03-17 appendix/appendix.Rmd
update todo meta-regressions

@@
 ```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <-  rma(yi = coef,
-              sei = SE,
+mod <- rma.mv(yi = coef,
+              V = VAR,
               data = dat,
               method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
               mods = ~indepvar2+year+published+elecsys2+method,
               test = "knha",
+              tdist = TRUE,
               subset = dat$depvar2=='PCTGDP',
               slab = dat$authoryear)
+
 summary(mod)
@@
 ```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma(yi = coef,
-              sei = SE,
+mod <- rma.mv(yi = coef,
+              V = VAR,
               data = fulldat,
               method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method,
               test = "knha",
+              tdist = TRUE,
             subset = fulldat$depvar2=='PCTGDP',

### 2021-03-17 appendix/appendix.Rmd
fix meta-regression first check

@@
 
-## Meta-Regressions for Expenditure as a Percentage of the GDP
-
-In this section, we show the coefficients for our meta-regressions. We start with expenditure as a percentage of GDP as the dependent variable.
+In the meta-regressions, we study the effects of a group of moderators on the reported government spending data. We select the following moderators:
+
+1. The independent variable (variable `indepvar2`):
+  - `K`: Upper House Size
+  - `N`: Lower House Size
+  - `logN`: Log of Lower House Size
+
+2. Year that the paper was published (for working papers, the year it was posted online; variable `year`)
+
+3. A dummy indicating whether the paper was published or not (variable `published`).
+
+4. A dummy for non-majoritarian electoral systems (variable `elecsys2`).
+
+5. The estimation method used in the papers (variable `method`):
+  - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
+  - `PANEL`: Time-Series Cross-Section models, with estimated fixed effects.
+  - `IV`: Instrumental Variables models.
+  - `RDD`: Regression Discontinuity Designs.
+
+The results follows below, for the three combinations of dependent variables: Expenditure Per Capita, Log of Expenditure Per Capita, and Expenditure as a Percentage of the GDP.
+
+## Meta-Regressions for Expenditure Per Capita
+
+Here we study the expenditure per capita as the main outcome, aggregating all types of independent variables.
+
+```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+              tdist = TRUE,
+              subset = dat$depvar2=='ExpPC',
+              slab = dat$authoryear)
+
+summary(mod)
+```
+
+For the meta-regressions of Expenditure Per Capita, we find no significant moderator. We also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+              tdist = TRUE,
+              subset = fulldat$depvar2=='ExpPC',
+              slab = fulldat$authoryear)
+
+summary(mod)
+```
+With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:
+
+1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
+
+2.  Year has now a positive effect on coefficient sizes.
+
+3.  All other coeffients were not significant.
+
+## Meta-Regressions for Log of Expenditure Per Capita
 
@@
               tdist = TRUE,
-              subset = dat$depvar2=='PCTGDP',
+              subset = dat$depvar2=='logExpPC',
               slab = dat$authoryear)
@@
 
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-```
-
-We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:
-
-1.  Compared with `K`, models with `N` and `logN` find significantly negative coefficients.
-2.  Year has null effect.
-3.  Unpublished papers tend to have higher coefficients than published papers.
-4.  Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-5.  In terms of modelling, passing from `OLS` to `PANEL` increases the detected effects.
-6.  When passing from `Country` to `Cross-Country`, it has no effect on the estimated coefficients.
+The only significant result points that published papers tend to report a smaller coefficient than unpublished papers.
 
@@
               tdist = TRUE,
+              subset = fulldat$depvar2=='logExpPC',
+              slab = fulldat$authoryear)
+
+summary(mod)
+```
+
+With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
+
+1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
+
+2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
+
+All other results are insignificant.
+
+## Meta-Regressions for Expenditure as a Percentage of the GDP
+
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+              tdist = TRUE,
+              subset = dat$depvar2=='PCTGDP',
+              slab = dat$authoryear)
+
+summary(mod)
+```
+
+We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:
+
+1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+
+2. All other moderators remain insignificant.
+
+Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+
+```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method,
+              test = "knha",
+              tdist = TRUE,
             subset = fulldat$depvar2=='PCTGDP',
@@
 
+For all the coefficients, we have the following results:
+
+1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
+
+2. All other moderators remain insignificant.
+
+# Robustness: Meta-Regressions (All Coefficients)
+
+In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:
+
+1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP).
+
+2. The type of the independent variable in the study (lower house size, upper house size, or log of lower house size).
+
+3. The electoral system (Majoritarian versus Non-Majoritarian).
+
+4. The year when the study was published.
+
+5. Whether the study is a working paper or published work.
+
+6. The estimation method used in the paper (OLS, PANEL, IV, or RDD).
+
+The results follow below, and show null effects for all variables, including the intercept.
+
 ```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-```
-
-For all the coefficients, we have the following results:
-
-1.  Compared with `K`, models with `N` and `logN` tend to have significantly negative coefficients.
-2.  Year has a positive effect: the younger the publication, the higher the detected coefficient.
-3.  Unpublished papers tend to have higher coefficients than published papers.
-4.  Passing from `Majoritarian` to `Non-Majoritarian` significantly decreases the effects found in our models.
-5.  Regarding statistical models, passing from `OLS` to `PANEL` increases the detected effects.
-
-## Meta-Regressions for Expenditure Per Capita
-
-Here we do the same exercise with expenditure per capita as the main outcome.
-
-```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
-mod <-  rma(yi = coef,
-              sei = SE,
+mod <- rma.mv(yi = coef,
+              V = VAR,
               data = dat,
               method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+
+                published+elecsys2+method,
               test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear,
-            control=list(maxiter=1000))
+              tdist = TRUE,
+              slab = dat$authoryear)
+
 summary(mod)
 ```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, size="footnotesize", error=F, warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-```
-
-We have the following results for the meta-regressions of Expenditure Per Capita:
-
-1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2.  Year has null effect.
-3.  `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
-4.  Regarding statistical models, passing from `OLS` to `PANEL` or `IV` increases the detected effects.
-
-We also run the meta-regressions adding all coefficients in the papers. The results follow below:
+In the restricted model, with only the main coefficients in the selected papers, no moderator has a significant effect.
+We also run the meta-regressions adding all coefficients in the papers.
+The results follow below:
 
 ```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma(yi = coef,
-              sei = SE,
+mod <- rma.mv(yi = coef,
+              V = VAR,
               data = fulldat,
               method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+
+                published+elecsys2+method,
               test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
+              tdist = TRUE,
               slab = fulldat$authoryear)
@@
 ```
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F, iter = 100)
-mod
-```
-
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:
-
-1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
-2.  Year has now a positive effect on coefficient sizes.
-3.  `Majoritarian`, when compared to `Non-Majoritarian` electoral systems, significantly increase per capita expenditure.
-4.  Regarding statistical models, passing from `OLS` to `PANEL` decreases the detected effects.
-5.  All other coeffients were not significant.
-
-## Meta-Regressions for Log of Expenditure Per Capita
-
-Lastly, we run the model with the natural logarithm of expenditure per capita.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F)
-mod
-```
-
-For the meta-regressions of Log of Expenditure Per Capita we find no significant results.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-summary(mod)
-```
-
-```{r, warning=F, cache=T, echo = FALSE}
-mod <- permutest(mod, progbar = F)
-```
-
-With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
-
-1.  In terms of the modelling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
-2.  All other coefficients remained insignificant.
-
-# Robustness: Meta-Regressions (All Coefficients)
-
-In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:
-
-1.  The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP)
-2.  The type of the independent variable in the study ($N$, $K$, $log (N)$);
-3.  The electoral system (Majoritarian, Proportional Representation, and Mixed).
-
-The results follow below, and show null effects for all variables, including the intercept.
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
-              test = "knha")
-summary(mod)
-```
-
-As we have considerable heterogeneity in our sample, we run a permutation test to ensure the validity of our estimates. The results follow below.
-
-```{r, size="footnotesize", cache=T, echo = FALSE}
-permutest(mod, progbar = F)
-```
-
-In the main text, we selected coefficients based on the regressions that had most observations and presented a full model (with fixed effects or intermediate bandwidth in RDD).
-We also run the meta-regressions adding all coefficients in the papers.
-The results follow below:
-
-```{r, size="footnotesize", warning=F, cache=T, echo = FALSE}
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ depvar2+indepvar2+year+published+elecsys2+method,
-              test = "knha")
-summary(mod)
-```
-
-```{r, size="footnotesize", cache=T, echo = FALSE}
-permutest(mod, progbar = F)
-```
-
-```{=html}
-<!---
-# Auxiliary Functions
-
-## Webscraping Code
-\label{sub:scrap}
-
-The code we used to download the articles cited in our paper are in the appendix, under the file name `building_metadata_dataset.R`. --->
-```
+In the full model, we can see that:
+
+1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.
+
+2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.
+
+3. Over time, the reported coefficients have been increasing in size.
+
+4. Compared with OLS, Panel and RDD report significantly smaller coefficients.
+
+5. All other moderators are insignificant.
+
 # Session Information

### 2021-03-18 appendix/appendix.Rmd
completes article selection procedures

@@
 This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "*The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics*", which is a seminal contribution to the field.
+To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field.
 Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
@@
 We set no restriction to unpublished articles.
-XXXX CATARINA AND HUZEYFE: FIX THIS
+
+We complemented this by doing a term search on Google Scholar after having finished the entire eligibility procedure on the first sample.
+We formulated the search string based on the terms and expressions that appeared most commonly in the articles included in our meta-analysis.
+The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending.
+The search string was as follows: *(“upper chamber size” OR "lower chamber size" OR “council size” OR “parliament size” OR “legislature size” OR “number of legislators” OR “legislative size") AND (“spending” OR “expenditure" OR “government size”)*.
+We scraped Google Scholar on March 5th, 2021.
+Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously.
+We then performed the exact same eligibility procedures, further explained below.
+This resulted in 3,041 additional records.
+
+Combining the two search strategies, we assessed a total of 5,705 records.
 
@@
 
-The selection process was conducted by two authors in three phases.
+The selection process was conducted by the authors in three phases.
 In the first round, we excluded all titles that were clearly unrelated to our topic of interest.
 For instance, we curiously found articles about car motors amidst our sample.
-We consider this a preliminary step, since we were not able to eliminate a large number of entries.
 Then, we read all abstracts.
@@
 Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were also included.
-This allowed us to significantly reduce our sample to 376 records.
+This allowed us to significantly reduce our sample to 475 records, combining the two search strategies.
 
@@
 If the publication had all three, it was maintained.
-Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
-
-The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility.
+Disagreements in this phase were discussed among the authors.
+
+The third phase consisted of filling out tables for each of the remaining articles to systematically evaluate their eligibility.
 Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information.
-We decided which variables to keep by following the current practices of the literature.
+We decided which variables to keep by following the most current practices of the literature.
 In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
 Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.
+Since the citation search was conducted first, it provided us with 29 papers, while with the term search we arrived at only 2 articles to add to our sample.
 
@@
   \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
-
+\caption{"PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
   \footnotesize
@@
 
+ \end{tikzpicture}
+```
+
+\bigskip
+
+```{tikz tikz-ex2, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
+\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
+\caption{"PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
+  \footnotesize
+  \linespread{1.0}
+  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
+  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
+  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
+  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
+  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
+  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
+  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
+  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
+  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
+  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
+  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 10)}};
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 3)}};
+  \draw [arrow] (id) -- (1st);
+  \draw [arrow] (id) -- (screen);
+  \draw [arrow] (screen) -- (2nd);
+  \draw [arrow] (screen) -- (elig);
+  \draw [arrow] (elig) -- (3rd);
+  \draw [arrow] (elig) -- (inc_1);
+  \draw [arrow] (inc_1) -- (4th);
+  \draw [arrow] (inc_1) -- (inc_2);
  \end{tikzpicture}

### 2021-03-19 appendix/appendix.Rmd
model 1

--- 2021-03-17 appendix/appendix.Rmd
@@
 
+# Law of 1/n Model
+
+In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive.
+Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the XXXX, but these two papers, in our view, present the most elementary theoretical argument
+
+In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark.
+Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout the entire tax pool (all constituencies).
+The corollary of their suggestion is that larger legislatures generate more expenditure.
+
+In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$ and there are convex costs associated with the project.\footnote{Concave in this case means that $b'>0$ and $b''<0$.
+Convex in this case mean that $c'>0$ and $c''>0$.
+We assume that the derivatives are well defined throughout the analysis.
+Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume equal constituencies.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e.
+g., hire a local company to build the project).
+The second cost, $c_2(x)$, captures the expenses outside the constituency (e.
+g., hire a company from another state).
+The third cost $c_3(x)$ captures the externalities generated by the project (e.
+g., how much prices shift because local economic factors are being used to provide the project).
+The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$.
+The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.
+
+Following their model, the economic efficiency is achieved when the marginal costs are equal the marginal benefits of increase the project size.
+This leads to the economic optimal project size, $x^E$.
+The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$.
+However, the actual projects that are implemented have a different structure.
+First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represent the number of constituencies.
+Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms.
+Therefore, the benefits and costs of implement a project with size $x$ have the following structure:
+
+\[
+N(x) = b(x) + c_1(x) - \frac{1}{n}[c_1(x) + c_2(x)] - c_3(x)
+\]
+
+Differentiating $N(x)$ with respect to $x$ gives us the first order condition for an optimal project implementation.
+
+\[
+b'(x) + c_1'(x) - \dfrac{1}{n}[c_1'(x) + c_2'(x)] - c_3'(x) = 0
+\]
+
+Totally differentiating $x$ with respect to $n$, gives us:
+
+\[
+b''(x)\dfrac{dx}{dn} + c_1''(x)\dfrac{dx}{dn} - \dfrac{1}{n}[c_1''(x) + c_2''(x)]\dfrac{dx}{dn} + \dfrac{1}{n^2}[c_1'(x) + c_2'(x)] - c_3''(x)\dfrac{dx}{dn} = 0
+\]
+
+And rearranging the terms, yields to the following expression for $\dfrac{dx}{dn}$:
+
+\[
+\dfrac{dx}{dn} = -\dfrac{n^{-2}[c_1'(x) + c_2'(x)]}{b''(x) + c_1''(x)-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x)}
+\]
+
+Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size.
+The law of 1/n holds when the denominator is negative.
+$b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$.
+Then, the law of 1/n is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
+
+XXXX PAREI AQUI
+
+As the above condition suggests, the law of 1/n holds in specific situations.
+@primo2008distributive XXXX cost is when the suppose that we have a set of representatives, indexed in districts $i \in \{1, \cdots, n \}$.
+
 # Search Criteria
+
+XXXX CATARINA AND HUZEYFE: FIX THIS
 
@@
 
-Another crucial assumption in the meta-analysis is the independence between the results (@harrer2019doing, @cheung2019guide, @veroniki2016methods, @borenstein2011introduction).
+Another crucial assumption in the meta-analysis is the independence between the results [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction].
 This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation.
@@
 While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
-This because the papers report an average of `r mean(as.numeric(table(fulldat$id)))` coefficients.
+This because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
 Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated.
-To correct for this problem, we use a multi-level random effects model (@cheung2014modeling).
+To correct for this problem, we use a multi-level random effects model [@cheung2014modeling].
 The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels.
@@
 
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in [@harrer2019doing](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
+In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in @harrer2019doing [here](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
 To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data (@veroniki2016methods).
+We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data [@veroniki2016methods].
 
@@
           method = "REML")
+
 mod
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower House Size x Expenditure Per Capita, controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
@@
 
-### Regression Method Subgroup Analysis
-
-Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenditure per capita.
-To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
-
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC', 
-         method == 'RDD')
-
-mod <- rma.mv(coef, VAR, data=aux,
-          slab=paste(authoryear),
-          test = 't',
-          random = ~ 1 | id_level1/id_level2, 
-          tdist = TRUE,
-          method = "REML")
-
-build_forest(mod, capt = NULL, ttl = NULL)
-```
-
-For the RDD subgroup analysis, we can see a much clearer picture.
-The subgroup effect is -0.085.
-This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.
-
-```{r, warning=F, cache=TRUE, echo = FALSE}
+```{r, warning=F, cache=TRUE, echo = FALSE, results='hide'}
 ## Plot 1

### 2021-03-21 dataset/datasetBuilding.R
add instdesign dataset and audit

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Mar 17, 2021                                  ##
+## Last Modified: Mar 21, 2021                                  ##
 ##################################################################
 
 # Needed packages
@@ -19,73 +19,38 @@ lapply(pkgs, installIfNot)
 lapply(pkgs, require, character.only = T)
 rm(pkgs, installIfNot)
 
-# Paper 367
+# Paper 585 K
 dat <- data.frame(
-  id = 367,
+  id = 585,
   published = 'Yes',
-  usemeta = 1,
-  method = 'OLS',
+  usemeta = 1, 
+  method = 'PANEL',
   method2 = 'OLS/PANEL',
-  elecsys = 'Maj',
-  elecsys2 = 'Maj', elecsys3 = 'M',
-  agglevel = 'States',
-  location = 'US',
-  locationISO = 'USA',
-  title = 'Spatially Targeted Government Spending and
-Heterogeneous Constituent Cost Shares',
-  author = 'Bradbury and Stephenson',
-  authorCite = 'J. Bradbury & E. F. Stephenson',
-  year = 2009,
-  authoryear = 'Bradbury and Stephenson (2009)',
-  journal = 'The Journal of Private Enterprise',
-  journalCode = 'JPriE',
-  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
+  elecsys = 'Mixed',
+  elecsys2 = 'Non-Maj', elecsys3 = 'NM',
+  agglevel = 'Countries',
+  location = 'World',
+  locationISO = 'Multiple (37)',
+  instdesign = 'Bicameral',
+  title = 'Legislative organization and government spending: cross-country evidence',
+  author = 'Bradbury and Crain',
+  authorCite = 'J. Bradbury & M. Crain',
+  year = 2001,
+  authoryear = 'Bradbury and Crain (2001)',
+  journal = 'Journal of Public Economics',
+  journalCode = 'JPubE',
+  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
   table = 2,
-  column = 2,
-  indepvar = 'MEMSENATE',
+  column = 5,
+  indepvar = 'Upper size',
   indepvar2 = 'K',
[…]

### 2021-03-21 dataset/datasetBuilding.R
add instdesign and audit dataset

@@ -1,7 +1,7 @@
 ##################################################################
 ## Script: Building the Dataset for Distributive Politics Paper ##
 ## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Mar 21, 2021                                  ##
+## Last Modified: Mar 22, 2021                                  ##
 ##################################################################
 
 # Needed packages

### 2021-03-21 appendix/appendix.Rmd
appendix with theory begin

@@
 In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive.
-Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the XXXX, but these two papers, in our view, present the most elementary theoretical argument
+Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the original law of 1/n, but these two papers, in our view, present the most elementary theoretical argument
 
@@
 
-XXXX PAREI AQUI
-
-As the above condition suggests, the law of 1/n holds in specific situations.
-@primo2008distributive XXXX cost is when the suppose that we have a set of representatives, indexed in districts $i \in \{1, \cdots, n \}$.
+As the above condition suggests, the law of 1/n holds only in specific situations.
+@primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i.
+e., larger legislatures leading to lower expenditures.
+Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
+Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i.
+e.
+how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
+In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's.
+The degree that taxes are shared is denoted by $s$.
+Moreover, there is a deadweight loss of the taxes $\theta \geq 1$.
+The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$.
+Collecting terms, the citizens receive the following net benefit of a project with size $x$:
+
+\[
+\pi = x^\alpha m^{\beta-1} - \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta
+\]
+
+Maximizing this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects yield to the following optimal project size:
+
+\[
+x^* = \left[\left(\dfrac{\alpha}{\theta}\right)^{\dfrac{1}{\theta-\alpha}}\right]\left[\left(nm\right)^{\dfrac{\beta+\theta-1}{\theta - \alpha}}\right]\left[\left( \dfrac{n^{2-\beta-\theta}}{n-ns+s}\right)^{\dfrac{1}{\theta-\alpha}}\right]
+\]
+
+And in the graph below, we show simulations for $n$ varying from 10 to 20, holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m = 100$, and $\alpha = 0.7$.
+
+```{r, echo=FALSE, cache=TRUE, fig.align='center'}
+xstar <- function(x, beta, theta, alpha = 0.7, s = 0.5, m = 10) {
+  n = x
+  a = (alpha/theta)^(1/(theta-alpha))
+  b = (n*m)^((beta+theta-1)/(theta-alpha))
+  c = ((n^(2-beta-theta))/(n-n*s+s))^(1/(theta-alpha))
+  return (a*b*c)
+}
+
+curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
+      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
+curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
+      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
+```
+
+Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive.
+Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX.
+Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.
 
@@
 
-5. The estimation method used in the papers (variable `method`):
+5. A institution design variable, with:
+ - `Unicameral` (e.g., US Municipalities)
+ - `Bicameral` (e.g., US States)
+ - `Mixed` (e.g., countries with unicameral and bicameral in the same dataset).
+
+6. The estimation method used in the papers (variable `method`):
   - `OLS`: Ordinary-Least Squares in Cross-Sectional data.
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+method,
               test = "knha",
@@
 
-We have the following results for the meta-regressions of Expenditure as a Percentage of GDP:
-
-1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-
-2. All other moderators remain insignificant.
+All moderators are insignificant in the meta-regressions of Expenditure as a Percentage of GDP.
 
@@
 
-For all the coefficients, we have the following results:
-
-1. Passing from `Majoritarian` to `Non-Majoritarian`, decreases significantly the effects found in our models.
-
-2. All other moderators remain insignificant.
+Even for all the coefficients, all moderators remain insignificant.
 
@@
 
-6. The estimation method used in the paper (OLS, PANEL, IV, or RDD).
+6. The institution design: whether the legislature in the analysis is unicameral, bicameral, or mixed.
+
+7. The estimation method used in the paper (OLS, PANEL, IV, or RDD).
 

### 2021-03-21 appendix/appendix.Rmd
change todo and para appendix

@@
 Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive.
-Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX.
+Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@chen_malhotra_2007], the XXXX, and XXXX.
 Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.

### 2021-03-23 appendix/appendix.Rmd
catarina points start

--- 2021-03-21 appendix/appendix.Rmd
@@
 
-In this section, we present the @weingast1981political theoretical arguments behind the law of 1/n, and their rebuttal by @primo2008distributive.
-Many of the papers included in this meta-analysis also have their own version of why we need a refined version of the original law of 1/n, but these two papers, in our view, present the most elementary theoretical argument
+In this section, we present the law of 1/n as in @weingast1981political, and the refinement proposed by @primo2008distributive. In our view, these two papers present the most theoretically  argument
 
 In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark.
-Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout the entire tax pool (all constituencies).
-The corollary of their suggestion is that larger legislatures generate more expenditure.
-
-In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$ and there are convex costs associated with the project.\footnote{Concave in this case means that $b'>0$ and $b''<0$.
-Convex in this case mean that $c'>0$ and $c''>0$.
+Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout all constituencies.
+The corollary of their model is that larger legislatures generate more public spending.
+
+In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$.
+Convex means that $c'>0$ and $c''>0$.
 We assume that the derivatives are well defined throughout the analysis.
-Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume equal constituencies.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e.
+Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume that we will always employ a symmetric Nash equilibrium.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e.
 g., hire a local company to build the project).
@@
 e., larger legislatures leading to lower expenditures.
+
 Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
@@
 
-Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as in @primo2008distributive.
-Here, we showed the variation changing only the deadweight losses, but there are many other theoretical reasons, such as the limiting power of the upper houses [@malhotra], the XXXX, and XXXX.
-Most of the literature after @weingast1981political, attempted to find the empirical complements to this original formulation.
+Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive.
+Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX.
+Most of the literature after @weingast1981political, focused on complement their original formulation.
 

### 2021-03-23 dataset/datasetBuilding.R
dataset fix

@@ -31,7 +31,7 @@ dat <- data.frame(
   agglevel = 'Countries',
   location = 'World',
   locationISO = 'Multiple (37)',
-  instdesign = 'Bicameral',
+  instdesign = 'Mixed',
   title = 'Legislative organization and government spending: cross-country evidence',
   author = 'Bradbury and Crain',
   authorCite = 'J. Bradbury & M. Crain',
@@ -63,7 +63,7 @@ dat <- rbind(dat,
                agglevel = 'Countries',
                location = 'World',
                locationISO = 'Multiple (37)',
-               instdesign = 'Bicameral',
+               instdesign = 'Mixed',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
                authorCite = 'J. Bradbury & M. Crain',
@@ -97,7 +97,7 @@ dat <- rbind(dat,
                agglevel = 'Countries',
                location = 'World',
                locationISO = 'Multiple (37)',
-               instdesign = 'Bicameral',
+               instdesign = 'Mixed',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
                authorCite = 'J. Bradbury & M. Crain',
@@ -131,7 +131,7 @@ dat <- rbind(dat,
                agglevel = 'Countries',
                location = 'World',
                locationISO = 'Multiple (37)',
-               instdesign = 'Bicameral',
+               instdesign = 'Mixed',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
                authorCite = 'J. Bradbury & M. Crain',
@@ -165,7 +165,7 @@ dat <- rbind(dat,
                agglevel = 'Countries',
                location = 'World',
                locationISO = 'Multiple (37)',
-               instdesign = 'Bicameral',
+               instdesign = 'Mixed',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
                authorCite = 'J. Bradbury & M. Crain',
@@ -198,7 +198,7 @@ dat <- rbind(dat,
                agglevel = 'Countries',
                location = 'World',
                locationISO = 'Multiple (37)',
-               instdesign = 'Bicameral',
+               instdesign = 'Mixed',
                title = 'Legislative organization and government spending: cross-country evidence',
                author = 'Bradbury and Crain',
[…]

### 2021-03-23 dataset/datasetBuilding.R
building only unicameral variable

@@ -5569,6 +5569,9 @@ dat <- arrange(dat, id) %>%
   relocate(id_level2, .after = id_level1) %>%
   mutate(VAR = SE^2)
 
+# Unicameralism dummy
+dat$unicamOnly <- ifelse(dat$instdesign == 'Unicameral', 1, 0)
+
 # Full data and partial data
 fulldat <- dat
 dat <- dat %>%

### 2021-03-23 appendix/appendix.Rmd
appendix institution design and sparse matrix in rma.mv

@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
+              sparse = TRUE,
               tdist = TRUE,
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               subset = fulldat$depvar2=='ExpPC',
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               subset = dat$depvar2=='logExpPC',
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               subset = fulldat$depvar2=='logExpPC',
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               subset = dat$depvar2=='PCTGDP',
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
             subset = fulldat$depvar2=='PCTGDP',
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+
-                published+elecsys2+method,
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               slab = dat$authoryear)
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+
-                published+elecsys2+method,
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
               tdist = TRUE,
+              sparse = TRUE,
               slab = fulldat$authoryear)

### 2021-03-23 dataset/datasetBuilding.R
change coeff

@@ -3225,7 +3225,7 @@ dat <- rbind(dat,
                coef = 0.1594,
                scoef = 'P',
                scoefsig = 'P',
-               SE = 0.1443/3.05
+               SE = 0.1594/3.05
              ))
 
 dat <- rbind(dat,
@@ -5420,40 +5420,6 @@ dat <- rbind(dat,
                SE = 0.0491
              ))
 
-# dat <- rbind(dat,
-#              data.frame(
-#                id = 'A258',
-#                published = 'Yes',
-#                usemeta = 0, 
-#                method = 'PANEL',
-#                method2 = 'OLS/PANEL',
-#                elecsys = 'Maj',
-#                elecsys2 = 'Maj', 
-#                elecsys3 = 'M',
-#                agglevel = 'Local',
-#                location = 'US',
-#                locationISO = 'USA',
-#                instdesign = 'Unicameral',
-#                title = 'Government Form and Public Spending: Theory and Evidence from US Municipalities',
-#                author = 'Coate and Knight',
-#                authorCite = 'S. Coate & B. Knight',
-#                year = 2011,
-#                authoryear = 'Coate and Knight (2011)',
-#                journal = 'American Economic Journal: Economic Policy',
-#                journalCode = 'AEJ',
-#                web = 'https://www.aeaweb.org/articles?id=10.1257/pol.3.3.82',
-#                table = 4,
-#                column = 4,
-#                indepvar = 'Log Council Size',
-#                indepvar2 = 'logN',
-#                depvar = 'Log Public Spending Per Capita',
-#                depvar2 = 'logExpPC',
-#                coef = 0.2132,
-#                scoef = 'P',
-#                scoefsig = 'P',
-#                SE = 0.0491
-#              ))
-
 dat <- rbind(dat,
              data.frame(
                id = 'A117',
@@ -5568,9 +5534,6 @@ dat <- arrange(dat, id) %>%
   relocate(id_level1, .after = id_model) %>%
   relocate(id_level2, .after = id_level1) %>%
   mutate(VAR = SE^2)
-
-# Unicameralism dummy
-dat$unicamOnly <- ifelse(dat$instdesign == 'Unicameral', 1, 0)
 
 # Full data and partial data
 fulldat <- dat

### 2021-03-23 appendix/appendix.Rmd
fixing appendix to match new dataset

@@
 library("compareGroups"); library(dmetar)
-
-# Load datasets
-load("../dataset/dataCoefs.RData")
 
@@
 }
+
+# Load datasets
+load("../dataset/dataCoefs.RData")
 ```
@@
 
-In this section, we present the law of 1/n as in @weingast1981political, and the refinement proposed by @primo2008distributive. In our view, these two papers present the most theoretically  argument
+In this section, we present the law of 1/n as formulated by @weingast1981political, and the refinement proposed by @primo2008distributive.
 

### 2021-04-02 dataset/datasetBuilding.R
dataset changes

@@ -483,6 +483,205 @@ dat <- rbind(dat,
                SE = 0.00048/2.72
              ))
 
+
+dat <- rbind(dat,
+             data.frame(
+               id = 585,
+               published = 'Yes',
+               usemeta = 0, 
+               method = 'PANEL',
+               method2 = 'OLS/PANEL',
+               elecsys = 'Mixed',
+               elecsys2 = 'Non-Maj', elecsys3 = 'NM',
+               agglevel = 'Countries',
+               location = 'World',
+               locationISO = 'Multiple (37)',
+               instdesign = 'Mixed',
+               title = 'Legislative organization and government spending: cross-country evidence',
+               author = 'Bradbury and Crain',
+               authorCite = 'J. Bradbury & M. Crain',
+               year = 2001,
+               authoryear = 'Bradbury and Crain (2001)',
+               journal = 'Journal of Public Economics',
+               journalCode = 'JPubE',
+               web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
+               table = 3,
+               column = 1,
+               indepvar = 'Unicameral Size',
+               indepvar2 = 'N',
+               depvar = 'Percent of GDP',
+               depvar2 = 'PCTGDP',
+               coef = 0.019286,
+               scoef = 'P',
+               scoefsig = 'P',
+               SE = 0.019286/14.97
+             ))
+
+dat <- rbind(dat,
+             data.frame(
+               id = 585,
+               published = 'Yes',
+               usemeta = 0, 
+               method = 'PANEL',
+               method2 = 'OLS/PANEL',
+               elecsys = 'Mixed',
+               elecsys2 = 'Non-Maj', elecsys3 = 'NM',
+               agglevel = 'Countries',
+               location = 'World',
+               locationISO = 'Multiple (37)',
+               instdesign = 'Mixed',
+               title = 'Legislative organization and government spending: cross-country evidence',
+               author = 'Bradbury and Crain',
+               authorCite = 'J. Bradbury & M. Crain',
+               year = 2001,
+               authoryear = 'Bradbury and Crain (2001)',
+               journal = 'Journal of Public Economics',
+               journalCode = 'JPubE',
+               web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
+               table = 3,
+               column = 2,
+               indepvar = 'Unicameral Size',
+               indepvar2 = 'N',
+               depvar = 'Percent of GDP',
+               depvar2 = 'PCTGDP',
[…]

### 2021-04-02 appendix/appendix.Rmd
changing dataset and appendix new dataset results

@@
 Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive.
-Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX.
+Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@matsusaka2005endogeneity], the type of government [@coate2011government], the existence of supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], ideological positions [@bjedov2014impact], among other characteristics.
 Most of the literature after @weingast1981political, focused on complement their original formulation.

### 2021-04-02 dataset/datasetBuilding.R
fix lines dataset

@@ -1944,105 +1944,6 @@ dat <- rbind(dat,
 
 dat <- rbind(dat,
              data.frame(
-               id = 849,
-               published = 'No',
-               usemeta = 0,
-               method = 'IV',
-               method2 = 'IV',
-               elecsys = 'Maj',
-               elecsys2 = 'Maj', elecsys3 = 'M',
-               agglevel = 'Local',
-               location = 'US',
-               locationISO = 'USA',
-               instdesign = 'Unicameral',
-               title = 'Districts, spillovers, and government overspending',
-               author = 'Baqir',
-               authorCite = 'R. Baqir',
-               year = 1999,
-               authoryear = 'Baqir (1999)',
-               journal = NA,
-               journalCode = 'Unpub',
-               web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-               table = 5,
-               column = 6,
-               indepvar = 'Log (Council Size)',
-               indepvar2 = 'logN',
-               depvar = 'Expenditure Share',
-               depvar2 = 'PCTGDP',
-               coef = 2.113,
-               scoef = 'P',
-               scoefsig = 'P',
-               SE = 2.113/6.095
-             ))
-
-dat <- rbind(dat,
-             data.frame(
-               id = 849,
-               published = 'No',
-               usemeta = 0,
-               method = 'OLS',
-               method2 = 'OLS/PANEL',
-               elecsys = 'Maj',
-               elecsys2 = 'Maj', elecsys3 = 'M',
-               agglevel = 'Local',
-               location = 'US',
-               locationISO = 'USA',
-               instdesign = 'Unicameral',
-               title = 'Districts, spillovers, and government overspending',
-               author = 'Baqir',
-               authorCite = 'R. Baqir',
-               year = 1999,
-               authoryear = 'Baqir (1999)',
-               journal = NA,
-               journalCode = 'Unpub',
-               web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-               table = 5,
-               column = 7,
-               indepvar = 'Log (Council Size)',
-               indepvar2 = 'logN',
-               depvar = 'Expenditure Share',
-               depvar2 = 'PCTGDP',
-               coef = 0.775,
-               scoef = 'P',
-               scoefsig = 'P',
-               SE = 0.775/2.088
-             ))
-
-dat <- rbind(dat,
-             data.frame(
-               id = 849,
[…]

### 2021-04-09 appendix/appendix.Rmd
some edits to the appendix, more coming

--- 2021-03-23 appendix/appendix.Rmd
@@
   }
-
   # Graph limits
   limg <- max(abs(c(mod2$lower, mod2$upper)))
-
   # Build plot
@@
 build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
-
   mod2 <- estim_het(dat = dat, 
@@
                     hetvar = hetvar)
-
   mod2 <- data.frame(mod2)
@@
   TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100
-
   # Graph limits
   limg <- max(abs(c(mod2$lower, mod2$upper)))
-
   # Build plot
@@
 
-# Law of 1/n Model
-
-In this section, we present the law of 1/n as formulated by @weingast1981political, and the refinement proposed by @primo2008distributive.
-
-In their seminal paper, @weingast1981political argue that the number of legislators will increase public spending more than the optimal economic benchmark.
-Politicians have the incentive to over-provide concentrated benefits to the constituencies, spreading the costs throughout all constituencies.
+# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_
+
+In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.
+
+In their seminal paper, @weingast1981political argue that a high number of legislators will increase public spending beyond the optimal economic benchmark.
+They suggest that politicians have an incentive to over-provide concentrated benefits to their constituencies, spreading the costs across all constituencies through generalised taxation.
 The corollary of their model is that larger legislatures generate more public spending.
@@
 We assume that the derivatives are well defined throughout the analysis.
-Moreover, we drop the constituency index, to facilitate reading the model and because of this, the reader should assume that we will always employ a symmetric Nash equilibrium.} The first cost, $c_1(x)$, comprises the expenses within the constituency (e.
+Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e.
 g., hire a local company to build the project).
@@
 g., hire a company from another state).
-The third cost $c_3(x)$ captures the externalities generated by the project (e.
+The third cost $c_3(x)$, captures the externalities generated by the project (e.
 g., how much prices shift because local economic factors are being used to provide the project).
-The total cost is then equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$.
+The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$.
 The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.
 
-Following their model, the economic efficiency is achieved when the marginal costs are equal the marginal benefits of increase the project size.
+Following their model, projects are economically efficient when the marginal costs are equal the marginal benefits of increase the project size.
 This leads to the economic optimal project size, $x^E$.
 The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$.
-However, the actual projects that are implemented have a different structure.
-First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represent the number of constituencies.
+However, the projects that are actually implemented have a different structure.
+First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies.
 Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms.
-Therefore, the benefits and costs of implement a project with size $x$ have the following structure:
+Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:
 
@@
 
-Totally differentiating $x$ with respect to $n$, gives us:
+Totally differentiating $x$ with respect to $n$ gives us the following:
 
@@
 Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size.
-The law of 1/n holds when the denominator is negative.
+The _law of 1/n_ holds when the denominator is negative.
 $b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$.
-Then, the law of 1/n is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
-
-As the above condition suggests, the law of 1/n holds only in specific situations.
-@primo2008distributive advances the theory by considering other situations where the law may not hold, and also situations when a reverse prediction of the law of 1/n holds, i.
+Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
+
+As the above condition suggests, the _law of 1/n_ holds only in specific situations.
+@primo2008distributive advances the theory by considering other situations where the law may not hold, and also argues that there are cases in which a reverse _law of 1/n_ holds, i.
 e., larger legislatures leading to lower expenditures.
@@
 Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
-Consider a local public good that generates a per capita benefit, according to its size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i.
+Consider a local public good that generates a per capita benefit according to size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i.
 e.
 how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
-In terms of costs, consider a linear cost $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's.
+In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's.
 The degree that taxes are shared is denoted by $s$.
@@
 
-Maximizing this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects yield to the following optimal project size:
+Maximising this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects, we find the following optimal project size:
 
@@
 
-Therefore, there are possibilities for having the law of 1/n in the direction predicted by @weingast1981political, and in a reverse direction, as proposed by @primo2008distributive.
-Here, we showed the variation in deadweight losses, but there are many other theoretical reasons, such as the existence of upper houses [@chen_malhotra_2007], the popular initiatives [@XXXX], and XXXX.
-Most of the literature after @weingast1981political, focused on complement their original formulation.
+Therefore, we see that both the _law of 1/n_ and its reverse formulation are equally plausible.
+Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen_malhotra_2007], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].
 
 # Search Criteria
-
-XXXX CATARINA AND HUZEYFE: FIX THIS
 
@@
 The selection process was conducted by two authors in three phases.
-In the first round, we excluded all titles that were clearly unrelated to our topic of interest.
-For instance, we curiously found articles about car motors amidst our sample.
-We consider this a preliminary step, since we were not able to eliminate a large number of entries.
+In the first phase, we excluded all titles that were clearly unrelated to our topic of interest.
+This was only a preliminary step, as we were not able to eliminate a large number of entries.
 Then, we read all abstracts.
-We chose to maintain those which indicated that either government expenditure or legislative structures were the main subject of the paper.
-For instance, if the paper sought to identify variables that increased government size, it was maintained.
-Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were also included.
-This allowed us to significantly reduce our sample to 376 records.
+We kept all publications whose main topics were either government expenditure or legislative structures.
+Abstracts that indicated that the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were included.
+This allowed us to significantly reduce our sample.
 
@@
 To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure.
-If the publication had all three, it was maintained.
+If the publication had all three, we kept it in our sample.
 Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
@@
 Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information.
-We decided which variables to keep by following the current practices of the literature.
-In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
+In this phase, we also collected information on whether the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
 Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.
@@
 
-We selected the final pool of articles based on two criteria regarding their reported coefficients:
-
-1.  Matched treatment variable:
+We selected the final pool of articles based on two criteria, namely the treatment and the outcome variables employed in the paper. The categories follow below:
+
+1.  Treatment variables:
 
@@
 
-2.  Matched outcome variable:
+2.  Outcome variables:
 
@@
 
-Our data are comprised of two datasets.
+Our meta-analytic data are comprised of two datasets.
 The first dataset has the main coefficients reported in the studies.
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
+```{r, fig.width=6, fig.height=3, fig.cap="Electoral Systems", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
+```{r, fig.width=6, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
+```{r, fig.width=6, fig.height=3, fig.cap="Independent variables across the law of 1/n studies", size="footnotesize", echo = FALSE, cache=TRUE}
 dat %>%
@@
 We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$).
-The additional moderators are: 1) electoral system; 2) data aggregation level; 3) estimation method; 4) publication year; 5) paper publication in an academic journal.
-The table below presents descriptive statistics for these moderators in our selection of articles.
-
-```{r, warning=F, message=F, echo = FALSE, cache=TRUE}
+The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal.
+The descriptive statistics for the moderators are available below.
+
+```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
-aux <- select(fulldat, usemeta2, indepvar2, year, published,
-              elecsys2, method) %>%
+levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
+aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
+              year, published) %>%
   rename(`Independent Variables` = indepvar2,
+         `Electoral system`      = elecsys2,
+         `Estimation method`     = method,
          `Year`                  = year,
-         `Published work` = published,
-         `Electoral system` = elecsys2,
-         `Estimation method` = method)
+         `Published work`        = published)
 
 export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-                        show.p.overall = F, show.all = T), caption = "Descriptive Statistics of Moderators")
+                        show.p.overall = F, show.all = T),
+          caption = "Descriptive Statistics of Moderators",
+          format  = "latex")
 ```
@@
 
--   $H_0$: the proportion of positive and negative signs are indistinguishable ($p=0.5$).
-
-As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) could be true.
+-   $H_0$: the proportion of positive and negative signs are statistically equal ($p=0.5$).
+
+As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true.
 In this case, the alternative hypothesis is $p\neq 0.5$.
@@
 This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not.
-All these factors increase the levels of study heterogeneity.
 The binomial test ignores the design discrepancies and focuses on the overall reported effect.
-Second, this test has the advantage of being straightforward and easy to interpret.
-It requires very few assumption and has a direct statistical formulation.
-The disadvantage is that we can extract more information from the articles with meta-regressions, as we see in the next sections.
+Second, this test has the advantages of requiring few assumptions and being easy to interpret.
+The disadvantage is that the test is not as informative as the meta-regressions, as we shall see in the next sections.
 
@@
 
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` studies, out of `r sum(table(aux$scoef))`, had a positive sign.
+Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
 The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
@@
 
-For the log of the number of legislators in the lower house ($\log(N)$), the results follow below.
+For the log of the number of legislators in the lower house ($\log(N)$), the results are as follows:
 
@@
 
-Out of `r sum(table(aux$scoef))`, `r as.numeric(table(aux$scoef)[2])` had a positive sign.
+Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])` have a positive sign.
 The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
@@
 
-Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` had a positive sign.
+Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
 The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`.
@@
 In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models.
-The fixed effects model assumes that there exists only one true effect, and that all estimates are an attempt to uncover this effect.
+The fixed effects model assumes that there exists a single true effect and all estimates are an attempt to uncover this effect.
 The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.
 
-In this paper, we a random-effects model.
+In this paper, we employ a random-effects model.
 The empirical papers testing the *law of 1/n* are very diverse.
@@
 First, they make our estimates notably disperse.
-All but one of our heterogeneity tests are significant.
-When the sample sizes are large enough, we removed more heterogeneous studies, but we still had considerable dispersion in our estimates.
 Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
@@
 
-Let each study having an effect of $T_i$.
+Assume that each study has an effect of $T_i$.
 In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
@@
 
-Another crucial assumption in the meta-analysis is the independence between the results [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction].
-This assumption states that for our findings be consistent and efficient, the coefficients used in the meta-analysis have to come from different sources of variation.
+Another crucial assumption in meta-analysis is that the coefficients should be independent [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction].
+This assumption states that for our findings to be consistent, the coefficients must come from different sources of variation.
 However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable.
-While our short dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
-This because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
-Between robustness tests, multiple dependent and independent variables, and the papers that share similar datasets, the independence assumption is violated.
-To correct for this problem, we use a multi-level random effects model [@cheung2014modeling].
-The main difference from the single-level random effects model is that we add two extra levels of dependence: the participants and the studies levels.
-All these levels are assumed to absorb the dependence in the data, leaving for the main coefficient, the independent effect of legislature size on public spending.
-
-There are two levels in the main models. First, we build a common index for papers that share the same dataset specifications. The papers with common indexing are:
-
-| Paper IDs                                   | Source of Dependence                                                     |
+While our restricted dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
+This is because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
+To correct for the violation of the independent assumption, we use a multi-level random effects model [@cheung2014modeling].
+We add two extra levels to the regular random effects model, one that indicates the publication ID and another that indicates the data used in the original article.
+These levels are assumed to remove dependence structures in the data, therefore improving the estimates of our coefficient of interest, which is the effect of legislature size on public spending.
+
+There are two levels in the main models. First, we build a common index for papers that share the same data specifications. The papers with common indexing are:
+
+| Publication IDs                             | Source of Dependence                                                     |
 |---------------------------------------------|--------------------------------------------------------------------------|
-| 3, 42, 132, <br>165, 439, 441, <br>467, 505 | US States Dataset                                                        |
-| 408, 208, A258                              | US Municipalities Dataset                                                |
-| 849, 578                                    | US Municipalities Dataset<br>and Same Author in two<br>Different Studies |
+| 3, 42, 132, 165, 439, 441, 467, 505         | US States Data                                                           |
+| 408, 208, A258                              | US Municipalities Data                                                   |
+| 849, 578                                    | US Municipalities Data and Same Author in Two Different Studies          |
 
@@
 g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs.
-In the case of the full dataset, the results change considerably, because authors fit several models within the same paper.
-In the case In any case, we use multi-level random effects for all the estimated models in this paper.
-
-To study the possibility of of publication bias, for all models we add a funnel plot and an @egger1997bias test for distribution asymmetry.
-The funnel plot displays the possibility of having a file-drawer effect, meaning that null results are disproportionately less represented in our sample.
-In this plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome.
-If they are asymmetric, it evidences a possible file-drawer effect.
-
-In all empirical estimates, we use the package `meta`, and the package `dmetar`, described in @harrer2019doing [here](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/random.html).
-To empirically implement the random effects model, we need to choose a method to estimate the true effect size variance, $\tau^2$, which in our formulation, represents the variance of $\xi_i$.
-We selected the **Restricted Maximum Likelihood Estimator**, as the literature regards it the most precise when analysing continuous measures, such as we have in our data [@veroniki2016methods].
-
-We combined the three independent variables ($N$, $\log(N)$, and $K$) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
-This formed a $3 \times 3$ table, and in the following pages we present the results for each of these combinations.
+In regards to the full dataset, the results change considerably, because authors fit several models within the same paper.
+In any case, we use multilevel random effects for all the estimated models in this paper.
+
+To study the possibility of of publication bias, we add a funnel plot and an @egger1997bias test for distribution asymmetry for every model.
+Funnel plots display the possibility of having a file-drawer effect, meaning that null results are under-represented in our sample.
+In this type of plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome.
+If they are asymmetric, it provides evidence for a file-drawer effect.
+
+We use the `R` packages `meta` and `dmetar` in all estimates [@harrer2019doing].
+We employ the *Restricted Maximum Likelihood Estimator* to assess the variance of the true effect size ($\tau^2$), which in our formulation represents the variance of $\xi_i$.
+The literature regards this estimator as the most precise when analysing continuous measures, such as the ones we have in our data [@veroniki2016methods].
+
+We combine the three independent variables ($n$, $\log(n)$, and $k$) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
+This formed a $3 \times 3$ table, yet not all combinations are available in the data.
+The results are shown below.
 
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+And to assess the possibility of publication bias, we add the funnel plot below:
 
@@
 
-The *law of 1/n* was created for majoritarian systems.
-In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
-We estimated a subgroup analysis using a binary electoral system.
+The *law of 1/n* was introduced to describe majoritarian systems, but the theory has also been applied to non-majoritarian electoral systems.
+We estimated a subgroup analysis using a binary indicator for electoral system.
 
@@
 
-Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved.
-Both are non-significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+Therefore, we find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita.
+Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
 
@@
 
-Now, we look into the upper house size (K). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+Now we look into the upper house size (*k*). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
 
@@
 5. All other moderators are insignificant.
-
-# Session Information
-
-```{r, size="footnotesize", echo = FALSE}
-sessionInfo()
-```

### 2021-04-11 appendix/appendix.Rmd
revised appendix

@@
 The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending.
-The search string was as follows: *(“upper chamber size” OR "lower chamber size" OR “council size” OR “parliament size” OR “legislature size” OR “number of legislators” OR “legislative size") AND (“spending” OR “expenditure" OR “government size”)*.
+The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`.
 We scraped Google Scholar on March 5th, 2021.
@@
 
-```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
+```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
 \usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
   \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
-
   \footnotesize
@@
 
+\bigskip
+
+```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
+\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
+  \footnotesize
+  \linespread{1.0}
+  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Screening 1}};
+  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening 2}};
+  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};
+  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};
+  \node (id) [phase, right of = ID, xshift = 1cm] {Clean records identified through webscraping  \\ \textbf{(n = 3041)}};
+  \node (1st) [exc, right of = id, xshift = 3cm] {Records excluded after reading title, or in languages other than English, book chapters, doctoral theses, and duplicates \\ \textbf{(n = 2603)}};
+  \node (screen) [phase, below of = id] {Abstracts assessed for Eligibility \\ \textbf{(n = 483)}};
+  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading abstract \\ \textbf{(n = 339)}};
+  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 99)}};
+  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 86)}};
+  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 10)}};
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 3)}};
+  \draw [arrow] (id) -- (1st);
+  \draw [arrow] (id) -- (screen);
+  \draw [arrow] (screen) -- (2nd);
+  \draw [arrow] (screen) -- (elig);
+  \draw [arrow] (elig) -- (3rd);
+  \draw [arrow] (elig) -- (inc_1);
+  \draw [arrow] (inc_1) -- (4th);
+  \draw [arrow] (inc_1) -- (inc_2);
+ \end{tikzpicture}
+```
+
 # Meta-Analysis Dataset
@@
 
-In this section, we show the descriptive statistics for our sample.
-We focus on the following paper characteristics: study year, whether the paper has been published or not, the electoral system of the country discussed in the original study, the data aggregation level, as well as the distribution of the dependent and independent variables of interest.
+Here we show the descriptive statistics for our sample.
+We focus on the following paper characteristics: study year; paper publication; the  electoral system mentioned in the publication; and the distribution of the dependent and independent variables of interest.
 
@@
 
-For study year, we have an average of `r round(mean(dat$year), 2)`, with standard deviation of `r round(sd(dat$year), 2)`.
+The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`.
 The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`.
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=2.5, fig.cap="Was the study published?", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, fig.width=6, fig.height=3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
+```{r, fig.width=6, fig.height=2.3, fig.cap="Dependent variables across the law of 1/n studies", size="footnotesize", cache=TRUE, echo = FALSE}
 dat %>%
@@
 
-```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
+```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
 dat %>%
@@
 
+\newpage
+
 Standard errors:
 
-```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=4, echo = FALSE}
+```{r, size="footnotesize", cache=TRUE, fig.width=5, fig.height=3.3, echo = FALSE}
 dat %>%
@@
 The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal.
-The descriptive statistics for the moderators are available below.
 
@@
 The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
+Thus, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
 
@@
 
+The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita is available below.
+
 ```{r, cache=TRUE, echo = FALSE, size="footnotesize"}
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 We estimated a subgroup analysis using a binary indicator for electoral system.
+The results may be seen below.
+
+We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita.
+Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
 
@@
 
-Therefore, we find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita.
-Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
-
-## Log Lower House Size and Expenditure per Capita
+## Log of Lower House Size and Expenditure per Capita
 
@@
 
-And the forest plot:
-
-```{r, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
+```{r, fig.width=7, fig.height=3, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+We see no evidence of publication bias:
+
+```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+The funnel plot shows no evidence of publication bias.
 
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=10, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+The funnel plot:
 
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+The funnel plot to test for publication bias:
 
@@
 
-The forest plot follows below:
-
-```{r, echo = FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
+```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+The funnel plot is available below:
 
@@
 
-The forest plot follows below:
-
 ```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+As in our previous estimations, we find no evidence of file-drawer effect.
 
@@
 
+Here we estimate a meta-analysis of the papers which use instrumental variables. The results may be seen below.
+
 ```{r, size="footnotesize", cache=TRUE, echo = FALSE}
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+No evidence of publication bias, as shown in the following tunnel plot:
 
@@
 
+In this subsection, we run a meta-analysis with papers that include regression discontinuity designs.
+
 ```{r, size="footnotesize", cache=TRUE, echo = FALSE}
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+And to assess the possibility of publication bias, we add the funnel plot below:
+
+```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=9, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
+We see that majoritarian systems do not have a clear positive effect on budgetary spending.
+The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
+Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
+
+```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
 build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
@@
 ```
-
-Therefore, we see that majoritarian systems do not have a clear positive effect on budgetary spending.
-The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08.
-Both are not statistically significant, but they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
 
@@
 
-And the forest plot:
-
-```{r, fig.width=9, fig.height=8, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+The forest plot:
+
+```{r, fig.width=9, fig.height=10, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+The funnel plot suggests no publication bias.
 
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
-
 ```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=7, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+And the funnel plot:
+
+```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=7, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+And here is the funnel plot to assess the possibility of publication bias:
+
+```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-And to assess the possibility of publication bias, we add funnel plot below:
+And the funnel plot:
 

### 2021-05-06 appendix/appendix.Rmd
edit text appendix

@@
 
-[^freire]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
+[^freire]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
 
@@
 Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e.
-g., hire a local company to build the project).
-The second cost, $c_2(x)$, captures the expenses outside the constituency (e.
-g., hire a company from another state).
-The third cost $c_3(x)$, captures the externalities generated by the project (e.
+g., hiring a local company for the project).
+The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e.
+g., hiring a company from another state).
+Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e.
 g., how much prices shift because local economic factors are being used to provide the project).
@@
 
-Following their model, projects are economically efficient when the marginal costs are equal the marginal benefits of increase the project size.
+Projects are economically efficient when the marginal costs are equal to the marginal benefits of the project size.
 This leads to the economic optimal project size, $x^E$.
@@
 
-And rearranging the terms, yields to the following expression for $\dfrac{dx}{dn}$:
+And rearranging the terms, we find the following expression for $\dfrac{dx}{dn}$:
 
@@
 
-Note that the numerator is always positive, as the marginal investment costs inside and outside the district increases with project size.
+Note that the numerator is always positive, as the marginal investment costs inside and outside the district increase according to the project size.
 The _law of 1/n_ holds when the denominator is negative.
@@
 As the above condition suggests, the _law of 1/n_ holds only in specific situations.
-@primo2008distributive advances the theory by considering other situations where the law may not hold, and also argues that there are cases in which a reverse _law of 1/n_ holds, i.
-e., larger legislatures leading to lower expenditures.
+@primo2008distributive advance that theory by considering other situations where the _law_ may not hold, and they also argue that there are cases in which a _reverse law of 1/n_ holds, that is, larger legislatures may lead to lower public expenditures.
 
 Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
-Consider a local public good that generates a per capita benefit according to size $x$ of $b(x, m) = x^\alpha m^{\beta-1}$, where $\beta$ is the degree of congestion of the public good, i.
-e.
-how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
-In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district share taxes between their payments and the central government's.
+Consider a local public good that generates a per capita benefit of $b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the degree of congestion of the public good, that is, how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
+In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district pay both local and federal government taxes.
 The degree that taxes are shared is denoted by $s$.
@@
 The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$.
-Collecting terms, the citizens receive the following net benefit of a project with size $x$:
+Therefore, the citizens receive the following net benefit of a project with size $x$:
 
@@
 
-Therefore, we see that both the _law of 1/n_ and its reverse formulation are equally plausible.
+Thus, we see that both the _law of 1/n_ and its reverse formulation are equally plausible.
 Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen_malhotra_2007], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].
@@
 This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is a seminal contribution to the field.
+To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is the fundamental contribution to the field.
 Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
@@
 The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated.
-Our code is available in section \ref{sub:scrap} below.
+Our code is available in the `R` script available in this repository.
 We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses.
@@
 
-We complemented this by doing a term search on Google Scholar after having finished the entire eligibility procedure on the first sample.
-We formulated the search string based on the terms and expressions that appeared most commonly in the articles included in our meta-analysis.
+We complemented this process by doing a term search on Google Scholar after having finished the entire eligibility procedure in the first sample.
+We formulated the search string based on the terms and expressions that appeared most frequently in the articles included in our meta-analysis.
 The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending.
 The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`.
-We scraped Google Scholar on March 5th, 2021.
+We scraped Google Scholar on March 5^th^, 2021.
 Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously.
@@
 This resulted in 3,041 additional records.
-
 Combining the two search strategies, we assessed a total of 5,705 records.
@@
 
-The third phase consisted of filling out tables for each of the remaining 47 articles to systematically evaluate their eligibility.
-Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information.
-In this phase, we also collected information on whether the paper had been published, and if it explicitly discussed the \textit{law of 1/n}.
-Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.
+The third phase consisted of filling out tables for each of the remaining 47
+articles to systematically evaluate their eligibility. Since authors use
+different measures for government spending and the number of lower/upper house
+members, we extracted all coefficients that provided this information. In this
+phase, we also collected information on whether the paper had been published,
+and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
+we excluded two studies from the first sample, as they did not have the
+dependent/independent variables we collected for our meta-analysis. We then
+included the 3 papers we found in the second search, as both conformed to our
+criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
+articles.
 
@@
 Our meta-analytic data are comprised of two datasets.
-The first dataset has the main coefficients reported in the studies.
+The first dataset has the main coefficients reported in the selected studies.
 These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them.
@@
 Studies were included in our sample regardless of their publication status.
-From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were not published.
+From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were not published.
 
@@
 One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies.
-In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, the votes are geographically concentrated.
+In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, votes are geographically concentrated.
 The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}
@@
 -   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Per Capita Expenditure papers
+-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
 -   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Natural Log of Per Capita Expenditure papers
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
 
@@
 
-Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[2])`).
+Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[3])`).
 The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`).
-Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[3])`).
+Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[1])`).
 As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.
@@
   mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
-                                                  "N (lower house legislators)",
-                                                  "Log N"))) %>%
+                                                  "Log N",
+                                                  "N (lower house legislators)"
+                                                  ))) %>%
   ggplot(aes(x = indepvar2)) +
@@
 
-The coefficients in the papers vary considerably. In this section, we plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
+The coefficients in the papers vary considerably.
+We plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
+Most coefficients and standard deviations are close to zero.
 
@@
 
-In this paper, we employ a random-effects model.
+In this paper, we employ a random effects model.
 The empirical papers testing the *law of 1/n* are very diverse.
@@
 
-1.  **Subjects**: Counties, Municipalities, States, Provinces, Countries.
+1.  **Study sample**: Counties, Municipalities, States, Provinces, Countries.
 2.  **Electoral systems**: Majoritarian, PR, Mixed.
@@
 This assumption states that for our findings to be consistent, the coefficients must come from different sources of variation.
-However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model for the same variable.
+However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model with similar variables.
 While our restricted dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
 This is because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
-To correct for the violation of the independent assumption, we use a multi-level random effects model [@cheung2014modeling].
+To correct for the violation of the independent assumption, we use a multilevel random effects model [@cheung2014modeling].
 We add two extra levels to the regular random effects model, one that indicates the publication ID and another that indicates the data used in the original article.
@@
 
-| Publication IDs                             | Source of Dependence                                                     |
+| Publication ID                              | Source of Dependence                                                     |
 |---------------------------------------------|--------------------------------------------------------------------------|
@@
 
-All the remaining papers receive a unique index.
-As the number of the papers with these dependencies are not very high, and many characteristics within papers vary (e.
+All the remaining papers received a unique index.
+As the number of the papers with these dependencies is not very high, and many characteristics within papers vary (e.
 g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs.
-In regards to the full dataset, the results change considerably, because authors fit several models within the same paper.
+In regard to the full dataset, the results change considerably, because authors fit several models within the same paper.
 In any case, we use multilevel random effects for all the estimated models in this paper.
@@
 
-```{r, fig.width=8, fig.height=10, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
+```{r, fig.width=6, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-1. In terms of the modeling, passing from `OLS` to `PANEL` or `RDD` decreases the detected effects.
+1. In regard to the estimation method, papers that use `PANEL` data or `RDD`
+   designs have smaller effects than articles that employ `OLS` estimations.
 
@@
 
-4. Compared with OLS, Panel and RDD report significantly smaller coefficients.
+4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.
 

### 2021-05-06 appendix/script.R
add R script

@@ -1,0 +1,852 @@
+#####################################################################################
+## R code for "The Effect of Legislature Size on Public Spending: A Meta-Analysis" ##
+## Huzeyfe Alptekin, Danilo Freire, Umberto Mignozzetti, and Catarina Roman        ##
+## May 2021                                                                        ##
+#####################################################################################
+
+## Install and load required packages
+set.seed(732578) # From random.org
+
+# Required packages
+pkgs <- c("tidyverse", "meta", "metafor",
+          "readxl", "devtools", "data.table",
+          "knitr", "gridGraphics", "gridExtra",
+          "ggpubr", "kableExtra", "magick",
+          'stargazer', 'pander', 'broom')
+
+# Install if not already installed
+install <- function(x) {
+  if (x %in% rownames(installed.packages()) == FALSE)
+    install.packages(x, dependencies = T,
+                     repos = "http://cran.us.r-project.org")
+}
+lapply(pkgs, install)
+devtools::install_github("isubirana/compareGroups")
+devtools::install_github("MathiasHarrer/dmetar")
+
+# Load packages
+lapply(pkgs, require, character.only = T)
+library("compareGroups"); library(dmetar)
+
+
+## Auxiliary functions to estimate meta-analysis models
+## and create plots
+
+# Broom the multilevel model
+broom_mod <- function(mod, subgroup = FALSE) {
+  aux <- data.frame(predict(mod))
+  if (subgroup) {
+    teeff = aux$pred
+    seteeff = aux$se
+    labeff = c("Subgroup Effect")
+    loeff = c(aux$ci.lb)
+    upeff = c(aux$ci.ub)
+  } else {
+    teeff = c(aux$pred, NA)
+    seteeff = c(aux$se, NA)
+    labeff = c("Overall Effect",
+               "Prediction Interval")
+    loeff = c(aux$ci.lb, aux$cr.lb)
+    upeff = c(aux$ci.ub, aux$cr.ub)
+  }
+  mod2 <- tibble(
+    TE = as.numeric(mod$yi),
+    seTE = sqrt(mod$vi),
+    studlab = mod$slab,
+    lower = as.numeric(mod$yi)-1.96*sqrt(mod$vi),
+    upper = as.numeric(mod$yi)+1.96*sqrt(mod$vi),
+    group = 'A') %>%
+    bind_rows(.,
+              aux = tibble(
+                TE = teeff,
+                seTE = seteeff,
[…]

### 2021-05-06 appendix/appendix.Rmd
fix code descriptive stats

@@
 The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`).
-Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[1])`).
+Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[2])`).
 As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.

### 2021-05-09 appendix/appendix.Rmd
fixes flow charts

@@
 
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 18)}};
-
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 29)}};
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 19)}};
+
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 28)}};
   \draw [arrow] (id) -- (1st);
@@
   \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 13)}};
-  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 10)}};
-\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 3)}};
+  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 11)}};
+\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 2)}};
   \draw [arrow] (id) -- (1st);

### 2021-05-09 dataset/datasetBuilding.R
comment coefficient with pctgdp in paper 849

@@ -1909,38 +1909,38 @@ dat <- rbind(dat,
                SE = 0.106/1.996
              ))
 
-dat <- rbind(dat,
-             data.frame(
-               id = 849,
-               published = 'No',
-               usemeta = 0,
-               method = 'OLS',
-               method2 = 'OLS/PANEL',
-               elecsys = 'Maj',
-               elecsys2 = 'Maj', elecsys3 = 'M',
-               agglevel = 'Local',
-               location = 'US',
-               locationISO = 'USA',
-               instdesign = 'Unicameral',
-               title = 'Districts, spillovers, and government overspending',
-               author = 'Baqir',
-               authorCite = 'R. Baqir',
-               year = 1999,
-               authoryear = 'Baqir (1999)',
-               journal = NA,
-               journalCode = 'Unpub',
-               web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
-               table = 5,
-               column = 5,
-               indepvar = 'Log (Council Size)',
-               indepvar2 = 'logN',
-               depvar = 'Expenditure Share',
-               depvar2 = 'PCTGDP',
-               coef = 1.963,
-               scoef = 'P',
-               scoefsig = 'P',
-               SE = 1.963/5.702
-             ))
+#dat <- rbind(dat,
+#             data.frame(
+#               id = 849,
+#               published = 'No',
+#               usemeta = 0,
+#               method = 'OLS',
+#               method2 = 'OLS/PANEL',
+#               elecsys = 'Maj',
+#               elecsys2 = 'Maj', elecsys3 = 'M',
+#               agglevel = 'Local',
+#               location = 'US',
+#               locationISO = 'USA',
+#               instdesign = 'Unicameral',
+#               title = 'Districts, spillovers, and government overspending',
+#               author = 'Baqir',
+#               authorCite = 'R. Baqir',
+#               year = 1999,
+#               authoryear = 'Baqir (1999)',
+#               journal = NA,
+#               journalCode = 'Unpub',
+#               web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
+#               table = 5,
+#               column = 5,
+#               indepvar = 'Log (Council Size)',
+#               indepvar2 = 'logN',
+#               depvar = 'Expenditure Share',
+#               depvar2 = 'PCTGDP',
+#               coef = 1.963,
+#               scoef = 'P',
[…]

### 2021-05-10 dataset/datasetBuilding.R
update appendix and data

@@ -5641,4 +5641,4 @@ dat <- dat %>%
   filter(usemeta == 1)
 
 ## Saving
-save.image('./dataset/dataCoefs.RData')
+save.image('../dataset/dataCoefs.RData')

### 2021-05-10 appendix/building_paper_dataset.R
housekeeping

@@ -1,288 +1,0 @@
-##############################################################
-## Script: Scrapping Papers for Distributive Politics Paper ##
-## Authors: Alptekin, Freire, Mignozzetti, and Roman        ##
-## Last Modified: Mar 12, 2021                              ##
-##############################################################
-
-# Note: this script is out of order, and contains
-#       the code for scraping the article's data
-
-# Required packages
-pkgs <- c("tidyverse", "rvest", "RSelenium")
-
-# Install the packages if necessary
-installIfNot <- function(x) {
-  if (x %in% rownames(installed.packages()) == FALSE)
-    install.packages(x, dependencies = T,
-                     repos = "http://cran.us.r-project.org")
-}
-lapply(pkgs, installIfNot)
-
-# Load packages
-lapply(pkgs, require, character.only = T)
-rm(pkgs, installIfNot)
-
-# Setting Up Selenium
-
-# Alternative 1: Setting up Selenium (head)
-rsD <- rsDriver(port = 1114L, browser = c("firefox"))
-remDr <- rsD$client
-remDr$open()
-
-# Google Scholar
-
-# site: https://scholar.google.com
-remDr$navigate("https://scholar.google.com/
-               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")
-
-articles_weingast <- tibble(
-  value = NA,
-  term = NA,
-  page = NA
-)
-
-k <- 0
-
-for (j in 1:213) { # we had to manually choose the number of pages here
-  
-  Sys.sleep(rpois(1, 5))
-  
-  # Getting articles basic information
-  k <- k + 1
-  
-  webElem <- remDr$findElement("css", "body")
-  
-  
-  title <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(
-      xpath = '//*[contains(concat( " ", @class, " " ),
-      concat( " ", "gs_rt", " " ))]'
-    ) %>%
-    html_text() %>%
-    enframe(name = NULL) %>%
-    rename("title" = "value") %>%
-    mutate(page = k)
-  
-  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
-    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
-    html_text() %>%
-    enframe(name = NULL) %>%
-    bind_rows(
-      tibble(
-        value = "delete",
[…]

### 2021-05-10 appendix/appendix.Rmd
small edits to appendix text

@@
 dependent/independent variables we collected for our meta-analysis. We then
-included the 3 papers we found in the second search, as both conformed to our
+included the 2 papers we found in the second search, as both conformed to our
 criteria, and compiled our final sample of `r length(unique(dat$authoryear))`
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)

### 2021-05-20 appendix/appendix.Rmd
rewrites result reports from meta regressions

@@
 
-[^roman]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 
@@
 
-With all coefficients, the results of the effect sizes on the Log of Expenditure Per Capita Regressions are the following:
-
-1. In regard to the estimation method, papers that use `PANEL` data or `RDD`
+With all coefficients, among the results of the effect sizes on the Log of Expenditure Per Capita Regressions, we find that in regard to the estimation method, papers that use `PANEL` data or `RDD`
    designs have smaller effects than articles that employ `OLS` estimations.
 
-2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
+```{r}
+# 2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
+```
 
@@
 
-All moderators are insignificant in the meta-regressions of Expenditure as a Percentage of GDP.
+In the meta-regressions of Expenditure as a Percentage of GDP, we found that:
+
+1. More recent papers find smaller effect sizes than older studies.
+
+2. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
 
@@
 
-Even for all the coefficients, all moderators remain insignificant.
+With all coefficients, the results of the effect sizes on the Expenditure as a Percentage of GDP regressions are the following:
+
+1. Recent papers find even smaller effect sizes than older studies.
+
+2. Studies using non-majoritarian systems find more positive effects between variables.
+
+3. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
 
@@
 ```
-In the restricted model, with only the main coefficients in the selected papers, no moderator has a significant effect.
+In the restricted model, with only the main coefficients in the selected papers, only Unicameralism has a positive, significant effect.
 We also run the meta-regressions adding all coefficients in the papers.
@@
 
-1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.
-
-2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.
-
-3. Over time, the reported coefficients have been increasing in size.
-
-4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.
-
-5. All other moderators are insignificant.
+1. Coefficients from non-majoritarian systems are significantly smaller than those found in purely majoritarian systems.
+
+2. Compared with `OLS`, `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
+
+3. Evidence from purely unicameral systems produces significantly larger effect sizes.
+
+4. All other moderators are insignificant.
+
+```{r}
+#1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.
+
+#2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.
+
+#3. Over time, the reported coefficients have been increasing in size.
+
+#4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.
+
+#5. All other moderators are insignificant.
+```

### 2021-05-20 article/resubmission.Rmd
adds draft of resubmission

--- 2020-12-08 article/article.Rmd
@@
 
-[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 
@@
 effect was often limited to one house [e.g., @baqir2002districting;
-@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
-questioned the validity of the "law of $1/n$". For instance, spending limits,
-bicameralism, or strong executives may reduce the inefficiency of pork barrel
-projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
+@gilligan1995deviations; @gilligan2001fiscal].
+More recently, the discussion of the "law of $1/n$" has surpassed its original formulation.
+Specifically, the theory meant to explain distributive behavior of US district legislators under majoritarian electoral rules.
+It has since then been applied to a number of contexts whose political features do not fit into what @weingast1981political had theorized.
+
+The mechanism behind $1/n$ is incumbents' choice of redistributive strategy to optimize chances of reelection.
+The _norm of universalism_, by which all legislators pass each other's bills, guarantees that all representatives are allotted an amount of resources to cater projects to their voters.
+@crowley2019law contests this scenario where coordination costs are minimal, aiming at solving the discrepancies in previous works.
+The literature finds that a number of players and features can override the $1/n$ effect by posing checks to legislative activity and altering coordination costs.
+First, shifts in the level of intra or intergovernmental competition based on district homogeneity, supermajority rules, the size of coalitions, and even gerrymandering have been shown to interfere with the effect of chamber size on spending [@bjedov; @crain1999; @crowley2015; @gilligan2006; @lee2015; @mukherjee2003; @pecorino2018].
+Second, we must take into account players who function as institutional checks, such as strong executives who take on legislative duties, other deliberative chambers, or spending limits, who also directly influence legislators' access to common pool funds [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
 Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
@@
 Our survey of the scholarship confirms this continuum of positive,
-insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
+insignificant, and negative results. Out 
+of the `r dim(dat)[1]` coefficients
 included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. Given this diversity of empirical
-findings, a systematic review of the existing evidence may help us reach a
+negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
 meaningful conclusion about the effect of legislature size on public spending.
@@
 Our independent variables consist of three measures, namely the size of the
-lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
-in the upper chamber ($k$). We evaluate their effect upon public expenditure per
+lower chamber, its natural logarithm, and the number of members
+in the upper chamber. We evaluate their effect upon public expenditure per
 capita, the natural logarithm of public expenditure per capita, and government
@@
 has high levels of heterogeneity, and effects differ substantially according to
-study specifications. We find that one reliable predictor of effect size is the
-research method employed in the original paper. While papers that employ
+study specifications. While papers that employ
 conventional linear regressions often find a positive relation between
@@
 expectations of the "law of $1/n$", and they do not have a relevant impact on
-the other measures of public expenditure. In summary, our analysis does not
+the other measures of public expenditure.
+However, unicameralism strongly supports the positive effect predicted by the original theory.
+This result is contradictory to the rest of our findings, even if unicameral cases mostly reflect the very specific framework under which the theory developed (loosely checked local governments).
+In summary, our analysis does not
 provide robust support for the theory as originally conceived, and causal
@@
 Google Scholar, three large academic databases.\footnote{See the Supplementary
-Material for code.}
+Material for code.} Based on the results obtained, we selected key terms to conduct a broader search of the literature. The same eligibility criteria were applied.
+
+Upon restricting the sample, we identified which were the measurement units most commonly used to translate legislature size and public spending.
+We found those to be public expenditure as a share of GDP, public expenditure per capita, log public expenditure per capita, lower chamber size, upper chamber size, and log lower chamber size.
+Log upper chamber size is not a commonly used measurement.
+Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).
+Since much of the literature dedicated to measuring the effects of bicameralism on this relationship, many articles use both lower and upper chamber sizes as key explanatory variables.
 
 After applying our exclusion criteria, the search produced a dataset of 
-`r length(unique(dat$id))` studies as of the 21\textsuperscript{st} of November,
-2019. Table \ref{tab:papers} contains the full list of articles from which we
+`r length(unique(dat$id))` studies as of the 5\textsuperscript{th} of March,
+2021. Table \ref{tab:papers} contains the full list of articles from which we
 drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
@@
 \citet{liberati2009prisma}.} flow diagram showing the number of resulting
-papers after each review step is available in the Supplementary Material.
+papers after each review step is available in section C.2 of the Supplementary Material.
 
@@
 Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
-Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
+Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
+\footnotetext{\textbf{Note:} 
 OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
 data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
-NM$=$Non-majoritarian (mixed or proportional representation). Country codes
+NM$=$Non-majoritarian (mixed or proportional representation).} 
+\footnotetext{\textbf{Note:} Country codes
 follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
@@
 legislatures on different measures of government spending. Our independent
-variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
-logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
+variables of interest are, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
+logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
 size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
@@
 the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study ($n$,
-log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
+indicator for the type of independent variable used in the original study (lower chamber size,
+log of lower chamber size, or upper chamber
+size). The additional moderators are: 1) publication year; 2) paper
 publication in an academic journal; 3) electoral system; 4) estimation method.
@@
 
-```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
+```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
-fulldat$usemeta2 <- as.character(fulldat$usemeta2)
-fulldat$usemeta2 <- factor(fulldat$usemeta2)
-aux <- select(fulldat, usemeta2, indepvar2, year, published,
-              elecsys2, method) %>%
+levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
+aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
+              year, published) %>%
   rename(`Independent Variables` = indepvar2,
+         `Electoral system`      = elecsys2,
+         `Estimation method`     = method,
          `Year`                  = year,
-         `Published work` = published,
-         `Electoral system` = elecsys2,
-         `Estimation method` = method)
-
-res <- export2latex(
-  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-             show.p.overall = F, show.all = T, all.last = T), 
-  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
-)
-res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
-cat(res)
+         `Published work`        = published)
+
+export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+                        show.p.overall = F, show.all = T),
+          caption = "Descriptive Statistics of Moderators",
+          format  = "latex")
 ```
 
-\footnotesize
-\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
-\hline  
-& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
-&       N=42        &       N=100        &    N=142    \\
-\hline
-\hline     
-\endfirsthead 
-\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
-\hline
-& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
-&       N=42        &       N=100        &    N=142    \\ 
-\hline
-\hline  
-\endhead   
-\hline
-\multicolumn{4}{l}{\textit{continued on next page}} \\ 
-\endfoot   
-\multicolumn{4}{l}{}  \\ 
-\endlastfoot 
-Independent Variables: &                   &                    &            \\ 
-$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
-$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
-$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
-Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
-Published work: &                   &                    &            \\ 
-$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
-$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
-Electoral system: &                   &                    &            \\ 
-$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
-$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
-Estimation method: &                   &                    &            \\ 
-$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
-$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
-$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
-$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\
-
-\hline
-\end{longtable}
-
-\normalsize
-
-Since most selected articles have more than one effect size, the observations
-in our dataset are not independent. To reduce the impact of multicollinearity,
+To ensure we do not violate the effect size independence assumption, we use two strategies.
+Since most selected articles submit their data to a number of tests, varying models and controls, each pair of variables has more than one effect size.
+First, to reduce the impact of multicollinearity within the same article,
 we estimate the models using two sets of study coefficients. The first group
@@
 lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
-sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
-sample as we consider them more robust, but the findings are very similar when
-we use the extended set. We discuss eventual differences in the next section.
-Please refer to the Supplementary Material for further information about our
-sampling process and for the complete results.
+ricciuti2003trading}.
+Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
+Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
+We discuss eventual differences in the next section.
+There is also dependence between studies when more than one article uses the same dataset or source of evidence.
+In our study, for instance, several papers used US state and municipal data from the Census Bureau and the Book of the States, for the same constituencies, under the same time period.
+To override dependence between articles, the second strategy we use is employing a multilevel random effects model, grouping the studies that use overlapping data.
 
@@
 possible sources of result heterogeneity. To recapitulate, our independent
-variables of interest are lower chamber size ($n$), the natural logarithm of
-lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
+variables of interest are lower chamber size, the natural logarithm of
+lower chamber size, and upper chamber size. The dependent
 variables are public expenditure per capita, the natural logarithm of public
@@
 sign of the coefficient is equally likely to be positive or negative. We start
-with $n$, lower house size. Our results indicate that there is no correlation
+with lower house size. Our results indicate that there is no correlation
 between the number of legislators in the lower house and public expenditure 
@@
 $p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
-association between both. The binomial test for log($n$) also shows a
+association between both. The binomial test for the natural logarithm of lower chamber size also shows a
 non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
 $p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
-positive result for the number of legislators in the upper house ($k$), which is
+positive result for the number of legislators in the upper house, which is
 in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
@@
 the article pool. Our sample includes no papers that analyse the relationships
-between log($n$) and public expenditure per capita or between $k$ and the
+between the log lower chamber size and public expenditure per capita or between upper chamber size and the
 logarithm of public expenditure per capita.
+We standardized effect sizes by drawing the coefficients and standard errors from the articles.
+When the latter were not directly available, we used t-statistics to retrieve them.
 
@@
 
-The first column of the graph reports the results for $n$, lower chamber size.
-In the first model, which correlates $n$ and expenditure per capita, we find a
+The first column of the graph reports the results for lower chamber size.
+In the first model, which correlates lower chamber size and expenditure per capita, we find a
 standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
@@
 
-We see similar results when we compare $n$ with log expenditure per capita. In
+We see similar results when we compare lower chamber size with log expenditure per capita. In
 this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
@@
 
-Next, we present the meta-analyses using log($n$), the logarithm of lower house
+Next, we present the meta-analyses using the logarithm of lower house
 size, as the main explanatory variable. We start with the relationship between
-log($n$) and the logarithm of expenditure per capita. The result is positive and
+this variable and the logarithm of expenditure per capita. The result is positive and
 statistically significant at 10\%, but the prediction interval encompasses zero
@@
 
-Our model that correlates log($n$) with public expenditures as a percentage of
+Our model that correlates log lower chamber size with public expenditures as a percentage of
 GDP fails to reach conventional levels of statistical significance (studies =
@@
 
-The third set of models uses $k$, upper house size, as the main independent
-variable. We find a positive correlation between $k$ and expenditure per capita
+The third set of models uses upper house size, as the main independent
+variable. We find a positive correlation between this variable and expenditure per capita
 but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
@@
 
-Our last estimation analyses the relationship between $k$ and government
+Our last estimation analyses the relationship between upper chamber size and government
 spending as a percentage of GDP. The coefficient is not statistically
@@
 account for differences across the selected papers. The first variable indicates
-whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
+whether the study uses lower chamber size, log lower chamber size, or upper chamber size as a main explanatory variable.
+We included the individual effect sizes for upper and lower chamber sizes when papers analyzed both.
 The second variable shows the study publication year, which we included to
@@
 restricted and extended samples. Each column represents one of the three
-measures of public spending we discuss in this paper. To reduce the risk of
+measures of public spending we discuss in this paper. Each subgroup uses a chosen category as reference. When it comes to the independent variable, the reference category is upper chamber size; for 
+publication bias, the reference is published articles; for electoral system, the reference is majoritarian systems; and for methodology, the reference is ordinary least squares linear regression.
+To reduce the risk of
 false positives in our analyses, we use permutation tests to calculate
@@
 variable reaches conventional levels of statistical significance in the
-restricted sample. In the extended sample, we find that models that use $n$ as
+restricted sample. In the extended sample, we find that models that use lower chamber size as
 an independent variable have lower effects when
-compared to $k$. This suggests that an additional member in the lower house has
+compared to upper chamber size. This suggests that an additional member in the lower house has
 a smaller impact on public spending than a member in the upper house. Moreover,
@@
 number of legislators has a significant effect on public expenditures. If such
-effect exists, it is likely driven by an increase in $k$, the size of the upper
+effect exists, it is likely driven by an increase in the size of the upper
 legislature, as suggested by several studies in the literature
@@
 
+The literature explores many mediating and alternative explanations for how or why the number of legislators in a chamber relates to their choice of commmon pool resource use.
+@crowley2019law argues that a variable that better translates how large legislatures decrease the efficiency of public spending is fragmentation, which also expresses the and that its effect is actually non-linear.
+Other studies echo this argument and develop other frgamentation mechanisms that explain relationships that are linear and non-linear.
+For instance, when it comes to district fragmentation, @baqir1999districts and @drew2017price support the "law of $1/n$"'s positive effect on public spending when one considers the amount of districts that share a common pool of resources.
+Many studies demonstrate how partisan fragmentation is a bigger predictor of increased spending, and analyze how majorities and veto powers respectively boost and curtail these effects [@baqir2002districting, cite all the papers].
+These findings dialogue directly with @weingast1981political's *norm of universalism* within US legislatures, which is the assumption that, when drawing from common pool resources, chambers will always approve of any singular legislators' projects.
+
+Applying the "law of $1/n$" in contexts too far removed from the US attests against it, as, for instance, public spending more strongly correlates to cabinet than legislature size in Swiss cantons and Malaysian (states or municipalities?), where decision-making power is concentrated in the executive.
+
 Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
@@
 \url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.} For instance, in our sample, papers added supermajority rules
+information.}
+
+For instance, in our sample, papers added supermajority rules
 [@lee2015supermajority; @lee2016supermajority], redistricting
@@
 procedural replication of the findings using different samples is yet to be
-written. The addition of new features has the benefit of enriching the original
+written.
+
+The addition of new features has the benefit of enriching the original
 theory with useful details, although it has the disadvantage of not providing a
@@
 sample did not include articles that evaluate the association between the
-log($n$) and public expenditure per capita or between $k$ and log expenditure
+log lower chamber size and public expenditure per capita or between upper chamber size and log expenditure
 per capita. New work on that area might clarify some of the inconsistencies we

### 2021-05-20 article/resubmission.Rmd
author affiliations

@@
 
-[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
 
@@
 
-[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 

### 2021-05-20 article/resubmission.Rmd
messy updates

@@
 
-The first column of the graph reports the results for lower chamber size.
+The first line of graphs reports the results for lower chamber size.
 In the first model, which correlates lower chamber size and expenditure per capita, we find a
@@
 `r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
-[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
-sample and the coefficient is statistically significant at the 10\% level
-(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
-`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
-result supports the "law of 1/$n$", but the evidence is moderate
-as the prediction interval include zero.
+[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%).
+In the extended sample the effect is negative, but it is also statistically insignificant.
+
+```{r}
+#We find a positive effect in our extended
+#sample and the coefficient is statistically significant at the 10\% level
+#(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
+#`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
+#result supports the "law of 1/$n$", but the evidence is moderate
+#as the prediction interval include zero.
+```
 
 Next, we present the meta-analyses using the logarithm of lower house
-size, as the main explanatory variable. We start with the relationship between
-this variable and the logarithm of expenditure per capita. The result is positive and
-statistically significant at 10\%, but the prediction interval encompasses zero
+size. We start with the relationship between
+this variable and the logarithm of expenditure per capita. The result is positive, but the coefficient is not significant, and the prediction interval encompasses zero
 (studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
-`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
-coefficient has the predicted sign, we should interpret the finding with caution
-as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.
+`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%).
+Results in the full sample are also null.
 
@@
 
-The third set of models uses upper house size, as the main independent
+The third set of models uses upper house size as the main independent
 variable. We find a positive correlation between this variable and expenditure per capita
@@
 whether studies focusing on non-majoritarian electoral systems report
-coefficients that are smaller or larger than those from majoritarian countries.
-Our last covariate is a categorical variable indicating the statistical
+coefficients that are smaller or larger than those from majoritarian countries. The fifth covariate is a categorical variable indicating the statistical
 procedure used in the original models (panel data, instrumental variables,
 OLS, or regression discontinuity design).
+In our last variable, we separate coefficients that use samples from unicameral or bicameral systems, and code papers using polities with different institutional designs as "mixed".
 
@@
 We report the results from the permutation tests.
-Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$.
+Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$; Institutional Design $= Bicameralism$.
 Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
@@
 restricted and extended samples. Each column represents one of the three
-measures of public spending we discuss in this paper. Each subgroup uses a chosen category as reference. When it comes to the independent variable, the reference category is upper chamber size; for 
-publication bias, the reference is published articles; for electoral system, the reference is majoritarian systems; and for methodology, the reference is ordinary least squares linear regression.
-To reduce the risk of
+measures of public spending we discuss in this paper. To reduce the risk of
 false positives in our analyses, we use permutation tests to calculate

### 2021-05-21 appendix/appendix.Rmd
fixes typos and updates pdf

@@
 
-The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita is available below.
+The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita are available below.
 
@@
 We find little evidence that either majoritarian or non-majoritarian systems produce systematically positive effects on expenditure per capita.
-Both coefficients are not statistically significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.
+Both coefficients are not statistically significant, and they reassure us that the absence of effect is not caused by pooling multiple types of electoral systems.
 
@@
 
-Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the expenduture per capita.
+Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenduture per capita.
 To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
@@
 
-Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers negative displaying negative effects.
+Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers displaying negative effects.
 The random effects model for the subgroup is 0.22, which is negative but non-significant.
-Improve the estimation technique, for the case of IVs, render still a null effect of legislature size on per capita government expenditure.
+Improving the estimation technique, for the case of IVs, still renders a null effect of legislature size on per capita government expenditure.
 
@@
 The *law of 1/n* was formulated to analyse the budgetary allocation in majoritarian systems.
-In the theoretical section below, we explain why the argument have potential issues when applied to non-majoritarian electoral systems.
+In the theoretical section below, we explain why the argument has potential issues when applied to non-majoritarian electoral systems.
 We estimated a subgroup analysis using a dummy variable indicating the electoral system included in each model.

### 2021-05-22 article/resubmission.Rmd
methods section

@@
 
+Agrupamentos possíveis (agrupar só os que batem no nosso resultado): 
+- métodos (esse bate)
+- institutional design
+- electoral system
+
+Introduction:
+1 - como está originalmente.
+2 - in this letter we run a meta analysis papapá, explicando o que fazemos no texto e o que encontramos.
+3 - resultados são all over the place: e a literatura ja sabia que eram all over the place (vira revisãozinha de literatura).
+4 - agora a gente diz o que nossos resultados representam pros estudos: no caso, podemos concluir que os autores x, y, z foram pela linha correta.
+
+Results: Colocar resultados da meta-regressão completa na última tabela.
+
+Discussion:
+1 - ok
+2 - ok, só corrigir
+3 - como nossos resultados "resolvem" as questões da teoria
+a linha que avalia o desenho institucional está certa dessa forma.
+sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, nós podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
+Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
+4 - ultimo paragrafo vira o que é o terceiro.
+uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.
+
 Over the past decades, a large literature has examined the relationship between
@@
 
+Colocar aqui no final desse paragrafo "in this paper we..."
+
 The mechanism behind $1/n$ is incumbents' choice of redistributive strategy to optimize chances of reelection.
@@
 meaningful conclusion about the effect of legislature size on public spending.
-Meta-analysis is the most appropriate method for this task. Meta-analysis
+
+Grudar aqui no final o início do pargrafo seguinte, retirando toda a descrição de ~como conduzimos a meta~, sem descrição das variaveis e modelos.
+
+XXXXXX Meta-analysis is the most appropriate method for this task. Meta-analysis
 combines the outcomes of multiple studies into a single estimation and allows
@@
 external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy].
+academic inquiry [@doucouliagos2008democracy]. XXXXXXXX
 
@@
 
-We collected the study sample using three criteria. First, the study should
-cite \citet{weingast1981political} as their work is foundational to the
-distributive politics literature. Second, the study had to use quantitative
-methods to estimate the relationship between our variables of
-interest.\footnote{As meta-analysis requires a single estimate per observation,
-we excluded articles that use interaction terms or quadratic specifications of
-our independent variables.} Third, the study should be written in the English
-language. We conducted a primary search using Scopus, Microsoft Academic, and
-Google Scholar, three large academic databases.\footnote{See the Supplementary
-Material for code.} Based on the results obtained, we selected key terms to conduct a broader search of the literature. The same eligibility criteria were applied.
-
-Upon restricting the sample, we identified which were the measurement units most commonly used to translate legislature size and public spending.
-We found those to be public expenditure as a share of GDP, public expenditure per capita, log public expenditure per capita, lower chamber size, upper chamber size, and log lower chamber size.
-Log upper chamber size is not a commonly used measurement.
+We compiled our final sample of papers from two large collections of records.
+In the first round of the search, we scraped three large academic databases (Scopus, Microsoft Academic, and Google Scholar) for studies that cited \citet{weingast1981political}.
+We developed exclusion criteria to select only articles written in the English language that used quantitative methods to investigate the relationship between legislature size and public spending.\footnote{Please refer to section C in the Supplementary Material for a more detailed description of the selection procedure, including a PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow diagram \citet{liberati2009prisma} showing the number of resulting papers after each review step.} Upon restricting the sample, we identified which were the most commonly used measurements to operationalise these variables of interest, and adopted them as our key explanatory variables.\footnote{As meta-analysis requires a single estimate per observation, we excluded articles that use interaction terms or quadratic specifications of our independent variables.} We found those to be public expenditure as a share of GDP, public expenditure per capita, and the natural logarithm of public expenditure per capita as dependent variables.
+As independent variables, most studies use lower chamber size, upper chamber size, and the natural logarithm of lower chamber size.\footnote{There are a few important nuances to the coding of these variables.
 Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).
-Since much of the literature dedicated to measuring the effects of bicameralism on this relationship, many articles use both lower and upper chamber sizes as key explanatory variables.
-
-After applying our exclusion criteria, the search produced a dataset of 
-`r length(unique(dat$id))` studies as of the 5\textsuperscript{th} of March,
-2021. Table \ref{tab:papers} contains the full list of articles from which we
-drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
-Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
-to improve the quality and transparency of study selection processes in
-meta-analyses. For more information on the PRISMA framework, see
-\citet{liberati2009prisma}.} flow diagram showing the number of resulting
-papers after each review step is available in section C.2 of the Supplementary Material.
+Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as key explanatory variables.
+We did not find any articles that used the natural logarithm of upper chamber size.} In the second round, we selected key terms to conduct a broader search of the literature on Google Scholar and applied the same eligibility criteria.
+Combined, the two searches produced a dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March, 2021.
+Table \ref{tab:papers} contains the full list of articles from which we drew data.
 
 \footnotesize
-\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
+\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
 \caption{Papers included in the meta-analysis, ordered by year of appearance}\\
 \toprule
-\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
+\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
 \tabularnewline
@@
 \endhead 
-```{r, echo = FALSE, results = 'asis', cache = T}
+```{r papers, echo = FALSE, results = 'asis', cache = T}
 build_nams <- function(x) {
@@
 aux <- dat %>%
-  select(authorCite, title, journalCode, year, locationISO, method, elecsys3) %>%
+  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
   unique() %>%
@@
 for (i in 1:dim(aux)[1]) {
-  cat(paste(build_nams(aux$authorCite[i]), ' & ', aux$title[i], ' & ',
-      aux$journalCode[i], ' & ', aux$year[i], ' & ', 
-      aux$locationISO[i], ' & ', aux$method[i], ' & ', 
+  cat(paste(build_nams(aux$authoryear[i]), ' & ', aux$journalCode[i], ' & ',
+      aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
+      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
       aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
@@
 \footnotetext{\textbf{Note:} Country codes
-follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
+follow the ISO 3166-1 alpha-3 international standard.}
+\footnotetext{\textbf{Note:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
 \end{longtable}
@@
 Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`).
-Five articles use cross-national data and analyse from 2 to 110
+Eight articles use cross-national data and analyse from 2 to 110
 countries. Early studies used OLS and panel data methods to estimate the
@@
 legislatures on different measures of government spending. Our independent
-variables of interest are, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
+variables of interest are lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
 logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
@@
 
-We also coded four moderators that may help us understand the heterogeneity in
+We also coded five moderators that may help us understand the heterogeneity in
 the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study (lower chamber size,
-log of lower chamber size, or upper chamber
-size). The additional moderators are: 1) publication year; 2) paper
-publication in an academic journal; 3) electoral system; 4) estimation method.
-Since the literature on the "law of $1/n$" is notably diverse, we were
-restricted to include only the moderators that either refer to important
+indicator for the type of independent variable used in the original study. The additional moderators are: 1) publication year; 2) paper
+publication in an academic journal; 3) estimation method; 4) institutional design; 5) electoral system.
+Since the literature on the "law of $1/n$" is notably diverse, we included only moderators that either refer to important
 theoretical questions, such as the effect of the electoral system on public
@@
 
-```{r, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
+\footnotesize
+```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
+levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published) %>%
+              year, published, instdesign) %>%
   rename(`Independent Variables` = indepvar2,
-         `Electoral system`      = elecsys2,
+         `Year`                  = year,
+         `Published work`        = published,
          `Estimation method`     = method,
-         `Year`                  = year,
-         `Published work`        = published)
+         `Institutional Design`  = instdesign,
+         `Electoral system`      = elecsys2)
 
@@
 ```
-
-To ensure we do not violate the effect size independence assumption, we use two strategies.
-Since most selected articles submit their data to a number of tests, varying models and controls, each pair of variables has more than one effect size.
-First, to reduce the impact of multicollinearity within the same article,
-we estimate the models using two sets of study coefficients. The first group
+\normalsize
+
+One of the assumptions in meta-analyses is effect size independence.
+In our sample of coefficients, we have sources of independence within and between articles, and we solve them using two distinct procedures.
+Since authors often submit their data to different models, each paper reports several effect sizes using the same variables.
+To reduce the impact of multicollinearity,
+we produce and analyse two sets of study coefficients. The first group
 includes only the most rigorous model from each paper, that is, those estimated
@@
 sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
-independent variables of interest \citep{baqir1999districts, bjedov2014impact,
-bradbury2001legislative, chen_malhotra_2007, crowley2019law,
-lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading}.
+independent variables of interest \footnote{The papers that used more than one dependent or independent variable of interest were \citet{baqir1999districts, bjedov2014impact,
+bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop, ricciuti2003trading, ricciuti2004legislatures}.}.
 Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
+In both restricted and extended sets, a number of papers use overlapping data -- from the same constituency, using the same variables, during the same time period.\footnote{For instance, 8 papers used U.S.
+State data from both the U.S.
+Census Bureau’s “Annual Survey of State and Local Government Finances” and The Council of State Government’s Book of the
+States.} We correct this source of bias by employing a multilevel random effects model [@cheung2014modeling], grouping redundant(?) studies.
 Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
 We discuss eventual differences in the next section.
-There is also dependence between studies when more than one article uses the same dataset or source of evidence.
-In our study, for instance, several papers used US state and municipal data from the Census Bureau and the Book of the States, for the same constituencies, under the same time period.
-To override dependence between articles, the second strategy we use is employing a multilevel random effects model, grouping the studies that use overlapping data.
 
@@
 
-```{r}
-#We find a positive effect in our extended
-#sample and the coefficient is statistically significant at the 10\% level
-#(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
-#`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
-#result supports the "law of 1/$n$", but the evidence is moderate
-#as the prediction interval include zero.
-```
+XXXXX We find a positive effect in our extended
+sample and the coefficient is statistically significant at the 10\% level
+(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
+`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
+result supports the "law of 1/$n$", but the evidence is moderate
+as the prediction interval include zero. XXXXXXXXX
 
@@
 
-```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
-res <- list()
-
-## Expenditure as percentage GDP -- Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='PCTGDP',
-            slab = dat$authoryear)
-
-res[[1]] <- tibble(
-     ` ` = c("Intercept",
-             "Indepvar: N",
-             "Indepvar: logN",
-             "Year",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "PCTGDP"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-## Expenditure as percentage GDP -- Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-res[[2]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Indepvar: logN",
-          "Year",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Expenditure per capita - Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear,
-            control=list(maxiter=1000))
-
-res[[3]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-res[[4]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Log of Expenditure per capita - Restricted
-mod <- rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-res[[5]] <- tibble(
-   ` ` = c("Intercept",
-           "Indepvar: N",
-           "Year",
-           "Published: No",
-           "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Log of Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-res[[6]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Method: Panel",
-          "Method: RDD"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-strep <- function (x) {
-  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
-}
-```
-
-```{=latex}
-\vspace{0.5cm}
-
-\begin{table}[htpb]
-\caption{Meta Regression Results\label{tabregressions}}
-\footnotesize
-\centering
-\begin{tabular}{lcccccc}
-\toprule
-\midrule
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
-& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
-\midrule
-Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
-                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
-%
-Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
-                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
-%
-Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\
-     & (`r round(res[[3]][3,3],3)`)`r strep(res[[3]][3,5])` & (`r round(res[[4]][3,3],3)`)`r strep(res[[4]][3,5])` & (`r round(res[[5]][3,3],3)`)`r strep(res[[5]][3,5])` & (`r round(res[[6]][3,3],3)`)`r strep(res[[6]][3,5])` & (`r round(res[[1]][4,3],3)`)`r strep(res[[1]][4,5])` & (`r round(res[[2]][4,3],3)`)`r strep(res[[2]][4,5])`\\
-%
-Published: No & `r round(res[[3]][4,2],3)` & `r round(res[[4]][4,2],3)` & `r round(res[[5]][4,2],3)` &  `r round(res[[6]][4,2],3)` &  & \\
-              & (`r round(res[[3]][4,3],3)`)`r strep(res[[3]][4,5])` & (`r round(res[[4]][4,3],3)`)`r strep(res[[4]][4,5])` & (`r round(res[[5]][4,3],3)`)`r strep(res[[5]][4,5])` & (`r round(res[[6]][4,3],3)`)`r strep(res[[6]][4,5])` &  & \\
-%
-Non-Majoritarian (PR \& Mixed) & `r round(res[[3]][5,2],3)` & `r round(res[[4]][5,2],3)` & &  & `r round(res[[1]][5,2],3)` & `r round(res[[2]][5,2],3)` \\
-                               & (`r round(res[[3]][5,3],3)`)`r strep(res[[3]][5,5])` & (`r round(res[[4]][5,3],3)`)`r strep(res[[4]][5,5])` & &  & (`r round(res[[1]][5,3],3)`)`r strep(res[[1]][5,5])` & (`r round(res[[2]][5,3],3)`)`r strep(res[[2]][5,5])`\\
-%
-Method: Panel & `r round(res[[3]][6,2],3)` & `r round(res[[4]][6,2],3)` & `r round(res[[5]][5,2],3)` & `r round(res[[6]][5,2],3)` & `r round(res[[1]][6,2],3)` & `r round(res[[2]][6,2],3)`\\
-              & (`r round(res[[3]][6,3],3)`)`r strep(res[[3]][6,5])` & (`r round(res[[4]][6,3],3)`)`r strep(res[[4]][6,5])` & (`r round(res[[5]][5,3],3)`)`r strep(res[[5]][5,5])` & (`r round(res[[6]][5,3],3)`)`r strep(res[[6]][5,5])` & (`r round(res[[1]][6,3],3)`)`r strep(res[[1]][6,5])` & (`r round(res[[2]][6,3],3)`)`r strep(res[[2]][6,5])`\\
-%
-Method: IV & `r round(res[[3]][7,2],3)` & `r round(res[[4]][7,2],3)` &  &  &  & \\
-           & (`r round(res[[3]][7,3],3)`)`r strep(res[[3]][7,5])` & (`r round(res[[4]][7,3],3)`)`r strep(res[[4]][7,5])` &  &  &  & \\
-%
-Method: RDD &  &  &  & `r round(res[[6]][6,2],3)` &  & \\
-            &  &  &  & (`r round(res[[6]][6,3],3)`)`r strep(res[[6]][6,5])` &  & \\
-% 
-Intercept & `r round(res[[3]][1,2],3)` & `r round(res[[4]][1,2],3)` & `r round(res[[5]][1,2], 3)` & `r round(res[[6]][1,2], 3)` & `r round(res[[1]][1,2], 3)` & `r round(res[[2]][1,2], 3)`\\
-          & (`r round(res[[3]][1,3],3)`)`r strep(res[[3]][1,5])` & (`r res[[4]][1,3]`)`r strep(res[[4]][1,5])` & (`r round(res[[5]][1,3],3)`)`r strep(res[[5]][1,5])` & (`r round(res[[6]][1,3],3)`)`r strep(res[[6]][1,5])` & (`r round(res[[1]][1,3],3)`)`r strep(res[[1]][1,5])` & (`r round(res[[2]][1,3],3)`)`r strep(res[[2]][1,5])`\\
-\bottomrule
-\end{tabular}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively.
-We report the results from the permutation tests.
-Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$; Institutional Design $= Bicameralism$.
-Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
-\end{minipage}
-\end{table}
-```
-
 \newpage
 
-Table \ref{tabregressions} presents the meta-regression results for our
+Table {tabregressions} presents the meta-regression results for our
 restricted and extended samples. Each column represents one of the three

### 2021-05-22 appendix/appendix.Rmd
cleaning up

@@
 
-3.  All other coeffients were not significant.
+3.  All other moderators were not significant.
 
@@
 
-With all coefficients, among the results of the effect sizes on the Log of Expenditure Per Capita Regressions, we find that in regard to the estimation method, papers that use `PANEL` data or `RDD`
-   designs have smaller effects than articles that employ `OLS` estimations.
-
-```{r}
-# 2. Having the log of lower house seats (`logN`) as the main independent variable increases the detected effect.
-```
-
+With all coefficients, results of the effect sizes on the Log of Expenditure Per Capita Regressions indicate that in regard to the estimation method, papers that use `PANEL` data or `RDD` designs have smaller effects than articles that employ `OLS` estimations.
 All other results are insignificant.
@@
 
-1. More recent papers find smaller effect sizes than older studies.
+1. Recent papers find smaller effect sizes than older studies.
 
@@
 
-1. Recent papers find even smaller effect sizes than older studies.
+1. Papers from more recent years find smaller effect sizes than older studies.
 
@@
 
-6. The institution design: whether the legislature in the analysis is unicameral, bicameral, or mixed.
+6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.
 
@@
 
-The results follow below, and show null effects for all variables, including the intercept.
+The results follow below, and show null effects for all variables except for Unicameral institutional designs.
 
@@
 
-1. Coefficients from non-majoritarian systems are significantly smaller than those found in purely majoritarian systems.
-
-2. Compared with `OLS`, `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
-
-3. Evidence from purely unicameral systems produces significantly larger effect sizes.
+1. Coefficients from non-majoritarian systems are significantly lower than those found in purely majoritarian systems.
+
+2. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
+
+3. Evidence from unicameral systems presents significantly larger effect sizes.
 
 4. All other moderators are insignificant.
-
-```{r}
-#1. For the dependent variable, models with Log of Per Capita Expenditure tend to report significantly smaller effects than models with Per Capita Expenditure.
-
-#2. For the independent variable, models with Log of Lower House Size tend to report significantly larger effects than models with Upper House Size.
-
-#3. Over time, the reported coefficients have been increasing in size.
-
-#4. Compared with `OLS`, `PANEL` and `RDD` report significantly smaller coefficients.
-
-#5. All other moderators are insignificant.
-```

### 2021-05-25 article/article.Rmd
draft methods section, add ref chen, cheung

@@
 title:  |
-        | The Effect of Legislature Size on Public Spending
+        | The Effect of Legislature Size on Public Spending:
         | A Meta-Analysis
@@
 
-[^danilo]: Independent Researcher, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
 
@@
 
-[^catarina]: Research Associate, School of International Relations, Fundação Getulio Vargas, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 
@@
 
-# Methods
+# Data and Methods
 
-We collected the study sample using three criteria. First, the study should
-cite \citet{weingast1981political} as their work is foundational to the
-distributive politics literature. Second, the study had to use quantitative
-methods to estimate the relationship between our variables of
-interest.\footnote{As meta-analysis requires a single estimate per observation,
-we excluded articles that use interaction terms or quadratic specifications of
-our independent variables.} Third, the study should be written in the English
-language. We conducted a primary search using Scopus, Microsoft Academic, and
-Google Scholar, three large academic databases.\footnote{See the Supplementary
-Material for code.}
+We compiled our study sample in three rounds. In the first search round, we
+gathered data from three large academic databases (Scopus, Microsoft Academic,
+and Google Scholar) and looked for studies that cited
+\citet{weingast1981political}, as it is the foundational work in the literature
+on the "law of $1/n$". We then restricted our query to articles written in
+English and, to ensure that studies were comparable, we only included papers
+that used quantitative methods to investigate the relationship between
+legislature size and public spending\footnote{Please refer to Section C in the
+Supplementary Material for a detailed description of the selection procedure.
+We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
+Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
+resulting papers after each review step.}. After this stage, we identified the
+variables authors most commonly employ to measure government expenditure and
+legislature size, our dependent and independent variables, respectively. For
+government expenditure, our study sample uses (i) public expenditure as a share
+of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
+public expenditure per capita as its main variables of interest\footnote{Since
+meta-analysis requires a single estimate per observation, we excluded articles
+that use interaction terms or quadratic specifications of our selected
+variables.}. In regards to legislature size, the variables are (i) lower
+chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
+house size\footnote{There are a few important nuances concerning coding of
+these variables. For instance, unicameralism is captured both by lower chamber
+size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
+literature estimates how institutional designs affect this relationship, ours
+and many other articles use both lower and upper chamber sizes as main
+explanatory variables. We did not find any articles that used the natural
+logarithm of upper chamber size.}.
 
-After applying our exclusion criteria, the search produced a dataset of 
-`r length(unique(dat$id))` studies as of the 21\textsuperscript{st} of November,
-2019. Table \ref{tab:papers} contains the full list of articles from which we
-drew data. A PRISMA\footnote{The Preferred Reporting Items for Systematic
-Reviews and Meta-Analyses (PRISMA) statement provides a checklist designed
-to improve the quality and transparency of study selection processes in
-meta-analyses. For more information on the PRISMA framework, see
-\citet{liberati2009prisma}.} flow diagram showing the number of resulting
-papers after each review step is available in the Supplementary Material.
+In the second round, we did not require articles to cite @weingast1981political
+and used a keyword-based query on Google Scholar to broaden the scope of the
+first search. We again restricted the search to articles written in English
+which employed quantitative methods. In the third search round, we looked into
+the personal webpages of every author we had already included in our previous
+sample. The purpose of this manual search was to assess whether there was any
+working paper or unpublished manuscript which we might had missed in the
+previous queries. All papers we found in that last search had already been
+included in our sample. Combined, the three searches produced a dataset of 
+`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
+2021. Table \ref{tab:papers} contains the full list of articles we analyse in
+this paper.
 
 \footnotesize
-\begin{longtable}{>{\raggedright\arraybackslash}p{2.9cm}>{\raggedright\arraybackslash}p{4.5cm}>{\centering\arraybackslash}p{1.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{1.4cm}>{\centering\arraybackslash}p{2.4cm}}
+\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
 \caption{Papers included in the meta-analysis, ordered by year of appearance}\\
 \toprule
-\raggedright Author(s) & \centering Title & \centering Journal & \centering Year & \centering Country & \centering Method & \raggedleft Electoral System
+\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
 \tabularnewline
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
-Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
-JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
-APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
-UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
-Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
-Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
-Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal,
-OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
-data/fixed effects, RDD$=$Regression discontinuity design, M$=$Majoritarian,
-NM$=$Non-majoritarian (mixed or proportional representation). Country codes
-follow the ISO 3166-1 alpha-3 international standard.} \end{minipage}
+\footnotetext{\textbf{Note:} Journals: Unpub$=$Unpublished, JPE$=$Journal of
+Political Economy, EJPE$=$European Journal of Political Economy, PC$=$Public
+Choice, JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private
+Enterprise, APSR$=$American Political Science Review, SEJ$=$Southern Economic
+Journal, UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative
+International Development, SSQ$=$Social Science Quarterly, SPPQ$=$State
+Politics and Policy Quarterly, CPS$=$Comparative Political Studies,
+RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics,
+NTJ$=$National Tax Journal. Country codes follow the ISO 3166-1 alpha-3
+international standard. Dependent variable: ExpPC$=$Per capita expenditure,
+logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
+a percentage of GDP. Method: OLS$=$Ordinary least squares, IV$=$Instrumental
+variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
+design. Electoral system: M$=$Majoritarian, NM$=$Non-majoritarian (mixed or
+proportional representation).} 
+\end{minipage} 
 \end{longtable}
@@
 Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`).
-Five articles use cross-national data and analyse from 2 to 110
+Eight articles use cross-national data and analyse from 2 to 110
 countries. Early studies used OLS and panel data methods to estimate the
-results, whereas the use of regression discontinuity designs is a recent
-addition to the literature, as the first paper to apply it was published in 2012.
+results, while studies from 2012 onward have also applied causal inference designs,
+such as instrumental variables and regression discontinuity models.
 
@@
 GDP. This indicates that the area has refined the original formulation of $1/n$
-suggested by \citet{weingast1981political} and tested the impact of larger
-legislatures on different measures of government spending. Our independent
-variables of interest are $n$, lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), ($\log(n)$), the natural
-logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and $k$, which represents upper chamber
-size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
+and tested the impact of larger legislatures on different measures of government
+spending. Our independent variables of interest are lower chamber size 
+(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
+logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
 
-We also coded four moderators that may help us understand the heterogeneity in
+We also coded five moderators that may help us understand the heterogeneity in
 the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study ($n$,
-log($n$), or $k$). The additional moderators are: 1) publication year; 2) paper
-publication in an academic journal; 3) electoral system; 4) estimation method.
-Since the literature on the "law of $1/n$" is notably diverse, we were
-restricted to include only the moderators that either refer to important
-theoretical questions, such as the effect of the electoral system on public
-spending, or to essential characteristics of the publications themselves.
-Although more moderators exist in the literature (ie., data aggregation level),
-they do not appear as often as required for the meta-regressions. Table
+indicator for the type of independent variable used in the original study. The
+additional moderators are: 1) publication year; 2) paper publication in an
+academic journal; 3) estimation method; 4) institutional design; 5) electoral
+system. Since the literature on the "law of $1/n$" is notably diverse, we
+included only moderators that either refer to important theoretical questions,
+such as the effect of the electoral system on public spending, or to essential
+characteristics of the publications themselves. Although more moderators exist
+in the literature (e.g., data aggregation level), they do not appear as often
+as necessary for their inclusion in the meta-regressions. Table
 \ref{tab:descriptive} shows the descriptive statistics of the moderator
@@
 
-```{r, echo = FALSE, results='hide', warning=FALSE, message=FALSE}
+\footnotesize
+```{r descriptive, warning=F, message=F, echo = FALSE, cache=TRUE, results='asis'}
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Coefficients")
-fulldat$usemeta2 <- as.character(fulldat$usemeta2)
-fulldat$usemeta2 <- factor(fulldat$usemeta2)
-aux <- select(fulldat, usemeta2, indepvar2, year, published,
-              elecsys2, method) %>%
+levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
+aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
+              year, published, instdesign) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Published work`        = published,
-         `Electoral system` = elecsys2,
-         `Estimation method` = method)
+         `Estimation method`     = method,
+         `Institutional Design`  = instdesign,
+         `Electoral system`      = elecsys2)
 
-res <- export2latex(
-  descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-             show.p.overall = F, show.all = T, all.last = T), 
-  caption = 'Descriptive statistics of moderators\\label{tab:descriptive}'
-)
-res <- gsub(pattern = '\\[ALL\\]', 'All Coefficients', res$desc, useBytes = T)
-cat(res)
+export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
+                        show.p.overall = F, show.all = T),
+          caption = "Descriptive Statistics of Moderators",
+          format  = "latex")
 ```
-
-\footnotesize
-\begin{longtable}{lccc}\caption{Descriptive Statistics of Moderators\label{tab:descriptive}}\\
-\hline  
-& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
-&       N=42        &       N=100        &    N=142    \\
-\hline
-\hline     
-\endfirsthead 
-\multicolumn{4}{l}{\tablename\ \thetable{} \textit{-- continued from previous page}}\\ 
-\hline
-& Main Coefficients & Other Coefficients &    All Coefficients   \\ 
-&       N=42        &       N=100        &    N=142    \\ 
-\hline
-\hline  
-\endhead   
-\hline
-\multicolumn{4}{l}{\textit{continued on next page}} \\ 
-\endfoot   
-\multicolumn{4}{l}{}  \\ 
-\endlastfoot 
-Independent Variables: &                   &                    &            \\ 
-$\qquad$K &    12 (28.6\%)     &     33 (33.0\%)     & 45 (31.7\%) \\ 
-$\qquad$N &    24 (57.1\%)     &     55 (55.0\%)     & 79 (55.6\%) \\ 
-$\qquad$logN &     6 (14.3\%)     &     12 (12.0\%)     & 18 (12.7\%) \\ 
-Year &    2009 (6.56)    &    2008 (5.82)     & 2008 (6.04)\\ 
-Published work: &                   &                    &            \\ 
-$\qquad$Yes &    36 (85.7\%)     &     93 (93.0\%)     & 129 (90.8\%)\\ 
-$\qquad$No &     6 (14.3\%)     &     7 (7.00\%)      & 13 (9.15\%) \\ 
-Electoral system: &                   &                    &            \\ 
-$\qquad$Majoritarian &    22 (52.4\%)     &     46 (46.0\%)     & 68 (47.9\%) \\ 
-$\qquad$Non-Majoritarian &    20 (47.6\%)     &     54 (54.0\%)     & 74 (52.1\%) \\ 
-Estimation method: &                   &                    &            \\ 
-$\qquad$OLS &    11 (26.2\%)     &     36 (36.0\%)     & 47 (33.1\%) \\ 
-$\qquad$PANEL &    23 (54.8\%)     &     51 (51.0\%)     & 74 (52.1\%) \\ 
-$\qquad$IV &     5 (11.9\%)     &     7 (7.00\%)      & 12 (8.45\%) \\ 
-$\qquad$RDD &     3 (7.14\%)     &     6 (6.00\%)      &  9 (6.34\%)  \\
-
-\hline
-\end{longtable}
-
 \normalsize
 
-Since most selected articles have more than one effect size, the observations
-in our dataset are not independent. To reduce the impact of multicollinearity,
-we estimate the models using two sets of study coefficients. The first group
-includes only the most rigorous model from each paper, that is, those estimated
-with the largest $n$, most control variables, and fixed effects if the authors
-added them. If the article employed a regression discontinuity design, we chose
-the coefficient from the optimal bandwidth or from the intermediate one. This
-sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
-independent variables of interest \citep{baqir1999districts, bjedov2014impact,
-bradbury2001legislative, chen_malhotra_2007, crowley2019law,
+A key methodological issue we had to address concerns the potential violation
+of an important assumption in a meta-analysis, that of effect size independence
+[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
+sample, authors frequently use similar datasets, and almost all papers fit more
+than one model with similar variables, what suggests that the assumption does
+not hold. We use two procedures to tackle this problem. First, we created two
+sets of study coefficients to reduce the impact of multicollinearity in our
+estimations. The first group includes only the most rigorous models from each
+paper, that is, those estimated with the largest $n$, most control variables,
+and fixed effects if the authors added them. If the article employed a
+regression discontinuity design, we chose the coefficient from the optimal
+bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
+estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
+two dependent or independent variables of interest\footnote{The papers that
+used more than one dependent or independent variable of interest are
+\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
+chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
 lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading}. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect
-sizes reported in the `r length(unique(dat$id))` papers. Here we focus on the results for our restricted
+ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
+contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
+`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
 sample as we consider them more robust, but the findings are very similar when
-we use the extended set. We discuss eventual differences in the next section.
-Please refer to the Supplementary Material for further information about our
-sampling process and for the complete results.
+we use the extended set.
 
-# Results
-
-## Binomial Z-Tests
-\label{sub:binomial}
-
-The "law of $1/n$" states that more legislators increase government expenditure.
-Here we employ three methods to assess the empirical validity of that
-relationship. First, we run a binomial one-proportion z-test to determine
-whether the study coefficients have a positive or negative sign. Then, we fit 9
-random-effect models using the \texttt{meta} \citep{balduzzi2019perform} and the
-\texttt{dmetar} \citep{dmetar2019} packages for the \texttt{R} statistical
-language \citep{rstats2019}. We estimate the true effect size variance
-($\tau^2$) with a Restricted Maximum Likelihood Estimator, which the literature
-considers the most precise for continuous dependent variables
-\citep{veroniki2016methods}. Lastly, we run a series of meta-regressions to test
-possible sources of result heterogeneity. To recapitulate, our independent
-variables of interest are lower chamber size ($n$), the natural logarithm of
-lower chamber size (log($n$)), and upper chamber size ($k$). The dependent
-variables are public expenditure per capita, the natural logarithm of public
-expenditure per capita, and government expenditure as a percentage of GDP. Since
-the outcomes have different scales, we treat them separately in our models.
-
-```{r, cache=TRUE, echo = FALSE}
-aux <- filter(dat, indepvar2 == "N")
-binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-aux <- filter(dat, indepvar2=='K')
-binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
-aux <- filter(dat, indepvar2 == "logN")
-binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
-```
-
-The binomial z-test evaluates whether the coefficient of our independent
-variables are positive or negative. The null hypothesis here states that the
-sign of the coefficient is equally likely to be positive or negative. We start
-with $n$, lower house size. Our results indicate that there is no correlation
-between the number of legislators in the lower house and public expenditure 
-(successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binN$p.value), 3)`). Note that the "law of $1/n$" suggests that there is a positive
-association between both. The binomial test for log($n$) also shows a
-non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
-positive result for the number of legislators in the upper house ($k$), which is
-in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binK$p.value), 3)`).
-
-## Meta-Analysis
-\label{sub:Meta-Analysis}
-
-We then proceed to the meta-analysis. We matched the house size variables with
-our measures of government spending and created a theoretical $3 \times 3$
-matrix. Out of the 9 possible variable combinations, we found only 7 in
-the article pool. Our sample includes no papers that analyse the relationships
-between log($n$) and public expenditure per capita or between $k$ and the
-logarithm of public expenditure per capita.
-
-```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
-mod <- list()
-# Pooling effects analysis -- ExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'ExpPC')
-
-mod[[1]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-# Pooling effects analysis -- ExpPC x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod[[2]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-# Pooling effects analysis -- logExpPC x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'logExpPC')
-
-mod[[3]] <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction = TRUE,
-  sm="SMD"
-  )
-
-# Pooling effects analysis -- logExpPC x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'logExpPC')
-
-mod[[4]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-# Pooling effects analysis -- PCTGDP x N
-aux <- dat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod[[5]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-# Pooling effects analysis -- PCTGDP x logN
-aux <- dat %>%
-  filter(indepvar2 == 'logN',
-         depvar2 == 'PCTGDP')
-
-mod[[6]] <- metagen(
-  coef, SE, data=aux,
-  studlab=paste(authoryear),
-  comb.fixed = FALSE,
-  comb.random = TRUE,
-  method.tau = "REML",
-  hakn = TRUE,
-  prediction=TRUE,
-  sm="SMD"
-  )
-
-# Pooling effects analysis -- PCTGDP x K
-aux <- dat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'PCTGDP')
-
-mod[[7]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-
-# Full model - Pooling effects analysis -- PCTGDP x N
-aux <- fulldat %>%
-  filter(indepvar2 == 'N',
-         depvar2 == 'PCTGDP')
-
-mod[[8]] <- metagen(coef, SE, data = aux,
-          studlab = paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm = "SMD")
-
-# Full data - Pooling effects analysis -- ExpPC x K
-aux <- fulldat %>%
-  filter(indepvar2 == 'K',
-         depvar2 == 'ExpPC')
-
-mod[[9]] <- metagen(coef, SE, data=aux,
-          studlab=paste(authoryear),
-          comb.fixed = FALSE,
-          comb.random = TRUE,
-          method.tau = "REML",
-          hakn = TRUE,
-          prediction=TRUE,
-          sm="SMD")
-```
-
-\begin{landscape}
-\begin{figure}[htb]
-\begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
-\vspace{.3cm}
-\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
-\label{fig:plots}
-\end{center}
-\end{figure}
-\end{landscape}
-
-Figure \ref{fig:plots} shows the forest plots for our restricted sample,
-which includes only the `r dim(dat)[1]` main coefficients of the 
-`r length(unique(dat$id))` selected papers. On the left side of the plots are 
-the name of the study authors and the paper publication year. For unpublished
-studies, we included the first year the paper was available online. The bars in
-the middle show the reported effect sizes and the vertical lines indicate their
-average, weighted by standard errors. The length of the lines represent the
-precision of the estimates. The red line at the bottom of the figures displays
-the aggregate coefficients plus their respective confidence intervals.
-
-The first column of the graph reports the results for $n$, lower chamber size.
-In the first model, which correlates $n$ and expenditure per capita, we find a
-standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
-(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
-= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
-effect size is zero. The $I^2$ statistic, which quantifies the degree of
-heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
-indicate very high study heterogeneity [@higgins2019cochrane].
-
-We see similar results when we compare $n$ with log expenditure per capita. In
-this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
-`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
-interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
-statistically indistinguishable from zero.
-
-In our restricted sample, larger lower house size also does not increase
-government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
-`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
-[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%). We find a positive effect in our extended
-sample and the coefficient is statistically significant at the 10\% level
-(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
-`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; `r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
-result supports the "law of 1/$n$", but the evidence is moderate
-as the prediction interval include zero.
-
-Next, we present the meta-analyses using log($n$), the logarithm of lower house
-size, as the main explanatory variable. We start with the relationship between
-log($n$) and the logarithm of expenditure per capita. The result is positive and
-statistically significant at 10\%, but the prediction interval encompasses zero
-(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
-`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%). Although the
-coefficient has the predicted sign, we should interpret the finding with caution
-as it does not replicate in our sample of `r dim(fulldat)[1]` effect sizes.
-
-Our model that correlates log($n$) with public expenditures as a percentage of
-GDP fails to reach conventional levels of statistical significance (studies =
-`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
-prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
-also gives us a null result.
-
-The third set of models uses $k$, upper house size, as the main independent
-variable. We find a positive correlation between $k$ and expenditure per capita
-but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
-= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
-[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
-interval again includes zero. When we run the same analysis in the extended
-sample, we see a significant coefficient for the estimate, yet the prediction interval also
-contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
-$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).
-
-Our last estimation analyses the relationship between $k$ and government
-spending as a percentage of GDP. The coefficient is not statistically
-significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
-= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
-$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.
-
-In a nutshell, we do not find strong evidence in favour of the "law of $1/n$".
-While some models do show a positive and statistically significant result, none
-of the prediction intervals are totally positive or negative. The studies also
-have considerable heterogeneity, what indicates that the original coefficients
-do not point consistently towards the same direction.
-
-One reason why we have not detected any strong effects may be due to the
-identification strategy authors use in their models. On the one hand, OLS and
-panel data models require too many controls to make units comparable, and they
-are vulnerable to omitted variable bias or post-treatment bias
-[@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
-methods such as instrumental variables and regression discontinuity designs
-have become popular because of their high internal validity
-[@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated effects
-for two sets of models that employ causal estimation techniques. They measure
-the impact of lower house size on expenditure per capita (left) and on the
-natural logarithm of expenditure per capita (right).
-
-\vspace{.06cm}
-
-\begin{figure}[htb]
-\begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
-\vspace{.3cm}
-\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
-\label{fig:plots2}
-\end{center}
-\end{figure}
-
-\newpage
-
-Papers that employed instrumental variables show some interesting variation: out
-of the four coefficients listed, two are positive and two are negative. Two of
-these four coefficients are significant, again one positive and one negative.
-The subgroup analysis presents a SMD which is negative but insignificant. In
-contrast, all papers that use regression discontinuity designs show negative and
-statistically significant results. Since only three papers in our sample use
-RDDs, we are cautious about predicting an overall negative relation, but they do
-indicate that better identification strategies yield a zero-to-negative impact
-of legislature size on expenditure, in support of the reverse "law of $1/n$".
-
-## Meta-Regressions
-\label{sub:regressions}
-
-In this section, we run a series of meta-regressions with covariates that may
-account for differences across the selected papers. The first variable indicates
-whether the study uses $n$, log($n$) or $k$ as its main explanatory variable.
-The second variable shows the study publication year, which we included to
-capture temporal variation in the study coefficients. We also add a dummy
-variable to assess whether published articles report effect sizes that are
-higher or lower than those from working papers. The fourth variable measures
-whether studies focusing on non-majoritarian electoral systems report
-coefficients that are smaller or larger than those from majoritarian countries.
-Our last covariate is a categorical variable indicating the statistical
-procedure used in the original models (panel data, instrumental variables,
-OLS, or regression discontinuity design).
-
-```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
-res <- list()
-
-## Expenditure as percentage GDP -- Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='PCTGDP',
-            slab = dat$authoryear)
-
-res[[1]] <- tibble(
-     ` ` = c("Intercept",
-             "Indepvar: N",
-             "Indepvar: logN",
-             "Year",
-             "Elecsys: Non-Majoritarian",
-             "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "PCTGDP"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 4)))
-
-## Expenditure as percentage GDP -- Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-res[[2]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Indepvar: logN",
-          "Year",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "PCTGDP - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Expenditure per capita - Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear,
-            control=list(maxiter=1000))
-
-res[[3]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-res[[4]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Elecsys: Non-Majoritarian",
-          "Method: Panel",
-          "Method: IV"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "ExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Log of Expenditure per capita - Restricted
-mod <- rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-res[[5]] <- tibble(
-   ` ` = c("Intercept",
-           "Indepvar: N",
-           "Year",
-           "Published: No",
-           "Method: Panel"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4 ), ")"),
-  model = "logExpPC"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-
-# Log of Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ indepvar2+year+published+elecsys2+method,
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-res[[6]] <- tibble(
-  ` ` = c("Intercept",
-          "Indepvar: N",
-          "Year",
-          "Published: No",
-          "Method: Panel",
-          "Method: RDD"),
-  Estimate = mod[["beta"]],
-  SE = mod[["se"]],
-  `T` = mod[["zval"]],
-  `P-Value` = mod[["pval"]],
-  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
-              round(mod[["ci.ub"]], digits = 4), ")"),
-  model = "logExpPC - All coefs"
-) %>%
-  mutate_if(is.numeric, list(~round(., digits = 3)))
-strep <- function (x) {
-  ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*','')))
-}
-```
-
-```{=latex}
-\vspace{0.5cm}
-
-\begin{table}[htpb]
-\caption{Meta Regression Results\label{tabregressions}}
-\footnotesize
-\centering
-\begin{tabular}{lcccccc}
-\toprule
-\midrule
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} \\
-\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7}
-& Restricted & Extended & Restricted & Extended & Restricted & Extended \\
-\midrule
-Independent Variable: $N$ & `r round(res[[3]][2,2],3)` & `r round(res[[4]][2,2],3)` & `r round(res[[5]][2,2],3)` & `r round(res[[6]][2,2],3)` & `r round(res[[1]][2,2],3)` & `r round(res[[2]][2,2],3)`\\
-                          & (`r round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])` & (`r round(res[[4]][2,3],3)`)`r strep(res[[4]][2,5])` & (`r round(res[[5]][2,3],3)`)`r strep(res[[5]][2,5])` & (`r round(res[[6]][2,3],3)`)`r strep(res[[6]][2,5])` & (`r round(res[[1]][2,3],3)`)`r strep(res[[1]][2,5])` & (`r round(res[[2]][2,3],3)`)`r strep(res[[2]][2,5])`\\
-%
-Independent Variable: log($N$) &  &  &  &  & `r round(res[[1]][3,2],3)` & `r round(res[[2]][3,2],3)`\\
-                               &  &  &  &  & (`r round(res[[1]][3,3],3)`)`r strep(res[[1]][3,5])` & (`r round(res[[2]][3,3],3)`)`r strep(res[[2]][3,5])`\\
-%
-Year & `r round(res[[3]][3,2],3)` & `r round(res[[4]][3,2],3)` & `r round(res[[5]][3,2],3)` & `r round(res[[6]][3,2],3)` & `r round(res[[1]][4,2],3)` & `r round(res[[2]][4,2],3)`\\
-     & (`r round(res[[3]][3,3],3)`)`r strep(res[[3]][3,5])` & (`r round(res[[4]][3,3],3)`)`r strep(res[[4]][3,5])` & (`r round(res[[5]][3,3],3)`)`r strep(res[[5]][3,5])` & (`r round(res[[6]][3,3],3)`)`r strep(res[[6]][3,5])` & (`r round(res[[1]][4,3],3)`)`r strep(res[[1]][4,5])` & (`r round(res[[2]][4,3],3)`)`r strep(res[[2]][4,5])`\\
-%
-Published: No & `r round(res[[3]][4,2],3)` & `r round(res[[4]][4,2],3)` & `r round(res[[5]][4,2],3)` &  `r round(res[[6]][4,2],3)` &  & \\
-              & (`r round(res[[3]][4,3],3)`)`r strep(res[[3]][4,5])` & (`r round(res[[4]][4,3],3)`)`r strep(res[[4]][4,5])` & (`r round(res[[5]][4,3],3)`)`r strep(res[[5]][4,5])` & (`r round(res[[6]][4,3],3)`)`r strep(res[[6]][4,5])` &  & \\
-%
-Non-Majoritarian (PR \& Mixed) & `r round(res[[3]][5,2],3)` & `r round(res[[4]][5,2],3)` & &  & `r round(res[[1]][5,2],3)` & `r round(res[[2]][5,2],3)` \\
-                               & (`r round(res[[3]][5,3],3)`)`r strep(res[[3]][5,5])` & (`r round(res[[4]][5,3],3)`)`r strep(res[[4]][5,5])` & &  & (`r round(res[[1]][5,3],3)`)`r strep(res[[1]][5,5])` & (`r round(res[[2]][5,3],3)`)`r strep(res[[2]][5,5])`\\
-%
-Method: Panel & `r round(res[[3]][6,2],3)` & `r round(res[[4]][6,2],3)` & `r round(res[[5]][5,2],3)` & `r round(res[[6]][5,2],3)` & `r round(res[[1]][6,2],3)` & `r round(res[[2]][6,2],3)`\\
-              & (`r round(res[[3]][6,3],3)`)`r strep(res[[3]][6,5])` & (`r round(res[[4]][6,3],3)`)`r strep(res[[4]][6,5])` & (`r round(res[[5]][5,3],3)`)`r strep(res[[5]][5,5])` & (`r round(res[[6]][5,3],3)`)`r strep(res[[6]][5,5])` & (`r round(res[[1]][6,3],3)`)`r strep(res[[1]][6,5])` & (`r round(res[[2]][6,3],3)`)`r strep(res[[2]][6,5])`\\
-%
-Method: IV & `r round(res[[3]][7,2],3)` & `r round(res[[4]][7,2],3)` &  &  &  & \\
-           & (`r round(res[[3]][7,3],3)`)`r strep(res[[3]][7,5])` & (`r round(res[[4]][7,3],3)`)`r strep(res[[4]][7,5])` &  &  &  & \\
-%
-Method: RDD &  &  &  & `r round(res[[6]][6,2],3)` &  & \\
-            &  &  &  & (`r round(res[[6]][6,3],3)`)`r strep(res[[6]][6,5])` &  & \\
-% 
-Intercept & `r round(res[[3]][1,2],3)` & `r round(res[[4]][1,2],3)` & `r round(res[[5]][1,2], 3)` & `r round(res[[6]][1,2], 3)` & `r round(res[[1]][1,2], 3)` & `r round(res[[2]][1,2], 3)`\\
-          & (`r round(res[[3]][1,3],3)`)`r strep(res[[3]][1,5])` & (`r res[[4]][1,3]`)`r strep(res[[4]][1,5])` & (`r round(res[[5]][1,3],3)`)`r strep(res[[5]][1,5])` & (`r round(res[[6]][1,3],3)`)`r strep(res[[6]][1,5])` & (`r round(res[[1]][1,3],3)`)`r strep(res[[1]][1,5])` & (`r round(res[[2]][1,3],3)`)`r strep(res[[2]][1,5])`\\
-\bottomrule
-\end{tabular}
-\begin{minipage}{\textwidth}
-\renewcommand{\footnoterule}{}
-\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively.
-We report the results from the permutation tests.
-Reference categories: Independent Variable $= k$; Published $= Yes$; Non-Majoritarian (PR \& Mixed) $= Majoritarian$; Method $= OLS$.
-Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
-\end{minipage}
-\end{table}
-```
-
-\newpage
-
-Table \ref{tabregressions} presents the meta-regression results for our
-restricted and extended samples. Each column represents one of the three
-measures of public spending we discuss in this paper. To reduce the risk of
-false positives in our analyses, we use permutation tests to calculate
-significance levels for the meta-regressions \citep{higgins2004controlling}.
-
-The first two models show the results for public expenditure per capita. No
-variable reaches conventional levels of statistical significance in the
-restricted sample. In the extended sample, we find that models that use $n$ as
-an independent variable have lower effects when
-compared to $k$. This suggests that an additional member in the lower house has
-a smaller impact on public spending than a member in the upper house. Moreover,
-the results for the extended sample point out that recent studies find larger
-effects than older ones.
-
-The third and fourth columns use the natural logarithm of expenditure per capita
-as the dependent variable. None of the covariates are statistically significant in our
-smaller sample, but two moderators are negatively associated with the outcome in
-our larger study pool. They both refer to estimation methods. Studies that
-employ panel/fixed effects or regression discontinuity designs (RDDs) have lower
-coefficients for log expenditure per capita if we take OLS as the reference
-category.
-
-Two variables are statistically significant in the last set of meta-regressions,
-which include public expenditures as a percentage of GDP as the dependent
-variable. Both in our restricted and in our extended samples, recent studies
-have smaller coefficients than early papers, which stands in contrast with
-our previous models. Non-majoritarian voting systems are also
-associated with lower levels of public spending, what is against the theoretical
-expectations of the "law of $1/n$". The results, however, do not replicate in
-the first set of estimations.
-
-Overall, our results suggest that study coefficients are highly sensitive to
-research design choices. The same study samples may produce different outcomes
-depending on the response variables scholars decide to analyse. Moreover, we
-find evidence that results vary considerably if the study employs different
-measures of legislature size or use causal research methods. The impact of
-factors such as the electoral system or year of publication also appear to be
-conditional on the selected model.
+Our second procedure consists of employing multilevel random effect models
+[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
+extra levels to the regular meta-analysis, one including a unique publication
+ID for each paper, and another indicating the data source used in the original
+study. By adding these two levels, we account for within- and between-study
+variation, thus removing these sources of effect size dependency. More
+information about the multilevel models can be found in Section H of the
+Supplementary Material.
 
@@
 
-In this article, we assess the empirical validity of the "law of $1/n$". Based
+In this letter, we assess the empirical validity of the "law of $1/n$". Based
 on a sample of `r length(unique(dat$id))` publications on the topic, our

### 2021-05-26 article/article.Rmd
edits to methods section

@@
 
-We compiled our study sample in three rounds. In the first search round, we
+We compiled our study sample in three search rounds. In the first round, we
 gathered data from three large academic databases (Scopus, Microsoft Academic,
@@
 \citet{weingast1981political}, as it is the foundational work in the literature
-on the "law of $1/n$". We then restricted our query to articles written in
-English and, to ensure that studies were comparable, we only included papers
-that used quantitative methods to investigate the relationship between
-legislature size and public spending\footnote{Please refer to Section C in the
-Supplementary Material for a detailed description of the selection procedure.
-We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
-Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
-resulting papers after each review step.}. After this stage, we identified the
-variables authors most commonly employ to measure government expenditure and
-legislature size, our dependent and independent variables, respectively. For
-government expenditure, our study sample uses (i) public expenditure as a share
-of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
-public expenditure per capita as its main variables of interest\footnote{Since
+on the "law of $1/n$". We then restricted our query to articles written in the
+English language, and to make our study sample comparable, we only selected
+papers that use quantitative methods to analyse data\footnote{Since
 meta-analysis requires a single estimate per observation, we excluded articles
 that use interaction terms or quadratic specifications of our selected
-variables.}. In regards to legislature size, the variables are (i) lower
-chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
-house size\footnote{There are a few important nuances concerning coding of
-these variables. For instance, unicameralism is captured both by lower chamber
-size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
-literature estimates how institutional designs affect this relationship, ours
-and many other articles use both lower and upper chamber sizes as main
-explanatory variables. We did not find any articles that used the natural
-logarithm of upper chamber size.}.
+variables. Please refer to Section C in the Supplementary Material for a
+detailed description of the selection procedure. We also included two PRISMA
+(Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow
+diagrammes \citep{liberati2009prisma} showing the number of resulting papers
+after each review step.}. After this stage, we identified the variables that
+authors employ more often to measure government expenditure and legislature
+size, our dependent and independent variables, respectively. For government
+expenditure, our study sample uses (i) public expenditure as a share of GDP;
+(ii) public expenditure per capita; and (iii) the natural logarithm of public
+expenditure per capita as its main variables of interest. In regards to
+legislature size, the variables are (i) lower chamber size; (ii) natural
+logarithm of lower chamber size; and (iii) upper house size\footnote{There are
+a few important nuances concerning coding of these variables. For instance,
+unicameralism is captured both by lower chamber size ($n = 7$) and by log lower
+chamber size ($n = 5$). Since much of the literature estimates how
+institutional designs affect this relationship, ours and many other articles
+use both lower and upper chamber sizes as main explanatory variables. We did
+not find any articles that used the natural logarithm of upper chamber size.}.
 
@@
 and used a keyword-based query on Google Scholar to broaden the scope of the
-first search. We again restricted the search to articles written in English
-which employed quantitative methods. In the third search round, we looked into
-the personal webpages of every author we had already included in our previous
-sample. The purpose of this manual search was to assess whether there was any
-working paper or unpublished manuscript which we might had missed in the
-previous queries. All papers we found in that last search had already been
-included in our sample. Combined, the three searches produced a dataset of 
-`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
-2021. Table \ref{tab:papers} contains the full list of articles we analyse in
-this paper.
+first search. The search string contained terms strongly associated with the
+literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
+"lower chamber size" OR "council size" OR "parliament size" OR "legislature
+size" OR "number of legislators" OR "legislative size") AND ("spending" OR
+"expenditure" OR "government size")`. We again restricted the search to
+articles written in English which employed quantitative methods. In the third
+search round, we looked into the personal webpages of every author we had
+already included in our previous sample. The purpose of this manual search was
+to assess whether there was any working paper or unpublished manuscript which
+we might had missed in the previous queries. All papers we found in the last
+search had already been included in our sample. Combined, the three searches
+produced a dataset of `r length(unique(dat$id))` studies as of the
+10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
+list of articles we analyse in this paper.
 
@@
 [@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
-sample, authors frequently use similar datasets, and almost all papers fit more
-than one model with similar variables, what suggests that the assumption does
-not hold. We use two procedures to tackle this problem. First, we created two
-sets of study coefficients to reduce the impact of multicollinearity in our
-estimations. The first group includes only the most rigorous models from each
-paper, that is, those estimated with the largest $n$, most control variables,
-and fixed effects if the authors added them. If the article employed a
-regression discontinuity design, we chose the coefficient from the optimal
-bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
-estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
-two dependent or independent variables of interest\footnote{The papers that
-used more than one dependent or independent variable of interest are
-\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
-chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
-lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
-contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
-`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
-sample as we consider them more robust, but the findings are very similar when
-we use the extended set.
+sample, authors frequently use similar datasets in their analyses,
+and almost all papers fit more than one model with similar variables, what
+suggests that the assumption does not hold. We use two procedures to tackle this
+problem. First, we created two sets of study coefficients to reduce the impact
+of multicollinearity in our estimations. The first group includes only the most
+rigorous models from each paper, that is, those estimated with the largest $n$,
+most control variables, and fixed effects if the authors added them. If the
+article employed a regression discontinuity design, we chose the coefficient
+from the optimal bandwidth or from the intermediate one. This sample
+encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
+articles analysed two dependent or independent variables of
+interest\footnote{The papers that used more than one dependent or independent
+variable of interest are \citet{baqir1999districts, bjedov2014impact,
+bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
+gilligan2001fiscal, lee2016supermajority, lee2018court,
+maldonado2013legislatures, primo2006stop, ricciuti2003trading,
+ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
+`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
+papers. Here we focus on the results for our restricted sample as we consider
+them more robust, but the findings are very similar when we use the extended
+set.
 
@@
 study. By adding these two levels, we account for within- and between-study
-variation, thus removing these sources of effect size dependency. More
-information about the multilevel models can be found in Section H of the
-Supplementary Material.
+variation, thus removing these sources of effect size dependency and improving
+the accuracy of the results. More information about the multilevel models can
+be found in Section H of the Supplementary Material.
 

### 2021-05-26 article/resubmission.Rmd

@@
 
-Agrupamentos possíveis (agrupar só os que batem no nosso resultado): 
-- métodos (esse bate)
-- institutional design
-- electoral system
-
-Introduction:
-1 - como está originalmente.
-2 - in this letter we run a meta analysis papapá, explicando o que fazemos no texto e o que encontramos.
-3 - resultados são all over the place: e a literatura ja sabia que eram all over the place (vira revisãozinha de literatura).
-4 - agora a gente diz o que nossos resultados representam pros estudos: no caso, podemos concluir que os autores x, y, z foram pela linha correta.
-
-Results: Colocar resultados da meta-regressão completa na última tabela.
-
-Discussion:
-1 - ok
-2 - ok, só corrigir
-3 - como nossos resultados "resolvem" as questões da teoria
-a linha que avalia o desenho institucional está certa dessa forma.
-sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, nós podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
-Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
-4 - ultimo paragrafo vira o que é o terceiro.
-uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.
-
 Over the past decades, a large literature has examined the relationship between
@@
 effect was often limited to one house [e.g., @baqir2002districting;
-@gilligan1995deviations; @gilligan2001fiscal].
-More recently, the discussion of the "law of $1/n$" has surpassed its original formulation.
-Specifically, the theory meant to explain distributive behavior of US district legislators under majoritarian electoral rules.
-It has since then been applied to a number of contexts whose political features do not fit into what @weingast1981political had theorized.
-
-Colocar aqui no final desse paragrafo "in this paper we..."
-
-The mechanism behind $1/n$ is incumbents' choice of redistributive strategy to optimize chances of reelection.
-The _norm of universalism_, by which all legislators pass each other's bills, guarantees that all representatives are allotted an amount of resources to cater projects to their voters.
-@crowley2019law contests this scenario where coordination costs are minimal, aiming at solving the discrepancies in previous works.
-The literature finds that a number of players and features can override the $1/n$ effect by posing checks to legislative activity and altering coordination costs.
-First, shifts in the level of intra or intergovernmental competition based on district homogeneity, supermajority rules, the size of coalitions, and even gerrymandering have been shown to interfere with the effect of chamber size on spending [@bjedov; @crain1999; @crowley2015; @gilligan2006; @lee2015; @mukherjee2003; @pecorino2018].
-Second, we must take into account players who function as institutional checks, such as strong executives who take on legislative duties, other deliberative chambers, or spending limits, who also directly influence legislators' access to common pool funds [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
-Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
+@gilligan1995deviations; @gilligan2001fiscal]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
 collection of small districts can supply public goods more efficiently than the
@@
 wherein a higher number of legislators in small constituencies decrease the
-overall public spending.
+overall public spending. Recent research has further
+questioned the validity of the "law of $1/n$".
+Since the wide range of empirical tests has produced conflicting results, scholars began to target the theoretical foundations of the law.
+Authors such as @crowley2019law and @pecorino2018supermajority accurately point out that collective action problems have been overlooked, but their expanded models cannot account for all the institutional variation previous studies explore.
 
-Our survey of the scholarship confirms this continuum of positive,
-insignificant, and negative results. Out 
+In this letter, we conduct the first meta-analysis that tests the generality of
+the "law of $1/n$". We select `r length(unique(dat$id))` articles that
+use quantitative methods to assess the impact of legislature size over
+government spending across several dimensions. Out 
 of the `r dim(dat)[1]` coefficients
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. A comprehensive survey and systematic review of the existing evidence may help us reach a
-meaningful conclusion about the effect of legislature size on public spending.
-
-Grudar aqui no final o início do pargrafo seguinte, retirando toda a descrição de ~como conduzimos a meta~, sem descrição das variaveis e modelos.
-
-XXXXXX Meta-analysis is the most appropriate method for this task. Meta-analysis
-combines the outcomes of multiple studies into a single estimation and allows
-scholars to draw robust conclusions from the aggregated data
-[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
+negative and statistically significant.
+Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
+us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
 sources of study heterogeneity, enabling researchers to assess threats to
 external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy]. XXXXXXXX
+academic inquiry [@doucouliagos2008democracy].
 
-In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
-use quantitative methods to assess the impact of legislature size over
-government spending across several dimensions. We run two sets of models: the
-first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
-while the second set includes all coefficients reported in our
-sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
-papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
-sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
-report separate estimates for the impact of lower and upper house size on 
-government expenditures. In the full model, we add every outcome reported in the 
-papers, regardless of whether the coefficient comes from the main tables or from 
-robustness checks. We discuss our sampling process in the Methods section and in 
-the Supplementary Material.}
-Our independent variables consist of three measures, namely the size of the
-lower chamber, its natural logarithm, and the number of members
-in the upper chamber. We evaluate their effect upon public expenditure per
-capita, the natural logarithm of public expenditure per capita, and government
-expenditure as a percentage of GDP. We then estimate if the results vary
-according to four potential sources of effect heterogeneity.
+We believe the scrutiny of the law expanded its initial scope in two directions.
+One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards.
+They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S.
+majoritarian local legislatures, for which the law was conceived.
+Another sector of the scholarship overrides this institutional context.
+They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc.
+produce more nuanced results.
+For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative.
+While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness.
+We address all of these developments in this study.
+We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.
 
 Aggregate results show that legislative size has no significant impact on
-public spending. However, the meta-regressions suggest that our study sample
-has high levels of heterogeneity, and effects differ substantially according to
-study specifications. While papers that employ
-conventional linear regressions often find a positive relation between
+public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
+Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications.
+In the broadest aggregation models, unicameralism supports the positive effect predicted by the
+law of $1/n$.
+Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework.
+It also indirectly endorses studies that find odd results in bicameralism.
+As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal].
+Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.
+
+The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods.
+While papers that employ conventional linear regressions often find a positive relation between
 legislature size and government budgets, recent studies using modern methods of
 causal inference, specially those with regression discontinuity designs,
-provide consistent evidence for a negative relation. This goes in contrast with
-the original theory and supports the existence of a "reverse law of $1/n$".
-Additionally, we find that non-majoritarian voting systems decrease government
-spending as a percentage of GDP, which is also evidence against the theoretical
-expectations of the "law of $1/n$", and they do not have a relevant impact on
-the other measures of public expenditure.
-However, unicameralism strongly supports the positive effect predicted by the original theory.
-This result is contradictory to the rest of our findings, even if unicameral cases mostly reflect the very specific framework under which the theory developed (loosely checked local governments).
-In summary, our analysis does not
-provide robust support for the theory as originally conceived, and causal
-inference models suggest that larger legislatures are associated with lower
-public spending.
+provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
+the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
+with previous findings that lend partial support to the law of $1/n$ 
+[@chen2007law; @crowley2015local; @primo2006stop].
+An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results.
+Overall, our analysis does not
+provide robust support for the theory as originally conceived.
 
@@
 
-We compiled our final sample of papers from two large collections of records.
-In the first round of the search, we scraped three large academic databases (Scopus, Microsoft Academic, and Google Scholar) for studies that cited \citet{weingast1981political}.
-We developed exclusion criteria to select only articles written in the English language that used quantitative methods to investigate the relationship between legislature size and public spending.\footnote{Please refer to section C in the Supplementary Material for a more detailed description of the selection procedure, including a PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow diagram \citet{liberati2009prisma} showing the number of resulting papers after each review step.} Upon restricting the sample, we identified which were the most commonly used measurements to operationalise these variables of interest, and adopted them as our key explanatory variables.\footnote{As meta-analysis requires a single estimate per observation, we excluded articles that use interaction terms or quadratic specifications of our independent variables.} We found those to be public expenditure as a share of GDP, public expenditure per capita, and the natural logarithm of public expenditure per capita as dependent variables.
-As independent variables, most studies use lower chamber size, upper chamber size, and the natural logarithm of lower chamber size.\footnote{There are a few important nuances to the coding of these variables.
-Unicameralism is captured by lower chamber size ($n = 7$) and by log lower chamber size ($n = 5$).
-Since much of the literature estimates how institutional designs affect this relationship, ours and many other articles use both lower and upper chamber sizes as key explanatory variables.
-We did not find any articles that used the natural logarithm of upper chamber size.} In the second round, we selected key terms to conduct a broader search of the literature on Google Scholar and applied the same eligibility criteria.
-Combined, the two searches produced a dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March, 2021.
-Table \ref{tab:papers} contains the full list of articles from which we drew data.
+We compiled our study sample in three rounds. In the first search round, we
+gathered data from three large academic databases (Scopus, Microsoft Academic,
+and Google Scholar) and looked for studies that cited
+\citet{weingast1981political}, as it is the foundational work in the literature
+on the "law of $1/n$". We then restricted our query to articles written in
+English and, to ensure that studies were comparable, we only included papers
+that used quantitative methods to investigate the relationship between
+legislature size and public spending\footnote{Please refer to Section C in the
+Supplementary Material for a detailed description of the selection procedure.
+We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
+Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
+resulting papers after each review step.}. After this stage, we identified the
+variables authors most commonly employ to measure government expenditure and
+legislature size, our dependent and independent variables, respectively. For
+government expenditure, our study sample uses (i) public expenditure as a share
+of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
+public expenditure per capita as its main variables of interest\footnote{Since
+meta-analysis requires a single estimate per observation, we excluded articles
+that use interaction terms or quadratic specifications of our selected
+variables.}. In regards to legislature size, the variables are (i) lower
+chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
+house size\footnote{There are a few important nuances concerning coding of
+these variables. For instance, unicameralism is captured both by lower chamber
+size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
+literature estimates how institutional designs affect this relationship, ours
+and many other articles use both lower and upper chamber sizes as main
+explanatory variables. We did not find any articles that used the natural
+logarithm of upper chamber size.}.
+
+In the second round, we did not require articles to cite @weingast1981political
+and used a keyword-based query on Google Scholar to broaden the scope of the
+first search. We again restricted the search to articles written in English
+which employed quantitative methods. In the third search round, we looked into
+the personal webpages of every author we had already included in our previous
+sample. The purpose of this manual search was to assess whether there was any
+working paper or unpublished manuscript which we might had missed in the
+previous queries. All papers we found in that last search had already been
+included in our sample. Combined, the three searches produced a dataset of 
+`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
+2021. Table \ref{tab:papers} contains the full list of articles we analyse in
+this paper.
 
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Note:} Unpub$=$Unpublished, JPE$=$Journal of Political
+\footnotetext{\textbf{Notre:} Country codes
+follow the ISO 3166-1 alpha-3 international standard.}
+\footnotetext{\textbf{Journals:} Unpub$=$Unpublished, JPE$=$Journal of Political
 Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
@@
 Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
-\footnotetext{\textbf{Note:} 
+\footnotetext{\textbf{Methods:} 
 OLS$=$Ordinary least squares, IV$=$Instrumental variables, Panel$=$Panel
@@
 NM$=$Non-majoritarian (mixed or proportional representation).} 
-\footnotetext{\textbf{Note:} Country codes
-follow the ISO 3166-1 alpha-3 international standard.}
-\footnotetext{\textbf{Note:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
+\footnotetext{\textbf{Dependent Variables:} ExpPC$=$Per capita expenditure, logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as a percentage of GDP.}\end{minipage}
 \end{longtable}
@@
 countries. Early studies used OLS and panel data methods to estimate the
-results, whereas the use of regression discontinuity designs is a recent
-addition to the literature, as the first paper to apply it was published in 2012.
+results, while studies from 2012 onward have also applied causal inference designs,
+such as instrumental variables and regression discontinuity models.
 
@@
 GDP. This indicates that the area has refined the original formulation of $1/n$
-suggested by \citet{weingast1981political} and tested the impact of larger
-legislatures on different measures of government spending. Our independent
-variables of interest are lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
-logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber
-size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
+and tested the impact of larger legislatures on different measures of government
+spending. Our independent variables of interest are lower chamber size 
+(`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
+logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
 
@@
 the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study. The additional moderators are: 1) publication year; 2) paper
-publication in an academic journal; 3) estimation method; 4) institutional design; 5) electoral system.
-Since the literature on the "law of $1/n$" is notably diverse, we included only moderators that either refer to important
-theoretical questions, such as the effect of the electoral system on public
-spending, or to essential characteristics of the publications themselves.
-Although more moderators exist in the literature (ie., data aggregation level),
-they do not appear as often as required for the meta-regressions. Table
+indicator for the type of independent variable used in the original study. The
+additional moderators are: 1) publication year; 2) paper publication in an
+academic journal; 3) estimation method; 4) institutional design; 5) electoral
+system. Since the literature on the "law of $1/n$" is notably diverse, we
+included only moderators that either refer to important theoretical questions,
+such as the effect of the electoral system on public spending, or to essential
+characteristics of the publications themselves. Although more moderators exist
+in the literature (e.g., data aggregation level), they do not appear as often
+as necessary for their inclusion in the meta-regressions. Table
 \ref{tab:descriptive} shows the descriptive statistics of the moderator
@@
          `Electoral system`      = elecsys2)
-
 export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
@@
 
-One of the assumptions in meta-analyses is effect size independence.
-In our sample of coefficients, we have sources of independence within and between articles, and we solve them using two distinct procedures.
-Since authors often submit their data to different models, each paper reports several effect sizes using the same variables.
-To reduce the impact of multicollinearity,
-we produce and analyse two sets of study coefficients. The first group
-includes only the most rigorous model from each paper, that is, those estimated
-with the largest $n$, most control variables, and fixed effects if the authors
-added them. If the article employed a regression discontinuity design, we chose
-the coefficient from the optimal bandwidth or from the intermediate one. This
-sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
-independent variables of interest \footnote{The papers that used more than one dependent or independent variable of interest were \citet{baqir1999districts, bjedov2014impact,
-bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop, ricciuti2003trading, ricciuti2004legislatures}.}.
-Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
-In both restricted and extended sets, a number of papers use overlapping data -- from the same constituency, using the same variables, during the same time period.\footnote{For instance, 8 papers used U.S.
-State data from both the U.S.
-Census Bureau’s “Annual Survey of State and Local Government Finances” and The Council of State Government’s Book of the
-States.} We correct this source of bias by employing a multilevel random effects model [@cheung2014modeling], grouping redundant(?) studies.
-Here we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended set.
-We discuss eventual differences in the next section.
+A key methodological issue we had to address concerns the potential violation
+of an important assumption in a meta-analysis, that of effect size independence
+[@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
+sample, authors frequently use similar datasets, and almost all papers fit more
+than one model with similar variables, what suggests that the assumption does
+not hold. We use two procedures to tackle this problem. First, we created two
+sets of study coefficients to reduce the impact of multicollinearity in our
+estimations. The first group includes only the most rigorous models from each
+paper, that is, those estimated with the largest $n$, most control variables,
+and fixed effects if the authors added them. If the article employed a
+regression discontinuity design, we chose the coefficient from the optimal
+bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
+estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
+two dependent or independent variables of interest\footnote{The papers that
+used more than one dependent or independent variable of interest are
+\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
+chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
+lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
+ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
+contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
+`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
+sample as we consider them more robust, but the findings are very similar when
+we use the extended set.
+
+Our second procedure consists of employing multilevel random effect models
+[@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
+extra levels to the regular meta-analysis, one including a unique publication
+ID for each paper, and another indicating the data source used in the original
+study. By adding these two levels, we account for within- and between-study
+variation, thus removing these sources of effect size dependency. More
+information about the multilevel models can be found in Section H of the
+Supplementary Material.
 
 # Results
+
+Resumir resultados das meta-análises.
+Incluir regressões com todos os coeficientes na tabela de meta-regressions.
+Incluir frases com "highlights" na sub-seção de meta-regressions.
+Trocar parágrafo introdutório e o de binomial z-tests pela nova versão do Danilo (que não subiu pro repo).
 
@@
 result supports the "law of 1/$n$", but the evidence is moderate
-as the prediction interval include zero. XXXXXXXXX
+as the prediction interval include zero.
 
@@
 
+Discussion:
+1 - ok
+2 - ok, só corrigir
+3 - como nossos resultados "resolvem" as questões da teoria
+a linha que avalia o desenho institucional está certa dessa forma.
+sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
+Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
+4 - ultimo paragrafo vira o que é o terceiro.
+uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.
+
 In this article, we assess the empirical validity of the "law of $1/n$". Based
@@
 [@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
-@chen_malhotra_2007; @gilligan2001fiscal; @primo2006stop]. Instead, we find
+@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
 better evidence for the "reverse law of $1/n$", which posits that larger
@@
 bicameralism [@ricciuti2004legislature], and the interplay between upper and
-lower houses [@chen_malhotra_2007] to the main theory, but a comprehensive
+lower houses [@chen2007law] to the main theory, but a comprehensive
 procedural replication of the findings using different samples is yet to be

### 2021-05-26 article/article.Rmd
changes to methods section and intro

@@
 burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity. Most
-early studies that empirically tested the "law of $1/n$", as the theory is
-currently known, indeed found a positive correlation between the number of
-legislature seats and different measures of government spending, although the
-effect was often limited to one house [e.g., @baqir2002districting;
-@gilligan1995deviations; @gilligan2001fiscal]. Recent research has further
-questioned the validity of the "law of $1/n$". For instance, spending limits,
-bicameralism, or strong executives may reduce the inefficiency of pork barrel
-projects [@bradbury2001legislative; @chen_malhotra_2007; @primo2006stop].
-Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
-collection of small districts can supply public goods more efficiently than the
-central government. The authors conclude that a "reverse law of $1/n$" may hold,
+overspend in their districts and transfer the costs to the entire polity. Early
+studies that empirically tested the "law of $1/n$", as the theory is currently
+known, indeed found a positive correlation between the number of legislature
+seats and different measures of government spending, although their results
+were mainly based on US state legislatures and the effect was often limited to
+one house [e.g., @baqir2002districting; @gilligan1995deviations;
+@gilligan2001fiscal].
+
+Later research, however, has questioned the validity of the "law of $1/n$".
+@primo2008distributive affirm that, due to spatial spillovers, a collection of
+small districts can supply public goods more efficiently than the central
+government. The authors conclude that a "reverse law of $1/n$" may hold,
 wherein a higher number of legislators in small constituencies decrease the
-overall public spending.
+overall public spending. Similarly, @primo2006stop and @chen2007law find that
+lower and upper chambers may have mixed effects on government spending, while
+@petterssonlidbom2012size argues that the impact of larger chamber sizes is
+negative when using data from Finland and Sweden.
 
-Our survey of the scholarship confirms this continuum of positive,
-insignificant, and negative results. Out of the `r dim(dat)[1]` coefficients
+Since the wide range of empirical tests of the "law of $1/n$" has produced
+conflicting results, scholars have expanded this research agenda and
+investigated how institutional factors condition the original formulation of
+the theory. For instance, authors such as @crowley2019law and
+@pecorino2018supermajority accurately point out that collective action problems
+have been overlooked in the literature, and recent findings indicate that
+bicameralism [@maldonado2013legislatures], intergovernmental competition
+[@crowley2015local], redistricting [@lee2018court], and party ideology
+[@bjedov2014impact] strongly influence the relationship between seats and
+spending. Moreover,
+
+In this letter, we conduct the first meta-analysis that tests the generality of
+the "law of $1/n$". We select `r length(unique(dat$id))` articles that
+use quantitative methods to assess the impact of legislature size over
+government spending across several dimensions. Out 
+of the `r dim(dat)[1]` coefficients
 included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. Given this diversity of empirical
-findings, a systematic review of the existing evidence may help us reach a
-meaningful conclusion about the effect of legislature size on public spending.
-Meta-analysis is the most appropriate method for this task. Meta-analysis
-combines the outcomes of multiple studies into a single estimation and allows
-scholars to draw robust conclusions from the aggregated data
-[@cooper2019handbook; @hedges1985statistical]. It can also identify potential
+negative and statistically significant.
+Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
+us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
 sources of study heterogeneity, enabling researchers to assess threats to
@@
 
-In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We have selected `r length(unique(dat$id))` articles that
-use quantitative methods to assess the impact of legislature size over
-government spending across several dimensions. We run two sets of models: the
-first group uses only the main estimates of each selected paper (`r dim(dat)[1]`),
-while the second set includes all coefficients reported in our
-sample (`r dim(fulldat)[1]`).\footnote{Although there are `r length(unique(dat$id))`
-papers in our review, we include `r dim(dat)[1]` coefficients in the restricted 
-sample. This is because `r as.numeric(sum(table(table(dat$id))[-1]))` articles 
-report separate estimates for the impact of lower and upper house size on 
-government expenditures. In the full model, we add every outcome reported in the 
-papers, regardless of whether the coefficient comes from the main tables or from 
-robustness checks. We discuss our sampling process in the Methods section and in 
-the Supplementary Material.}
-Our independent variables consist of three measures, namely the size of the
-lower chamber ($n$), its natural logarithm (log($n$)), and the number of members
-in the upper chamber ($k$). We evaluate their effect upon public expenditure per
-capita, the natural logarithm of public expenditure per capita, and government
-expenditure as a percentage of GDP. We then estimate if the results vary
-according to four potential sources of effect heterogeneity.
+We believe the scrutiny of the law expanded its initial scope in two directions.
+One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards.
+They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S.
+majoritarian local legislatures, for which the law was conceived.
+Another sector of the scholarship overrides this institutional context.
+They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc.
+produce more nuanced results.
+For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative.
+While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness.
+We address all of these developments in this study.
+We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.
 
 Aggregate results show that legislative size has no significant impact on
-public spending. However, the meta-regressions suggest that our study sample
-has high levels of heterogeneity, and effects differ substantially according to
-study specifications. We find that one reliable predictor of effect size is the
-research method employed in the original paper. While papers that employ
-conventional linear regressions often find a positive relation between
+public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
+Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications.
+In the broadest aggregation models, unicameralism supports the positive effect predicted by the
+law of $1/n$.
+Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework.
+It also indirectly endorses studies that find odd results in bicameralism.
+As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal].
+Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.
+
+The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods.
+While papers that employ conventional linear regressions often find a positive relation between
 legislature size and government budgets, recent studies using modern methods of
 causal inference, specially those with regression discontinuity designs,
-provide consistent evidence for a negative relation. This goes in contrast with
-the original theory and supports the existence of a "reverse law of $1/n$".
-Additionally, we find that non-majoritarian voting systems decrease government
-spending as a percentage of GDP, which is also evidence against the theoretical
-expectations of the "law of $1/n$", and they do not have a relevant impact on
-the other measures of public expenditure. In summary, our analysis does not
-provide robust support for the theory as originally conceived, and causal
-inference models suggest that larger legislatures are associated with lower
-public spending.
+provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
+the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
+with previous findings that lend partial support to the law of $1/n$ 
+[@chen2007law; @crowley2015local; @primo2006stop].
+An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results.
+Overall, our analysis does not
+provide robust support for the theory as originally conceived.
 
@@
 gathered data from three large academic databases (Scopus, Microsoft Academic,
-and Google Scholar) and looked for studies that cited
-\citet{weingast1981political}, as it is the foundational work in the literature
-on the "law of $1/n$". We then restricted our query to articles written in the
-English language, and to make our study sample comparable, we only selected
-papers that use quantitative methods to analyse data\footnote{Since
-meta-analysis requires a single estimate per observation, we excluded articles
-that use interaction terms or quadratic specifications of our selected
-variables. Please refer to Section C in the Supplementary Material for a
-detailed description of the selection procedure. We also included two PRISMA
-(Preferred Reporting Items for Systematic Reviews and Meta-Analyses) flow
-diagrammes \citep{liberati2009prisma} showing the number of resulting papers
-after each review step.}. After this stage, we identified the variables that
-authors employ more often to measure government expenditure and legislature
-size, our dependent and independent variables, respectively. For government
-expenditure, our study sample uses (i) public expenditure as a share of GDP;
-(ii) public expenditure per capita; and (iii) the natural logarithm of public
-expenditure per capita as its main variables of interest. In regards to
-legislature size, the variables are (i) lower chamber size; (ii) natural
-logarithm of lower chamber size; and (iii) upper house size\footnote{There are
-a few important nuances concerning coding of these variables. For instance,
-unicameralism is captured both by lower chamber size ($n = 7$) and by log lower
-chamber size ($n = 5$). Since much of the literature estimates how
-institutional designs affect this relationship, ours and many other articles
-use both lower and upper chamber sizes as main explanatory variables. We did
-not find any articles that used the natural logarithm of upper chamber size.}.
+and Google Scholar) and looked for studies that were published in English and
+cited \citet{weingast1981political}, as it is the foundational work in the
+literature on the "law of $1/n$". To ensure that our sample was comparable, we
+only selected papers that used quantitative methods to analyse
+data\footnote{Since meta-analysis requires a single estimate per observation,
+we excluded articles that use interaction terms or quadratic specifications of
+our selected variables. Please refer to Section C in the Supplementary Material
+for a detailed description of the selection procedure. We also included two
+PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
+flow diagrammes \citep{liberati2009prisma} showing the number of resulting
+papers after each review step.}. After this stage, we identified six
+measurements that the literature often employs to quantify government
+expenditure and legislature size. For government expenditure, our study sample
+uses (i) public expenditure as a share of GDP; (ii) public expenditure per
+capita; and (iii) the natural logarithm of public expenditure per capita as its
+main variables of interest. In regards to legislature size, the variables are
+(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
+upper house size\footnote{There are a few important nuances concerning coding
+of these variables. Unicameralism, for example, is captured both by lower
+chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
+the literature estimates how institutional designs affect this relationship,
+ours and many other articles use both lower and upper chamber sizes as main
+explanatory variables. We did not find any article that used the natural
+logarithm of upper chamber size in their models.}.
 
@@
 "expenditure" OR "government size")`. We again restricted the search to
-articles written in English which employed quantitative methods. In the third
-search round, we looked into the personal webpages of every author we had
-already included in our previous sample. The purpose of this manual search was
-to assess whether there was any working paper or unpublished manuscript which
-we might had missed in the previous queries. All papers we found in the last
-search had already been included in our sample. Combined, the three searches
-produced a dataset of `r length(unique(dat$id))` studies as of the
-10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
-list of articles we analyse in this paper.
+articles written in English which employed quantitative methods. This search
+added two new results to our sample (**CITE**), but neither of them included
+variables beyond the six measures we had previously identified. In the third
+search round, we looked into the personal webpages of every author whom we had
+already included in our sample. The purpose of this manual search was to assess
+whether there was any working paper or unpublished manuscript that we had
+missed in the two former queries. All papers we found in the last search had
+already been included in our sample. Combined, the three searches produced a
+dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th}
+of March 2021. Table \ref{tab:papers} contains the full list of articles we analyse in
+this paper.
 
@@
 and tested the impact of larger legislatures on different measures of government
-spending. Our independent variables of interest are lower chamber size 
+spending. Our independent variables are lower chamber size 
 (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='N')])`), the natural
 logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
-
-We also coded five moderators that may help us understand the heterogeneity in
-the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study. The
-additional moderators are: 1) publication year; 2) paper publication in an
-academic journal; 3) estimation method; 4) institutional design; 5) electoral
-system. Since the literature on the "law of $1/n$" is notably diverse, we
-included only moderators that either refer to important theoretical questions,
-such as the effect of the electoral system on public spending, or to essential
-characteristics of the publications themselves. Although more moderators exist
-in the literature (e.g., data aggregation level), they do not appear as often
-as necessary for their inclusion in the meta-regressions. Table
-\ref{tab:descriptive} shows the descriptive statistics of the moderator
-variables.
+These six variables formed a $3 \times 3$ table, yet not all combinations were
+available in the data. We found no studies that correlate public expenditure
+per capita with either upper chamber size or the natural logarithm of lower
+house size. Thus, our meta-analysis contains seven of the nine possible
+variable combinations.
 
@@
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
+levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
@@
                         show.p.overall = F, show.all = T),
-          caption = "Descriptive Statistics of Moderators",
+          caption = "Descriptive statistics of moderators",
           format  = "latex")
@@
 
+We also coded five moderators that may help us understand the heterogeneity in
+the reported results. We included them in our meta-regressions alongside an
+indicator for the type of independent variable used in the original study. The
+additional moderators are: 1) publication year; 2) paper publication in an
+academic journal; 3) estimation method; 4) institutional design; 5) electoral
+system. Since the literature on the "law of $1/n$" is notably diverse, we
+added only moderators that either refer to important theoretical questions,
+such as the effect of the electoral system on public spending, or to essential
+characteristics of the publications themselves. Although more moderators exist
+in the literature (e.g., data aggregation level), they do not appear as often
+as necessary for their inclusion in the meta-regressions. Table
+\ref{tab:descriptive} shows the descriptive statistics of the moderator
+variables.
+
 A key methodological issue we had to address concerns the potential violation
@@
 [@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
-sample, authors frequently use similar datasets in their analyses,
-and almost all papers fit more than one model with similar variables, what
-suggests that the assumption does not hold. We use two procedures to tackle this
+sample, authors frequently use similar datasets in their models,
+and almost all papers fit more than one regression with similar variables, what
+suggests that the assumption above does not hold. We use two procedures to tackle this
 problem. First, we created two sets of study coefficients to reduce the impact

### 2021-05-27 article/article.Rmd
change intro text

@@
 
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>. Corresponding author.
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
 
@@
 known, indeed found a positive correlation between the number of legislature
-seats and different measures of government spending, although their results
-were mainly based on US state legislatures and the effect was often limited to
-one house [e.g., @baqir2002districting; @gilligan1995deviations;
+seats and different measures of government spending, although these first
+results were mainly based on US state legislatures and the effect was often
+limited to one house [e.g., @baqir2002districting; @gilligan1995deviations;
 @gilligan2001fiscal].
@@
 
-Since the wide range of empirical tests of the "law of $1/n$" has produced
-conflicting results, scholars have expanded this research agenda and
-investigated how institutional factors condition the original formulation of
-the theory. For instance, authors such as @crowley2019law and
-@pecorino2018supermajority accurately point out that collective action problems
-have been overlooked in the literature, and recent findings indicate that
-bicameralism [@maldonado2013legislatures], intergovernmental competition
+Since many empirical tests of the "law of $1/n$" have produced conflicting
+results, scholars have expanded this research agenda and investigated how
+institutional factors condition the original formulation of the theory. For
+instance, authors such as @crowley2019law and @pecorino2018supermajority
+accurately point out that collective action problems have been overlooked in
+the literature, and recent findings indicate that bicameralism
+[@maldonado2013legislatures], intergovernmental competition
 [@crowley2015local], redistricting [@lee2018court], and party ideology
 [@bjedov2014impact] strongly influence the relationship between seats and
-spending. Moreover,
+spending. Moreover, the literature has increasingly applied causal inference
+designs to estimate the effect of the "law of $1/n$", and in contrast to
+previous studies using panel data, regression discontinuity designs generally
+indicate that more legislators decrease public expenditures
+[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
+respect, scholars have long been aware of the theoretical and empirical
+limitations of the "law of $1/n$", and the proliferation of new studies reflect
+a conscious attempt to assess the robustness of the theory [@crowley2019law].
 
@@
 the "law of $1/n$". We select `r length(unique(dat$id))` articles that
-use quantitative methods to assess the impact of legislature size over
-government spending across several dimensions. Out 
-of the `r dim(dat)[1]` coefficients
-included in our article sample, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
+use quantitative methods to evaluate the impact of legislature size over
+government spending across several dimensions. Our study sample mirrors the
+diversity of the literature. Out of the `r dim(dat)[1]` coefficients
+included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
 them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant.
-Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
-us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
-sources of study heterogeneity, enabling researchers to assess threats to
-external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy].
+negative and statistically significant. Meta-analysis provides a rigorous
+approach to combine heterogeneous outcomes into a single estimation, and it
+allows scholars to gain valuable insights from the aggregated data
+[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
+potential sources of study variability, enabling researchers to assess threats
+to external validity and direct future efforts into more promising areas of
+academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
+been successfully used in medicine and psychology since the 1970s
+[@glass2015meta], and our work contributes to the burgeoning literature that
+applies meta-analytic methods to understand challenging questions in political
+science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
+@lau2007effects; @schwarz2020supporting].
 
-We believe the scrutiny of the law expanded its initial scope in two directions.
-One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards.
-They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S.
-majoritarian local legislatures, for which the law was conceived.
-Another sector of the scholarship overrides this institutional context.
-They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc.
-produce more nuanced results.
-For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative.
-While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness.
-We address all of these developments in this study.
-We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.
+We run binomial tests and meta-regressions to further evaluate the relationship
+between legislature size and government expenditures. We use the binomial tests
+to asses whether the proportion of positive and negative coefficients in our
+sample are statistically different from each other. In the meta-regressions, we
+measure the effect of five moderators that capture different sources of
+heterogeneity in the literature. As our sample includes both published and
+unpublished articles, we also construct a series of funnel plots to test for
+publication bias in existing research on the "law of $1/n$"
+[@easterbrook1991publication; @gerber2001testing].
 
-Aggregate results show that legislative size has no significant impact on
-public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
-Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications.
-In the broadest aggregation models, unicameralism supports the positive effect predicted by the
-law of $1/n$.
-Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework.
-It also indirectly endorses studies that find odd results in bicameralism.
-As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal].
-Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.
+Aggregate results indicate that legislature size has no significant impact on
+public spending. All of our main meta-analysis estimates show that the overall
+effect is not statistically different from zero, thus confirming the
+conflicting findings reported by the literature. However, when we look only at
+articles that employ regression discontinuity designs (RDDs), we see that all
+three papers included in our sample suggest that a higher number of legislators
+leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
+@lewis2019legislature]. In this regard, it is possible that methodological
+choices explain part of the disparity observed in the literature, as studies
+which use causal inference methods consistently point to the same direction.
+One limitation of this finding is that these studies only test the impact of
+lower house size on the natural logarithm of expenditure per capita, and it
+remains unclear whether the results hold with other variables.
 
-The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods.
-While papers that employ conventional linear regressions often find a positive relation between
-legislature size and government budgets, recent studies using modern methods of
-causal inference, specially those with regression discontinuity designs,
-provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
-the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
-with previous findings that lend partial support to the law of $1/n$ 
-[@chen2007law; @crowley2015local; @primo2006stop].
-An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results.
-Overall, our analysis does not
-provide robust support for the theory as originally conceived.
+The meta-regressions provide additional evidence that our study sample is
+highly heterogeneous and that effect sizes differ substantially according to
+study specifications. When using our extended sample of `r dim(fulldat)[1]`
+coefficients, we find that unicameralism is associated with higher public
+spending, as predicted by the "law of $1/n$". Since most unicameral
+legislatures are located in local governments (municipalities or districts),
+this result supports the theory strictly in its first formulation. Moreover,
+our meta-regressions indicate that larger upper chambers spend more in terms of
+per capita expenditure than lower chambers, a result that also appears in the
+binomial tests [@gilligan1995deviations; @gilligan2001fiscal]. Non-majoritarian
+voting systems decrease government spending as a percentage of GDP, but they do
+not have a relevant impact on the other measures of public expenditure,
+following the idea that the $1/n$ effect grows weaker as the empirical cases
+distance from the original definition of the law. Finally, meta-regression
+results confirm that regression discontinuity models reduce public spending
+estimates.
+
+In summary, our results are in line with previous findings that lend partial
+support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
+An assessment of the effects of collective action costs in these analyses is
+crucial to determine the full mechanism operating behind these results.
+Overall, our analysis does not provide robust support for the theory as
+originally conceived.
 
@@
 analyse the impact of legislature size on public expenditures as a percentage of
-GDP. This indicates that the area has refined the original formulation of $1/n$
+GDP. This indicates that the area has refined the original definition of the "law of $1/n$"
 and tested the impact of larger legislatures on different measures of government
@@
 variable combinations.
+
+We also coded five moderators that may help us understand the heterogeneity in
+the reported results. We included them in our meta-regressions alongside an
+indicator for the type of independent variable used in the original study. The
+additional moderators are: 1) publication year; 2) paper publication in an
+academic journal; 3) estimation method; 4) institutional design; 5) electoral
+system. Since the literature on the "law of $1/n$" is notably diverse, we
+added only moderators that either refer to important theoretical questions,
+such as the effect of the electoral system on public spending, or to essential
+characteristics of the publications themselves. Although more moderators exist
+in the literature (e.g., data aggregation level), they do not appear as often
+as necessary for their inclusion in the meta-regressions. Table
+\ref{tab:descriptive} shows the descriptive statistics of the moderator
+variables.
 
@@
 \normalsize
-
-We also coded five moderators that may help us understand the heterogeneity in
-the reported results. We included them in our meta-regressions alongside an
-indicator for the type of independent variable used in the original study. The
-additional moderators are: 1) publication year; 2) paper publication in an
-academic journal; 3) estimation method; 4) institutional design; 5) electoral
-system. Since the literature on the "law of $1/n$" is notably diverse, we
-added only moderators that either refer to important theoretical questions,
-such as the effect of the electoral system on public spending, or to essential
-characteristics of the publications themselves. Although more moderators exist
-in the literature (e.g., data aggregation level), they do not appear as often
-as necessary for their inclusion in the meta-regressions. Table
-\ref{tab:descriptive} shows the descriptive statistics of the moderator
-variables.
 

### 2021-05-27 article/resubmission.Rmd
adds results 1st draft

@@
 burden each one will bear ($1/n$), thus legislators have an incentive to
-overspend in their districts and transfer the costs to the entire polity. Most
-early studies that empirically tested the "law of $1/n$", as the theory is
-currently known, indeed found a positive correlation between the number of
-legislature seats and different measures of government spending, although the
-effect was often limited to one house [e.g., @baqir2002districting;
-@gilligan1995deviations; @gilligan2001fiscal]. Moreover, @primo2008distributive affirm that, due to spatial spillovers, a
-collection of small districts can supply public goods more efficiently than the
-central government. The authors conclude that a "reverse law of $1/n$" may hold,
+overspend in their districts and transfer the costs to the entire polity. Early
+studies that empirically tested the "law of $1/n$", as the theory is currently
+known, indeed found a positive correlation between the number of legislature
+seats and different measures of government spending, although these first
+results were mainly based on US state legislatures and the effect was often
+limited to one house [e.g., @baqir2002districting; @gilligan1995deviations;
+@gilligan2001fiscal].
+
+Later research, however, has questioned the validity of the "law of $1/n$".
+@primo2008distributive affirm that, due to spatial spillovers, a collection of
+small districts can supply public goods more efficiently than the central
+government. The authors conclude that a "reverse law of $1/n$" may hold,
 wherein a higher number of legislators in small constituencies decrease the
-overall public spending. Recent research has further
-questioned the validity of the "law of $1/n$".
-Since the wide range of empirical tests has produced conflicting results, scholars began to target the theoretical foundations of the law.
-Authors such as @crowley2019law and @pecorino2018supermajority accurately point out that collective action problems have been overlooked, but their expanded models cannot account for all the institutional variation previous studies explore.
+overall public spending. Similarly, @primo2006stop and @chen2007law find that
+lower and upper chambers may have mixed effects on government spending, while
+@petterssonlidbom2012size argues that the impact of larger chamber sizes is
+negative when using data from Finland and Sweden.
+
+Since many empirical tests of the "law of $1/n$" have produced conflicting
+results, scholars have expanded this research agenda and investigated how
+institutional factors condition the original formulation of the theory. For
+instance, authors such as @crowley2019law and @pecorino2018supermajority
+accurately point out that collective action problems have been overlooked in
+the literature, and recent findings indicate that bicameralism
+[@maldonado2013legislatures], intergovernmental competition
+[@crowley2015local], redistricting [@lee2018court], and party ideology
+[@bjedov2014impact] strongly influence the relationship between seats and
+spending. Moreover, the literature has increasingly applied causal inference
+designs to estimate the effect of the "law of $1/n$", and in contrast to
+previous studies using panel data, regression discontinuity designs generally
+indicate that more legislators decrease public expenditures
+[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
+respect, scholars have long been aware of the theoretical and empirical
+limitations of the "law of $1/n$", and the proliferation of new studies reflect
+a conscious attempt to assess the robustness of the theory [@crowley2019law].
 
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant.
-Although other studies aimed at solving this inconsistency, meta-analysis is the most appropriate tool, as it combines multiple outcomes into a single estimation and allows
-us to draw robust conclusions from the aggregated data [@cooper2019handbook; @hedges1985statistical]. It can also identify potential
-sources of study heterogeneity, enabling researchers to assess threats to
-external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy].
-
-We believe the scrutiny of the law expanded its initial scope in two directions.
-One group of scholars investigates the original institutional framework for the presence of coalitions, supermajorities, veto powers, and spending limits, which the theory disregards.
-They suggest these dynamics strongly influence the $1/n$ effect -- specifically in U.S.
-majoritarian local legislatures, for which the law was conceived.
-Another sector of the scholarship overrides this institutional context.
-They find that the different political arrangements in national congresses, State legislatures, regional European governments, etc.
-produce more nuanced results.
-For instance, intergovernmental competition, the size ratio between assemblies, and strong executives demonstrated the effect of legislative size on public spending could be non-linear, asymmetrical, and even negative.
-While these trends evolved, causal inference tools became more sophisticated, allowing this inquiry to grow also in roubstness.
-We address all of these developments in this study.
-We coded five different moderators that translate methodological advances in time, the similarity of the empirical cases to the original @weingast1981political framework, and key theoretical issues to identify sources of variation in the literature.
-
-Aggregate results show that legislative size has no significant impact on
-public spending. Our meta-analysis estimates are exactly half positive, and half negative. 
-Meta-regressions suggest that our study sample is highly heterogeneous, and effects differ substantially according to study specifications.
-In the broadest aggregation models, unicameralism supports the positive effect predicted by the
-law of $1/n$.
-Since most unicameral cases in our sample refer to local governments (municipalities or districts), this result supports the theory strictly in its original institutional framework.
-It also indirectly endorses studies that find odd results in bicameralism.
-As follows, meta-regressions confirm previous findings that larger upper chambers spend more in terms of per capita expenditure than lower chambers [@gilligan1995deviations; @gilligan2001fiscal].
-Moreover, non-majoritarian voting systems decrease government spending as a percentage of GDP, and they do not have a relevant impact on the other measures of public expenditure, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original formulation of the law.
-
-The meta-regressions also indicate that the $1/n$ effect found in earlier studies might be sensitive to more robust estimation methods.
-While papers that employ conventional linear regressions often find a positive relation between
-legislature size and government budgets, recent studies using modern methods of
-causal inference, specially those with regression discontinuity designs,
-provide consistent evidence for a negative relation [@crowley2019law; @debenedetto2018; @hohmann2017effect; @lewis2019legislature]. This goes in contrast with
-the original theory and supports the existence of a "reverse law of $1/n$". In summary, our results are in line 
-with previous findings that lend partial support to the law of $1/n$ 
-[@chen2007law; @crowley2015local; @primo2006stop].
-An assessment of the effects of collective action costs in these analyses is crucial to determine the full mechanism operating behind these results.
-Overall, our analysis does not
-provide robust support for the theory as originally conceived.
-
-# Methods
-
-We compiled our study sample in three rounds. In the first search round, we
+negative and statistically significant. Meta-analysis provides a rigorous
+approach to combine heterogeneous outcomes into a single estimation, and it
+allows scholars to gain valuable insights from the aggregated data
+[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
+potential sources of study variability, enabling researchers to assess threats
+to external validity and direct future efforts into more promising areas of
+academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
+been successfully used in medicine and psychology since the 1970s
+[@glass2015meta], and our work contributes to the burgeoning literature that
+applies meta-analytic methods to understand challenging questions in political
+science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
+@lau2007effects; @schwarz2020supporting].
+
+We run binomial tests and meta-regressions to further evaluate the relationship
+between legislature size and government expenditures. We use the binomial tests
+to asses whether the proportion of positive and negative coefficients in our
+sample are statistically different from each other. In the meta-regressions, we
+measure the effect of five moderators that capture different sources of
+heterogeneity in the literature. As our sample includes both published and
+unpublished articles, we also construct a series of funnel plots to test for
+publication bias in existing research on the "law of $1/n$"
+[@easterbrook1991publication; @gerber2001testing].
+
+Aggregate results indicate that legislature size has no significant impact on
+public spending. All of our main meta-analysis estimates show that the overall
+effect is not statistically different from zero, thus confirming the
+conflicting findings reported by the literature. However, when we look only at
+articles that employ regression discontinuity designs (RDDs), we see that all
+three papers included in our sample suggest that a higher number of legislators
+leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
+@lewis2019legislature]. In this regard, it is possible that methodological
+choices explain part of the disparity observed in the literature, as studies
+which use causal inference methods consistently point to the same direction.
+One limitation of this finding is that these studies only test the impact of
+lower house size on the natural logarithm of expenditure per capita, and it
+remains unclear whether the results hold with other variables.
+
+The meta-regressions provide additional evidence that our study sample is
+highly heterogeneous and that effect sizes differ substantially according to
+study specifications. When using our extended sample of `r dim(fulldat)[1]`
+coefficients, we find that unicameralism is associated with higher public
+spending, as predicted by the "law of $1/n$". Since most unicameral
+legislatures are located in local governments (municipalities or districts),
+this result supports the theory strictly in its first formulation. Moreover,
+our meta-regressions indicate that larger upper chambers spend more in terms of
+per capita expenditure than lower chambers, a result that also appears in the
+binomial tests [@gilligan1995deviations; @gilligan2001fiscal]. Non-majoritarian
+voting systems decrease government spending as a percentage of GDP, but they do
+not have a relevant impact on the other measures of public expenditure,
+following the idea that the $1/n$ effect grows weaker as the empirical cases
+distance from the original definition of the law. Finally, meta-regression
+results confirm that regression discontinuity models reduce public spending
+estimates.
+
+In summary, our results are in line with previous findings that lend partial
+support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
+An assessment of the effects of collective action costs in these analyses is
+crucial to determine the full mechanism operating behind these results.
+Overall, our analysis does not provide robust support for the theory as
+originally conceived.
+
+# Data and Methods
+
+We compiled our study sample in three search rounds. In the first round, we
 gathered data from three large academic databases (Scopus, Microsoft Academic,
-and Google Scholar) and looked for studies that cited
-\citet{weingast1981political}, as it is the foundational work in the literature
-on the "law of $1/n$". We then restricted our query to articles written in
-English and, to ensure that studies were comparable, we only included papers
-that used quantitative methods to investigate the relationship between
-legislature size and public spending\footnote{Please refer to Section C in the
-Supplementary Material for a detailed description of the selection procedure.
-We include two PRISMA (Preferred Reporting Items for Systematic Reviews and
-Meta-Analyses) flow diagrammes \citep{liberati2009prisma} showing the number of
-resulting papers after each review step.}. After this stage, we identified the
-variables authors most commonly employ to measure government expenditure and
-legislature size, our dependent and independent variables, respectively. For
-government expenditure, our study sample uses (i) public expenditure as a share
-of GDP; (ii) public expenditure per capita; and (iii) the natural logarithm of
-public expenditure per capita as its main variables of interest\footnote{Since
-meta-analysis requires a single estimate per observation, we excluded articles
-that use interaction terms or quadratic specifications of our selected
-variables.}. In regards to legislature size, the variables are (i) lower
-chamber size; (ii) natural logarithm of lower chamber size; and (iii) upper
-house size\footnote{There are a few important nuances concerning coding of
-these variables. For instance, unicameralism is captured both by lower chamber
-size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of the
-literature estimates how institutional designs affect this relationship, ours
-and many other articles use both lower and upper chamber sizes as main
-explanatory variables. We did not find any articles that used the natural
-logarithm of upper chamber size.}.
+and Google Scholar) and looked for studies that were published in English and
+cited \citet{weingast1981political}, as it is the foundational work in the
+literature on the "law of $1/n$". To ensure that our sample was comparable, we
+only selected papers that used quantitative methods to analyse
+data\footnote{Since meta-analysis requires a single estimate per observation,
+we excluded articles that use interaction terms or quadratic specifications of
+our selected variables. Please refer to Section C in the Supplementary Material
+for a detailed description of the selection procedure. We also included two
+PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
+flow diagrammes \citep{liberati2009prisma} showing the number of resulting
+papers after each review step.}. After this stage, we identified six
+measurements that the literature often employs to quantify government
+expenditure and legislature size. For government expenditure, our study sample
+uses (i) public expenditure as a share of GDP; (ii) public expenditure per
+capita; and (iii) the natural logarithm of public expenditure per capita as its
+main variables of interest. In regards to legislature size, the variables are
+(i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
+upper house size\footnote{There are a few important nuances concerning coding
+of these variables. Unicameralism, for example, is captured both by lower
+chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
+the literature estimates how institutional designs affect this relationship,
+ours and many other articles use both lower and upper chamber sizes as main
+explanatory variables. We did not find any article that used the natural
+logarithm of upper chamber size in their models.}.
 
@@
 and used a keyword-based query on Google Scholar to broaden the scope of the
-first search. We again restricted the search to articles written in English
-which employed quantitative methods. In the third search round, we looked into
-the personal webpages of every author we had already included in our previous
-sample. The purpose of this manual search was to assess whether there was any
-working paper or unpublished manuscript which we might had missed in the
-previous queries. All papers we found in that last search had already been
-included in our sample. Combined, the three searches produced a dataset of 
-`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March,
-2021. Table \ref{tab:papers} contains the full list of articles we analyse in
+first search. The search string contained terms strongly associated with the
+literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
+"lower chamber size" OR "council size" OR "parliament size" OR "legislature
+size" OR "number of legislators" OR "legislative size") AND ("spending" OR
+"expenditure" OR "government size")`. We again restricted the search to
+articles written in English which employed quantitative methods. This search
+added two new results to our sample [@coate2011government; @debenedetto2018effect], but neither of them included
+variables beyond the six measures we had previously identified. In the third
+search round, we looked into the personal webpages of every author whom we had
+already included in our sample. The purpose of this manual search was to assess
+whether there was any working paper or unpublished manuscript that we had
+missed in the two former queries. All papers we found in the last search had
+already been included in our sample. Combined, the three searches produced a
+dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th}
+of March 2021. Table \ref{tab:papers} contains the full list of articles we analyse in
 this paper.
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Notre:} Country codes
+\footnotetext{\textbf{Note:} Country codes
 follow the ISO 3166-1 alpha-3 international standard.}
@@
 [@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
-sample, authors frequently use similar datasets, and almost all papers fit more
-than one model with similar variables, what suggests that the assumption does
-not hold. We use two procedures to tackle this problem. First, we created two
-sets of study coefficients to reduce the impact of multicollinearity in our
-estimations. The first group includes only the most rigorous models from each
-paper, that is, those estimated with the largest $n$, most control variables,
-and fixed effects if the authors added them. If the article employed a
-regression discontinuity design, we chose the coefficient from the optimal
-bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]`
-estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed
-two dependent or independent variables of interest\footnote{The papers that
-used more than one dependent or independent variable of interest are
-\citet{baqir1999districts, bjedov2014impact, bradbury2001legislative,
-chen2007law, crowley2019law, erler2007termlimits, gilligan2001fiscal,
-lee2016supermajority, lee2018court, maldonado2013legislatures, primo2006stop,
-ricciuti2003trading, ricciuti2004legislatures}.}. Our second sample, in
-contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the 
-`r length(unique(dat$id))` papers. Here we focus on the results for our restricted
-sample as we consider them more robust, but the findings are very similar when
-we use the extended set.
+sample, authors frequently use similar datasets in their models,
+and almost all papers fit more than one regression with similar variables, what
+suggests that the assumption above does not hold. We use two procedures to tackle this
+problem. First, we created two sets of study coefficients to reduce the impact
+of multicollinearity in our estimations. The first group includes only the most
+rigorous models from each paper, that is, those estimated with the largest $n$,
+most control variables, and fixed effects if the authors added them. If the
+article employed a regression discontinuity design, we chose the coefficient
+from the optimal bandwidth or from the intermediate one. This sample
+encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
+articles analysed two dependent or independent variables of
+interest\footnote{The papers that used more than one dependent or independent
+variable of interest are \citet{baqir1999districts, bjedov2014impact,
+bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
+gilligan2001fiscal, lee2016supermajority, lee2018court,
+maldonado2013legislatures, primo2006stop, ricciuti2003trading,
+ricciuti2004legislatures}.}. Our second sample, in contrast, contains all the
+`r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
+papers. Here we focus on the results for our restricted sample as we consider
+them more robust, but the findings are very similar when we use the extended
+set.
 
@@
 study. By adding these two levels, we account for within- and between-study
-variation, thus removing these sources of effect size dependency. More
-information about the multilevel models can be found in Section H of the
-Supplementary Material.
+variation, thus removing these sources of effect size dependency and improving
+the accuracy of the results. More information about the multilevel models can
+be found in Section H of the Supplementary Material.
 
 # Results
-
-Resumir resultados das meta-análises.
-Incluir regressões com todos os coeficientes na tabela de meta-regressions.
-Incluir frases com "highlights" na sub-seção de meta-regressions.
-Trocar parágrafo introdutório e o de binomial z-tests pela nova versão do Danilo (que não subiu pro repo).
 
@@
 matrix. Out of the 9 possible variable combinations, we found only 7 in
-the article pool. Our sample includes no papers that analyse the relationships
-between the log lower chamber size and public expenditure per capita or between upper chamber size and the
+the article pool. Our sample does not contain any papers that analyse the relationships
+between the log lower chamber size and public expenditure per capita, or between upper chamber size and the
 logarithm of public expenditure per capita.
-We standardized effect sizes by drawing the coefficients and standard errors from the articles.
+We standardised effect sizes by drawing the coefficients and standard errors from the articles.
 When the latter were not directly available, we used t-statistics to retrieve them.
@@
 which includes only the `r dim(dat)[1]` main coefficients of the 
-`r length(unique(dat$id))` selected papers. On the left side of the plots are 
-the name of the study authors and the paper publication year. For unpublished
+`r length(unique(dat$id))` selected papers.\footnote{Please refer to Sections H and I in the Supplementary Material for full results regarding both samples.} On the left side of the plots are 
+the names of the study authors and paper publication year. For unpublished
 studies, we included the first year the paper was available online. The bars in
@@
 The first line of graphs reports the results for lower chamber size. 
-In the first model, which correlates lower chamber size and expenditure per capita, we find a
-standardised mean difference (SMD) of `r round(mod[[1]]$TE.random,3)` and a standard error of `r round(mod[[1]]$seTE.random,3)`
-(studies = `r mod[[1]]$k`, 95\% CI = [`r round(mod[[1]]$lower.random,3)`; `r round(mod[[1]]$upper.random,3)`], $p$-value = `r round(mod[[1]]$pval.random,3)` , prediction interval
-= [`r round(mod[[1]]$lower.predict,3)`; `r round(mod[[1]]$upper.predict,3)`]). Therefore, we cannot reject the null hypothesis that the
-effect size is zero. The $I^2$ statistic, which quantifies the degree of
-heterogeneity among studies, is equal to `r round(mod[[1]]$I2*100, 2)`\%. $I^2$ values above 75\%
-indicate very high study heterogeneity [@higgins2019cochrane].
-
-We see similar results when we compare lower chamber size with log expenditure per capita. In
-this model, the average effect size is `r round(mod[[3]]$TE.random,3)` and the standard error is
-`r round(mod[[3]]$seTE.random,3)` (studies = `r mod[[3]]$k`, 95\% CI = [`r round(mod[[3]]$lower.random,3)`; `r round(mod[[3]]$upper.random,3)`], $p$-value = `r round(mod[[3]]$pval.random,3)`, prediction
-interval = [`r round(mod[[3]]$lower.predict,3)`; `r round(mod[[3]]$upper.predict,3)`]; $I^2$ = `r round(mod[[3]]$I2*100, 2)`\%). The coefficient is 
-statistically indistinguishable from zero.
-
-In our restricted sample, larger lower house size also does not increase
-government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD = `r round(mod[[5]]$TE.random,3)`, SE =
-`r round(mod[[5]]$seTE.random,3)`, 95\% CI = [`r round(mod[[5]]$lower.random,3)`; `r round(mod[[5]]$upper.random,3)`], $p$-value = `r round(mod[[5]]$pval.random,3)`, prediction interval =
-[`r round(mod[[5]]$lower.predict,3)`; `r round(mod[[5]]$upper.predict,3)`], $I^2$ = `r round(mod[[5]]$I2*100, 2)`\%).
-In the extended sample the effect is negative, but it is also statistically insignificant.
-
-XXXXX We find a positive effect in our extended
-sample and the coefficient is statistically significant at the 10\% level
-(coefficients = `r mod[[8]]$k`, SMD = `r round(mod[[8]]$TE.random,3)`, SE = `r round(mod[[8]]$seTE.random,3)`, 95\% CI = [`r round(mod[[8]]$lower.random,3)`; `r round(mod[[8]]$upper.random,3)`], $p$-value =
-`r round(mod[[8]]$pval.random,3)`, prediction interval = [`r round(mod[[8]]$lower.predict,3)`; #`r round(mod[[8]]$upper.predict,3)`], $I^2$ = `r round(mod[[8]]$I2*100, 2)`\%). The 
-result supports the "law of 1/$n$", but the evidence is moderate
-as the prediction interval include zero.
+In the first model, which correlates lower house and expenditure per capita, we find a
+standardised mean difference (SMD) of 0.022 and a standard error of 0.131
+(studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value = 0.87).
+In the restricted sample, the effect of lower chamber size on the other two dependent variables is negative, but the remaining statistics are very similar.
+When we compare lower chamber size with log expenditure per capita, the average effect size is -0.031 and the standard error is
+0.049 (studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58).
+Larger lower house size also does not increase government spending as a percentage of GDP (studies = `r mod[[5]]$k`, SMD =
+- 0.006, 95\% CI = [-0.0334; 0.021], $p$-value = 0.563).
+In the extended sample, the effect of lower house size on per capita expenditure and spending as a share of the GDP is positive, but the relationship with the logarithm of per capita expenditure is negative.
+In all cases, coefficients are statistically indistinguishable from zero.
 
 Next, we present the meta-analyses using the logarithm of lower house
-size. We start with the relationship between
-this variable and the logarithm of expenditure per capita. The result is positive, but the coefficient is not significant, and the prediction interval encompasses zero
-(studies = `r mod[[4]]$k`, SMD = `r round(mod[[4]]$TE.random,3)`, SE = `r round(mod[[4]]$seTE.random,3)`, 95\% CI = [`r round(mod[[4]]$lower.random,3)`; `r round(mod[[4]]$upper.random,3)`], $p$-value =
-`r round(mod[[4]]$pval.random,3)`, prediction interval = [`r round(mod[[4]]$lower.predict,3)`; `r round(mod[[4]]$upper.predict,3)`], $I^2$ = `r round(mod[[4]]$I2*100, 2)`\%).
-Results in the full sample are also null.
-
-Our model that correlates log lower chamber size with public expenditures as a percentage of
-GDP fails to reach conventional levels of statistical significance (studies =
-`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`,
-prediction interval = [`r round(mod[[6]]$lower.predict,3)`; `r round(mod[[6]]$upper.predict,3)`], $I^2$ = `r round(mod[[6]]$I2*100, 2)`\%). The extended sample
-also gives us a null result.
+size. The relationship between this variable and the log of per capita expenditure is positive, but the coefficient is not significant
+(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381], $p$-value =
+0.515. The effect of log lower house size on expenditure as a percentage of the GDP is very similar, although the SMD is negative (studies =
+`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`], $p$-value = `r round(mod[[6]]$pval.random,3)`).
+Results in the full sample are also null, and the coefficients for each dependent variable have the same sign as the restricted sample -- positive and negative, respectively.
 
 The third set of models uses upper house size as the main independent
-variable. We find a positive correlation between this variable and expenditure per capita
-but the coefficient is not significant (studies = `r mod[[2]]$k`, SMD = `r round(mod[[2]]$TE.random,3)`, SE
-= `r round(mod[[2]]$seTE.random,3)`, 95\% CI = [`r round(mod[[2]]$lower.random,3)`; `r round(mod[[2]]$upper.random,3)`], $p$-value = `r round(mod[[2]]$pval.random,3)`, prediction interval =
-[`r round(mod[[2]]$lower.predict,3)`; `r round(mod[[2]]$upper.predict,3)`], $I^2$ = `r round(mod[[2]]$I2*100, 2)`\%). But as with the other models, the prediction
-interval again includes zero. When we run the same analysis in the extended
-sample, we see a significant coefficient for the estimate, yet the prediction interval also
-contains zero (coefficients = `r mod[[9]]$k`, SMD = `r round(mod[[9]]$TE.random,3)`, SE = `r round(mod[[9]]$seTE.random,3)`, 95\% CI = [`r round(mod[[9]]$lower.random,3)`; `r round(mod[[9]]$upper.random,3)`],
-$p$-value $<$ 0.001, prediction interval = [`r round(mod[[9]]$lower.predict,3)`; `r round(mod[[9]]$upper.predict,3)`], $I^2$ = `r round(mod[[9]]$I2*100, 2)`\%).
-
-Our last estimation analyses the relationship between upper chamber size and government
-spending as a percentage of GDP. The coefficient is not statistically
-significant, indicating a null effect (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
-= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`, prediction interval = [`r round(mod[[7]]$lower.predict,3)`; `r round(mod[[7]]$upper.predict,3)`],
-$I^2$ = `r round(mod[[7]]$I2*100, 2)`\%). The result is very similar in the extended sample.
-
-In a nutshell, we do not find strong evidence in favour of the "law of $1/n$".
-While some models do show a positive and statistically significant result, none
-of the prediction intervals are totally positive or negative. The studies also
-have considerable heterogeneity, what indicates that the original coefficients
-do not point consistently towards the same direction.
-
-One reason why we have not detected any strong effects may be due to the
+variable. We find a positive correlation between this variable and expenditure per capita (studies = `r mod[[2]]$k`, SMD = 3.658, SE
+= 4.299, 95\% CI = [-6.255; 13.572], $p$-value = 0.419), and a negative relationship with government spending as a percentage of GDP (studies = `r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI
+= [`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`], $p$-value = `r round(mod[[7]]$pval.random,3)`).
+Neither coefficients are significant.
+Results are very similar in the extended sample.
+
+These results yield conservative interpretations.
+Besides all average effect sizes not reaching conventional levels of statistical significance, they are also highly heterogeneous.
+The $I^2$ statistic quantifies the degree of
+heterogeneity among studies.
+@higgins2019cochrane consider any $1/n$ value above 75\% to indicate high heterogeneity, and the lowest $I^2$ we find in the restricted sample is `r round(mod[[2]]$I2*100, 2)`\% (for the subset of upper chamber size and per capita expenditure).
+Additionally, all prediction intervals encompass zero.
+Therefore, we cannot reject the null hypothesis that the effect size is zero in any variable combinations.
+
+In a nutshell, we do not find strong evidence in favour of the "law of $1/n$". One reason for this may be the
 identification strategy authors use in their models. On the one hand, OLS and
@@
 [@cinelli2020making; @pearl2015conditioning]. On the other hand, estimation
-methods such as instrumental variables and regression discontinuity designs
+methods such as instrumental variables (IV) and regression discontinuity designs (RDD)
 have become popular because of their high internal validity
@@
 
-\newpage
-
-Papers that employed instrumental variables show some interesting variation: out
-of the four coefficients listed, two are positive and two are negative. Two of
-these four coefficients are significant, again one positive and one negative.
-The subgroup analysis presents a SMD which is negative but insignificant. In
-contrast, all papers that use regression discontinuity designs show negative and
+Papers that employ instrumental variables and panel/fixed-effects models show somewhat symmetrical distributions.
+Out of the five papers listed under IV, two are positive, two are negative, and one is null.
+In the plot for panel data, although more studies accumulate negative coefficients, the positive shifts are more pronounced.
+Thus, the overall effect is also null.
+In contrast, all papers that use regression discontinuity designs show negative and
 statistically significant results. Since only three papers in our sample use
@@
 indicate that better identification strategies yield a zero-to-negative impact
-of legislature size on expenditure, in support of the reverse "law of $1/n$".
+of legislature size on expenditure, in support of the "reverse law of $1/n$".
 
@@
 OLS, or regression discontinuity design).
-In our last variable, we separate coefficients that use samples from unicameral or bicameral systems, and code papers using polities with different institutional designs as "mixed".
-
-\newpage
-
-Table {tabregressions} presents the meta-regression results for our
+In our last variable, we separate coefficients produced from samples of unicameral or bicameral systems, and code papers that analyse multiple polities with different institutional designs as "mixed".
+
+Table {tab:regressions} presents the meta-regression results for our
 restricted and extended samples. Each column represents one of the three
-measures of public spending we discuss in this paper. To reduce the risk of
+measures of public spending we discuss in this paper, and the last one uses all coefficients. To reduce the risk of
 false positives in our analyses, we use permutation tests to calculate
 significance levels for the meta-regressions \citep{higgins2004controlling}.
+To interpret these results, the sign of coefficients matters the most.
+These meta-regression coefficients can be viewed as representing "the effect of the moderator on the $1/n$ effect".
+This means positive coefficients predict a strengthening of the $1/n$ effect, and negative ones predict it will get weaker under that moderator category, when compared to its reference.
+Since we aggregate different types of independent variables under the same models, the size of the effects does not accurately translate the scale of variations.
+
+[TABLE GOES HERE]
 
@@
 The third and fourth columns use the natural logarithm of expenditure per capita
-as the dependent variable. None of the covariates are statistically significant in our
-smaller sample, but two moderators are negatively associated with the outcome in
+as the dependent variable.
+Among the coefficients in the restricted sample, those in published studies are significantly smaller than those in working papers.
+Another two moderators are negatively associated with the outcome in
 our larger study pool. They both refer to estimation methods. Studies that
@@
 
-Two variables are statistically significant in the last set of meta-regressions,
-which include public expenditures as a percentage of GDP as the dependent
+Three variables are statistically significant in the third set of meta-regressions,
+which include public expenditure as a percentage of GDP as the dependent
 variable. Both in our restricted and in our extended samples, recent studies
-have smaller coefficients than early papers, which stands in contrast with
-our previous models. Non-majoritarian voting systems are also
-associated with lower levels of public spending, what is against the theoretical
-expectations of the "law of $1/n$". The results, however, do not replicate in
+have smaller coefficients than older papers, which stands in contrast with
+our previous models.
+Moreover, the institutional design also affects outcomes.
+Papers that use mixed samples of bicameral and unicameral systems report significantly lower coefficients than those that analyse bicameral legislatures exclusively.
+Non-majoritarian electoral systems are also associated with lower levels of public spending, which may be justified since the "law of $1/n$" was conceived for majoritarian voting.
+These latter results, however, do not replicate in
 the first set of estimations.
 
-Overall, our results suggest that study coefficients are highly sensitive to
-research design choices. The same study samples may produce different outcomes
-depending on the response variables scholars decide to analyse. Moreover, we
-find evidence that results vary considerably if the study employs different
-measures of legislature size or use causal research methods. The impact of
-factors such as the electoral system or year of publication also appear to be
-conditional on the selected model.
+The last two columns report meta-regressions that aggregate all selected studies.
+In the restricted sample of coefficients, unicameralism has a pro-$1/n$ effect.
+This strongly supports the theory's original formulation, as most unicameral occurrences are local governments, for which the "law" was originally conceived.
+This result holds for the extended sample as well.
+When we regress all `r dim(fulldat)[1]` coefficients, the effects of estimation methods become stronger once again.
+Panel/fixed-effects models and regression discontinuity designs both decrease the $1/n$ effect at the .1\% significance level.
+Instrumental variable models follow along these lines.
+Additionally, non-majoritarian voting constituencies appear once again as settings where the law of $1/n$ becomes weaker.
+
+The evidence seems to be sensitive to the methodological design. Our results suggest that the same study samples may produce different outcomes
+depending on the response variables scholars decide to analyse.
+The broadest aggregation level presented the most insightful results in dialogue with the literature.
+The additional legislator in non-majoritarian legislatures does not increase expenditure as much as she would if the system were majoritarian.
+We are also more likely to witness legislative expenditure growing along with the amount of representatives in unicameral legislatures rather than in bicameral systems.
+This indicates that while the law of $1/n$ is not generalisable, its predicted effects are stronger when the institutional features of a polity come closer to its original theoretical framework.
 
@@
 \label{sec:discussion}
+
+1 paragrafo para collective action problems -- raciocionio no "industrial something of legislatures", que é um paper do weingast
+1 para cada problema que o umberto falou
+pargrafo final eh o de acumulo de conhecimento
+
+Temos de manter esse mdoelo porque tem muita variancia nos modelos.
+É inteligível nao ter nenhum resultado, justamente pq tem *muita* variância.
+Quando tinha mais graus de liberdade, dava mais resultado. À medida que fomos colocando mais, diminuiu efeito.
+
+Justificando os null results: 
+Erro do weingast: você acha que cria um novo distrito e que o numero de pessoas se mantem fixo. só que diminui a população!!
+o modelo do weingast funciona numa situação muito especifica, e mudando ela um tiquinho ja nao funciona mais.
+
+jeitos de avançar a literatura:
+ter uma ideia melhor de quais as assumptions você precisa pra funcionar o negocio.
+tem mil assumptions entre os 3 custos/beneficios
+os 3 componentes podem variar da forma que for. um deles é externalidade (no mercado das firmas que estão no outro lugar e que vão contratar).
+e ninguem que fala da lei discute as assumptions!!!
+As assumptions são dificeis de mensurar.
+
+Problemas de identificação (desenho). RDs funcionam melhor.
+Moreover replicação/acumulo na disciplina basicamente nao existe.
+Seria muito surpreendente encontrar resultados dado esse quadro geral, na verdade.
+
+existe um desconforto geral com a teoria mas ninguém toca nos mecanismos.
+
+outro veio teórico:
+os papers de RDD sao todos pra PR, mas o paper do weingast nao eh pra PR.
+Pra PR, eh preciso relaxar a hipotese do weingast: existem sustemas PR mas que a votação dos caras eh concentrada num territorio.
+é uma hipotese fraca do weingast para que ela funcione.
+mas a teoria nao foi feita pra isso.
+por ex. 70% dos vereadores em sp têm votacao concentrada por territorio.
+mas existe uma big assumption da qual ninguém fala.
+se a votacao eh dispersa (geograficamente), a lei do 1/n faz zero sentido.
+PR reforça esse mecanismo, que pode estar correlacionado de formas que a teoria nao prevê.
+
+os padroes desse tipo de paper nao eh o mesmo dos papers de experimento.
+o nosso paper eh uma meta analise muito mais dificil de fazer do que a da mia costa, em que tem todas as stats e todos os coeficientes reportados bonitinhos.
+
+tem uma seleção de qual modelo vai entrar: modelo mais completo. (maior n, efeito fixo - max possivel, maximo de controle, optimal/intermediate bandwidth do RD, etc).
+se tem mais de um modelo que comply com a regra, é o n maior.
+para ser comparavel: soh comparar modelos com as mesmas DV e indvar.
+na meta-regression, a gente coloca todas as indvars, e nao as depvars. porque soh nos interessa que direção o efeito vai, e nao o tamanho do efeito.
+
+a gente nao tem controle sobre o tamanho/scale da variação. a meta regression eh o melhor que a gente pdoe fazer pra limpar essa variação doida.
+forest plots: o que fazemos bem para tornar todas em comparaveis eh ter o good coefficient do modelo, e ter o desvio padrão.
+toda vez que fazemos esse tipo de meta analise, o pacote transforma o coeficiente em seu Hedges’ \(g\).
+
+pergunta pode ser: (A) como fazemos para botar no mesmo saco um RD e um panel? resp: isso eh um problea mesmo nas meta analises, mas na meta regressao isso limpa.
+(B) coeficientes sao all over the place. como vocês conseguiram comparar cada um?
+Daí explicar o procedimento. Na restricted sample, we cherry picked, mas no appendix rodamos a analise com tudo junto pra vc, revisor, ver.
 
@@
 stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
-matsusaka2005endogeneity, ricciuti2004legislatures}
+matsusaka2005endogeneity, ricciuti2004legislatures, coate2011government}

### 2021-05-29 article/article.Rmd
revise methods section, add results

@@
 We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
-Replication materials are available at <https://github.com/danilofreire/distributive-politics-meta-analysis>.
+Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>.
 We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
@@
 Since many empirical tests of the "law of $1/n$" have produced conflicting
-results, scholars have expanded this research agenda and investigated how
-institutional factors condition the original formulation of the theory. For
+results, scholars have expanded this research agenda and closely investigated
+how institutional factors condition the original formulation of the theory. For
 instance, authors such as @crowley2019law and @pecorino2018supermajority
@@
 are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. Meta-analysis provides a rigorous
-approach to combine heterogeneous outcomes into a single estimation, and it
-allows scholars to gain valuable insights from the aggregated data
-[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
-potential sources of study variability, enabling researchers to assess threats
-to external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
-been successfully used in medicine and psychology since the 1970s
-[@glass2015meta], and our work contributes to the burgeoning literature that
-applies meta-analytic methods to understand challenging questions in political
-science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
-@lau2007effects; @schwarz2020supporting].
+negative and statistically significant. Given the volume and the disparity of
+the studies, we employ meta-analysis to summarise the results. Meta-analysis
+provides a rigorous approach to combine heterogeneous outcomes into a single
+estimation, and it allows scholars to gain valuable insights from the
+aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
+can also identify potential sources of study variability, enabling researchers
+to assess threats to external validity and direct future efforts into more
+promising areas of academic inquiry [@doucouliagos2008democracy]. Research
+synthesis methods have been successfully applied in medicine and psychology
+since the 1970s [@glass2015meta], and our work contributes to the burgeoning
+literature that uses meta-analytic methods to understand challenging questions
+in political science [@costa2017responsive; @doucouliagos2008democracy;
+@green2013field; @lau2007effects; @schwarz2020supporting].
 
 We run binomial tests and meta-regressions to further evaluate the relationship
-between legislature size and government expenditures. We use the binomial tests
-to asses whether the proportion of positive and negative coefficients in our
+between legislature size and government expenditures. We use binomial tests
+to assess whether the proportions of positive and negative coefficients in our
 sample are statistically different from each other. In the meta-regressions, we
@@
 conflicting findings reported by the literature. However, when we look only at
-articles that employ regression discontinuity designs (RDDs), we see that all
-three papers included in our sample suggest that a higher number of legislators
-leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
+articles that employ regression discontinuity designs, we see that all three
+papers included in our sample suggest that a higher number of legislators leads
+to lower public spending [@debenedetto2018effect; @hohmann2017effect;
 @lewis2019legislature]. In this regard, it is possible that methodological
-choices explain part of the disparity observed in the literature, as studies
-which use causal inference methods consistently point to the same direction.
-One limitation of this finding is that these studies only test the impact of
-lower house size on the natural logarithm of expenditure per capita, and it
-remains unclear whether the results hold with other variables.
+choices partially explain the divergent results observed in the literature, as
+studies that use causal inference methods consistently point to the same
+direction. One limitation of this finding is that these studies only test the
+impact of lower house size on the natural logarithm of expenditure per capita,
+thus it remains unclear whether the results hold with other variables.
 
@@
 per capita expenditure than lower chambers, a result that also appears in the
-binomial tests [@gilligan1995deviations; @gilligan2001fiscal]. Non-majoritarian
-voting systems decrease government spending as a percentage of GDP, but they do
-not have a relevant impact on the other measures of public expenditure,
-following the idea that the $1/n$ effect grows weaker as the empirical cases
-distance from the original definition of the law. Finally, meta-regression
-results confirm that regression discontinuity models reduce public spending
-estimates.
+binomial tests. Non-majoritarian voting systems decrease government spending as
+a percentage of GDP, but they do not have a relevant impact on the other
+measures of public expenditure, following the idea that the $1/n$ effect grows
+weaker as the empirical cases distance from the original definition of the law.
+Finally, meta-regression results confirm that regression discontinuity models
+reduce public spending estimates.
 
@@
 articles written in English which employed quantitative methods. This search
-added two new results to our sample (**CITE**), but neither of them included
-variables beyond the six measures we had previously identified. In the third
-search round, we looked into the personal webpages of every author whom we had
-already included in our sample. The purpose of this manual search was to assess
-whether there was any working paper or unpublished manuscript that we had
-missed in the two former queries. All papers we found in the last search had
-already been included in our sample. Combined, the three searches produced a
-dataset of `r length(unique(dat$id))` studies as of the 10\textsuperscript{th}
-of March 2021. Table \ref{tab:papers} contains the full list of articles we analyse in
-this paper.
+added two new results to our sample [@coate2011government;
+@debenedetto2018effect], but neither of them included variables beyond the six
+measures we had previously identified. In the third search round, we looked
+into the personal webpages of every author whom we had already included in our
+sample. The purpose of this manual search was to assess whether there was any
+working paper or unpublished manuscript that we had missed in the two former
+queries. All papers we found in the last search had already been included in
+our sample. Combined, the three searches produced a dataset of 
+`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March 2021.
+Table \ref{tab:papers} contains the full list of articles we analyse in this
+paper.
 
 \footnotesize
-\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1cm}}
+\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
 \caption{Papers included in the meta-analysis, ordered by year of appearance}\\
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Note:} Journals: Unpub$=$Unpublished, JPE$=$Journal of
-Political Economy, EJPE$=$European Journal of Political Economy, PC$=$Public
-Choice, JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private
-Enterprise, APSR$=$American Political Science Review, SEJ$=$Southern Economic
-Journal, UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative
-International Development, SSQ$=$Social Science Quarterly, SPPQ$=$State
-Politics and Policy Quarterly, CPS$=$Comparative Political Studies,
-RivPE$=$Rivista di Politica Economica, E\&P$=$Economics and Politics,
-NTJ$=$National Tax Journal. Country codes follow the ISO 3166-1 alpha-3
-international standard. Dependent variable: ExpPC$=$Per capita expenditure,
+\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
+Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
+JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
+APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
+UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
+Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
+Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
+Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
+\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
+international standard.} 
+\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
 logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
-a percentage of GDP. Method: OLS$=$Ordinary least squares, IV$=$Instrumental
+a percentage of GDP.}
+\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
 variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
-design. Electoral system: M$=$Majoritarian, NM$=$Non-majoritarian (mixed or
-proportional representation).} 
+design.}
+\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
+representation).} 
 \end{minipage} 
 \end{longtable}
-
 \normalsize
@@
 countries. Early studies used OLS and panel data methods to estimate the
-results, while studies from 2012 onward have also applied causal inference designs,
-such as instrumental variables and regression discontinuity models.
+results, while studies from 2012 onward have also applied causal inference
+designs such as instrumental variables and regression discontinuity models to
+test the relationship between house size and public spending.
 
@@
 
+We use Hedges' $g$ to calculate effect sizes in our meta-analysis
+[@hedges1981distribution]. While there are other methods to standardise
+coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in
+small sample sizes and is considered more robust than measures such as Cohen's
+$d$ [@lakens2013calculating]. We estimate the Standardised Mean Difference
+(SMD), which represents the effect size in each study relative to the
+variability observed in that study, by extracting the coefficients and the
+standard errors from all articles included in our sample and converting them to
+Hedges' $g$. In cases where authors did not report the standard errors for
+their estimates, we computed them using the t-statistic presented in the
+original tables.
+
+# Results
+
+The "law of $1/n$" states that more legislators increase government
+expenditure. In this paper, we employ three methods to test the empirical
+validity of that relationship. First, we run binomial z-tests to assess the
+frequency of positive and negative coefficients in our sample. Then, we fit 9
+multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
+`dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
+Lastly, we run two sets of meta-regressions to measure the effects of a group
+of moderators on the effect sizes of our study sample. To recapitulate, our
+independent variables of interest are lower chamber size, the natural logarithm
+of lower chamber size, and upper chamber size. The dependent variables are
+public expenditure per capita, the natural logarithm of public expenditure per
+capita, and government expenditure as a percentage of GDP. Since the outcomes
+have different scales, we treat them separately in our models.
+
+```{r, cache=TRUE, echo = FALSE}
+aux <- filter(dat, indepvar2 == "N")
+binN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
+aux <- filter(dat, indepvar2=='K')
+binK <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5)
+aux <- filter(dat, indepvar2 == "logN")
+binlogN <- binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p = 0.5)
+```
+
+## Binomial Z-Tests
+\label{sub:binomial}
+
+The binomial z-test evaluates whether the majority of the coefficients of our
+independent variables are positive or negative[^binomial]. If increasing the
+number of legislators leads to higher public expending, we should expect most
+coefficients to be positive. Conversely, if the "reverse law of $1/n" is true,
+our results should indicate that $p < 0.5$, that is, the proportion of positive
+coefficients is lower than 0.5. The null hypothesis here states that the sign
+of the coefficient is equally likely to be positive or negative.
+
+[^binomial]: Since coefficients are either positive or negative, each of them
+can be considered a Bernoulli trial. Thus, the aggregate results for all papers
+follow a Binomial distribution where parameters $n$ equals the number of papers
+and $p$ is the chance of a positive coefficient. The "law of $1/n$" can be
+reformulated as the chance of $p > 0.5$, which facilitates the testing of the
+theory.
+
+We start with lower house size. Our results indicate that there is no
+correlation between the number of legislators in the lower house and public
+expenditure (successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`], $p$-value = `r round(as.numeric(binN$p.value), 3)`).
+Note that the "law of $1/n$" suggests that there is a positive
+association between both. The binomial test for the natural logarithm of lower
+chamber size also shows a
+non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
+$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
+positive result for the number of legislators in the upper house, which is
+in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
+$p$-value = `r round(as.numeric(binK$p.value), 3)`).
+
+## Meta-Analysis
+\label{sub:Meta-Analysis}
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
+mod <- list()
+# Pooling effects analysis -- ExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'ExpPC')
+
+mod[[1]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- ExpPC x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod[[2]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+# Pooling effects analysis -- logExpPC x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'logExpPC')
+
+mod[[3]] <- metagen(
+  coef, SE, data=aux,
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction = TRUE,
+  sm="SMD"
+  )
+
+# Pooling effects analysis -- logExpPC x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'logExpPC')
+
+mod[[4]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- PCTGDP x N
+aux <- dat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod[[5]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Pooling effects analysis -- PCTGDP x logN
+aux <- dat %>%
+  filter(indepvar2 == 'logN',
+         depvar2 == 'PCTGDP')
+
+mod[[6]] <- metagen(
+  coef, SE, data=aux,
+  studlab=paste(authoryear),
+  comb.fixed = FALSE,
+  comb.random = TRUE,
+  method.tau = "REML",
+  hakn = TRUE,
+  prediction=TRUE,
+  sm="SMD"
+  )
+
+# Pooling effects analysis -- PCTGDP x K
+aux <- dat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'PCTGDP')
+
+mod[[7]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+
+# Full model - Pooling effects analysis -- PCTGDP x N
+aux <- fulldat %>%
+  filter(indepvar2 == 'N',
+         depvar2 == 'PCTGDP')
+
+mod[[8]] <- metagen(coef, SE, data = aux,
+          studlab = paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm = "SMD")
+
+# Full data - Pooling effects analysis -- ExpPC x K
+aux <- fulldat %>%
+  filter(indepvar2 == 'K',
+         depvar2 == 'ExpPC')
+
+mod[[9]] <- metagen(coef, SE, data=aux,
+          studlab=paste(authoryear),
+          comb.fixed = FALSE,
+          comb.random = TRUE,
+          method.tau = "REML",
+          hakn = TRUE,
+          prediction=TRUE,
+          sm="SMD")
+```
+
+We then proceed to the meta-analysis. We matched the house size variables with
+our measures of government spending and created a theoretical $3 \times 3$
+matrix. Out of the 9 possible variable combinations, we found only 7 in the
+article pool. Our sample does not contain any papers that analyse the
+relationships between the log lower chamber size and public expenditure per
+capita, or between upper chamber size and the logarithm of public expenditure
+per capita. We calculated the effect sizes by drawing the coefficients and
+standard errors from the articles and computing Hedges' $g$, which is a widely
+used measure of standardised difference between means. When standard errors
+were not directly available in the texts, we used t-statistics to retrieve
+them.
+
+Figure \ref{fig:plots} shows the forest plots for our restricted sample, which
+includes the `r dim(dat)[1]` main coefficients of the `r length(unique(dat$id))`
+selected papers.\footnote{Please refer to Sections H and I in the Supplementary
+Material for full results regarding both samples.} On the left side of the
+plots are the names of the study authors and paper publication year. For
+unpublished studies, we included the first year the paper was available online.
+The bars in the middle show the reported effect sizes and the vertical lines
+indicate their average, weighted by standard errors. The length of the lines
+represent the precision of the estimates. The red line at the bottom of the
+figures displays the overall effects plus their respective confidence
+intervals.
+
+\begin{landscape}
+\begin{figure}[!ht]
+\centering
+\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
+\vspace{0.3cm}
+\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
+\label{fig:plots}
+\end{figure}
+\end{landscape}
+
+The uppermost row shows the results for lower chamber size in our restricted
+sample. In the first model, which correlates lower house and expenditure per
+capita, we find a standardised mean difference (SMD) of 0.022 and a standard
+error of 0.131 (studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value
+= 0.87), so we cannot rule that the effect is different from zero. Indeed, the
+effect of lower chamber size on the other two dependent variables is also null
+in statistical terms. When we compare lower chamber size with log expenditure
+per capita, the overall effect size is -0.031 and the standard error is 0.049
+(studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58), and
+the impact of larger lower houses on government spending as a percentage of GDP
+is also negligible (studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI =
+[-0.0334; 0.021], $p$-value = 0.563). The results are virtually identical when
+we estimate the meta-analyses using our extended sample, and the all three
+coefficients are again statistically indistinguishable from zero.
+
+Next, we present the meta-analyses using the logarithm of lower house size as
+an independent variable. The relationship between this variable and the log of
+per capita expenditure is positive, but the coefficient is not significant
+(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381],
+$p$-value = 0.515. The effect of log lower house size on expenditure as a
+percentage of the GDP is very similar, although the SMD is negative (studies =
+`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = 
+`r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`;
+`r round(mod[[6]]$upper.random,3)`], $p$-value = 
+`r round(mod[[6]]$pval.random,3)`). Results in the full sample are also null, and
+the coefficients for each dependent variable have the same sign as the
+restricted sample -- positive and negative, respectively.
+
+The third set of models uses upper house size as the main independent variable.
+We find a positive correlation between this variable and expenditure per capita
+(studies = `r mod[[2]]$k`, SMD = 3.658, SE = 4.299, 95\% CI = [-6.255; 13.572],
+$p$-value = 0.419), and a negative relationship with government spending as a
+percentage of GDP (studies = `r mod[[7]]$k`, SMD = 
+`r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI =
+[`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`],
+$p$-value = `r round(mod[[7]]$pval.random,3)`), yet neither coefficient is
+statistically significant. Results are the same in our extended sample.
+
+Taken together, these results yield conservative interpretations. Besides all
+average effect sizes not reaching conventional levels of statistical
+significance, the studies are also notably heterogeneous. The $I^2$ statistic
+quantifies the degree of heterogeneity among studies. @higgins2019cochrane
+consider any $I^2$ value above 75\% to indicate high heterogeneity, and the
+lowest $I^2$ we find in the restricted sample is `r round(mod[[2]]$I2*100,
+2)`\% (for the subset of upper chamber size and per capita expenditure).
+Additionally, all prediction intervals encompass zero. Therefore, we cannot
+reject the null hypothesis that the effect size is zero in any variable
+combination.
+
+In a nutshell, we do not find evidence in favour of the "law of $1/n$".
+One reason for this may be the identification strategy authors use in their
+models. On the one hand, OLS and panel data models require too many controls to
+make units comparable, and they are vulnerable to omitted variable bias or
+post-treatment bias [@cinelli2020making; @pearl2015conditioning]. On the other
+hand, estimation methods such as instrumental variables (IV) and regression
+discontinuity designs (RDD) have become popular because of their high internal
+validity [@angrist2008mostly]. Figure \ref{fig:plots2} shows the disaggregated
+effects for two sets of models that employ causal estimation techniques. They
+measure the impact of lower house size on expenditure per capita (left) and on
+the natural logarithm of expenditure per capita (right).
+
+\vspace{.5cm}
+
+\begin{figure}[htb]
+\begin{center}
+\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
+\vspace{.3cm}
+\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
+\label{fig:plots2}
+\end{center}
+\end{figure}
+
+Papers that employ instrumental variables and panel/fixed-effects models show
+somewhat symmetrical distributions. Out of the five papers listed under IV, two
+are positive, two are negative, and one is null. In the plot for panel data,
+although more studies accumulate negative coefficients, the positive shifts are
+more pronounced, so the overall effect is also null. In contrast, all papers
+that use regression discontinuity designs show negative and statistically
+significant results. Since only three papers in our sample use RDDs, we are
+cautious about predicting an overall negative relationship, but they do
+indicate that better identification strategies yield a zero-to-negative impact
+of legislature size on expenditure, in support of the "reverse law of $1/n$".
+
+## Meta-Regressions
+\label{sub:regressions}
+
+In this section, we run a series of meta-regressions with six moderators to
+account for the heterogeneity across the selected papers. The first variable
+indicates whether the study uses lower chamber size, log lower chamber size, or
+upper chamber size as a main explanatory variable. We include separate effect
+sizes for upper and lower chamber sizes when papers analysed both. The second
+variable shows the study publication year, which we included to capture
+temporal variation in the study coefficients. We also add a dummy variable to
+assess whether published articles report effect sizes that are higher or lower
+than those from working papers. The fourth variable measures whether studies
+focusing on non-majoritarian electoral systems report coefficients that are
+smaller or larger than those from majoritarian countries. The fifth covariate
+is a categorical variable indicating the statistical procedure used in the
+original models (panel data, instrumental variables, OLS, or regression
+discontinuity design). In our last variable, we separate coefficients produced
+from samples of unicameral or bicameral systems, and code papers that analyse
+multiple polities with different institutional designs as "mixed".
+
+Table {tab:regressions} presents the meta-regression results for our restricted
+and extended samples. Each column represents one of the three measures of
+public spending we discuss in this paper, and the last one uses all
+coefficients. To reduce the risk of false positives in our analyses, we use
+permutation tests to calculate significance levels for the meta-regressions
+\citep{higgins2004controlling}. To interpret these results, the sign of
+coefficients matters the most. These meta-regression coefficients can be viewed
+as representing "the effect of the moderator on the $1/n$ effect". This means
+positive coefficients predict a strengthening of the $1/n$ effect, and negative
+ones predict it will get weaker under that moderator category, when compared to
+its reference category. Since we aggregate different types of independent
+variables under the same models, the size of the effects does not accurately
+translate the scale of variations.
+
+\vspace{0.5cm}
+[TABLE GOES HERE]
+\vspace{0.5cm}
+
+The first two models show the results for public expenditure per capita. No
+variable reaches conventional levels of statistical significance in the
+restricted sample. In the extended sample, we find that models that use lower
+chamber size as an independent variable have lower effects when compared to
+upper chamber size. This suggests that an additional member in the lower house
+has a smaller impact on public spending than a member in the upper house.
+Moreover, the results for the extended sample point out that recent studies
+find larger effects than older ones.
+
+The third and fourth columns use the natural logarithm of expenditure per
+capita as the dependent variable. Among the coefficients in the restricted
+sample, those in published studies are significantly smaller than those in
+working papers. Another two moderators are negatively associated with the
+outcome in our larger study pool. They both refer to estimation methods.
+Studies that employ panel/fixed effects or regression discontinuity designs
+(RDDs) have lower coefficients for log expenditure per capita if we take OLS as
+the reference category.
+
+Three variables are statistically significant in the third set of
+meta-regressions, which include public expenditure as a percentage of GDP as
+the dependent variable. Both in our restricted and in our extended samples,
+recent studies have smaller coefficients than older papers, which stands in
+contrast with our previous models. Moreover, institutional design also affects
+outcomes. Papers that use mixed samples of bicameral and unicameral systems
+report significantly lower coefficients than those that analyse bicameral
+legislatures exclusively. Non-majoritarian electoral systems are also
+associated with lower levels of public spending, which may be justified since
+the "law of $1/n$" was conceived for majoritarian voting. These latter results,
+however, do not replicate in the first set of estimations.
+
+The last two columns report meta-regressions that aggregate all selected
+studies. In the restricted sample of coefficients, unicameralism has a
+pro-$1/n$ effect. This strongly supports the theory's original formulation, as
+most unicameral occurrences are local governments, for which the "law" was
+originally conceived. This result holds for the extended sample as well. When
+we regress all `r dim(fulldat)[1]` coefficients, the effects of estimation
+methods become stronger once again. Panel/fixed-effects models and regression
+discontinuity designs both decrease the $1/n$ effect at the .1\% significance
+level. Instrumental variable models follow along these lines. Additionally,
+non-majoritarian voting constituencies appear once again as settings where the
+law of $1/n$ becomes weaker.
+
+The evidence seems to be sensitive to the methodological design. Our results
+suggest that the same study samples may produce different outcomes depending on
+the response variables scholars decide to analyse. The broadest aggregation
+level presented the most insightful results in dialogue with the literature.
+The additional legislator in non-majoritarian legislatures does not increase
+expenditure as much as she would if the system were majoritarian. We are also
+more likely to witness legislative expenditure growing along with the amount of
+representatives in unicameral legislatures rather than in bicameral systems.
+This indicates that while the law of $1/n$ is not generalisable, its predicted
+effects are stronger when the institutional features of a polity come closer to
+its original theoretical framework.
+
 # Discussion

### 2021-05-29 article/resubmission.Rmd
adds discussion

@@
 
-## Binomial Z-Tests
-\label{sub:binomial}
-
 The "law of $1/n$" states that more legislators increase government expenditure.
@@
 
+## Binomial Z-Tests
+\label{sub:binomial}
+
 ```{r, cache=TRUE, echo = FALSE}
@@
 
-1 paragrafo para collective action problems -- raciocionio no "industrial something of legislatures", que é um paper do weingast
-1 para cada problema que o umberto falou
-pargrafo final eh o de acumulo de conhecimento
-
-Temos de manter esse mdoelo porque tem muita variancia nos modelos.
-É inteligível nao ter nenhum resultado, justamente pq tem *muita* variância.
-Quando tinha mais graus de liberdade, dava mais resultado. À medida que fomos colocando mais, diminuiu efeito.
-
-Justificando os null results: 
-Erro do weingast: você acha que cria um novo distrito e que o numero de pessoas se mantem fixo. só que diminui a população!!
-o modelo do weingast funciona numa situação muito especifica, e mudando ela um tiquinho ja nao funciona mais.
-
-jeitos de avançar a literatura:
-ter uma ideia melhor de quais as assumptions você precisa pra funcionar o negocio.
-tem mil assumptions entre os 3 custos/beneficios
-os 3 componentes podem variar da forma que for. um deles é externalidade (no mercado das firmas que estão no outro lugar e que vão contratar).
-e ninguem que fala da lei discute as assumptions!!!
-As assumptions são dificeis de mensurar.
-
-Problemas de identificação (desenho). RDs funcionam melhor.
-Moreover replicação/acumulo na disciplina basicamente nao existe.
-Seria muito surpreendente encontrar resultados dado esse quadro geral, na verdade.
-
-existe um desconforto geral com a teoria mas ninguém toca nos mecanismos.
-
-outro veio teórico:
-os papers de RDD sao todos pra PR, mas o paper do weingast nao eh pra PR.
-Pra PR, eh preciso relaxar a hipotese do weingast: existem sustemas PR mas que a votação dos caras eh concentrada num territorio.
-é uma hipotese fraca do weingast para que ela funcione.
-mas a teoria nao foi feita pra isso.
-por ex. 70% dos vereadores em sp têm votacao concentrada por territorio.
-mas existe uma big assumption da qual ninguém fala.
-se a votacao eh dispersa (geograficamente), a lei do 1/n faz zero sentido.
-PR reforça esse mecanismo, que pode estar correlacionado de formas que a teoria nao prevê.
-
-os padroes desse tipo de paper nao eh o mesmo dos papers de experimento.
-o nosso paper eh uma meta analise muito mais dificil de fazer do que a da mia costa, em que tem todas as stats e todos os coeficientes reportados bonitinhos.
-
-tem uma seleção de qual modelo vai entrar: modelo mais completo. (maior n, efeito fixo - max possivel, maximo de controle, optimal/intermediate bandwidth do RD, etc).
-se tem mais de um modelo que comply com a regra, é o n maior.
-para ser comparavel: soh comparar modelos com as mesmas DV e indvar.
-na meta-regression, a gente coloca todas as indvars, e nao as depvars. porque soh nos interessa que direção o efeito vai, e nao o tamanho do efeito.
-
-a gente nao tem controle sobre o tamanho/scale da variação. a meta regression eh o melhor que a gente pdoe fazer pra limpar essa variação doida.
-forest plots: o que fazemos bem para tornar todas em comparaveis eh ter o good coefficient do modelo, e ter o desvio padrão.
-toda vez que fazemos esse tipo de meta analise, o pacote transforma o coeficiente em seu Hedges’ \(g\).
-
-pergunta pode ser: (A) como fazemos para botar no mesmo saco um RD e um panel? resp: isso eh um problea mesmo nas meta analises, mas na meta regressao isso limpa.
-(B) coeficientes sao all over the place. como vocês conseguiram comparar cada um?
-Daí explicar o procedimento. Na restricted sample, we cherry picked, mas no appendix rodamos a analise com tudo junto pra vc, revisor, ver.
-
-Discussion:
-1 - ok
-2 - ok, só corrigir
-3 - como nossos resultados "resolvem" as questões da teoria
-a linha que avalia o desenho institucional está certa dessa forma.
-sobre a galera que escreve sobre as dinâmicas internas de competição e coalisão, podemos inferir que essas dinâmicas influenciam muito mais do que legislature size.
-Juntar a lit review com nosso ultimo paragrafo falando sobre as recomendações de para onde deve avançar a literatura. "Apesar de ela ser extensa, vemos que ainda poderiam ser explorados A B C".
-4 - ultimo paragrafo vira o que é o terceiro.
-uma das sugestões é aumentar o numero de replicações, etc, de como a disciplina como um todo deve avançar, sobre como construimos conhecimento na disciplina.
-
-In this article, we assess the empirical validity of the "law of $1/n$". Based
+In this letter, we assess the empirical validity of the "law of $1/n$". Based
 on a sample of `r length(unique(dat$id))` publications on the topic, our
 meta-analyses show that there is no strong evidence that an increase in the
-number of legislators has a significant effect on public expenditures. If such
-effect exists, it is likely driven by an increase in the size of the upper
-legislature, as suggested by several studies in the literature
-[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
-@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
-better evidence for the "reverse law of $1/n$", which posits that larger
-legislatures lead to lower government spending. This is mainly because studies
-using regression discontinuity designs, a method that has robust internal
-validity, consistently indicate a negative relationship between lower house size
-and the logarithm of expenditure per capita [@hohmann2017effect;
-@lewis2019legislature; @petterssonlidbom2012size].
-
-The meta-regressions show that study characteristics have a considerable
+number of legislators has a significant effect on public expenditures. The meta-regressions show that study characteristics have a considerable
 influence on reported results. Electoral system affects the relationship
 between legislature size and public expenditure, but the results are not
-replicable in all estimations. Publication year generates conflicting findings
-in our models. Nevertheless, the meta-regressions confirm that RDDs produce
-negative effects more frequently than OLS regressions.
-
-The literature explores many mediating and alternative explanations for how or why the number of legislators in a chamber relates to their choice of commmon pool resource use.
-@crowley2019law argues that a variable that better translates how large legislatures decrease the efficiency of public spending is fragmentation, which also expresses the and that its effect is actually non-linear.
-Other studies echo this argument and develop other frgamentation mechanisms that explain relationships that are linear and non-linear.
-For instance, when it comes to district fragmentation, @baqir1999districts and @drew2017price support the "law of $1/n$"'s positive effect on public spending when one considers the amount of districts that share a common pool of resources.
-Many studies demonstrate how partisan fragmentation is a bigger predictor of increased spending, and analyze how majorities and veto powers respectively boost and curtail these effects [@baqir2002districting, cite all the papers].
-These findings dialogue directly with @weingast1981political's *norm of universalism* within US legislatures, which is the assumption that, when drawing from common pool resources, chambers will always approve of any singular legislators' projects.
-
-Applying the "law of $1/n$" in contexts too far removed from the US attests against it, as, for instance, public spending more strongly correlates to cabinet than legislature size in Swiss cantons and Malaysian (states or municipalities?), where decision-making power is concentrated in the executive.
-
-Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
-plausible reason may be that there are few incentives for the pure accumulation
+replicable in all estimations. In the broadest aggregation models, unicameralism favours the $1/n$ effect. Publication year generates conflicting findings
+in our models, but recent papers tend to present smaller coefficients than older ones.
+The meta-regressions confirm that more modern estimation methods such as RDDs and panel/fixed-effects models decrease effects more frequently than OLS regressions.
+
+While the vast literature covering the law of $1/n$ builds important empirical knowledge, few studies dedicate enough to the theory itself.
+Naturally, there are exceptions [@primo2008distributive].
+Among others, @crowley2019law and @pecorino2018supermajority expand the original model targeting the absence of transaction costs in the firm-like behaviour of legislatures [@weingast1988industrial].
+Yet, a few issues remain unadressed.
+Namely, the model assumes three types of costs for legislative public good provision: expenses for the constituency, expenses outside the constituency, and externalities.
+The main issue in testing this empirically is that externalities such as shifts in prices of local firms, for example, are extremely hard to measure.
+Thus, it is very difficult to properly translate the mechanism using empirical data, making it is easy to accidentally distort results.
+Therefore, it should not come as a surprise that slight differences in political features generate highly heterogeneous results.
+
+In this sense, the empirical cases in the literature are not always the most fortunate testing ground for the law of $1/n$.
+While we believe that moving beyond the majoritarian districts framework could produce valuable insight, institutional features that are central to the theory cannot be overrun.
+For instance, proportional representation (PR) electoral systems allow candidates whose constituents are spread across large territories to provide diffused public goods and win elections.
+However, geographically-targeted service provision is at the very core of the legislative behaviour that produces the law of $1/n$.
+Thus, testing this theory in PR systems may be ineffective and misleading.
+It is important to note that all of our studies employing RDDs analyse PR systems.
+This forces us to hypothesise the negative effects in RDDs may not be caused by the estimation method, but because we coincidentally gather a subsample where PR systems specially weaken the $1/n$ effect.\footnote{Given that the other more sophisticated causal inference methods point in the same direction as the RDDs, we do believe RDDs decrease effect sizes.
+However, the method's effect becomes hard to disentangle from that of proportional representation since the latter entirely encompasses the prior.}
+
+Another plausible reason why there is no clear-cut evidence in favour or against the "law of $1/n$" may be that there are few incentives for the pure accumulation
 of knowledge in the social sciences, at least when compared to the benefits
@@
 \url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.}
-
-For instance, in our sample, papers added supermajority rules
-[@lee2015supermajority; @lee2016supermajority], redistricting
-[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
-coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
-bicameralism [@ricciuti2004legislature], and the interplay between upper and
-lower houses [@chen2007law] to the main theory, but a comprehensive
-procedural replication of the findings using different samples is yet to be
-written.
-
-The addition of new features has the benefit of enriching the original
-theory with useful details, although it has the disadvantage of not providing a
-conclusive test to the "law of $1/n$".
+information.} We advocate that continuously producing and consuming meta-analyses is a covetable path towards knowledge-building for the social sciences.
+Although aggregating observational -- instead of experimental -- data can be especially challenging mathematically, we have shown it to be possible and effective.
 
@@
 sample did not include articles that evaluate the association between the
-log lower chamber size and public expenditure per capita or between upper chamber size and log expenditure
+natural logarithm of lower chamber size and public expenditure per capita, or between upper house size and log expenditure
 per capita. New work on that area might clarify some of the inconsistencies we
@@
 as party dynamics or gerrymandering [@lee2015supermajority;
-@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
-regard. Finally, we highlight the need for more causal inference studies in the
-literature. Whenever possible, authors should leverage natural and
-quasi-experiments to assess whether the current results hold when tested with
-such research designs. These suggestions may help scholars and policy-makers to
+@mukherjee2003politicalparties; @gilligan2006public] may prove useful in explaining particular dynamics.
+Third, authors should leverage natural and quasi-experiments to assess whether the current results hold when systematically tested.
+Fortunately, we acknowledge this may also be a trend under way, as all four studies using regression discontinuity designs in our sample were published within less than 10 years prior to this meta-analysis.
+These suggestions may help scholars and policy-makers to
 reach an optimal balance between sound fiscal policy and the demands for

### 2021-05-30 dataset/datasetBuilding.R
variable for unicameralism new

@@ -5635,6 +5635,12 @@ dat <- arrange(dat, id) %>%
   relocate(id_level2, .after = id_level1) %>%
   mutate(VAR = SE^2)
 
+# Inst Design 2
+dat <- dat %>%
+  mutate(instdesign2 = ifelse(instdesign == 'Unicameral',
+                              'Unicameral', 'Non-Unicameral')) %>%
+  relocate(instdesign2, .after = instdesign)
+
 # Full data and partial data
 fulldat <- dat
 dat <- dat %>%

### 2021-05-30 appendix/appendix.Rmd
unicameral x non-unicameral binomial tests

@@
 
-In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$.
+In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{For our purposes, concave means that $b'>0$ and $b''<0$.
 Convex means that $c'>0$ and $c''>0$.
@@
   unique() %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
+  mutate(indepvar2 = factor(indepvar2, 
+                            labels = c("K (upper house legislators)",
                                        "Log N",
@@
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published) %>%
+              year, published, instdesign2) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Year`                  = year,
-         `Published work`        = published)
+         `Published work`        = published,
+         `Institution design`    = instdesign2)
 
@@
 This is the only test that presents evidence of an association between the legislature size and expenditure.
+
+We also tested the possibility that the signs change heterogeneously, based on whether the paper studied unicameral versus non-unicameral legislative bodies.
+This analysis does not take into consideration the size of the upper house, as it would indicate that the cases in the paper had trivially a non-unicameral legislature.
+The results in the Table XXXX, show that there is no significant change controlling by this variable.
+
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
+aux <- list()
+aux[[1]] <- filter(dat, indepvar2 == "N", instdesign2 == 'Unicameral')
+aux[[2]] <- filter(dat, indepvar2 == "N", instdesign2 != 'Unicameral')
+aux[[3]] <- filter(dat, indepvar2 == "logN", instdesign2 == 'Unicameral')
+aux[[4]] <- filter(dat, indepvar2 == "logN", instdesign2 != 'Unicameral')
+aux[[1]] <- binom.test(table(aux[[1]]$scoef)[2],
+                       sum(table(aux[[1]]$scoef)), p = 0.5)
+aux[[2]] <- binom.test(table(aux[[2]]$scoef)[2],
+                       sum(table(aux[[2]]$scoef)), p = 0.5)
+aux[[3]] <- binom.test(table(aux[[3]]$scoef)[2],
+                       sum(table(aux[[3]]$scoef)), p = 0.5)
+aux[[4]] <- binom.test(table(aux[[4]]$scoef)[2],
+                       sum(table(aux[[4]]$scoef)), p = 0.5)
+aux2 <- tidy(aux[[1]])[,-c(2,4,5,6)][,c(3,4,1,2)]
+aux2 <- bind_rows(aux2, tidy(aux[[2]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- bind_rows(aux2, tidy(aux[[3]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- bind_rows(aux2, tidy(aux[[4]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- aux2 %>%
+  mutate(`Indep. Variable` = c('Lower House Size', 'Lower House Size', 'Log of Lower House Size', 'Log of Lower House Size'),
+         `Legislative Inst.` = c('Unicameral', 'Non-unicameral', 'Unicameral', 'Non-unicameral')) %>%
+  relocate(`Indep. Variable`, `Legislative Inst.`, .before = method)
+aux2$method <- NULL
+aux2$alternative <- NULL
+pander(aux2)
+```
 
@@
  - `Unicameral` (e.g., US Municipalities)
- - `Bicameral` (e.g., US States)
- - `Mixed` (e.g., countries with unicameral and bicameral in the same dataset).
+ - `Non-unicameral`: (e.g. `Bicameral` or `Mixed`).
 
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
               test = "knha",

### 2021-05-30 appendix/appendix.Rmd
unicameralism added to meta-regressions

@@
 
-2. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
+2. Papers whose samples included unicameral legislatures report slightly higher coefficients.
 
@@
 
-3. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
+3. Papers whose samples included unicameral legislatures report significantly higher coefficients.
 
@@
 
-6. The institutional design: whether the legislature in the analysis is unicameral, bicameral, or mixed.
+6. The institutional design: whether the legislature in the analysis is unicameral or non-unicameral (bicameral or mixed).
 
@@
               random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
               test = "knha",
@@
 ```
-In the restricted model, with only the main coefficients in the selected papers, only Unicameralism has a positive, significant effect.
+In the restricted model, with only the main coefficients in the selected papers, Unicameralism has a positive, significant effect.
+Also, papers using Regression Discontinuity Design tend to have a negative effect, significant at the 10% level.
 We also run the meta-regressions adding all coefficients in the papers.
@@
 
-1. Coefficients from non-majoritarian systems are significantly lower than those found in purely majoritarian systems.
-
-2. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
-
-3. Evidence from unicameral systems presents significantly larger effect sizes.
-
-4. All other moderators are insignificant.
+1. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
+
+2. Evidence from unicameral systems presents significantly larger effect sizes.
+
+3. All other moderators are insignificant.

### 2021-05-30 article/article.Rmd
fix paper list

@@
   unique() %>%
-  arrange(year)
+  arrange(year, depvar2)
+aux2 <- aux %>%
+  mutate(depvar2 = 'aux') %>%
+  unique()
+for(i in 1:dim(aux)[1]) {
+  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
+    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
+  } else {
+    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
+      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
+      aux$depvar2[i], sep = ', ')
+  }
+}
+aux <- aux2
 for (i in 1:dim(aux)[1]) {

### 2021-05-30 article/article.Rmd
add discussion

--- 2021-05-29 article/article.Rmd
@@
 In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending.
-Based on a sample of 29 articles, we find no robust evidence for the effect of legislature size on government budgets.
+Based on a sample of 30 articles, we find no robust evidence for the effect of legislature size on government budgets.
 Yet the aggregate results show significant heterogeneity.
@@
 queries. All papers we found in the last search had already been included in
-our sample. Combined, the three searches produced a dataset of 
-`r length(unique(dat$id))` studies as of the 10\textsuperscript{th} of March 2021.
-Table \ref{tab:papers} contains the full list of articles we analyse in this
-paper.
+our sample. The full list of excluded records is available for online
+consultation in the replication materials. Combined, the three searches
+produced a dataset of `r length(unique(dat$id))` studies as of the
+10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains the full
+list of articles we analyse in this paper.
 
@@
 capita, we find a standardised mean difference (SMD) of 0.022 and a standard
-error of 0.131 (studies = `r mod[[1]]$k`, 95\% CI = [-0.256; 0.299], $p$-value
-= 0.87), so we cannot rule that the effect is different from zero. Indeed, the
-effect of lower chamber size on the other two dependent variables is also null
-in statistical terms. When we compare lower chamber size with log expenditure
-per capita, the overall effect size is -0.031 and the standard error is 0.049
-(studies = `r mod[[3]]$k`, 95\% CI = [-0.188; 0.127], $p$-value = 0.58), and
-the impact of larger lower houses on government spending as a percentage of GDP
-is also negligible (studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI =
-[-0.0334; 0.021], $p$-value = 0.563). The results are virtually identical when
-we estimate the meta-analyses using our extended sample, and the all three
-coefficients are again statistically indistinguishable from zero.
+error of 0.131 (figure 1.1, studies = `r mod[[1]]$k`, 95\% CI = [-0.256;
+0.299], $p$-value = 0.87), so we cannot rule that the effect is different from
+zero. Indeed, the effect of lower chamber size on the other two dependent
+variables is also null in statistical terms. When we compare lower chamber size
+with log expenditure per capita, the overall effect size is -0.031 and the
+standard error is 0.049 (figure 1.2, studies = `r mod[[3]]$k`, 95\% CI =
+[-0.188; 0.127], $p$-value = 0.58), and the impact of larger lower houses on
+government spending as a percentage of GDP  is also negligible (figure 1.3,
+studies = `r mod[[5]]$k`, SMD = - 0.006, 95\% CI = [-0.0334; 0.021], $p$-value
+= 0.563). The results are virtually identical when we estimate the
+meta-analyses using our extended sample, and the all three coefficients are
+again statistically indistinguishable from zero.
 
@@
 per capita expenditure is positive, but the coefficient is not significant
-(studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI = [-0.225; 0.381],
-$p$-value = 0.515. The effect of log lower house size on expenditure as a
-percentage of the GDP is very similar, although the SMD is negative (studies =
-`r mod[[6]]$k`, SMD = `r round(mod[[6]]$TE.random,3)`, SE = 
-`r round(mod[[6]]$seTE.random,3)`, 95\% CI = [`r round(mod[[6]]$lower.random,3)`;
-`r round(mod[[6]]$upper.random,3)`], $p$-value = 
-`r round(mod[[6]]$pval.random,3)`). Results in the full sample are also null, and
-the coefficients for each dependent variable have the same sign as the
-restricted sample -- positive and negative, respectively.
+(figure 1.4, studies = `r mod[[4]]$k`, SMD = 0.078, SE = 0.109, 95\% CI =
+[-0.225; 0.381], $p$-value = 0.515). The effect of log lower house size on
+expenditure as a percentage of the GDP is negative, but it is again
+non-statistically significant (figure 1.5, studies = `r mod[[6]]$k`, SMD = 
+`r round(mod[[6]]$TE.random,3)`, SE = `r round(mod[[6]]$seTE.random,3)`, 95\% CI =
+[`r round(mod[[6]]$lower.random,3)`; `r round(mod[[6]]$upper.random,3)`],
+$p$-value = `r round(mod[[6]]$pval.random,3)`). Results in the full sample are
+also null, and the coefficients for each dependent variable have the same sign
+as the restricted sample -- positive and negative, respectively.
 
@@
 We find a positive correlation between this variable and expenditure per capita
-(studies = `r mod[[2]]$k`, SMD = 3.658, SE = 4.299, 95\% CI = [-6.255; 13.572],
-$p$-value = 0.419), and a negative relationship with government spending as a
-percentage of GDP (studies = `r mod[[7]]$k`, SMD = 
-`r round(mod[[7]]$TE.random,3)`, SE = `r round(mod[[7]]$seTE.random,3)`, 95\% CI =
-[`r round(mod[[7]]$lower.random,3)`; `r round(mod[[7]]$upper.random,3)`],
-$p$-value = `r round(mod[[7]]$pval.random,3)`), yet neither coefficient is
-statistically significant. Results are the same in our extended sample.
+(figure 1.6, studies = `r mod[[2]]$k`, SMD = 3.658, SE = 4.299, 95\% CI =
+[-6.255; 13.572], $p$-value = 0.419), and a negative relationship with
+government spending as a percentage of GDP (figure 1.7, studies = 
+`r mod[[7]]$k`, SMD = `r round(mod[[7]]$TE.random,3)`, SE = 
+`r round(mod[[7]]$seTE.random,3)`, 95\% CI = [`r round(mod[[7]]$lower.random,3)`;
+`r round(mod[[7]]$upper.random,3)`], $p$-value = 
+`r round(mod[[7]]$pval.random,3)`), yet neither coefficient is statistically
+significant. Results are the same in our extended sample.
 
@@
 
-In this letter, we assess the empirical validity of the "law of $1/n$". Based
-on a sample of `r length(unique(dat$id))` publications on the topic, our
-meta-analyses show that there is no strong evidence that an increase in the
-number of legislators has a significant effect on public expenditures. If such
-effect exists, it is likely driven by an increase in $k$, the size of the upper
-legislature, as suggested by several studies in the literature
-[@baqir2002districting; @bradbury2001legislative; @bradbury2003local;
-@chen2007law; @gilligan2001fiscal; @primo2006stop]. Instead, we find
-better evidence for the "reverse law of $1/n$", which posits that larger
-legislatures lead to lower government spending. This is mainly because studies
-using regression discontinuity designs, a method that has robust internal
-validity, consistently indicate a negative relationship between lower house size
-and the logarithm of expenditure per capita [@hohmann2017effect;
-@lewis2019legislature; @petterssonlidbom2012size].
-
-The meta-regressions show that study characteristics have a considerable
+In this letter, we use meta-analytic methods to assess the generality of the
+"law of $1/n$". Based on a sample of `r length(unique(dat$id))` publications,
+our meta-analyses show that there is no strong evidence that an increase in the
+number of legislators has a significant effect on public expenditures. The
+meta-regressions indicate that study characteristics have a considerable
 influence on reported results. Electoral system affects the relationship
 between legislature size and public expenditure, but the results are not
-replicable in all estimations. Publication year generates conflicting findings
-in our models. Nevertheless, the meta-regressions confirm that RDDs produce
-negative effects more frequently than OLS regressions.
-
-Why is there no clear-cut evidence in favour or against the "law of $1/n$"? A
-plausible reason may be that there are few incentives for the pure accumulation
-of knowledge in the social sciences, at least when compared to the benefits
-scholars may accrue when they challenge or add features to existing theories
-[@geddes2003paradigms]. This leads to a reduced number of replication studies in
-the field, although we have seen some positive changes in this respect, such as
-EGAP's _Metaketa Initiative_.\footnote{See
+replicable in all estimations. In our extended sample, we find that
+unicameralism favours the $1/n$ effect. Publication year generates conflicting
+findings in our models, but recent papers tend to present smaller coefficients
+than older ones. The meta-regressions confirm that modern estimation methods
+such as RDDs and panel/fixed-effects models decrease effects more frequently
+than OLS regressions. In a nutshell, we only find moderate support for the "law
+of $1/n$" in unicameral governments and in the upper house, mostly when authors
+used OLS estimators.
+
+While the vast literature covering the "law of $1/n$" builds important
+empirical knowledge, we hypothesise that some of the null findings that we
+present here are due to difficulties in testing important assumptions behind
+the theory itself. For instance, the theory assumes three types of costs for
+legislative public good provision, namely expenses for the constituency,
+expenses outside the constituency, and externalities. The main issue in
+assessing their actual impact is that externalities such as shifts in prices of
+local firms, for example, are extremely hard to measure. Thus, it is very
+difficult to properly translate the mechanism to empirical data, making it is
+easy to accidentally distort results. Therefore, it should not come as a
+surprise that slight differences in political features generate highly
+heterogeneous results.
+
+In this sense, the empirical cases in the literature may not always be the most
+fortunate testing ground for the "law of $1/n$". While we believe that moving
+beyond the majoritarian districts framework could produce valuable insights,
+institutional features that are central to the theory cannot be overrun. For
+example, proportional representation (PR) electoral systems allow candidates
+whose constituents are spread across large territories to provide diffused
+public goods and win elections. However, geographically-targeted service
+provision is at the very core of the legislative behaviour that produces the
+"law of $1/n$". Thus, scholars should consider the possible implications of
+these micro-level dynamics when applying the "law of $1/n$" logic to different
+settings.
+
+Another plausible reason why there is no clear-cut evidence in favour or
+against the "law of $1/n$" may be that there are few incentives for the pure
+accumulation of knowledge in the social sciences, at least when compared to the
+benefits scholars may accrue when they challenge or add features to existing
+theories [@geddes2003paradigms]. This leads to a reduced number of replication
+studies and research syntheses in the field, although we have seen some
+positive changes in this respect, such as EGAP's _Metaketa
+Initiative_.\footnote{See
 \url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.} For instance, in our sample, papers added supermajority rules
-[@lee2015supermajority; @lee2016supermajority], redistricting
-[@baqir2002districting; @lee2018court], party ideology [@bjedov2014impact],
-coalition sizes [@baskaran2013coalition], term limits [@erler2007termlimits],
-bicameralism [@ricciuti2004legislature], and the interplay between upper and
-lower houses [@chen2007law] to the main theory, but a comprehensive
-procedural replication of the findings using different samples is yet to be
-written. The addition of new features has the benefit of enriching the original
-theory with useful details, although it has the disadvantage of not providing a
-conclusive test to the "law of $1/n$".
-
-Our analyses suggest three areas for further research. First, our study
+information.} Here we show that continuously producing and consuming
+meta-analyses is a viable path towards knowledge-building in our discipline.
+Although aggregating observational -- instead of experimental -- data can be
+especially challenging, we believe that research synthesis methods play an
+essential role in advancing our understanding of complex political phenomena.
+
+Our analyses suggest other avenues for further research. First, our study
 sample did not include articles that evaluate the association between the
-log($n$) and public expenditure per capita or between $k$ and log expenditure
-per capita. New work on that area might clarify some of the inconsistencies we
-find here. Second, despite the inclusion of several moderators in our models,
-aggregate results still show considerable heterogeneity. Domestic factors such
-as party dynamics or gerrymandering [@lee2015supermajority;
-@mukherjee2003politicalparties; @gilligan2006public] may prove useful in this
-regard. Finally, we highlight the need for more causal inference studies in the
-literature. Whenever possible, authors should leverage natural and
-quasi-experiments to assess whether the current results hold when tested with
-such research designs. These suggestions may help scholars and policy-makers to
-reach an optimal balance between sound fiscal policy and the demands for
-increased political representation.
-
-\newpage
+natural logarithm of lower chamber size and public expenditure per capita, or
+between upper house size and log expenditure per capita. New work on that area
+might clarify some of the inconsistencies we find here. Second, despite the
+inclusion of several moderators in our models, aggregate results still show
+considerable heterogeneity. Domestic factors such as party dynamics or
+gerrymandering [@lee2015supermajority; @mukherjee2003politicalparties;
+@gilligan2006public] may prove useful in explaining those divergent results.
+Third, authors should leverage natural and quasi-experiments to assess whether
+the current results hold when systematically tested. Fortunately, this may also
+be a trend under way, as all four studies using regression discontinuity
+designs in our sample were published within less than 10 years prior to this
+meta-analysis. These suggestions may help scholars to validate the robustness
+of their findings and policy-makers to reach an optimal balance between sound
+fiscal policy and the demands for increased political representation.
+
 \setlength{\parindent}{0cm}

### 2021-05-30 article/article.Rmd
add tables, need fixing

--- 2021-05-30 article/article.Rmd
@@
 
-[^huzeyfe]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
+[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
 
@@
 aux <- dat %>%
-  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
+  select(authoryear, journalCode, locationISO, depvar2, method, instdesign2, elecsys3, year) %>%
   unique() %>%
-  arrange(year)
+  arrange(year, depvar2)
+aux2 <- aux %>%
+  mutate(depvar2 = 'aux') %>%
+  unique()
+for(i in 1:dim(aux)[1]) {
+  if(aux2$depvar2[aux2$authoryear == aux$authoryear[i]] == 'aux') {
+    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = aux$depvar2[i]
+  } else {
+    aux2$depvar2[aux2$authoryear == aux$authoryear[i]] = paste(
+      aux2$depvar2[aux2$authoryear == aux$authoryear[i]],
+      aux$depvar2[i], sep = ', ')
+  }
+}
+aux <- aux2
 for (i in 1:dim(aux)[1]) {
@@
       aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
-      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
+      aux$method[i], ' & ', aux$instdesign2[i], ' & ', 
       aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Journal:} Unpub$=$Unpublished, JPE$=$Journal of Political
-Economy, EJPE$=$European Journal of Political Economy, PC$=$Public Choice,
-JPubE$=$Journal of Public Economics, JPriE$=$Journal of Private Enterprise,
-APSR$=$American Political Science Review, SEJ$=$Southern Economic Journal,
-UAR$=$Urban Affairs Review, SCID$=$Studies in Comparative International
-Development, SSQ$=$Social Science Quarterly, SPPQ$=$State Politics and Policy
-Quarterly, CPS$=$Comparative Political Studies, RivPE$=$Rivista di Politica
-Economica, E\&P$=$Economics and Politics, NTJ$=$National Tax Journal.}
+\footnotetext{\textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
+Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
+JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
+APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
+UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
+Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
+Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
+Economica, E\&P $=$ Economics and Politics, NTJ$=$National Tax Journal.}
 \footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
 international standard.} 
-\footnotetext{\textbf{Dependent Variable:} ExpPC$=$Per capita expenditure,
-logExpPC$=$Natural logarithm of per capita expenditure, PCTGDP$=$Expenditure as
+\footnotetext{\textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
+logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
 a percentage of GDP.}
-\footnotetext{\textbf{Method:} OLS$=$Ordinary least squares, IV$=$Instrumental
-variables, Panel$=$Panel data/fixed effects, RDD$=$Regression discontinuity
+\footnotetext{\textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
+variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
 design.}
-\footnotetext{\textbf{Electoral System:} M$=$Majoritarian, NM$=$Non-majoritarian (mixed or proportional
+\footnotetext{\textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
 representation).} 
@@
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published, instdesign) %>%
+              year, published, instdesign2) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Estimation method`     = method,
-         `Institutional Design`  = instdesign,
+         `Institutional Design`  = instdesign2,
          `Electoral system`      = elecsys2)
@@
 
+```{r, echo = FALSE, warning = FALSE, message = FALSE, results = 'hide', cache = TRUE}
+res <- list()
+
+# Aux fctns
+strep <- function (x) {
+  if(!is.na(x)) {
+    return(ifelse(x<0.01, '***',ifelse(x<0.05,'**', ifelse(x<0.1,'*',''))))
+  } else {
+    return('')
+  }
+}
+
+extract_coefs <- function(mod, modnam) {
+  dfr <- data.frame(
+     nams2 = row.names(mod[["beta"]]),
+     est = mod[["beta"]],
+     se = mod[["se"]],
+     pval = mod[["pval"]],
+     model = modnam
+  )
+  aux <- data.frame(nams = c("Intercept",
+             "Indepvar: logN",
+             "Indepvar: N",
+             "Year",
+             "Elecsys: Non-Majoritarian",
+             "Published",
+             "Method: Panel",
+             "Method: IV",
+             "Method: RDD",
+             "Legislature: Unicameral"), 
+             nams2 = c("intrcpt", 
+                       "indepvar2logN", 
+                       "indepvar2N", 
+                       "year", 
+                       "publishedYes", 
+                       "elecsys2Non-Maj", 
+                       "methodPANEL", 
+                       "methodIV", 
+                       "methodRDD",
+                       "instdesign2Unicameral"))
+  dfr <- left_join(aux, dfr) %>%
+    mutate_if(is.numeric, list(~round(., digits = 4)))
+  dfr$nams2 <- NULL
+  return(dfr)
+}
+
+# Expenditure per capita - Restricted
+mod <-  rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+            subset = dat$depvar2=='ExpPC',
+            slab = dat$authoryear,
+            control=list(maxiter=1000))
+
+res[[1]] <- extract_coefs(mod, "ExpPC")
+
+# Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+            subset = fulldat$depvar2=='ExpPC',
+            slab = fulldat$authoryear)
+
+res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
+
+# Log of Expenditure per capita - Restricted
+mod <- rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+            subset = dat$depvar2=='logExpPC',
+            slab = dat$authoryear)
+
+res[[3]] <- extract_coefs(mod, "logExpPC")
+
+# Log of Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+            subset = fulldat$depvar2=='logExpPC',
+            slab = fulldat$authoryear)
+
+res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
+
+## Expenditure as percentage GDP -- Restricted
+mod <-  rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+              sparse = TRUE,
+              tdist = TRUE,
+              subset = dat$depvar2=='PCTGDP',
+              slab = dat$authoryear)
+
+res[[5]] <- extract_coefs(mod, "PCTGDP")
+
+## Expenditure as percentage GDP -- Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+            subset = fulldat$depvar2=='PCTGDP',
+            slab = fulldat$authoryear)
+
+res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")
+
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              slab = dat$authoryear)
+
+res[[7]] <- extract_coefs(mod, "Full Model")
+
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              slab = fulldat$authoryear)
+
+res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
+gcf <- function(mod, pos) {
+  x <- mod$est[pos]
+  y <- mod$pval[pos]
+  if(!is.na(x)) {
+    return(paste0(round(x, digits = 3), strep(y)))
+  } else {
+    return('')
+  }
+}
+gcf2 <- function(mod, pos) {
+  # round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])`
+  x <- mod$se[pos]
+  if(!is.na(x)) {
+    return(paste0('(', round(x, digits = 3), ')'))
+  } else {
+    return('')
+  }
+}
+```
+
 \vspace{0.5cm}
-[TABLE GOES HERE]
+
+```{=latex}
+\begin{table}[htpb]
+\caption{Meta Regression Results\label{tabregressions}}
+\footnotesize
+\centering
+\begin{tabular}{lcccccccc}
+\toprule
+\midrule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{Full Model} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
+& Restricted & Extended & Restricted & Extended & Restricted & Extended & Restricted & Extended \\
+\midrule
+Independent Variable: log($N$) & 
+`r gcf(res[[1]], 2)` & `r gcf(res[[2]], 2)` & 
+`r gcf(res[[3]], 2)` & `r gcf(res[[4]], 2)` & 
+`r gcf(res[[5]], 2)` & `r gcf(res[[6]], 2)` &
+`r gcf(res[[7]], 2)` & `r gcf(res[[8]], 2)` \\
+& `r gcf2(res[[1]], 2)` & `r gcf2(res[[2]], 2)` & 
+`r gcf2(res[[3]], 2)` & `r gcf2(res[[4]], 2)` & 
+`r gcf2(res[[5]], 2)` & `r gcf2(res[[6]], 2)` & 
+`r gcf2(res[[7]], 2)` & `r gcf2(res[[8]], 2)` \\
+%
+Independent Variable: $N$ &
+`r gcf(res[[1]], 3)` & `r gcf(res[[2]], 3)` & 
+`r gcf(res[[3]], 3)` & `r gcf(res[[4]], 3)` & 
+`r gcf(res[[5]], 3)` & `r gcf(res[[6]], 3)` &
+`r gcf(res[[7]], 3)` & `r gcf(res[[8]], 3)` \\
+& `r gcf2(res[[1]], 3)` & `r gcf2(res[[2]], 3)` & 
+`r gcf2(res[[3]], 3)` & `r gcf2(res[[4]], 3)` & 
+`r gcf2(res[[5]], 3)` & `r gcf2(res[[6]], 3)` & 
+`r gcf2(res[[7]], 3)` & `r gcf2(res[[8]], 3)` \\
+%
+Year & 
+`r gcf(res[[1]], 4)` & `r gcf(res[[2]], 4)` & 
+`r gcf(res[[3]], 4)` & `r gcf(res[[4]], 4)` & 
+`r gcf(res[[5]], 4)` & `r gcf(res[[6]], 4)` &
+`r gcf(res[[7]], 4)` & `r gcf(res[[8]], 4)` \\
+& `r gcf2(res[[1]], 4)` & `r gcf2(res[[2]], 4)` & 
+`r gcf2(res[[3]], 4)` & `r gcf2(res[[4]], 4)` & 
+`r gcf2(res[[5]], 4)` & `r gcf2(res[[6]], 4)` & 
+`r gcf2(res[[7]], 4)` & `r gcf2(res[[8]], 4)` \\
+%
+Non-Majoritarian (PR \& Mixed) & 
+`r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
+`r gcf(res[[3]], 5)` & `r gcf(res[[4]], 5)` & 
+`r gcf(res[[5]], 5)` & `r gcf(res[[6]], 5)` &
+`r gcf(res[[7]], 5)` & `r gcf(res[[8]], 5)` \\
+& `r gcf2(res[[1]], 5)` & `r gcf2(res[[2]], 5)` & 
+`r gcf2(res[[3]], 5)` & `r gcf2(res[[4]], 5)` & 
+`r gcf2(res[[5]], 5)` & `r gcf2(res[[6]], 5)` & 
+`r gcf2(res[[7]], 5)` & `r gcf2(res[[8]], 5)` \\
+%
+Published: Yes & 
+`r gcf(res[[1]], 6)` & `r gcf(res[[2]], 6)` & 
+`r gcf(res[[3]], 6)` & `r gcf(res[[4]], 6)` & 
+`r gcf(res[[5]], 6)` & `r gcf(res[[6]], 6)` &
+`r gcf(res[[7]], 6)` & `r gcf(res[[8]], 6)` \\
+& `r gcf2(res[[1]], 6)` & `r gcf2(res[[2]], 6)` & 
+`r gcf2(res[[3]], 6)` & `r gcf2(res[[4]], 6)` & 
+`r gcf2(res[[5]], 6)` & `r gcf2(res[[6]], 6)` & 
+`r gcf2(res[[7]], 6)` & `r gcf2(res[[8]], 6)` \\
+%
+Method: Panel & 
+`r gcf(res[[1]], 7)` & `r gcf(res[[2]], 7)` & 
+`r gcf(res[[3]], 7)` & `r gcf(res[[4]], 7)` & 
+`r gcf(res[[5]], 7)` & `r gcf(res[[6]], 7)` &
+`r gcf(res[[7]], 7)` & `r gcf(res[[8]], 7)` \\
+& `r gcf2(res[[1]], 7)` & `r gcf2(res[[2]], 7)` & 
+`r gcf2(res[[3]], 7)` & `r gcf2(res[[4]], 7)` & 
+`r gcf2(res[[5]], 7)` & `r gcf2(res[[6]], 7)` & 
+`r gcf2(res[[7]], 7)` & `r gcf2(res[[8]], 7)` \\
+%
+Method: IV & 
+`r gcf(res[[1]], 8)` & `r gcf(res[[2]], 8)` & 
+`r gcf(res[[3]], 8)` & `r gcf(res[[4]], 8)` & 
+`r gcf(res[[5]], 8)` & `r gcf(res[[6]], 8)` &
+`r gcf(res[[7]], 8)` & `r gcf(res[[8]], 8)` \\
+& `r gcf2(res[[1]], 8)` & `r gcf2(res[[2]], 8)` & 
+`r gcf2(res[[3]], 8)` & `r gcf2(res[[4]], 8)` & 
+`r gcf2(res[[5]], 8)` & `r gcf2(res[[6]], 8)` & 
+`r gcf2(res[[7]], 8)` & `r gcf2(res[[8]], 8)` \\
+%
+Method: RDD &
+`r gcf(res[[1]], 9)` & `r gcf(res[[2]], 9)` & 
+`r gcf(res[[3]], 9)` & `r gcf(res[[4]], 9)` & 
+`r gcf(res[[5]], 9)` & `r gcf(res[[6]], 9)` &
+`r gcf(res[[7]], 9)` & `r gcf(res[[8]], 9)` \\
+& `r gcf2(res[[1]], 9)` & `r gcf2(res[[2]], 9)` & 
+`r gcf2(res[[3]], 9)` & `r gcf2(res[[4]], 9)` & 
+`r gcf2(res[[5]], 9)` & `r gcf2(res[[6]], 9)` & 
+`r gcf2(res[[7]], 9)` & `r gcf2(res[[8]], 9)` \\
+% 
+Inst.: Unicameral & 
+`r gcf(res[[1]], 10)` & `r gcf(res[[2]], 10)` & 
+`r gcf(res[[3]], 10)` & `r gcf(res[[4]], 10)` & 
+`r gcf(res[[5]], 10)` & `r gcf(res[[6]], 10)` &
+`r gcf(res[[7]], 10)` & `r gcf(res[[8]], 10)` \\
+& `r gcf2(res[[1]], 10)` & `r gcf2(res[[2]], 10)` & 
+`r gcf2(res[[3]], 10)` & `r gcf2(res[[4]], 10)` & 
+`r gcf2(res[[5]], 10)` & `r gcf2(res[[6]], 10)` & 
+`r gcf2(res[[7]], 10)` & `r gcf2(res[[8]], 10)` \\
+% 
+Intercept & 
+`r gcf(res[[1]], 1)` & `r gcf(res[[2]], 1)` & 
+`r gcf(res[[3]], 1)` & `r gcf(res[[4]], 1)` & 
+`r gcf(res[[5]], 1)` & `r gcf(res[[6]], 1)` &
+`r gcf(res[[7]], 1)` & `r gcf(res[[8]], 1)` \\
+& `r gcf2(res[[1]], 1)` & `r gcf2(res[[2]], 1)` & 
+`r gcf2(res[[3]], 1)` & `r gcf2(res[[4]], 1)` & 
+`r gcf2(res[[5]], 1)` & `r gcf2(res[[6]], 1)` & 
+`r gcf2(res[[7]], 1)` & `r gcf2(res[[8]], 1)` \\
+\bottomrule
+\end{tabular}
+\begin{minipage}{\textwidth}
+\renewcommand{\footnoterule}{}
+\footnotetext{\textbf{Note:} {The restricted and extended samples include `r length(dat$id)` and `r length(fulldat$id)` study coefficients, respectively.
+We report the results from the permutation tests.
+Reference categories: Independent Variable: Upper House Size; Published $= No$; Non-Majoritarian; Method $= OLS$, Legislative: $= Non-Unicameral$.
+Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
+\end{minipage}
+\end{table}
+```
+
 \vspace{0.5cm}

### 2021-05-31 article/article.Rmd
small changes in article

@@
 spending. Moreover, the literature has increasingly applied causal inference
-designs to estimate the effect of the "law of $1/n$", and in contrast to
+methods to estimate the effect of the "law of $1/n$", and in contrast to
 previous studies using panel data, regression discontinuity designs generally
 indicate that more legislators decrease public expenditures
-[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature]. In this
-respect, scholars have long been aware of the theoretical and empirical
-limitations of the "law of $1/n$", and the proliferation of new studies reflect
-a conscious attempt to assess the robustness of the theory [@crowley2019law].
+[@debenedetto2018effect; @hohmann2017effect; @lewis2019legislature;
+@petterssonlidbom2012size]. In this respect, scholars have long been aware of
+the theoretical and empirical limitations of the "law of $1/n$", and the
+proliferation of new studies reflect a conscious attempt to assess the
+robustness of the theory.
 
@@
 We run binomial tests and meta-regressions to further evaluate the relationship
-between legislature size and government expenditures. We use binomial tests
-to assess whether the proportions of positive and negative coefficients in our
+between legislature size and government expenditures. We use binomial tests to
+assess whether the proportions of positive and negative coefficients in our
 sample are statistically different from each other. In the meta-regressions, we
 measure the effect of five moderators that capture different sources of
-heterogeneity in the literature. As our sample includes both published and
-unpublished articles, we also construct a series of funnel plots to test for
-publication bias in existing research on the "law of $1/n$"
+heterogeneity in the literature. We also construct a series of funnel plots to
+test for publication bias in existing research on the "law of $1/n$"
 [@easterbrook1991publication; @gerber2001testing].
@@
 conflicting findings reported by the literature. However, when we look only at
-articles that employ regression discontinuity designs, we see that all three
-papers included in our sample suggest that a higher number of legislators leads
-to lower public spending [@debenedetto2018effect; @hohmann2017effect;
-@lewis2019legislature]. In this regard, it is possible that methodological
-choices partially explain the divergent results observed in the literature, as
-studies that use causal inference methods consistently point to the same
-direction. One limitation of this finding is that these studies only test the
-impact of lower house size on the natural logarithm of expenditure per capita,
-thus it remains unclear whether the results hold with other variables.
+articles that employ regression discontinuity designs (RDDs), we see that all
+four papers included in our sample suggest that a higher number of legislators
+leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
+@lewis2019legislature; @petterssonlidbom2012size]. In this regard, it is
+possible that methodological choices partially explain the divergent results
+observed in the literature, as articles that use RDDs consistently point to the
+same direction. One limitation of this finding is that these studies only test
+the impact of lower house size on the natural logarithm of expenditure per
+capita, thus it remains unclear whether the results hold with other variables.
 
@@
 highly heterogeneous and that effect sizes differ substantially according to
-study specifications. When using our extended sample of `r dim(fulldat)[1]`
+study specifications. When using an extended sample of `r dim(fulldat)[1]`
 coefficients, we find that unicameralism is associated with higher public
 spending, as predicted by the "law of $1/n$". Since most unicameral
-legislatures are located in local governments (municipalities or districts),
-this result supports the theory strictly in its first formulation. Moreover,
+legislatures in our sample are local governments (municipalities or districts),
+this result supports the predictions of @weingast1981political. Moreover,
 our meta-regressions indicate that larger upper chambers spend more in terms of
@@
 weaker as the empirical cases distance from the original definition of the law.
-Finally, meta-regression results confirm that regression discontinuity models
+Finally, meta-regression results confirm that regression discontinuity designs
 reduce public spending estimates.
-
-In summary, our results are in line with previous findings that lend partial
-support to the law of $1/n$ [@chen2007law; @crowley2015local; @primo2006stop].
-An assessment of the effects of collective action costs in these analyses is
-crucial to determine the full mechanism operating behind these results.
-Overall, our analysis does not provide robust support for the theory as
-originally conceived.
 
@@
 gathered data from three large academic databases (Scopus, Microsoft Academic,
-and Google Scholar) and looked for studies that were published in English and
+and Google Scholar) and looked for studies that were written in English and
 cited \citet{weingast1981political}, as it is the foundational work in the
@@
 (i) lower chamber size; (ii) natural logarithm of lower chamber size; and (iii)
-upper house size\footnote{There are a few important nuances concerning coding
+upper chamber size\footnote{There are a few important nuances concerning coding
 of these variables. Unicameralism, for example, is captured both by lower
@@
 working paper or unpublished manuscript that we had missed in the two former
-queries. All papers we found in the last search had already been included in
-our sample. The full list of excluded records is available for online
+queries. We did not find any new article that satisfied the inclusion criteria
+in this search. The full list of excluded records is available for online
 consultation in the replication materials. Combined, the three searches
@@
 
-\footnotesize
+\newpage
+
+\scriptsize
 \begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
@@
 aux <- dat %>%
-  select(authoryear, journalCode, locationISO, depvar2, method, instdesign2, elecsys3, year) %>%
+  select(authoryear, journalCode, locationISO, depvar2, method, instdesign, elecsys3, year) %>%
   unique() %>%
@@
       aux$locationISO[i], ' & ', aux$depvar2[i], ' & ', 
-      aux$method[i], ' & ', aux$instdesign2[i], ' & ', 
+      aux$method[i], ' & ', aux$instdesign[i], ' & ', 
       aux$elecsys3[i], ' \\\\ [0.5ex]', sep = ''), '\n')
@@
 \vspace{-0.5cm}
-\footnotetext{\textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
+\scriptsize
+\footnotetext{\scriptsize \textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
 Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
@@
 Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
-Economica, E\&P $=$ Economics and Politics, NTJ$=$National Tax Journal.}
-\footnotetext{\textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
+Economica, E\&P $=$ Economics and Politics, NTJ $=$ National Tax Journal.}
+\footnotetext{\scriptsize \textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
 international standard.} 
-\footnotetext{\textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
+\footnotetext{\scriptsize \textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
 logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
 a percentage of GDP.}
-\footnotetext{\textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
+\footnotetext{\scriptsize \textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
 variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
 design.}
-\footnotetext{\textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
+\footnotetext{\scriptsize \textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
 representation).} 
@@
 results, while studies from 2012 onward have also applied causal inference
-designs such as instrumental variables and regression discontinuity models to
+models such as instrumental variables and regression discontinuity designs to
 test the relationship between house size and public spending.
@@
 logarithm of lower chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='logN')])`), and upper chamber size (`r as.numeric(table(dat$indepvar2)[which(names(table(dat$indepvar2))=='K')])`).
-These six variables formed a $3 \times 3$ table, yet not all combinations were
+These variables formed a $3 \times 3$ table, yet not all combinations were
 available in the data. We found no studies that correlate public expenditure
@@
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published, instdesign2) %>%
+              year, published, instdesign) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Estimation method`     = method,
-         `Institutional Design`  = instdesign2,
+         `Institutional Design`  = instdesign,
          `Electoral system`      = elecsys2)
+aux$`Independent Variables` <- recode(aux$`Independent Variables`,
+                                      `N` = "Lower Chamber Size",
+                                      `K` = "Upper Chamber Size",
+                                      `logN` = "Log of Lower Chamber Size")
+aux$`Electoral system` <- recode(aux$`Electoral system`,
+                                 `Non-Maj` = "Non-Majoritarian",
+                                 `Maj` = "Majoritarian")
+aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)
 
@@
 [@cheung2014modeling; @cheung2019guide; @veroniki2016methods]. In our study
-sample, authors frequently use similar datasets in their models,
-and almost all papers fit more than one regression with similar variables, what
-suggests that the assumption above does not hold. We use two procedures to tackle this
-problem. First, we created two sets of study coefficients to reduce the impact
-of multicollinearity in our estimations. The first group includes only the most
+sample, authors frequently use the same datasets, and almost all papers fit more
+than one regression with similar variables, what suggests that the assumption
+above does not hold. We use two procedures to tackle this problem. First, we
+created two sets of study coefficients to reduce the impact of
+multicollinearity in our estimations. The first group includes only the most
 rigorous models from each paper, that is, those estimated with the largest $n$,
@@
 from the optimal bandwidth or from the intermediate one. This sample
-encompasses `r dim(dat)[1]` estimates, as `r as.numeric(sum(table(table(dat$id))[-1]))`
-articles analysed two dependent or independent variables of
-interest\footnote{The papers that used more than one dependent or independent
-variable of interest are \citet{baqir1999districts, bjedov2014impact,
-bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
-gilligan2001fiscal, lee2016supermajority, lee2018court,
+encompasses `r dim(dat)[1]` estimates, as 
+`r as.numeric(sum(table(table(dat$id))[-1]))` articles analysed two dependent or
+independent variables of interest\footnote{The papers that used more than one
+dependent or independent variable of interest are \citet{baqir1999districts,
+bjedov2014impact, bradbury2001legislative, chen2007law, crowley2019law,
+erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court,
 maldonado2013legislatures, primo2006stop, ricciuti2003trading,
@@
 papers. Here we focus on the results for our restricted sample as we consider
-them more robust, but the findings are very similar when we use the extended
+them more robust, but the findings are nearly identical when we use the extended
 set.
@@
 validity of that relationship. First, we run binomial z-tests to assess the
-frequency of positive and negative coefficients in our sample. Then, we fit 9
-multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
+frequency of positive and negative coefficients in our sample. Then, we fit
+nine multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
 `dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
-Lastly, we run two sets of meta-regressions to measure the effects of a group
+Lastly, we run four sets of meta-regressions to measure the effects of a group
 of moderators on the effect sizes of our study sample. To recapitulate, our
@@
 number of legislators leads to higher public expending, we should expect most
-coefficients to be positive. Conversely, if the "reverse law of $1/n" is true,
+coefficients to be positive. Conversely, if the "reverse law of $1/n$" is true,
 our results should indicate that $p < 0.5$, that is, the proportion of positive
@@
 our measures of government spending and created a theoretical $3 \times 3$
-matrix. Out of the 9 possible variable combinations, we found only 7 in the
-article pool. Our sample does not contain any papers that analyse the
-relationships between the log lower chamber size and public expenditure per
-capita, or between upper chamber size and the logarithm of public expenditure
-per capita. We calculated the effect sizes by drawing the coefficients and
-standard errors from the articles and computing Hedges' $g$, which is a widely
-used measure of standardised difference between means. When standard errors
-were not directly available in the texts, we used t-statistics to retrieve
-them.
+matrix. Out of the nine variable combinations, we found only seven the article
+pool. Our sample does not contain any papers that analyse the relationships
+between log lower chamber size and public expenditure per capita, or between
+upper chamber size and the logarithm of public expenditure per capita.
 
@@
 
-\begin{landscape}
-\begin{figure}[!ht]
-\centering
-\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
-\vspace{0.3cm}
-\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
-\label{fig:plots}
-\end{figure}
-\end{landscape}
-
 The uppermost row shows the results for lower chamber size in our restricted
@@
 error of 0.131 (figure 1.1, studies = `r mod[[1]]$k`, 95\% CI = [-0.256;
-0.299], $p$-value = 0.87), so we cannot rule that the effect is different from
+0.299], $p$-value = 0.87), so we cannot rule out that the effect is 
 zero. Indeed, the effect of lower chamber size on the other two dependent
@@
 standard error is 0.049 (figure 1.2, studies = `r mod[[3]]$k`, 95\% CI =
-[-0.188; 0.127], $p$-value = 0.58), and the impact of larger lower houses on
+[-0.188; 0.127], $p$-value = 0.58). The impact of larger lower houses on
 government spending as a percentage of GDP  is also negligible (figure 1.3,
@@
 = 0.563). The results are virtually identical when we estimate the
-meta-analyses using our extended sample, and the all three coefficients are
+meta-analyses using our extended sample, and all three coefficients are
 again statistically indistinguishable from zero.
@@
 
+\begin{landscape}
+\begin{figure}[!ht]
+\centering
+\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
+\vspace{0.3cm}
+\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
+\label{fig:plots}
+\end{figure}
+\end{landscape}
+
 The third set of models uses upper house size as the main independent variable.
@@
 that use regression discontinuity designs show negative and statistically
-significant results. Since only three papers in our sample use RDDs, we are
-cautious about predicting an overall negative relationship, but they do
-indicate that better identification strategies yield a zero-to-negative impact
-of legislature size on expenditure, in support of the "reverse law of $1/n$".
+significant results. Since only three papers in this model use
+RDDs[^pettersson], we are cautious about predicting an overall negative
+relationship, but they do indicate that better identification strategies yield
+a zero-to-negative impact of legislature size on expenditure, in support of the
+"reverse law of $1/n$".
+
+[^pettersson]: @petterssonlidbom2012size also uses RDDs but the study is not
+included in this model as it employs log lower chamber size as the independent
+variable.
 
@@
 
-Table {tab:regressions} presents the meta-regression results for our restricted
+Table \ref{tab:regressions} presents the meta-regression results for our restricted
 and extended samples. Each column represents one of the three measures of
@@
 \begin{table}[htpb]
-\caption{Meta Regression Results\label{tabregressions}}
-\footnotesize
+\caption{Meta-regression results\label{tab:regressions}}
+\scriptsize
 \centering
@@
 \midrule
-\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{Full Model} \\
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{All Coefficients} \\
 \cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
@@
 \midrule
-Independent Variable: log($N$) & 
+Log of Lower Chamber Size & 
 `r gcf(res[[1]], 2)` & `r gcf(res[[2]], 2)` & 
@@
 %
-Independent Variable: $N$ &
+Lower Chamber Size &
 `r gcf(res[[1]], 3)` & `r gcf(res[[2]], 3)` & 
@@
 %
-Non-Majoritarian (PR \& Mixed) & 
+Non-Majoritarian & 
 `r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
@@
 % 
-Inst.: Unicameral & 
+Inst. Design: Mixed & 
 `r gcf(res[[1]], 10)` & `r gcf(res[[2]], 10)` & 
@@
 `r gcf2(res[[7]], 10)` & `r gcf2(res[[8]], 10)` \\
+% 
+Inst. Design: Unicameral & 
+`r gcf(res[[1]], 11)` & `r gcf(res[[2]], 11)` & 
+`r gcf(res[[3]], 11)` & `r gcf(res[[4]], 11)` & 
+`r gcf(res[[5]], 11)` & `r gcf(res[[6]], 11)` &
+`r gcf(res[[7]], 11)` & `r gcf(res[[8]], 11)` \\
+& `r gcf2(res[[1]], 11)` & `r gcf2(res[[2]], 11)` & 
+`r gcf2(res[[3]], 11)` & `r gcf2(res[[4]], 11)` & 
+`r gcf2(res[[5]], 11)` & `r gcf2(res[[6]], 11)` & 
+`r gcf2(res[[7]], 11)` & `r gcf2(res[[8]], 11)` \\
 % 
@@
 We report the results from the permutation tests.
-Reference categories: Independent Variable: Upper House Size; Published $= No$; Non-Majoritarian; Method $= OLS$, Legislative: $= Non-Unicameral$.
-Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.}}
+Reference categories: Independent Variable $=$ Upper House Size; Published $=$ No; Method $=$ OLS, Inst.
+Design $=$ Bicameral.
+Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.
+Blank cells mean that there is no sufficient data to estimate the paramater.}}
 \end{minipage}
@@
 ```
-
 \vspace{0.5cm}
@@
 sample, those in published studies are significantly smaller than those in
-working papers. Another two moderators are negatively associated with the
-outcome in our larger study pool. They both refer to estimation methods.
+working papers\footnote{We find no evidence of publication bias in our models.
+The funnel plots for all estimations are available Sections H and I of the
+Supplementary Material.}. Another two moderators are negatively associated with
+the outcome in our larger study pool. They both refer to estimation methods.
 Studies that employ panel/fixed effects or regression discontinuity designs
@@
 recent studies have smaller coefficients than older papers, which stands in
-contrast with our previous models. Moreover, institutional design also affects
+contrast with the first model. Moreover, institutional design also affects
 outcomes. Papers that use mixed samples of bicameral and unicameral systems
@@
 The last two columns report meta-regressions that aggregate all selected
-studies. In the restricted sample of coefficients, unicameralism has a
-pro-$1/n$ effect. This strongly supports the theory's original formulation, as
-most unicameral occurrences are local governments, for which the "law" was
-originally conceived. This result holds for the extended sample as well. When
-we regress all `r dim(fulldat)[1]` coefficients, the effects of estimation
-methods become stronger once again. Panel/fixed-effects models and regression
-discontinuity designs both decrease the $1/n$ effect at the .1\% significance
-level. Instrumental variable models follow along these lines. Additionally,
-non-majoritarian voting constituencies appear once again as settings where the
-law of $1/n$ becomes weaker.
+studies. In the restricted sample of coefficients, unicameralism has a positive
+effect. This result holds for the extended sample as well. When we regress all
+`r dim(fulldat)[1]` coefficients, the effects of estimation methods become
+stronger once again. Panel/fixed-effects models and regression discontinuity
+designs both significantly decrease the $1/n$ effect. Instrumental variable
+models follow along these lines. Additionally, non-majoritarian voting
+constituencies appear once again as settings where the "law of $1/n$" becomes
+weaker.
 
@@
 representatives in unicameral legislatures rather than in bicameral systems.
-This indicates that while the law of $1/n$ is not generalisable, its predicted
+This indicates that while the "law of $1/n$" is not generalisable, its predicted
 effects are stronger when the institutional features of a polity come closer to
@@
 positive changes in this respect, such as EGAP's _Metaketa
-Initiative_.\footnote{See
+Initiative_\footnote{See
 \url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.} Here we show that continuously producing and consuming
+information.}. Here we show that continuously producing and consuming
 meta-analyses is a viable path towards knowledge-building in our discipline.

### 2021-06-01 appendix/appendix.Rmd
changes to appendix, article, R script

--- 2021-05-22 appendix/appendix.Rmd
@@
 author:
-- "Huzeyfe Alptekin[^alptekin]"
-- "Danilo Freire[^freire]"
-- "Umberto Mignozzetti[^mignozzetti]"
-- "Catarina Roman[^roman]"
+- "Huzeyfe Alptekin[^huzeyfe]"
+- "Danilo Freire[^danilo]"
+- "Umberto Mignozzetti[^umberto]"
+- "Catarina Roman[^catarina]"
 date: \today
@@
 
-[^alptekin]: Research Associate, Contemporary Brazilian History Research and Documentation Center, School of Social Sciences, Fundação Getulio Vargas, <huzeyfealptekin@gmail.com>.
-
-[^freire]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.
-
-[^roman]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
+[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
+
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 
@@
 
-# A Brief Introduction to the Law of _1/n_ and the Reverse Law of _1/n_
-
-In this section, we present the intuition behind the _law of 1/n_, as well as the alternative _reverse law of 1/n_ proposed by @primo2008distributive.
-
-In their seminal paper, @weingast1981political argue that a high number of legislators will increase public spending beyond the optimal economic benchmark.
-They suggest that politicians have an incentive to over-provide concentrated benefits to their constituencies, spreading the costs across all constituencies through generalised taxation.
-The corollary of their model is that larger legislatures generate more public spending.
-
-In their model, every local public goods project of size $x$ generates a concave benefit $b(x)$, and there are convex costs associated with the project.\footnote{Concave means that $b'>0$ and $b''<0$.
-Convex means that $c'>0$ and $c''>0$.
-We assume that the derivatives are well defined throughout the analysis.
-Moreover, we drop the constituency index to make the model more intuitive, so the reader should assume that we always employ a symmetric Nash equilibrium.} The first type of cost, $c_1(x)$, comprises the expenses within the constituency (e.
-g., hiring a local company for the project).
-The second type of cost, $c_2(x)$, captures the expenses outside the constituency (e.
-g., hiring a company from another state).
-Finally, the third cost, $c_3(x)$, captures the externalities generated by the project (e.
-g., how much prices shift because local economic factors are being used to provide the project).
-The total cost is equal to $c(x) = c_1(x) + c_2(x) + c_3(x)$.
-The tax burden generated by the project is equal to $T(x) = c_1(x) + c_2(x)$.
-
-Projects are economically efficient when the marginal costs are equal to the marginal benefits of the project size.
-This leads to the economic optimal project size, $x^E$.
-The optimal project size is $b'(x^E) - c_1'(x^E) - c_2'(x^E) - c_3'(x^E) = 0$.
-However, the projects that are actually implemented have a different structure.
-First, assume that the constituency in question has a tax burden $t = 1/n$, where $n$ represents the number of constituencies.
-Also, suppose that benefits are distorted by the fact that costs within the constituency ($c_1(x)$) become investments in local firms.
-Therefore, the costs and benefits of implementing a project with size $x$ have the following structure:
+# A Brief Introduction to the "Law of _1/n_" and the "Reverse Law of _1/n_"
+
+In this section, we present the intuition behind the "law of $1/n$", as well as
+the alternative "reverse law of $1/n$" proposed by @primo2008distributive.
+
+In their seminal paper, @weingast1981political argue that a high number of
+legislators will increase public spending beyond the optimal economic
+benchmark. They suggest that politicians have an incentive to over-provide
+concentrated benefits to their constituencies, spreading the costs across all
+constituencies through generalised taxation. The corollary of their model is
+that larger legislatures generate more public spending.
+
+In their model, every local public goods project of size $x$ generates a
+concave benefit $b(x)$, and there are convex costs associated with the
+project\footnote{The concavity assumption implies that $b'>0$ and $b''<0$. A
+similarly convex assumption would mean that $c'>0$ and $c''>0$. We assume that
+the derivatives are well defined throughout the analysis. Moreover, we drop the
+constituency index to make the model more intuitive, so the reader should
+assume that we always employ a symmetric Nash equilibrium.}. The first type of
+cost, $c_1(x)$, comprises the expenses within the constituency (e. g., hiring a
+local company for the project). The second type of cost, $c_2(x)$, captures the
+expenses outside the constituency (e. g., hiring a company from another state).
+Finally, the third cost, $c_3(x)$, captures the externalities generated by the
+project (e. g., how much prices shift because local economic factors are being
+used to provide the project). The total cost is equal to $c(x) = c_1(x) +
+c_2(x) + c_3(x)$. The tax burden generated by the project is equal to $T(x) =
+c_1(x) + c_2(x)$.
+
+Projects are economically efficient when the marginal costs are equal to the
+marginal benefits of the project size. This leads to the economic optimal
+project size, $x^E$, which is defined as $b'(x^E) - c_1'(x^E) - c_2'(x^E) -
+c_3'(x^E) = 0$. However, the projects that are actually implemented have a
+different structure. First, assume that the constituency in question has a tax
+burden $t = 1/n$, where $n$ represents the number of constituencies. Also,
+suppose that benefits are distorted by the fact that costs within the
+constituency ($c_1(x)$) become investments in local firms. Therefore, the costs
+and benefits of implementing a project with size $x$ have the following
+structure:
 
@@
 
-Differentiating $N(x)$ with respect to $x$ gives us the first order condition for an optimal project implementation.
+Differentiating $N(x)$ with respect to $x$ gives us the first order condition
+for an optimal project implementation.
 
@@
 
-Note that the numerator is always positive, as the marginal investment costs inside and outside the district increase according to the project size.
-The _law of 1/n_ holds when the denominator is negative.
-$b''(x) < 0$ by assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'', c_3'' > 0$.
-Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than $n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
-
-As the above condition suggests, the _law of 1/n_ holds only in specific situations.
-@primo2008distributive advance that theory by considering other situations where the _law_ may not hold, and they also argue that there are cases in which a _reverse law of 1/n_ holds, that is, larger legislatures may lead to lower public expenditures.
-
-Following @primo2008distributive, let $n$ be the number of districts, $m$ the number of citizens in each district, and $nm$ is the total population in the country.
-Consider a local public good that generates a per capita benefit of $b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the degree of congestion of the public good, that is, how much the addition of individuals reduce the benefits for other individuals (note that the lower the $\beta$, the higher the congestion).
-In terms of costs, consider a linear cost function $C(x) = x$, and in terms of taxation, assume that the people in the district pay both local and federal government taxes.
-The degree that taxes are shared is denoted by $s$.
-Moreover, there is a deadweight loss of the taxes $\theta \geq 1$.
-The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns – s)X}{nm}\right)^\theta$.
-Therefore, the citizens receive the following net benefit of a project with size $x$:
+Note that the numerator is always positive, as the marginal investment costs
+inside and outside the district increase according to the project size. The
+"law of $1/n$" holds when the denominator is negative. $b''(x) < 0$ by
+assumption, and $-n^{-1}[c_1''(x) + c_2''(x)] - c_3''(x) < 0$ as $c_1'', c_2'',
+c_3'' > 0$. Then, the _law of 1/n_ is true when $c_1''(x)$ is smaller than
+$n^{-1}[c_1''(x) + c_2''(x)] + c_3''(x) - b''(x)$.
+
+As the above condition suggests, the "law of $1/n$" holds only in specific
+situations. @primo2008distributive advance that theory by considering other
+situations where the "law" may not hold, and they also argue that there are
+cases in which a "reverse law of $1/n$" may exist, that is, where larger
+legislatures may lead to lower public expenditures.
+
+Following @primo2008distributive, let $n$ be the number of districts, $m$ the
+number of citizens in each district, and $nm$ the total population in the
+country. Consider a local public good that generates a per capita benefit of
+$b(x, m) = x^\alpha m^{\beta-1}$ according to size $x$, where $\beta$ is the
+degree of congestion of the public good, that is, how much the addition of
+individuals reduce the benefits for other individuals (note that the lower the
+$\beta$, the higher the congestion). In terms of costs, consider a linear cost
+function $C(x) = x$, and in terms of taxation, assume that the people in the
+district pay both local and federal government taxes. The degree that taxes are
+shared is denoted by $s$. Moreover, there is a deadweight loss of the taxes
+$\theta \geq 1$. The tax then becomes: $t = \left(\dfrac{(n – ns + s)x + (ns –
+s)X}{nm}\right)^\theta$. Therefore, the citizens receive the following net
+benefit of a project with size $x$:
 
@@
 
-Maximising this function, and solving for the symmetric Nash equilibrium where $x = X$ for all projects, we find the following optimal project size:
+Maximising this function, and solving for the symmetric Nash equilibrium where
+$x = X$ for all projects, we find the following optimal project size:
 
@@
 
-And in the graph below, we show simulations for $n$ varying from 10 to 20, holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m = 100$, and $\alpha = 0.7$.
+And in the graph below, we show simulations for $n$ varying from 10 to 20,
+holding constant $\beta = 0.35$, $\theta \in \{0.65, 0.75\}$, $s = 0.5$, $m =
+100$, and $\alpha = 0.7$.
 
@@
 curve(xstar(x, beta = 0.35, theta = 0.8), from = 10, to = 20,
-      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
+      main = 'Increasing project size when varying legislature size \n (high deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
 curve(xstar(x, beta = 0.35, theta = 0.5), from = 10, to = 20,
-      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Project Size', ylab = 'Number of Districts (legislature size)')
-```
-
-Thus, we see that both the _law of 1/n_ and its reverse formulation are equally plausible.
-Here we show how the results change just by changing the levels of deadweight losses, but authors have suggested other reasons why the _law of 1/n_ may not apply, such as bicameralism [@chen_malhotra_2007], popular initiatives [@matsusaka2005endogeneity], type of government [@coate2011government], supermajorities [@lee2015supermajority], political fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].
+      main = 'Decreasing project size when varying legislature size \n (low deadweight losses)', xlab = 'Legislature Size', ylab = 'Project Size')
+```
+
+Thus, we see that both the "law of $1/n$" and its reverse formulation are
+equally plausible. Here we show how the results change just by changing the
+levels of deadweight losses, but authors have suggested other reasons why the
+"law of $1/n$" may not apply, such as bicameralism [@chen2007law], popular
+initiatives [@matsusaka2005endogeneity], type of government
+[@coate2011government], supermajorities [@lee2015supermajority], political
+fragmentation [@lledo2003electoral], and ideology [@bjedov2014impact].
 
@@
 The first step in our systematic review consisted in gathering a study sample.
-We started our data collection with a manual search based on a set of keywords we scouted from the distributive politics literature.
-This search produced a database with many entries that were unrelated to our subject of investigation.
-To reduce the number of false positives in our sample, we restricted our search to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The Political Economy of Benefits and Costs: A Neoclassical Approach to Distributive Politics_", which is the fundamental contribution to the field.
-Although \href{https://scholar.google.com/}{Google Scholar} reports the article has received \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
-
-We webscraped three large academic databases: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and \href{https://www.scopus.com/}{Scopus} (n = 736).
-The `R` script we wrote extracted the article title, abstract, authors, year, journal of publication, and database from which the record originated.
-Our code is available in the `R` script available in this repository.
-We screened these results with an English language and article restriction, that is, we excluded all records written in other languages and all that were not academic papers, such as book chapters or doctoral theses.
-We set no restriction to unpublished articles.
-
-We complemented this process by doing a term search on Google Scholar after having finished the entire eligibility procedure in the first sample.
-We formulated the search string based on the terms and expressions that appeared most frequently in the articles included in our meta-analysis.
-The choice of string translates the central point of our inquiry: the relationship between legislature size and public spending.
-The search string was as follows: `("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")`.
-We scraped Google Scholar on March 5^th^, 2021.
-Using the titles of this new database's records, we did a fuzzy matching with the database of @weingast1981political citations mentioned previously.
-We then performed the exact same eligibility procedures, further explained below.
-This resulted in 3,041 additional records.
-Combining the two search strategies, we assessed a total of 5,705 records.
+We started our data collection with a manual search based on a set of keywords
+we scouted from the distributive politics literature. This search produced a
+database with many entries that were unrelated to our subject of investigation.
+To reduce the number of false positives in our sample, we restricted our search
+to studies that cited Weingast, Shepsle and Johnsen's 1981 paper "_The
+Political Economy of Benefits and Costs: A Neoclassical Approach to
+Distributive Politics_", which is the fundamental contribution to the field.
+Although \href{https://scholar.google.com/}{Google Scholar} reports the article
+has received
+\href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180}
+citations, our search resulted in 2,664 records on the 21^st^ of November 2019.
+
+We webscraped three large academic databases:
+\href{https://scholar.google.com/}{Google Scholar} (n = 1001);
+\href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
+\href{https://www.scopus.com/}{Scopus} (n = 736). The `R` script we wrote
+extracted the article title, abstract, authors, year, journal of publication,
+and database from which the record originated. Our code is in the `R` script
+available in this repository. We then filtered these results and selected only
+articles that were written in English. While we included unpublished papers in
+our search, we excluded book chapters and doctoral theses from our sample.
+
+We complemented this process by doing a term search on Google Scholar after
+having finished the entire eligibility procedure in the first sample. We
+formulated the search string based on the terms and expressions that appeared
+most frequently in the articles included in our meta-analysis. The choice of
+string translates the central point of our inquiry: the relationship between
+legislature size and public spending. The search string was as follows:
+`("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament
+size" OR "legislature size" OR "number of legislators" OR "legislative size")
+AND ("spending" OR "expenditure" OR "government size")`. We scraped Google
+Scholar on March 5^th^, 2021. Using the titles of this new database's records,
+we fuzzy-matched those articles with the database of @weingast1981political
+citations mentioned previously to check for duplicates. We then performed the
+exact same eligibility procedures, further explained below. This resulted in
+3,041 additional records. Combining the two search strategies, we assessed a
+total of 5,705 records.
 
@@
 
-The selection process was conducted by two authors in three phases.
-In the first phase, we excluded all titles that were clearly unrelated to our topic of interest.
-This was only a preliminary step, as we were not able to eliminate a large number of entries.
-Then, we read all abstracts.
-We kept all publications whose main topics were either government expenditure or legislative structures.
-Abstracts that indicated that the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics were included.
-This allowed us to significantly reduce our sample.
-
-In the second phase, we assessed full texts.
-To remain in our sample, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also include data on public expenditure.
-If the publication had all three, we kept it in our sample.
-Disagreements in this phase were discussed among the authors, and a third investigator was consulted when needed.
-
-The third phase consisted of filling out tables for each of the remaining 47
+The selection process was conducted by two authors in three phases. In the
+first phase, we excluded all titles that were clearly unrelated to our topic of
+interest. This was only a preliminary step, as we were not able to eliminate a
+large number of entries. Then, we read all abstracts. We kept all publications
+whose main topics were either government expenditure or legislative structures.
+Abstracts that indicated that the paper discussed or estimated the impacts of
+representative institutions, elections, or chamber dynamics were included. This
+allowed us to significantly reduce our sample.
+
+In the second phase, we assessed full texts. To remain in our sample, the paper
+should (i) conduct a quantitative analysis, (ii) report data on the number of
+legislators, and (iii) also include data on public expenditure. If the
+publication had all three, we kept it in our sample. Disagreements in this
+phase were discussed among the authors, and a third investigator was consulted
+when needed.
+
+The third phase consisted of filling out tables for each of the remaining 
 articles to systematically evaluate their eligibility. Since authors use
@@
 phase, we also collected information on whether the paper had been published,
-and if it explicitly discussed the _law of 1/n_. Upon choosing the variables,
+and if it explicitly discussed the "law of $1/n$". Upon choosing the variables,
 we excluded two studies from the first sample, as they did not have the
@@
 
-We selected the final pool of articles based on two criteria, namely the treatment and the outcome variables employed in the paper. The categories follow below:
-
-1.  Treatment variables:
-
--   *N*: Number Legislators in the Lower House
--   *logN*: Log Number Legislators in the Lower House
--   *K*: Number Legislators in the Upper House
-
-2.  Outcome variables:
+We selected the final pool of articles based on two criteria, namely the independent and the dependent variables employed in the paper. The categories follow below:
+
+1.  Independent variables:
+
+-   *N*: Lower Chamber Size
+-   *logN*: Log Lower Chamber Size
+-   *K*: Upper Chamber Size
+
+2.  Dependent variables:
 
@@
 -   *logExpPC*: Log Expenditure Per Capita
--   *PCTGDP*: Percent GDP Public Expenditure
+-   *PCTGDP*: Expenditure as Percentage of GDP
 
@@
 
-```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
+```{tikz tikz-ex, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.height=2, fig.cap = "PRISMA Flow Chart for First Search Strategy: Weingast et al. Citations"}
 \usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+\scalebox{0.9}{
   \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
@@
   \draw [arrow] (inc_1) -- (inc_2);
-
  \end{tikzpicture}
-```
-
-\bigskip
-
-```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.width=5, fig.height=2, fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
+}
+```
+
+```{tikz tikz-ex2, echo=FALSE, cache=TRUE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex"), fig.cap="PRISMA Flow Chart for First Search Strategy: Search String with Terms"}
 \usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
+\scalebox{0.9}{
   \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]
@@
  \end{tikzpicture}
+}
 ```
@@
 
-Our meta-analytic data are comprised of two datasets.
-The first dataset has the main coefficients reported in the selected studies.
-These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them.
-If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one.
-This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest.
-Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.
-
-In the main text, we focus on the results for our restricted sample as we consider them more robust, but the findings are very similar when we use the extended dataset.
-Here we present the results of all tests performed in both reduced and full samples.
+Our meta-analytic data are comprised of two datasets. The first dataset has the
+main coefficients reported in the selected studies. These data include only the
+most rigorous model from each paper, that is, those estimated with the largest
+sample size, most control variables, and fixed effects if the authors added
+them. If the article employed a regression discontinuity design, we chose the
+coefficient from the optimal bandwidth or from the intermediate one. This
+sample encompasses `r dim(dat)[1]` estimates, as 
+`r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or
+independent variables of interest. Our second sample, in contrast, contains all
+the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))`
+papers.
+
+In the main text, we focus on the results for our restricted sample as we
+consider them more robust, but the findings are very similar when we use the
+extended dataset. Here we present the results of all tests performed in both
+reduced and full samples.
 
@@
 
-Here we show the descriptive statistics for our sample.
-We focus on the following paper characteristics: study year; paper publication; the  electoral system mentioned in the publication; and the distribution of the dependent and independent variables of interest.
+Here we show the descriptive statistics for our sample. We focus on the
+following paper characteristics: study year; paper publication; the electoral
+system mentioned in the publication; and the distribution of the dependent and
+independent variables of interest.
 
@@
 
-The average year of publication in our sample is `r round(mean(dat$year), 2)` with standard deviation of `r round(sd(dat$year), 2)`.
-The oldest study included in the paper is from `r min(dat$year)`, while the most recent paper was written in `r max(dat$year)`.
-Therefore, we cover `r max(dat$year)-min(dat$year)` years of tests of the *law of 1/n*.
+The average year of publication in our sample is `r round(mean(dat$year), 2)`
+with standard deviation of `r round(sd(dat$year), 2)`. The oldest study
+included in the paper is from `r min(dat$year)`, while the most recent paper
+was written in `r max(dat$year)`. Therefore, we cover 
+`r max(dat$year)-min(dat$year)` years of tests of the "law of $1/n$".
 
@@
 Studies were included in our sample regardless of their publication status.
-From the `r length(unique(dat$id))` papers in the sample, `r as.numeric(table(unique(select(dat, id, published))$published)[2])` were published while `r as.numeric(table(unique(select(dat, id, published))$published)[1])` were not published.
+From the `r length(unique(dat$id))` papers in the sample,
+`r as.numeric(table(unique(select(dat, id, published))$published)[2])` were
+published while `r as.numeric(table(unique(select(dat, id, published))$published)[1])`
+were not published.
 
@@
     geom_bar(color = "black") +
-  labs(x = "Published Study?",
+  labs(x = "",
        y = "") +
@@
 
-Our sample differs considerably in regards to research design.
-One remarkable difference is that several authors apply the logics of the *law of 1/n*, which was built with majoritarian systems in mind, to non-majoritarian democracies.
-In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])` of the papers study *Majoritarian* systems while `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study *Non-Majoritarian* electoral systems.\footnote{Note that for the \textit{law of 1/n} to be valid in a non-majoritarian system, we need to assume that despite the fact that politicians are able to campaign in every place in the district, votes are geographically concentrated.
-The concentration facilitates politicians to use pork-barrel projects to captivate their electoral supporters.}
+Our sample differs considerably in regards to research design. One remarkable
+difference is that several authors apply the logics of the "law of $1/n$", which
+was built with majoritarian systems in mind, to non-majoritarian democracies.
+In the sample, `r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[1])`
+of the papers study *Majoritarian* systems while 
+`r as.numeric(table(unique(select(dat, id, elecsys2))$elecsys2)[2])` study
+*Non-Majoritarian* electoral systems\footnote{Note that for the "law of
+$1/n$" to be valid in a non-majoritarian system, we need to assume that despite
+the fact that politicians are able to campaign in every place in the district,
+votes are geographically concentrated. The concentration facilitates
+politicians to use pork-barrel projects to captivate their electoral
+supporters.}.
 
@@
     geom_bar(color = "black") +
-  labs(x = "Electoral Systems",
+  labs(x = "",
        y = "") +
@@
 
-The outcome variables included in the paper are:
-
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Per Capita Expenditure papers
+The dependent variables included in the paper are:
+
+-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[1])` Expenditure Per Capita papers
 -   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[2])` Expenditure as a Percentage of the GDP papers
--   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Natural Log of Per Capita Expenditure papers
+-   `r as.numeric(table(unique(select(dat, id, depvar2))$depvar2)[3])` Log of Expenditure Per Capita papers
 
@@
   mutate(depvar2 = factor(depvar2,
-                          labels = c("Per Capita Expenditure",
-                                     "Percentage GDP Government Expenditure",
-                                     "Log Per Capita Expenditure"))) %>%
+                          labels = c("Expenditure Per Capita",
+                                     "Expenditure as Percentage GDP",
+                                     "Log Expenditure Per Capita"))) %>%
   ggplot(aes(x = depvar2)) +
@@
   labs(x = "",
-       y = "Dependent Variables") +
+       y = "") +
   coord_flip() +
@@
 
-Most papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(dat$indepvar2)[3])`).
-The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(dat$indepvar2)[1])`).
-Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(dat$indepvar2)[2])`).
-As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.
+Most papers in our sample analyse the number of legislators in the lower
+chamber (`r as.numeric(table(dat$indepvar2)[3])`). The second most frequent
+independent variable is the number of legislators in the upper chamber 
+(`r as.numeric(table(dat$indepvar2)[1])`). Finally, the minority of papers use the
+natural log of the number of legislators in the lower chamber as an independent
+variable (`r as.numeric(table(dat$indepvar2)[2])`). As we noted above, some
+papers had multiple coefficients, and thus the total number of coefficients is
+`r dim(dat)[1]`, while the number of papers is only `r length(unique(dat$id))`.
 
@@
   unique() %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
-                                                  "Log N",
-                                                  "N (lower house legislators)"
+  mutate(indepvar2 = factor(indepvar2, 
+                            labels = c("Upper Chamber Size",
+                                       "Log of Lower Chamber Size",
+                                       "Lower Chamber Size"
                                                   ))) %>%
@@
   labs(x = "",
-       y = "Independent Variables") +
+       y = "") +
   coord_flip() +
@@
 
-The coefficients in the papers vary considerably.
-We plot a histogram of the coefficients for all measurements included in the meta-analytic dataset.
-Most coefficients and standard deviations are close to zero.
+The coefficients in the papers vary considerably. We plot a histogram of the
+coefficients for all measurements included in the meta-analytic dataset. Most
+coefficients and standard deviations are close to zero.
 
@@
 
-\newpage
-
 Standard errors:
@@
 
-One simple statistic that we can compute to assess the validity of the *law of 1/n* is the frequency of positive and negative estimates in the study sample.
-Below we plot the frequency for all the papers included in the meta-analytic dataset.
+One simple statistic that we can compute to assess the validity of the "law of
+$1/n$" is the frequency of positive and negative estimates in the study sample.
+Below we plot the frequency for all papers included in the meta-analytic
+dataset.
 
@@
   geom_bar(color = "black") +
-  labs(x = "Coefficient Sign",
+  labs(x = "",
        y = "") +
@@
 
-We chose a set of moderators that frequently appear in the literature and may help us interpret our results.
-We included them in our meta-regressions alongside an indicator for the type of independent variable used in the original study ($n$, log($n$), or $k$).
-The additional moderators are: electoral system; estimation method; publication year; paper publication in an academic journal.
+We chose a set of moderators that frequently appear in the literature and may
+help us interpret our results. We included them in our meta-regressions
+alongside an indicator for the type of independent variable used in the
+original study: lower chamber size; natural logarithm of lower chamber size; or
+upper chamber size. The additional moderators are: publication year; whether
+the paper was published in an academic journal; the estimation method used in
+the paper; the institutional design in terms of the division of legislative
+power; and the electoral system.
 
@@
 levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
-aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
-              year, published) %>%
+aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
+              instdesign, elecsys2) %>%
+  mutate(indepvar2 = recode(indepvar2,
+                            `N` = "Lower Chamber Size",
+                            `K` = "Upper Chamber Size",
+                            `logN` = "Log of Lower Chamber Size"),
+         elecsys2 = recode(elecsys2,
+                           `Non-Maj` = "Non-Majoritarian",
+                           `Maj` = "Majoritarian")) %>%
   rename(`Independent Variables` = indepvar2,
-         `Electoral system`      = elecsys2,
+         `Year`                  = year,
+         `Published work`        = published,
          `Estimation method`     = method,
-         `Year`                  = year,
-         `Published work`        = published)
-
+         `Institutional Design`  = instdesign,
+         `Electoral system`      = elecsys2)
 export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
@@
 
-The *law of 1/n* posits that we should expect a positive influence of legislature size on public expenditures.
-A general test of the theory could investigate whether the papers tend to find a higher frequency of positive coefficients in their estimations.
-In statistical terms, consider a random variable representing the coefficient sign for the papers.
-As each sign of the paper is a Bernoulli trial, the aggregate result for all papers follows a Binomial distribution with parameters $n$ equals the number of papers, and $p$ the chance of a positive sign.
-The *law of 1/n* can be reformulated as the chance of $p>0.5$, which facilitates the testing of the theory.
-The null hypothesis for such a test is that:
-
--   $H_0$: the proportion of positive and negative signs are statistically equal ($p=0.5$).
-
-As we are taking an agnostic approach, we acknowledge that either the *law of 1/n* ($p>0.5$), or the *reverse law of 1/n* ($p<0.5$) may be true.
-In this case, the alternative hypothesis is $p\neq 0.5$.
-To perform this test, we run binomial tests in `R`, using the function `binom.test(.)`.
-
-This test has two advantages.
-First, it is robust to the design of the paper.
-This is an important feature as papers analyse different countries, samples, and have distinct characteristics, such as whether they were published or not.
-The binomial test ignores the design discrepancies and focuses on the overall reported effect.
-Second, this test has the advantages of requiring few assumptions and being easy to interpret.
-The disadvantage is that the test is not as informative as the meta-regressions, as we shall see in the next sections.
-
-For the number of legislators in the lower house ($N$), the results follow below.
+The "law of $1/n$" posits that we should expect a positive influence of
+legislature size on public expenditures. A general test of the theory could
+investigate whether the papers find a higher frequency of positive coefficients
+in their estimations. In statistical terms, consider a random variable
+representing the coefficient sign for the papers. As each sign of the paper is
+a Bernoulli trial, the aggregate result for all papers follows a Binomial
+distribution with parameters $n$ equals the number of papers, and $p$ the
+chance of a positive sign. The "law of $1/n$" can be reformulated as the chance
+of $p>0.5$, which facilitates the testing of the theory. The null statistical
+hypothesis for such a test is that:
+
+- $H_0$: the proportion of positive and negative signs are statistically equal
+  ($p=0.5$).
+
+We take an agnostic approach and acknowledge that either the "law of $1/n$"
+($p>0.5$), or the "reverse law of $1/n$" ($p<0.5$) may be true. In this case,
+the alternative hypothesis is $p \neq 0.5$. To perform this test, we run
+binomial exact tests in `R`, using the function `binom.test(.)`.
+
+This test has two advantages. First, the binomial test ignores the design
+discrepancies and focuses on the overall reported effect. This is an important
+feature as papers analyse different countries, samples, and have distinct
+characteristics, such as whether they were published or not. Second, this test
+has the advantages of requiring few assumptions and being easy to interpret.
+The disadvantage is that the test is not as informative as the
+meta-regressions, as we shall see in the next sections.
+
+For the lower chamber size, the results follow below.
 
@@
 
-Under the null hypothesis of $p=0.5$, we find that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
-The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-Thus, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-
-For the log of the number of legislators in the lower house ($\log(N)$), the results are as follows:
+Under the null hypothesis of $p=0.5$, we find that 
+`r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have
+a positive sign. The chance of a distribution with $p=0.5$ generate this sample
+is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. Thus, we 
+`r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that
+$p \neq 0.5$.
+
+For the log of lower chamber size, the results are as follows:
 
@@
 
-Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])` have a positive sign.
-The chance of a distribution with $p=0.5$ generate this sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`.
-So we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-
-Finally, for the number of legislators in the upper house ($K$), the results are:
+Out of `r sum(table(aux$scoef))` studies, `r as.numeric(table(aux$scoef)[2])`
+have a positive sign. The chance of a distribution with $p=0.5$ generate this
+sample is equal to p-value = `r round(as.numeric(aux2$p.value), 3)`. So we 
+`r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that
+$p \neq 0.5$.
+
+Finally, for upper chamber size, the results are:
 
@@
 
-Here we see that `r as.numeric(table(aux$scoef)[2])` out of `r sum(table(aux$scoef))` studies have a positive sign.
-The p-value for this test is `r round(as.numeric(aux2$p.value), 3)`.
-Therefore, we `r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that $p \neq 0.5$.
-This is the only test that presents evidence of an association between the legislature size and expenditure.
+Here we see that `r as.numeric(table(aux$scoef)[2])` out of 
+`r sum(table(aux$scoef))` studies have a positive sign. The p-value for this test
+is `r round(as.numeric(aux2$p.value), 3)`. Therefore, we 
+`r ifelse(as.numeric(aux2$p.value)<0.1, 'accept', 'reject')` the hypothesis that
+$p \neq 0.5$. This is the only test that presents evidence of an association
+between the legislature size and expenditure.
+
+We also tested the possibility that the signs change depending on whether the
+study analyses unicameral or non-unicameral legislative bodies. This analysis
+does not take into consideration the size of the upper house, as it would
+indicate that the cases in the paper have a non-unicameral legislature. The
+results for this analysis follow below. They show that there is no significant
+change in the sign of the relationship between public spending and legislature
+size, when controlling by the institutional design.
+
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
+aux <- list()
+aux[[1]] <- filter(dat, indepvar2 == "N", instdesign2 == 'Unicameral')
+aux[[2]] <- filter(dat, indepvar2 == "N", instdesign2 != 'Unicameral')
+aux[[3]] <- filter(dat, indepvar2 == "logN", instdesign2 == 'Unicameral')
+aux[[4]] <- filter(dat, indepvar2 == "logN", instdesign2 != 'Unicameral')
+aux[[1]] <- binom.test(table(aux[[1]]$scoef)[2],
+                       sum(table(aux[[1]]$scoef)), p = 0.5)
+aux[[2]] <- binom.test(table(aux[[2]]$scoef)[2],
+                       sum(table(aux[[2]]$scoef)), p = 0.5)
+aux[[3]] <- binom.test(table(aux[[3]]$scoef)[2],
+                       sum(table(aux[[3]]$scoef)), p = 0.5)
+aux[[4]] <- binom.test(table(aux[[4]]$scoef)[2],
+                       sum(table(aux[[4]]$scoef)), p = 0.5)
+aux2 <- tidy(aux[[1]])[,-c(2,4,5,6)][,c(3,4,1,2)]
+aux2 <- bind_rows(aux2, tidy(aux[[2]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- bind_rows(aux2, tidy(aux[[3]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- bind_rows(aux2, tidy(aux[[4]])[,-c(2,4,5,6)][,c(3,4,1,2)])
+aux2 <- aux2 %>%
+  mutate(`Indep. Variable` = c('Lower House Size', 'Lower House Size', 'Log of Lower House Size', 'Log of Lower House Size'),
+         `Legislative Inst.` = c('Unicameral', 'Non-unicameral', 'Unicameral', 'Non-unicameral')) %>%
+  relocate(`Indep. Variable`, `Legislative Inst.`, .before = method)
+aux2$method <- NULL
+aux2$alternative <- NULL
+pander(aux2)
+```
 
@@
 
-In general terms, there are two main ways to conduct a meta-analysis, either by using fixed effects or by employing random effects models.
-The fixed effects model assumes that there exists a single true effect and all estimates are an attempt to uncover this effect.
-The random effects model, in contrast, assumes that there is a distribution of true effects, and that the coefficients vary based on sampling and tests characteristics.
-
-In this paper, we employ a random effects model.
-The empirical papers testing the *law of 1/n* are very diverse.
-We tried to capture some of this diversity by considering the main dependent and independent variables separately, but they have at least three other important sources of dispersion:
+In general terms, there are two main ways to conduct a meta-analysis. Scholars
+either use fixed effects or random effects models. The fixed effects model
+assumes that there exists a single true effect and all estimates are an attempt
+to uncover this effect. The random effects model, in contrast, assumes that
+there is a distribution of true effects, and that the coefficients vary based
+on sampling and tests characteristics.
+
+In this paper, we employ a random effects model. The empirical papers testing
+the *law of 1/n* are very diverse. We tried to capture some of this diversity
+by considering the main dependent and independent variables separately, but
+they have at least three other important sources of dispersion:
 
@@
 3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
-
-These sources of heterogeneity have two implications.
-First, they make our estimates notably disperse.
-Second, the amount of heterogeneity makes fixed effects estimates unrealistic and biased.
-Thus, we opt for random effects model.
-
-Assume that each study has an effect of $T_i$.
-In a random effects model, we can decompose this effect into two components, the true effect that the study with the same specifications as $i$ comes from, $\theta_i$, and a within-study error $\varepsilon_i$:
+4.  **Institutional design**: Unicameral, Bicameral, or the Mixed of both Unicameral and Bicameral.
+
+These sources of heterogeneity have two implications. First, they make our
+estimates notably disperse. Second, the amount of heterogeneity makes fixed
+effects estimates unrealistic and biased. Thus, we opt for the random effects
+model.
+
+Assume that each study has an effect of $T_i$. In a random effects model, we
+can decompose this effect into two components, the true effect that the study
+with the same specifications as $i$ comes from, $\theta_i$, and a within-study
+error $\varepsilon_i$:
 
@@
 
-And the random effects model assumes that the $\theta_i$ varies from study to study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
+And the random effects model assumes that the $\theta_i$ varies from study to
+study, having a true parameter $\mu$, plus a between-study error, $\xi_i$:
 
@@
 
-And the random effects model estimates the parameter $\mu$, under the challenge of estimating both the within-and-between-study sampling errors.
-
-Another crucial assumption in meta-analysis is that the coefficients should be independent [@harrer2019doing; @cheung2019guide; @veroniki2016methods; @borenstein2011introduction].
-This assumption states that for our findings to be consistent, the coefficients must come from different sources of variation.
-However, in the political economy literature, authors frequently use similar datasets, and almost all papers fit more than one model with similar variables.
-While our restricted dataset contains `r nrow(dat)` estimates, our full dataset has `r nrow(fulldat)` coefficients.
-This is because the papers report an average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients.
-To correct for the violation of the independent assumption, we use a multilevel random effects model [@cheung2014modeling].
-We add two extra levels to the regular random effects model, one that indicates the publication ID and another that indicates the data used in the original article.
-These levels are assumed to remove dependence structures in the data, therefore improving the estimates of our coefficient of interest, which is the effect of legislature size on public spending.
-
-There are two levels in the main models. First, we build a common index for papers that share the same data specifications. The papers with common indexing are:
+And the random effects model estimates the parameter $\mu$, under the challenge
+of estimating both the within-and-between-study sampling errors.
+
+Another crucial assumption in meta-analysis is that the coefficients should be
+independent [@harrer2019doing; @cheung2019guide; @veroniki2016methods;
+@borenstein2011introduction]. This assumption states that for our findings to
+be consistent, the coefficients must come from different sources of variation.
+However, in the political economy literature, authors frequently use similar
+datasets, and almost all papers fit more than one model with similar variables.
+While our restricted dataset contains `r nrow(dat)` estimates, our full dataset
+has `r nrow(fulldat)` coefficients. This is because the papers report an
+average of `r round(mean(as.numeric(table(fulldat$id))), 2)` coefficients. To
+correct for the violation of the study independence assumption, we use a
+multilevel random effects model [@cheung2014modeling]. We add two extra levels
+to the regular random effects model, one that indicates the publication ID and
+another that indicates the data used in the original article. These levels are
+assumed to remove dependence structures in the data, therefore improving the
+estimates of our coefficient of interest, which is the effect of legislature
+size on public spending.
+
+There are two levels in the main models. First, we build a common index for
+papers that share the same data specifications. The papers with common indexing
+are:
 
@@
 
-All the remaining papers received a unique index.
-As the number of the papers with these dependencies is not very high, and many characteristics within papers vary (e.
-g., state-wise ad-hoc exclusions, start and end points variations, region selection, etc), we show that it makes little difference to change from this index to the paper IDs.
-In regard to the full dataset, the results change considerably, because authors fit several models within the same paper.
-In any case, we use multilevel random effects for all the estimated models in this paper.
-
-To study the possibility of of publication bias, we add a funnel plot and an @egger1997bias test for distribution asymmetry for every model.
-Funnel plots display the possibility of having a file-drawer effect, meaning that null results are under-represented in our sample.
-In this type of plot, under the assumption of no file-drawer effect, the coefficients are expected to lie symmetrically around the mean observed outcome.
-If they are asymmetric, it provides evidence for a file-drawer effect.
-
-We use the `R` packages `meta` and `dmetar` in all estimates [@harrer2019doing].
-We employ the *Restricted Maximum Likelihood Estimator* to assess the variance of the true effect size ($\tau^2$), which in our formulation represents the variance of $\xi_i$.
-The literature regards this estimator as the most precise when analysing continuous measures, such as the ones we have in our data [@veroniki2016methods].
-
-We combine the three independent variables ($n$, $\log(n)$, and $k$) with our dependent variables of interest (Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a Percentage of the GDP).
-This formed a $3 \times 3$ table, yet not all combinations are available in the data.
-The results are shown below.
-
-## Lower House Size and Expenditure per Capita
-
-The results for the meta-analysis that compares lower house size (_n_) and expenditure per capita are available below.
+All of the remaining papers received a unique index. As the number of papers
+with these dependencies is not very high, and many characteristics within
+papers vary (e. g., state-wise ad-hoc exclusions, start and end points
+variations, region selection, etc), we show that it makes little difference to
+change from this index to the paper IDs. In regard to the full dataset, the
+results change considerably, because authors fit several models within the same
+paper. In any case, we use multilevel random effects for all the estimated
+models in this paper.
+
+To check the possibility of publication bias, we add a funnel plot and an
+@egger1997bias test for distribution asymmetry for every model. Funnel plots
+display the possibility of having a file-drawer effect, meaning that null
+results are under-represented in our sample. In this type of plot, under the
+assumption of no file-drawer effect, the coefficients are expected to lie
+symmetrically around the mean observed outcome. If they are asymmetric, it
+provides evidence for a file-drawer effect.
+
+We use the `R` packages `meta` and `dmetar` in all estimates
+[@harrer2019doing]. We employ the *Restricted Maximum Likelihood Estimator* to
+assess the variance of the true effect size ($\tau^2$), which in our
+formulation represents the variance of $\xi_i$. The literature regards this
+estimator as the most precise when analysing continuous measures, such as the
+ones we have in our data [@veroniki2016methods].
+
+We combine the three independent variables (Lower Chamber Size, Log of Lower
+Chamber Size, and Upper Chamber Size) with our dependent variables of interest
+(Expenditure Per Capita, Log of Expenditure Per Capita, Expenditure as a
+Percentage of the GDP). This formed a $3 \times 3$ table, yet not all
+combinations are available in the data. The results are shown below.
+
+## Lower Chamber Size and Expenditure Per Capita
+
+The results for the meta-analysis that compares lower chamber size and
+expenditure per capita are available below.
 
@@
 
-```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4.5, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 ```{r,include=F, warning=F, cache=TRUE, echo = FALSE}
-f1 <- build_forest(mod, NULL, lsize = 15, ttl = 'Lower House Size\nand Expenditure per Capita')
+f1 <- build_forest(mod, NULL, lsize = 15, ttl = '1.1 - Lower Chamber Size\nand Expenditure Per Capita')
 ```
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower House Size x Expenditure Per Capita, controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
@@
 
-## Log of Lower House Size and Expenditure per Capita
-
-There are no studies that have per capita expenditure as the dependent variable and log of lower house size as the treatment variable.
-
-## Upper House Size and Expenditure per Capita
-
-Now we look into the upper house size (*k*). In this model, we investigate the effect of upper house size on expenditure per capita (ExpPC).
+### Institutional Design Subgroup Analysis
+
+The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure.
+However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber.
+Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study.
+To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design.
+The results may be seen below.
+
+We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita.
+However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship, that is masked by the low statistical power.
+
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Institutional Design", warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
+                 capt = NULL, hetvar = aux$instdesign2)
+```
+
+## Log of Lower Chamber Size and Expenditure Per Capita
+
+There are no studies that have per capita expenditure as the dependent variable
+and log of lower chamber size as the independent variable.
+
+## Upper House Size and Expenditure Per Capita
+
+Now we look into the upper chamber size. In this model, we investigate the
+effect of upper house size on expenditure per capita.
 
@@
 
-```{r, fig.width=7, fig.height=3, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)", warning=FALSE, echo = FALSE}
+```{r, fig.width=7, fig.height=3, fig.cap="Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of upper house size (K) on per capita government expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r, include=FALSE, warning=FALSE, echo = FALSE}
-f2 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure Per Capita')
+f2 <- build_forest(mod, NULL, 15, ttl = '1.6 - Upper Chamber Size\nand Expenditure Per Capita')
 ```
@@
 
-## Lower House Size and Log Expenditure Per Capita
-
-This model estimates the Log of Per Capita Expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
+## Lower Chamber Size and Log of Expenditure Per Capita
+
+This model estimates the effect of lower chamber size on log of expenditure per
+capita.
 
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, echo = FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, echo = FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of per capita expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
-f3 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Log Expenditure Per Capita')
+f3 <- build_forest(mod, NULL, 15, ttl = '1.2 - Lower Chamber Size\nand Log Expenditure Per Capita')
 ```
@@
 
-## Log of Lower House Size and Log of Expenditure Per Capita
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+## Log of Lower Chamber Size and Log of Expenditure Per Capita
+
+In this specification, we measure how changes in the log of lower chamber size
+impact the log of per capita expenditure.
 
@@
 
-The forest plot is available below:
-
-```{r, fig.width=6, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)", echo = FALSE, warning=FALSE, cache=TRUE}
+The forest plot:
+
+```{r, fig.width=6, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Log Expenditure Per Capita", echo = FALSE, warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-The funnel plot:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on log of per capita government expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+And the funnel plot:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r,include=F, echo = FALSE, warning=F, cache=TRUE}
-f4  <- build_forest(mod, NULL, 15, ttl = 'Log of Lower House Size\nand Log of Expenditure Per Capita')
+f4  <- build_forest(mod, NULL, 15, ttl = '1.4 - Log Lower Chamber Size\nand Log Expenditure Per Capita')
 ```
@@
 
-## Upper House Size and Log of Expenditure Per Capita
-
-No studies correlate the log of per capita expenditure with the size of upper house (K).
-
-## Lower House Size and Expenditure as Percentage of GDP
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the treatment variable.
+## Upper Chamber Size and Log of Expenditure Per Capita
+
+No studies correlate the log of per capita expenditure with the size of the
+upper chamber.
+
+## Lower Chamber Size and Expenditure as Percentage of GDP
+
+This model evaluates the relationship between lower house size and percentage
+of GDP as public expenditure.
 
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, echo = FALSE, cache=TRUE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, echo = FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r, include=F, warning=F, echo = FALSE, cache=TRUE}
-f5 <- build_forest(mod, NULL, 15, ttl = 'Lower House Size\nand Expenditure as Percentage of GDP')
+f5 <- build_forest(mod, NULL, 15, ttl = '1.3 - Lower Chamber Size\nand Expenditure as Percentage of GDP')
 ```
@@
 
-## Log Lower House Size and Expenditure as Percentage of GDP
-
-This model investigates the percentage of GDP as public expenditure as the dependent variable and the log lower house size (logN) as the treatment variable.
+## Log Lower Chamber Size and Expenditure as Percentage of GDP
+
+This model correlates the percentage of GDP as public expenditure as the
+dependent variable and the log lower chamber size as the independent variable.
 
@@
 
-```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE}
+```{r, echo = FALSE, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE}
 build_forest(mod, NULL)
@@
 
-The funnel plot is available below:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log lower houses size (N) on the GDP share of public expenditure (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+Funnel plot:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-f6 <- build_forest(mod, NULL, 15, ttl = 'Log Lower House Size\nand Expenditure as Percentage of GDP')
+f6 <- build_forest(mod, NULL, 15, ttl = '1.5 - Log Lower Chamber Size\nand Expenditure as Percentage of GDP')
 ```
@@
 
-## Upper House Size and Expenditure as Percentage of GDP
-
-This model looks into the effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP).
+## Upper Chamber Size and Expenditure as Percentage of GDP
+
+This model measures the effect of upper chamber size on the public expenditure
+share of the GDP.
 
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 ```{r, include=F, warning=F, cache=TRUE, echo = FALSE}
-f7 <- build_forest(mod, NULL, 15, ttl = 'Upper House Size\nand Expenditure as Percentage of GDP')
+f7 <- build_forest(mod, NULL, 15, ttl = '1.7 - Upper Chamber Size\nand Expenditure as Percentage of GDP')
 ```
@@
 
-## Lower House Size and Expenditure per Capita (IV)
-
-Here we estimate a meta-analysis of the papers which use instrumental variables. The results may be seen below.
+## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)
+
+Here we estimate a meta-analysis of the papers which use instrumental
+variables. The results may be seen below.
 
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-No evidence of publication bias, as shown in the following tunnel plot:
-
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+No evidence of publication bias, as shown in the following funnel plot:
+
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
                        capt = NULL, lsize = 15, 
-                       ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
+                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(subgrouping by the estimation technique)', 
                        hetvar = aux$method)
@@
 
-Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenduture per capita.
+Over time, the literature evolved to use causally identified techniques to determine the effect of legislature size on the expenditure per capita.
 To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Methods", warning=FALSE, cache=TRUE, echo = FALSE}
 aux <- dat %>%
@@
 
-## Lower House Size and Log of Expenditure per Capita (RDD)
-
-In this subsection, we run a meta-analysis with papers that include regression discontinuity designs.
+## Lower Chamber Size and Log of Expenditure per Capita (Regression Discontinuity Design Only)
+
+In this subsection, we run a meta-analysis with papers that include regression
+discontinuity designs.
 
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 f9 <- build_forest(mod, capt = NULL, 
-                       lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by RDD)')
+                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(subgrouping by RDD)')
 ```
@@
 4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
+5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. The reason is because in that paper, the author uses Log of Expenditure Per Capita x Log of Legislature Size.
 
@@
 
-## Lower House Size and Expenditure Per Capita
-
-Here we estimate the relationship between expenditure per capita as a dependent variable, and the lower house size as the independent variable.
+## Lower Chamber Size and Expenditure Per Capita
+
+Here we estimate the relationship between expenditure per capita as a dependent
+variable, and the lower chamber as the independent variable.
 
@@
 
-```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower House Size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=12, fig.height=11, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system", warning=FALSE, cache=T, echo = FALSE}
+```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Electoral System", warning=FALSE, cache=T, echo = FALSE}
 build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
@@
 
-## Log of Lower House Size and Expenditure Per Capita
-
-There are no studies that have per capita expenditure as the dependent variable and log of lower house size as the treatment variable.
-
-## Upper House Size and Expenditure Per Capita
-
-Now we investigate the effect of the upper house size ($K$) on government spending. In the model below, we evaluate the relationship between upper house size and expenditure per capita (ExpPC).
+### Institutional Design Subgroup Analysis
+
+The *law of 1/n* was conceived to explain the expected effect of chamber size on public expenditure.
+However, papers such as @chen2007law demonstrated that the relationship is mediated by the size of the upper chamber.
+Their finding suggests that the institutional design of the legislature influences the empirical predictions in the sample we study.
+To test this possibility, we estimated a subgroup analysis using a binary indicator for institutional design.
+The results may be seen below.
+
+We find little evidence that either unicameral or non-unicameral legislative institutions produce systematically positive effects on expenditure per capita.
+However, the coefficients tend to be weakly positive for unicameral studies, suggesting that there might be a relationship that is masked by the low statistical power.
+
+```{r, fig.width=8, fig.height=12, fig.cap="Subgroup Analysis of Lower Chamber Size and Expenditure Per Capita, Controlling by Institutional Design", warning=FALSE, cache=TRUE, echo = FALSE}
+build_forest_het(aux, aux$coef, aux$VAR, slab = aux$authoryear,
+                 capt = NULL, hetvar = aux$instdesign2)
+```
+
+## Log of Lower Chamber Size and Expenditure Per Capita
+
+There are no studies that have per capita expenditure as the dependent variable
+and log of lower chamber size as the independent variable.
+
+## Upper Chamber Size and Expenditure Per Capita
+
+Now we investigate the effect of the upper chamber size on expenditure per
+capita.
 
@@
 
-```{r, fig.width=9, fig.height=10, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=9, fig.height=10, fig.cap="Effect of Upper Chamber Size on the Per Capita Government Expenditure",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Lower House Size and Log of Expenditure Per Capita
-
-This model estimates the log of per capita expenditure as the dependent variable, and the number of lower house legislators as the treatment variable.
+## Lower Chamber Size and Log of Expenditure Per Capita
+
+Here we test the relationship between log of per capita expenditure
+and the number of lower chamber legislators.
 
@@
 
-```{r, fig.width=8, fig.height=5, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=5, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Log of Lower House Size and Log of Expenditure Per Capita
-
-In this specification, we study the log of per capita expenditure (logExpPC) as a function of the log of lower house size (logN).
+## Log of Lower Chamber Size and Log of Expenditure Per Capita
+
+In this specification, we analyse log of per capita expenditure as a function
+of the log of lower chamber size.
 
@@
 
-```{r, fig.width=8, fig.height=7, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=7, fig.cap="Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3.5, fig.cap="Funnel Plot -- Effect of Log of Lower Chamber Size on Log of Expenditure Per Capita", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Upper House Size and Log of Expenditure Per Capita
-
-No studies related the log of per capita expenditure with the size of upper house ($K$).
-
-## Lower House Size and Expenditure as Percentage of GDP
-
-This model fits the random effects for the percentage of GDP as public expenditure as the main outcome, and the size of lower house as the treatment variable.
+## Upper Chamber Size and Log of Expenditure Per Capita
+
+No studies correlate log of per capita expenditure with the size of upper
+chamber.
+
+## Lower Chamber Size and Expenditure as Percentage of GDP
+
+Here we test how lower house size impact public expenditures as a percentage of
+GDP.
 
@@
 
-```{r, fig.width=8, fig.height=7, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=7, fig.cap="Effect of Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=3.75, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Log of Lower House Size and Expenditure as Percentage of GDP
-
-This meta-regression investigates the percentage of GDP as public expenditure as the dependent variable and the natural logarithm of lower house size (log($N$)) as the treatment variable.
+## Log of Lower Chamber Size and Expenditure as Percentage of GDP
+
+This meta-regression assesses how public expenditure as a percentage of GDP
+varies according to log of lower chamber size.
 
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of log of lower houses size (logN) on log of Per Capita Expenditure (logExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Log Lower Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Upper House Size and Expenditure as Percentage of GDP
-
-This model looks into the effect of upper house size ($K$) on the public expenditure share of the GDP (PCTGDP).
+## Upper Chamber Size and Expenditure as Percentage of GDP
+
+This model measures the effect of upper chamber size on the expenditure as a
+percentage of the GDP.
 
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of Upper Chamber Size on Expenditure as Percentage of GDP",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of upper houses size (K) on the public expenditure share of GDP (PCTGDP)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Upper Chamber Size on Expenditure as Percentage of GDP", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Lower House Size and Expenditure per Capita (IV)
+## Lower Chamber Size and Expenditure per Capita (Instrumental Variables Only)
+
+The model below evaluates only papers that use instrumental variables and
+correlate lower chamber size with public expenditure per capita.
 
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Expenditure Per Capita (IV Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-## Lower House Size and Log of Expenditure per Capita (RDD)
+## Lower Chamber Size and Log of Expenditure Per Capita (Regression Discontinuity Designs Only)
+
+Lastly, we run a meta-analysis with papers that use regression discontinuity
+designs and assess the effect of lower house size on log of expenditure per
+capita.
 
@@
 
-```{r, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on log of Per Capita Expenditure (logExpPC)",warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=4, fig.cap="Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)",warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 
-```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of lower houses size (N) on log of Per Capita Expenditure (ExpPC)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=4, fig.height=4, fig.cap="Funnel Plot -- Effect of Lower Chamber Size on Log Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
 funnel(mod)
@@
 
-In the meta-regressions, we study the effects of a group of moderators on the reported government spending data. We select the following moderators:
+In the meta-regressions, we study the effects of a group of moderators on the
+reported government spending data. We select the following moderators:
 
 1. The independent variable (variable `indepvar2`):
-  - `K`: Upper House Size
-  - `N`: Lower House Size
-  - `logN`: Log of Lower House Size
+  - `K`: Upper Chamber Size
+  - `N`: Lower Chamber Size
+  - `logN`: Log of Lower Chamber Size
 
@@
 
-5. A institution design variable, with:
- - `Unicameral` (e.g., US Municipalities)
- - `Bicameral` (e.g., US States)
- - `Mixed` (e.g., countries with unicameral and bicameral in the same dataset).
+5. A variable describing the papers' institutional design, with:
+ - `Bicameral`: a legislative system comprised of two chambers (e.g. US Federal Senate and House).
+ - `Unicameral`: a system with only a lower chamber (e.g. US Municipalities).
+ - `Mixed`: more than one system in the same sample (cross-country regressions).
 
@@
 
-The results follows below, for the three combinations of dependent variables: Expenditure Per Capita, Log of Expenditure Per Capita, and Expenditure as a Percentage of the GDP.
+The results follows below for the three dependent variables: expenditure per
+capita, log of expenditure per capita, and expenditure as a percentage of GDP.
 
@@
 
-Here we study the expenditure per capita as the main outcome, aggregating all types of independent variables.
+Here we study the impact of our moderators on expenditure per capita.
 
@@
 
-For the meta-regressions of Expenditure Per Capita, we find no significant moderator. We also run the meta-regressions adding all coefficients in the papers. The results follow below:
+For the meta-regressions of expenditure per capita, we find no significant
+moderator. We also run the meta-regressions adding all coefficients included in
+the papers. The results follow below:
 
@@
 ```
-With all coefficients, the results of the effect sizes on the Expenditure Per Capita regressions are the following:
-
-1.  Compared with `K`, models with `N` tend to detect significantly smaller effects.
+
+With all coefficients, the results of the effect sizes on the expenditure per capita regressions are the following:
+
+1.  Compared with upper chamber size, models with lower chamber size tend to detect significantly smaller effects.
 
@@
 
-3.  All other moderators were not significant.
+3.  All other moderators were statistically insignificant.
 
 ## Meta-Regressions for Log of Expenditure Per Capita
+
+The next meta-regression models use log of expenditure per capita as the
+dependent variable.
 
@@
 
-The only significant result points that published papers tend to report a smaller coefficient than unpublished papers.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+The only significant result suggests that published papers tend to report a
+smaller coefficient than unpublished papers.
+
+Below we also run the meta-regressions with all coefficients included in the
+papers.
 
@@
 
-With all coefficients, results of the effect sizes on the Log of Expenditure Per Capita Regressions indicate that in regard to the estimation method, papers that use `PANEL` data or `RDD` designs have smaller effects than articles that employ `OLS` estimations.
-All other results are insignificant.
-
-## Meta-Regressions for Expenditure as a Percentage of the GDP
+When we include all coefficients in the meta-regression, we see that papers
+that use panel data or regression discontinuity designs have smaller effects
+than articles that employ simple OLS regressions. All other results are
+insignificant.
+
+## Meta-Regressions for Expenditure as a Percentage of GDP
+
+Here we conduct the same analysis, but using public spending as a percentage of
+GDP as our dependent variable.
 
@@
 
-In the meta-regressions of Expenditure as a Percentage of GDP, we found that:
-
-1. Recent papers find smaller effect sizes than older studies.
-
-2. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
-
-Below we also run the meta-regressions adding all coefficients in the papers. The results follow below:
+We find that:
+
+1. Recent papers report smaller effect sizes than older studies.
+
+2. Papers whose models include unicameral legislatures report slightly higher coefficients.
+
+Below, we show the results for our meta-regression when we use our full study sample. The results follow below:
 
@@
 
-With all coefficients, the results of the effect sizes on the Expenditure as a Percentage of GDP regressions are the following:
+The model indicates that:
 
@@
 
-3. Papers whose samples included both unicameral and bicameral legislatures report significantly lower coefficients.
-
-# Robustness: Meta-Regressions (All Coefficients)
-
-In this section, we aggregate all the coefficients and run a multivariate meta-regression, controlling for:
-
-1. The type of the dependent variable in the study (expenditure per capita, log of the expenditure per capita, and share of government expenditure in the GDP).
-
-2. The type of the independent variable in the study (lower house size, upper house size, or log of lower house size).
+3. Papers whose models included unicameral legislatures report significantly higher coefficients.
+
+# Meta-Regressions (All Coefficients)
+
+Here we aggregate all the papers in our sample and run a multivariate meta-regression, controlling for:
+
+1. The type of the dependent variable in the study (expenditure per capita, log
+   expenditure per capita, and expenditure as percentage of GDP).
+
+2. The type of the independent variable in the study (lower chamber size, upper
+   chamber size, or log of lower chamber size).
 
@@
 
-The results follow below, and show null effects for all variables except for Unicameral institutional designs.
+The results follow below, and show null effects for all variables except for unicameral institutional designs.
 
@@
 ```
-In the restricted model, with only the main coefficients in the selected papers, only Unicameralism has a positive, significant effect.
-We also run the meta-regressions adding all coefficients in the papers.
-The results follow below:
+
+In the restricted sample, which included only the main coefficients in the selected papers, unicameralism has a positive, significant effect.
+Also, papers that employ regression discontinuity design tend to have a negative effect, significant at the 10% level.
+We also run the same meta-regression with every coefficient reported in all papers.
+The results are:
 
@@
 ```
-In the full model, we can see that:
-
-1. Coefficients from non-majoritarian systems are significantly lower than those found in purely majoritarian systems.
-
-2. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and `RDD` report significantly smaller coefficients.
-
-3. Evidence from unicameral systems presents significantly larger effect sizes.
-
-4. All other moderators are insignificant.
+In the full model, we see that:
+
+1. Compared with papers that employ `OLS`, those that use `PANEL`, `IV` and
+   `RDD` report significantly smaller coefficients.
+
+2. Evidence from unicameral systems presents significantly larger effect sizes.
+
+3. All other moderators are insignificant.

### 2021-06-01 article/article.Rmd
changes to appendix, article, R script

@@
 However, recent studies have questioned the validity of the theory.
-In this letter, we estimate the first meta-analysis of the relationship between the number of legislators and public spending.
+In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\".
 Based on a sample of 30 articles, we find no robust evidence for the effect of legislature size on government budgets.
 Yet the aggregate results show significant heterogeneity.
-While earlier studies provide moderate support for the \"law of $1/n$\", papers using causal inference methods consistently find a negative relationship between seats and spending.
-The available evidence also indicates that proportional representation and mixed voting systems are no more likely to overspend than majoritarian ones."
+We find moderate support for the \"law of $1/n$\" in unicameral legislatures and in the upper house, but panel/fixed-effects models and regression discontinuity designs reduce public spending estimates.
+Our results also indicate that proportional representation systems are no more likely to overspend than majoritarian ones."
 abstractspacing: double
@@
 \vspace{.3cm}
-\includegraphics[width=1\linewidth, height=7.5cm]{../graphs/graph2.pdf}
+\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
 \label{fig:plots2}
@@
              "Method: RDD",
+             "Legislature: Mixed",
              "Legislature: Unicameral"), 
@@
                        "methodRDD",
-                       "instdesign2Unicameral"))
+                       "instdesignMixed",
+                       "instdesignUnicameral"))
   dfr <- left_join(aux, dfr) %>%
@@
 
-# Expenditure per capita - Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear,
-            control=list(maxiter=1000))
-
-res[[1]] <- extract_coefs(mod, "ExpPC")
-
-# Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
-
-# Log of Expenditure per capita - Restricted
-mod <- rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-res[[3]] <- extract_coefs(mod, "logExpPC")
-
-# Log of Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
-
-## Expenditure as percentage GDP -- Restricted
-mod <-  rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-              sparse = TRUE,
-              tdist = TRUE,
-              subset = dat$depvar2=='PCTGDP',
-              slab = dat$authoryear)
-
-res[[5]] <- extract_coefs(mod, "PCTGDP")
-
-## Expenditure as percentage GDP -- Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-            subset = fulldat$depvar2=='PCTGDP',
-            slab = fulldat$authoryear)
-
-res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")
-
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = dat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = dat$authoryear)
-
-res[[7]] <- extract_coefs(mod, "Full Model")
-
-mod <- rma.mv(yi = coef,
-              V = VAR,
-              data = fulldat,
-              method = "REML",
-              random = ~ 1 | id_level1/id_level2, 
-              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign2,
-              test = "knha",
-              tdist = TRUE,
-              sparse = TRUE,
-              slab = fulldat$authoryear)
-
-res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
 gcf <- function(mod, pos) {
@@
 gcf2 <- function(mod, pos) {
-  # round(res[[3]][2,3],3)`)`r strep(res[[3]][2,5])`
   x <- mod$se[pos]
@@
 }
+
+# Expenditure per capita - Restricted
+mod <-  rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+            subset = dat$depvar2=='ExpPC',
+            slab = dat$authoryear,
+            control=list(maxiter=1000))
+
+res[[1]] <- extract_coefs(mod, "ExpPC")
+
+# Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+            subset = fulldat$depvar2=='ExpPC',
+            slab = fulldat$authoryear)
+
+res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
+
+# Log of Expenditure per capita - Restricted
+mod <- rma(yi = coef,
+              sei = SE,
+              data = dat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+            subset = dat$depvar2=='logExpPC',
+            slab = dat$authoryear)
+
+res[[3]] <- extract_coefs(mod, "logExpPC")
+
+# Log of Expenditure per capita - Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+            subset = fulldat$depvar2=='logExpPC',
+            slab = fulldat$authoryear)
+
+res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
+
+## Expenditure as percentage GDP -- Restricted
+mod <-  rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              sparse = TRUE,
+              tdist = TRUE,
+              subset = dat$depvar2=='PCTGDP',
+              slab = dat$authoryear)
+
+res[[5]] <- extract_coefs(mod, "PCTGDP")
+
+## Expenditure as percentage GDP -- Extended
+mod <- rma(yi = coef,
+              sei = SE,
+              data = fulldat,
+              method = "REML",
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+            subset = fulldat$depvar2=='PCTGDP',
+            slab = fulldat$authoryear)
+
+res[[6]] <- extract_coefs(mod, "PCTGDP - All coefs")
+
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              slab = dat$authoryear)
+
+res[[7]] <- extract_coefs(mod, "Full Model")
+
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~depvar2+indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              slab = fulldat$authoryear)
+
+res[[8]] <- extract_coefs(mod, "Full Model - All coefs")
 ```

### 2021-06-01 appendix/script.R

@@ -1,7 +1,7 @@
 #####################################################################################
 ## R code for "The Effect of Legislature Size on Public Spending: A Meta-Analysis" ##
 ## Huzeyfe Alptekin, Danilo Freire, Umberto Mignozzetti, and Catarina Roman        ##
-## May 2021                                                                        ##
+## June 2021                                                                       ##
 #####################################################################################
 
 ## Install and load required packages
@@ -226,7 +226,6 @@ build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, h
   return(p)
 }
 
-
 ## Load datasets
 load("../dataset/dataCoefs.RData")
 
@@ -270,7 +269,7 @@ dat %>%
 dat %>%
   select(id, elecsys2) %>%
   unique() %>%
-  ggplot(aes(x=as.factor(elecsys2))) +
+  ggplot(aes(x = as.factor(elecsys2))) +
     geom_bar(color = "black") +
   labs(x = "Electoral Systems",
        y = "") +
@@ -281,13 +280,13 @@ dat %>%
   select(id, depvar2) %>%
   unique() %>%
   mutate(depvar2 = factor(depvar2,
-                          labels = c("Per Capita Expenditure",
-                                     "Percentage GDP Government Expenditure",
-                                     "Log Per Capita Expenditure"))) %>%
+                          labels = c("Expenditure Per Capita",
+                                     "Expenditure as Percentage GDP",
+                                     "Log Expenditure Per Capita"))) %>%
   ggplot(aes(x = depvar2)) +
     geom_bar(color = "black") +
   labs(x = "",
-       y = "Dependent Variables") +
+       y = "") +
   coord_flip() +
   theme_bw()
 
@@ -295,14 +294,15 @@ dat %>%
 dat %>%
   select(id, indepvar2) %>%
   unique() %>%
-  mutate(indepvar2 = factor(indepvar2, labels = c("K (upper house legislators)",
-                                                  "Log N",
[…]

### 2021-06-01 article/article.Rmd
final corrections

@@
 same direction. One limitation of this finding is that these studies only test
-the impact of lower house size on the natural logarithm of expenditure per
+the impact of lower house size and its natural logarithm on the natural logarithm of expenditure per
 capita, thus it remains unclear whether the results hold with other variables.
@@
 coefficients, we find that unicameralism is associated with higher public
-spending, as predicted by the "law of $1/n$". Since most unicameral
-legislatures in our sample are local governments (municipalities or districts),
-this result supports the predictions of @weingast1981political. Moreover,
-our meta-regressions indicate that larger upper chambers spend more in terms of
+spending, as predicted by the "law of $1/n$". Moreover,
+one of our meta-regressions indicates that larger upper chambers spend more in terms of
 per capita expenditure than lower chambers, a result that also appears in the
-binomial tests. Non-majoritarian voting systems decrease government spending as
-a percentage of GDP, but they do not have a relevant impact on the other
-measures of public expenditure, following the idea that the $1/n$ effect grows
+binomial tests. Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows
 weaker as the empirical cases distance from the original definition of the law.
@@
 first search. The search string contained terms strongly associated with the
-literature on the "law of $1/n$" and was as follows: `("upper chamber size" OR
+literature on the "law of $1/n$" and it was as follows: `("upper chamber size" OR
 "lower chamber size" OR "council size" OR "parliament size" OR "legislature
@@
 Switzerland (`r as.numeric(table(unique(dat[,c('id','locationISO')])$locationISO)[which(names(table(unique(dat[,c('id','locationISO')])$locationISO))=='CHE')])`).
-Eight articles use cross-national data and analyse from 2 to 110
+Seven articles use cross-national data and analyse from 2 to 110
 countries. Early studies used OLS and panel data methods to estimate the
-results, while studies from 2012 onward have also applied causal inference
+results, while studies from 2005 onward have also applied causal inference
 models such as instrumental variables and regression discontinuity designs to
@@
 independent variables of interest\footnote{The papers that used more than one
-dependent or independent variable of interest are \citet{baqir1999districts,
-bjedov2014impact, bradbury2001legislative, chen2007law, crowley2019law,
-erler2007termlimits, gilligan2001fiscal, lee2016supermajority, lee2018court,
+dependent or independent variable of interest are \citet{bjedov2014impact, bradbury2001legislative, chen2007law, crowley2019law,
+erler2007termlimits, gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court,
 maldonado2013legislatures, primo2006stop, ricciuti2003trading,
@@
 the accuracy of the results. More information about the multilevel models can
-be found in Section H of the Supplementary Material.
+be found in Section H.1 of the Supplementary Material.
 
@@
              "Year",
+             "Published",
              "Elecsys: Non-Majoritarian",
-             "Published",
              "Method: Panel",
@@
   if(!is.na(x)) {
-    return(paste0(round(x, digits = 3), strep(y)))
+    return(paste0(format(round(x, digits = 3), nsmall = 3), strep(y)))
   } else {
@@
   if(!is.na(x)) {
-    return(paste0('(', round(x, digits = 3), ')'))
+    return(paste0('(', format(round(x, digits = 3), nsmall = 3), ')'))
   } else {
@@
 # Expenditure per capita - Restricted
-mod <-  rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-            subset = dat$depvar2=='ExpPC',
-            slab = dat$authoryear,
-            control=list(maxiter=1000))
-
-res[[1]] <- extract_coefs(mod, "ExpPC")
-
-# Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-            subset = fulldat$depvar2=='ExpPC',
-            slab = fulldat$authoryear)
-
-res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
-
-# Log of Expenditure per capita - Restricted
-mod <- rma(yi = coef,
-              sei = SE,
-              data = dat,
-              method = "REML",
-              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-            subset = dat$depvar2=='logExpPC',
-            slab = dat$authoryear)
-
-res[[3]] <- extract_coefs(mod, "logExpPC")
-
-# Log of Expenditure per capita - Extended
-mod <- rma(yi = coef,
-              sei = SE,
-              data = fulldat,
-              method = "REML",
-              mods = ~ ~indepvar2+year+published+elecsys2+method+instdesign,
-              test = "knha",
-            subset = fulldat$depvar2=='logExpPC',
-            slab = fulldat$authoryear)
-
-res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
-
-## Expenditure as percentage GDP -- Restricted
 mod <- rma.mv(yi = coef,
@@
               tdist = TRUE,
+              subset = dat$depvar2=='ExpPC',
+              slab = dat$authoryear)
+
+res[[1]] <- extract_coefs(mod, "ExpPC")
+
+# Expenditure per capita - Extended
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              subset = fulldat$depvar2=='ExpPC',
+              slab = fulldat$authoryear)
+
+res[[2]] <- extract_coefs(mod, "ExpPC - All coefs")
+
+# Log of Expenditure per capita - Restricted
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              subset = dat$depvar2=='logExpPC',
+              slab = dat$authoryear)
+
+res[[3]] <- extract_coefs(mod, "logExpPC")
+
+# Log of Expenditure per capita - Extended
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = fulldat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
+              subset = fulldat$depvar2=='logExpPC',
+              slab = fulldat$authoryear)
+
+res[[4]] <- extract_coefs(mod, "logExpPC - All coefs")
+
+## Expenditure as percentage GDP -- Restricted
+mod <- rma.mv(yi = coef,
+              V = VAR,
+              data = dat,
+              method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
+              mods = ~indepvar2+year+published+elecsys2+method+instdesign,
+              test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
               subset = dat$depvar2=='PCTGDP',
@@
 ## Expenditure as percentage GDP -- Extended
-mod <- rma(yi = coef,
-              sei = SE,
+mod <- rma.mv(yi = coef,
+              V = VAR,
               data = fulldat,
               method = "REML",
+              random = ~ 1 | id_level1/id_level2, 
               mods = ~indepvar2+year+published+elecsys2+method+instdesign,
               test = "knha",
+              tdist = TRUE,
+              sparse = TRUE,
             subset = fulldat$depvar2=='PCTGDP',
@@
 %
-Non-Majoritarian & 
+Published: Yes & 
 `r gcf(res[[1]], 5)` & `r gcf(res[[2]], 5)` & 
@@
 %
-Published: Yes & 
+Non-Majoritarian & 
 `r gcf(res[[1]], 6)` & `r gcf(res[[2]], 6)` & 
@@
 Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$.
-Blank cells mean that there is no sufficient data to estimate the paramater.}}
+Blank cells mean that there is no sufficient data to estimate the parameter.}}
 \end{minipage}
@@
 capita as the dependent variable. Among the coefficients in the restricted
-sample, those in published studies are significantly smaller than those in
+sample, those in published studies tend to be smaller than those in
 working papers\footnote{We find no evidence of publication bias in our models.
@@
 Supplementary Material.}. Another two moderators are negatively associated with
-the outcome in our larger study pool. They both refer to estimation methods.
+the outcome in our larger coefficient pool. They both refer to estimation methods.
 Studies that employ panel/fixed effects or regression discontinuity designs
@@
 
-Three variables are statistically significant in the third set of
+Three estimates are statistically significant in the third set of
 meta-regressions, which include public expenditure as a percentage of GDP as
@@
 report significantly lower coefficients than those that analyse bicameral
-legislatures exclusively. Non-majoritarian electoral systems are also
-associated with lower levels of public spending, which may be justified since
-the "law of $1/n$" was conceived for majoritarian voting. These latter results,
-however, do not replicate in the first set of estimations.
+legislatures exclusively.
+Non-majoritarian electoral systems, a category that encompasses proportional representation and mixed systems, may have a positive effect on the "law of $1/n$", but the estimate only borders on statistical significance.
 
@@
 designs both significantly decrease the $1/n$ effect. Instrumental variable
-models follow along these lines. Additionally, non-majoritarian voting
-constituencies appear once again as settings where the "law of $1/n$" becomes
-weaker.
+models follow along these lines. Non-majoritarian electoral systems are also
+significantly associated with lower levels of public spending, which may be justified since
+the "law of $1/n$" was conceived for majoritarian voting. These latter results,
+however, do not replicate in the other sets of estimations.
 

### 2021-06-01 appendix/appendix.Rmd
anonymizes documents

@@
        | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
-author:
-- "Huzeyfe Alptekin[^huzeyfe]"
-- "Danilo Freire[^danilo]"
-- "Umberto Mignozzetti[^umberto]"
-- "Catarina Roman[^catarina]"
 date: \today
@@
 ---
-
-[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^catarina]: PhD Student, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 

### 2021-06-01 article/article.Rmd
anonymizes documents

@@
         | A Meta-Analysis
-author: 
-  - Huzeyfe Alptekin[^huzeyfe]
-  - Danilo Freire[^danilo]
-  - Umberto Mignozzetti[^umberto]
-  - Catarina Roman[^catarina]
 date: \today
-thanks: "The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback.
-We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
-Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>.
-We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
 abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures.
@@
 ```
-
-[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
-
-[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <danilofreire@gmail.com>, <https://danilofreire.github.io>.
-
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
-
-[^catarina]: PhD Student, Department of Political Science, University of California San Diego, <catarinamroman@gmail.com>, <http://catarinaroman.github.io>.
 

### 2021-06-01 appendix/script.R

@@ -1,6 +1,5 @@
 #####################################################################################
 ## R code for "The Effect of Legislature Size on Public Spending: A Meta-Analysis" ##
-## Huzeyfe Alptekin, Danilo Freire, Umberto Mignozzetti, and Catarina Roman        ##
 ## June 2021                                                                       ##
 #####################################################################################
 

### 2021-09-09 appendix/appendix.Rmd
descrip stats moderators, reg coeff dv

@@
 
-# Estimation of the 
+# Estimation of the heterogeneous effects
 estim_het <- function(dat, yi, v, random, slab, hetvar = NULL) {
@@
 
+export2md2<-function(x, which.table="descr", nmax=TRUE, header.labels=c(),
+                    caption=NULL, format="html", width=Inf,
+                    strip=FALSE, first.strip=FALSE, background="#D2D2D2",
+                    size=NULL, landscape=FALSE,
+                    header.background=NULL, header.color=NULL,
+                    position="center", ...){
+
+  trim <- function(x){
+    x <- gsub("^[ ]+","",x)
+    x <- gsub("[ ]+$","",x)
+    x
+  }
+
+  prepare <- function (x, nmax, header.labels)
+    {
+
+        # x <- tab[1:3]
+        # nmax <- TRUE
+        # header.labels <- c()
+        # names(attributes(x))
+
+        show.all <- attr(x, "show.all")
+        show.descr <- attr(x, "show.descr")
+        groups <- attr(x, "groups")
+        ny <- attr(x, "ny")
+        all.last <- attr(x, "all.last")
+
+        varnames <- attr(x, "varnames")
+        nr <- attr(x, "nr")
+        desc <- x$desc
+        avail <- x$avail
+        nmax.pos <- attr(x, "nmax.pos")
+        nmax.avail.pos <- NULL
+        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- integer(0)
+        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- nmax.pos[[2]] + 1
+        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- 1
+        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- c(1, nmax.pos[[2]])
+        if (length(nmax.avail.pos) > 0 && nmax) {
+            Nmax <- apply(avail[, nmax.avail.pos, drop = FALSE],2, function(x) max(as.double(x)))
+        } else {
+            Nmax <- NULL
+            nmax <- FALSE
+        }
+
+        dd.pos <- attr(x, "dd.pos")
+        j <- 1
+        table1 <- NULL
+        if (!is.null(attr(x, "caption")))
+            cc <- character(0)
+        for (i in 1:length(varnames)) {
+            if (nr[i] == 1) {
+                t.i <- desc[j, , drop = FALSE]
+            } else {
+                t.i <- rbind(rep(NA, ncol(desc)), desc[j:(j + nr[i] -
+                                                              1), , drop = FALSE])
+                rownames(t.i)[1] <- paste(varnames[i], ":", sep = "")
+                rownames(t.i)[-1] <- sub(varnames[i], "", rownames(t.i)[-1], fixed = TRUE)
+                rownames(t.i)[-1] <- sub(": ", "    ", rownames(t.i)[-1])
+                if (length(dd.pos) < ncol(t.i)) {
+                    t.i[1, -dd.pos] <- t.i[2, -dd.pos]
+                    t.i[2, -dd.pos] <- NA
+                }
+            }
+            table1 <- rbind(table1, t.i)
+            j <- j + nr[i]
+            if (!is.null(attr(x, "caption"))) {
+                if (attr(x, "caption")[[i]] == "")
+                    cc <- c(cc, rep("", NROW(t.i)))
+                else cc <- c(cc, attr(x, "caption")[[i]], rep("",
+                                                              NROW(t.i) - 1))
+            }
+        }
+        if (ncol(table1) == 0) table1 <- table1[-1, ]
+        if (nmax) table1 <- rbind(colnames(table1), c(paste("N=", Nmax, sep = ""), rep("", ncol(table1) - length(Nmax))), table1) else table1 <- rbind(colnames(table1), table1)
+        table1 <- ifelse(is.na(table1), "", table1)
+        if (length(header.labels)==6 && is.null(names(header.labels))){
+            names(header.labels)<-c("all","p.overall","p.trend","ratio","p.ratio","N")
+        }
+        if ("all"%in%names(header.labels)){
+            ww.all<-grep("^\\[ALL\\]",trim(table1[1,]))
+            if (length(ww.all)>0){
+                ww.all<-ww.all[1]
+                table1[1,ww.all]<-header.labels["all"]
+            }
+        }
+        if ("p.overall"%in%names(header.labels)){
+            ww.p.overall<-which(table1[1,]=="p.overall")
+            if (length(ww.p.overall)>0){
+                ww.p.overall<-rev(ww.p.overall)[1]
+                table1[1,ww.p.overall]<-header.labels["p.overall"]
+            }
+        }
+        if ("p.trend"%in%names(header.labels)){
+            ww.p.trend<-which(table1[1,]=="p.trend")
+            if (length(ww.p.trend)>0){
+                ww.p.trend<-rev(ww.p.trend)[1]
+                table1[1,ww.p.trend]<-header.labels["p.trend"]
+            }
+        }
+        if ("ratio"%in%names(header.labels)){
+            ww.ratio<-which(table1[1,]%in%c("OR","HR"))
+            if (length(ww.ratio)>0){
+                ww.ratio<-rev(ww.ratio)[1]
+                table1[1,ww.ratio]<-header.labels["ratio"]
+            }
+        }
+        if ("p.ratio"%in%names(header.labels)){
+            ww.p.ratio<-which(table1[1,]=="p.ratio")
+            if (length(ww.p.ratio)>0){
+                ww.p.ratio<-rev(ww.p.ratio)[1]
+                table1[1,ww.p.ratio]<-header.labels["p.ratio"]
+            }
+        }
+        if ("N"%in%names(header.labels)){
+            ww.N<-which(table1[1,]=="N")
+            if (length(ww.N)>0){
+                ww.N<-rev(ww.N)[1]
+                table1[1,ww.N]<-header.labels["N"]
+            }
+        }
+        table1 <- apply(table1, 2, format, justify = "centre")
+        colnames(table1) <- rep("", ncol(table1))
+
+        table2 <- x[[2]]
+        table2 <- as.matrix(table2)
+        table2 <- ifelse(is.na(table2), "", table2)
+        table2 <- rbind(colnames(table2), table2)
+        table2 <- apply(table2, 2, format, justify = "centre")
+        colnames(table2) <- rep("", ncol(table2))
+
+        # rearrange table 1 and table 2 by putting all column after descriptives by groups.
+        if (all.last & show.all & show.descr & groups){
+            table1[,1:(ny+1)] <- table1[,c(2:(ny+1),1)]
+        }
+        if (all.last){
+            table2[,1:(ny+1)] <- table2[,c(2:(ny+1),1)]
+        }
+
+        # out
+        out <- list(table1 = table1, table2 = table2)
+        if (!is.null(attr(x, "caption"))) attr(out, "cc") <- cc
+        attr(out, "nmax") <- nmax
+        nr <- ifelse(nr>1, nr+1, nr)
+        nr <- cbind(nr, rep(0:1, length(nr))[1:length(nr)])
+        nr <- unlist(apply(nr, 1, function(x) rep(x[2],x[1])))
+        attr(out, "nr") <- nr
+        out
+
+    }
+
+  # compiled.format <- try(rmarkdown::all_output_formats(knitr::current_input())[1],silent=TRUE)
+  #
+  # if (inherits(compiled.format, "try-error") || is.null(compiled.format)){
+  #   warning("you are using export2md out of Rmarkdown context...")
+  # } else {
+  #   if (compiled.format%in%c("html_document","ioslides_presentation","slidy_presentation")) format <- "html"
+  #   if (compiled.format%in%c("pdf_document","beamer_presentation")) format <- "latex"
+  #   if (compiled.format=="word_document") format <- "markdown"
+  # }
+
+  if (missing(format)){
+    format <- NA
+    if (!interactive()){ # execute inside Rmarkdown
+      if (knitr::is_html_output()) format="html"
+      if (knitr::is_latex_output()) format="latex"
+      if (!knitr::is_html_output() & !knitr::is_latex_output()) format="markdown"
+      if (is.na(format)){
+        warning("Unable to identify format -> HTML assigned.")
+        format <- "html"
+      }
+    } else {# execute inside Rmarkdown
+      warning("You are calling export2md outside Rmarkdown without specifying format -> html format is assigned")
+      format <- "html"
+    }
+  }
+
+  extras <- list(...)
+  if (!inherits(x, "createTable"))
+    stop("x must be of class 'createTable'")
+  if (inherits(x, "cbind.createTable"))
+    stop("x cannot be of class 'cbind.createTable'")
+  ww <- charmatch(which.table, c("descr", "avail"))
+  if (is.na(ww))
+    stop(" argument 'which.table' must be either 'descr' or 'avail'")
+
+  if (attr(x,"groups")){
+    y.name.label<-attr(x,"yname")
+  }
+
+  if (!is.null(caption)){
+    if (!is.character(caption))
+      stop(" argument 'caption' must be a character'")
+  } else {
+    if (ww==1){
+      if (attr(x,"groups"))
+        if (inherits(x,"missingTable"))
+          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
+      else
+        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
+      else
+        if (inherits(x,"missingTable"))
+          caption<-"Missingess table"
+        else
+          caption<-"Summary descriptives table"
+    }
+    if (ww==2){
+      if (attr(x,"groups"))
+        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
+      else
+        caption<-"Available data"
+    }
+  }
+  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
+  #pp <- prepare(x, nmax = nmax, header.labels)
+  cc <- unlist(attr(pp, "cc"))
+  if (ww %in% c(1)) {
+    table1 <- pp[[1]]
+    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
+    table1 <- cbind(rownames(table1), table1)
+    align <- c("l", rep("c", ncol(table1)))
+    table1[1, 1] <- " "
+    colnames(table1) <- table1[1, ]
+    colnames(table1)[-1] <- trim(colnames(table1)[-1])
+    table1 <- table1[-1, , drop = FALSE]
+    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
+    #table1 <- table1[-2]
+    #names(table1)[1] <- 'Extended Sample'
+    # N in the second row
+    table1 <- table1[,-3]
+    colnames(table1)[2] <- 'Extended Sample'
+    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
+    if (format=="latex" & strip)
+      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
+    if (format=="latex") caption <- gsub("%","\\\\%",caption)
+    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
+                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
+    ans <- add_indent(ans, grep("^ ",table1[,1]))
+    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
+    # groups
+    if (!is.null(cc)){
+      for (cci in 1:length(cc)){
+        if (cc[cci]!=""){
+          group.label <- cc[cci]
+          inici <- 0
+          final <- 0
+        } else {
+          if (cc[cci-1]!="")
+            group.begin <- cci-1
+          if (cci==length(cc) || cc[cci+1]!=""){
+            group.end <- cci
+            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
+          }
+        }
+      }
+    }
+    if (strip){
+      nr <- attr(pp, "nr")
+      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
+    }
+    if (n.exists){
+      ans <- row_spec(ans, 1, hline_after=TRUE)
+    }
+
+    if (landscape) ans <- landscape(ans)
+    if (format=="latex"){
+      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size=size, position=position)
+      #if (n.exists) ans <- gsub("\\\\midrule", "", ans) # remove lines after N
+      if (n.exists) ans <- gsub("\\\\midrule\n\\\\endfirsthead", "\\\\endfirsthead", ans) # remove lines after N
+      if (strip) ans <- gsub("\\textbackslash{}vphantom\\{\\}", "\\vphantom{}", ans, fixed=TRUE)
+    }
+    if (format=="html"){
+      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width=FALSE, font_size=size, position=position)
+      ans <- row_spec(ans, 0, background=header.background, color=header.color)
+      ans <- row_spec(ans, if (sum(unlist(attr(x, "nmax.pos")))>0) 1 else 0, italic=sum(unlist(attr(x, "nmax.pos")))>0, extra_css = "border-bottom: 1px solid grey")
+    }
+    return(ans)
+  }
+  if (ww %in% c(2)){
+    # table2 <- compareGroups:::prepare(x, nmax = nmax, c())[[2]]
+    table2 <- prepare(x, nmax = nmax, c())[[2]]
+    table2 <- cbind(rownames(table2), table2)
+    if (!is.null(attr(x, "caption"))) {
+      cc <- unlist(attr(x, "caption"))
+      table2[, 1] <- paste("    ", table2[, 1])
+    }
+    table2[1, 1] <- " "
+    align <- c("l", rep("c", ncol(table2)))
+    colnames(table2)[-1] <- trim(table2[1, -1])
+    table2 <- table2[-1, ,drop=FALSE]
+    ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex", longtable=TRUE, ...)
+    # ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex")
+    # groups
+    if (!is.null(cc)){
+      for (cci in 1:length(cc)){
+        if (cc[cci]!=""){
+          group.label <- cc[cci]
+          inici <- 0
+          final <- 0
+        } else {
+          if (cc[cci-1]!="")
+            group.begin <- cci-1
+          if (cci==length(cc) || cc[cci+1]!=""){
+            group.end <- cci
+            ans <- group_rows(ans, group.label, group.begin, group.end)
+          }
+        }
+      }
+    }
+    ans <- add_indent(ans, integer())
+    if (strip) ans <- row_spec(ans, which(rep(0:1, nrow(table2))[1:nrow(table2)]==!first.strip), background = background)
+    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
+    if (landscape) ans <- landscape(ans)
+    if (format=="latex"){
+      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size = size, position=position)
+    }
+    if (format=="html"){
+      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width = FALSE, font_size = size, position=position)
+      ans <- row_spec(ans, 0, background=header.background, color=header.color)
+      ans <- row_spec(ans, 0, italic=FALSE, extra_css = "border-bottom: 1px solid grey")
+    }
+
+    return(ans)
+  }
+}
+
 # Load datasets
@@
 
-In this section, we present the intuition behind the "law of $1/n$", as well as
-the alternative "reverse law of $1/n$" proposed by @primo2008distributive.
+Here we present the intuition behind the "law of $1/n$", as well as the
+alternative "reverse law of $1/n$" proposed by @primo2008distributive.
 
@@
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Extended Sample", "Main Sample")
-aux <- select(fulldat, usemeta2, indepvar2, year, published, method,
-              instdesign, elecsys2) %>%
-  mutate(indepvar2 = recode(indepvar2,
-                            `N` = "Lower Chamber Size",
-                            `K` = "Upper Chamber Size",
-                            `logN` = "Log of Lower Chamber Size"),
-         elecsys2 = recode(elecsys2,
-                           `Non-Maj` = "Non-Majoritarian",
-                           `Maj` = "Majoritarian")) %>%
+levels(fulldat$usemeta2) <- c("Other Coefficients", "Main Sample")
+aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
+              year, published, instdesign) %>%
   rename(`Independent Variables` = indepvar2,
@@
          `Electoral system`      = elecsys2)
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-                        show.p.overall = F, show.all = T),
+aux$`Independent Variables` <- recode(aux$`Independent Variables`,
+                                      `N` = "Lower Chamber Size",
+                                      `K` = "Upper Chamber Size",
+                                      `logN` = "Log of Lower Chamber Size")
+aux$`Electoral system` <- recode(aux$`Electoral system`,
+                                 `Non-Maj` = "Non-Majoritarian",
+                                 `Maj` = "Majoritarian")
+aux <- select(aux, usemeta2, `Independent Variables`, Year, `Published work`, `Estimation method`, `Institutional Design`, `Electoral system`)
+
+aux3 <- descrTable(~.-usemeta2,
+                   aux, y = aux$usemeta2,
+                   show.p.overall = F,
+                   show.all = T)
+export2md2(aux3,
            caption = "Descriptive Statistics of Moderators",
@@
 
-# Meta-Analysis
+# Meta-Analysis (Main Sample)
 
@@
 
-# Meta-Analysis (All Coefficients)
+# Meta-Analysis (Extended Sample)
 
@@
 
-# Meta-Regressions (All Coefficients)
+## Meta-Regressions (All Coefficients)
 
@@
 3. All other moderators are insignificant.
+
+## Comparing Coefficient Sizes and Dependent Variables
+
+Finally, we run a simple linear regression to check whether there are
+significant differences between effect sizes for our dependent variables.
+Although the meta-regressions show that the difference is statistically
+negligible, we can still witness larger or smaller coefficient sizes in
+different models. The results below show that the differences are indeed mostly
+negligible.
+
+```{r, size="footnotesize", echo = FALSE, cache=TRUE}
+aux <- dat
+aux$depvar2 <- factor(aux$depvar2, levels = c('PCTGDP', 'ExpPC', 'logExpPC'))
+summary(lm(coef~depvar2, data = aux))
+```

### 2021-09-09 article/article.Rmd
remove binom tests, edits to table 2 and text

@@
 We find moderate support for the \"law of $1/n$\" in unicameral legislatures and in the upper house, but panel/fixed-effects models and regression discontinuity designs reduce public spending estimates.
-Our results also indicate that proportional representation systems are no more likely to overspend than majoritarian ones."
+Electoral system does not strongly affect the \"law of $1/n$\", although one coefficient indicates that majoritarian systems may be more prone to overspending than others."
 abstractspacing: double
@@
 }
+
+export2md2<-function(x, which.table="descr", nmax=TRUE, header.labels=c(),
+                    caption=NULL, format="html", width=Inf,
+                    strip=FALSE, first.strip=FALSE, background="#D2D2D2",
+                    size=NULL, landscape=FALSE,
+                    header.background=NULL, header.color=NULL,
+                    position="center", ...){
+
+  trim <- function(x){
+    x <- gsub("^[ ]+","",x)
+    x <- gsub("[ ]+$","",x)
+    x
+  }
+
+  prepare <- function (x, nmax, header.labels)
+    {
+
+        # x <- tab[1:3]
+        # nmax <- TRUE
+        # header.labels <- c()
+        # names(attributes(x))
+
+        show.all <- attr(x, "show.all")
+        show.descr <- attr(x, "show.descr")
+        groups <- attr(x, "groups")
+        ny <- attr(x, "ny")
+        all.last <- attr(x, "all.last")
+
+        varnames <- attr(x, "varnames")
+        nr <- attr(x, "nr")
+        desc <- x$desc
+        avail <- x$avail
+        nmax.pos <- attr(x, "nmax.pos")
+        nmax.avail.pos <- NULL
+        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- integer(0)
+        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- nmax.pos[[2]] + 1
+        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- 1
+        if (length(nmax.pos[[1]]) > 0 & length(nmax.pos[[2]]) > 0) nmax.avail.pos <- c(1, nmax.pos[[2]])
+        if (length(nmax.avail.pos) > 0 && nmax) {
+            Nmax <- apply(avail[, nmax.avail.pos, drop = FALSE],2, function(x) max(as.double(x)))
+        } else {
+            Nmax <- NULL
+            nmax <- FALSE
+        }
+
+        dd.pos <- attr(x, "dd.pos")
+        j <- 1
+        table1 <- NULL
+        if (!is.null(attr(x, "caption")))
+            cc <- character(0)
+        for (i in 1:length(varnames)) {
+            if (nr[i] == 1) {
+                t.i <- desc[j, , drop = FALSE]
+            } else {
+                t.i <- rbind(rep(NA, ncol(desc)), desc[j:(j + nr[i] -
+                                                              1), , drop = FALSE])
+                rownames(t.i)[1] <- paste(varnames[i], ":", sep = "")
+                rownames(t.i)[-1] <- sub(varnames[i], "", rownames(t.i)[-1], fixed = TRUE)
+                rownames(t.i)[-1] <- sub(": ", "    ", rownames(t.i)[-1])
+                if (length(dd.pos) < ncol(t.i)) {
+                    t.i[1, -dd.pos] <- t.i[2, -dd.pos]
+                    t.i[2, -dd.pos] <- NA
+                }
+            }
+            table1 <- rbind(table1, t.i)
+            j <- j + nr[i]
+            if (!is.null(attr(x, "caption"))) {
+                if (attr(x, "caption")[[i]] == "")
+                    cc <- c(cc, rep("", NROW(t.i)))
+                else cc <- c(cc, attr(x, "caption")[[i]], rep("",
+                                                              NROW(t.i) - 1))
+            }
+        }
+        if (ncol(table1) == 0) table1 <- table1[-1, ]
+        if (nmax) table1 <- rbind(colnames(table1), c(paste("N=", Nmax, sep = ""), rep("", ncol(table1) - length(Nmax))), table1) else table1 <- rbind(colnames(table1), table1)
+        table1 <- ifelse(is.na(table1), "", table1)
+        if (length(header.labels)==6 && is.null(names(header.labels))){
+            names(header.labels)<-c("all","p.overall","p.trend","ratio","p.ratio","N")
+        }
+        if ("all"%in%names(header.labels)){
+            ww.all<-grep("^\\[ALL\\]",trim(table1[1,]))
+            if (length(ww.all)>0){
+                ww.all<-ww.all[1]
+                table1[1,ww.all]<-header.labels["all"]
+            }
+        }
+        if ("p.overall"%in%names(header.labels)){
+            ww.p.overall<-which(table1[1,]=="p.overall")
+            if (length(ww.p.overall)>0){
+                ww.p.overall<-rev(ww.p.overall)[1]
+                table1[1,ww.p.overall]<-header.labels["p.overall"]
+            }
+        }
+        if ("p.trend"%in%names(header.labels)){
+            ww.p.trend<-which(table1[1,]=="p.trend")
+            if (length(ww.p.trend)>0){
+                ww.p.trend<-rev(ww.p.trend)[1]
+                table1[1,ww.p.trend]<-header.labels["p.trend"]
+            }
+        }
+        if ("ratio"%in%names(header.labels)){
+            ww.ratio<-which(table1[1,]%in%c("OR","HR"))
+            if (length(ww.ratio)>0){
+                ww.ratio<-rev(ww.ratio)[1]
+                table1[1,ww.ratio]<-header.labels["ratio"]
+            }
+        }
+        if ("p.ratio"%in%names(header.labels)){
+            ww.p.ratio<-which(table1[1,]=="p.ratio")
+            if (length(ww.p.ratio)>0){
+                ww.p.ratio<-rev(ww.p.ratio)[1]
+                table1[1,ww.p.ratio]<-header.labels["p.ratio"]
+            }
+        }
+        if ("N"%in%names(header.labels)){
+            ww.N<-which(table1[1,]=="N")
+            if (length(ww.N)>0){
+                ww.N<-rev(ww.N)[1]
+                table1[1,ww.N]<-header.labels["N"]
+            }
+        }
+        table1 <- apply(table1, 2, format, justify = "centre")
+        colnames(table1) <- rep("", ncol(table1))
+
+        table2 <- x[[2]]
+        table2 <- as.matrix(table2)
+        table2 <- ifelse(is.na(table2), "", table2)
+        table2 <- rbind(colnames(table2), table2)
+        table2 <- apply(table2, 2, format, justify = "centre")
+        colnames(table2) <- rep("", ncol(table2))
+
+        # rearrange table 1 and table 2 by putting all column after descriptives by groups.
+        if (all.last & show.all & show.descr & groups){
+            table1[,1:(ny+1)] <- table1[,c(2:(ny+1),1)]
+        }
+        if (all.last){
+            table2[,1:(ny+1)] <- table2[,c(2:(ny+1),1)]
+        }
+
+        # out
+        out <- list(table1 = table1, table2 = table2)
+        if (!is.null(attr(x, "caption"))) attr(out, "cc") <- cc
+        attr(out, "nmax") <- nmax
+        nr <- ifelse(nr>1, nr+1, nr)
+        nr <- cbind(nr, rep(0:1, length(nr))[1:length(nr)])
+        nr <- unlist(apply(nr, 1, function(x) rep(x[2],x[1])))
+        attr(out, "nr") <- nr
+        out
+
+    }
+
+  # compiled.format <- try(rmarkdown::all_output_formats(knitr::current_input())[1],silent=TRUE)
+  #
+  # if (inherits(compiled.format, "try-error") || is.null(compiled.format)){
+  #   warning("you are using export2md out of Rmarkdown context...")
+  # } else {
+  #   if (compiled.format%in%c("html_document","ioslides_presentation","slidy_presentation")) format <- "html"
+  #   if (compiled.format%in%c("pdf_document","beamer_presentation")) format <- "latex"
+  #   if (compiled.format=="word_document") format <- "markdown"
+  # }
+
+  if (missing(format)){
+    format <- NA
+    if (!interactive()){ # execute inside Rmarkdown
+      if (knitr::is_html_output()) format="html"
+      if (knitr::is_latex_output()) format="latex"
+      if (!knitr::is_html_output() & !knitr::is_latex_output()) format="markdown"
+      if (is.na(format)){
+        warning("Unable to identify format -> HTML assigned.")
+        format <- "html"
+      }
+    } else {# execute inside Rmarkdown
+      warning("You are calling export2md outside Rmarkdown without specifying format -> html format is assigned")
+      format <- "html"
+    }
+  }
+
+  extras <- list(...)
+  if (!inherits(x, "createTable"))
+    stop("x must be of class 'createTable'")
+  if (inherits(x, "cbind.createTable"))
+    stop("x cannot be of class 'cbind.createTable'")
+  ww <- charmatch(which.table, c("descr", "avail"))
+  if (is.na(ww))
+    stop(" argument 'which.table' must be either 'descr' or 'avail'")
+
+  if (attr(x,"groups")){
+    y.name.label<-attr(x,"yname")
+  }
+
+  if (!is.null(caption)){
+    if (!is.character(caption))
+      stop(" argument 'caption' must be a character'")
+  } else {
+    if (ww==1){
+      if (attr(x,"groups"))
+        if (inherits(x,"missingTable"))
+          caption<-paste("Missingness table by groups of `",y.name.label,"'",sep="")
+      else
+        caption<-paste("Summary descriptives table by groups of `",y.name.label,"'",sep="")
+      else
+        if (inherits(x,"missingTable"))
+          caption<-"Missingess table"
+        else
+          caption<-"Summary descriptives table"
+    }
+    if (ww==2){
+      if (attr(x,"groups"))
+        caption<-paste("Available data by groups of `",y.name.label,"'",sep="")
+      else
+        caption<-"Available data"
+    }
+  }
+  pp <- compareGroups:::prepare(x, nmax = nmax, header.labels)
+  #pp <- prepare(x, nmax = nmax, header.labels)
+  cc <- unlist(attr(pp, "cc"))
+  if (ww %in% c(1)) {
+    table1 <- pp[[1]]
+    ii <- ifelse(rownames(table1)[2] == "", 2, 1)
+    table1 <- cbind(rownames(table1), table1)
+    align <- c("l", rep("c", ncol(table1)))
+    table1[1, 1] <- " "
+    colnames(table1) <- table1[1, ]
+    colnames(table1)[-1] <- trim(colnames(table1)[-1])
+    table1 <- table1[-1, , drop = FALSE]
+    table1[,2:ncol(table1)] <- apply(table1[,-1,drop=FALSE],2,trim)
+    #table1 <- table1[-2]
+    #names(table1)[1] <- 'Extended Sample'
+    # N in the second row
+    table1 <- table1[,-3]
+    colnames(table1)[2] <- 'Extended Sample'
+    n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
+    if (format=="latex" & strip)
+      table1[((1+n.exists):nrow(table1)),ncol(table1)] <- ifelse(table1[((1+n.exists):nrow(table1)),ncol(table1)]=="", "\\vphantom{}", table1[((1+n.exists):nrow(table1)),ncol(table1)])
+    if (format=="latex") caption <- gsub("%","\\\\%",caption)
+    ans <- knitr::kable(table1, align = align, row.names = FALSE, caption=caption[1], format=format,
+                        booktabs=format=="latex", longtable=TRUE, linesep="", ...)
+    ans <- add_indent(ans, grep("^ ",table1[,1]))
+    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
+    # groups
+    if (!is.null(cc)){
+      for (cci in 1:length(cc)){
+        if (cc[cci]!=""){
+          group.label <- cc[cci]
+          inici <- 0
+          final <- 0
+        } else {
+          if (cc[cci-1]!="")
+            group.begin <- cci-1
+          if (cci==length(cc) || cc[cci+1]!=""){
+            group.end <- cci
+            ans <- group_rows(ans, group.label, group.begin+n.exists, group.end+n.exists)
+          }
+        }
+      }
+    }
+    if (strip){
+      nr <- attr(pp, "nr")
+      ans <- row_spec(ans, which(nr==!first.strip)+n.exists, background = background)
+    }
+    if (n.exists){
+      ans <- row_spec(ans, 1, hline_after=TRUE)
+    }
+
+    if (landscape) ans <- landscape(ans)
+    if (format=="latex"){
+      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size=size, position=position)
+      #if (n.exists) ans <- gsub("\\\\midrule", "", ans) # remove lines after N
+      if (n.exists) ans <- gsub("\\\\midrule\n\\\\endfirsthead", "\\\\endfirsthead", ans) # remove lines after N
+      if (strip) ans <- gsub("\\textbackslash{}vphantom\\{\\}", "\\vphantom{}", ans, fixed=TRUE)
+    }
+    if (format=="html"){
+      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width=FALSE, font_size=size, position=position)
+      ans <- row_spec(ans, 0, background=header.background, color=header.color)
+      ans <- row_spec(ans, if (sum(unlist(attr(x, "nmax.pos")))>0) 1 else 0, italic=sum(unlist(attr(x, "nmax.pos")))>0, extra_css = "border-bottom: 1px solid grey")
+    }
+    return(ans)
+  }
+  if (ww %in% c(2)){
+    # table2 <- compareGroups:::prepare(x, nmax = nmax, c())[[2]]
+    table2 <- prepare(x, nmax = nmax, c())[[2]]
+    table2 <- cbind(rownames(table2), table2)
+    if (!is.null(attr(x, "caption"))) {
+      cc <- unlist(attr(x, "caption"))
+      table2[, 1] <- paste("    ", table2[, 1])
+    }
+    table2[1, 1] <- " "
+    align <- c("l", rep("c", ncol(table2)))
+    colnames(table2)[-1] <- trim(table2[1, -1])
+    table2 <- table2[-1, ,drop=FALSE]
+    ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex", longtable=TRUE, ...)
+    # ans <- knitr::kable(table2, align = align, row.names = FALSE, caption=caption[1], format=format, booktabs=format=="latex")
+    # groups
+    if (!is.null(cc)){
+      for (cci in 1:length(cc)){
+        if (cc[cci]!=""){
+          group.label <- cc[cci]
+          inici <- 0
+          final <- 0
+        } else {
+          if (cc[cci-1]!="")
+            group.begin <- cci-1
+          if (cci==length(cc) || cc[cci+1]!=""){
+            group.end <- cci
+            ans <- group_rows(ans, group.label, group.begin, group.end)
+          }
+        }
+      }
+    }
+    ans <- add_indent(ans, integer())
+    if (strip) ans <- row_spec(ans, which(rep(0:1, nrow(table2))[1:nrow(table2)]==!first.strip), background = background)
+    if (width!=Inf) ans <- column_spec(ans, 1, width = width)
+    if (landscape) ans <- landscape(ans)
+    if (format=="latex"){
+      ans <- kable_styling(ans, latex_options = c("repeat_header"), font_size = size, position=position)
+    }
+    if (format=="html"){
+      ans <- kable_styling(ans, bootstrap_options=c(if (!strip) "striped" else NULL, "condensed"), full_width = FALSE, font_size = size, position=position)
+      ans <- row_spec(ans, 0, background=header.background, color=header.color)
+      ans <- row_spec(ans, 0, italic=FALSE, extra_css = "border-bottom: 1px solid grey")
+    }
+
+    return(ans)
+  }
+}
 ```
@@
 government spending across several dimensions. Our study sample mirrors the
-diversity of the literature. Out of the `r dim(dat)[1]` coefficients
-included in our main analysis, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Significant')])`\% of
-them are positive and statistically significant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Positive Insignificant')])`\%
-are positive and statistically insignificant, `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Insignificant')])`\%
-are negative and statistically insignificant, and `r as.numeric(round(prop.table(table(dat$scoefnd))*100, 1)[which(names(prop.table(table(dat$scoefnd)))=='Negative Significant')])`\% are
-negative and statistically significant. Given the volume and the disparity of
+diversity of the literature. We found studies that present both negative and positive coefficients, often reaching statistical significance in either. Given the volume and the disparity of
 the studies, we employ meta-analysis to summarise the results. Meta-analysis
@@
 
-We run binomial tests and meta-regressions to further evaluate the relationship
-between legislature size and government expenditures. We use binomial tests to
-assess whether the proportions of positive and negative coefficients in our
-sample are statistically different from each other. In the meta-regressions, we
+We run meta-regressions to further evaluate the relationship
+between legislature size and government expenditures. In those analyses, we
 measure the effect of five moderators that capture different sources of
-heterogeneity in the literature. We also construct a series of funnel plots to
+heterogeneity in the literature. In section G of the Supplementary Materials, we use binomial tests to assess whether the proportions of positive and negative coefficients in our
+sample are statistically different from each other. We also construct a series of funnel plots to
 test for publication bias in existing research on the "law of $1/n$"
@@
 fulldat$usemeta2 <- factor(fulldat$usemeta)
-levels(fulldat$usemeta2) <- c("Other coefficients", "Main sample")
+levels(fulldat$usemeta2) <- c("Other coefficients", "Main Sample")
 aux <- select(fulldat, usemeta2, indepvar2, elecsys2, method,
@@
 
-export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2,
-                        show.p.overall = F, show.all = T),
-          caption = "Descriptive statistics of moderators",
+aux3 <- descrTable(~.-usemeta2, 
+                   aux, y = aux$usemeta2,
+                   show.p.overall = F, 
+                   show.all = T)
+export2md2(aux3, 
+           caption = "Descriptive Statistics of Moderators", 
            format  = "latex")
@@
 extra levels to the regular meta-analysis, one including a unique publication
-ID for each paper, and another indicating the data source used in the original
-study. By adding these two levels, we account for within- and between-study
-variation, thus removing these sources of effect size dependency and improving
-the accuracy of the results. More information about the multilevel models can
-be found in Section H.1 of the Supplementary Material.
+ID for each paper, and another building a common index for papers that share
+the same data specifications. By adding these two levels, we account for
+within- and between-study variation, thus removing these sources of effect size
+dependency and improving the accuracy of the results. More information about
+the multilevel models can be found in Section H.1 of the Supplementary
+Material.
 
@@
 The "law of $1/n$" states that more legislators increase government
-expenditure. In this paper, we employ three methods to test the empirical
-validity of that relationship. First, we run binomial z-tests to assess the
-frequency of positive and negative coefficients in our sample. Then, we fit
-nine multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
+expenditure. In this paper, we employ two methods to test the empirical
+validity of that relationship.\footnote{We also run preliminary binomial Z
+tests in section G of the Supplementary Materials.} First, we fit nine
+multilevel meta-analyses using the `meta` [@balduzzi2019perform] and the
 `dmetar` [@dmetar2019] packages for the `R` statistical language [@rstats2019].
-Lastly, we run four sets of meta-regressions to measure the effects of a group
-of moderators on the effect sizes of our study sample. To recapitulate, our
+Then, we run four sets of meta-regressions to measure the effects of a group of
+moderators on the effect sizes of our study sample. To recapitulate, our
 independent variables of interest are lower chamber size, the natural logarithm
@@
 ```
-
-## Binomial Z-Tests
-\label{sub:binomial}
-
-The binomial z-test evaluates whether the majority of the coefficients of our
-independent variables are positive or negative[^binomial]. If increasing the
-number of legislators leads to higher public expending, we should expect most
-coefficients to be positive. Conversely, if the "reverse law of $1/n$" is true,
-our results should indicate that $p < 0.5$, that is, the proportion of positive
-coefficients is lower than 0.5. The null hypothesis here states that the sign
-of the coefficient is equally likely to be positive or negative.
-
-[^binomial]: Since coefficients are either positive or negative, each of them
-can be considered a Bernoulli trial. Thus, the aggregate results for all papers
-follow a Binomial distribution where parameters $n$ equals the number of papers
-and $p$ is the chance of a positive coefficient. The "law of $1/n$" can be
-reformulated as the chance of $p > 0.5$, which facilitates the testing of the
-theory.
-
-We start with lower house size. Our results indicate that there is no
-correlation between the number of legislators in the lower house and public
-expenditure (successes = `r as.numeric(binN$statistic)`, trials = `r as.numeric(binN$parameter)`, p~success~ = `r round(as.numeric(binN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binN$conf.int[1]), 3)`; `r round(as.numeric(binN$conf.int[2]), 3)`], $p$-value = `r round(as.numeric(binN$p.value), 3)`).
-Note that the "law of $1/n$" suggests that there is a positive
-association between both. The binomial test for the natural logarithm of lower
-chamber size also shows a
-non-statistically significant result (successes = `r as.numeric(binlogN$statistic)`, trials = `r as.numeric(binlogN$parameter)`, p~success~ = `r round(as.numeric(binlogN$estimate), 3)`, 95\% CI = [`r round(as.numeric(binlogN$conf.int[1]), 3)`; `r round(as.numeric(binlogN$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binlogN$p.value), 3)`). In contrast, we find a
-positive result for the number of legislators in the upper house, which is
-in line with the mainstream literature (successes = `r as.numeric(binK$statistic)`, trials = `r as.numeric(binK$parameter)`, p~success~ = `r round(as.numeric(binK$estimate), 3)`, 95\% CI = [`r round(as.numeric(binK$conf.int[1]), 3)`; `r round(as.numeric(binK$conf.int[2]), 3)`],
-$p$-value = `r round(as.numeric(binK$p.value), 3)`).
 
@@
 
-We then proceed to the meta-analysis. We matched the house size variables with
+We begin with the meta-analysis. We matched the house size variables with
 our measures of government spending and created a theoretical $3 \times 3$
@@
 \centering
-\caption{Forest plots of the relationship between legislature size and government spending (reduced sample)}
+\caption{Forest plots of the relationship between legislature size and government spending (main sample)}
 \vspace{0.3cm}
@@
 \begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (restricted sample)}
+\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (main sample)}
 \vspace{.3cm}

### 2021-09-09 article/article.Rmd
main paper function

@@
     colnames(table1)[2] <- 'Extended Sample'
+    table1 <- table1[,c(1,3,2)]
     n.exists <- nrow(table1) > 1 && length(grep("^N=", trim(table1[1, 2])))
@@
            format  = "latex")
+
 ```

### 2021-09-10 article/article.Rmd
rewrite abstract, add changes to text

@@
 In this letter, we conduct the first meta-analysis that assesses the generality of the \"law of $1/n$\".
-Based on a sample of 30 articles, we find no robust evidence for the effect of legislature size on government budgets.
-Yet the aggregate results show significant heterogeneity.
-We find moderate support for the \"law of $1/n$\" in unicameral legislatures and in the upper house, but panel/fixed-effects models and regression discontinuity designs reduce public spending estimates.
-Electoral system does not strongly affect the \"law of $1/n$\", although one coefficient indicates that majoritarian systems may be more prone to overspending than others."
+Based on a sample of 30 articles, we find no robust evidence suggesting that legislature size has either a positive or a negative effect on government budgets.
+Yet the aggregate results mask considerable heterogeneity.
+Our findings provide moderate support for the \"law of $1/n$\" in unicameral legislatures and in upper houses, but they also indicate that papers using panel/fixed-effects models or regression discontinuity designs report negative public spending estimates.
+We find only limited evidence that electoral systems impact public spending, what suggests that proportional representation systems may not be more prone to overspending than majoritarian ones."
 abstractspacing: double
@@
 In this letter, we conduct the first meta-analysis that tests the generality of
-the "law of $1/n$". We select `r length(unique(dat$id))` articles that
-use quantitative methods to evaluate the impact of legislature size over
-government spending across several dimensions. Our study sample mirrors the
-diversity of the literature. We found studies that present both negative and positive coefficients, often reaching statistical significance in either. Given the volume and the disparity of
-the studies, we employ meta-analysis to summarise the results. Meta-analysis
-provides a rigorous approach to combine heterogeneous outcomes into a single
-estimation, and it allows scholars to gain valuable insights from the
-aggregated data [@cooper2019handbook; @hedges1985statistical]. Meta-analysis
-can also identify potential sources of study variability, enabling researchers
-to assess threats to external validity and direct future efforts into more
-promising areas of academic inquiry [@doucouliagos2008democracy]. Research
-synthesis methods have been successfully applied in medicine and psychology
-since the 1970s [@glass2015meta], and our work contributes to the burgeoning
-literature that uses meta-analytic methods to understand challenging questions
-in political science [@costa2017responsive; @doucouliagos2008democracy;
-@green2013field; @lau2007effects; @schwarz2020supporting].
-
-We run meta-regressions to further evaluate the relationship
-between legislature size and government expenditures. In those analyses, we
-measure the effect of five moderators that capture different sources of
-heterogeneity in the literature. In section G of the Supplementary Materials, we use binomial tests to assess whether the proportions of positive and negative coefficients in our
-sample are statistically different from each other. We also construct a series of funnel plots to
-test for publication bias in existing research on the "law of $1/n$"
+the "law of $1/n$". We select `r length(unique(dat$id))` articles that use
+quantitative methods to evaluate the impact of legislature size over government
+spending across several dimensions. Our study sample mirrors the diversity of
+the literature. We found articles that present a positive association between
+the number of legislators and public expenditures, others suggesting that such
+relationship is negative, and yet others that claim that there is no
+correlation between them. Given the volume and the disparity of the studies, we
+employ meta-analysis to summarise the results. Meta-analysis provides a
+rigorous approach to combine heterogeneous outcomes into a single estimation,
+and it allows scholars to gain valuable insights from the aggregated data
+[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
+potential sources of study variability, enabling researchers to assess threats
+to external validity and direct future efforts into more promising areas of
+academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
+been successfully applied in medicine and psychology since the 1970s
+[@glass2015meta], and our work contributes to the burgeoning literature that
+uses meta-analytic methods to understand challenging questions in political
+science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
+@lau2007effects; @schwarz2020supporting].
+
+We run meta-regressions to further evaluate the relationship between
+legislature size and government expenditures. In those analyses, we measure the
+effect of five moderators that capture different sources of heterogeneity in
+the literature. In our Supplementary Materials, we also include binomial
+tests to assess whether the proportions of positive and negative coefficients
+are statistically different from each other, as well as funnel plots to test
+for publication bias in existing research on the "law of $1/n$"
 [@easterbrook1991publication; @gerber2001testing].
@@
 same direction. One limitation of this finding is that these studies only test
-the impact of lower house size and its natural logarithm on the natural logarithm of expenditure per
-capita, thus it remains unclear whether the results hold with other variables.
+the impact of lower house size and its natural logarithm on the natural
+logarithm of expenditure per capita, thus it remains unclear whether the
+results hold with other variables.
 
@@
 coefficients, we find that unicameralism is associated with higher public
-spending, as predicted by the "law of $1/n$". Moreover,
-one of our meta-regressions indicates that larger upper chambers spend more in terms of
+spending, as predicted by the "law of $1/n$". Moreover, one of our
+meta-regressions indicates that larger upper chambers spend more in terms of
 per capita expenditure than lower chambers, a result that also appears in the
-binomial tests. Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows
-weaker as the empirical cases distance from the original definition of the law.
-Finally, meta-regression results confirm that regression discontinuity designs
-reduce public spending estimates.
+binomial tests. Overall, non-majoritarian voting systems seem to decrease
+government spending, following the idea that the $1/n$ effect grows weaker as
+the empirical cases distance from the original definition of the law. Finally,
+meta-regression results confirm that regression discontinuity designs reduce
+public spending estimates.
 
@@
 independent variables of interest\footnote{The papers that used more than one
-dependent or independent variable of interest are \citet{bjedov2014impact, bradbury2001legislative, chen2007law, crowley2019law,
-erler2007termlimits, gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court,
+dependent or independent variable of interest are \citet{bjedov2014impact,
+bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
+gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court,
 maldonado2013legislatures, primo2006stop, ricciuti2003trading,
@@
 papers. Here we focus on the results for our restricted sample as we consider
-them more robust, but the findings are nearly identical when we use the extended
-set.
+them more robust, but the findings are nearly identical when we use the
+extended set.
 
@@
 
-Table \ref{tab:regressions} presents the meta-regression results for our restricted
-and extended samples. Each column represents one of the three measures of
-public spending we discuss in this paper, and the last one uses all
+Table \ref{tab:regressions} presents the meta-regression results for our
+restricted and extended samples. Each column represents one of the three
+measures of public spending we discuss in this paper, and the last one uses all
 coefficients. To reduce the risk of false positives in our analyses, we use
@@
 The funnel plots for all estimations are available Sections H and I of the
-Supplementary Material.}. Another two moderators are negatively associated with
+Supplementary Material.}. Two other moderators are negatively associated with
 the outcome in our larger coefficient pool. They both refer to estimation methods.
@@
 recent studies have smaller coefficients than older papers, which stands in
-contrast with the first model. Moreover, institutional design also affects
-outcomes. Papers that use mixed samples of bicameral and unicameral systems
-report significantly lower coefficients than those that analyse bicameral
-legislatures exclusively.
-Non-majoritarian electoral systems, a category that encompasses proportional representation and mixed systems, may have a positive effect on the "law of $1/n$", but the estimate only borders on statistical significance.
+contrast with the first model. Institutional design also affects outcomes.
+Papers that include mixed political systems report significantly lower
+coefficients than those that analyse bicameral exclusively. Non-majoritarian
+electoral systems have a small, positive effect in our extended sample model,
+yet the coefficient is only significant at the 10\% level.
 
@@
 models follow along these lines. Non-majoritarian electoral systems are also
-significantly associated with lower levels of public spending, which may be justified since
-the "law of $1/n$" was conceived for majoritarian voting. These latter results,
-however, do not replicate in the other sets of estimations.
+significantly associated with lower levels of public spending, which may be
+justified since the "law of $1/n$" was conceived for majoritarian voting. These
+latter results, however, do not replicate in the other sets of estimations.
 

### 2021-09-10 appendix/script.R
add descriptive stats mods, reorder table 2, dv test

@@ -1,6 +1,6 @@
 #####################################################################################
 ## R code for "The Effect of Legislature Size on Public Spending: A Meta-Analysis" ##
-## June 2021                                                                       ##
+## September 2021                                                                  ##
 #####################################################################################
 
 ## Install and load required packages
@@ -29,7 +29,7 @@ library("compareGroups"); library(dmetar)
 
 
 ## Auxiliary functions to estimate meta-analysis models
-## and create plots
+## and create plots and tables
 
 # Broom the multilevel model
 broom_mod <- function(mod, subgroup = FALSE) {
@@ -225,6 +225,335 @@ build_forest_het <- function(dat, coef, v, slab, capt, lsize = 22, ttl = NULL, h
   return(p)
 }
 
+# Export compareGroups table to Markdown and LaTeX
+export2md2<-function(x, which.table="descr", nmax=TRUE, header.labels=c(),
+                    caption=NULL, format="html", width=Inf,
+                    strip=FALSE, first.strip=FALSE, background="#D2D2D2",
+                    size=NULL, landscape=FALSE,
+                    header.background=NULL, header.color=NULL,
+                    position="center", ...){
+
+  trim <- function(x){
+    x <- gsub("^[ ]+","",x)
+    x <- gsub("[ ]+$","",x)
+    x
+  }
+
+  prepare <- function (x, nmax, header.labels)
+    {
+
+        # x <- tab[1:3]
+        # nmax <- TRUE
+        # header.labels <- c()
+        # names(attributes(x))
+
+        show.all <- attr(x, "show.all")
+        show.descr <- attr(x, "show.descr")
+        groups <- attr(x, "groups")
+        ny <- attr(x, "ny")
+        all.last <- attr(x, "all.last")
+
+        varnames <- attr(x, "varnames")
+        nr <- attr(x, "nr")
+        desc <- x$desc
+        avail <- x$avail
+        nmax.pos <- attr(x, "nmax.pos")
+        nmax.avail.pos <- NULL
+        if (length(nmax.pos[[1]]) == 0 & length(nmax.pos[[2]]) == 0) nmax.avail.pos <- integer(0)
[…]

### 2021-09-10 article/article.Rmd
change one word in abstract

@@
 Our findings provide moderate support for the \"law of $1/n$\" in unicameral legislatures and in upper houses, but they also indicate that papers using panel/fixed-effects models or regression discontinuity designs report negative public spending estimates.
-We find only limited evidence that electoral systems impact public spending, what suggests that proportional representation systems may not be more prone to overspending than majoritarian ones."
+We find only limited evidence that electoral systems impact public spending, which suggests that proportional representation systems may not be more prone to overspending than majoritarian ones."
 abstractspacing: double

### 2021-09-10 appendix/appendix.Rmd
final version

@@
        | Supplementary Materials for "The Effect of Legislature Size on Public Spending: A Meta-Analysis"
+author:
+- "Danilo Freire[^danilo]"
+- "Umberto Mignozzetti[^umberto]"
+- "Catarina Roman[^catarina]"
+- "Huzeyfe Alptekin[^huzeyfe]"
 date: \today
@@
 ---
+
+[^danilo]: Senior Lecturer, School of Social and Political Sciences, University of Lincoln, <dfeire@lincoln.ac.uk>, <https://danilofreire.github.io>.
+
+[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+
+[^catarina]: PhD Student, University of California, San Diego, <acroman@ucsd.edu>, <http://catarinaroman.github.io>.
+
+[^huzeyfe]: Independent Researcher, <huzeyfealptekin@gmail.com>.
 

### 2021-09-10 article/article.Rmd
final version

@@
         | A Meta-Analysis
+author:
+- "Danilo Freire[^danilo]"
+- "Umberto Mignozzetti[^umberto]"
+- "Catarina Roman[^catarina]"
+- "Huzeyfe Alptekin[^huzeyfe]"
 date: \today
+thanks: "Freire, Mignozzetti, and Roman contributed equally to all parts of the manuscript.
+Alptekin helped collect data in the early stages of the project.
+The authors thank Guilherme Duarte, Robert Myles McDonnell, and David Skarbek for their constructive feedback.
+We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
+Replication materials are available at <https://github.com/danilofreire/legislature-size-meta-analysis>.
+We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP grant number 2018/00646-1)."
 abstract: "In a seminal article, @weingast1981political argue that there is a positive relationship between legislature size and inefficiency in public expenditures.

### 2021-12-02 appendix/appendix.Rmd
revisions - article intro, appendix, R script

@@
 3.  **Modelling strategies**: Panel data, Standard OLS, IV, RDD.
-4.  **Institutional design**: Unicameral, Bicameral, or the Mixed of both Unicameral and Bicameral.
+4.  **Institutional design**: Unicameral, Bicameral, or a Mix of both Unicameral and Bicameral.
 
@@
                        capt = NULL, lsize = 15,
-                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(subgrouping by the estimation technique)',
+                       ttl = 'Lower Chamber Size and Expenditure per Capita\n(Subgrouping by Estimation Technique)',
                        hetvar = aux$method)
@@
 
-```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Methods", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of Lower Chamber Size x Expenditure Per Capita, Controlling by Estimation Method", warning=FALSE, cache=TRUE, echo = FALSE}
 aux <- dat %>%
@@
 
-```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDD Only)", warning=FALSE, cache=TRUE, echo = FALSE}
+```{r, fig.width=8, fig.height=3, fig.cap="Effect of Lower Chamber Size on Expenditure Per Capita (RDDs)", warning=FALSE, cache=TRUE, echo = FALSE}
 build_forest(mod, NULL)
@@
 f9 <- build_forest(mod, capt = NULL,
-                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(subgrouping by RDD)')
+                       lsize = 15, ttl = 'Lower Chamber Size and Log Expenditure per Capita\n(RDDs)')
 ```
@@
 4. The @egger1997bias test `r ifelse(ranktest(mod)$pval<0.05, 'confirmed', 'rejected')` the hypothesis of publication bias.
-5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. The reason is because in that paper, the author uses Log of Expenditure Per Capita x Log of Legislature Size.
+5. One notable absence in the analysis is the seminar paper by @petterssonlidbom2012size. This is because the author uses Log of Expenditure Per Capita x Log of Legislature Size.
 

### 2021-12-02 article/article.Rmd
revisions - article intro, appendix, R script

@@
 and it allows scholars to gain valuable insights from the aggregated data
-[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also identify
-potential sources of study variability, enabling researchers to assess threats
-to external validity and direct future efforts into more promising areas of
-academic inquiry [@doucouliagos2008democracy]. Research synthesis methods have
-been successfully applied in medicine and psychology since the 1970s
-[@glass2015meta], and our work contributes to the burgeoning literature that
-uses meta-analytic methods to understand challenging questions in political
-science [@costa2017responsive; @doucouliagos2008democracy; @green2013field;
-@lau2007effects; @schwarz2020supporting].
-
-We run meta-regressions to further evaluate the relationship between
-legislature size and government expenditures. In those analyses, we measure the
-effect of five moderators that capture different sources of heterogeneity in
-the literature. In our Supplementary Materials, we also include binomial
-tests to assess whether the proportions of positive and negative coefficients
-are statistically different from each other, as well as funnel plots to test
-for publication bias in existing research on the "law of $1/n$"
-[@easterbrook1991publication; @gerber2001testing].
+[@cooper2019handbook; @hedges1985statistical]. Meta-analysis can also
+identify potential sources of study variability, enabling researchers to assess
+threats to external validity and direct future efforts into more promising
+areas of academic inquiry [@doucouliagos2008democracy]. Research synthesis
+methods have been successfully applied in medicine and psychology since the
+1970s [@glass2015meta], and our work contributes to the burgeoning literature
+that uses meta-analytic methods to understand challenging questions in
+political science [@costa2017responsive; @doucouliagos2008democracy;
+@green2013field; @lau2007effects; @schwarz2020supporting].
 
 Aggregate results indicate that legislature size has no significant impact on
-public spending. All of our main meta-analysis estimates show that the overall
-effect is not statistically different from zero, thus confirming the
-conflicting findings reported by the literature. However, when we look only at
-articles that employ regression discontinuity designs (RDDs), we see that all
-four papers included in our sample suggest that a higher number of legislators
-leads to lower public spending [@debenedetto2018effect; @hohmann2017effect;
-@lewis2019legislature; @petterssonlidbom2012size]. In this regard, it is
-possible that methodological choices partially explain the divergent results
-observed in the literature, as articles that use RDDs consistently point to the
-same direction. One limitation of this finding is that these studies only test
-the impact of lower house size and its natural logarithm on the natural
-logarithm of expenditure per capita, thus it remains unclear whether the
-results hold with other variables.
-
-The meta-regressions provide additional evidence that our study sample is
-highly heterogeneous and that effect sizes differ substantially according to
-study specifications. When using an extended sample of `r dim(fulldat)[1]`
-coefficients, we find that unicameralism is associated with higher public
-spending, as predicted by the "law of $1/n$". Moreover, one of our
-meta-regressions indicates that larger upper chambers spend more in terms of
-per capita expenditure than lower chambers, a result that also appears in the
-binomial tests. Overall, non-majoritarian voting systems seem to decrease
-government spending, following the idea that the $1/n$ effect grows weaker as
-the empirical cases distance from the original definition of the law. Finally,
-meta-regression results confirm that regression discontinuity designs reduce
-public spending estimates.
+public spending. Our main meta-analysis estimates show that the overall effect
+is not statistically different from zero, thus confirming the conflicting
+findings reported by the literature. However, methodological choices partially
+explain these divergent results. When we look only at articles that use
+regression discontinuity designs (RDDs), all four papers included in our sample
+consistently report a negative relationship between a higher number of
+legislators and public expenditures. Our meta-regressions provide further
+evidence that study designs significantly influence the results. Using a sample
+of `r dim(fulldat)[1]` coefficients, we find that articles that use causal
+inference methods report lower effects than those that use OLS, and that
+unicameralism is associated with higher government expenditures.
 
@@
 
-\newpage
-
 \scriptsize
 \begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
-\caption{Papers included in the meta-analysis, ordered by year of appearance}\\
+\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance}\\
+\toprule
+\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
+\tabularnewline
+\midrule
+\endfirsthead
+\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance (\textit{Continued})}\\
 \toprule
@@
 [@cheung2014modeling; @matthes2019meta] in all of our estimations. We add two
-extra levels to the regular meta-analysis, one including a unique publication
-ID for each paper, and another building a common index for papers that share
-the same data specifications. By adding these two levels, we account for
-within- and between-study variation, thus removing these sources of effect size
-dependency and improving the accuracy of the results. More information about
-the multilevel models can be found in Section H.1 of the Supplementary
-Material.
+extra levels to the regular meta-analysis, the first including a unique
+publication ID for each paper, and a second one containing a common index for
+papers that share the same data specifications. By adding these two levels, we
+account for within- and between-study variation, thus removing these sources of
+effect size dependency and improving the accuracy of the results. More
+information about the multilevel models can be found in Section H.1 of the
+Supplementary Material.
 
@@
 
-We begin with the meta-analysis. We matched the house size variables with
-our measures of government spending and created a theoretical $3 \times 3$
-matrix. Out of the nine variable combinations, we found only seven the article
-pool. Our sample does not contain any papers that analyse the relationships
-between log lower chamber size and public expenditure per capita, or between
-upper chamber size and the logarithm of public expenditure per capita.
+We begin with the meta-analysis. We matched the house size variables with our
+measures of government spending and created a theoretical $3 \times 3$ matrix.
+Out of the nine variable combinations, we found only seven in the article pool.
+Our sample does not contain any papers that analyse the relationships between
+log lower chamber size and public expenditure per capita, or between upper
+chamber size and the logarithm of public expenditure per capita.
 
@@
 \centering
-\caption{Forest plots of the relationship between legislature size and government spending (main sample)}
+\caption{Forest Plots of the Relationship between Legislature Size and Government Spending (Main Sample)}
 \vspace{0.3cm}
@@
 \begin{center}
-\caption{Forest plots of the relationship between legislature size and government spending with regression method heterogeneity (main sample)}
+\caption{Forest Plots of the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Main Sample)}
 \vspace{.3cm}
@@
 \begin{table}[htpb]
-\caption{Meta-regression results\label{tab:regressions}}
+\caption{Meta-Regression Results\label{tab:regressions}}
 \scriptsize
@@
 contrast with the first model. Institutional design also affects outcomes.
-Papers that include mixed political systems report significantly lower
-coefficients than those that analyse bicameral exclusively. Non-majoritarian
-electoral systems have a small, positive effect in our extended sample model,
-yet the coefficient is only significant at the 10\% level.
+Papers that include both unicameral and bicameral political systems report
+lower coefficients than those that analyse bicameral exclusively.
+Non-majoritarian electoral systems have a small, positive effect in our
+extended sample model, yet the coefficient is only significant at the 10\%
+level.
 
@@
 "law of $1/n$". Based on a sample of `r length(unique(dat$id))` publications,
-our meta-analyses show that there is no strong evidence that an increase in the
-number of legislators has a significant effect on public expenditures. The
-meta-regressions indicate that study characteristics have a considerable
-influence on reported results. Electoral system affects the relationship
-between legislature size and public expenditure, but the results are not
-replicable in all estimations. In our extended sample, we find that
-unicameralism favours the $1/n$ effect. Publication year generates conflicting
-findings in our models, but recent papers tend to present smaller coefficients
-than older ones. The meta-regressions confirm that modern estimation methods
-such as RDDs and panel/fixed-effects models decrease effects more frequently
-than OLS regressions. In a nutshell, we only find moderate support for the "law
-of $1/n$" in unicameral governments and in the upper house, mostly when authors
-used OLS estimators.
+our meta-analyses show that there is no strong evidence that more legislators
+increase public expenditures. The meta-regressions indicate that methodological
+considerations have a considerable influence on reported results. In our
+extended sample, we find that modern inference methods, such as RDDs, IVs and
+panel data yield lower coefficients than OLS estimators. The models also
+indicate that unicameralism favours the $1/n$ effect. The remaining moderators
+show no consistent effects.
 
@@
 beyond the majoritarian districts framework could produce valuable insights,
-institutional features that are central to the theory cannot be overrun. For
-example, proportional representation (PR) electoral systems allow candidates
-whose constituents are spread across large territories to provide diffused
-public goods and win elections. However, geographically-targeted service
-provision is at the very core of the legislative behaviour that produces the
-"law of $1/n$". Thus, scholars should consider the possible implications of
-these micro-level dynamics when applying the "law of $1/n$" logic to different
-settings.
+institutional features that are central to the theory cannot be disregarded.
+For example, proportional representation (PR) electoral systems allow
+candidates whose constituents are spread across large territories to provide
+diffused public goods and win elections. However, geographically-targeted
+service provision is at the very core of the legislative behaviour that
+produces the "law of $1/n$". Thus, scholars should consider the possible
+implications of these micro-level dynamics when applying the "law of $1/n$"
+logic to different settings.
 
@@
 \url{https://egap.org/our-work/the-metaketa-initiative} for further
-information.}. Here we show that continuously producing and consuming
-meta-analyses is a viable path towards knowledge-building in our discipline.
-Although aggregating observational -- instead of experimental -- data can be
-especially challenging, we believe that research synthesis methods play an
-essential role in advancing our understanding of complex political phenomena.
+information.}. Here we show that meta-analyses provide a viable path towards
+knowledge-building in our discipline. Although aggregating observational --
+instead of experimental -- data can be especially challenging, we believe that
+research synthesis methods play an essential role in advancing our
+understanding of complex political phenomena.
 
@@
 
+\newpage
 \setlength{\parindent}{0cm}

### 2021-12-02 dataset/datasetBuilding.R

@@ -1,8 +1,8 @@
-##################################################################
-## Script: Building the Dataset for Distributive Politics Paper ##
-## Authors: Alptekin, Freire, Mignozzetti, and Roman            ##
-## Last Modified: Mar 22, 2021                                  ##
-##################################################################
+#################################################################################
+## Article: The Effect of Legislature Size on Public Spending: A Meta-Analysis ##
+## Authors: Freire, Mignozzetti, Roman, and Alptekin                           ##
+## Last Modified: 01 Dec, 2021                                                 ##
+#################################################################################
 
 # Needed packages
 rm(list=ls())

### 2022-09-16 article/article.Rmd
creating tex version for publication

@@
     number_sections: yes
-    keep_tex: no
+    keep_tex: yes
     toc: no
@@
 
+# Backmatter Headings
+
+* **Supplementary Materials**: The supplementary materials for this paper can be found at <https://URL_JOURNAL_HERE>.
+
+* **Data Availability Statement**: Replication data for this paper can be found at <https://doi.org/10.7910/DVN/5DEGYP>.
+Replication materials are also available at <https://github.com/danilofreire/legislature-size-meta-analysis>.
+
+* **Acknowledgements**: The authors thank Guilherme Duarte, Cathy Hafer, Robert Myles McDonnell, David Skarbek, and Howard Rosenthal for their constructive feedback.
+We also thank Cedric Antunes, Luis Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their excellent research assistance.
+
+* **Author Contributions**: Freire, Mignozzetti, and Roman contributed equally to all parts of the manuscript. Alptekin helped collect data in the early stages of the project.
+
+* **Financial Support**: We kindly acknowledge funding from the São Paulo State Science Foundation (FAPESP), grant number 2018/00646-1.
+
+* **Competing Interests**: None.
+
 \newpage
@@
 
-\nocite{baskaran2013coalition, bradbury2009spatially, drew2017price,
+\nocite{datasetCite, baskaran2013coalition, bradbury2009spatially, drew2017price,
 erler2007termlimits, fiorino2007legislature, hohmann2017effect,

### 2022-09-16 article/article.tex
creating tex version for publication

% !TEX program = XeLaTeX
\documentclass[11pt,a4paper,]{article}

% Fonts
\usepackage{libertine}
% This is a nice mathfont, it fits well with Libertine
% Comment the line if you want to use a different one
\usepackage[libertine]{newtxmath}
% The default monofont 
% Again, comment the line below if you want to change it
\usepackage[scaled=.95]{inconsolata}

% Add the following packages to support kableExtra
\usepackage{booktabs, longtable, makecell}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{etoolbox}
\usepackage{tocloft}
\usepackage{rotating}
\usepackage{afterpage}
\usepackage{adjustbox}

% Dots in toc
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}

% Colours
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}

% Spacing
\usepackage{setspace}

% Margin
\usepackage[margin=2cm]{geometry}

% Packages I've been using for different reasons...
\usepackage{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}

% UK English
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon

% Penalties
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000

% Hypersetup
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; Umberto Mignozzetti; Catarina Roman; Huzeyfe Alptekin},
      pdfkeywords={distributive politics; law of \(1/n\); legislature
size; meta-analysis; public spending},
  }

% If XeTex, LuaLaTeX, etc
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

% Language

% Bibliography
\usepackage{natbib}
\bibliographystyle{apalike}
\makeatletter
% Remove comma after author
\setcitestyle{aysep={}}
\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
	\patchcmd{\NAT@citex}
	  {\@citea\NAT@hyper@{%
		 \NAT@nmfmt{\NAT@nm}%
		 \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
		   {\@citeb\@extra@b@citeb}%
		 \NAT@date}}
	  {\@citea\NAT@nmfmt{\NAT@nm}%
	   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
	  {}{}
% Patch case where name and year are separated by aysep
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@aysep\NAT@spacechar}{\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@aysep\NAT@spacechar\NAT@hyper@{\NAT@date}}{}{}
% Patch case where name and year are separated by opening bracket
\patchcmd{\NAT@citex}
  {\@citea\NAT@hyper@{%
     \NAT@nmfmt{\NAT@nm}%
     \hyper@natlinkbreak{\NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi}%
       {\@citeb\@extra@b@citeb}%
     \NAT@date}}
  {\@citea\NAT@nmfmt{\NAT@nm}%
   \NAT@spacechar\NAT@@open\if*#1*\else#1\NAT@spacechar\fi\NAT@hyper@{\NAT@date}}
  {}{}
\makeatother

% Listings

% Verbatim

% Tables

% Graphics

% Make links footnotes instead of hotlinks:
%  \setlength{\emergencystretch}{3em}  % prevent overfull lines
 \providecommand{\tightlist}{%
   \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Numbered sections
\setcounter{secnumdepth}{5}
% % % Redefines (sub)paragraphs to behave more like sections
% \ifx\paragraph\undefined\else
% \let\oldparagraph\paragraph
% \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
% \fi
% \ifx\subparagraph\undefined\else
% \let\oldsubparagraph\subparagraph
% \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
% \fi
% \usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

% Spacing
\doublespacing

% Title
\title{The Effect of Legislature Size on Public Spending:\\
A Meta-Analysis\thanks{Freire, Mignozzetti, and Roman contributed
equally to all parts of the manuscript. Alptekin helped collect data in
the early stages of the project. The authors thank Guilherme Duarte,
Robert Myles McDonnell, and David Skarbek for their constructive
feedback. We also thank Cedric Antunes, Luis Castro, Giovanna França,
Julia Oriente, and Lucas Mingardi for their excellent research
assistance. Replication materials are available at
\url{https://github.com/danilofreire/legislature-size-meta-analysis}. We
kindly acknowledge funding from the São Paulo State Science Foundation
(FAPESP grant number 2018/00646-1).}}

% Author
\author{Danilo Freire\footnote{Senior Lecturer, School of Social and
  Political Sciences, University of Lincoln,
  \href{mailto:dfeire@lincoln.ac.uk}{\nolinkurl{dfeire@lincoln.ac.uk}},
  \url{https://danilofreire.github.io}.} \and Umberto
Mignozzetti\footnote{Visiting Assistant Professor, Quantitative Theory
  and Methods Department, Emory University,
  \href{mailto:umberto.mignozzetti@emory.edu}{\nolinkurl{umberto.mignozzetti@emory.edu}},
  \url{http://umbertomig.com}. Corresponding author.} \and Catarina
Roman\footnote{PhD Student, University of California, San Diego,
  \href{mailto:acroman@ucsd.edu}{\nolinkurl{acroman@ucsd.edu}},
  \url{http://catarinaroman.github.io}.} \and Huzeyfe
Alptekin\footnote{Independent Researcher,
  \href{mailto:huzeyfealptekin@gmail.com}{\nolinkurl{huzeyfealptekin@gmail.com}}.}}

% Date
\date{\today}

% Begin document
\begin{document}
\maketitle

% Abstract
\begin{abstract}
\doublespacing \noindent In a seminal article,
\citet{weingast1981political} argue that there is a positive
relationship between legislature size and inefficiency in public
expenditures. Their proposition is currently known as the ``law of
\(1/n\)'' and has been widely debated in political science and public
administration. However, recent studies have questioned the validity of
the theory. In this letter, we conduct the first meta-analysis that
assesses the generality of the ``law of \(1/n\)''. Based on a sample of
30 articles, we find no robust evidence suggesting that legislature size
has either a positive or a negative effect on government budgets. Yet
the aggregate results mask considerable heterogeneity. Our findings
provide moderate support for the ``law of \(1/n\)'' in unicameral
legislatures and in upper houses, but they also indicate that papers
using panel/fixed-effects models or regression discontinuity designs
report negative public spending estimates. We find only limited evidence
that electoral systems impact public spending, which suggests that
proportional representation systems may not be more prone to
overspending than majoritarian ones.
\vspace{.25cm}

\noindent \textbf{Keywords}: distributive politics; law of \(1/n\);
legislature size; meta-analysis; public spending
\vspace{.25cm}

\noindent \textbf{JEL Classification Codes}: H21; H23; H50; H61
\end{abstract}

% Table of Contents
\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\label{sec:intro}

Over the past decades, a large literature has examined the relationship
between legislature size and public expenditure.
\citet{weingast1981political} provided the general framework to analyse
distributive politics. The authors argue that the larger the number of
legislative districts (\(n\)), the smaller the share of tax burden each
one will bear (\(1/n\)), thus legislators have an incentive to overspend
in their districts and transfer the costs to the entire polity. Early
studies that empirically tested the ``law of \(1/n\)'', as the theory is
currently known, indeed found a positive correlation between the number
of legislature seats and different measures of government spending,
although these first results were mainly based on US state legislatures
and the effect was often limited to one house
\citep[e.g.,][]{baqir2002districting, gilligan1995deviations, gilligan2001fiscal}.

Later research, however, has questioned the validity of the ``law of
\(1/n\)''. \citet{primo2008distributive} affirm that, due to spatial
spillovers, a collection of small districts can supply public goods more
efficiently than the central government. The authors conclude that a
``reverse law of \(1/n\)'' may hold, wherein a higher number of
legislators in small constituencies decrease the overall public
spending. Similarly, \citet{primo2006stop} and \citet{chen2007law} find
that lower and upper chambers may have mixed effects on government
spending, while \citet{petterssonlidbom2012size} argues that the impact
of larger chamber sizes is negative when using data from Finland and
Sweden.

Since many empirical tests of the ``law of \(1/n\)'' have produced
conflicting results, scholars have expanded this research agenda and
closely investigated how institutional factors condition the original
formulation of the theory. For instance, authors such as
\citet{crowley2019law} and \citet{pecorino2018supermajority} accurately
point out that collective action problems have been overlooked in the
literature, and recent findings indicate that bicameralism
\citep{maldonado2013legislatures}, intergovernmental competition
\citep{crowley2015local}, redistricting \citep{lee2018court}, and party
ideology \citep{bjedov2014impact} strongly influence the relationship
between seats and spending. Moreover, the literature has increasingly
applied causal inference methods to estimate the effect of the ``law of
\(1/n\)'', and in contrast to previous studies using panel data,
regression discontinuity designs generally indicate that more
legislators decrease public expenditures
\citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}.
In this respect, scholars have long been aware of the theoretical and
empirical limitations of the ``law of \(1/n\)'', and the proliferation
of new studies reflect a conscious attempt to assess the robustness of
the theory.

In this letter, we conduct the first meta-analysis that tests the
generality of the ``law of \(1/n\)''. We select 30 articles that use
quantitative methods to evaluate the impact of legislature size over
government spending across several dimensions. Our study sample mirrors
the diversity of the literature. We found articles that present a
positive association between the number of legislators and public
expenditures, others suggesting that such relationship is negative, and
yet others that claim that there is no correlation between them. Given
the volume and the disparity of the studies, we employ meta-analysis to
summarise the results. Meta-analysis provides a rigorous approach to
combine heterogeneous outcomes into a single estimation, and it allows
scholars to gain valuable insights from the aggregated data
\citep{cooper2019handbook, hedges1985statistical}. Meta-analysis can
also identify potential sources of study variability, enabling
researchers to assess threats to external validity and direct future
efforts into more promising areas of academic inquiry
\citep{doucouliagos2008democracy}. Research synthesis methods have been
successfully applied in medicine and psychology since the 1970s
\citep{glass2015meta}, and our work contributes to the burgeoning
literature that uses meta-analytic methods to understand challenging
questions in political science
\citep{costa2017responsive, doucouliagos2008democracy, green2013field, lau2007effects, schwarz2020supporting}.

Aggregate results indicate that legislature size has no significant
impact on public spending. Our main meta-analysis estimates show that
the overall effect is not statistically different from zero, thus
confirming the conflicting findings reported by the literature. However,
methodological choices partially explain these divergent results. When
we look only at articles that use regression discontinuity designs
(RDDs), all four papers included in our sample consistently report a
negative relationship between a higher number of legislators and public
expenditures. Our meta-regressions provide further evidence that study
designs significantly influence the results. Using a sample of 162
coefficients, we find that articles that use causal inference methods
report lower effects than those that use OLS, and that unicameralism is
associated with higher government expenditures.

\hypertarget{data-and-methods}{%
\section{Data and Methods}\label{data-and-methods}}

We compiled our study sample in three search rounds. In the first round,
we gathered data from three large academic databases (Scopus, Microsoft
Academic, and Google Scholar) and looked for studies that were written
in English and cited \citet{weingast1981political}, as it is the
foundational work in the literature on the ``law of \(1/n\)''. To ensure
that our sample was comparable, we only selected papers that used
quantitative methods to analyse
data\footnote{Since meta-analysis requires a single estimate per observation,
we excluded articles that use interaction terms or quadratic specifications of
our selected variables. Please refer to Section C in the Supplementary Material
for a detailed description of the selection procedure. We also included two
PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-Analyses)
flow diagrammes \citep{liberati2009prisma} showing the number of resulting
papers after each review step.}. After this stage, we identified six
measurements that the literature often employs to quantify government
expenditure and legislature size. For government expenditure, our study
sample uses (i) public expenditure as a share of GDP; (ii) public
expenditure per capita; and (iii) the natural logarithm of public
expenditure per capita as its main variables of interest. In regards to
legislature size, the variables are (i) lower chamber size; (ii) natural
logarithm of lower chamber size; and (iii) upper chamber
size\footnote{There are a few important nuances concerning coding
of these variables. Unicameralism, for example, is captured both by lower
chamber size ($n = 7$) and by log lower chamber size ($n = 5$). Since much of
the literature estimates how institutional designs affect this relationship,
ours and many other articles use both lower and upper chamber sizes as main
explanatory variables. We did not find any article that used the natural
logarithm of upper chamber size in their models.}.

In the second round, we did not require articles to cite
\citet{weingast1981political} and used a keyword-based query on Google
Scholar to broaden the scope of the first search. The search string
contained terms strongly associated with the literature on the ``law of
\(1/n\)'' and it was as follows:
\texttt{("upper\ chamber\ size"\ OR\ "lower\ chamber\ size"\ OR\ "council\ size"\ OR\ "parliament\ size"\ OR\ "legislature\ size"\ OR\ "number\ of\ legislators"\ OR\ "legislative\ size")\ AND\ ("spending"\ OR\ "expenditure"\ OR\ "government\ size")}.
We again restricted the search to articles written in English which
employed quantitative methods. This search added two new results to our
sample \citep{coate2011government, debenedetto2018effect}, but neither
of them included variables beyond the six measures we had previously
identified. In the third search round, we looked into the personal
webpages of every author whom we had already included in our sample. The
purpose of this manual search was to assess whether there was any
working paper or unpublished manuscript that we had missed in the two
former queries. We did not find any new article that satisfied the
inclusion criteria in this search. The full list of excluded records is
available for online consultation in the replication materials.
Combined, the three searches produced a dataset of 30 studies as of the
10\textsuperscript{th} of March 2021. Table \ref{tab:papers} contains
the full list of articles we analyse in this paper.

\scriptsize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.9cm}>{\centering\arraybackslash}p{1.5cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{2.3cm}>{\centering\arraybackslash}p{1cm}>{\centering\arraybackslash}p{2cm}>{\centering\arraybackslash}p{1.1cm}}
\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endfirsthead
\caption{Papers Included in the Meta-Analysis, Ordered by Year of Appearance (\textit{Continued})}\\
\toprule
\raggedright Author(s) & \centering Journal & \centering Country & \centering Dependent Variable & \centering Method & \centering Institutional Design & \centering Electoral System
\tabularnewline
\midrule
\endhead
Stein et al. (1998) & Unpub & Multiple (26) & PCTGDP & OLS & Mixed & NM \\ [0.5ex] 
Baqir (1999) & Unpub & USA & logExpPC & OLS & Unicameral & M \\ [0.5ex] 
Bradbury and Crain (2001) & JPubE & Multiple (37) & ExpPC, PCTGDP & PANEL & Mixed & NM \\ [0.5ex] 
Gilligan and Matsusaka (2001) & NTJ & USA & ExpPC & PANEL & Bicameral & M \\ [0.5ex] 
Baqir (2002) & PC & USA & logExpPC & OLS & Unicameral & M \\ [0.5ex] 
Ricciuti (2003) & Unpub & Multiple (23) & ExpPC & PANEL & Mixed & NM \\ [0.5ex] 
Mukherjee (2003) & CPS & Multiple (110) & PCTGDP & PANEL & Mixed & NM \\ [0.5ex] 
Lledo (2003) & Unpub & BRA & PCTGDP & PANEL & Unicameral & NM \\ [0.5ex] 
Ricciuti (2004) & RivPE & Multiple (75) & PCTGDP & OLS & Mixed & NM \\ [0.5ex] 
Matsusaka (2005) & SPPQ & USA & ExpPC & IV & Bicameral & M \\ [0.5ex] 
Primo (2006) & E\&P & USA & ExpPC & PANEL & Bicameral & M \\ [0.5ex] 
Erler (2007) & PC & USA & ExpPC, PCTGDP & PANEL & Bicameral & M \\ [0.5ex] 
Chen and Malhotra (2007) & APSR & USA & ExpPC & PANEL & Bicameral & M \\ [0.5ex] 
Fiorino and Ricciuti (2007) & PC & ITA & ExpPC & IV & Unicameral & NM \\ [0.5ex] 
MacDonald (2008) & PC & USA & logExpPC & OLS & Unicameral & M \\ [0.5ex] 
Schaltegger and Feld (2009) & JPubE & CHE & ExpPC & PANEL & Unicameral & NM \\ [0.5ex] 
Coate and Knight (2011) & AEJ & USA & logExpPC & OLS & Unicameral & M \\ [0.5ex] 
Pettersson-Lidbom (2012) & JPubE & FIN \& SWE & logExpPC & RDD & Unicameral & NM \\ [0.5ex] 
Baskaran (2013) & EJPE & DEU & ExpPC & IV & Unicameral & NM \\ [0.5ex] 
Maldonado (2013) & SSQ & Multiple (92) & PCTGDP & OLS & Mixed & NM \\ [0.5ex] 
Kessler (2014) & JPE & USA & ExpPC & PANEL & Unicameral & M \\ [0.5ex] 
Bjedov et al. (2014) & PC & CHE & ExpPC, PCTGDP & PANEL & Unicameral & NM \\ [0.5ex] 
Lee (2015) & PC & USA & ExpPC & IV & Bicameral & M \\ [0.5ex] 
Lee (2016) & PC & USA & ExpPC & IV & Bicameral & M \\ [0.5ex] 
Drew and Dollery (2017) & UAR & AUS & logExpPC & PANEL & Unicameral & NM \\ [0.5ex] 
Höhmann (2017) & PC & DEU & logExpPC & RDD & Unicameral & NM \\ [0.5ex] 
Lee and Park (2018) & PC & USA & ExpPC & PANEL & Bicameral & M \\ [0.5ex] 
De Benedetto (2018) & Unpub & ITA & logExpPC & RDD & Unicameral & NM \\ [0.5ex] 
Crowley (2019) & SEJ & USA & ExpPC & PANEL & Bicameral & M \\ [0.5ex] 
Lewis (2019) & SCID & IDN & logExpPC & RDD & Unicameral & NM \\ [0.5ex] 
\bottomrule
\label{tab:papers}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\vspace{-0.5cm}
\scriptsize
\footnotetext{\scriptsize \textbf{Journal:} Unpub $=$ Unpublished, JPE $=$ Journal of Political
Economy, EJPE $=$ European Journal of Political Economy, PC $=$ Public Choice,
JPubE $=$ Journal of Public Economics, JPriE $=$ Journal of Private Enterprise,
APSR $=$ American Political Science Review, SEJ $=$ Southern Economic Journal,
UAR $=$ Urban Affairs Review, SCID $=$ Studies in Comparative International
Development, SSQ $=$ Social Science Quarterly, SPPQ $=$ State Politics and Policy
Quarterly, CPS $=$ Comparative Political Studies, RivPE $=$ Rivista di Politica
Economica, E\&P $=$ Economics and Politics, NTJ $=$ National Tax Journal.}
\footnotetext{\scriptsize \textbf{Country:} Country codes follow the ISO 3166-1 alpha-3
international standard.} 
\footnotetext{\scriptsize \textbf{Dependent Variable:} ExpPC $=$ Per capita expenditure,
logExpPC $=$ Natural logarithm of per capita expenditure, PCTGDP $=$ Expenditure as
a percentage of GDP.}
\footnotetext{\scriptsize \textbf{Method:} OLS $=$ Ordinary least squares, IV $=$ Instrumental
variables, Panel $=$ Panel data/fixed effects, RDD $=$ Regression discontinuity
design.}
\footnotetext{\scriptsize \textbf{Electoral System:} M $=$ Majoritarian, NM $=$ Non-majoritarian (mixed or proportional
representation).} 
\end{minipage} 
\end{longtable}
\normalsize

Our study sample reflects the development of the literature. Although
the ``law of \(1/n\)'' was first formulated in 1981, the empirical
assessment of the theory only started a few years later, as dates of
publishing range from 1998 to 2019. Most studies focus on the United
States (14), but our sample also contains papers on Australia (1),
Brazil (1), Germany (2), Indonesia (1), Italy (2), and Switzerland (2).
Seven articles use cross-national data and analyse from 2 to 110
countries. Early studies used OLS and panel data methods to estimate the
results, while studies from 2005 onward have also applied causal
inference models such as instrumental variables and regression
discontinuity designs to test the relationship between house size and
public spending.

Regarding the dependent variables included in the sample, 16 studies
employ public expenditure per capita, 9 papers use its natural
logarithm, and 8 of them analyse the impact of legislature size on
public expenditures as a percentage of GDP. This indicates that the area
has refined the original definition of the ``law of \(1/n\)'' and tested
the impact of larger legislatures on different measures of government
spending. Our independent variables are lower chamber size (26), the
natural logarithm of lower chamber size (7), and upper chamber size
(12). These variables formed a \(3 \times 3\) table, yet not all
combinations were available in the data. We found no studies that
correlate public expenditure per capita with either upper chamber size
or the natural logarithm of lower house size. Thus, our meta-analysis
contains seven of the nine possible variable combinations.

We also coded five moderators that may help us understand the
heterogeneity in the reported results. We included them in our
meta-regressions alongside an indicator for the type of independent
variable used in the original study. The additional moderators are: 1)
publication year; 2) paper publication in an academic journal; 3)
estimation method; 4) institutional design; 5) electoral system. Since
the literature on the ``law of \(1/n\)'' is notably diverse, we added
only moderators that either refer to important theoretical questions,
such as the effect of the electoral system on public spending, or to
essential characteristics of the publications themselves. Although more
moderators exist in the literature (e.g., data aggregation level), they
do not appear as often as necessary for their inclusion in the
meta-regressions. Table \ref{tab:descriptive} shows the descriptive
statistics of the moderator variables.

\vspace{.5cm}

\footnotesize

\begin{longtable}[t]{lcc}
\caption{\label{tab:descriptive}Descriptive Statistics of Moderators}\\
\toprule
  & Main Sample & Extended Sample\\
\endfirsthead
\caption[]{Descriptive Statistics of Moderators \textit{(continued)}}\\
\toprule
  & Main Sample & Extended Sample\\
\midrule
\endhead

\endfoot
\bottomrule
\endlastfoot
 & N=45 & N=162\\
\midrule
Independent Variables: &  & \\
\hspace{1em}Log of Lower Chamber Size & 7 (15.6\%) & 33 (20.4\%)\\
\hspace{1em}Lower Chamber Size & 26 (57.8\%) & 82 (50.6\%)\\
\hspace{1em}Upper Chamber Size & 12 (26.7\%) & 47 (29.0\%)\\
Year & 2009 (6.54) & 2008 (6.15)\\
Published work: &  & \\
\hspace{1em}No & 6 (13.3\%) & 17 (10.5\%)\\
\hspace{1em}Yes & 39 (86.7\%) & 145 (89.5\%)\\
Estimation method: &  & \\
\hspace{1em}OLS & 9 (20.0\%) & 49 (30.2\%)\\
\hspace{1em}PANEL & 25 (55.6\%) & 83 (51.2\%)\\
\hspace{1em}IV & 7 (15.6\%) & 19 (11.7\%)\\
\hspace{1em}RDD & 4 (8.89\%) & 11 (6.79\%)\\
Institutional Design: &  & \\
\hspace{1em}Bicameral & 17 (37.8\%) & 49 (30.2\%)\\
\hspace{1em}Mixed & 12 (26.7\%) & 50 (30.9\%)\\
\hspace{1em}Unicameral & 16 (35.6\%) & 63 (38.9\%)\\
Electoral system: &  & \\
\hspace{1em}Majoritarian & 22 (48.9\%) & 73 (45.1\%)\\
\hspace{1em}Non-Majoritarian & 23 (51.1\%) & 89 (54.9\%)\\*
\end{longtable}
\normalsize

A key methodological issue we had to address concerns the potential
violation of an important assumption in a meta-analysis, that of effect
size independence
\citep{cheung2014modeling, cheung2019guide, veroniki2016methods}. In our
study sample, authors frequently use the same datasets, and almost all
papers fit more than one regression with similar variables, what
suggests that the assumption above does not hold. We use two procedures
to tackle this problem. First, we created two sets of study coefficients
to reduce the impact of multicollinearity in our estimations. The first
group includes only the most rigorous models from each paper, that is,
those estimated with the largest \(n\), most control variables, and
fixed effects if the authors added them. If the article employed a
regression discontinuity design, we chose the coefficient from the
optimal bandwidth or from the intermediate one. This sample encompasses
45 estimates, as 13 articles analysed two dependent or independent
variables of interest\footnote{The papers that used more than one
dependent or independent variable of interest are \citet{bjedov2014impact,
bradbury2001legislative, chen2007law, crowley2019law, erler2007termlimits,
gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court,
maldonado2013legislatures, primo2006stop, ricciuti2003trading,
ricciuti2004legislatures}.}. Our second sample, in contrast, contains
all the 162 effect sizes reported in the 30 papers. Here we focus on the
results for our restricted sample as we consider them more robust, but
the findings are nearly identical when we use the extended set.

Our second procedure consists of employing multilevel random effect
models \citep{cheung2014modeling, matthes2019meta} in all of our
estimations. We add two extra levels to the regular meta-analysis, the
first including a unique publication ID for each paper, and a second one
containing a common index for papers that share the same data
specifications. By adding these two levels, we account for within- and
between-study variation, thus removing these sources of effect size
dependency and improving the accuracy of the results. More information
about the multilevel models can be found in Section H.1 of the
Supplementary Material.

We use Hedges' \(g\) to calculate effect sizes in our meta-analysis
\citep{hedges1981distribution}. While there are other methods to
standardise coefficients in meta-analytic studies, Hedges' \(g\)
corrects for upward bias in small sample sizes and is considered more
robust than measures such as Cohen's \(d\)
\citep{lakens2013calculating}. We estimate the Standardised Mean
Difference (SMD), which represents the effect size in each study
relative to the variability observed in that study, by extracting the
coefficients and the standard errors from all articles included in our
sample and converting them to Hedges' \(g\). In cases where authors did
not report the standard errors for their estimates, we computed them
using the t-statistic presented in the original tables.

\hypertarget{results}{%
\section{Results}\label{results}}

The ``law of \(1/n\)'' states that more legislators increase government
expenditure. In this paper, we employ two methods to test the empirical
validity of that
relationship.\footnote{We also run preliminary binomial Z
tests in section G of the Supplementary Materials.} First, we fit nine
multilevel meta-analyses using the \texttt{meta}
\citep{balduzzi2019perform} and the \texttt{dmetar} \citep{dmetar2019}
packages for the \texttt{R} statistical language \citep{rstats2019}.
Then, we run four sets of meta-regressions to measure the effects of a
group of moderators on the effect sizes of our study sample. To
recapitulate, our independent variables of interest are lower chamber
size, the natural logarithm of lower chamber size, and upper chamber
size. The dependent variables are public expenditure per capita, the
natural logarithm of public expenditure per capita, and government
expenditure as a percentage of GDP. Since the outcomes have different
scales, we treat them separately in our models.

\hypertarget{meta-analysis}{%
\subsection{Meta-Analysis}\label{meta-analysis}}

\label{sub:Meta-Analysis}

We begin with the meta-analysis. We matched the house size variables
with our measures of government spending and created a theoretical
\(3 \times 3\) matrix. Out of the nine variable combinations, we found
only seven in the article pool. Our sample does not contain any papers
that analyse the relationships between log lower chamber size and public
expenditure per capita, or between upper chamber size and the logarithm
of public expenditure per capita.

Figure \ref{fig:plots} shows the forest plots for our restricted sample,
which includes the 45 main coefficients of the 30 selected
papers.\footnote{Please refer to Sections H and I in the Supplementary
Material for full results regarding both samples.} On the left side of
the plots are the names of the study authors and paper publication year.
For unpublished studies, we included the first year the paper was
available online. The bars in the middle show the reported effect sizes
and the vertical lines indicate their average, weighted by standard
errors. The length of the lines represent the precision of the
estimates. The red line at the bottom of the figures displays the
overall effects plus their respective confidence intervals.

The uppermost row shows the results for lower chamber size in our
restricted sample. In the first model, which correlates lower house and
expenditure per capita, we find a standardised mean difference (SMD) of
0.022 and a standard error of 0.131 (figure 1.1, studies = 16, 95\% CI =
{[}-0.256; 0.299{]}, \(p\)-value = 0.87), so we cannot rule out that the
effect is zero. Indeed, the effect of lower chamber size on the other
two dependent variables is also null in statistical terms. When we
compare lower chamber size with log expenditure per capita, the overall
effect size is -0.031 and the standard error is 0.049 (figure 1.2,
studies = 4, 95\% CI = {[}-0.188; 0.127{]}, \(p\)-value = 0.58). The
impact of larger lower houses on government spending as a percentage of
GDP is also negligible (figure 1.3, studies = 6, SMD = - 0.006, 95\% CI
= {[}-0.0334; 0.021{]}, \(p\)-value = 0.563). The results are virtually
identical when we estimate the meta-analyses using our extended sample,
and all three coefficients are again statistically indistinguishable
from zero.

Next, we present the meta-analyses using the logarithm of lower house
size as an independent variable. The relationship between this variable
and the log of per capita expenditure is positive, but the coefficient
is not significant (figure 1.4, studies = 5, SMD = 0.078, SE = 0.109,
95\% CI = {[}-0.225; 0.381{]}, \(p\)-value = 0.515). The effect of log
lower house size on expenditure as a percentage of the GDP is negative,
but it is again non-statistically significant (figure 1.5, studies = 2,
SMD = -1.576, SE = 2.223, 95\% CI = {[}-29.82; 26.668{]}, \(p\)-value =
0.607). Results in the full sample are also null, and the coefficients
for each dependent variable have the same sign as the restricted sample
-- positive and negative, respectively.

\begin{landscape}
\begin{figure}[!ht]
\centering
\caption{Forest Plots of the Relationship between Legislature Size and Government Spending (Main Sample)}
\vspace{0.3cm}
\includegraphics[width=25cm,height=17cm]{../graphs/graph1.pdf}
\label{fig:plots}
\end{figure}
\end{landscape}

The third set of models uses upper house size as the main independent
variable. We find a positive correlation between this variable and
expenditure per capita (figure 1.6, studies = 9, SMD = 3.658, SE =
4.299, 95\% CI = {[}-6.255; 13.572{]}, \(p\)-value = 0.419), and a
negative relationship with government spending as a percentage of GDP
(figure 1.7, studies = 3, SMD = -0.003, SE = 0.018, 95\% CI = {[}-0.079;
0.074{]}, \(p\)-value = 0.891), yet neither coefficient is statistically
significant. Results are the same in our extended sample.

Taken together, these results yield conservative interpretations.
Besides all average effect sizes not reaching conventional levels of
statistical significance, the studies are also notably heterogeneous.
The \(I^2\) statistic quantifies the degree of heterogeneity among
studies. \citet{higgins2019cochrane} consider any \(I^2\) value above
75\% to indicate high heterogeneity, and the lowest \(I^2\) we find in
the restricted sample is 80.7\% (for the subset of upper chamber size
and per capita expenditure). Additionally, all prediction intervals
encompass zero. Therefore, we cannot reject the null hypothesis that the
effect size is zero in any variable combination.

In a nutshell, we do not find evidence in favour of the ``law of
\(1/n\)''. One reason for this may be the identification strategy
authors use in their models. On the one hand, OLS and panel data models
require too many controls to make units comparable, and they are
vulnerable to omitted variable bias or post-treatment bias
\citep{cinelli2020making, pearl2015conditioning}. On the other hand,
estimation methods such as instrumental variables (IV) and regression
discontinuity designs (RDD) have become popular because of their high
internal validity \citep{angrist2008mostly}. Figure \ref{fig:plots2}
shows the disaggregated effects for two sets of models that employ
causal estimation techniques. They measure the impact of lower house
size on expenditure per capita (left) and on the natural logarithm of
expenditure per capita (right).

\vspace{.5cm}

\begin{figure}[htb]
\begin{center}
\caption{Forest Plots of the Relationship between Legislature Size and Government Spending with Regression Method Heterogeneity (Main Sample)}
\vspace{.3cm}
\includegraphics[width=1\linewidth, height=7.8cm]{../graphs/graph2.pdf}
\label{fig:plots2}
\end{center}
\end{figure}

Papers that employ instrumental variables and panel/fixed-effects models
show somewhat symmetrical distributions. Out of the five papers listed
under IV, two are positive, two are negative, and one is null. In the
plot for panel data, although more studies accumulate negative
coefficients, the positive shifts are more pronounced, so the overall
effect is also null. In contrast, all papers that use regression
discontinuity designs show negative and statistically significant
results. Since only three papers in this model use RDDs\footnote{\citet{petterssonlidbom2012size}
  also uses RDDs but the study is not included in this model as it
  employs log lower chamber size as the independent variable.}, we are
cautious about predicting an overall negative relationship, but they do
indicate that better identification strategies yield a zero-to-negative
impact of legislature size on expenditure, in support of the ``reverse
law of \(1/n\)''.

\hypertarget{meta-regressions}{%
\subsection{Meta-Regressions}\label{meta-regressions}}

\label{sub:regressions}

In this section, we run a series of meta-regressions with six moderators
to account for the heterogeneity across the selected papers. The first
variable indicates whether the study uses lower chamber size, log lower
chamber size, or upper chamber size as a main explanatory variable. We
include separate effect sizes for upper and lower chamber sizes when
papers analysed both. The second variable shows the study publication
year, which we included to capture temporal variation in the study
coefficients. We also add a dummy variable to assess whether published
articles report effect sizes that are higher or lower than those from
working papers. The fourth variable measures whether studies focusing on
non-majoritarian electoral systems report coefficients that are smaller
or larger than those from majoritarian countries. The fifth covariate is
a categorical variable indicating the statistical procedure used in the
original models (panel data, instrumental variables, OLS, or regression
discontinuity design). In our last variable, we separate coefficients
produced from samples of unicameral or bicameral systems, and code
papers that analyse multiple polities with different institutional
designs as ``mixed''.

Table \ref{tab:regressions} presents the meta-regression results for our
restricted and extended samples. Each column represents one of the three
measures of public spending we discuss in this paper, and the last one
uses all coefficients. To reduce the risk of false positives in our
analyses, we use permutation tests to calculate significance levels for
the meta-regressions \citep{higgins2004controlling}. To interpret these
results, the sign of coefficients matters the most. These
meta-regression coefficients can be viewed as representing ``the effect
of the moderator on the \(1/n\) effect''. This means positive
coefficients predict a strengthening of the \(1/n\) effect, and negative
ones predict it will get weaker under that moderator category, when
compared to its reference category. Since we aggregate different types
of independent variables under the same models, the size of the effects
does not accurately translate the scale of variations.

\vspace{0.5cm}

\begin{table}[htpb]
\caption{Meta-Regression Results\label{tab:regressions}}
\scriptsize
\centering
\begin{tabular}{lcccccccc}
\toprule
\midrule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Expenditure Per Capita} & \multicolumn{2}{c}{Log Expenditure Per Capita} & \multicolumn{2}{c}{Gov. Spending \% GDP} & \multicolumn{2}{c}{All Coefficients} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
& Restricted & Extended & Restricted & Extended & Restricted & Extended & Restricted & Extended \\
\midrule
Log of Lower Chamber Size & 
 &  & 
-0.035 & -0.128 & 
-0.047 & -0.033 &
-0.222 & -0.148 \\
 &  &  & 
(0.134) & (0.124) & 
(0.028) & (0.024) & 
(0.144) & (0.090) \\
%
Lower Chamber Size &
-0.779 & -2.590*** & 
 &  & 
-0.009 & 0.002 &
-0.055 & -0.012 \\
 & (1.045) & (0.643) & 
 &  & 
(0.005) & (0.005) & 
(0.067) & (0.013) \\
%
Year & 
0.033 & 0.142** & 
0.000 & -0.005 & 
-0.007** & -0.006*** &
-0.013 & -0.001 \\
& (0.081) & (0.060) & 
(0.012) & (0.010) & 
(0.002) & (0.002) & 
(0.009) & (0.006) \\
%
Published: Yes & 
0.712 & 0.946 & 
-0.167* & 0.009 & 
 &  &
-0.084 & -0.009 \\
& (1.725) & (1.150) & 
(0.058) & (0.045) & 
 &  & 
(0.093) & (0.035) \\
%
Non-Majoritarian & 
0.455 & 0.819 & 
-0.300 & 0.006 & 
0.043 & 0.038* &
-0.082 & -0.190** \\
& (1.814) & (1.181) & 
(0.134) & (0.134) & 
(0.028) & (0.020) & 
(0.142) & (0.086) \\
%
Method: Panel & 
0.491 & -0.361 & 
0.200 & -0.354*** & 
-0.018 & -0.010 &
-0.027 & -0.137*** \\
& (0.975) & (0.977) & 
(0.104) & (0.050) & 
(0.017) & (0.013) & 
(0.114) & (0.032) \\
%
Method: IV & 
 & -0.565 & 
 & -0.052 & 
 &  &
-0.160 & -0.069** \\
&  & (0.894) & 
 & (0.050) & 
 &  & 
(0.190) & (0.034) \\
%
Method: RDD &
 &  & 
 & -0.308*** & 
 &  &
-0.168 & -0.200*** \\
&  &  & 
 & (0.041) & 
 &  & 
(0.147) & (0.036) \\
% 
Inst. Design: Mixed & 
-0.739 & -1.262 & 
 &  & 
-0.074* & -0.058*** &
0.123 & 0.192 \\
& (2.233) & (1.388) & 
 &  & 
(0.033) & (0.015) & 
(0.196) & (0.119) \\
% 
Inst. Design: Unicameral & 
-0.155 & -0.945 & 
 &  & 
 &  &
0.396** & 0.277** \\
& (1.718) & (1.000) & 
 &  & 
 &  & 
(0.162) & (0.115) \\
% 
Intercept & 
-67.291 & -282.761** & 
-0.030 & 10.432 & 
13.621** & 12.496*** &
26.032 & 2.505 \\
& (163.078) & (120.473) & 
(23.652) & (20.215) & 
(3.884) & (3.396) & 
(18.812) & (11.485) \\
\bottomrule
\end{tabular}
\begin{minipage}{\textwidth}
\renewcommand{\footnoterule}{}
\footnotetext{\textbf{Note:} {The restricted and extended samples include 45 and 162 study coefficients, respectively. We report the results from the permutation tests. Reference categories: Independent Variable $=$ Upper House Size; Published $=$ No; Method $=$ OLS, Inst. Design $=$ Bicameral. Significance codes: *** $p < 0.01$; ** $p < 0.05$; * $p < 0.10$. Blank cells mean that there is no sufficient data to estimate the parameter.}}
\end{minipage}
\end{table}

\vspace{0.5cm}

The first two models show the results for public expenditure per capita.
No variable reaches conventional levels of statistical significance in
the restricted sample. In the extended sample, we find that models that
use lower chamber size as an independent variable have lower effects
when compared to upper chamber size. This suggests that an additional
member in the lower house has a smaller impact on public spending than a
member in the upper house. Moreover, the results for the extended sample
point out that recent studies find larger effects than older ones.

The third and fourth columns use the natural logarithm of expenditure
per capita as the dependent variable. Among the coefficients in the
restricted sample, those in published studies tend to be smaller than
those in working
papers\footnote{We find no evidence of publication bias in our models.
The funnel plots for all estimations are available Sections H and I of the
Supplementary Material.}. Two other moderators are negatively associated
with the outcome in our larger coefficient pool. They both refer to
estimation methods. Studies that employ panel/fixed effects or
regression discontinuity designs (RDDs) have lower coefficients for log
expenditure per capita if we take OLS as the reference category.

Three estimates are statistically significant in the third set of
meta-regressions, which include public expenditure as a percentage of
GDP as the dependent variable. Both in our restricted and in our
extended samples, recent studies have smaller coefficients than older
papers, which stands in contrast with the first model. Institutional
design also affects outcomes. Papers that include both unicameral and
bicameral political systems report lower coefficients than those that
analyse bicameral exclusively. Non-majoritarian electoral systems have a
small, positive effect in our extended sample model, yet the coefficient
is only significant at the 10\% level.

The last two columns report meta-regressions that aggregate all selected
studies. In the restricted sample of coefficients, unicameralism has a
positive effect. This result holds for the extended sample as well. When
we regress all 162 coefficients, the effects of estimation methods
become stronger once again. Panel/fixed-effects models and regression
discontinuity designs both significantly decrease the \(1/n\) effect.
Instrumental variable models follow along these lines. Non-majoritarian
electoral systems are also significantly associated with lower levels of
public spending, which may be justified since the ``law of \(1/n\)'' was
conceived for majoritarian voting. These latter results, however, do not
replicate in the other sets of estimations.

The evidence seems to be sensitive to the methodological design. Our
results suggest that the same study samples may produce different
outcomes depending on the response variables scholars decide to analyse.
The broadest aggregation level presented the most insightful results in
dialogue with the literature. The additional legislator in
non-majoritarian legislatures does not increase expenditure as much as
she would if the system were majoritarian. We are also more likely to
witness legislative expenditure growing along with the amount of
representatives in unicameral legislatures rather than in bicameral
systems. This indicates that while the ``law of \(1/n\)'' is not
generalisable, its predicted effects are stronger when the institutional
features of a polity come closer to its original theoretical framework.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\label{sec:discussion}

In this letter, we use meta-analytic methods to assess the generality of
the ``law of \(1/n\)''. Based on a sample of 30 publications, our
meta-analyses show that there is no strong evidence that more
legislators increase public expenditures. The meta-regressions indicate
that methodological considerations have a considerable influence on
reported results. In our extended sample, we find that modern inference
methods, such as RDDs, IVs and panel data yield lower coefficients than
OLS estimators. The models also indicate that unicameralism favours the
\(1/n\) effect. The remaining moderators show no consistent effects.

While the vast literature covering the ``law of \(1/n\)'' builds
important empirical knowledge, we hypothesise that some of the null
findings that we present here are due to difficulties in testing
important assumptions behind the theory itself. For instance, the theory
assumes three types of costs for legislative public good provision,
namely expenses for the constituency, expenses outside the constituency,
and externalities. The main issue in assessing their actual impact is
that externalities such as shifts in prices of local firms, for example,
are extremely hard to measure. Thus, it is very difficult to properly
translate the mechanism to empirical data, making it is easy to
accidentally distort results. Therefore, it should not come as a
surprise that slight differences in political features generate highly
heterogeneous results.

In this sense, the empirical cases in the literature may not always be
the most fortunate testing ground for the ``law of \(1/n\)''. While we
believe that moving beyond the majoritarian districts framework could
produce valuable insights, institutional features that are central to
the theory cannot be disregarded. For example, proportional
representation (PR) electoral systems allow candidates whose
constituents are spread across large territories to provide diffused
public goods and win elections. However, geographically-targeted service
provision is at the very core of the legislative behaviour that produces
the ``law of \(1/n\)''. Thus, scholars should consider the possible
implications of these micro-level dynamics when applying the ``law of
\(1/n\)'' logic to different settings.

Another plausible reason why there is no clear-cut evidence in favour or
against the ``law of \(1/n\)'' may be that there are few incentives for
the pure accumulation of knowledge in the social sciences, at least when
compared to the benefits scholars may accrue when they challenge or add
features to existing theories \citep{geddes2003paradigms}. This leads to
a reduced number of replication studies and research syntheses in the
field, although we have seen some positive changes in this respect, such
as EGAP's \emph{Metaketa Initiative}\footnote{See
\url{https://egap.org/our-work/the-metaketa-initiative} for further
information.}. Here we show that meta-analyses provide a viable path
towards knowledge-building in our discipline. Although aggregating
observational -- instead of experimental -- data can be especially
challenging, we believe that research synthesis methods play an
essential role in advancing our understanding of complex political
phenomena.

Our analyses suggest other avenues for further research. First, our
study sample did not include articles that evaluate the association
between the natural logarithm of lower chamber size and public
expenditure per capita, or between upper house size and log expenditure
per capita. New work on that area might clarify some of the
inconsistencies we find here. Second, despite the inclusion of several
moderators in our models, aggregate results still show considerable
heterogeneity. Domestic factors such as party dynamics or gerrymandering
\citep{lee2015supermajority, mukherjee2003politicalparties, gilligan2006public}
may prove useful in explaining those divergent results. Third, authors
should leverage natural and quasi-experiments to assess whether the
current results hold when systematically tested. Fortunately, this may
also be a trend under way, as all four studies using regression
discontinuity designs in our sample were published within less than 10
years prior to this meta-analysis. These suggestions may help scholars
to validate the robustness of their findings and policy-makers to reach
an optimal balance between sound fiscal policy and the demands for
increased political representation.

\hypertarget{backmatter-headings}{%
\section{Backmatter Headings}\label{backmatter-headings}}

\begin{itemize}
\item
  \textbf{Supplementary Materials}: The supplementary materials for this
  paper can be found at \url{https://URL_JOURNAL_HERE}.
\item
  \textbf{Data Availability Statement}: Replication data for this paper
  can be found at \url{https://doi.org/10.7910/DVN/5DEGYP}. Replication
  materials are also available at
  \url{https://github.com/danilofreire/legislature-size-meta-analysis}.
\item
  \textbf{Acknowledgements}: The authors thank Guilherme Duarte, Cathy
  Hafer, Robert Myles McDonnell, David Skarbek, and Howard Rosenthal for
  their constructive feedback. We also thank Cedric Antunes, Luis
  Castro, Giovanna França, Julia Oriente, and Lucas Mingardi for their
  excellent research assistance.
\item
  \textbf{Author Contributions}: Freire, Mignozzetti, and Roman
  contributed equally to all parts of the manuscript. Alptekin helped
  collect data in the early stages of the project.
\item
  \textbf{Financial Support}: We kindly acknowledge funding from the São
  Paulo State Science Foundation (FAPESP), grant number 2018/00646-1.
\item
  \textbf{Competing Interests}: None.
\end{itemize}

\newpage
\setlength{\parindent}{0cm}
\setlength{\parskip}{5pt}

\nocite{datasetCite, baskaran2013coalition, bradbury2009spatially, drew2017price,
erler2007termlimits, fiorino2007legislature, hohmann2017effect,
kessler2014communication, lewis2019legislature, lledo2003electoral,
mukherjee2003politicalparties, petterssonlidbom2012size, schaltegger2009large,
stein1998institutional, mukherjee2003politicalparties, macdonald2008impact,
matsusaka2005endogeneity, ricciuti2004legislatures, coate2011government}

% More bibliography
\bibliography{references.bib}

\end{document}

### 2022-09-16 article/article.Rmd
commit final touches paper

@@
 
-[^umberto]: Visiting Assistant Professor, Quantitative Theory and Methods Department, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>. Corresponding author.
+[^umberto]: Assistant Teaching Professor, Department of Political Science and Computational Social Sciences Program, University of California, San Diego, <umbertomig@ucsd.edu>, <http://umbertomig.com>.
+Corresponding author.
 

### 2022-09-16 article/article.tex
commit final touches paper

@@
   \url{https://danilofreire.github.io}.} \and Umberto
-Mignozzetti\footnote{Visiting Assistant Professor, Quantitative Theory
-  and Methods Department, Emory University,
-  \href{mailto:umberto.mignozzetti@emory.edu}{\nolinkurl{umberto.mignozzetti@emory.edu}},
+Mignozzetti\footnote{Assistant Teaching Professor, Department of
+  Political Science and Computational Social Sciences Program,
+  University of California, San Diego,
+  \href{mailto:umbertomig@ucsd.edu}{\nolinkurl{umbertomig@ucsd.edu}},
   \url{http://umbertomig.com}. Corresponding author.} \and Catarina
